### 2014-01-22 intro.tex
Provisional intro.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{Introduction}
\label{sec:intro}

(Something about the importance of IFC).

One barrier to the adoption of information flow control has been the
fact that it often incurs a large performance cost.  This usually stems
from the fact that most existing programming languages do not have
facilities for enforcing isolation.  Thus information flow control
checks must be applied at a very fine-grained level, e.g.\ all values in
the system must be labeled, resulting in large overhead for ordinary
operations.

Motivated by these problems, there has been increasing interest in
coarse-grained IFC systems, which trade-off precision for reduced
overhead.  These systems are characterized by floating label associated
with a thread of execution, so that access to labeled data taints the
entire thread, solving the problem of flow-sensitivity.  Typically,
these systems require strong isolation between threads, which previously
has been enforced by the type system. (LIO)  This has made this method
difficult to apply to languages which are unable to statically enforce
such strong isolation.

In this paper, we describe a simple but general methodology for using
isolation of \emph{execution contexts}, e.g.\ an instance of the
JavaScript engine, in order to add information-flow control to an
existing language.  This is a very practical approach, as there are many
languages which have built-in capabilities for dynamically enforced
strong isolation (i.e. Web Workers).  To validate this methodology, we
describe its application to Haskell (LIO), to JavaScript (Browbound), to
C (HipStar) and to Java (Aeolis).  The essential idea is to combine the
formal models of the source language and a minimal IFC language, using
the embedding technique described in Matthews and Findler '07.

Our contributions are as follows:

\begin{itemize}
    \item We define a minimal IFC language which describes the essence
        of coarse-grained information flow control.

    \item We describe how to combine this IFC language with an existing
        source language in the style of Matthews-Findler, with a twist:
        there are arbitrarily many copies of the source language, which
        do not share execution contexts.  Mediating between these languages
        requires serialization of some sort (we make this notion precise
        in our paper), making our combined system a distributed one.

    \item We carry out this methodology on four existing languages, and
        show its adequacy with respect to systems that were specialized
        for these languages.  In particular, our definitions are general
        enough to enable relaxed isolation when the source language is
        able to give stronger static guarantees.

    \item We show how to extend the Matthews-Findler method from just
        languages that are not simply expressions evaluating to values,
        but may be collections of threads executing nondeterministically.
\end{itemize}

### 2014-01-22 intro.tex
Make it compile
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Not really dynamically forced isolation
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 existing language.  This is a very practical approach, as there are many
-languages which have built-in capabilities for dynamically enforced
-strong isolation (i.e. Web Workers).  To validate this methodology, we
-describe its application to Haskell (LIO), to JavaScript (Browbound), to
-C (HipStar) and to Java (Aeolis).  The essential idea is to combine the
-formal models of the source language and a minimal IFC language, using
-the embedding technique described in Matthews and Findler '07.
+languages which have built-in capabilities for strong isolation by
+forking an execution context (i.e. Web Workers).  To validate this
+methodology, we describe its application to Haskell (LIO), to JavaScript
+(Browbound), to C (HipStar) and to Java (Aeolis).  The essential idea is
+to combine the formal models of the source language and a minimal IFC
+language, using the embedding technique described in Matthews and
+Findler '07.
 
@@
 \end{itemize}
+
+The organization of the paper is as follows: first, we describe how to
+add information flow control to JavaScript, showing the general outline of
+our procedure. Next, we describe the procedure in generality.  Finally, we
+apply the procedure to a number of systems.

### 2014-01-22 ifc.tex
Add more scaffold
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{The methodology (XXX fix title)}
\label{sec:methodology}

We now formally state our information-flow control transformation.  For
simplicity's sake, we consider only single-threaded source languages,
whose primary notion of execution is evaluation of an expression into a
value.  (Later, we consider how to accomodate systems which have
semantics for concurrent execution.)

\subsection{A tiny information-flow control calculus}

Our first task is to define a information-flow control mini-language
which will be combined with the source language. (Reference)  This
language is not Turing-complete; this is intentional, as (1) the ability
to call across the language boundary means that any control flow can be
implemented in the source language, and (2) it simplifies the
non-interference proof.  The language has a very simple set of typing
rules.  The operational semantics for this language are worth remarking
on (write a bit about how this IFC system works).  We can now state and
prove a simple non-interference theorem about this language:

\begin{theorem}
(Statement of noninterference)
\end{theorem}
\begin{proof}
XXX TODO should be simple
\end{proof}

\subsection{Combination (XXX)}

### 2014-01-30 paper/javascript.tex
Move paper to /paper.

\section{Example: JavaScript}
\label{sec:javascript}

(NB:\ the JS spec refers to execution context and state; when we refer to
execution context, we refer to both the context AND the state)

(Some background on JavaScript versus ECMAScript, since ECMAScript
constitutes the semantics we're actually going to combine with
IFC;\ everything else has to be locked down or made IFC-specific).

(Lay out how ECMAScript semantics work. Execution context and syntax.
Don't go into too much detail.  Point out that the execution context/state
corresponds implementation-wise to a JavaEngine)

(Minimal IFC fragment.  Actually, this wants to be in the general section.
So specialize this some more?)

(Combined ECMAScript and IFC\@. Talk about serialization. Draw parallel to web
workers, note the similarity.)

### 2014-02-14 paper/example.tex
Notes from session
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{A simple embedding}
\label{sec:example}

To get the flavor for our approach, we will first show how our embedding
works for a simple, ML-like language, with references and general recursion.

\begin{figure}
\begin{verbatim}
e ::= e e
    | x
    | ref e
    | !e
    | e := e
    | fix e
    | if e then e else e
    | v

v ::= \ x . e
    | #t
    | #f
    | a
\end{verbatim}
\label{fig:ml}
\end{figure}

(Selected rules from evaluation semantics. It's typed in the usual way.)

(Maybe this section needs to get moved) Sketch how a traditional account
of IFC would go about extending these rules.  These things are:

\begin{enumerate}
    \item Extend values with labels. (Values are isolated in runtimes,
        so runtime is labeled not values)
    \item Extend semantics to have a label on the program counter.
        (Ditto, runtime is values.)
    \item Extend semantics for assignment, as addresses need labels.
        (Labeled references are internalized in IFC language, and
        traditional references are isolated in runtimes.)
    \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
        flow sensitivity by reduction.)
\end{enumerate}

% No longer describing a "minimal non-Turing complete IFC calculus",
% instead, we jump straight to the combination.

We'd like to construct a coarse-grained IFC system on top of our language.
Intuitively, programs written in the target language are running on top of
an IFC ``operating system''.  The way we will perform our embedding is
by allowing programs to perform ``syscalls'' into the IFC runtime, and
vice-versa.  The IFC runtime is responsible for performing label checks
and ensuring TSNI is not violated.

We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
the IFC language from the previous section with our example language.  Key points:

\Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
over-the-top.}

\begin{itemize}
    \item Expression and evaluation contexts are considered separately,
        so that some of our operational rules are easier to write
    \item IT/TI mediate cross-language type boundary (mention that this
        is where monitor failure/exceptions get handled)
\end{itemize}

First, we associate a label with every evaluation context.  Suppose you had
a function \verb|readFile|, you need to raise your label to write this
kind of program.

Motivate why we have labeled values. How to I avoid label creep problem? We
have fork. \Red{EZY shouldn't be in the ``background'' section.}

\Red{Give a fake rule with how you raise your label when you read from a file.
We give you labeled values explicitly.}

\Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
is pretty weird, why'd you do the API that way?}

\begin{verbatim}
% colored differently
e ::= fork e
    # let's do channels?
    | sendMessage e e  # asynchronous
    | receiveMessage e # registers the callback
    | label e e
    | unlabel e
    | IT e

v ::= tid
    | l
    | Labeled l v
\end{verbatim}

\Red{Prove type safety for combined language?}

\Red{Problem: synchronization primitives which are blocking. OK, talk
about this at the end. You can do whatever you want.}
% NB: the nice thing about sendMessage is we can just drop messages
% when the labels don't work out
%
% Intuitively, it would seem to me that any concurrency primitive
% would be fine, as long as you proved it safe, we don't really care.

(Full operational semantics. Provide type rules.)

\Red{What to do when you get stuck when you are about to invalidate IFC}

### 2014-02-14 paper/extensions.tex
Notes from session
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{Extensions to the IFC language}
\label{sec:extensions}

The good thing about our approach is that we are indifferent to the
functionality implemented in the IFC language: as long as you can
prove termination sensitive non-interference with the IFC language
\Red{What is the IFC language? Make sure it is written down}, you
can combine it with another target language.  In this section,
we briefly review various extensions you can make to the base IFC
language to provide IFC-aware versions of target language features.

### 2014-02-14 paper/cesk.tex
conditions on label+fork; CSK -> CESK

\section{Generalizing to a CESK machine}
\label{sec:cesk}

Why is CSK not enough? Well if we want to write a correct condition
for label we need to make sure that if the target language is say just
STLC, then a lambda term that captures variables is properly handled.

(Definition of CESK)

Control-State-Environment-Kontinuations

** Insert definition from plt redex book **
We consider languages that can be modeled using imperatice SOS, with
an explicit store and evaluation contexts.

\paragraph{Conditions on label}
$\forall
\TE,
\Istore_1, \Il_1, \Ic_1,
\Istore_2, \Il_2, \Ic_2.
\Iconf{\Istore_1}{\Il_1}{\Ic_1}{\inTE{\Tv}} \Tarrow^* k
\Leftrightarrow              
\Iconf{\Tstore_2}{\Il_2}{\Ic_2}{\inTE{\Tv}} \Tarrow^* k
$
and\\
$
\Iconf{\Istore_1}{\Il_1}{\Ic_1}{\inTE{\Tv}} \Tarrow^*
\Iconf{\Istore'}{\Il'}{\Ic'}{\diverge}
\Leftrightarrow              
\Iconf{\Tstore_2}{\Il_2}{\Ic_2}{\inTE{\Tv}} \Tarrow^*
\Iconf{\Istore'}{\Il'}{\Ic'}{\diverge}
$

\begin{enumerate}
 \item What is this saying? In any evaluation context $\TE$ the value
 \Tv reduces to the same configuration regardless of the store (and
 environment).
 \item We must consider the evaluation in the combined language; this
 e.g., allows labeling already-labeled values.
 \item The typing rule $\forall \Delta, \Gamma. \Delta;\Gamma \vdash
 \Tv : \tau$ is necessary when we want to preserve the type of \Tv,
 but no sufficient (e.g., can have same values of same type, but
 different value in the store; hence, we also need the SOS condition).
 \item The stronger condition: $\cdot \vdash \Tv : \tau$ implies the
 SOS condition.
\end{enumerate}

\paragraph{Conditions on fork}
If we do not allow sharing of state between threads then there is no
SOS condition for fork. We don't care if the term gets stuck in the
new thread because $\Tklone$ removed elements. However, we do need a
condition when we consider typed systems. The condition for this is
given in the typing rule for fork:
%\Ifork{\Il'}{(\IT{\Te})})
\begin{mathpar}
\inferrule
{
\Delta; \Gamma \vdash \Ie_1 : l\\
\Tklone_\Delta(\Delta); \Gamma \vdash \Ie_2 : \tau
}
{
\Delta; \Gamma \vdash \Ifork{\Ie_1}{\Ie_2} : \tau
}
\end{mathpar}

### 2014-02-14 paper/example.tex
conditions on label+fork; CSK -> CESK

@@
 
+Background talks about IFC calculus in general; here we talk about
+embedding and give the precise semantics for the IFC embedding.
+
 \Red{Give a fake rule with how you raise your label when you read from a file.
@@
 \Red{What to do when you get stuck when you are about to invalidate IFC}
+
+Which rules do we want to talk about?
+
+\begin{enumerate}
+\item fork: most complicated; shows side-condition (what do we do with stores on fork?)
+\item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
+\item unlabel: shows raising of label
+\item sendMessage: will give type for (maybe encapsulate queue in env)
+\end{enumerate}

### 2014-02-14 paper/cesk.tex
send/recv

@@
 \end{mathpar}
+
+\Red{ds: Should we consider the case where the state is shared among
+threads? If so, then we need to actually give an SOS condition. For
+Browbound we don't need this because this model would correspond to
+the event loop and we have our threads running with different global;
+of course message handlers do share state, but we can handle this case
+without changes (I think)}

### 2014-02-14 paper/cesk.tex
idea of guard on what can be labeled from the target language

@@
  different value in the store; hence, we also need the SOS condition).
- \item The stronger condition: $\cdot \vdash \Tv : \tau$ implies the
- SOS condition.
+ \item The simpler condition: $\cdot \vdash \Tv : \tau$ for typed
+ langauges may be easier to user; in this case the embedder needs to
+ only prove that this implies the SOS condition.
+ \item Really we want to add a meta-level function $\nu: \Tv
+ \rightharpoonup \Tv$; this allows adding more ``guards'' for what can
+ be labled. In the case of Browbound, $\nu$ can, for example, throw an
+ exception if the value is not a string, thus forcing the programmer
+ to only pass in stringyfied data. In turn, proving that the condition
+ holds for this subset of values (strings) is trivial.
+
 \end{enumerate}

### 2014-02-20 paper/concrete.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff

\section{Concrete implementation}
\label{sec:concrete}

### 2014-02-20 paper/monad.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff

\section{Monadic interpretation}
\label{sec:monad}

### 2014-02-20 paper/real.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff

--- 2014-01-30 paper/javascript.tex
@@
-\section{Example: JavaScript}
-\label{sec:javascript}
+\section{Real world languages}
+\label{sec:real}
+\cut{
+
+\subsection{Example: JavaScript}
+\label{sec:real:javascript}
 
@@
 corresponds implementation-wise to a JavaEngine)
-
+g
 (Minimal IFC fragment.  Actually, this wants to be in the general section.
@@
 
-(Combined ECMAScript and IFC\@. Talk about serialization. Draw parallel to web
+(Combined ECMAScript and IFC. Talk about serialization. Draw parallel to web
 workers, note the similarity.)
+}

### 2014-02-20 paper/retrofit.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff

--- 2014-02-14 paper/example.tex
@@
-\section{A simple embedding}
-\label{sec:example}
+\section{Retrofitting languages with IFC}
+\label{sec:retrofit}
+\cut{
 
@@
 \end{enumerate}
+
+\subsection{The methodology (XXX fix title)}
+\label{sec:methodology}
+
+We now formally state our information-flow control transformation.  For
+simplicity's sake, we consider only single-threaded source languages,
+whose primary notion of execution is evaluation of an expression into a
+value.  (Later, we consider how to accomodate systems which have
+semantics for concurrent execution.)
+
+\subsection{A tiny information-flow control calculus}
+
+\begin{figure}[h]
+\begin{align*}
+\textrm{Thread \#:}   && \Ii          &   \\
+\textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
+\textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
+                                        \ |\ \ifc{\glb}
+                                        \ |\ \ifc{\flows}\\
+\textrm{Value:}       && \Iv          & ::=  \Itrue 
+                                        \ |\ \Ifalse
+                                        \ |\ \Iunit
+                                        \ |\ \Il
+                                        \ |\ \Ierr
+                                        \ |\ \Ii\\
+%                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
+\textrm{Expression:}  && \Ie          & ::=  \Iv
+                                        \ |\ \Ilop{\Ie}{\Ie}
+                                        \ |\ \IgetLabel
+                                        \ |\ \IgetClr\\&&&
+                                        \ |\ \Ifork{\Ie}{\Ie}
+                                        \ |\ \IT{\Te}\\
+\textrm{Context:}     && \IE          & ::=  \Ihole{\ }
+                                        \ |\ \Ilop{\IE}{\Ie}
+                                        \ |\ \Ilop{\Iv}{\IE}\\&&&
+                                        \ |\ \Ifork{\IE}{\Ie}
+                                        \ |\ \Ifork{\Iv}{\IE}
+                                        \ |\ \IT{\TE}\\
+\textrm{Store (of target language):} && \Istore\\
+\textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
+\end{align*}
+% reduction rules
+\begin{mathpar}
+
+\inferrule[I-target]{
+  \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
+  \Tarrow
+  \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
+  \\
+  \TIstore{\Tstore}{\Tenv} = \Istore
+  \\
+  \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
+}
+{
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
+  \Iarrow
+  \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
+}
+
+\and
+
+\inferrule[I-boundary]{ }
+{
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
+  \Iarrow
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
+}
+
+\and
+
+\inferrule[I-label]{ }
+{
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
+  \Iarrow
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
+}
+
+\and
+
+\inferrule[I-clearance]{ }
+{
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
+  \Iarrow
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
+}
+
+% fork
+\inferrule[I-fork]
+{ 
+  \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
+  \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
+  \ifc{\Istore'} = \Tklone(\Istore)\\
+}
+{
+  \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
+    \inTE{\TI{
+      (\Ifork{\Il'}{(\IT{\Te})})
+    }}
+  }
+  \Itasksep\cdots
+  %
+  \Iarrow
+  %
+  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
+  \Itasksep\cdots\Itasksep
+  \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
+  \Itasksep\cdots
+}{\operatorname{fresh}(\Ii)}
+
+\end{mathpar}
+
+\caption{IFC calculus}
+\end{figure}
+
+\begin{figure}[h]
+\begin{align*}
+\textrm{Address:}     && \Ta          & \\
+\textrm{Variable:}    && \Tx          & \\
+\textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
+\textrm{Expression:}  && \Te          & ::=  \Tv
+                                        \ |\ \Tlambda{\Tx}{\Te}
+                                        \ |\ \Tx
+                                        \ |\ \Te\ \Te
+                                        \ |\ \Tset{\Te}{\Te}
+                                        \ |\ \TI{\Ie}\\
+\textrm{Context:}     && \TE          & ::=  \Thole{\ }
+                                        \ |\ \TE\ \Te
+                                        \ |\ \Tv\ \TE\\&&&
+                                        \ |\ \Tset{\TE}{\Te}
+                                        \ |\ \Tset{\Tx}{\TE}
+                                        \ |\ \TI{\IE}\\
+\textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
+\textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
+\textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
+\end{align*}
+% reduction rules
+\begin{mathpar}
+
+% lambda to closure
+\inferrule[T-lam]{ }
+{
+\Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
+\Tarrow
+\Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
+}
+
+\and
+
+% lookup variable
+\inferrule[T-var]{ }
+{
+\Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
+\Tarrow
+\Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
+}
+
+\and
+
+% beta reduction
+\inferrule[T-$\beta$]
+{
+\tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
+\tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
+}
+{
+\Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
+\Tarrow
+\Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
+}{\operatorname{fresh}(\Ta)}
+
+\and
+
+% set!
+\inferrule[T-set]
+{
+\tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
+}
+{
+\Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
+\Tarrow
+\Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
+}
+% fork
+%\inferrule[E-fork]
+%{ 
+%\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
+%\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
+%\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
+%\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
+%}
+%{
+%\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
+%      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
+%}}}\|\cdots
+%\to
+%\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
+%\Iconf{\Il}{\Il}{\inE{
+%}}\|\cdots
+%}{fresh(\Ii)}
+
+\end{mathpar}
+\caption{Simple calculus}
+\end{figure}
+
+Our first task is to define a information-flow control mini-language
+which will be combined with the source language. (Reference)  This
+language is not Turing-complete; this is intentional, as (1) the ability
+to call across the language boundary means that any control flow can be
+implemented in the source language, and (2) it simplifies the
+non-interference proof.  The language has a very simple set of typing
+rules.  The operational semantics for this language are worth remarking
+on (write a bit about how this IFC system works).  We can now state and
+prove a simple non-interference theorem about this language:
+
+\begin{theorem}
+(Statement of noninterference)
+\end{theorem}
+\begin{proof}
+XXX TODO should be simple
+\end{proof}
+
+\subsection{Combination (XXX)}
+
+}

### 2014-02-20 paper/retrofit.tex
mini ml

@@
 \label{sec:retrofit}
-\cut{
+
+We consider language of the form |(S, E, e, -->)|, where |S| is some
+global state, |E| is an evaluation context, |e| is an expression in
+the language and |-->| is the reduction relation on the state,
+evaluation context and expression;
+we say expression |e| in context |E| and state |S| reduces to
+expression |e'| in context |E'| and state |S'| and write
+|conf S (E[e]) --> conf S' (E'[e'])|.
 
@@
 \begin{figure}
-\begin{verbatim}
-e ::= e e
-    | x
-    | ref e
-    | !e
-    | e := e
-    | fix e
-    | if e then e else e
-    | v
+\begin{code}
+tv   ::= \x.te | true | false | ta
+te   ::= tv | x | te te | if te then te else te | ref te | !te | te := te | diverge
+tE   ::= tE te | tv tE | if tE then te else te
+       | ref tE | !tE | tE := te | tv := tE
 
-v ::= \ x . e
-    | #t
-    | #f
-    | a
-\end{verbatim}
+te1 ; te2           @= (\x.te2) te1  where  x notmember FV(te2)
+let x = te1 in te2  @= (\x.te2) te1
+\end{code}
+
+\begin{mathpar}
+\inferrule[T-app]
+{ } {| conf tS (tE[(\x.te) tv]) --> conf tS (tE[{tv/x} tv]) |}
+
+\and
+\inferrule[T-ifTrue]
+{ } {| conf tS (tE[if true then te1 else te2]) --> conf tS (tE[te1]) |}
+
+\and
+\inferrule[T-ifFalse]
+{ } {| conf tS (tE[if false then te1 else te2]) --> conf tS (tE[te2]) |}
+
+\and
+\inferrule[T-ref]
+{| tS' = tS [ ta mapsto tv ] |} 
+{| conf tS (tE[ref tv]) --> conf tS' (tE[tv]) |}
+{| fresh ta |}
+
+\and
+\inferrule[T-deref]
+{| (ta, tv) member tS |}
+{| conf tS (tE[!ta]) --> conf tS (tE[tv]) |}
+
+\and
+\inferrule[T-ass]
+{| tS' = tS [ ta mapsto tv ] |} 
+{| conf tS (tE[ta := tv]) --> conf tS' (tE[tv]) |}
+\end{mathpar}
+
+\caption{Simple ML-like language}
 \label{fig:ml}
@@
 
+\cut{
 (Selected rules from evaluation semantics. It's typed in the usual way.)

### 2014-02-20 paper/retrofit.tex
first draft of semantics

@@
 \inferrule[T-app]
-{ } {| conf tS (tE[(\x.te) tv]) --> conf tS (tE[{tv/x} tv]) |}
+{ } {| conf tS (intE ((\x.te) tv)) --> conf tS (intE ({tv/x} tv)) |}
 
@@
 \inferrule[T-ifTrue]
-{ } {| conf tS (tE[if true then te1 else te2]) --> conf tS (tE[te1]) |}
+{ } {| conf tS (intE (if true then te1 else te2)) --> conf tS (intE te1) |}
 
@@
 \inferrule[T-ifFalse]
-{ } {| conf tS (tE[if false then te1 else te2]) --> conf tS (tE[te2]) |}
+{ } {| conf tS (intE (if false then te1 else te2)) --> conf tS (intE te2) |}
 
@@
 {| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (tE[ref tv]) --> conf tS' (tE[tv]) |}
+{| conf tS (intE (ref tv)) --> conf tS' (intE tv) |}
 {| fresh ta |}
@@
 {| (ta, tv) member tS |}
-{| conf tS (tE[!ta]) --> conf tS (tE[tv]) |}
+{| conf tS (intE (!ta)) --> conf tS (intE tv) |}
 
@@
 {| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (tE[ta := tv]) --> conf tS' (tE[tv]) |}
+{| conf tS (intE (ta := tv)) --> conf tS' (intE tv) |}
 \end{mathpar}
@@
 \caption{Simple ML-like language}
+\label{fig:ml}
+\end{figure}
+
+\begin{figure}
+\begin{code}
+lop  ::=  canFlowTo | lub | glb
+iv   ::=  id | il | true | false | unit
+ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
+       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
+iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
+       |  send iE ie ie | send iv iE ie | send iv iv iE
+       |  x, y <= recv. ie ie |  IT tE
+
+tE   ::=  cdots | TI iE
+
+x, y <= brecv . ie @= IT (let te' = TI (x, y <= recv. ie  (IT te')) in te')
+\end{code}
+
+\begin{mathpar}
+\inferrule[I-getLabel]
+{ }
+{|
+iconf iS (lconf id il tS (iniE (getLabel)), ldots)
+-->
+iconf iS (lconf id il tS (iniE il), ldots)
+|}
+\and
+\inferrule[I-setLabel]
+{ |il canFlowTo il'| }
+{|
+iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
+-->
+iconf iS (lconf id il' tS (iniE unit), ldots)
+|}
+\and
+\inferrule[I-fork]
+{ 
+|iS' = iS [ id' mapsto nil ]|
+}
+{|
+iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
+-->
+iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
+|}
+{|fresh (id')|}
+\and
+\inferrule[I-send]
+{
+|il canFlowTo il'|\\
+|iS(id') = Q|\\
+|iS' = iS [ id' mapsto (il', id,  ie) cons Q ]|
+}
+{|
+iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
+-->
+iconf iS' (lconf id il tS (iniE unit), ldots)
+|}
+\and
+\inferrule[I-recv]
+{
+| filter il (iS(id)) = (il', id', ie') :: Q'|\\
+| iS' = iS[id mapsto Q']|
+}
+{|
+iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
+-->
+iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
+|}
+\and
+\inferrule[I-noRecv]
+{
+| filter il (iS(id)) = nil|\\
+| iS' = iS[id mapsto nil]|
+}
+{|
+iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
+-->
+iconf iS' (lconf id il tS (iniE ie2), ldots)
+|}
+\and
+\inferrule[I-border]
+{ }
+{| iniE (IT (TI (ie))) --> iniE ie |}
+\and
+\inferrule[T-border]
+{ }
+{| intE (TI (IT (te))) --> intE te |}
+\end{mathpar}
+
+\caption{IFC language}
 \label{fig:ml}

### 2014-02-20 paper/retrofit.tex
minor

@@
        |  x, y <= recv. ie ie |  IT tE
+Q    ::=  nil | (il, id, ie) :: Q
 
@@
 |iS(id') = Q|\\
-|iS' = iS [ id' mapsto (il', id,  ie) cons Q ]|
+|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
 }

### 2014-02-20 paper/retrofit.tex
color vars

@@
 \begin{code}
-tv   ::= \x.te | true | false | ta
-te   ::= tv | x | te te | if te then te else te | ref te | !te | te := te | diverge
+tv   ::= \tx.te | true | false | ta
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | diverge
 tE   ::= tE te | tv tE | if tE then te else te
@@
 
-te1 ; te2           @= (\x.te2) te1  where  x notmember FV(te2)
-let x = te1 in te2  @= (\x.te2) te1
+te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
+let tx = te1 in te2  @= (\tx.te2) te1
 \end{code}
@@
 iv   ::=  id | il | true | false | unit
-ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
-       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
+ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
+       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
 iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
        |  send iE ie ie | send iv iE ie | send iv iv iE
-       |  x, y <= recv. ie ie |  IT tE
+       |  ix1, ix2 <= recv. ie ie |  IT tE
 Q    ::=  nil | (il, id, ie) :: Q
 
+te   ::=  cdots | TI ie
 tE   ::=  cdots | TI iE
 
-x, y <= brecv . ie @= IT (let te' = TI (x, y <= recv. ie  (IT te')) in te')
+ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
 \end{code}
@@
 { 
-|iS' = iS [ id' mapsto nil ]|
+|iS' = iS [ id' mapsto nil ]|\\
+|tS' = q(tS)|
 }
 {|
-iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
+iconf iS (lconf id il tS (iniE (fork ie)), ldots)
 -->
-iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
+iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
 |}
@@
 {|
-iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
+iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
 -->
-iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
+iconf iS' (lconf id il tS (iniE ({ie'/ix1,id'/ix2} ie1)), ldots)
 |}
@@
 {|
-iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
+iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
 -->
@@
 \and
+\inferrule[I-bool]
+{ |b member {true, false}|  } {| iniE (IT b) --> iniE b |}
+\and
 \inferrule[I-border]
-{ }
-{| iniE (IT (TI (ie))) --> iniE ie |}
+{ } {| iniE (IT (TI (ie))) --> iniE ie |}
+\and
+\inferrule[T-bool]
+{ |b member {true, false}| } {| intE (TI b) --> intE b |}
 \and
 \inferrule[T-border]
-{ }
-{| intE (TI (IT (te))) --> intE te |}
+{ } {| intE (TI (IT (te))) --> intE te |}
 \end{mathpar}
@@
 
-\cut{
-(Selected rules from evaluation semantics. It's typed in the usual way.)
+The filter function |filter il Q| removes message whose labels do not
+flow to |il|. Specifically, if |Q| is the empty list |nil|, the
+function is simply the identity function, i.e.,
+|filter il nil = nil|; otherwise:
+\[
+|filter il ((il', id, ie) :: Q )| = \left\{
+\begin{array}{l l}
+|(il', id, ie) :: filter il Q| & \quad \text{if |il' canFlowTo il|}\\
+|filter il Q| & \quad \text{otherwise}
+\end{array} \right.
+\]
 
-(Maybe this section needs to get moved) Sketch how a traditional account
-of IFC would go about extending these rules.  These things are:
-
-\begin{enumerate}
-    \item Extend values with labels. (Values are isolated in runtimes,
-        so runtime is labeled not values)
-    \item Extend semantics to have a label on the program counter.
-        (Ditto, runtime is values.)
-    \item Extend semantics for assignment, as addresses need labels.
-        (Labeled references are internalized in IFC language, and
-        traditional references are isolated in runtimes.)
-    \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
-        flow sensitivity by reduction.)
-\end{enumerate}
-
-% No longer describing a "minimal non-Turing complete IFC calculus",
-% instead, we jump straight to the combination.
-
-We'd like to construct a coarse-grained IFC system on top of our language.
-Intuitively, programs written in the target language are running on top of
-an IFC ``operating system''.  The way we will perform our embedding is
-by allowing programs to perform ``syscalls'' into the IFC runtime, and
-vice-versa.  The IFC runtime is responsible for performing label checks
-and ensuring TSNI is not violated.
-
-We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
-the IFC language from the previous section with our example language.  Key points:
-
-\Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
-over-the-top.}
-
-\begin{itemize}
-    \item Expression and evaluation contexts are considered separately,
-        so that some of our operational rules are easier to write
-    \item IT/TI mediate cross-language type boundary (mention that this
-        is where monitor failure/exceptions get handled)
-\end{itemize}
-
-First, we associate a label with every evaluation context.  Suppose you had
-a function \verb|readFile|, you need to raise your label to write this
-kind of program.
-
-Motivate why we have labeled values. How to I avoid label creep problem? We
-have fork. \Red{EZY shouldn't be in the ``background'' section.}
-
-Background talks about IFC calculus in general; here we talk about
-embedding and give the precise semantics for the IFC embedding.
-
-\Red{Give a fake rule with how you raise your label when you read from a file.
-We give you labeled values explicitly.}
-
-\Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
-is pretty weird, why'd you do the API that way?}
-
-\begin{verbatim}
-% colored differently
-e ::= fork e
-    # let's do channels?
-    | sendMessage e e  # asynchronous
-    | receiveMessage e # registers the callback
-    | label e e
-    | unlabel e
-    | IT e
-
-v ::= tid
-    | l
-    | Labeled l v
-\end{verbatim}
-
-\Red{Prove type safety for combined language?}
-
-\Red{Problem: synchronization primitives which are blocking. OK, talk
-about this at the end. You can do whatever you want.}
-% NB: the nice thing about sendMessage is we can just drop messages
-% when the labels don't work out
-%
-% Intuitively, it would seem to me that any concurrency primitive
-% would be fine, as long as you proved it safe, we don't really care.
-
-(Full operational semantics. Provide type rules.)
-
-\Red{What to do when you get stuck when you are about to invalidate IFC}
-
-Which rules do we want to talk about?
-
-\begin{enumerate}
-\item fork: most complicated; shows side-condition (what do we do with stores on fork?)
-\item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
-\item unlabel: shows raising of label
-\item sendMessage: will give type for (maybe encapsulate queue in env)
-\end{enumerate}
-
-\subsection{The methodology (XXX fix title)}
-\label{sec:methodology}
-
-We now formally state our information-flow control transformation.  For
-simplicity's sake, we consider only single-threaded source languages,
-whose primary notion of execution is evaluation of an expression into a
-value.  (Later, we consider how to accomodate systems which have
-semantics for concurrent execution.)
-
-\subsection{A tiny information-flow control calculus}
-
-\begin{figure}[h]
-\begin{align*}
-\textrm{Thread \#:}   && \Ii          &   \\
-\textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
-\textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
-                                        \ |\ \ifc{\glb}
-                                        \ |\ \ifc{\flows}\\
-\textrm{Value:}       && \Iv          & ::=  \Itrue 
-                                        \ |\ \Ifalse
-                                        \ |\ \Iunit
-                                        \ |\ \Il
-                                        \ |\ \Ierr
-                                        \ |\ \Ii\\
-%                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
-\textrm{Expression:}  && \Ie          & ::=  \Iv
-                                        \ |\ \Ilop{\Ie}{\Ie}
-                                        \ |\ \IgetLabel
-                                        \ |\ \IgetClr\\&&&
-                                        \ |\ \Ifork{\Ie}{\Ie}
-                                        \ |\ \IT{\Te}\\
-\textrm{Context:}     && \IE          & ::=  \Ihole{\ }
-                                        \ |\ \Ilop{\IE}{\Ie}
-                                        \ |\ \Ilop{\Iv}{\IE}\\&&&
-                                        \ |\ \Ifork{\IE}{\Ie}
-                                        \ |\ \Ifork{\Iv}{\IE}
-                                        \ |\ \IT{\TE}\\
-\textrm{Store (of target language):} && \Istore\\
-\textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
-\end{align*}
-% reduction rules
-\begin{mathpar}
-
-\inferrule[I-target]{
-  \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
-  \Tarrow
-  \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
-  \\
-  \TIstore{\Tstore}{\Tenv} = \Istore
-  \\
-  \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
-}
-{
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
-  \Iarrow
-  \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
-}
-
-\and
-
-\inferrule[I-boundary]{ }
-{
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
-  \Iarrow
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
-}
-
-\and
-
-\inferrule[I-label]{ }
-{
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
-  \Iarrow
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
-}
-
-\and
-
-\inferrule[I-clearance]{ }
-{
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
-  \Iarrow
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
-}
-
-% fork
-\inferrule[I-fork]
-{ 
-  \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
-  \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
-  \ifc{\Istore'} = \Tklone(\Istore)\\
-}
-{
-  \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
-    \inTE{\TI{
-      (\Ifork{\Il'}{(\IT{\Te})})
-    }}
-  }
-  \Itasksep\cdots
-  %
-  \Iarrow
-  %
-  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
-  \Itasksep\cdots\Itasksep
-  \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
-  \Itasksep\cdots
-}{\operatorname{fresh}(\Ii)}
-
-\end{mathpar}
-
-\caption{IFC calculus}
-\end{figure}
-
-\begin{figure}[h]
-\begin{align*}
-\textrm{Address:}     && \Ta          & \\
-\textrm{Variable:}    && \Tx          & \\
-\textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
-\textrm{Expression:}  && \Te          & ::=  \Tv
-                                        \ |\ \Tlambda{\Tx}{\Te}
-                                        \ |\ \Tx
-                                        \ |\ \Te\ \Te
-                                        \ |\ \Tset{\Te}{\Te}
-                                        \ |\ \TI{\Ie}\\
-\textrm{Context:}     && \TE          & ::=  \Thole{\ }
-                                        \ |\ \TE\ \Te
-                                        \ |\ \Tv\ \TE\\&&&
-                                        \ |\ \Tset{\TE}{\Te}
-                                        \ |\ \Tset{\Tx}{\TE}
-                                        \ |\ \TI{\IE}\\
-\textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
-\textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
-\textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
-\end{align*}
-% reduction rules
-\begin{mathpar}
-
-% lambda to closure
-\inferrule[T-lam]{ }
-{
-\Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
-\Tarrow
-\Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
-}
-
-\and
-
-% lookup variable
-\inferrule[T-var]{ }
-{
-\Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
-\Tarrow
-\Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
-}
-
-\and
-
-% beta reduction
-\inferrule[T-$\beta$]
-{
-\tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
-\tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
-}
-{
-\Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
-\Tarrow
-\Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
-}{\operatorname{fresh}(\Ta)}
-
-\and
-
-% set!
-\inferrule[T-set]
-{
-\tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
-}
-{
-\Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
-\Tarrow
-\Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
-}
-% fork
-%\inferrule[E-fork]
-%{ 
-%\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
-%\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
-%\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
-%\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
-%}
-%{
-%\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
-%      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
-%}}}\|\cdots
-%\to
-%\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
-%\Iconf{\Il}{\Il}{\inE{
-%}}\|\cdots
-%}{fresh(\Ii)}
-
-\end{mathpar}
-\caption{Simple calculus}
-\end{figure}
-
-Our first task is to define a information-flow control mini-language
-which will be combined with the source language. (Reference)  This
-language is not Turing-complete; this is intentional, as (1) the ability
-to call across the language boundary means that any control flow can be
-implemented in the source language, and (2) it simplifies the
-non-interference proof.  The language has a very simple set of typing
-rules.  The operational semantics for this language are worth remarking
-on (write a bit about how this IFC system works).  We can now state and
-prove a simple non-interference theorem about this language:
-
-\begin{theorem}
-(Statement of noninterference)
-\end{theorem}
-\begin{proof}
-XXX TODO should be simple
-\end{proof}
-
-\subsection{Combination (XXX)}
-
-}
+%% \cut{
+%% (Selected rules from evaluation semantics. It's typed in the usual way.)
+%% 
+%% (Maybe this section needs to get moved) Sketch how a traditional account
+%% of IFC would go about extending these rules.  These things are:
+%% 
+%% \begin{enumerate}
+%%     \item Extend values with labels. (Values are isolated in runtimes,
+%%         so runtime is labeled not values)
+%%     \item Extend semantics to have a label on the program counter.
+%%         (Ditto, runtime is values.)
+%%     \item Extend semantics for assignment, as addresses need labels.
+%%         (Labeled references are internalized in IFC language, and
+%%         traditional references are isolated in runtimes.)
+%%     \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
+%%         flow sensitivity by reduction.)
+%% \end{enumerate}
+%% 
+%% % No longer describing a "minimal non-Turing complete IFC calculus",
+%% % instead, we jump straight to the combination.
+%% 
+%% We'd like to construct a coarse-grained IFC system on top of our language.
+%% Intuitively, programs written in the target language are running on top of
+%% an IFC ``operating system''.  The way we will perform our embedding is
+%% by allowing programs to perform ``syscalls'' into the IFC runtime, and
+%% vice-versa.  The IFC runtime is responsible for performing label checks
+%% and ensuring TSNI is not violated.
+%% 
+%% We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
+%% the IFC language from the previous section with our example language.  Key points:
+%% 
+%% \Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
+%% over-the-top.}
+%% 
+%% \begin{itemize}
+%%     \item Expression and evaluation contexts are considered separately,
+%%         so that some of our operational rules are easier to write
+%%     \item IT/TI mediate cross-language type boundary (mention that this
+%%         is where monitor failure/exceptions get handled)
+%% \end{itemize}
+%% 
+%% First, we associate a label with every evaluation context.  Suppose you had
+%% a function \verb|readFile|, you need to raise your label to write this
+%% kind of program.
+%% 
+%% Motivate why we have labeled values. How to I avoid label creep problem? We
+%% have fork. \Red{EZY shouldn't be in the ``background'' section.}
+%% 
+%% Background talks about IFC calculus in general; here we talk about
+%% embedding and give the precise semantics for the IFC embedding.
+%% 
+%% \Red{Give a fake rule with how you raise your label when you read from a file.
+%% We give you labeled values explicitly.}
+%% 
+%% \Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
+%% is pretty weird, why'd you do the API that way?}
+%% 
+%% \begin{verbatim}
+%% % colored differently
+%% e ::= fork e
+%%     # let's do channels?
+%%     | sendMessage e e  # asynchronous
+%%     | receiveMessage e # registers the callback
+%%     | label e e
+%%     | unlabel e
+%%     | IT e
+%% 
+%% v ::= tid
+%%     | l
+%%     | Labeled l v
+%% \end{verbatim}
+%% 
+%% \Red{Prove type safety for combined language?}
+%% 
+%% \Red{Problem: synchronization primitives which are blocking. OK, talk
+%% about this at the end. You can do whatever you want.}
+%% % NB: the nice thing about sendMessage is we can just drop messages
+%% % when the labels don't work out
+%% %
+%% % Intuitively, it would seem to me that any concurrency primitive
+%% % would be fine, as long as you proved it safe, we don't really care.
+%% 
+%% (Full operational semantics. Provide type rules.)
+%% 
+%% \Red{What to do when you get stuck when you are about to invalidate IFC}
+%% 
+%% Which rules do we want to talk about?
+%% 
+%% \begin{enumerate}
+%% \item fork: most complicated; shows side-condition (what do we do with stores on fork?)
+%% \item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
+%% \item unlabel: shows raising of label
+%% \item sendMessage: will give type for (maybe encapsulate queue in env)
+%% \end{enumerate}
+%% 
+%% \subsection{The methodology (XXX fix title)}
+%% \label{sec:methodology}
+%% 
+%% We now formally state our information-flow control transformation.  For
+%% simplicity's sake, we consider only single-threaded source languages,
+%% whose primary notion of execution is evaluation of an expression into a
+%% value.  (Later, we consider how to accomodate systems which have
+%% semantics for concurrent execution.)
+%% 
+%% \subsection{A tiny information-flow control calculus}
+%% 
+%% \begin{figure}[h]
+%% \begin{align*}
+%% \textrm{Thread \#:}   && \Ii          &   \\
+%% \textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
+%% \textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
+%%                                         \ |\ \ifc{\glb}
+%%                                         \ |\ \ifc{\flows}\\
+%% \textrm{Value:}       && \Iv          & ::=  \Itrue 
+%%                                         \ |\ \Ifalse
+%%                                         \ |\ \Iunit
+%%                                         \ |\ \Il
+%%                                         \ |\ \Ierr
+%%                                         \ |\ \Ii\\
+%% %                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
+%% \textrm{Expression:}  && \Ie          & ::=  \Iv
+%%                                         \ |\ \Ilop{\Ie}{\Ie}
+%%                                         \ |\ \IgetLabel
+%%                                         \ |\ \IgetClr\\&&&
+%%                                         \ |\ \Ifork{\Ie}{\Ie}
+%%                                         \ |\ \IT{\Te}\\
+%% \textrm{Context:}     && \IE          & ::=  \Ihole{\ }
+%%                                         \ |\ \Ilop{\IE}{\Ie}
+%%                                         \ |\ \Ilop{\Iv}{\IE}\\&&&
+%%                                         \ |\ \Ifork{\IE}{\Ie}
+%%                                         \ |\ \Ifork{\Iv}{\IE}
+%%                                         \ |\ \IT{\TE}\\
+%% \textrm{Store (of target language):} && \Istore\\
+%% \textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
+%% \end{align*}
+%% % reduction rules
+%% \begin{mathpar}
+%% 
+%% \inferrule[I-target]{
+%%   \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
+%%   \Tarrow
+%%   \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
+%%   \\
+%%   \TIstore{\Tstore}{\Tenv} = \Istore
+%%   \\
+%%   \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
+%% }
+%% {
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
+%%   \Iarrow
+%%   \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
+%% }
+%% 
+%% \and
+%% 
+%% \inferrule[I-boundary]{ }
+%% {
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
+%%   \Iarrow
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
+%% }
+%% 
+%% \and
+%% 
+%% \inferrule[I-label]{ }
+%% {
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
+%%   \Iarrow
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
+%% }
+%% 
+%% \and
+%% 
+%% \inferrule[I-clearance]{ }
+%% {
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
+%%   \Iarrow
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
+%% }
+%% 
+%% % fork
+%% \inferrule[I-fork]
+%% { 
+%%   \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
+%%   \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
+%%   \ifc{\Istore'} = \Tklone(\Istore)\\
+%% }
+%% {
+%%   \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
+%%     \inTE{\TI{
+%%       (\Ifork{\Il'}{(\IT{\Te})})
+%%     }}
+%%   }
+%%   \Itasksep\cdots
+%%   %
+%%   \Iarrow
+%%   %
+%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
+%%   \Itasksep\cdots\Itasksep
+%%   \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
+%%   \Itasksep\cdots
+%% }{\operatorname{fresh}(\Ii)}
+%% 
+%% 
+%% \end{mathpar}
+%% 
+%% \caption{IFC calculus}
+%% \end{figure}
+%% 
+%% \begin{figure}[h]
+%% \begin{align*}
+%% \textrm{Address:}     && \Ta          & \\
+%% \textrm{Variable:}    && \Tx          & \\
+%% \textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
+%% \textrm{Expression:}  && \Te          & ::=  \Tv
+%%                                         \ |\ \Tlambda{\Tx}{\Te}
+%%                                         \ |\ \Tx
+%%                                         \ |\ \Te\ \Te
+%%                                         \ |\ \Tset{\Te}{\Te}
+%%                                         \ |\ \TI{\Ie}\\
+%% \textrm{Context:}     && \TE          & ::=  \Thole{\ }
+%%                                         \ |\ \TE\ \Te
+%%                                         \ |\ \Tv\ \TE\\&&&
+%%                                         \ |\ \Tset{\TE}{\Te}
+%%                                         \ |\ \Tset{\Tx}{\TE}
+%%                                         \ |\ \TI{\IE}\\
+%% \textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
+%% \textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
+%% \textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
+%% \end{align*}
+%% % reduction rules
+%% \begin{mathpar}
+%% 
+%% % lambda to closure
+%% \inferrule[T-lam]{ }
+%% {
+%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
+%% \Tarrow
+%% \Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
+%% }
+%% 
+%% \and
+%% 
+%% % lookup variable
+%% \inferrule[T-var]{ }
+%% {
+%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
+%% \Tarrow
+%% \Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
+%% }
+%% 
+%% \and
+%% 
+%% % beta reduction
+%% \inferrule[T-$\beta$]
+%% {
+%% \tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
+%% \tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
+%% }
+%% {
+%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
+%% \Tarrow
+%% \Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
+%% }{\operatorname{fresh}(\Ta)}
+%% 
+%% \and
+%% 
+%% % set!
+%% \inferrule[T-set]
+%% {
+%% \tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
+%% }
+%% {
+%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
+%% \Tarrow
+%% \Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
+%% }
+%% % fork
+%% %\inferrule[E-fork]
+%% %{ 
+%% %\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
+%% %\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
+%% %\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
+%% %\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
+%% %}
+%% %{
+%% %\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
+%% %      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
+%% %}}}\|\cdots
+%% %\to
+%% %\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
+%% %\Iconf{\Il}{\Il}{\inE{
+%% %}}\|\cdots
+%% %}{fresh(\Ii)}
+%% 
+%% 
+%% \end{mathpar}
+%% \caption{Simple calculus}
+%% \end{figure}
+%% 
+%% Our first task is to define a information-flow control mini-language
+%% which will be combined with the source language. (Reference)  This
+%% language is not Turing-complete; this is intentional, as (1) the ability
+%% to call across the language boundary means that any control flow can be
+%% implemented in the source language, and (2) it simplifies the
+%% non-interference proof.  The language has a very simple set of typing
+%% rules.  The operational semantics for this language are worth remarking
+%% on (write a bit about how this IFC system works).  We can now state and
+%% prove a simple non-interference theorem about this language:
+%% 
+%% \begin{theorem}
+%% (Statement of noninterference)
+%% \end{theorem}
+%% \begin{proof}
+%% XXX TODO should be simple
+%% \end{proof}
+%% 
+%% \subsection{Combination (XXX)}
+%% 
+%% 
+%% }

### 2014-02-21 paper/retrofit.tex
minor
fix

@@
 
-We consider language of the form |(S, E, e, -->)|, where |S| is some
+We consider language of the form |(S, E, e, ->)|, where |S| is some
 global state, |E| is an evaluation context, |e| is an expression in
-the language and |-->| is the reduction relation on the state,
+the language and |->| is the reduction relation on the state,
 evaluation context and expression;
@@
 expression |e'| in context |E'| and state |S'| and write
-|conf S (E[e]) --> conf S' (E'[e'])|.
+|conf S (E[e]) -> conf S' (E'[e'])|.
+$|->| : (|S| \times |E| \times |e|) \rightharpoonup (|S| \times |E| \times |e|)$
 
@@
 \begin{mathpar}
+\and
+\inferrule[T-pure]
+{| te ~> te'|}
+{| conf tS te -> conf tS te' |}
+
+\and
 \inferrule[T-app]
-{ } {| conf tS (intE ((\x.te) tv)) --> conf tS (intE ({tv/x} tv)) |}
+{ } {| intE ((\x.te) tv) ~> intE ({tv/x} tv) |}
 
@@
 \inferrule[T-ifTrue]
-{ } {| conf tS (intE (if true then te1 else te2)) --> conf tS (intE te1) |}
+{ } {| intE (if true then te1 else te2)  ~> intE te1 |}
 
@@
 \inferrule[T-ifFalse]
-{ } {| conf tS (intE (if false then te1 else te2)) --> conf tS (intE te2) |}
+{ } {| intE (if false then te1 else te2) ~> intE te2 |}
 
@@
 \inferrule[T-ref]
-{| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (intE (ref tv)) --> conf tS' (intE tv) |}
-{| fresh ta |}
+{| tS' = tS [ ta mapsto tv ] | } 
+{| conf tS (intE (ref tv)) -> conf tS' (intE ta) |}
+{| fresh (ta) |}
 
@@
 \inferrule[T-deref]
-{| (ta, tv) member tS |}
-{| conf tS (intE (!ta)) --> conf tS (intE tv) |}
+{| tv = tS(ta) |}
+{| conf tS (intE (!ta)) -> conf tS (intE tv) |}
 
@@
 {| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (intE (ta := tv)) --> conf tS' (intE tv) |}
+{| conf tS (intE (ta := tv)) -> conf tS' (intE tv) |}
 \end{mathpar}
@@
        |  ix1, ix2 <= recv. ie ie |  IT tE
-Q    ::=  nil | (il, id, ie) :: Q
+io   ::=  (il, id ie)
+Q    ::=  nil | io :: Q
 
@@
 \begin{mathpar}
+\inferrule[I-step]
+{|
+  conf tS (intE te) -> conf tS (intE te')
+|}
+{|
+iconf iS (lconf id il tS (IT (intE te)), ldots)
+.->
+iconf iS (lconf id il tS' (IT (intE te')), ldots)
+|}
+
+\and
 \inferrule[I-getLabel]
@@
 iconf iS (lconf id il tS (iniE (getLabel)), ldots)
--->
+.->
 iconf iS (lconf id il tS (iniE il), ldots)
 |}
+
 \and
@@
 iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
--->
+.->
 iconf iS (lconf id il' tS (iniE unit), ldots)
 |}
+
 \and
@@
 |iS' = iS [ id' mapsto nil ]|\\
-|tS' = q(tS)|
+|tS' = q(tS)|\\
+|fresh (id')|
 }
@@
 iconf iS (lconf id il tS (iniE (fork ie)), ldots)
--->
+.->
 iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
 |}
-{|fresh (id')|}
+%{|fresh (id')|}
+
 \and
@@
 iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
--->
+.->
 iconf iS' (lconf id il tS (iniE unit), ldots)
 |}
+
 \and
@@
 {
-| filter il (iS(id)) = (il', id', ie') :: Q'|\\
-| iS' = iS[id mapsto Q']|
+| filter il (iS(id)) = io1 :: cdots :: iok :: (il', id', ie')|\\
+| iS' = iS[id mapsto io1 :: cdots :: iok]|\\
+| ie1'' = {ie'/ix1,id'/ix2} ie1|
 }
 {|
-iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
--->
-iconf iS' (lconf id il tS (iniE ({ie'/ix1,id'/ix2} ie1)), ldots)
+iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+.->
+iconf iS' (lconf id il tS (iniE ie1''), ldots)
 |}
+
 \and
@@
 {|
-iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
--->
+iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+.->
 iconf iS' (lconf id il tS (iniE ie2), ldots)
 |}
+
+\inferrule[I-pure]
+{| ie .~> ie'|}
+{|
+  iconf iS (lconf id il tS ie)
+.->
+  iconf iS (lconf id il tS ie)
+|}
+
 \and
-\inferrule[I-bool]
-{ |b member {true, false}|  } {| iniE (IT b) --> iniE b |}
+\inferrule[I-labelOp]
+{ |denot (il lop il') = iv|}
+{ |iniE (il lop il') .~> iniE iv| }
+
 \and
 \inferrule[I-border]
-{ } {| iniE (IT (TI (ie))) --> iniE ie |}
-\and
-\inferrule[T-bool]
-{ |b member {true, false}| } {| intE (TI b) --> intE b |}
+{ } {| iniE (IT (TI (ie))) .~> iniE ie |}
+
 \and
 \inferrule[T-border]
-{ } {| intE (TI (IT (te))) --> intE te |}
+{ } {| intE (TI (IT (te))) ~> intE te |}
 \end{mathpar}
-
-\caption{IFC language}
+\caption{IFC language nad general embedding.}
 \label{fig:ml}
@@
 \]
+
+In the case of extending
+\begin{mathpar}
+\inferrule[I-bool]
+{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
+\and
+\inferrule[T-bool]
+{ |b member {true, false}| } {| intE (TI b) -> intE b |}
+\end{mathpar}
 

### 2014-02-21 paper/retrofit.tex
minor

@@
 {| te ~> te'|}
-{| conf tS te -> conf tS te' |}
+{| conf tS (iniE te) -> conf tS (iniE te') |}
 
@@
 \inferrule[T-app]
-{ } {| intE ((\x.te) tv) ~> intE ({tv/x} tv) |}
+{ } {| (\x.te) tv ~> {tv/x} te |}
 
@@
 \inferrule[T-ifTrue]
-{ } {| intE (if true then te1 else te2)  ~> intE te1 |}
+{ } {| if true then te1 else te2  ~> te1|}
 
@@
 \inferrule[T-ifFalse]
-{ } {| intE (if false then te1 else te2) ~> intE te2 |}
+{ } {| if false then te1 else te2  ~> te2|}
 
@@
 io   ::=  (il, id ie)
-Q    ::=  nil | io :: Q
+Q    ::=  nil | io , Q
 
@@
 |iS(id') = Q|\\
-|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
+|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
 }
@@
 {
-| filter il (iS(id)) = io1 :: cdots :: iok :: (il', id', ie')|\\
-| iS' = iS[id mapsto io1 :: cdots :: iok]|\\
+| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
+| iS' = iS[id mapsto io1 , ... , iok]|\\
 | ie1'' = {ie'/ix1,id'/ix2} ie1|
@@
 {|
-  iconf iS (lconf id il tS ie)
+  iconf iS (lconf id il tS (iniE ie))
 .->
-  iconf iS (lconf id il tS ie)
+iconf iS (lconf id il tS (iniE ie))
 |}
@@
 { |denot (il lop il') = iv|}
-{ |iniE (il lop il') .~> iniE iv| }
+{ |il lop il' .~> iv| }
 
@@
 \inferrule[I-border]
-{ } {| iniE (IT (TI (ie))) .~> iniE ie |}
+{ } {| IT (TI (ie)) .~> ie |}
 
@@
 \[
-|filter il ((il', id, ie) :: Q )| = \left\{
+|filter il ((il', id, ie) , Q )| = \left\{
 \begin{array}{l l}
-|(il', id, ie) :: filter il Q| & \quad \text{if |il' canFlowTo il|}\\
+|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
 |filter il Q| & \quad \text{otherwise}

### 2014-02-21 paper/retrofit.tex
I-step2.
rm old step

@@
 {|
-  conf tS (intE te) -> conf tS (intE te')
+conf tS (te) -> conf tS' te'
 |}
 {|
-iconf iS (lconf id il tS (IT (intE te)), ldots)
+iconf iS (lconf id il tS (iniE te), ldots)
 .->
-iconf iS (lconf id il tS' (IT (intE te')), ldots)
+iconf iS (lconf id il tS' (iniE te'), ldots)
 |}

### 2014-02-21 paper/retrofit.tex
hole for e's

@@
 te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | diverge
-tE   ::= tE te | tv tE | if tE then te else te
+tE   ::= tHole | tE te | tv tE | if tE then te else te
        | ref tE | !tE | tE := te | tv := tE
@@
        |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
-iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
+iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
        |  send iE ie ie | send iv iE ie | send iv iv iE

### 2014-02-21 paper/retrofit.tex
fix step

@@
 {|
-iconf iS (lconf id il tS (iniE te), ldots)
+iconf iS (lconf id il tS (iniE (IT te)), ldots)
 .->
-iconf iS (lconf id il tS' (iniE te'), ldots)
+iconf iS (lconf id il tS' (iniE (IT te')), ldots)
 |}

### 2014-02-21 paper/retrofit.tex
idiot typo
minor

@@
 
-We consider language of the form |(S, E, e, ->)|, where |S| is some
-global state, |E| is an evaluation context, |e| is an expression in
-the language and |->| is the reduction relation on the state,
-evaluation context and expression;
-we say expression |e| in context |E| and state |S| reduces to
-expression |e'| in context |E'| and state |S'| and write
-|conf S (E[e]) -> conf S' (E'[e'])|.
-$|->| : (|S| \times |E| \times |e|) \rightharpoonup (|S| \times |E| \times |e|)$
+We consider languages in the form of abstract state machines |(tS, tE,
+te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
+context, |te| is an expression in the language and |->| is the
+reduction relation on such configuration, i.e., $|->| : (|tS| \times
+|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$
 
@@
 {| te ~> te'|}
-{| conf tS (iniE te) -> conf tS (iniE te') |}
+{| conf tS (intE te) -> conf tS (intE te') |}
 
@@
 \end{mathpar}
+
+\subsection{Generalizing further}
+
+\begin{itemize}
+\item Label transition systems.
+\item Arbitrary scheduling policies $\alpha$
+\end{itemize}
 

### 2014-02-22 paper/retrofit.tex
fold in the eval ctx in ml

@@
 \and
-\inferrule[T-pure]
-{| te ~> te'|}
-{| conf tS (intE te) -> conf tS (intE te') |}
+\inferrule[T-evalCtx]
+{| conf tS te -> conf tS' te')|}
+{| conf tS (intE te) -> conf tS' (intE te') |}
 
@@
 \inferrule[T-app]
-{ } {| (\x.te) tv ~> {tv/x} te |}
+{ } {| conf tS ((\x.te) tv) ~> conf tS ({tv/x} te) |}
 
@@
 \inferrule[T-ifTrue]
-{ } {| if true then te1 else te2  ~> te1|}
+{ } {| conf tS (if true then te1 else te2)  ~> conf tS te1|}
 
@@
 \inferrule[T-ifFalse]
-{ } {| if false then te1 else te2  ~> te2|}
+{ } {| conf tS (if false then te1 else te2)  ~> conf tS te2|}
 
@@
 {| tS' = tS [ ta mapsto tv ] | } 
-{| conf tS (intE (ref tv)) -> conf tS' (intE ta) |}
+{| conf tS (ref tv) -> conf tS' ta |}
 {| fresh (ta) |}
@@
 {| tv = tS(ta) |}
-{| conf tS (intE (!ta)) -> conf tS (intE tv) |}
+{| conf tS (!ta) -> conf tS tv |}
 
@@
 {| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (intE (ta := tv)) -> conf tS' (intE tv) |}
+{| conf tS (ta := tv) -> conf tS' tv |}
 \end{mathpar}
@@
 \item Label transition systems.
+\item Non-deterministic reduction.
 \item Arbitrary scheduling policies $\alpha$

### 2014-02-22 paper/retrofit.tex
wip

@@
 \begin{mathpar}
+\inferrule[I-evalCtx]
+{|
+iconf iS (lconf id il tS ie, ldots)
+.->
+iconf iS' (lconf id il' tS' ie', ldots)
+|}
+{|
+iconf iS (lconf id il tS (iniE ie), ldots)
+.->
+iconf iS' (lconf id il' tS' (iniE ie'), ldots)
+|}
+
+\and
 \inferrule[I-step]
@@
 {|
-iconf iS (lconf id il tS (iniE (IT te)), ldots)
+iconf iS (lconf id il tS (IT te), ldots)
 .->
-iconf iS (lconf id il tS' (iniE (IT te')), ldots)
+iconf iS (lconf id il tS' (IT te'), ldots)
 |}
+
+%% \and
+%% \inferrule[I-getLabel]
+%% { }
+%% {|
+%% iconf iS (lconf id il tS getLabel, ldots)
+%% .->
+%% iconf iS (lconf id il tS il, ldots)
+%% |}
 
@@
 {|
-iconf iS (lconf id il tS (iniE (getLabel)), ldots)
+iconf iS (inTE id il getLabel)
 .->
-iconf iS (lconf id il tS (iniE il), ldots)
+iconf iS (inTE id il il)
 |}
+
+%% \and
+%% \inferrule[I-setLabel]
+%% { |il canFlowTo il'| }
+%% {|
+%% iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
+%% .->
+%% iconf iS (lconf id il' tS (iniE unit), ldots)
+%% |}
 
@@
 {|
-iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
+iconf iS (inTE id il (setLabel il'))
 .->
-iconf iS (lconf id il' tS (iniE unit), ldots)
+iconf iS (inTE id il' unit)
 |}
@@
 
+%% \and
+%% \inferrule[I-send]
+%% {
+%% |il canFlowTo il'|\\
+%% |iS(id') = Q|\\
+%% |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
+%% }
+%% {|
+%% iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
+%% .->
+%% iconf iS' (lconf id il tS (iniE unit), ldots)
+%% |}
+
 \and
@@
 {|
-iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
+iconf iS  (inTE id il (send id' il' ie))
 .->
-iconf iS' (lconf id il tS (iniE unit), ldots)
+iconf iS' (inTE id il unit)
 |}
+
+%% \and
+%% \inferrule[I-recv]
+%% {
+%% | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
+%% | iS' = iS[id mapsto io1 , ... , iok]|\\
+%% | ie1'' = {ie'/ix1,id'/ix2} ie1|
+%% }
+%% {|
+%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+%% .->
+%% iconf iS' (lconf id il tS (iniE ie1''), ldots)
+%% |}
 
@@
 | iS' = iS[id mapsto io1 , ... , iok]|\\
-| ie1'' = {ie'/ix1,id'/ix2} ie1|
 }
 {|
-iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
 .->
-iconf iS' (lconf id il tS (iniE ie1''), ldots)
+iconf iS' (inTE id il ({ie'/ix1,id'/ix2} ie1))
 |}
+
+%% \and
+%% \inferrule[I-noRecv]
+%% {
+%% | filter il (iS(id)) = nil|\\
+%% | iS' = iS[id mapsto nil]|
+%% }
+%% {|
+%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+%% .->
+%% iconf iS' (lconf id il tS (iniE ie2), ldots)
+%% |}
 
@@
 {|
-iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
+iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
 .->
-iconf iS' (lconf id il tS (iniE ie2), ldots)
+iconf iS' (inTE id il ie2)
 |}
 
-\inferrule[I-pure]
-{| ie .~> ie'|}
-{|
-  iconf iS (lconf id il tS (iniE ie))
-.->
-iconf iS (lconf id il tS (iniE ie))
-|}
-
-\and
 \inferrule[I-labelOp]
-{ |denot (il lop il') = iv|}
-{ |il lop il' .~> iv| }
+{ |denot (il1 lop il2) = iv|}
+{ |iconf iS (inTE id il (il1 lop il2)) .-> iconf iS (inTE id il iv)| }
 
@@
 \inferrule[I-border]
-{ } {| IT (TI (ie)) .~> ie |}
+{ }
+{|
+iconf iS (inTE id il (IT (TI (ie))))
+.->
+iconf iS (inTE id il ie)
+|}
 

### 2014-02-22 paper/retrofit.tex
more

@@
 
+iTE  ::=  iTE, lconf id il tS ie, ldots
+
 ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
@@
 {|
-iconf iS (lconf id il tS ie, ldots)
+iconf iS (tconf id il ie)
 .->
-iconf iS' (lconf id il' tS' ie', ldots)
+iconf iS' (tconf id il' ie')
 |}
 {|
-iconf iS (lconf id il tS (iniE ie), ldots)
+iconf iS (iniTE (lconf id il tS ie))
 .->
-iconf iS' (lconf id il' tS' (iniE ie'), ldots)
+iconf iS' (iniTE (lconf id il' tS ie'))
 |}
@@
 {|
-iconf iS (lconf id il tS (IT te), ldots)
+iconf iS (iniTE (lconf id il tS (IT te)))
 .->
-iconf iS (lconf id il tS' (IT te'), ldots)
+iconf iS (iniTE (lconf id il tS' (IT te')))
 |}
@@
 {|
-iconf iS (inTE id il getLabel)
+iconf iS (tconf id il getLabel)
 .->
-iconf iS (inTE id il il)
+iconf iS (tconf id il il)
 |}
@@
 {|
-iconf iS (inTE id il (setLabel il'))
+iconf iS (tconf id il (setLabel il'))
 .->
-iconf iS (inTE id il' unit)
+iconf iS (tconf id il' unit)
 |}
@@
 {|
-iconf iS  (inTE id il (send id' il' ie))
+iconf iS  (tconf id il (send id' il' ie))
 .->
-iconf iS' (inTE id il unit)
+iconf iS' (tconf id il unit)
 |}
@@
 {|
-iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
+iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
 .->
-iconf iS' (inTE id il ({ie'/ix1,id'/ix2} ie1))
+iconf iS' (tconf id il ({ie'/ix1,id'/ix2} ie1))
 |}
@@
 {|
-iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
+iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
 .->
-iconf iS' (inTE id il ie2)
+iconf iS' (tconf id il ie2)
 |}
@@
 { |denot (il1 lop il2) = iv|}
-{ |iconf iS (inTE id il (il1 lop il2)) .-> iconf iS (inTE id il iv)| }
+{ |iconf iS (tconf id il (il1 lop il2)) .-> iconf iS (tconf id il iv)| }
 
@@
 {|
-iconf iS (inTE id il (IT (TI (ie))))
+iconf iS (tconf id il (IT (TI (ie))))
 .->
-iconf iS (inTE id il ie)
+iconf iS (tconf id il ie)
 |}
@@
 \inferrule[T-border]
-{ } {| intE (TI (IT (te))) ~> intE te |}
+{ } {| conf tS (intE (TI (IT (te)))) -> conf tS (intE te)|}
 \end{mathpar}
@@
 \end{itemize}
-
-%% \cut{
-%% (Selected rules from evaluation semantics. It's typed in the usual way.)
-%% 
-%% (Maybe this section needs to get moved) Sketch how a traditional account
-%% of IFC would go about extending these rules.  These things are:
-%% 
-%% \begin{enumerate}
-%%     \item Extend values with labels. (Values are isolated in runtimes,
-%%         so runtime is labeled not values)
-%%     \item Extend semantics to have a label on the program counter.
-%%         (Ditto, runtime is values.)
-%%     \item Extend semantics for assignment, as addresses need labels.
-%%         (Labeled references are internalized in IFC language, and
-%%         traditional references are isolated in runtimes.)
-%%     \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
-%%         flow sensitivity by reduction.)
-%% \end{enumerate}
-%% 
-%% % No longer describing a "minimal non-Turing complete IFC calculus",
-%% % instead, we jump straight to the combination.
-%% 
-%% We'd like to construct a coarse-grained IFC system on top of our language.
-%% Intuitively, programs written in the target language are running on top of
-%% an IFC ``operating system''.  The way we will perform our embedding is
-%% by allowing programs to perform ``syscalls'' into the IFC runtime, and
-%% vice-versa.  The IFC runtime is responsible for performing label checks
-%% and ensuring TSNI is not violated.
-%% 
-%% We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
-%% the IFC language from the previous section with our example language.  Key points:
-%% 
-%% \Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
-%% over-the-top.}
-%% 
-%% \begin{itemize}
-%%     \item Expression and evaluation contexts are considered separately,
-%%         so that some of our operational rules are easier to write
-%%     \item IT/TI mediate cross-language type boundary (mention that this
-%%         is where monitor failure/exceptions get handled)
-%% \end{itemize}
-%% 
-%% First, we associate a label with every evaluation context.  Suppose you had
-%% a function \verb|readFile|, you need to raise your label to write this
-%% kind of program.
-%% 
-%% Motivate why we have labeled values. How to I avoid label creep problem? We
-%% have fork. \Red{EZY shouldn't be in the ``background'' section.}
-%% 
-%% Background talks about IFC calculus in general; here we talk about
-%% embedding and give the precise semantics for the IFC embedding.
-%% 
-%% \Red{Give a fake rule with how you raise your label when you read from a file.
-%% We give you labeled values explicitly.}
-%% 
-%% \Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
-%% is pretty weird, why'd you do the API that way?}
-%% 
-%% \begin{verbatim}
-%% % colored differently
-%% e ::= fork e
-%%     # let's do channels?
-%%     | sendMessage e e  # asynchronous
-%%     | receiveMessage e # registers the callback
-%%     | label e e
-%%     | unlabel e
-%%     | IT e
-%% 
-%% v ::= tid
-%%     | l
-%%     | Labeled l v
-%% \end{verbatim}
-%% 
-%% \Red{Prove type safety for combined language?}
-%% 
-%% \Red{Problem: synchronization primitives which are blocking. OK, talk
-%% about this at the end. You can do whatever you want.}
-%% % NB: the nice thing about sendMessage is we can just drop messages
-%% % when the labels don't work out
-%% %
-%% % Intuitively, it would seem to me that any concurrency primitive
-%% % would be fine, as long as you proved it safe, we don't really care.
-%% 
-%% (Full operational semantics. Provide type rules.)
-%% 
-%% \Red{What to do when you get stuck when you are about to invalidate IFC}
-%% 
-%% Which rules do we want to talk about?
-%% 
-%% \begin{enumerate}
-%% \item fork: most complicated; shows side-condition (what do we do with stores on fork?)
-%% \item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
-%% \item unlabel: shows raising of label
-%% \item sendMessage: will give type for (maybe encapsulate queue in env)
-%% \end{enumerate}
-%% 
-%% \subsection{The methodology (XXX fix title)}
-%% \label{sec:methodology}
-%% 
-%% We now formally state our information-flow control transformation.  For
-%% simplicity's sake, we consider only single-threaded source languages,
-%% whose primary notion of execution is evaluation of an expression into a
-%% value.  (Later, we consider how to accomodate systems which have
-%% semantics for concurrent execution.)
-%% 
-%% \subsection{A tiny information-flow control calculus}
-%% 
-%% \begin{figure}[h]
-%% \begin{align*}
-%% \textrm{Thread \#:}   && \Ii          &   \\
-%% \textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
-%% \textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
-%%                                         \ |\ \ifc{\glb}
-%%                                         \ |\ \ifc{\flows}\\
-%% \textrm{Value:}       && \Iv          & ::=  \Itrue 
-%%                                         \ |\ \Ifalse
-%%                                         \ |\ \Iunit
-%%                                         \ |\ \Il
-%%                                         \ |\ \Ierr
-%%                                         \ |\ \Ii\\
-%% %                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
-%% \textrm{Expression:}  && \Ie          & ::=  \Iv
-%%                                         \ |\ \Ilop{\Ie}{\Ie}
-%%                                         \ |\ \IgetLabel
-%%                                         \ |\ \IgetClr\\&&&
-%%                                         \ |\ \Ifork{\Ie}{\Ie}
-%%                                         \ |\ \IT{\Te}\\
-%% \textrm{Context:}     && \IE          & ::=  \Ihole{\ }
-%%                                         \ |\ \Ilop{\IE}{\Ie}
-%%                                         \ |\ \Ilop{\Iv}{\IE}\\&&&
-%%                                         \ |\ \Ifork{\IE}{\Ie}
-%%                                         \ |\ \Ifork{\Iv}{\IE}
-%%                                         \ |\ \IT{\TE}\\
-%% \textrm{Store (of target language):} && \Istore\\
-%% \textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
-%% \end{align*}
-%% % reduction rules
-%% \begin{mathpar}
-%% 
-%% \inferrule[I-target]{
-%%   \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
-%%   \Tarrow
-%%   \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
-%%   \\
-%%   \TIstore{\Tstore}{\Tenv} = \Istore
-%%   \\
-%%   \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
-%% }
-%% {
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
-%%   \Iarrow
-%%   \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
-%% }
-%% 
-%% \and
-%% 
-%% \inferrule[I-boundary]{ }
-%% {
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
-%%   \Iarrow
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
-%% }
-%% 
-%% \and
-%% 
-%% \inferrule[I-label]{ }
-%% {
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
-%%   \Iarrow
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
-%% }
-%% 
-%% \and
-%% 
-%% \inferrule[I-clearance]{ }
-%% {
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
-%%   \Iarrow
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
-%% }
-%% 
-%% % fork
-%% \inferrule[I-fork]
-%% { 
-%%   \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
-%%   \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
-%%   \ifc{\Istore'} = \Tklone(\Istore)\\
-%% }
-%% {
-%%   \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
-%%     \inTE{\TI{
-%%       (\Ifork{\Il'}{(\IT{\Te})})
-%%     }}
-%%   }
-%%   \Itasksep\cdots
-%%   %
-%%   \Iarrow
-%%   %
-%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
-%%   \Itasksep\cdots\Itasksep
-%%   \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
-%%   \Itasksep\cdots
-%% }{\operatorname{fresh}(\Ii)}
-%% 
-%% 
-%% \end{mathpar}
-%% 
-%% \caption{IFC calculus}
-%% \end{figure}
-%% 
-%% \begin{figure}[h]
-%% \begin{align*}
-%% \textrm{Address:}     && \Ta          & \\
-%% \textrm{Variable:}    && \Tx          & \\
-%% \textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
-%% \textrm{Expression:}  && \Te          & ::=  \Tv
-%%                                         \ |\ \Tlambda{\Tx}{\Te}
-%%                                         \ |\ \Tx
-%%                                         \ |\ \Te\ \Te
-%%                                         \ |\ \Tset{\Te}{\Te}
-%%                                         \ |\ \TI{\Ie}\\
-%% \textrm{Context:}     && \TE          & ::=  \Thole{\ }
-%%                                         \ |\ \TE\ \Te
-%%                                         \ |\ \Tv\ \TE\\&&&
-%%                                         \ |\ \Tset{\TE}{\Te}
-%%                                         \ |\ \Tset{\Tx}{\TE}
-%%                                         \ |\ \TI{\IE}\\
-%% \textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
-%% \textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
-%% \textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
-%% \end{align*}
-%% % reduction rules
-%% \begin{mathpar}
-%% 
-%% % lambda to closure
-%% \inferrule[T-lam]{ }
-%% {
-%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
-%% \Tarrow
-%% \Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
-%% }
-%% 
-%% \and
-%% 
-%% % lookup variable
-%% \inferrule[T-var]{ }
-%% {
-%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
-%% \Tarrow
-%% \Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
-%% }
-%% 
-%% \and
-%% 
-%% % beta reduction
-%% \inferrule[T-$\beta$]
-%% {
-%% \tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
-%% \tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
-%% }
-%% {
-%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
-%% \Tarrow
-%% \Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
-%% }{\operatorname{fresh}(\Ta)}
-%% 
-%% \and
-%% 
-%% % set!
-%% \inferrule[T-set]
-%% {
-%% \tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
-%% }
-%% {
-%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
-%% \Tarrow
-%% \Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
-%% }
-%% % fork
-%% %\inferrule[E-fork]
-%% %{ 
-%% %\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
-%% %\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
-%% %\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
-%% %\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
-%% %}
-%% %{
-%% %\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
-%% %      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
-%% %}}}\|\cdots
-%% %\to
-%% %\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
-%% %\Iconf{\Il}{\Il}{\inE{
-%% %}}\|\cdots
-%% %}{fresh(\Ii)}
-%% 
-%% 
-%% \end{mathpar}
-%% \caption{Simple calculus}
-%% \end{figure}
-%% 
-%% Our first task is to define a information-flow control mini-language
-%% which will be combined with the source language. (Reference)  This
-%% language is not Turing-complete; this is intentional, as (1) the ability
-%% to call across the language boundary means that any control flow can be
-%% implemented in the source language, and (2) it simplifies the
-%% non-interference proof.  The language has a very simple set of typing
-%% rules.  The operational semantics for this language are worth remarking
-%% on (write a bit about how this IFC system works).  We can now state and
-%% prove a simple non-interference theorem about this language:
-%% 
-%% \begin{theorem}
-%% (Statement of noninterference)
-%% \end{theorem}
-%% \begin{proof}
-%% XXX TODO should be simple
-%% \end{proof}
-%% 
-%% \subsection{Combination (XXX)}
-%% 
-%% 
-%% }

### 2014-02-22 paper/retrofit.tex
fix evalctx rule

@@
 {|
-iconf iS (iniTE (lconf id il tS ie))
+iconf iS (iniTE (lconf id il tS (iniE ie)))
 .->
-iconf iS' (iniTE (lconf id il' tS ie'))
+iconf iS' (iniTE (lconf id il' tS (iniE ie')))
 |}

### 2014-02-22 paper/retrofit.tex
fork you

@@
 {|
-iconf iS (lconf id il tS (iniE (fork ie)), ldots)
+iconf iS (lconf id il tS (fork ie), ldots)
 .->
-iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
+iconf iS' (lconf id il tS id', ldots, lconf id' il tS' (TI ie))
 |}

### 2014-02-22 paper/retrofit.tex
no definition for T yet

@@
 
-iTE  ::=  iTE, lconf id il tS ie, ldots
-
 ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
@@
 {|
-iconf iS (iniTE (lconf id il tS (iniE ie)))
-.->
-iconf iS' (iniTE (lconf id il' tS (iniE ie')))
+iS ,(iniTE (lconf id il tS (iniE ie)))
+.-.>
+iS', (iniTE (lconf id il' tS (iniE ie')))
 |}
@@
 {|
-iconf iS (iniTE (lconf id il tS (IT te)))
-.->
-iconf iS (iniTE (lconf id il tS' (IT te')))
+iS, (iniTE (lconf id il tS (IT te)))
+.-.>
+iS, (iniTE (lconf id il tS' (IT te')))
 |}
@@
 |tS' = q(tS)|\\
-|fresh (id')|
+|fresh (id')|\\
+|iTE' THole = iniTE (lconf id il tS id'), THole|
 }
 {|
-iconf iS (lconf id il tS (fork ie), ldots)
-.->
-iconf iS' (lconf id il tS id', ldots, lconf id' il tS' (TI ie))
+iS, iniTE (lconf id il tS (fork ie))
+.-.>
+iS', iniTE' (lconf id' il tS' (TI ie))
 |}

### 2014-02-22 paper/retrofit.tex
wip

@@
 tv   ::= \tx.te | true | false | ta
-te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | diverge
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
 tE   ::= tHole | tE te | tv tE | if tE then te else te
@@
 
+iTE  ::=  THole | iTE, lconf id il tS ie
+
 ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
@@
 \and
+\inferrule[I-evalCtx2]
+{|
+iS ,(iniTE (lconf id il tS ie))
+.-.>
+iS', (iniTE' (lconf id il' tS ie'))
+|}
+{|
+iS ,(iniTE (lconf id il tS (iniE ie)))
+.-.>
+iS', (iniTE' (lconf id il' tS (iniE ie')))
+|}
+
+\and
 \inferrule[I-step]
@@
 
-%% \and
-%% \inferrule[I-getLabel]
-%% { }
-%% {|
-%% iconf iS (lconf id il tS getLabel, ldots)
-%% .->
-%% iconf iS (lconf id il tS il, ldots)
-%% |}
-
 \and
@@
 |}
-
-%% \and
-%% \inferrule[I-setLabel]
-%% { |il canFlowTo il'| }
-%% {|
-%% iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-%% .->
-%% iconf iS (lconf id il' tS (iniE unit), ldots)
-%% |}
 
@@
 
-%% \and
-%% \inferrule[I-send]
-%% {
-%% |il canFlowTo il'|\\
-%% |iS(id') = Q|\\
-%% |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
-%% }
-%% {|
-%% iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-%% .->
-%% iconf iS' (lconf id il tS (iniE unit), ldots)
-%% |}
-
 \and
@@
 
-%% \and
-%% \inferrule[I-recv]
-%% {
-%% | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
-%% | iS' = iS[id mapsto io1 , ... , iok]|\\
-%% | ie1'' = {ie'/ix1,id'/ix2} ie1|
-%% }
-%% {|
-%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
-%% .->
-%% iconf iS' (lconf id il tS (iniE ie1''), ldots)
-%% |}
-
 \and
@@
 |}
-
-%% \and
-%% \inferrule[I-noRecv]
-%% {
-%% | filter il (iS(id)) = nil|\\
-%% | iS' = iS[id mapsto nil]|
-%% }
-%% {|
-%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
-%% .->
-%% iconf iS' (lconf id il tS (iniE ie2), ldots)
-%% |}
 

### 2014-02-22 paper/retrofit.tex
threads
kappa

@@
 \inferrule[T-app]
-{ } {| conf tS ((\x.te) tv) ~> conf tS ({tv/x} te) |}
+{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}
 
@@
 \inferrule[T-ifTrue]
-{ } {| conf tS (if true then te1 else te2)  ~> conf tS te1|}
+{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}
 
@@
 \inferrule[T-ifFalse]
-{ } {| conf tS (if false then te1 else te2)  ~> conf tS te2|}
+{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}
 
@@
 |iS' = iS [ id' mapsto nil ]|\\
-|tS' = q(tS)|\\
+|tS' = klone(tS)|\\
 |fresh (id')|\\

### 2014-02-22 paper/retrofit.tex
Fix reduction arrow.

@@
 |iS' = iS [ id' mapsto nil ]|\\
-|tS' = klone(tS)|\\
+|tS' = q(tS)|\\
 |fresh (id')|\\

### 2014-02-23 paper/retrofit.tex
wip, no step

@@
 
-iTE  ::=  THole | iTE, lconf id il tS ie
+it   ::=  lconf id il tS ie
+iTE  ::=  THole | iTE, it
 
@@
 .-.>
-iS', (iniTE (lconf id il' tS (iniE ie')))
+iS', sched step (iniTE (lconf id il' tS (iniE ie')))
 |}
@@
 .-.>
-iS, (iniTE (lconf id il tS' (IT te')))
+iS, sched step (iniTE (lconf id il tS' (IT te')))
+|}
+
+\and
+\inferrule[I-noStep]
+{|
+it nostep
+|}
+{|
+iS, (iniTE it)
+.-.>
+iS, sched noStep (iniTE it)
 |}
@@
 .-.>
-iS', iniTE' (lconf id' il tS' (TI ie))
+iS', sched fork (iniTE' (lconf id' il tS' (TI ie)))
 |}
@@
 
+\begin{figure}
+  Round robin:
+\begin{code}
+  sched step (it1, it2, ...)    = it2, ..., it1
+  sched noStep (it1, it2, ...)  = it2, ...
+  sched fork                    = sched step
+\end{code}
+  Browbound:
+\begin{code}
+  sched step                    = Id
+  sched noStep (it1, it2, ...)  = it2, ...
+  sched fork                    = Id
+\end{code}
+  Sequential:
+\begin{code}
+  sched step                       = Id
+  sched noStep (it1, it2, ...)     = Id
+  sched fork (it1, it2, ... it1n)  = itn, t1, t2, ...
+\end{code}
+\caption{scheduling policies}
+\end{figure}
+
 \subsection{Generalizing further}

### 2014-02-23 paper/retrofit.tex
expand scheduling policies; sequential is not right; wip

@@
   sched noStep (it1, it2, ...)  = it2, ...
-  sched fork                    = sched step
+  sched fork (it1, it2, ...)    = it2, ..., it1
 \end{code}
@@
 \begin{code}
-  sched step                    = Id
+  sched step (it1, it2, ...)    = it1, it2, ...
   sched noStep (it1, it2, ...)  = it2, ...
-  sched fork                    = Id
+  sched fork (it1, it2, ...)    = it1, it2, ...
 \end{code}
@@
 \begin{code}
-  sched step                       = Id
-  sched noStep (it1, it2, ...)     = Id
-  sched fork (it1, it2, ... it1n)  = itn, t1, t2, ...
+  sched step (it1, it2, ...)       = it1, it2, ...
+  sched noStep (it1, it2, ...)     = it1, it2, ...
+  sched fork (it1, it2, ... it1n)  = itn, it1, it2, ...
 \end{code}

### 2014-02-23 paper/retrofit.tex
inlinging thread pool

--- 2014-02-22 paper/retrofit.tex
@@
 lop  ::=  canFlowTo | lub | glb
-iv   ::=  id | il | true | false | unit
+iv   ::=  id | il | true | false | unit | IT tv
 ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
@@
 tE   ::=  cdots | TI iE
-
-iTE  ::=  THole | iTE, lconf id il tS ie
 
@@
 {|
-iS ,(iniTE (lconf id il tS (iniE ie)))
-.-.>
-iS', (iniTE (lconf id il' tS (iniE ie')))
+iconf iS (lconf id il tS (iniE ie), ldots)
+.->
+iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
 |}
@@
 \and
-\inferrule[I-evalCtx2]
+\inferrule[I-done]
 {|
-iS ,(iniTE (lconf id il tS ie))
-.-.>
-iS', (iniTE' (lconf id il' tS ie'))
 |}
 {|
-iS ,(iniTE (lconf id il tS (iniE ie)))
-.-.>
-iS', (iniTE' (lconf id il' tS (iniE ie')))
+iconf iS (lconf id il tS iv, ldots)
+.->
+iS ; sched done (lconf id il tS iv, ldots)
 |}
@@
 \and
-\inferrule[I-step]
+\inferrule[I-stepT]
 {|
@@
 {|
-iS, (iniTE (lconf id il tS (IT te)))
-.-.>
-iS, (iniTE (lconf id il tS' (IT te')))
+iconf iS (lconf id il tS (iniE (IT te)), ldots)
+.->
+iS ; sched step (lconf id il tS' (iniE (IT te')), ldots)
+|}
+
+\and
+\inferrule[I-noStepT]
+{|
+conf tS (te) -/> 
+|}
+{|
+iconf iS (lconf id il tS (iniE (IT te)), ldots)
+.->
+iS ; sched noStep (lconf id il tS (iniE (IT te)), ldots)
+|}
+
+\and
+\inferrule[I-noStep]
+{|
+it .-/> 
+|}
+{|
+iconf iS (it, ldots)
+.->
+iS ; sched noStep (it, ldots)
 |}
@@
 |iS' = iS [ id' mapsto nil ]|\\
-|tS' = q(tS)|\\
-|fresh (id')|\\
-|iTE' THole = iniTE (lconf id il tS id'), THole|
+|tS' = klone(tS)|\\
+|it1 = lconf id il tS (iniE id')|\\
+|itnew = lconf id' il tS' (TI ie)|\\
+|fresh (id')|
 }
 {|
-iS, iniTE (lconf id il tS (fork ie))
-.-.>
-iS', iniTE' (lconf id' il tS' (TI ie))
+iconf iS (lconf id il tS (iniE (fork ie)), ldots)
+.->
+iS'; sched fork (it1, ldots, itnew)
 |}
@@
 
+\begin{figure}
+  Round robin:
+\begin{code}
+  sched step (it1, it2, ...)    = {it2, ..., it1}
+  sched done (it1, it2, ...)    = {it2, ...}
+  sched noStep (it1, it2, ...)  = {it2, ...}
+  sched fork (it1, it2, ...)    = {it2, ..., it1}
+\end{code}
+  Browbound:
+\begin{code}
+  sched step (it1, it2, ...)    = {it1, it2, ...}
+  sched noStep (it1, it2, ...)  = {it2, ...}
+  sched done (it1, it2, ...)    = {it2, ...}
+  sched fork (it1, it2, ...)    = {it1, it2, ...}
+\end{code}
+  Sequential:
+\begin{code}
+  sched step (it1, it2, ...)       = {it1, it2, ...}
+  sched noStep (it1, it2, ...)     = {it1, it2, ...}
+  sched done (it1, it2, ...)       = {it2, ...}
+  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
+\end{code}
+\caption{scheduling policies}
+\end{figure}
+
 \subsection{Generalizing further}

### 2014-02-23 paper/concrete.tex

@@
 \label{sec:concrete}
+
+The operational semantics we have derived in the previous section
+constitutes an abstract \emph{specification}: a semantics for which
+non-interference is (obviously) true.  This specification can guide the
+design of an information-flow calculus which would not be directly
+derivable from our procedure, but is related to some such derivation.
+For example, in our mini-ML language, the combined semantics requires
+each thread to have a separate ML heap.  In an actual implementation, we
+might like to only have a \emph{single} heap, with some restrictions to
+enforce the illusion of separate heaps.  If these restrictions cause our
+implementation semantics to behave in the same way as the specification
+semantics (modulo some extra conditions), we might hope that we also
+automatically achieve non-interference.
+
+We can make this formal as follows: \Red{Define some notation}
+
+\begin{theorem}
+    Suppose we have a abstract specification language $L$ with machine
+    states $|C|$, evaluation relation $|.->|$ and erasure function $e$.
+    Furthermore we have a proof that this language fulfills termination
+    sensitive non-interference: if $|C1| \approx_l |C2|$ and $|C1|
+    |.->|^* |C1'|$, then there exists a $|C2'|$ such that $|C2| |.->|^*
+    |C2'|$ and $|C1'| \approx_l |C2'|$.
+
+    Next, suppose we have a language $L'$ with machine states $|Q|$,
+    evaluation relation $|.->|'$ and erasure function $e'$.  Given
+    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
+    states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
+    id$.  Then to show termination sensitive non-interference for $L'$,
+    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
+    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
+    \ldots
+\end{theorem}
+
+\begin{proof}
+Our proof proceeds along the same lines as a traditional TSNI proof.
+\ldots (wait for the proof to be done)
+\end{proof}
+
+To provide a sense of how these conditions work, we give an example
+use of these theorem:
+
+\begin{theorem}
+    The language described in Figure X satisfies termination sensitive non-interference.
+\end{theorem}
+
+\begin{code}
+\end{code}
+
+\begin{figure}
+    \begin{code}
+
+    \end{code}
+
+\caption{ML with a single heap}
+\label{fig:comb}
+\end{figure}
+
+This version

### 2014-02-23 paper/concrete.tex
Start building combined version.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
More tweaks.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \begin{figure}
-    \begin{code}
 
-    \end{code}
+\begin{mathpar}
+\inferrule[I-stepT]
+{|
+conf tS (te) -> conf tS' te'
+|}
+{|
+coconf iS tS (cconf id il (iniE (IT te)), ldots)
+.->
+iS ; tS' ; sched step (cconf id il (iniE (IT te')), ldots)
+|}
+
+\and
+% This rule is not complete, needs the FV condition
+\inferrule[C-fork]
+{ 
+|iS' = iS [ id' mapsto nil ]|\\
+|it1 = cconf id il (iniE id')|\\
+|itnew = cconf id' il (TI ie)|\\
+|fresh (id')|
+}
+{|
+coconf iS tS (lconf id il (iniE (fork ie)), ldots)
+.->
+iS'; tS; sched fork (it1, ldots, itnew)
+|}
+\end{mathpar}
 

### 2014-02-23 paper/retrofit.tex
Split ifc figure into two parts.
TSNI theorem.

@@
 \end{code}
+\caption{IFC grammar.}
+\label{fig:ifc-grammar}
+\end{figure}
 
+\begin{figure}
 \begin{mathpar}
@@
 \end{mathpar}
-\caption{IFC language nad general embedding.}
-\label{fig:ml}
+\caption{IFC language and general embedding.}
+\label{fig:ifc}
 \end{figure}
@@
 
+\subsection{Formal Guarantees}
+
+\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
+  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
+  IFC states |iS1|, |iS2|, |iS1'|, where
+  \[
+    |its1| \approx_{|il|} |its2| \qquad \text{and} \qquad
+    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
+  \]
+  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
+  \[
+    |iconf iS2 its2| |.->|^* |iconf iS2' its2'| \qquad \text{and} \qquad
+    |its1'| \approx_{|il|} |its2'|
+    \ \text{.}
+  \]
+\end{theorem}
+
 \subsection{Generalizing further}

### 2014-02-23 paper/retrofit.tex
Start adding typing.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 tv   ::= \tx.te | true | false | ta
+tt   ::= bool | tt -> tt | ref tt
 te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
@@
 \end{code}
+
+Typing judgment: $|tyrule tG tS te tt|$
 
@@
 \label{fig:ml}
+\end{figure}
+
+\begin{figure}
+\begin{mathpar}
+
+\end{mathpar}
+
+\caption{Typing rules for ML-like language}
+\label{fig:ml-typing}
 \end{figure}

### 2014-02-23 paper/retrofit.tex
Mini-note, remove when we fix the text or the rules
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 reduction relation on such configuration, i.e., $|->| : (|tS| \times
-|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$
+|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$ \Red{This doesn't match the way the evaluation rules are currently done with a frame rule}
 

### 2014-02-23 paper/retrofit.tex
Proof of TSNI theorem (relying on a not-yet-existing lemma with the main proof).

--- 2014-02-23 paper/retrofit.tex
@@
   IFC states |iS1|, |iS2|, |iS1'|, where
+  \begin{equation} \label{eq:tsni-lhs}
+    |its1| \approx_{|il|} |its2|
+    \qquad \text{and} \qquad
+    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
+  \end{equation}
+  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
+  \begin{equation} \label{eq:tsni-rhs}
+    |its1'| \approx_{|il|} |its2'|
+     \qquad \text{and} \qquad
+    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
+    \ \text{.}
+  \end{equation}
+\end{theorem}
+
+\begin{proof}
+  We proof the theorem by induction on the length of the derivation sequence in~(1).
+  The base case for derivations
+  of length 0 is trivial, allowing
+  us to simple chose $|its2'=its2|$ and $|iS2'=iS2|$.  In the step case, we assume
+  the theorem holds for derivation sequences of length up to $n$, and show that it also
+  holds for those of length $n+1$.  We split the derivation sequence from~(1) as follows:
   \[
-    |its1| \approx_{|il|} |its2| \qquad \text{and} \qquad
-    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
+  |iconf iS1 its1| |.->| |iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|
   \]
-  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
-  \[
-    |iconf iS2 its2| |.->|^* |iconf iS2' its2'| \qquad \text{and} \qquad
+  for some IFC state |iS1''| and task list |its1''|.  By Lemma~1, we get
+  |its2''| and |iS2''| with
+  \begin{equation} \label{eq:tsni-proof-1}
+  |its1''| \approx_{|il|} |its2''|
+  \qquad \text{and} \qquad
+  |iconf iS2 its2| |.->|^* |iconf iS2'' its2''|
+  \end{equation}
+  Applying the induction hypotisis to
+  $|iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|$, we get |its2'| and |iS2'| with
+  \begin{equation} \label{eq:tsni-proof-2}
   |its1'| \approx_{|il|} |its2'|
-    \ \text{.}
-  \]
-\end{theorem}
+  \qquad \text{and} \qquad
+  |iconf iS2'' its2''| |.->|^* |iconf iS2' its2'|
+  \end{equation}
+  Stitching together the derivation sequences from (3) and (4) directly gives
+  us (2), which concludes the proof.
+\end{proof}
 

### 2014-02-23 paper/retrofit.tex
More typing rules.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Start of an erasure function.

@@
 \begin{mathpar}
-
+\inferrule[T-ty-address]
+{}
+{| tyrule tG tS a (ref (tyLookup tS a)) |}
 \end{mathpar}
 
-\caption{Typing rules for ML-like language}
+\caption{Selected typing rules for ML-like language}
 \label{fig:ml-typing}
@@
 \label{fig:ifc-grammar}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  &|erase il (iconf iS its) = iconf iS its| \\
+  &|erase il (tconf id il' ie) =| \begin{cases}
+    |tconf id il' bullet| & |il' cantFlowTo il| \\
+    |tconf id il' (erase ie)| & \text{otherwise}
+  \end{cases}
+\end{align*}
+\caption{Erasure function.}
 \end{figure}

### 2014-02-23 paper/retrofit.tex
Finish erase.

--- 2014-02-23 paper/retrofit.tex
@@
 \label{fig:ifc-grammar}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  &|erase il (iconf iS its) =
+  iconf (erase il iS) (fltr (\ lconf id il' tS te . te = bullet) (map (erasef il) its))| \\
+  &|erase il (tconf id il' ie) =| \begin{cases}
+    |tconf id il' bullet| & |il' cantFlowTo il| \\
+    |tconf id il' (erase il ie)| & \text{otherwise}
+  \end{cases} \\
+  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
+  &|erase il ((il', id, ie), Q) =| \begin{cases}
+    |erase il Q| & |il' cantFlowTo il| \\
+    |(il', id, ie), (erase il Q)| & \text{otherwise}
+  \end{cases} \\
+  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
+    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
+    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
+  \end{cases} \\
+  &\text{In all other cases, |erasef il| is applied homomorphically.}
+\end{align*}
+\caption{Erasure function.}
 \end{figure}

### 2014-02-23 paper/retrofit.tex
fix erase.

--- 2014-02-23 paper/retrofit.tex
@@
 \label{fig:ifc-grammar}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  &|erase il (iconf iS its) =
+  iconf (erase il iS) (fltr (\ lconf id il' tS te . te = bullet) (map (erasef il) its))| \\
+  &|erase il (tconf id il' ie) =| \begin{cases}
+    |tconf bullet bullet bullet| & |il' cantFlowTo il| \\
+    |tconf id il' (erase il ie)| & \text{otherwise}
+  \end{cases} \\
+  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
+  &|erase il Q = filter il Q|
+  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
+    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
+    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
+  \end{cases} \\
+  &\text{In all other cases, |erasef il| is applied homomorphically.}
+\end{align*}
+\caption{Erasure function.}
 \end{figure}

### 2014-02-23 paper/retrofit.tex
Fix typo.

@@
   %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
-  &|erase il Q = filter il Q|
+  &|erase il Q = filter il Q|\\
   &|erase il (send ie1 ie2 ie3) =| \begin{cases}

### 2014-02-24 paper/retrofit.tex
Properly erase target state.

@@
   &|erase il (iconf iS its) =
-  iconf (erase il iS) (fltr (\ lconf id il' tS te . te = bullet) (map (erasef il) its))| \\
+  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
   &|erase il (tconf id il' ie) =| \begin{cases}
-    |tconf bullet bullet bullet| & |il' cantFlowTo il| \\
-    |tconf id il' (erase il ie)| & \text{otherwise}
+    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
+    |bullet| & |il' cantFlowTo il| \\
+    |lconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
   \end{cases} \\

### 2014-02-24 paper/retrofit.tex
typofix
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Add lemma.

@@
 \begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
-  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
+  For any list of tasks |its1|, |its2|, |its2|, label |il|,
   IFC states |iS1|, |iS2|, |iS1'|, where
@@
   \end{equation}
-  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
+  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
   \begin{equation} \label{eq:tsni-rhs}
@@
 \end{theorem}
+
+\begin{lemma}
+  For any list of tasks |its1|, |its2|, |its2|, label |il|,
+  IFC states |iS1|, |iS2|, |iS1'|, where
+  \begin{equation} \label{eq:tsni-lhs}
+  |its1| \approx_{|il|} |its2|
+  \qquad \text{and} \qquad
+  |iconf iS1 its1| |.->| |iconf iS1' its1'|
+  \end{equation}
+  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
+  \begin{equation} \label{eq:tsni-rhs}
+  |its1'| \approx_{|il|} |its2'|
+  \qquad \text{and} \qquad
+  |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
+  \ \text{.}
+  \end{equation}
+\end{lemma}
 

### 2014-02-24 paper/retrofit.tex
Note that the lemma is not a real reference.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
   \]
-  for some IFC state |iS1''| and task list |its1''|.  By Lemma~1, we get
+  for some IFC state |iS1''| and task list |its1''|.  By \Red{Lemma~1}, we get
   |its2''| and |iS2''| with
@@
   \end{equation}
-  Applying the induction hypotisis to
+  Applying the induction hypothesis to
   $|iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|$, we get |its2'| and |iS2'| with

### 2014-02-24 paper/retrofit.tex
Fix references in proofs/lemmas.

@@
 \begin{lemma}
+  \label{lemma:tsni}
   For any list of tasks |its1|, |its2|, |its2|, label |il|,
   IFC states |iS1|, |iS2|, |iS1'|, where
-  \begin{equation} \label{eq:tsni-lhs}
+  \begin{equation} \label{eq:tsni-lemma-lhs}
   |its1| \approx_{|il|} |its2|
@@
   then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
-  \begin{equation} \label{eq:tsni-rhs}
+  \begin{equation} \label{eq:tsni-lemma-rhs}
   |its1'| \approx_{|il|} |its2'|
@@
 \begin{proof}
-  We proof the theorem by induction on the length of the derivation sequence in~(1).
+  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
   The base case for derivations
@@
   the theorem holds for derivation sequences of length up to $n$, and show that it also
-  holds for those of length $n+1$.  We split the derivation sequence from~(1) as follows:
+  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
   \[
@@
   \]
-  for some IFC state |iS1''| and task list |its1''|.  By \Red{Lemma~1}, we get
+  for some IFC state |iS1''| and task list |its1''|.  By Lemma~\ref{lemma:tsni}, we get
   |its2''| and |iS2''| with
@@
   \end{equation}
-  Stitching together the derivation sequences from (3) and (4) directly gives
-  us (2), which concludes the proof.
+  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
+  us~\eqref{eq:tsni-rhs}, which concludes the proof.
 \end{proof}

### 2014-02-24 paper/concrete.tex
Note that the lemma is not a real reference.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Other stuff.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
-    id$.  Then to show termination sensitive non-interference for $L'$,
+    id$ and $f^{-1} \circ e' \circ f = e$.  Then to show termination sensitive non-interference for $L'$,
     it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
@@
 \begin{proof}
-Our proof proceeds along the same lines as a traditional TSNI proof.
-\ldots (wait for the proof to be done)
+Our proof proceeds along the same lines as a traditional TSNI proof,
+we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
+over reduction derivations in the first step.
 \end{proof}

### 2014-02-24 paper/retrofit.tex
New world syntax!
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-Typing judgment: $|tyrule tG tS te tt|$
+Typing judgment: $|tyrule tG tS te tty|$
 
 \begin{mathpar}
-\and
-\inferrule[T-evalCtx]
-{| conf tS te -> conf tS' te')|}
-{| conf tS (intE te) -> conf tS' (intE te') |}
 
@@
 ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
+
+conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
+niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
 \end{code}
@@
     |bullet| & |il' cantFlowTo il| \\
-    |lconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
+    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
   \end{cases} \\
@@
 \begin{mathpar}
-\inferrule[I-evalCtx]
-{|
-iconf iS (tconf id il ie)
-.->
-iconf iS' (tconf id il' ie')
-|}
-{|
-iconf iS (lconf id il tS (iniE ie), ldots)
-.->
-iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
-|}
-
 \and
@@
 {|
-iconf iS (lconf id il tS iv, ldots)
+iconf iS (fullconf id il tS iv, ldots)
 .->
-iS ; sched done (lconf id il tS iv, ldots)
-|}
-
-\and
-\inferrule[I-stepT]
-{|
-conf tS (te) -> conf tS' te'
-|}
-{|
-iconf iS (lconf id il tS (iniE (IT te)), ldots)
-.->
-iS ; sched step (lconf id il tS' (iniE (IT te')), ldots)
-|}
-
-\and
-\inferrule[I-noStepT]
-{|
-conf tS (te) -/> 
-|}
-{|
-iconf iS (lconf id il tS (iniE (IT te)), ldots)
-.->
-iS ; sched noStep (lconf id il tS (iniE (IT te)), ldots)
+iS ; sched done (fullconf id il tS iv, ldots)
 |}
@@
 {|
-it .-/> 
+iconf iS (it, ldots) .-/> 
 |}
@@
 \and
+\inferrule[I-fork]
+{ 
+|iS' = iS [ id' mapsto nil ]|\\
+|tS' = klone(tS)|\\
+|it1 = fullconf id il tS (iniE id')|\\
+|itnew = fullconf id' il tS' (TI ie)|\\
+|fresh (id')|
+}
+{|
+iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
+.->
+iS'; sched fork (it1, ldots, itnew)
+|}
+
+\and
 \inferrule[I-getLabel]
@@
 {|
-iconf iS (tconf id il getLabel)
+niconf iS id il getLabel
 .->
-iconf iS (tconf id il il)
+niconf iS id il il
 |}
@@
 {|
-iconf iS (tconf id il (setLabel il'))
+niconf iS id il (setLabel il')
 .->
-iconf iS (tconf id il' unit)
-|}
-
-\and
-\inferrule[I-fork]
-{ 
-|iS' = iS [ id' mapsto nil ]|\\
-|tS' = klone(tS)|\\
-|it1 = lconf id il tS (iniE id')|\\
-|itnew = lconf id' il tS' (TI ie)|\\
-|fresh (id')|
-}
-{|
-iconf iS (lconf id il tS (iniE (fork ie)), ldots)
-.->
-iS'; sched fork (it1, ldots, itnew)
+niconf iS id il' unit
 |}
@@
 {|
-iconf iS  (tconf id il (send id' il' ie))
+niconf iS  id il (send id' il' ie)
 .->
-iconf iS' (tconf id il unit)
+niconf iS' id il unit
 |}
@@
 {|
-iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
+niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
 .->
-iconf iS' (tconf id il ({ie'/ix1,id'/ix2} ie1))
+niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
 |}
@@
 {|
-iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
+niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
 .->
-iconf iS' (tconf id il ie2)
+niconf iS' id il ie2
 |}
@@
 { |denot (il1 lop il2) = iv|}
-{ |iconf iS (tconf id il (il1 lop il2)) .-> iconf iS (tconf id il iv)| }
+{ |niconf iS id il (il1 lop il2) .-> niconf iS id il iv| }
 
@@
 {|
-iconf iS (tconf id il (IT (TI (ie))))
+niconf iS id il (IT (TI (ie)))
 .->
-iconf iS (tconf id il ie)
+niconf iS id il ie
 |}
@@
 \inferrule[T-border]
-{ } {| conf tS (intE (TI (IT (te)))) -> conf tS (intE te)|}
+{ } {| conf tS (TI (IT (te))) -> conf tS te|}
 \end{mathpar}

### 2014-02-24 paper/retrofit.tex
Fix tau.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 tv   ::= \tx.te | true | false | ta
-tt   ::= bool | tt -> tt | ref tt
+tty   ::= bool | tty -> tty | ref tty
 te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te

### 2014-02-24 paper/retrofit.tex
.
Straight arrow-ify things that are implicitly applying step.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
   &|erase il Q = filter il Q|\\
-  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
-    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
-    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
+  &|erase il (send id il' ie) =| \begin{cases}
+    |send ie1 ie2 bullet| & |il' cantFlowTo il| \\
+    |send id il' (erase il ie)| & \text{otherwise}
   \end{cases} \\
@@
 niconf iS id il getLabel
-.->
+->
 niconf iS id il il
@@
 niconf iS id il (setLabel il')
-.->
+->
 niconf iS id il' unit
@@
 niconf iS  id il (send id' il' ie)
-.->
+->
 niconf iS' id il unit
@@
 niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
-.->
+->
 niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
@@
 niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
-.->
+->
 niconf iS' id il ie2
@@
 niconf iS id il (IT (TI (ie)))
-.->
+->
 niconf iS id il ie
@@
 
+\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
+  We proof the lemma by induction on the derivation
+  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
+  could have been used to make the reduction step.
+  \begin{description}
+    \item[Case \textsc{I-done}] 
+    \item[Case \textsc{I-noStep}] 
+    \item[Case \textsc{I-fork}] 
+    \item[Case \textsc{I-setLabel}]
+  \end{description}
+\end{proof}
+
 \subsection{Generalizing further}

### 2014-02-24 paper/retrofit.tex
Get step back in.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-24 paper/retrofit.tex
@@
 niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
+CE[e] -> iconf iS (t, ldots) @= CE[e] .-> iconf iS (sched step (t, ldots))
 \end{code}

### 2014-02-24 paper/retrofit.tex
properly fix erase

--- 2014-02-24 paper/retrofit.tex
@@
   &|erase il (send id il' ie) =| \begin{cases}
-    |send ie1 ie2 bullet| & |il' cantFlowTo il| \\
+    |send id il' bullet| & |il' cantFlowTo il| \\
     |send id il' (erase il ie)| & \text{otherwise}

### 2014-02-24 paper/retrofit.tex
Grab missing thread.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-24 paper/retrofit.tex
@@
 { |denot (il1 lop il2) = iv|}
-{ |niconf iS id il (il1 lop il2) .-> niconf iS id il iv| }
+{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
 

### 2014-02-24 paper/retrofit.tex
temporary clearpage to make things more readable.
Some descriptive text.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-We consider languages in the form of abstract state machines |(tS, tE,
-te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
-context, |te| is an expression in the language and |->| is the
-reduction relation on such configuration, i.e., $|->| : (|tS| \times
-|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$ \Red{This doesn't match the way the evaluation rules are currently done with a frame rule}
+While we would like to add information flow control to \emph{any}
+language, we will have to make some assumptions about the form of the
+target language.  We consider languages whose semantics can be expressed
+in the form of abstract machines |(tS, tE, te, ->)|, where |tS| is the
+global machine state, |tE| is an evaluation context, |te| is an
+expression in the language and |->| is the reduction relation on such
+configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
+\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
+target language have been colored red.
 
-To get the flavor for our approach, we will first show how our embedding
-works for a simple, ML-like language, with references and general recursion.
+In Figure~\ref{fig:ml}, we give an example of a standard ML-like
+language with mutable references.  These semantics have been prepared
+for interoperability in the style of Matthews and Findler~\nocite{}, in
+particular, the evaluation rules have been expressed in terms of an
+evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
+this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
+when we perform the embedding, we will reinterpret the meaning
+of this operator, moving .
 
@@
 
-Typing judgment: $|tyrule tG tS te tty|$
+\Red{Suggestion: Only give the rules for references, because otherwise this is all standard.}
 
@@
 \begin{figure}
+Typing judgment: $|tyrule tG tS te tty|$
 \begin{mathpar}
@@
 niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
-CE[e] -> iconf iS (t, ldots) @= CE[e] .-> iconf iS (sched step (t, ldots))
+CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
 \end{code}

### 2014-02-25 paper/retrofit.tex
Restructure the rules a little bit.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 target language.  We consider languages whose semantics can be expressed
-in the form of abstract machines |(tS, tE, te, ->)|, where |tS| is the
+in the form of abstract machines |(tS, tE, te, tv, ->)|, where |tS| is the
 global machine state, |tE| is an evaluation context, |te| is an
-expression in the language and |->| is the reduction relation on such
+expression in the language, |tv| is the set of values, and |->| is the reduction relation on such
 configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
@@
 language with mutable references.  These semantics have been prepared
-for interoperability in the style of Matthews and Findler~\nocite{}, in
+for interoperability in the style of Matthews and Findler~\Red{XXX}; in
 particular, the evaluation rules have been expressed in terms of an
@@
 when we perform the embedding, we will reinterpret the meaning
-of this operator, moving .
+of this evaluation context, lifting these semantics to an IFC setting.
 
@@
 
-\begin{figure}
-Typing judgment: $|tyrule tG tS te tty|$
-\begin{mathpar}
-\inferrule[T-ty-address]
-{}
-{| tyrule tG tS a (ref (tyLookup tS a)) |}
-\end{mathpar}
+%   \begin{figure}
+%   Typing judgment: $|tyrule tG tS te tty|$
+%   \begin{mathpar}
+%   \inferrule[T-ty-address]
+%   {}
+%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
+%   \end{mathpar}
 
-\caption{Selected typing rules for ML-like language}
-\label{fig:ml-typing}
-\end{figure}
+%   \caption{Selected typing rules for ML-like language}
+%   \label{fig:ml-typing}
+%   \end{figure}
 
@@
 lop  ::=  canFlowTo | lub | glb
-iv   ::=  id | il | true | false | unit | IT tv
+iv   ::=  id | il | true | false | unit
 ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
-       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
+       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
 iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
        |  send iE ie ie | send iv iE ie | send iv iv iE
-       |  ix1, ix2 <= recv. ie ie |  IT tE
+       |  ix1, ix2 <= recv. ie ie
 io   ::=  (il, id ie)
@@
 
-te   ::=  cdots | TI ie
-tE   ::=  cdots | TI iE
-
-ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
-
-conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
-niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
 CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
 \end{code}
-\caption{IFC grammar.}
-\label{fig:ifc-grammar}
-\end{figure}
 
-\begin{figure}
-\begin{align*}
-  &|erase il (iconf iS its) =
-  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
-  &|erase il (tconf id il' ie) =| \begin{cases}
-    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
-    |bullet| & |il' cantFlowTo il| \\
-    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
-  \end{cases} \\
-  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
-  &|erase il Q = filter il Q|\\
-  &|erase il (send id il' ie) =| \begin{cases}
-    |send id il' bullet| & |il' cantFlowTo il| \\
-    |send id il' (erase il ie)| & \text{otherwise}
-  \end{cases} \\
-  &\text{In all other cases, |erasef il| is applied homomorphically.}
-\end{align*}
-\caption{Erasure function.}
-\end{figure}
-
-\begin{figure}
 \begin{mathpar}
-\and
-\inferrule[I-done]
-{|
-|}
-{|
-iconf iS (fullconf id il tS iv, ldots)
-.->
-iS ; sched done (fullconf id il tS iv, ldots)
-|}
+%   \and
+%   \inferrule[I-done]
+%   {|
+%   |}
+%   {|
+%   iconf iS (fullconf id il tS iv, ldots)
+%   .->
+%   iS ; sched done (fullconf id il tS iv, ldots)
+%   |}
 
@@
 iS ; sched noStep (it, ldots)
-|}
-
-\and
-\inferrule[I-fork]
-{ 
-|iS' = iS [ id' mapsto nil ]|\\
-|tS' = klone(tS)|\\
-|it1 = fullconf id il tS (iniE id')|\\
-|itnew = fullconf id' il tS' (TI ie)|\\
-|fresh (id')|
-}
-{|
-iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
-.->
-iS'; sched fork (it1, ldots, itnew)
 |}
@@
 { |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
+\end{mathpar}
+\caption{IFC language}
+\label{fig:ifc}
+\end{figure}
+
+\begin{figure}
+\begin{tabular}{ll}
+\begin{minipage}{.22\textwidth}
+\begin{code}
+iv ::= cdots | IT tv
+ie ::= cdots | IT te
+iE ::= cdots | IT tE
+\end{code}
+\end{minipage} &
+\begin{minipage}{.22\textwidth}
+\begin{code}
+tv ::= cdots | TI iv
+te  ::=  cdots | TI ie
+tE   ::=  cdots | TI iE
+\end{code}
+\end{minipage}
+\end{tabular}
+
+\begin{code}
+ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
+
+conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
+niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
+\end{code}
+
+\begin{mathpar}
+\and
+\inferrule[I-fork]
+{ 
+|iS' = iS [ id' mapsto nil ]|\\
+|tS' = klone(tS)|\\
+|it1 = fullconf id il tS (iniE id')|\\
+|itnew = fullconf id' il tS' (TI ie)|\\
+|fresh (id')|
+}
+{|
+iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
+.->
+iS'; sched fork (it1, ldots, itnew)
+|}
 
@@
 \end{mathpar}
-\caption{IFC language and general embedding.}
-\label{fig:ifc}
+\caption{The embedding}
+\label{fig:embedding-grammar}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  &|erase il (iconf iS its) =
+  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
+  &|erase il (tconf id il' ie) =| \begin{cases}
+    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
+    |bullet| & |il' cantFlowTo il| \\
+    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
+  \end{cases} \\
+  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
+  &|erase il Q = filter il Q|\\
+  &|erase il (send id il' ie) =| \begin{cases}
+    |send id il' bullet| & |il' cantFlowTo il| \\
+    |send id il' (erase il ie)| & \text{otherwise}
+  \end{cases} \\
+  &\text{In all other cases, |erasef il| is applied homomorphically.}
+\end{align*}
+\caption{Erasure function.}
 \end{figure}

### 2014-02-25 paper/retrofit.tex
Proof checkpoint.

--- 2014-02-24 paper/retrofit.tex
@@
 
+\clearpage % TODO: remove again, but keep for now to not have the text be split across 4 pages.
 \subsection{Formal Guarantees}
@@
 \begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
+  \Red{It seems that the theorem, lemma as well as the proofs need to talk
+    about |il| equivalence of |iS|, too, not just |il| equivalence of tasks.}
+
   We proof the lemma by induction on the derivation
   for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
-  could have been used to make the reduction step.
+  could have been used to make the reduction step.  In all cases, there
+  needs to exist a task |it1| at the beginning of the list of |its1|.
+  Consider two cases:
+  \begin{itemize}
+    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
+    step for
+    |its2|, because |its2'=its2| will already be |il|-equivalent to |its'|.
+    In particular, note that 
+    To see that, note that all existing tasks in |its1| are left in the
+    same order and unmodified, except for |it1| (which has no
+    corresponding task in |its2|, since it gets filtered).  The task |it1|
+    gets dropped (by \textsc{I-noStep}), or
+    transforms into a new task |it1'| as well as potentially spawning a new
+    task |it1''|.  Since both |it1'| and |it1''| have a label that is
+    at least as high as the label of |it1|, they will also get filtered.
+
+    \alphacondition{We need all scheduling policies to not change the order
+      of any tasks (except for the first one).  Newly spawned task can appear
+      anywhere in the list.}
+    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
+    task |it2|, such that $|it1|\approx_{|il|}|it2|$ (otherwise |its1| and
+    |its2| could not be |il| equivalent).
+    However, |it2| might not be at the beginning of the task list yet, but
+    all tasks occurring before it must get erased by |erasef il|.
+    In |its2|, we can first take some number of steps until |it2| moves
+    to the front of the list (\Red{Say more precisely why
+      (basically because we require the scheduling policy to do that)}).
+
+    \alphacondition{The scheduling policy must eventually let any task in
+      the task list evaluate.  In particular, it cannot get stuck when the
+      first task gets stuck, or keep executing a small number of tasks
+      exclusively forever (e.g. just execute the first task all the time
+      if it gets into an infinite loop).}
+
+    Therefore, after |its2| has potentially executed some number of steps
+    to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
+    get erased and are |il| equivalent.  We consider all
+    possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
     \begin{description}
@@
     \end{description}
+  \end{itemize}
 \end{proof}

### 2014-02-25 paper/retrofit.tex
More text
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
+Next, we describe the IFC language.  \Red{Description of the IFC language as
+a standard floating label system, or backwards reference to the
+background section.}  In Figure~\ref{fig:ifc}, we describe the syntax
+of the language, and provide rules for all operations which operate on a single
+thread.  \Red{One could imagine these rules giving the definition of a very
+boring information flow control language, by defining |niconf iS id il ie| appropriately
+and providing an appropriate erasure function.}
+
+We use the notation |filter il Q| to indicate a filter function which removes message whose labels do not
+flow to |il|. Specifically, if |Q| is the empty list |nil|, the
+function is simply the identity function, i.e.,
+|filter il nil = nil|; otherwise:
+\[
+|filter il ((il', id, ie) , Q )| = \left\{
+\begin{array}{l l}
+|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
+|filter il Q| & \quad \text{otherwise}
+\end{array} \right.
+\]
+
 %   \begin{figure}
@@
 Q    ::=  nil | io , Q
-
-CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
 \end{code}
@@
 \begin{mathpar}
-%   \and
-%   \inferrule[I-done]
-%   {|
-%   |}
-%   {|
-%   iconf iS (fullconf id il tS iv, ldots)
-%   .->
-%   iS ; sched done (fullconf id il tS iv, ldots)
-%   |}
-
-\and
-\inferrule[I-noStep]
-{|
-iconf iS (it, ldots) .-/> 
-|}
-{|
-iconf iS (it, ldots)
-.->
-iS ; sched noStep (it, ldots)
-|}
 
@@
 \end{mathpar}
-\caption{IFC language}
+\caption{IFC language, single-thread operations}
 \label{fig:ifc}
 \end{figure}
+
+Finally, in Figure~\ref{fig:embedding},
+we provide all of the rules responsible for actually carrying out the embedding:
+
+\begin{itemize}
+    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
+\Red{For now, we defer discussion on how these boundaries mediate between the type systems of the two languages.}
+    \item We reinterpret |CE| to be evaluation contexts on threadpools.  By assumption, only the first thread in the threadpool executes.
+    \item We define |->|, operation on a single thread, in terms of |.->|, operation on thread pools.
+The correspondence is simple: a thread executes a step, and then is rescheduled in the thread pool according to schedule policy $\alpha$.
+\Red{More on schedule policies later}
+    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
+\Red{As written, these rules will not preserve type-safety of the underyling language, but it is easy to adjust them to ensure they do so.}
+\end{itemize}
+
+The fork rule is of particular interest; it is defined in terms of a function $\kappa$.
+Conservatively, $\kappa$ may be simply thought of as the identity function, in which
+case the semantics of fork are such that the state of the target language is \emph{cloned}
+when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
+to remove entries from the state.  \Red{For more information about when this is not the
+fork semantics you want, see the concrete implementation section.}
 
@@
 ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
-
 conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
 niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
+CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
 \end{code}
@@
 \and
+\inferrule[I-done]
+{|
+|}
+{|
+iconf iS (fullconf id il tS iv, ldots)
+.->
+iS ; sched done (fullconf id il tS iv, ldots)
+|}
+
+\and
+\inferrule[I-noStep]
+{|
+iconf iS (it, ldots) .-/> 
+|}
+{|
+iconf iS (it, ldots)
+.->
+iS ; sched noStep (it, ldots)
+|}
+
+\and
 \inferrule[I-border]
@@
 \caption{The embedding}
-\label{fig:embedding-grammar}
+\label{fig:embedding}
 \end{figure}
@@
 
-The filter function |filter il Q| removes message whose labels do not
-flow to |il|. Specifically, if |Q| is the empty list |nil|, the
-function is simply the identity function, i.e.,
-|filter il nil = nil|; otherwise:
-\[
-|filter il ((il', id, ie) , Q )| = \left\{
-\begin{array}{l l}
-|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
-|filter il Q| & \quad \text{otherwise}
-\end{array} \right.
-\]
-
-In the case of extending
+\Red{When both languages have booleans, it is relatively simple to define
+a natural embedding which preserves booleans across boundaries.}
 \begin{mathpar}

### 2014-02-25 paper/retrofit.tex
Caps
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Proof checkpoint.

@@
 \end{code}
-\caption{scheduling policies}
+\caption{Scheduling policies}
 \end{figure}
@@
     to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
-    get erased and are |il| equivalent.  We consider all
+    get erased and are |il| equivalent.
+    We consider all
     possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
     \begin{description}
+      \item[Case \textsc{I-setLabel}]
+        From the form of the rule we know that the expression |ie1| executing
+        in task |it1| is of the form |iniE (setLabel il)|.
+        If |it2| is also of the form |iniE' (setLabel il)| for some
+        |iniE'| that is |il| equivalent to |iniE|,
+        then~\eqref{eq:tsni-lemma-rhs}
+        holds by executing the same step.
+        Otherwise, if the two are not syntactically equivalent, then
+        |it1| must contain a |send| that gets erased by |erasef il|, and
+        must currently be executing the part that got erased.
+        \Red{this reasoning is not actually right.  will be fixed shortly.}
       \item[Case \textsc{I-done}] 
@@
       \item[Case \textsc{I-fork}] 
-      \item[Case \textsc{I-setLabel}]
     \end{description}

### 2014-02-25 paper/retrofit.tex
Fix erase.

@@
     |bullet| & |il' cantFlowTo il| \\
-    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
+    |tconf id il' ie| & \text{otherwise}
   \end{cases} \\
@@
   &|erase il Q = filter il Q|\\
-  &|erase il (send id il' ie) =| \begin{cases}
-    |send id il' bullet| & |il' cantFlowTo il| \\
-    |send id il' (erase il ie)| & \text{otherwise}
-  \end{cases} \\
   &\text{In all other cases, |erasef il| is applied homomorphically.}

### 2014-02-25 paper/concrete.tex
More text.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 each thread to have a separate ML heap.  In an actual implementation, we
-might like to only have a \emph{single} heap, with some restrictions to
-enforce the illusion of separate heaps.  If these restrictions cause our
-implementation semantics to behave in the same way as the specification
-semantics (modulo some extra conditions), we might hope that we also
-automatically achieve non-interference.
+might like to only have a single heap, but disallowing the
+passing of references between threads.  This restriction maintains a
+correspondence between the abstract multiple heaps and the concrete
+single heap.  As long as we don't add any extra transitions which directly
+leak secret data, we might hope that non-interference follows
+immediately.
 
-We can make this formal as follows: \Red{Define some notation}
+However, when proving termination-\emph{sensitive} non-interference, we
+cannot allow an arbitrary restrictions.  Consider a trivial state
+machine as shown in Figure~\ref{fig:trivial-sm}, whose second projection
+is classified secret.  With all three transitions, this language
+fulfills termination-sensitive noninterference.  Furthermore, if the
+dashed line is removed, the language continues to satisfy TSNI.
+However, if any solid line is removed, however, the language fails TSNI.
+Only \emph{some} transitions may be removed safely.
+
+\begin{figure}
+    States: $(x,y)$ for $x,y \in \{0,1\}$ \\
+    Erasure function: $f(x,y) = (x,\bullet)$
+
+    \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
+        \node (A) {$(1,1)$};
+        \node (B) [right of=A] {$(1,0)$};
+        \node (C) [below of=A] {$(0,1)$};
+        \node (D) [right of=C] {$(0,0)$};
+        \draw[->] (A) to node {} (B);
+        \draw[->] (C) to node {} (D);
+        \draw[->, dashed] (B) to node {} (D);
+    \end{tikzpicture}\end{center}
+
+    \label{fig:trivial-sm}
+    \caption{A trivial state machine}
+\end{figure}
+
+In order to capture the condition with which transitions may be removed
+safely, we require a novel, stronger variant of termination-sensitive
+noninterference:
+
+\begin{lemma}[Erased-transition/transition simulation (ETTS)]
+    For any state |C|, if |erase l C .-> delta|, then there exists a |C'| such that
+    |erase l C' = delta| and |C .=> C'|.
+\end{lemma}
+
+Traditional TSNI is an easy corollary of this lemma.  Now we can state
+the result:
 
@@
     functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
-    states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
-    id$ and $f^{-1} \circ e' \circ f = e$.  Then to show termination sensitive non-interference for $L'$,
+    states between $L$ and $L'$, obeying the conditions:
+
+    \begin{itemize}
+        \item $f$ is functorial over $l$-equivalence: if
+            $|Q1| \approx'_l |Q2|$ then $f(|Q1|) \approx_l f(|Q2|)$.
+    \end{itemize}
+
+    (Probably $f^{-1} \circ f =
+    id$ and $f^{-1} \circ e' \circ f = e$)  Then to show termination sensitive non-interference for $L'$,
     it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
@@
 over reduction derivations in the first step.
+
+We have $ts'_1 \approx_l ts'_2$ and would like to show $f(ts'_1) \approx_l f(ts'_2)$;
+this can be seen by expanding the definition of
 \end{proof}

### 2014-02-25 paper/retrofit.tex
Clean up theorem statement.

@@
 \begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
-  For any list of tasks |its1|, |its2|, |its2|, label |il|,
-  IFC states |iS1|, |iS2|, |iS1'|, where
+  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
   \begin{equation} \label{eq:tsni-lhs}
-    |its1| \approx_{|il|} |its2|
+    |ic1| \approx_{|il|} |ic2|
     \qquad \text{and} \qquad
-    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
+    |ic1| |.->|^* |ic1'|
   \end{equation}
-  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
+  then there exists a configuration |ic2'| such that
   \begin{equation} \label{eq:tsni-rhs}
-    |its1'| \approx_{|il|} |its2'|
+    |ic1'| \approx_{|il|} |ic2'|
      \qquad \text{and} \qquad
-    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
+    |ic2| |.->|^* |ic2'|
     \ \text{.}
@@
   \label{lemma:tsni}
-  For any list of tasks |its1|, |its2|, |its2|, label |il|,
-  IFC states |iS1|, |iS2|, |iS1'|, where
+  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
   \begin{equation} \label{eq:tsni-lemma-lhs}
-  |its1| \approx_{|il|} |its2|
+  |ic1| \approx_{|il|} |ic2|
   \qquad \text{and} \qquad
-  |iconf iS1 its1| |.->| |iconf iS1' its1'|
+  |ic1| |.->| |ic1'|
   \end{equation}
-  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
+  then there exists a configuration |ic2'| such that
   \begin{equation} \label{eq:tsni-lemma-rhs}
-  |its1'| \approx_{|il|} |its2'|
+  |ic1'| \approx_{|il|} |ic2'|
   \qquad \text{and} \qquad
-  |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
+  |ic2| |.->|^* |ic2'|
   \ \text{.}

### 2014-02-25 paper/retrofit.tex
Improve proof.

@@
   of length 0 is trivial, allowing
-  us to simple chose $|its2'=its2|$ and $|iS2'=iS2|$.  In the step case, we assume
+  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
   the theorem holds for derivation sequences of length up to $n$, and show that it also
@@
   \[
-  |iconf iS1 its1| |.->| |iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|
+  |ic1| |.->| |ic1''| |.->|^n |ic1'|
   \]
-  for some IFC state |iS1''| and task list |its1''|.  By Lemma~\ref{lemma:tsni}, we get
-  |its2''| and |iS2''| with
+  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
+  |ic''| with
   \begin{equation} \label{eq:tsni-proof-1}
-  |its1''| \approx_{|il|} |its2''|
+  |ic1''| \approx_{|il|} |ic2''|
   \qquad \text{and} \qquad
-  |iconf iS2 its2| |.->|^* |iconf iS2'' its2''|
+  |ic2| |.->|^* |ic2''|
   \end{equation}
   Applying the induction hypothesis to
-  $|iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|$, we get |its2'| and |iS2'| with
+  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
   \begin{equation} \label{eq:tsni-proof-2}
-  |its1'| \approx_{|il|} |its2'|
+  |ic1'| \approx_{|il|} |ic2'|
   \qquad \text{and} \qquad
-  |iconf iS2'' its2''| |.->|^* |iconf iS2' its2'|
+  |ic2''| |.->|^* |ic2'|
   \end{equation}
@@
 \begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
-  \Red{It seems that the theorem, lemma as well as the proofs need to talk
-    about |il| equivalence of |iS|, too, not just |il| equivalence of tasks.}
-
   We proof the lemma by induction on the derivation
   for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
-  could have been used to make the reduction step.  In all cases, there
-  needs to exist a task |it1| at the beginning of the list of |its1|.
-  Consider two cases:
+  could have been used to make the reduction step.
+  First, we observe there must be at least one task in |ic1|, otherwise
+  it could not take a step.  Thus, |ic1| is of the form
+  |iconf iS1 (it1, its1)|.  Consider two cases:
   \begin{itemize}
@@
     step for
-    |its2|, because |its2'=its2| will already be |il|-equivalent to |its'|.
-    In particular, note that 
-    To see that, note that all existing tasks in |its1| are left in the
-    same order and unmodified, except for |it1| (which has no
-    corresponding task in |its2|, since it gets filtered).  The task |it1|
+    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
+    To see that, note that the tasks |its1| in |ic1| are left in the
+    same order and unmodified. The task |it1| either
     gets dropped (by \textsc{I-noStep}), or
@@
     task |it1''|.  Since both |it1'| and |it1''| have a label that is
-    at least as high as the label of |it1|, they will also get filtered.
+    at least as high as the label of |it1|, they will get filtered
+    by |erasef il| in |ic1'|.
+    Finally, lets consider the possible changes to |iS1|: If |it1| sends a
+    message, then the corresponding queue in |iS1'| will contain one
+    more message.  However, that message has the label of |it1| (or a higher
+    label), and will thus get erased by |erasef il|.
+    \Red{The task could also send a message}
+    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.
 
@@
     \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
-    task |it2|, such that $|it1|\approx_{|il|}|it2|$ (otherwise |its1| and
-    |its2| could not be |il| equivalent).
+    task |it2| in |ic2|,
+    such that |it1=it2| (otherwise |ic1| and
+    |ic2| could not be |il| equivalent).
     However, |it2| might not be at the beginning of the task list yet, but
     all tasks occurring before it must get erased by |erasef il|.
-    In |its2|, we can first take some number of steps until |it2| moves
+    In |ic2|, we can first take some number of steps until |it2| moves
     to the front of the list (\Red{Say more precisely why
@@
 
-    Therefore, after |its2| has potentially executed some number of steps
-    to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
-    get erased and are |il| equivalent.
-    We consider all
-    possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
-    \begin{description}
-      \item[Case \textsc{I-setLabel}]
-        From the form of the rule we know that the expression |ie1| executing
-        in task |it1| is of the form |iniE (setLabel il)|.
-        If |it2| is also of the form |iniE' (setLabel il)| for some
-        |iniE'| that is |il| equivalent to |iniE|,
-        then~\eqref{eq:tsni-lemma-rhs}
-        holds by executing the same step.
-        Otherwise, if the two are not syntactically equivalent, then
-        |it1| must contain a |send| that gets erased by |erasef il|, and
-        must currently be executing the part that got erased.
-        \Red{this reasoning is not actually right.  will be fixed shortly.}
-      \item[Case \textsc{I-done}] 
-      \item[Case \textsc{I-noStep}] 
-      \item[Case \textsc{I-fork}] 
-    \end{description}
+    Therefore, after |ic2| has potentially executed some number of steps
+    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
+    get erased and are thus equivalent.
+    The task |it2| can now take exactly the same step as |it1|;  we only
+    need to argue that the potential differences in |iS1| and |iS2| cannot
+    have an influence on the execution (and we know |iS1| and |iS2| are
+    |il| equivalent).
+    \Red{Actually show this}
   \end{itemize}

### 2014-02-25 paper/retrofit.tex
Fix erase, and proof.

@@
   \end{cases} \\
-  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
+  &|erase il nil = nil|\\
+  &|erase il (iS [id mapsto Q]) =| \begin{cases}
+    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
+    & \text{the label of thread |id|} \\
+    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
+  \end{cases} \\
   &|erase il Q = filter il Q|\\
@@
     by |erasef il| in |ic1'|.
-    Finally, lets consider the possible changes to |iS1|: If |it1| sends a
+    Lets consider the possible changes to |iS1|: If |it1| sends a
     message, then the corresponding queue in |iS1'| will contain one
@@
     label), and will thus get erased by |erasef il|.
-    \Red{The task could also send a message}
+    Finally, receiving or not receiving a message (by
+    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
+    task |it1|, which are erased from |iS1|.
     This ensures that $|ic1'|\approx_{|il|}|ic2'|$.
@@
     |il| equivalent).
-    \Red{Actually show this}
+    Again, only send and receive will change |iS|, so we consider all
+    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
+    a message is sent, then the message is added to the same queue.  This
+    queue is either completely erased, or it is |il| equivalent.  In both
+    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
+    When the tasks are receiving a message, then by the reduction rules
+    we know that they first filter the queue by the label of |it1|.  We
+    also know that the queues are equivalent when filtered by the less
+    restrictive label |il|, thus the messages received (or dropped) from the
+    queue are equivalent.
   \end{itemize}

### 2014-02-26 paper/concrete.tex
More nattering around.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \begin{lemma}[Erased-transition/transition simulation (ETTS)]
-    For any state |C|, if |erase l C .-> delta|, then there exists a |C'| such that
+    For any state |C|, if |erase l C ..-> delta|, then there exists a |C'| such that
     |erase l C' = delta| and |C .=> C'|.
@@
 
-Traditional TSNI is an easy corollary of this lemma.  Now we can state
-the result:
+Traditional TSNI is an easy corollary of this lemma.  \Red{Need to argue
+this is provable!} Now we can state the result:
 
@@
     Suppose we have a abstract specification language $L$ with machine
-    states $|C|$, evaluation relation $|.->|$ and erasure function $e$.
-    Furthermore we have a proof that this language fulfills termination
-    sensitive non-interference: if $|C1| \approx_l |C2|$ and $|C1|
-    |.->|^* |C1'|$, then there exists a $|C2'|$ such that $|C2| |.->|^*
-    |C2'|$ and $|C1'| \approx_l |C2'|$.
+    states $|C|$, evaluation relation $|.->|$, erasure function $|erasef l|$,
+    and a proof that ETTS holds.
 
-    Next, suppose we have a language $L'$ with machine states $|Q|$,
-    evaluation relation $|.->|'$ and erasure function $e'$.  Given
-    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
-    states between $L$ and $L'$, obeying the conditions:
+    Next, suppose we have a language $L'$ with machine states $|C'|$,
+    evaluation relation $|.->|'$ and erasure function $|erasef l|'$.  We demand that this
+    language be related to $L$ in the following way:
 
     \begin{itemize}
-        \item $f$ is functorial over $l$-equivalence: if
-            $|Q1| \approx'_l |Q2|$ then $f(|Q1|) \approx_l f(|Q2|)$.
+        \item There are functions $f : |C' -> C|$ and $f^{-1} : |C -> C'|$ which is functorial
+            over $l$-equivalences: e.g. if $|C| \approx'_l |C'|$ then
+            $f(|C|) \approx_l f(|C'|)$ and vice versa.
     \end{itemize}
 
-    (Probably $f^{-1} \circ f =
-    id$ and $f^{-1} \circ e' \circ f = e$)  Then to show termination sensitive non-interference for $L'$,
-    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
-    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
-    \ldots
+    Then ETTS holds for language $L'$.
 \end{theorem}
@@
 \begin{proof}
+We need to show that for all choices of $|C1'|$, there exists a $|C2'|$ with
+the desired properties.  We proceed by induction on the erased-transition.
+There are two cases.  In the first case, there is a one-to-one correspondence
+between reduction relations in
+
 Our proof proceeds along the same lines as a traditional TSNI proof,

### 2014-02-26 paper/concrete.tex
Theorem statement.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 each thread to have a separate ML heap.  In an actual implementation, we
-might like to only have a single heap, but disallowing the
-passing of references between threads.  This restriction maintains a
-correspondence between the abstract multiple heaps and the concrete
-single heap.  As long as we don't add any extra transitions which directly
-leak secret data, we might hope that non-interference follows
-immediately.
+might like to only have a single heap and disallow the passing of
+references between threads.  This restriction maintains a correspondence
+between the abstract multiple heaps and the concrete single heap.  We might
+hope that we can prove noninterference for this new system by reusing
+noninterference for the old system.
 
-However, when proving termination-\emph{sensitive} non-interference, we
-cannot allow an arbitrary restrictions.  Consider a trivial state
-machine as shown in Figure~\ref{fig:trivial-sm}, whose second projection
-is classified secret.  With all three transitions, this language
-fulfills termination-sensitive noninterference.  Furthermore, if the
-dashed line is removed, the language continues to satisfy TSNI.
-However, if any solid line is removed, however, the language fails TSNI.
-Only \emph{some} transitions may be removed safely.
+However, modifying operational rules poses a distinct problem for
+preserving non-interference.  Consider a trivial state machine as shown
+in Figure~\ref{fig:trivial-sm}, whose second projection is classified
+secret.  With all three transitions, this language fulfills
+termination-sensitive noninterference.  Furthermore, if the dashed line
+is removed, the language continues to satisfy TSNI.  However, if any
+solid line is removed, however, the language fails TSNI.
 
@@
 
-In order to capture the condition with which transitions may be removed
-safely, we require a novel, stronger variant of termination-sensitive
-noninterference:
+The approach we will take is in two steps.  First, we sidestep the
+restriction problem by demanding that the concrete implementation be
+\emph{isomorphic} to the abstract specification, but perhaps having a different
+runtime representation (a single heap) and some well-formedness
+condition (every item on the heap only contains pointers from a single
+location).  Isomorphism will preserve nonintereference, but it will also means all
+transitions in the abstract language have to be implemented, including
+undesirable transitions such as sending a pointer to another thread makes
+the pointer dangling.  Next, we define a desugaring into this language
+which adds dynamic checks, eliminating the possibility for these undesirable
+transitions to be exercised.
 
-\begin{lemma}[Erased-transition/transition simulation (ETTS)]
-    For any state |C|, if |erase l C ..-> delta|, then there exists a |C'| such that
-    |erase l C' = delta| and |C .=> C'|.
-\end{lemma}
-
-Traditional TSNI is an easy corollary of this lemma.  \Red{Need to argue
-this is provable!} Now we can state the result:
-
-\begin{theorem}
-    Suppose we have a abstract specification language $L$ with machine
-    states $|C|$, evaluation relation $|.->|$, erasure function $|erasef l|$,
-    and a proof that ETTS holds.
-
-    Next, suppose we have a language $L'$ with machine states $|C'|$,
-    evaluation relation $|.->|'$ and erasure function $|erasef l|'$.  We demand that this
-    language be related to $L$ in the following way:
-
-    \begin{itemize}
-        \item There are functions $f : |C' -> C|$ and $f^{-1} : |C -> C'|$ which is functorial
-            over $l$-equivalences: e.g. if $|C| \approx'_l |C'|$ then
-            $f(|C|) \approx_l f(|C'|)$ and vice versa.
-    \end{itemize}
-
-    Then ETTS holds for language $L'$.
+\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+    Consider a language \tar{L} with configurations |tc|, reduction
+    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
+    language \ifc{L} with configurations |ic|, reduction relation
+    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
+    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
+    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
+    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
+    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
+    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
+    Then if \ifc{L} satisfies termination sensitive non-interference,
+    then \tar{L} satisfies termination sensitive non-interference.
 \end{theorem}
@@
 \begin{proof}
-We need to show that for all choices of $|C1'|$, there exists a $|C2'|$ with
-the desired properties.  We proceed by induction on the erased-transition.
-There are two cases.  In the first case, there is a one-to-one correspondence
-between reduction relations in
-
-Our proof proceeds along the same lines as a traditional TSNI proof,
-we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
-over reduction derivations in the first step.
-
-We have $ts'_1 \approx_l ts'_2$ and would like to show $f(ts'_1) \approx_l f(ts'_2)$;
-this can be seen by expanding the definition of
+    Easy application of TSNI \tar{L} by applying $f$
 \end{proof}
-
-To provide a sense of how these conditions work, we give an example
-use of these theorem:
-
-\begin{theorem}
-    The language described in Figure X satisfies termination sensitive non-interference.
-\end{theorem}
-
-\begin{code}
-\end{code}
 

### 2014-02-26 paper/concrete.tex
Fix typo and put in the proof.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
-    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
+    = id$, $f^{-1} \circ f = id$, and that $f$ and $f^{-1}$ are
     functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
@@
 \begin{proof}
-    Easy application of TSNI \tar{L} by applying $f$
+    Easily shown by transporting configurations and reduction derivations
+    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
+    configuration and derivation back.
 \end{proof}

### 2014-02-26 paper/concrete.tex
Definitions
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-26 paper/concrete.tex
@@
 
-\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
-    Consider a language \tar{L} with configurations |tc|, reduction
-    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
-    language \ifc{L} with configurations |ic|, reduction relation
-    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
-    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
-    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
-    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
+\begin{definition}[Information-flow control language]
+    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
+    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
+    $|C|^*$ is the type of erased machine configurations, |.->| is a
+    reduction relation between machine configurations and $|erasef l|$
+    is an erasure function from machine configurations to erased machine
+    configurations.
+\end{definition}
+
+\begin{definition}[$l$-equivalence]
+    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
+    if $|erase l c| = |erase l c'|$.
+\end{definition}
+
+\begin{definition}[Isomorphism of information-flow control languages]
+    Two languages
+    \tar{L} $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ and \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist (total) functions
+    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
+    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and that $f$ and $f^{-1}$ are
     functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
     |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
+\end{definition}
+
+\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
     Then if \ifc{L} satisfies termination sensitive non-interference,
@@
 \begin{proof}
-    Easy application of TSNI \tar{L} by applying $f$
+    Easily shown by transporting configurations and reduction derivations
+    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
+    configuration and multi-step derivation back.
 \end{proof}

### 2014-02-26 paper/concrete.tex
Add back the necessary thing.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \begin{theorem}[Isomorphism preserves termination sensitive non-interference]
-    Then if \ifc{L} satisfies termination sensitive non-interference,
-    then \tar{L} satisfies termination sensitive non-interference.
+    If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
+    \tar{L} satisfies TSNI.
 \end{theorem}

### 2014-02-26 paper/retrofit.tex
tini

@@
 .->
-iS'; sched fork (it1, ldots, itnew)
+iS'; sched F (it1, ldots, itnew)
 |}
@@
 .->
-iS ; sched done (fullconf id il tS iv, ldots)
+iS ; sched D (fullconf id il tS iv, ldots)
 |}
@@
 .->
-iS ; sched noStep (it, ldots)
+iS ; sched N (it, ldots)
 |}
@@
   \end{cases} \\
-  &|erase il nil = nil|\\
   &|erase il (iS [id mapsto Q]) =| \begin{cases}
@@
   \end{cases} \\
-  &|erase il Q = filter il Q|\\
-  &\text{In all other cases, |erasef il| is applied homomorphically.}
+  &|erase il Q = filter il Q|
 \end{align*}
-\caption{Erasure function.}
+\caption{
+Erasure function for configurations, threads, system state, and
+message queus.  In all other cases, |erasef il| is applied
+homomorphically.
+\label{fig:erasure}
+}
 \end{figure}
@@
 \begin{figure}
-  Round robin:
+  Concurrent, round robin:
 \begin{code}
-  sched step (it1, it2, ...)    = {it2, ..., it1}
-  sched done (it1, it2, ...)    = {it2, ...}
-  sched noStep (it1, it2, ...)  = {it2, ...}
-  sched fork (it1, it2, ...)    = {it2, ..., it1}
-\end{code}
-  Browbound:
-\begin{code}
-  sched step (it1, it2, ...)    = {it1, it2, ...}
-  sched noStep (it1, it2, ...)  = {it2, ...}
-  sched done (it1, it2, ...)    = {it2, ...}
-  sched fork (it1, it2, ...)    = {it1, it2, ...}
+  sched S (it1, it2, ldots)  = it2, ldots, it1
+  sched D (it1, it2, ldots)  = it2, ldots
+  sched N (it1, it2, ldots)  = it2, ldots
+  sched F (it1, it2, ldots)  = it2, ldots, it1
 \end{code}
@@
 \begin{code}
-  sched step (it1, it2, ...)       = {it1, it2, ...}
-  sched noStep (it1, it2, ...)     = {it1, it2, ...}
-  sched done (it1, it2, ...)       = {it2, ...}
-  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
+  sched S (it1, it2, ldots)        = it1, it2, ldots
+  sched N (it1, it2, ldots)        = it1, it2, ldots
+  sched D (it1, it2, ldots)        = it2, ldots
+  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
 \end{code}
@@
 
+\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
+  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
+  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
+   $|ic1| \approx_{|il|} |ic2|$,
+   $|ic1| |.->|^* |ic1'|$, and
+   $|ic2| |.->|^* |ic2'|$, then
+   $|ic1'| \approx_{|il|} |ic2'|$.
+\end{theorem}
+
 \subsection{Generalizing further}

### 2014-02-27 paper/concrete.tex
concrete checkpoint.

--- 2014-02-26 paper/concrete.tex
@@
 \label{sec:concrete}
+
+The operational semantics we have derived in the previous section
+satisfy termination sensitive non-interference by design.  However,
+these abstract semantics essentially require that different tasks
+execute completely isolated.  For instance, for the mini-ML language,
+this means that every task has it's own heap.  For practical
+implementations this is often not desirable.  Instead, we would like to
+more tightly couple the integration of the target and IFC
+language by reusing existing infrastructure.  In the running example,
+a concrete implementation might use a single global heap, and ensure
+that references do not cross task boundaries, and thus preserving
+non-interference.
+
+In this section, we will detail an approach that allows one to implement
+a concrete system differently from our proposal in the previous
+section, and give conditions for when such a system preserves termination
+sensitive non-interference.
+We explain the idea for the single heap mini-ML language, and then
+generalize to arbitrary systems.
+
+\subsection{IFC-Mini-ML with a Single Heap}
+
+Instead of using a configuration of the form
+|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|
+where every task has its
+own ML heap, we would like a single global heap as in
+|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
+Furthermore, we keep up a fictional separation between the portions
+of the global heap that tasks can use by forbidding references to
+cross task boundaries. Most
+of the operational rules can easily be adapted to work with these
+new configurations.  In the abstract system, the \textsc{I-fork}
+rule created a new heap for the new task to execute in.  Since we
+want to forbid references to cross task boundaries, we do not modify
+the global heap and instead add an additional premise that the forked
+expression |ie| must not contain any references.
+Finally, we add the same condition to the \textsc{I-send} rule.
+Tasks that try to fork or send an expression that contains a
+reference will now get stuck, and will stop executing by the
+\textsc{I-noStep} rule.
+
+\Red{Show the key rules here.}
+
+As we have outlined the IFC-Mini-ML language with a single heap, we
+effectively restrict the abstract semantics in some cases (namely
+to not allow the passing of references) as well as using a different
+way to represent the heap.  How can we be sure that these
+new, \textit{concrete semantics} for our system still satisfy
+termination-sensitive non-interference?
+
+This isn't trivial, as it is not sound to add arbitrary additional
+conditions on evaluation rules.  To see this, consider a contrived
+concrete system where we add a premise to a reduction rule that
+stops a task based on secret information.  Such a system will
+not satisfy non-interference, as it allows other tasks on the
+same level to observe the termination of that task and thus the
+secret information which was used to decide if the task terminates
+or not.
+\Red{This last part is written poorly.  Let's do it better, or remove it.}
+
+\subsection{Correctness of Concrete Semantics}
+
+\Red{Say what do we do here.}
+
+\Red{At some point in this section we should say a little about
+  why the abstract setting needs complete isolation (because it
+  works for \textit{any} language), and that this is sometimes
+  what you want.}
+
+\subsection{\Red{Previous Stuff (to be merged/removed as necessary)}}
 
@@
     $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
-    = id$, $f^{-1} \circ f = id$, and that $f$ and $f^{-1}$ are
+    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
     functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
@@
 \begin{proof}
-    Easily shown by transporting configurations and reduction derivations
-    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
-    configuration and derivation back.
+    Easy application of TSNI \tar{L} by applying $f$
 \end{proof}

### 2014-02-27 paper/concrete.tex

@@
 
-\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
-    Consider a language \tar{L} with configurations |tc|, reduction
-    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
-    language \ifc{L} with configurations |ic|, reduction relation
-    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
-    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
-    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
-    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
+\begin{definition}[Information-flow control language]
+    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
+    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
+    $|C|^*$ is the type of erased machine configurations, |.->| is a
+    reduction relation between machine configurations and $|erasef l|$
+    is an erasure function from machine configurations to erased machine
+    configurations.
+\end{definition}
+
+\begin{definition}[$l$-equivalence]
+    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
+    if $|erase l c| = |erase l c'|$.
+\end{definition}
+
+\begin{definition}[Isomorphism of information-flow control languages]
+    Two languages
+    \tar{L} $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ and \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist (total) functions
+    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
+    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and that $f$ and $f^{-1}$ are
     functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
     |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
-    Then if \ifc{L} satisfies termination sensitive non-interference,
-    then \tar{L} satisfies termination sensitive non-interference.
+\end{definition}
+
+\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+    If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
+    \tar{L} satisfies TSNI.
 \end{theorem}

### 2014-02-27 paper/concrete.tex
Finish iso proofs.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
+\Red{Move these definitions earlier}
+
 \begin{definition}[Information-flow control language]
@@
     is an erasure function from machine configurations to erased machine
-    configurations.
+    configurations.  For sequential languages, we may also speak of
+    values, e.g. a configurations $V \subseteq |C|$ for which there are
+    no possible further transitions.
 \end{definition}
@@
 
+Before we show isomorphism preserves termination sensitive
+non-interference, we'd like to remark that one can safely remove transitions
+and preserve termination \emph{insensitive} interference:
+
+\begin{definition}[Inclusion of information-flow control languages]
+    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
+    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
+    l|})$ if there exists a total function $f : |tC -> iC|$ such that
+    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
+    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
+    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
+    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
+    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
+\end{definition}
+
+\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
+    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
+    \tar{L} satisfies TINI.
+\end{theorem}
+
+\begin{proof}
+    Shown by transporting configurations and reduction derivations
+    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
+    equivalence back using bijectivity of $f$ over $l$-equivalences.
+\end{proof}
+
+Now we strengthen the condition to show TSNI:
+
 \begin{definition}[Isomorphism of information-flow control languages]
-    Two languages
-    \tar{L} $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ and \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist (total) functions
+    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
+    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
     $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
-    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and that $f$ and $f^{-1}$ are
-    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
-    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
+    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
+    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
+    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
+    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
 \end{definition}
@@
 \begin{proof}
-    Easily shown by transporting configurations and reduction derivations
-    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
-    configuration and multi-step derivation back.
+    Shown by transporting configurations and reduction derivations from
+    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
+    resulting configuration and multi-step derivation back.
 \end{proof}

### 2014-02-27 paper/retrofit.tex
grammar for blue Sigma
minor

@@
 Q    ::=  nil | io , Q
+iS   ::=  emptyset | iS [ id mapsto Q ]
 \end{code}
@@
   \end{cases} \\
+  &|erase il emptyset = emptyset|\\
   &|erase il (iS [id mapsto Q]) =| \begin{cases}
@@
 \begin{code}
-  sched S (it1, it2, ldots)  = it2, ldots, it1
+  sched step (it1, it2, ldots)  = it2, ldots, it1
   sched D (it1, it2, ldots)     = it2, ldots
@@
 \begin{code}
-  sched S (it1, it2, ldots)        = it1, it2, ldots
+  sched step (it1, it2, ldots)     = it1, it2, ldots
   sched N (it1, it2, ldots)        = it1, it2, ldots
+  sched D (it)                     = it
   sched D (it1, it2, ldots)        = it2, ldots

### 2014-02-27 paper/concrete.tex
thm as def

@@
 
-\begin{definition}[Information-flow control language]
-    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
-    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
-    $|C|^*$ is the type of erased machine configurations, |.->| is a
-    reduction relation between machine configurations and $|erasef l|$
-    is an erasure function from machine configurations to erased machine
-    configurations.  For sequential languages, we may also speak of
-    values, e.g. a configurations $V \subseteq |C|$ for which there are
-    no possible further transitions.
-\end{definition}
-
-\begin{definition}[$l$-equivalence]
-    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
-    if $|erase l c| = |erase l c'|$.
-\end{definition}
-
 Before we show isomorphism preserves termination sensitive

### 2014-02-27 paper/retrofit.tex
thm as def

@@
 \begin{code}
-  sched step (it1, it2, ldots)  = it2, ldots, it1
-  sched D (it1, it2, ldots)     = it2, ldots
-  sched N (it1, it2, ldots)     = it2, ldots
-  sched F (it1, it2, ldots)     = it2, ldots, it1
+  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
+  roundrobin D (it1, it2, ldots)     = it2, ldots
+  roundrobin N (it1, it2, ldots)     = it2, ldots
+  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
 \end{code}
@@
 \begin{code}
-  sched step (it1, it2, ldots)     = it1, it2, ldots
-  sched N (it1, it2, ldots)        = it1, it2, ldots
-  sched D (it)                     = it
-  sched D (it1, it2, ldots)        = it2, ldots
-  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
+  seq step (it1, it2, ldots)     = it1, it2, ldots
+  seq N (it1, it2, ldots)        = it1, it2, ldots
+  seq D (it)                     = it
+  seq D (it1, it2, ldots)        = it2, ldots
+  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
 \end{code}
@@
 
-\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
-  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
+\begin{definition}[Information-flow control language]
+    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
+    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
+    $|C|^*$ is the type of erased machine configurations, |.->| is a
+    reduction relation between machine configurations and $|erasef l|$
+    is an erasure function from machine configurations to erased machine
+    configurations.  For sequential languages, we may also speak of
+    values, e.g. a configurations $V \subseteq |C|$ for which there are
+    no possible further transitions.
+\end{definition}
+
+\begin{definition}[$l$-equivalence]
+    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
+    if $|erase l c| = |erase l c'|$.
+\end{definition}
+
+\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
+  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
+  sensitive non-interfering if for any label |l|, and configurations
+  |c1, c1', c2 member C|, if
   \begin{equation} \label{eq:tsni-lhs}
-    |ic1| \approx_{|il|} |ic2|
+    |c1| \approx_{|l|} |c2|
     \qquad \text{and} \qquad
-    |ic1| |.->|^* |ic1'|
+    |c1| |.->|^* |c1'|
   \end{equation}
-  then there exists a configuration |ic2'| such that
+  then there exists a configuration |c2' member C| such that
   \begin{equation} \label{eq:tsni-rhs}
-    |ic1'| \approx_{|il|} |ic2'|
+    |c1'| \approx_{|l|} |c2'|
      \qquad \text{and} \qquad
-    |ic2| |.->|^* |ic2'|
+    |c2| |.->|^* |c2'|
     \ \text{.}
   \end{equation}
+\end{definition}
+
+\begin{theorem}[TSNI]
 \end{theorem}
@@
 
+\begin{definition}[Termination Insensitive Non-Interference (TINI)]
+  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
+  insensitive non-interfering if for any label |l|, and configurations
+  |c1, c2, V1, V2 member C|, if
+   $|c1| \approx_{|l|} |c2|$,
+   $|c1| |.->|^* |V1|$, and
+   $|c2| |.->|^* |V2|$, then
+   $|V1| \approx_{|l|} |V2|$.
+\end{definition}
+
 \begin{theorem}[Termination Insensitive Non-Interference (TINI)]

### 2014-02-27 paper/concrete.tex
checkpoint.

--- 2014-02-27 paper/concrete.tex
@@
 \label{sec:concrete}
+
+\Red{In this section I only talk about TSNI.  Once we finish the previous
+  section to both talk about TSNI and TINI, we should do the same here.}
 
@@
 
-This isn't trivial, as it is not sound to add arbitrary additional
-conditions on evaluation rules.  To see this, consider a contrived
-concrete system where we add a premise to a reduction rule that
-stops a task based on secret information.  Such a system will
-not satisfy non-interference, as it allows other tasks on the
-same level to observe the termination of that task and thus the
-secret information which was used to decide if the task terminates
-or not.
-\Red{This last part is written poorly.  Let's do it better, or remove it.}
+%This isn't trivial, as it is not sound to add arbitrary additional
+%conditions on evaluation rules.  To see this, consider a contrived
+%concrete system where we add a premise to a reduction rule that
+%stops a task based on secret information.  Such a system will
+%not satisfy non-interference, as it allows other tasks on the
+%same level to observe the termination of that task and thus the
+%secret information which was used to decide if the task terminates
+%or not.
 
@@
 
-\Red{Say what do we do here.}
+We now have a concrete semantics, which both uses a different
+representation for some of the constructs in language (a single
+heap rather than a heap per task in our running example), as well
+as restricting some of the operational rules to disallow
+undesirable transitions.  To show that the concrete semantics
+still satisfy TSNI, we use two techniques.  First, we give a
+condition on what kind of restrictions can be allowed on the
+operational rules.  Secondly, we define the notation of an
+isomorphism between IFC languages and show that it preserves
+non-interference.
+
+Intuitively, there are two scenarios in which non-interference
+can be violated when restricting the transition relation:
+\begin{itemize}
+  \item Adding an additional premise to one of the rules that inspects
+  information which is above the security label of the thread currently
+  executing.
+  \item
+\end{itemize}
 

### 2014-02-27 paper/concrete.tex
Begin portage.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-27 paper/concrete.tex
@@
 
+%{
+%format tyerase c = "\varepsilon("c")"
+%format tyerasef = "\varepsilon"
+%format ^ = " "
+%format c = "c"
+%format c'
+%format cc = "\con{"c"}"
+%format cc'
+%format ac = "\abs{"c"}"
+%format ac'
+%format V = "V"
+%format cV = "\con{"V"}"
+%format aV = "\abs{"V"}"
+%format ~= = "\approx_l"
+%format clequiv = "\con{"~="}"
+%format alequiv = "\abs{"~="}"
+%format creduce = "\con{".->"}"
+%format areduce = "\abs{".->"}"
+%format creducestar = "\con{".=>"}"
+%format areducestar = "\abs{".=>"}"
+%format (ap (f) (x)) = f"("x")"
+
+\begin{definition}[Information-flow control language]
+    An information-flow control language L is a tuple |(C, .->,
+    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
+    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
+    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
+    configurations |tyerase C|.  For sequential languages, the
+    language is augmented with a set of terminal configuration states $V
+    \subseteq |C|$ for which there are no possible further transitions.
+\end{definition}
+
+\begin{definition}[$l$-equivalence]
+    In a language |(C, .->, erasef l)|, two machine configurations
+    $|memberf (c, c') C|$ are considered $l$-equivalent (|c ~= c'|)
+    if |erase l c = erase l c'|.
+\end{definition}
+
+\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
+\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}
+
 Before we show isomorphism preserves termination sensitive
@@
 \begin{definition}[Inclusion of information-flow control languages]
-    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
-    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
-    l|})$ if there exists a total function $f : |tC -> iC|$ such that
-    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
-    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
-    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
-    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
-    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
+    A language \con{|(C, Ce, V, .->, erasef l)|} is included in another
+    language \abs{|(C, Ce, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
+    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
+    |(ap f cc) alequiv (ap f cc')|),
+    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
+    functorial over |.=>| (if
+    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
 \end{definition}
@@
 \begin{theorem}[Isomorphism preserves termination insensitive non-interference]
-    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
-    \tar{L} satisfies TINI.
+    If a language \con{L} is included in a language \abs{L}, and \abs{L}
+    satisfies TINI, then \con{L} satisfies TINI.
 \end{theorem}
@@
     Shown by transporting configurations and reduction derivations
-    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
+    from \con{L} to \abs{L}, applying TINI and transporting the resulting
     equivalence back using bijectivity of $f$ over $l$-equivalences.
@@
     functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
-    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
+    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
     $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
@@
 \end{proof}
+%}
 

### 2014-02-27 paper/concrete.tex
Updated concrete.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-27 paper/concrete.tex
@@
 %format ac'
+%format finv = f"^{-1}"
 %format V = "V"
@@
 %format (ap (f) (x)) = f"("x")"
+%format .. = "\circ"
+%format idf (t) = "id_{"t"}"
 
@@
 \begin{definition}[Inclusion of information-flow control languages]
-    A language \con{|(C, Ce, V, .->, erasef l)|} is included in another
-    language \abs{|(C, Ce, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
+    A language \con{|(C, V, .->, erasef l)|} is included in another
+    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
     |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
@@
 \begin{definition}[Isomorphism of information-flow control languages]
-    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
-    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
-    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
-    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
-    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
-    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
+    A language \con{|(C, .->, erasef l)|} is
+    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
+    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
+    functorial over both $l$-equivalences (if |cc clequiv
+    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
     $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).

### 2014-02-27 paper/concrete.tex
typofix
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     In a language |(C, .->, erasef l)|, two machine configurations
-    $|memberf (c, c') C|$ are considered $l$-equivalent (|c ~= c'|)
+    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
     if |erase l c = erase l c'|.

### 2014-02-27 paper/concrete.tex
Done converting.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-\begin{definition}[Inclusion of information-flow control languages]
-    A language \con{|(C, V, .->, erasef l)|} is included in another
-    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
-    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
-    |(ap f cc) alequiv (ap f cc')|),
-    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
-    functorial over |.=>| (if
-    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
+\begin{definition}[Weak isomorphism of information-flow control languages]
+    A language \con{|(C, .->, erasef l)|} is weakly isomorphic to a
+    language \abs{|(iC, .->, erasef l)|} if there exist total functions
+    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
+    |finv .. f = idf iC|.  Furthermore, the following coherence conditions
+    must hold:
+    \begin{itemize}
+        \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
+            $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
+            $l$-equivalences and |.->|, and
+        \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
+    \end{itemize}
 \end{definition}
 
-\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
+\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
     If a language \con{L} is included in a language \abs{L}, and \abs{L}
@@
     from \con{L} to \abs{L}, applying TINI and transporting the resulting
-    equivalence back using bijectivity of $f$ over $l$-equivalences.
+    equivalence back using functoriality of |finv| over $l$-equivalences.
 \end{proof}
 
-Now we strengthen the condition to show TSNI:
+Isomorphism requires that |finv| is functorial over reduction relations
+as well, i.e. that we can extract a concrete reduction sequence from an abstract one.
 
@@
     A language \con{|(C, .->, erasef l)|} is
-    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
-    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
-    functorial over both $l$-equivalences (if |cc clequiv
-    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
-    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
+    isomorphic to a language \abs{|(iC, .->, erasef l)|} if there exist total functions
+    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and both |f| and |finv| are
+    functorial over both $l$-equivalences and |.->|.
+%(if |cc clequiv
+%   cc'| then
+%   |(ap f cc) alequiv (ap f cc')| and if |ac alequiv ac'|
+%   then |(ap finv ac) clequiv (ap finv ac')|) and
+%   |.->| (if
+%   |cc creduce cc'| then |(ap f cc) areduce (ap f cc')| and
+%   if |ac areduce ac'| then |(ap finv ac) creduce (ap finv ac')|)
 \end{definition}
@@
     \tar{L} to \ifc{L}, applying TSNI, and then transporting the
-    resulting configuration and multi-step derivation back.
+    resulting configuration, $l$-equivalence and multi-step derivation back.
 \end{proof}

### 2014-02-27 paper/concrete.tex
checkpoint

--- 2014-02-27 paper/concrete.tex
@@
 
-This isn't trivial, as it is not sound to add arbitrary additional
-conditions on evaluation rules.  To see this, consider a contrived
-concrete system where we add a premise to a reduction rule that
-stops a task based on secret information.  Such a system will
-not satisfy non-interference, as it allows other tasks on the
-same level to observe the termination of that task and thus the
-secret information which was used to decide if the task terminates
-or not.
-\Red{This last part is written poorly.  Let's do it better, or remove it.}
+Intuitively, there are two scenarios in which non-interference
+can be violated when restricting the transition relation:
+\begin{itemize}
+  \item Adding an additional premise to one of the rules that inspects
+  information which is above the security label of the task currently
+  executing.  This would allow another task to observe the termination
+  of the other if both are at the same security level, and thus observe
+  the secret information that was used in the additional
+  premise of the rule.
+  \item Adding additional restrictions to transition rules can
+  also cause the whole configuration to get stuck, which can leak
+  information through the termination channel.
+\end{itemize}
+
+%This isn't trivial, as it is not sound to add arbitrary additional
+%conditions on evaluation rules.  To see this, consider a contrived
+%concrete system where we add a premise to a reduction rule that
+%stops a task based on secret information.  Such a system will
+%not satisfy non-interference, as it allows other tasks on the
+%same level to observe the termination of that task and thus the
+%secret information which was used to decide if the task terminates
+%or not.
 
@@
 
-\Red{Say what do we do here.}
+To formalize the conditions under which we can show the concrete
+semantics preserve non-interference, we require some notation:
+
+\Red{isomorphism definition here}
+
+Now, we propose the following two-step process to ensure that
+TSNI is preserved:
+\begin{enumerate}
+  \item First, any of the reduction rules of the abstract
+  semantics presented in Section~\ref{sec:retrofit} can
+  be restricted by adding a predicate $P$ to the premise of
+  any rule other than \textsc{I-noStep}.  The predicate $P$
+  can depend only on the \textit{erased} configuration
+  |erase il ic|, where |il| is the label of the first task
+  in the task list.
+\end{enumerate}
+
+We now have a concrete semantics, which both uses a different
+representation for some of the constructs in language (a single
+heap rather than a heap per task in our running example), as well
+as restricting some of the operational rules to disallow
+undesirable transitions.  To show that the concrete semantics
+still satisfy TSNI, we use two techniques.  First, we give a
+condition on what kind of restrictions can be allowed on the
+operational rules.  Secondly, we define the notation of an
+isomorphism between IFC languages and show that it preserves
+non-interference.
 
@@
 
-%{
-%format tyerase c = "\varepsilon("c")"
-%format tyerasef = "\varepsilon"
-%format ^ = " "
-%format c = "c"
-%format c'
-%format cc = "\con{"c"}"
-%format cc'
-%format ac = "\abs{"c"}"
-%format ac'
-%format finv = f"^{-1}"
-%format V = "V"
-%format cV = "\con{"V"}"
-%format aV = "\abs{"V"}"
-%format ~= = "\approx_l"
-%format clequiv = "\con{"~="}"
-%format alequiv = "\abs{"~="}"
-%format creduce = "\con{".->"}"
-%format areduce = "\abs{".->"}"
-%format creducestar = "\con{".=>"}"
-%format areducestar = "\abs{".=>"}"
-%format (ap (f) (x)) = f"("x")"
-%format .. = "\circ"
-%format idf (t) = "id_{"t"}"
-
-\begin{definition}[Information-flow control language]
-    An information-flow control language L is a tuple |(C, .->,
-    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
-    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
-    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  For sequential languages, the
-    language is augmented with a set of terminal configuration states $V
-    \subseteq |C|$ for which there are no possible further transitions.
-\end{definition}
-
-\begin{definition}[$l$-equivalence]
-    In a language |(C, .->, erasef l)|, two machine configurations
-    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
-    if |erase l c = erase l c'|.
-\end{definition}
-
-\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
-\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}
-
 Before we show isomorphism preserves termination sensitive
@@
 \begin{definition}[Inclusion of information-flow control languages]
-    A language \con{|(C, V, .->, erasef l)|} is included in another
-    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
-    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
-    |(ap f cc) alequiv (ap f cc')|),
-    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
-    functorial over |.=>| (if
-    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
+    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
+    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
+    l|})$ if there exists a total function $f : |tC -> iC|$ such that
+    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
+    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
+    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
+    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
+    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
 \end{definition}
@@
 \begin{theorem}[Isomorphism preserves termination insensitive non-interference]
-    If a language \con{L} is included in a language \abs{L}, and \abs{L}
-    satisfies TINI, then \con{L} satisfies TINI.
+    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
+    \tar{L} satisfies TINI.
 \end{theorem}
@@
     Shown by transporting configurations and reduction derivations
-    from \con{L} to \abs{L}, applying TINI and transporting the resulting
+    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
     equivalence back using bijectivity of $f$ over $l$-equivalences.
@@
 \begin{definition}[Isomorphism of information-flow control languages]
-    A language \con{|(C, .->, erasef l)|} is
-    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
-    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
-    functorial over both $l$-equivalences (if |cc clequiv
-    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
+    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
+    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
+    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
+    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
+    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
+    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
     $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
@@
 \end{proof}
-%}
 

### 2014-02-27 paper/concrete.tex
mv local defs to global
moved defs

@@
 
-\Red{Move these definitions earlier}
-
-%{
-%format tyerase c = "\varepsilon("c")"
-%format tyerasef = "\varepsilon"
-%format ^ = " "
-%format c = "c"
-%format c'
-%format cc = "\con{"c"}"
-%format cc'
-%format ac = "\abs{"c"}"
-%format ac'
-%format finv = f"^{-1}"
-%format V = "V"
-%format cV = "\con{"V"}"
-%format aV = "\abs{"V"}"
-%format ~= = "\approx_l"
-%format clequiv = "\con{"~="}"
-%format alequiv = "\abs{"~="}"
-%format creduce = "\con{".->"}"
-%format areduce = "\abs{".->"}"
-%format creducestar = "\con{".=>"}"
-%format areducestar = "\abs{".=>"}"
-%format (ap (f) (x)) = f"("x")"
-%format .. = "\circ"
-%format idf (t) = "id_{"t"}"
-
-\begin{definition}[Information-flow control language]
-    An information-flow control language L is a tuple |(C, .->,
-    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
-    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
-    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  For sequential languages, the
-    language is augmented with a set of terminal configuration states $V
-    \subseteq |C|$ for which there are no possible further transitions.
-\end{definition}
-
-\begin{definition}[$l$-equivalence]
-    In a language |(C, .->, erasef l)|, two machine configurations
-    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
-    if |erase l c = erase l c'|.
-\end{definition}
-
 \newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}

### 2014-02-27 paper/retrofit.tex
Lss
macros
moved defs

@@
 
-\caption{Simple ML-like language}
+\caption{Simple ML-like language |targetLang ML|}
 \label{fig:ml}
@@
 \begin{figure}
+%{
+%format .->  = "\overset{\alpha}{\hookrightarrow}"
+%format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
 \begin{tabular}{ll}
@@
 \begin{mathpar}
-\and
 \inferrule[I-fork]
@@
 \end{mathpar}
-\caption{The embedding}
+\caption{The embedding |specLang alpha (targetLang nop)|, where
+$|targetLang nop| = (|tS|\times|tE|\times|te|\times|tv|, |->|)$}
 \label{fig:embedding}
+%}
 \end{figure}
@@
 \begin{definition}[Information-flow control language]
-    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
-    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
-    $|C|^*$ is the type of erased machine configurations, |.->| is a
-    reduction relation between machine configurations and $|erasef l|$
-    is an erasure function from machine configurations to erased machine
-    configurations.  For sequential languages, we may also speak of
-    values, e.g. a configurations $V \subseteq |C|$ for which there are
-    no possible further transitions.
+    An information-flow control language L is a tuple |(C, .->,
+    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
+    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
+    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
+    configurations |tyerase C|.  For sequential languages, the
+    language is augmented with a set of terminal configuration states $V
+    \subseteq |C|$ for which there are no possible further transitions.
 \end{definition}
@@
 \begin{definition}[$l$-equivalence]
-    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
-    if $|erase l c| = |erase l c'|$.
+    In a language |(C, .->, erasef l)|, two machine configurations
+    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
+    if |erase l c = erase l c'|.
 \end{definition}

### 2014-02-27 paper/retrofit.tex
tsni for rr

@@
 \caption{The embedding |specLang alpha (targetLang nop)|, where
-$|targetLang nop| = (|tS|\times|tE|\times|te|\times|tv|, |->|)$}
+|targetLang nop = (tS, tE, te, tv, ->)|}
 \label{fig:embedding}
@@
 
-\clearpage % TODO: remove again, but keep for now to not have the text be split across 4 pages.
 \subsection{Formal Guarantees}
@@
 \end{definition}
+
+%{
+%format .->  = "\overset{\alpha}{\hookrightarrow}"
+Using this definition, our specification language |specLang alpha
+(targetLang nop) = ((iS,its), .->, erasef il)|, where |its| is a task
+list containing terms from the embeddeding.
+%}
 
@@
 
-\begin{theorem}[TSNI]
+\begin{theorem}[Concurrent specification language is TSNI]
+For any target language |targetLang nop|,
+|specLang roundrobinf (targetLang nop)| satisfies TSNI.
 \end{theorem}
 
+\begin{definition}[Termination Insensitive Non-Interference (TINI)]
+  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
+  insensitive non-interfering if for any label |l|, and configurations
+  |c1, c2, V1, V2 member C|, if
+   $|c1| \approx_{|l|} |c2|$,
+   $|c1| |.->|^* |V1|$, and
+   $|c2| |.->|^* |V2|$, then
+   $|V1| \approx_{|l|} |V2|$.
+\end{definition}
+
+\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
+  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
+  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
+   $|ic1| \approx_{|il|} |ic2|$,
+   $|ic1| |.->|^* |ic1'|$, and
+   $|ic2| |.->|^* |ic2'|$, then
+   $|ic1'| \approx_{|il|} |ic2'|$.
+\end{theorem}
+
+\subsection{Generalizing further}
+
+\begin{itemize}
+\item Label transition systems.
+\item Non-deterministic reduction.
+\item Arbitrary scheduling policies $\alpha$
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\cut{
 \begin{lemma}
@@
 \end{proof}
-
 \begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
@@
 \end{proof}
-
-\begin{definition}[Termination Insensitive Non-Interference (TINI)]
-  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
-  insensitive non-interfering if for any label |l|, and configurations
-  |c1, c2, V1, V2 member C|, if
-   $|c1| \approx_{|l|} |c2|$,
-   $|c1| |.->|^* |V1|$, and
-   $|c2| |.->|^* |V2|$, then
-   $|V1| \approx_{|l|} |V2|$.
-\end{definition}
-
-\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
-  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
-  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
-   $|ic1| \approx_{|il|} |ic2|$,
-   $|ic1| |.->|^* |ic1'|$, and
-   $|ic2| |.->|^* |ic2'|$, then
-   $|ic1'| \approx_{|il|} |ic2'|$.
-\end{theorem}
-
-\subsection{Generalizing further}
-
-\begin{itemize}
-\item Label transition systems.
-\item Non-deterministic reduction.
-\item Arbitrary scheduling policies $\alpha$
-\end{itemize}
+}

### 2014-02-27 paper/retrofit.tex
checkin wip

@@
 \begin{definition}[Information-flow control language]
-    An information-flow control language L is a tuple |(C, .->,
+    An information-flow control language |L| is a tuple |(C, .->,
     erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
-    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
+    reduction relation between machine configurations and |erasef l : C -> tyerase C|
     is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-Using this definition, our specification language |specLang alpha
-(targetLang nop) = ((iS,its), .->, erasef il)|, where |its| is a task
-list containing terms from the embeddeding.
+Using this definition, we can no expand the definition for the
+specification family of languages.
+%
+Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
+erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
+= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
+tasks whose expressions have been reduced to values.\footnote{
+Here we abuse notation by using metavariables to describe types that
+we previously, e.g., |it| for the type of task.
+}
 %}
@@
 \begin{definition}[Termination Sensitive Non-Interference (TSNI)]
-  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
+  A language |(C, .->, erasef l)| is termination
   sensitive non-interfering if for any label |l|, and configurations
@@
 \begin{theorem}[Concurrent specification language is TSNI]
-For any target language |targetLang nop|,
-|specLang roundrobinf (targetLang nop)| satisfies TSNI.
+For any target language |targetLang nop|, |specLang roundrobinf
+(targetLang nop)| satisfies TSNI.
 \end{theorem}
@@
 \begin{definition}[Termination Insensitive Non-Interference (TINI)]
-  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
+  A language |(C, V, .->, erasef l)| is termination
   insensitive non-interfering if for any label |l|, and configurations
-  |c1, c2, V1, V2 member C|, if
+  |c1, c2 member C| and |c1', c2' member V| if
    $|c1| \approx_{|l|} |c2|$,
-   $|c1| |.->|^* |V1|$, and
-   $|c2| |.->|^* |V2|$, then
-   $|V1| \approx_{|l|} |V2|$.
+   $|c1| |.->|^* |c1'|$, and
+   $|c2| |.->|^* |c2'|$, then
+   $|c1'| \approx_{|l|} |c2'|$.
 \end{definition}
 
-\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
-  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
-  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
-   $|ic1| \approx_{|il|} |ic2|$,
-   $|ic1| |.->|^* |ic1'|$, and
-   $|ic2| |.->|^* |ic2'|$, then
-   $|ic1'| \approx_{|il|} |ic2'|$.
+\begin{theorem}[Sequential specification language is TINI]
+For any target language |targetLang nop|, |specLang seqf (targetLang
+nop)| satisfies TINI.
 \end{theorem}

### 2014-02-27 paper/concrete.tex
checkpoint.

--- 2014-02-27 paper/concrete.tex
@@
 TSNI is preserved:
+\Red{We should find a better name for this.}
+\begin{definition}[Non-Interference preserving, restricted isomorphism (NPRI)]
+  We call an IFC language
+  |concreteLang alpha targetLang| (which can be thought of as
+  the concrete language) a \textit{non-intereference preserving,
+  restricted isomorphism} with regard to the IFC language
+  |specLang alpha targetLang|
+  (which can be thought of as the abstract language) if the following
+  two conditions hold:
   \begin{enumerate}
-  \item First, any of the reduction rules of the abstract
-  semantics presented in Section~\ref{sec:retrofit} can
+    \item Any of the reduction rules of the abstract
+    semantics |specLang alpha targetLang|
+    presented in Section~\ref{sec:retrofit} can
     be restricted by adding a predicate $P$ to the premise of
@@
     in the task list.
+    \item The concrete language
+    |concreteLang alpha targetLang|
+    must be isomorphic to the abstract semantics |specLang alpha targetLang|
+    with the additional predicates $P$ on the rules.
   \end{enumerate}
+\end{definition}
+
+\begin{theorem}[NPRI implies TSNI]
+  If the language |concreteLang alpha targetLang| is a NPRI, then
+  |concreteLang alpha targetLang| satisfies TSNI.
+\end{theorem}
 

### 2014-02-27 paper/retrofit.tex
checkpoint.

--- 2014-02-27 paper/retrofit.tex
@@
 
-\caption{Simple ML-like language |targetLang ML|}
+\caption{Simple ML-like language |targetLangML|}
 \label{fig:ml}
@@
 \begin{definition}[Information-flow control language]
-    An information-flow control language L is a tuple |(C, .->,
-    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
-    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
-    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  For sequential languages, the
-    language is augmented with a set of terminal configuration states $V
-    \subseteq |C|$ for which there are no possible further transitions.
+    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
+    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
+    $|C|^*$ is the type of erased machine configurations, |.->| is a
+    reduction relation between machine configurations and $|erasef l|$
+    is an erasure function from machine configurations to erased machine
+    configurations.  For sequential languages, we may also speak of
+    values, e.g. a configurations $V \subseteq |C|$ for which there are
+    no possible further transitions.
 \end{definition}
@@
 \begin{definition}[$l$-equivalence]
-    In a language |(C, .->, erasef l)|, two machine configurations
-    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
-    if |erase l c = erase l c'|.
+    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
+    if $|erase l c| = |erase l c'|$.
 \end{definition}

### 2014-02-27 paper/retrofit.tex
english

--- 2014-02-27 paper/retrofit.tex
@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-Using this definition, we can no expand the definition for the
+Using this definition, we can now expand the definition for the
 specification family of languages.
@@
 tasks whose expressions have been reduced to values.\footnote{
-Here we abuse notation by using metavariables to describe types that
-we previously, e.g., |it| for the type of task.
+Here, we abuse notation by using metavariables to describe types of
+the corresponding non-terminals, e.g., |it| for the type of task.
 }

### 2014-02-27 paper/related.tex
Pile of notes about monadic approaches to IFC.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{Related work}
\label{sec:related}

\Red{
Monads and IFC:

Basically, monads and IFC go together like toads and holes, or pigs and blankets, etc.  But the role the monad plays varies widely.  First, you have static systems (Abadi, Tse-Zdancewic), which utilize a lattice of monads: if a value is in a monad with a label that's too high, you're not allowed to unpeel it and look at the value inside.  Next, you have dynamic systems.  It seems pretty clear that making the IFC TCB be in a monad is a good idea, and the cluster of papers around LIO are all about that. Some of these papers talk about monad transformers: Devriese/Piessens focuses on how you might implement something like LIO by applying a monad transformer to some base monad to run the appropriate restrictions; Harrison/Hook do some more close to what we're doing, where they actually try to say something like "transformers do not interfere." But I can't tell if they're actually doing what we're doing, and their work has a number of unrelated technical restrictions.

In more detail:

Information Flow Enforcement in Monadic Libraries (Devriese/Piessens): Talks about how to use a monad transformer to take a non-IFC base monad and turn it into a IFC monad, namely the lifting operation should enforce extra constraints.  We take closely related ideas, and apply it to settings where there are not any monads.  Devriese/Piessens doesn't note the idea that untrusted monad transformers can be applied to add extra effects.

Achieving information flow security through monadic control of effects (Harrison/Hook): separation kernel is the basic idea behind our constructed (everything is partioned).  Notion of atomic noninterference between layers of effects, ``sufficient condition for atomic noninterference to be inherited through monad transformer application''.  But atomic noninterference is not proper noninterference as we've defined here! No proof of separation of kernels, instead prove weaker property no write down.

A Core Calculus of Dependency (Abadi et al): define a calculus, which calculi you want to prove IFC secure can be translated into.  It's a static system.  Why do they use monads?  Something about that
}

IFC for any language:

Gotta talk about secure multi-execution

### 2014-02-27 paper/concrete.tex

--- 2014-02-27 paper/concrete.tex
@@
 \label{sec:concrete}
+
+\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
+\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}
 
@@
 |iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|
+as is done in |specLangML alpha|
 where every task has its
@@
 \textsc{I-noStep} rule.
+We call this family of languages |concreteLangMl alpha|, which
+is still parametrized by the scheduling policy |alpha|.
 
@@
 
+Next, we will make these two intuitions precise and give a general
+definition for how non-interference can be preserved.  Then, we
+show that the definition in Figure~\Red{XXX} satisfy these
+conditions.
+
 %This isn't trivial, as it is not sound to add arbitrary additional
@@
 
-\Red{isomorphism definition here}
+\begin{definition}[Weak isomorphism of information-flow control languages]
+  A language \con{|(C, .->, erasef l)|} is \textit{weakly isomorphic} to a
+  language \abs{|(iC, .->, erasef l)|} if there exist total functions
+  |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
+  |finv .. f = idf iC|.  Furthermore, the following coherence conditions
+  must hold:
+  \begin{itemize}
+    \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
+    $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
+    $l$-equivalences and |.->|, and
+    \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
+  \end{itemize}
+  We furthermore call the two languages \textit{isomorphic} if both
+  |f| and |finv| are functorial over |.->|.
+\end{definition}
 
-Now, we propose the following two-step process to ensure that
+Now, we can propose the following two-step process to ensure that
 TSNI is preserved:
+\Red{We should find a better name for this, or not use a name, or something.}
+\begin{definition}[Non-Interference preserving, restricted isomorphism (NPRI)]
+  We call an IFC language
+  |concreteLang alpha targetLang| (which can be thought of as
+  the concrete language) a \textit{non-intereference preserving,
+  restricted isomorphism} with regard to the IFC language
+  |specLang alpha targetLang|
+  (which can be thought of as the abstract language) if the following
+  two conditions hold:
   \begin{enumerate}
-  \item First, any of the reduction rules of the abstract
-  semantics presented in Section~\ref{sec:retrofit} can
+    \item Any of the reduction rules of the abstract
+    semantics |specLang alpha targetLang|
+    presented in Section~\ref{sec:retrofit} can
     be restricted by adding a predicate $P$ to the premise of
@@
     in the task list.
+    \item The concrete language
+    |concreteLang alpha targetLang|
+    must be isomorphic to the abstract semantics |specLang alpha targetLang|
+    with the additional predicates $P$ on the rules.
   \end{enumerate}
+\end{definition}
 
-We now have a concrete semantics, which both uses a different
-representation for some of the constructs in language (a single
-heap rather than a heap per task in our running example), as well
-as restricting some of the operational rules to disallow
-undesirable transitions.  To show that the concrete semantics
-still satisfy TSNI, we use two techniques.  First, we give a
-condition on what kind of restrictions can be allowed on the
-operational rules.  Secondly, we define the notation of an
-isomorphism between IFC languages and show that it preserves
-non-interference.
+\begin{theorem}[NPRI implies TSNI]
+  If a language |concreteLang alpha targetLang| is a NPRI, then
+  |concreteLang alpha targetLang| satisfies TSNI.
+\end{theorem}
+
+With this machinery in place, we can now state and prove that our
+single-heap ML-like IFC language is NPRI, and thus non-interfering.
+
+\begin{theorem}
+  The language |concreteLangMl alpha| is a NPRI.
+\end{theorem}
+As a trivial corollary, it follows that |concreteLangMl roundrobinf| is
+TSNI, and |concreteLangMl seqf| is TINI.
+
+\begin{proof}
+  It is easy to see that condition 1.\ of NPRI is satisfied, since
+  we only add a side condition to the rules \textsc{I-fork} and
+  \textsc{I-send}, and the condition only inspects the expression
+  of the current task, which is by the definition of |erasef il| not
+  erased.
+
+  This leaves us to give an isomorphism between |concreteLangMl alpha|
+  and |concreteLang alpha targetLangMl|, which we do as follows.
+  \Red{Actually give an isomorphism.}
+\end{proof}
 
@@
 
-\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
-\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}
-
 Before we show isomorphism preserves termination sensitive
@@
 and preserve termination \emph{insensitive} interference:
-
-\begin{definition}[Weak isomorphism of information-flow control languages]
-    A language \con{|(C, .->, erasef l)|} is weakly isomorphic to a
-    language \abs{|(iC, .->, erasef l)|} if there exist total functions
-    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
-    |finv .. f = idf iC|.  Furthermore, the following coherence conditions
-    must hold:
-    \begin{itemize}
-        \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
-            $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
-            $l$-equivalences and |.->|, and
-        \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
-    \end{itemize}
-\end{definition}
 

### 2014-02-27 paper/monad.tex
Start monads
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
-\section{Monadic interpretation}
+\section{The monadic interpretation}
 \label{sec:monad}
+
+In the previous sections, we have been primarily concerned with the
+combination of operational semantics in order to automatically augment a
+language with information flow control.  In this section, we present
+a more abstract view of what is going on, phrased in the language of monads
+and monad transformers.  The key idea is that the computational effects
+of the target language should be thought of as a \emph{monad transformer}
+on top of the information-flow control base monad.  Readers who are not
+familiar with monads should feel free to skip this section.
+
+Monads were originally proposed as a method for organizing computational
+effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
+of interest was how to modularly build more complex computational
+effects out of simpler ones.  One particular approach, the
+\emph{incremental
+approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
+monad transformers, which add an extra computation feature to a
+pre-existing monad.  In the past, this approach has been criticized for
+a number of failings, including the fact that the order in meaning of a
+monad can depend on the order in which the monad transformers are
+applied. \Red{cite} The canonical example of this phenomenon is the
+composition of the state monad and the error monad: depending on the
+ordering of the two monad transformers, state is preserved or thrown away
+upon an error.
+
+These problems can be viewed as defects in a setting where we are
+simply interested in combining effects.  However, in the setting of information
+flow control, we are primarily interested in augmenting the
+computational effects of a target language with information flow control
+\emph{without} compromising noninterference.  When the base monad is
+kept abstract (in the style of a restricted IO monad~\cite{Terei:2012:SH:2364506.2364524}),
+there is an easy argument why any monad transformer must also preserve noninterference:
+the monad transformer could have been implemented simply as a \emph{pure} interpreter, and
+the pure interpreter is just another program like any other that may run on top of
+a restricted IO monad.
+
+Now, one shouldn't simply force an interpreter to be reimplemented on
+top of a language supporting information flow control.  As suggested by
+Filinski et al~\cite{Filinski:2010:MA:1707801.1706354}, we should use
+pure implementations of computational effects to understand
+computational effects when built into information flow languages: they
+give a good hint what the operational rules should be.  This intuition
+backed the development of Section~\ref{sec:retrofit}.  Furthermore,
+developing the relationship between concrete semantics and abstract
+semantics in \ref{sec:concrete} relates to the question of monad
+isomorphisms in the presence of data abstraction.  We leave
+investigating this connection in more detail to future work.

### 2014-02-27 paper/concrete.tex
checkpoint
# Please enter a commit message to explain why this merge is necessary,
# especially if it merges an updated upstream into a topic branch.
#
# Lines starting with '#' will be ignored, and an empty message aborts
# the commit.

@@
 
-The operational semantics we have derived in the previous section
-satisfy termination sensitive non-interference by design.  However,
-these abstract semantics essentially require that different tasks
-execute completely isolated.  For instance, for the mini-ML language,
-this means that every task has it's own heap.  For practical
-implementations this is often not desirable.  Instead, we would like to
+The operational semantics we have defined in the previous section
+satisfy termination sensitive non-interference by design.
+We achieve this general statement that works for a large class of
+languages by having different task execute completely isolated from
+each other, such that every task has it's own state.
+In some cases, this strong separation is desirable, or even necessary.
+Languages like C provide direct access to the addresses without
+mechanisms in the language to achieve a separation of the heap.
+However, for other languages this isolation of tasks can be
+undesirable, e.g., for performance reasons.
+For instance, for the mini-ML language, our presentation so far
+requires a separate heap per task, which is not very practical.
+Instead, we would like to
 more tightly couple the integration of the target and IFC
@@
 In this section, we will detail an approach that allows one to implement
-a concrete system differently from our proposal in the previous
-section, and give conditions for when such a system preserves termination
-sensitive non-interference.
-We explain the idea for the single heap mini-ML language, and then
-generalize to arbitrary systems.
+a concrete system guided conceptually by the ideas in the previous
+section but making different choice for ease of implementation or
+performance, and give conditions for when such a system preserves
+non-interference.
+We first explain the idea for the single heap mini-ML language, and then
+generalize to arbitrary languages.
 

### 2014-02-27 paper/concrete.tex
move proofs.

@@
 Instead of using a configuration of the form
-|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|
+\[|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|\]
 as is done in |specLangML alpha|
@@
 |oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
-Furthermore, we keep up a fictional separation between the portions
-of the global heap that tasks can use by forbidding references to
-cross task boundaries. Most
-of the operational rules can easily be adapted to work with these
+To keep up a fictional separation between the portions
+of the global heap that tasks can use, we forbid references to
+cross task boundaries.  To achieve such a system, we can
+adapt most of the operational rules easily to work with these
 new configurations.  In the abstract system, the \textsc{I-fork}
-rule created a new heap for the new task to execute in.  Since we
+rule created a fresh heap for the new task to execute in.  Since we
 want to forbid references to cross task boundaries, we do not modify
@@
 
-As we have outlined the IFC-Mini-ML language with a single heap, we
+In |concreteLangMl alpha| we
 effectively restrict the abstract semantics in some cases (namely
@@
 new, \textit{concrete semantics} for our system still satisfy
-termination-sensitive non-interference?
+non-interference?
+
+We will use two techniques to ensure non-interference.  First,
+we require some form of isomorphism to the abstract language
+|specLangML alpha| that ensures that the concrete system behaves
+in a similar way.  Secondly, we pose conditions on what kind
+of restrictions the concrete language is allowed to make
+on the abstract language.
 
@@
   also cause the whole configuration to get stuck, which can leak
-  information through the termination channel.
+  information through the termination channel (which is only
+  of interest for TSNI, but not TINI, of course).
 \end{itemize}
@@
 definition for how non-interference can be preserved.  Then, we
-show that the definition in Figure~\Red{XXX} satisfy these
+show that the language |concreteLangMl alpha| satisfies these
 conditions.
+
+\Red{Should we give an example why removing transitions in general
+  is not OK?  Edward has already typeset one that we could
+  use.}
 
@@
 Now, we can propose the following two-step process to ensure that
-TSNI is preserved:
+non-interference is preserved:
 \Red{We should find a better name for this, or not use a name, or something.}
-\begin{definition}[Non-Interference preserving, restricted isomorphism (NPRI)]
+\begin{definition}[Non-interference preserving, restricted isomorphism (NPRI)]
   We call an IFC language
-  |concreteLang alpha targetLang| (which can be thought of as
-  the concrete language) a \textit{non-intereference preserving,
+  |concreteLang alpha targetLang| (the concrete language for a given
+  target language |targetLang| and scheduling policy |alpha|)
+  a \textit{non-intereference preserving,
   restricted isomorphism} with regard to the IFC language
   |specLang alpha targetLang|
-  (which can be thought of as the abstract language) if the following
+  (the abstract language) if the following
   two conditions hold:
@@
     |erase il ic|, where |il| is the label of the first task
-    in the task list.
+    in the task list and |ic| the full configuration.
     \item The concrete language
@@
 
-\begin{theorem}[NPRI implies TSNI]
-  If a language |concreteLang alpha targetLang| is a NPRI, then
-  |concreteLang alpha targetLang| satisfies TSNI.
+\begin{theorem}[NPRI implies non-interference]
+  \label{thm:npri}
+  If a language |concreteLang alpha targetLang| is a NPRI, and |alpha|
+  is a scheduling policy that makes |specLang alpha targetLang| satisfy
+  TINI or TSNI, then also
+  |concreteLang alpha targetLang| satisfies TINI, or TSNI, respectively.
 \end{theorem}
 
-With this machinery in place, we can now state and prove that our
-single-heap ML-like IFC language is NPRI, and thus non-interfering.
+We give the proof of this in Section~\ref{sec:proofs}.
+Going back to our single-heap ML-like IFC language, we can
+show that it is in fact NPRI, and thus non-interfering.
 
@@
 \begin{proof}
-  It is easy to see that condition 1.\ of NPRI is satisfied, since
+  It is easy to see that condition (1) of NPRI is satisfied, since
   we only add a side condition to the rules \textsc{I-fork} and
@@
 
-\Red{At some point in this section we should say a little about
-  why the abstract setting needs complete isolation (because it
-  works for \textit{any} language), and that this is sometimes
-  what you want.}
+\subsection{Proof of Theorem~\ref{thm:npri}}
+\label{sec:proofs}
+
+Before we give the actual proof, we state and proof some properties
+of isomorphisms.
+
+\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
+  If a language \con{L} is included in a language \abs{L}, and \abs{L}
+  satisfies TINI, then \con{L} satisfies TINI.
+\end{theorem}
+
+\begin{proof}
+  Shown by transporting configurations and reduction derivations
+  from \con{L} to \abs{L}, applying TINI and transporting the resulting
+  equivalence back using functoriality of |finv| over $l$-equivalences.
+\end{proof}
+
+\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
+  \tar{L} satisfies TSNI.
+\end{theorem}
+
+\begin{proof}
+  Shown by transporting configurations and reduction derivations from
+  \tar{L} to \ifc{L}, applying TSNI, and then transporting the
+  resulting configuration, $l$-equivalence and multi-step derivation back.
+\end{proof}
+
+\Red{Adapt proofs.}
+
+\begin{lemma}
+  \label{lemma:tsni}
+  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
+  \begin{equation} \label{eq:tsni-lemma-lhs}
+  |ic1| \approx_{|il|} |ic2|
+  \qquad \text{and} \qquad
+  |ic1| |.->| |ic1'|
+  \end{equation}
+  then there exists a configuration |ic2'| such that
+  \begin{equation} \label{eq:tsni-lemma-rhs}
+  |ic1'| \approx_{|il|} |ic2'|
+  \qquad \text{and} \qquad
+  |ic2| |.->|^* |ic2'|
+  \ \text{.}
+  \end{equation}
+\end{lemma}
+
+\begin{proof}
+  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+  The base case for derivations
+  of length 0 is trivial, allowing
+  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
+  the theorem holds for derivation sequences of length up to $n$, and show that it also
+  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
+  \[
+  |ic1| |.->| |ic1''| |.->|^n |ic1'|
+  \]
+  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
+  |ic''| with
+  \begin{equation} \label{eq:tsni-proof-1}
+  |ic1''| \approx_{|il|} |ic2''|
+  \qquad \text{and} \qquad
+  |ic2| |.->|^* |ic2''|
+  \end{equation}
+  Applying the induction hypothesis to
+  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
+  \begin{equation} \label{eq:tsni-proof-2}
+  |ic1'| \approx_{|il|} |ic2'|
+  \qquad \text{and} \qquad
+  |ic2''| |.->|^* |ic2'|
+  \end{equation}
+  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
+  us~\eqref{eq:tsni-rhs}, which concludes the proof.
+\end{proof}
+\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
+  We proof the lemma by induction on the derivation
+  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
+  could have been used to make the reduction step.
+  First, we observe there must be at least one task in |ic1|, otherwise
+  it could not take a step.  Thus, |ic1| is of the form
+  |iconf iS1 (it1, its1)|.  Consider two cases:
+  \begin{itemize}
+    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
+    step for
+    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
+    To see that, note that the tasks |its1| in |ic1| are left in the
+    same order and unmodified. The task |it1| either
+    gets dropped (by \textsc{I-noStep}), or
+    transforms into a new task |it1'| as well as potentially spawning a new
+    task |it1''|.  Since both |it1'| and |it1''| have a label that is
+    at least as high as the label of |it1|, they will get filtered
+    by |erasef il| in |ic1'|.
+    Lets consider the possible changes to |iS1|: If |it1| sends a
+    message, then the corresponding queue in |iS1'| will contain one
+    more message.  However, that message has the label of |it1| (or a higher
+    label), and will thus get erased by |erasef il|.
+    Finally, receiving or not receiving a message (by
+    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
+    task |it1|, which are erased from |iS1|.
+    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.
+
+    \alphacondition{We need all scheduling policies to not change the order
+      of any tasks (except for the first one).  Newly spawned task can appear
+      anywhere in the list.}
+    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
+    task |it2| in |ic2|,
+    such that |it1=it2| (otherwise |ic1| and
+    |ic2| could not be |il| equivalent).
+    However, |it2| might not be at the beginning of the task list yet, but
+    all tasks occurring before it must get erased by |erasef il|.
+    In |ic2|, we can first take some number of steps until |it2| moves
+    to the front of the list (\Red{Say more precisely why
+      (basically because we require the scheduling policy to do that)}).
+
+    \alphacondition{The scheduling policy must eventually let any task in
+      the task list evaluate.  In particular, it cannot get stuck when the
+      first task gets stuck, or keep executing a small number of tasks
+      exclusively forever (e.g. just execute the first task all the time
+      if it gets into an infinite loop).}
+
+    Therefore, after |ic2| has potentially executed some number of steps
+    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
+    get erased and are thus equivalent.
+    The task |it2| can now take exactly the same step as |it1|;  we only
+    need to argue that the potential differences in |iS1| and |iS2| cannot
+    have an influence on the execution (and we know |iS1| and |iS2| are
+    |il| equivalent).
+    Again, only send and receive will change |iS|, so we consider all
+    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
+    a message is sent, then the message is added to the same queue.  This
+    queue is either completely erased, or it is |il| equivalent.  In both
+    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
+    When the tasks are receiving a message, then by the reduction rules
+    we know that they first filter the queue by the label of |it1|.  We
+    also know that the queues are equivalent when filtered by the less
+    restrictive label |il|, thus the messages received (or dropped) from the
+    queue are equivalent.
+  \end{itemize}
+\end{proof}
 
@@
 
-\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
-    If a language \con{L} is included in a language \abs{L}, and \abs{L}
-    satisfies TINI, then \con{L} satisfies TINI.
-\end{theorem}
-
-\begin{proof}
-    Shown by transporting configurations and reduction derivations
-    from \con{L} to \abs{L}, applying TINI and transporting the resulting
-    equivalence back using functoriality of |finv| over $l$-equivalences.
-\end{proof}
-
-Isomorphism requires that |finv| is functorial over reduction relations
-as well, i.e. that we can extract a concrete reduction sequence from an abstract one.
-
-\begin{definition}[Isomorphism of information-flow control languages]
-    A language \con{|(C, .->, erasef l)|} is
-    isomorphic to a language \abs{|(iC, .->, erasef l)|} if there exist total functions
-    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and both |f| and |finv| are
-    functorial over both $l$-equivalences and |.->|.
-%(if |cc clequiv
-%   cc'| then
-%   |(ap f cc) alequiv (ap f cc')| and if |ac alequiv ac'|
-%   then |(ap finv ac) clequiv (ap finv ac')|) and
-%   |.->| (if
-%   |cc creduce cc'| then |(ap f cc) areduce (ap f cc')| and
-%   if |ac areduce ac'| then |(ap finv ac) creduce (ap finv ac')|)
-\end{definition}
-
-\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
-    If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
-    \tar{L} satisfies TSNI.
-\end{theorem}
-
-\begin{proof}
-    Shown by transporting configurations and reduction derivations from
-    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
-    resulting configuration, $l$-equivalence and multi-step derivation back.
-\end{proof}
-
 \begin{figure}
@@
 \end{figure}
-
-This version

### 2014-02-27 paper/retrofit.tex
move proofs.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\cut{
-\begin{lemma}
-  \label{lemma:tsni}
-  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
-  \begin{equation} \label{eq:tsni-lemma-lhs}
-  |ic1| \approx_{|il|} |ic2|
-  \qquad \text{and} \qquad
-  |ic1| |.->| |ic1'|
-  \end{equation}
-  then there exists a configuration |ic2'| such that
-  \begin{equation} \label{eq:tsni-lemma-rhs}
-  |ic1'| \approx_{|il|} |ic2'|
-  \qquad \text{and} \qquad
-  |ic2| |.->|^* |ic2'|
-  \ \text{.}
-  \end{equation}
-\end{lemma}
-
-\begin{proof}
-  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
-  The base case for derivations
-  of length 0 is trivial, allowing
-  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
-  the theorem holds for derivation sequences of length up to $n$, and show that it also
-  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
-  \[
-  |ic1| |.->| |ic1''| |.->|^n |ic1'|
-  \]
-  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
-  |ic''| with
-  \begin{equation} \label{eq:tsni-proof-1}
-  |ic1''| \approx_{|il|} |ic2''|
-  \qquad \text{and} \qquad
-  |ic2| |.->|^* |ic2''|
-  \end{equation}
-  Applying the induction hypothesis to
-  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
-  \begin{equation} \label{eq:tsni-proof-2}
-  |ic1'| \approx_{|il|} |ic2'|
-  \qquad \text{and} \qquad
-  |ic2''| |.->|^* |ic2'|
-  \end{equation}
-  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
-  us~\eqref{eq:tsni-rhs}, which concludes the proof.
-\end{proof}
-\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
-  We proof the lemma by induction on the derivation
-  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
-  could have been used to make the reduction step.
-  First, we observe there must be at least one task in |ic1|, otherwise
-  it could not take a step.  Thus, |ic1| is of the form
-  |iconf iS1 (it1, its1)|.  Consider two cases:
-  \begin{itemize}
-    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
-    step for
-    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
-    To see that, note that the tasks |its1| in |ic1| are left in the
-    same order and unmodified. The task |it1| either
-    gets dropped (by \textsc{I-noStep}), or
-    transforms into a new task |it1'| as well as potentially spawning a new
-    task |it1''|.  Since both |it1'| and |it1''| have a label that is
-    at least as high as the label of |it1|, they will get filtered
-    by |erasef il| in |ic1'|.
-    Lets consider the possible changes to |iS1|: If |it1| sends a
-    message, then the corresponding queue in |iS1'| will contain one
-    more message.  However, that message has the label of |it1| (or a higher
-    label), and will thus get erased by |erasef il|.
-    Finally, receiving or not receiving a message (by
-    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
-    task |it1|, which are erased from |iS1|.
-    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.
-
-    \alphacondition{We need all scheduling policies to not change the order
-      of any tasks (except for the first one).  Newly spawned task can appear
-      anywhere in the list.}
-    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
-    task |it2| in |ic2|,
-    such that |it1=it2| (otherwise |ic1| and
-    |ic2| could not be |il| equivalent).
-    However, |it2| might not be at the beginning of the task list yet, but
-    all tasks occurring before it must get erased by |erasef il|.
-    In |ic2|, we can first take some number of steps until |it2| moves
-    to the front of the list (\Red{Say more precisely why
-      (basically because we require the scheduling policy to do that)}).
-
-    \alphacondition{The scheduling policy must eventually let any task in
-      the task list evaluate.  In particular, it cannot get stuck when the
-      first task gets stuck, or keep executing a small number of tasks
-      exclusively forever (e.g. just execute the first task all the time
-      if it gets into an infinite loop).}
-
-    Therefore, after |ic2| has potentially executed some number of steps
-    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
-    get erased and are thus equivalent.
-    The task |it2| can now take exactly the same step as |it1|;  we only
-    need to argue that the potential differences in |iS1| and |iS2| cannot
-    have an influence on the execution (and we know |iS1| and |iS2| are
-    |il| equivalent).
-    Again, only send and receive will change |iS|, so we consider all
-    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
-    a message is sent, then the message is added to the same queue.  This
-    queue is either completely erased, or it is |il| equivalent.  In both
-    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
-    When the tasks are receiving a message, then by the reduction rules
-    we know that they first filter the queue by the label of |it1|.  We
-    also know that the queues are equivalent when filtered by the less
-    restrictive label |il|, thus the messages received (or dropped) from the
-    queue are equivalent.
-  \end{itemize}
-\end{proof}
-}

### 2014-02-27 paper/concrete.tex
minor tweaks.

@@
 \newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}
-
-\Red{In this section I only talk about TSNI.  Once we finish the previous
-  section to both talk about TSNI and TINI, we should do the same here.}
 
@@
 
-We give the proof of this in Section~\ref{sec:proofs}.
-Going back to our single-heap ML-like IFC language, we can
+Before we give the proof of this theorem in Section~\ref{sec:proofs},
+let's consider our single-heap ML-like IFC language and
 show that it is in fact NPRI, and thus non-interfering.
@@
 
-\Red{Adapt proofs.}
+\Red{Adapt the following proofs.}
 

### 2014-02-27 paper/formal.tex
minor

--- 2014-02-27 paper/retrofit.tex
@@
-\section{Retrofitting languages with IFC}
-\label{sec:retrofit}
+\section{Security Guarantees}
+\label{sec:formal}
 
-While we would like to add information flow control to \emph{any}
-language, we will have to make some assumptions about the form of the
-target language.  We consider languages whose semantics can be expressed
-in the form of abstract machines |(tS, tE, te, tv, ->)|, where |tS| is the
-global machine state, |tE| is an evaluation context, |te| is an
-expression in the language, |tv| is the set of values, and |->| is the reduction relation on such
-configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
-\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
-target language have been colored red.
+In this section we present the formal security guarantees provided by
+our embedding.
+%
+Specifically, we show that a combined langauge, |specLang alpha
+(targetLang nop)|, satisfies a form of non-interference.
+%
+Intuitively, non-interference states that secret values cannot be
+leaked by programs written in the language.
 
-In Figure~\ref{fig:ml}, we give an example of a standard ML-like
-language with mutable references.  These semantics have been prepared
-for interoperability in the style of Matthews and Findler~\Red{XXX}; in
-particular, the evaluation rules have been expressed in terms of an
-evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
-this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
-when we perform the embedding, we will reinterpret the meaning
-of this evaluation context, lifting these semantics to an IFC setting.
-
-\begin{figure}
-\begin{code}
-tv   ::= \tx.te | true | false | ta
-tty   ::= bool | tty -> tty | ref tty
-te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
-tE   ::= tHole | tE te | tv tE | if tE then te else te
-       | ref tE | !tE | tE := te | tv := tE
-
-te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
-let tx = te1 in te2  @= (\tx.te2) te1
-\end{code}
-
-\Red{Suggestion: Only give the rules for references, because otherwise this is all standard.}
-
-\begin{mathpar}
-
-\and
-\inferrule[T-app]
-{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}
-
-\and
-\inferrule[T-ifTrue]
-{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}
-
-\and
-\inferrule[T-ifFalse]
-{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}
-
-\and
-\inferrule[T-ref]
-{| tS' = tS [ ta mapsto tv ] | } 
-{| conf tS (ref tv) -> conf tS' ta |}
-{| fresh (ta) |}
-
-\and
-\inferrule[T-deref]
-{| tv = tS(ta) |}
-{| conf tS (!ta) -> conf tS tv |}
-
-\and
-\inferrule[T-ass]
-{| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (ta := tv) -> conf tS' tv |}
-\end{mathpar}
-
-\caption{Simple ML-like language |targetLangML|}
-\label{fig:ml}
-\end{figure}
-
-Next, we describe the IFC language.  \Red{Description of the IFC language as
-a standard floating label system, or backwards reference to the
-background section.}  In Figure~\ref{fig:ifc}, we describe the syntax
-of the language, and provide rules for all operations which operate on a single
-thread.  \Red{One could imagine these rules giving the definition of a very
-boring information flow control language, by defining |niconf iS id il ie| appropriately
-and providing an appropriate erasure function.}
-
-We use the notation |filter il Q| to indicate a filter function which removes message whose labels do not
-flow to |il|. Specifically, if |Q| is the empty list |nil|, the
-function is simply the identity function, i.e.,
-|filter il nil = nil|; otherwise:
-\[
-|filter il ((il', id, ie) , Q )| = \left\{
-\begin{array}{l l}
-|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
-|filter il Q| & \quad \text{otherwise}
-\end{array} \right.
-\]
-
-%   \begin{figure}
-%   Typing judgment: $|tyrule tG tS te tty|$
-%   \begin{mathpar}
-%   \inferrule[T-ty-address]
-%   {}
-%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
-%   \end{mathpar}
-
-%   \caption{Selected typing rules for ML-like language}
-%   \label{fig:ml-typing}
-%   \end{figure}
-
-\begin{figure}
-\begin{code}
-lop  ::=  canFlowTo | lub | glb
-iv   ::=  id | il | true | false | unit
-ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
-       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
-iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
-       |  send iE ie ie | send iv iE ie | send iv iv iE
-       |  ix1, ix2 <= recv. ie ie
-io   ::=  (il, id ie)
-Q    ::=  nil | io , Q
-iS   ::=  emptyset | iS [ id mapsto Q ]
-\end{code}
-
-\begin{mathpar}
-
-\and
-\inferrule[I-getLabel]
-{ }
-{|
-niconf iS id il getLabel
-->
-niconf iS id il il
-|}
-
-\and
-\inferrule[I-setLabel]
-{ |il canFlowTo il'| }
-{|
-niconf iS id il (setLabel il')
-->
-niconf iS id il' unit
-|}
-%{|fresh (id')|}
-
-\and
-\inferrule[I-send]
-{
-|il canFlowTo il'|\\
-|iS(id') = Q|\\
-|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
-}
-{|
-niconf iS  id il (send id' il' ie)
-->
-niconf iS' id il unit
-|}
-
-\and
-\inferrule[I-recv]
-{
-| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
-| iS' = iS[id mapsto io1 , ... , iok]|\\
-}
-{|
-niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
-->
-niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
-|}
-
-\and
-\inferrule[I-noRecv]
-{
-| filter il (iS(id)) = nil|\\
-| iS' = iS[id mapsto nil]|
-}
-{|
-niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
-->
-niconf iS' id il ie2
-|}
-
-\inferrule[I-labelOp]
-{ |denot (il1 lop il2) = iv|}
-{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
-\end{mathpar}
-\caption{IFC language, single-thread operations}
-\label{fig:ifc}
-\end{figure}
-
-Finally, in Figure~\ref{fig:embedding},
-we provide all of the rules responsible for actually carrying out the embedding:
-
-\begin{itemize}
-    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-\Red{For now, we defer discussion on how these boundaries mediate between the type systems of the two languages.}
-    \item We reinterpret |CE| to be evaluation contexts on threadpools.  By assumption, only the first thread in the threadpool executes.
-    \item We define |->|, operation on a single thread, in terms of |.->|, operation on thread pools.
-The correspondence is simple: a thread executes a step, and then is rescheduled in the thread pool according to schedule policy $\alpha$.
-\Red{More on schedule policies later}
-    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
-\Red{As written, these rules will not preserve type-safety of the underyling language, but it is easy to adjust them to ensure they do so.}
-\end{itemize}
-
-The fork rule is of particular interest; it is defined in terms of a function $\kappa$.
-Conservatively, $\kappa$ may be simply thought of as the identity function, in which
-case the semantics of fork are such that the state of the target language is \emph{cloned}
-when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
-to remove entries from the state.  \Red{For more information about when this is not the
-fork semantics you want, see the concrete implementation section.}
-
-\begin{figure}
-%{
-%format .->  = "\overset{\alpha}{\hookrightarrow}"
-%format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
-\begin{tabular}{ll}
-\begin{minipage}{.22\textwidth}
-\begin{code}
-iv  ::= cdots | IT tv
-ie  ::= cdots | IT te
-iE  ::= cdots | IT tE
-\end{code}
-\end{minipage} &
-\begin{minipage}{.22\textwidth}
-\begin{code}
-tv  ::= cdots | TI iv
-te  ::= cdots | TI ie
-tE  ::= cdots | TI iE
-\end{code}
-\end{minipage}
-\end{tabular}
-
-\begin{code}
-ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
-conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
-niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
-CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
-\end{code}
-
-\begin{mathpar}
-\inferrule[I-fork]
-{ 
-|iS' = iS [ id' mapsto nil ]|\\
-|tS' = klone(tS)|\\
-|it1 = fullconf id il tS (iniE id')|\\
-|itnew = fullconf id' il tS' (TI ie)|\\
-|fresh (id')|
-}
-{|
-iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
-.->
-iS'; sched F (it1, ldots, itnew)
-|}
-
-\and
-\inferrule[I-done]
-{|
-|}
-{|
-iconf iS (fullconf id il tS iv, ldots)
-.->
-iS ; sched D (fullconf id il tS iv, ldots)
-|}
-
-\and
-\inferrule[I-noStep]
-{|
-iconf iS (it, ldots) .-/> 
-|}
-{|
-iconf iS (it, ldots)
-.->
-iS ; sched N (it, ldots)
-|}
-
-\and
-\inferrule[I-border]
-{ }
-{|
-niconf iS id il (IT (TI (ie)))
-->
-niconf iS id il ie
-|}
-
-\and
-\inferrule[T-border]
-{ } {| conf tS (TI (IT (te))) -> conf tS te|}
-\end{mathpar}
-\caption{The embedding |specLang alpha (targetLang nop)|, where
-|targetLang nop = (tS, tE, te, tv, ->)|}
-\label{fig:embedding}
-%}
-\end{figure}
+In this section, we show that LIO computations satisfy
+termination-sensitive non-interference. As in ~\cite{Li+:2010:arrows,Russo+:Haskell08,stefan:lio}, 
+we prove this property by using the
+\emph{term erasure} technique. The erasure function $\eraseName_L$
+rewrites data at security levels that the attacker cannot observe into
+the syntax node $\hole$.
 
@@
 \end{figure}
-
-\Red{When both languages have booleans, it is relatively simple to define
-a natural embedding which preserves booleans across boundaries.}
-\begin{mathpar}
-\inferrule[I-bool]
-{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-\and
-\inferrule[T-bool]
-{ |b member {true, false}| } {| intE (TI b) -> intE b |}
-\end{mathpar}
-
-\begin{figure}
-  Concurrent, round robin:
-\begin{code}
-  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
-  roundrobin D (it1, it2, ldots)     = it2, ldots
-  roundrobin N (it1, it2, ldots)     = it2, ldots
-  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
-\end{code}
-  Sequential:
-\begin{code}
-  seq step (it1, it2, ldots)     = it1, it2, ldots
-  seq N (it1, it2, ldots)        = it1, it2, ldots
-  seq D (it)                     = it
-  seq D (it1, it2, ldots)        = it2, ldots
-  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
-\end{code}
-\caption{Scheduling policies}
-\end{figure}
-
-\subsection{Formal Guarantees}
 
@@
 \end{theorem}
-
-\subsection{Generalizing further}
-
-\begin{itemize}
-\item Label transition systems.
-\item Non-deterministic reduction.
-\item Arbitrary scheduling policies $\alpha$
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-02-27 paper/retrofit.tex
minor

@@
 
-\begin{figure}
-\begin{align*}
-  &|erase il (iconf iS its) =
-  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
-  &|erase il (tconf id il' ie) =| \begin{cases}
-    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
-    |bullet| & |il' cantFlowTo il| \\
-    |tconf id il' ie| & \text{otherwise}
-  \end{cases} \\
-  &|erase il emptyset = emptyset|\\
-  &|erase il (iS [id mapsto Q]) =| \begin{cases}
-    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
-    & \text{the label of thread |id|} \\
-    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
-  \end{cases} \\
-  &|erase il Q = filter il Q|
-\end{align*}
-\caption{
-Erasure function for configurations, threads, system state, and
-message queus.  In all other cases, |erasef il| is applied
-homomorphically.
-\label{fig:erasure}
-}
-\end{figure}
-
 \Red{When both languages have booleans, it is relatively simple to define
@@
 
-\subsection{Formal Guarantees}
-
-\begin{definition}[Information-flow control language]
-    An information-flow control language |L| is a tuple |(C, .->,
-    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
-    reduction relation between machine configurations and |erasef l : C -> tyerase C|
-    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  For sequential languages, the
-    language is augmented with a set of terminal configuration states $V
-    \subseteq |C|$ for which there are no possible further transitions.
-\end{definition}
-
-%{
-%format .->  = "\overset{\alpha}{\hookrightarrow}"
-Using this definition, we can now expand the definition for the
-specification family of languages.
-%
-Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
-erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
-= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
-tasks whose expressions have been reduced to values.\footnote{
-Here, we abuse notation by using metavariables to describe types of
-the corresponding non-terminals, e.g., |it| for the type of task.
-}
-%}
-
-\begin{definition}[$l$-equivalence]
-    In a language |(C, .->, erasef l)|, two machine configurations
-    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
-    if |erase l c = erase l c'|.
-\end{definition}
-
-\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
-  A language |(C, .->, erasef l)| is termination
-  sensitive non-interfering if for any label |l|, and configurations
-  |c1, c1', c2 member C|, if
-  \begin{equation} \label{eq:tsni-lhs}
-    |c1| \approx_{|l|} |c2|
-    \qquad \text{and} \qquad
-    |c1| |.->|^* |c1'|
-  \end{equation}
-  then there exists a configuration |c2' member C| such that
-  \begin{equation} \label{eq:tsni-rhs}
-    |c1'| \approx_{|l|} |c2'|
-     \qquad \text{and} \qquad
-    |c2| |.->|^* |c2'|
-    \ \text{.}
-  \end{equation}
-\end{definition}
-
-\begin{theorem}[Concurrent specification language is TSNI]
-For any target language |targetLang nop|, |specLang roundrobinf
-(targetLang nop)| satisfies TSNI.
-\end{theorem}
-
-\begin{definition}[Termination Insensitive Non-Interference (TINI)]
-  A language |(C, V, .->, erasef l)| is termination
-  insensitive non-interfering if for any label |l|, and configurations
-  |c1, c2 member C| and |c1', c2' member V| if
-   $|c1| \approx_{|l|} |c2|$,
-   $|c1| |.->|^* |c1'|$, and
-   $|c2| |.->|^* |c2'|$, then
-   $|c1'| \approx_{|l|} |c2'|$.
-\end{definition}
-
-\begin{theorem}[Sequential specification language is TINI]
-For any target language |targetLang nop|, |specLang seqf (targetLang
-nop)| satisfies TINI.
-\end{theorem}
-
 \subsection{Generalizing further}

### 2014-02-27 paper/formal.tex
more + fix erasure function

@@
-\section{Security Guarantees}
-\label{sec:formal}
+\subsection{Security guarantees}
+\label{sec:retrofit:formal}
 
@@
 %
-Specifically, we show that a combined langauge, |specLang alpha
-(targetLang nop)|, satisfies a form of non-interference.
+Concretely, we show that an IFC langauge, |specLang alpha (targetLang
+nop)|, satisfies non-interference(NI)~\tocite{}.
 %
@@
 leaked by programs written in the language.
+%
+As we show below, the precise scheduling policy |alpha| dictates
+whether or not the guarantee holds for programs with diverging tasks.
 
-In this section, we show that LIO computations satisfy
-termination-sensitive non-interference. As in ~\cite{Li+:2010:arrows,Russo+:Haskell08,stefan:lio}, 
-we prove this property by using the
-\emph{term erasure} technique. The erasure function $\eraseName_L$
-rewrites data at security levels that the attacker cannot observe into
-the syntax node $\hole$.
-
-\begin{figure}
-\begin{align*}
-  &|erase il (iconf iS its) =
-  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
-  &|erase il (tconf id il' ie) =| \begin{cases}
-    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
-    |bullet| & |il' cantFlowTo il| \\
-    |tconf id il' ie| & \text{otherwise}
-  \end{cases} \\
-  &|erase il emptyset = emptyset|\\
-  &|erase il (iS [id mapsto Q]) =| \begin{cases}
-    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
-    & \text{the label of thread |id|} \\
-    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
-  \end{cases} \\
-  &|erase il Q = filter il Q|
-\end{align*}
-\caption{
-Erasure function for configurations, threads, system state, and
-message queus.  In all other cases, |erasef il| is applied
-homomorphically.
-\label{fig:erasure}
-}
-\end{figure}
+We prove non-interference for |specLang alpha (targetLang nop)| using
+the \emph{term erasure} technique of~\tocite{}.
+%
+Intuitively the term erasure technique allows us to show that a an
+attacker does not learn any sensitive information from a program
+written in a NI language, if the program behaves identically to the
+same program with all sensitive data ``erased.''
+% 
+To accommodate for this, we extend our formalism to account for
+programs with erased configurations and a function |erasef l| that
+performs erasures, usually by rewriting (parts of) configurations that
+are more sensitive than |l| to a new syntactic construct |bullet|.
+%
+Directly, we can now give a precise definition for the kinds of
+languages we wish to prove NI.
 
@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-Using this definition, we can now expand the definition for the
-specification family of languages.
+Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
+V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
+$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
+type for tasks whose expressions have been reduced to
+values.\footnote{
+  Here, we abuse notation by describing types for configuration parts using the
+  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
+  task.
+}
 %
-Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
-erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
-= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
-tasks whose expressions have been reduced to values.\footnote{
-Here, we abuse notation by using metavariables to describe types of
-the corresponding non-terminals, e.g., |it| for the type of task.
+Figure~\ref{fig:erasure} gives the precise definition for our erasure function.
+%
+%}
+
+\begin{figure}
+\begin{align*}
+  &|erase il (iconf iS its) =
+  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
+  &|fullconf id il' tS ie| \begin{cases}
+    |bullet| & |il' cantFlowTo il| \\
+    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
+  \end{cases} \\
+  &|erase il emptyset = emptyset|\\
+  &|erase il (iS [id mapsto Q]) =| \begin{cases}
+    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
+    & \text{the label of thread |id|} \\
+    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
+  \end{cases} \\
+  &|erase il Q = filter il Q|
+\end{align*}
+\caption{
+Erasure function for configurations, tasks, queue map, and message queues.
+In all other cases, including target-language constructs, |erasef il| is
+applied homomorphically.
+\label{fig:erasure}
 }
-%}
+\end{figure}
 

### 2014-02-27 paper/concrete.tex
update first half of the proof.

@@
 \begin{definition}[Non-interference preserving, restricted isomorphism (NPRI)]
+  \label{def:npri}
   We call an IFC language
@@
 
-\Red{Adapt the following proofs.}
+For the proof of Theorem~\ref{thm:npri}, we first show that the
+abstract language, potentially augmented with predicates as described
+in the first point of Definition~\ref{def:npri}, satisfies
+non-interference.  Combining this result with the isomorphism theorems
+will prove the goal as desired.
+
+\begin{theorem}
+  \label{thm:rr-tsni-general}
+  For any target language |targetLang|,
+  the language |specLang roundrobinf targetLang| where predicates $P$
+  have potentially been added to the reduction rules as described in
+  Definition~\ref{def:npri} satisfies TSNI.
+\end{theorem}
+
+Theorem~\ref{thm:rr-tsni} is a simple consequence of this
+(for the case where without any additional predicates).
+Before we proceed with the proof of this theorem, we state a
+lemma we will use.
 
 \begin{lemma}
-  \label{lemma:tsni}
-  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
+  \label{lemma:rr-tsni-general}
+  We consider, for any target language |targetLang|,
+  the information-flow control
+  language |specLang roundrobinf targetLang| where a predicate $P$
+  has potentially been added to the reduction rules as described in
+  Definition~\ref{def:npri}.  Then,
+  for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
   \begin{equation} \label{eq:tsni-lemma-lhs}
@@
   \end{equation}
-  then there exists a configuration |ic2'| such that
+  there exists a configuration |ic2'| such that
   \begin{equation} \label{eq:tsni-lemma-rhs}
@@
   \]
-  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
+  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
   |ic''| with
@@
   Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
-  us~\eqref{eq:tsni-rhs}, which concludes the proof.
+  us the right-hand side of the implication in the TSNI
+  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
 \end{proof}
-\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
-  We proof the lemma by induction on the derivation
-  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
-  could have been used to make the reduction step.
+\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
   First, we observe there must be at least one task in |ic1|, otherwise
@@
   \begin{itemize}
-    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
-    step for
+    \item $|erase il it1|=|bullet|$.
+    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
+    where |lcurr| is the label of |it1|.
+    In this case, we do not need to take a step for
     |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
     To see that, note that the tasks |its1| in |ic1| are left in the
-    same order and unmodified. The task |it1| either
+    same order and unmodified (the scheduling policy only
+    modifies the first task). The task |it1| either
     gets dropped (by \textsc{I-noStep}), or
-    transforms into a new task |it1'| as well as potentially spawning a new
+    transforms into a task |it1'| as well as potentially spawning a new
     task |it1''|.  Since both |it1'| and |it1''| have a label that is
-    at least as high as the label of |it1|, they will get filtered
-    by |erasef il| in |ic1'|.
-    Lets consider the possible changes to |iS1|: If |it1| sends a
-    message, then the corresponding queue in |iS1'| will contain one
-    more message.  However, that message has the label of |it1| (or a higher
-    label), and will thus get erased by |erasef il|.
-    Finally, receiving or not receiving a message (by
-    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
-    task |it1|, which are erased from |iS1|.
-    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.
-
-    \alphacondition{We need all scheduling policies to not change the order
-      of any tasks (except for the first one).  Newly spawned task can appear
-      anywhere in the list.}
-    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
+    at least as high as the label of |it1| (can be seen
+    by inspecting all reduction rules), they will get filtered
+    by |erasef il| in |ic1'|.  Therefore, the |il| equivalence of the
+    task list is guaranteed.
+    Lets consider the possible changes to |iS1|:
+    Only three reduction rules change |iS1|,
+    thus it suffices to consider these cases:
+    \begin{description}
+      \item[Case \textsc{I-send}]
+      A new message triple with label |il'| gets added to the message
+      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
+      the triple will get erased.
+      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
+      In this case, only the queue of
+      task |it1| can change, which gets erased.
+    \end{description}
+    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
+%    \alphacondition{We need all scheduling policies to not change the order
+%      of any tasks (except for the first one).  Newly spawned task can appear
+%      anywhere in the list.}
+    \item $|erase il it1|\neq|bullet|$.
+    Here, there must be a corresponding
     task |it2| in |ic2|,

### 2014-02-27 paper/retrofit.tex
update first half of the proof.

--- 2014-02-27 paper/retrofit.tex
@@
 \begin{theorem}[Concurrent specification language is TSNI]
+  \label{thm:rr-tsni}
 For any target language |targetLang nop|, |specLang roundrobinf

### 2014-02-27 paper/formal.tex

@@
 %
-Figure~\ref{fig:erasure} gives the precise definition for our erasure function.
+The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
+containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
+our erasure function.
+%
+A task and its corresponding message queue is completely removed from the task
+list if its label does not flow to the attacker observation level |il|;
+otherwsie, apply the erasure function homomorphically and remove any message
+from the task's message queue that are more sensitive than |il|.\footnote{
+We note that the definition of |erasef il| precisely captures the IFC
+language's attacker model.  For instance, in our case, by removing sensitive
+tasks and messages from the system, we assume that that the attacker cannot
+observe the number of sensitive tasks or messages.
+}
 %
@@
 
-\begin{figure}
+\begin{figure} % fig:erasure
 \begin{align*}
   &|erase il (iconf iS its) =
-  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
+  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
   &|fullconf id il' tS ie| \begin{cases}
@@
 \caption{
-Erasure function for configurations, tasks, queue map, and message queues.
+Erasure function for tasks, queue maps, message queues, and configurations.
 In all other cases, including target-language constructs, |erasef il| is

### 2014-02-27 paper/formal.tex
rm formal from retrofit.tex

@@
-\subsection{Security guarantees}
-\label{sec:retrofit:formal}
+\section{Security guarantees}
+\label{sec:formal}
 
@@
 list if its label does not flow to the attacker observation level |il|;
-otherwsie, apply the erasure function homomorphically and remove any message
-from the task's message queue that are more sensitive than |il|.\footnote{
+otherwsie, we apply the erasure function homomorphically and remove any message
+from the task's message queue that are more sensitive than |il|.
+
 We note that the definition of |erasef il| precisely captures the IFC
@@
 observe the number of sensitive tasks or messages.
-}
 %
@@
   \end{cases} \\
-  &|erase il Q = filter il Q|
+  &|erase il Q = filter il Q|\\
+  &|erase il v = v|
 \end{align*}

### 2014-02-27 paper/concrete.tex
Isomorphism is most important.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-\begin{definition}[Weak isomorphism of information-flow control languages]
-  A language \con{|(C, .->, erasef l)|} is \textit{weakly isomorphic} to a
-  language \abs{|(iC, .->, erasef l)|} if there exist total functions
-  |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
-  |finv .. f = idf iC|.  Furthermore, the following coherence conditions
-  must hold:
-  \begin{itemize}
-    \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
-    $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
-    $l$-equivalences and |.->|, and
-    \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
-  \end{itemize}
-  We furthermore call the two languages \textit{isomorphic} if both
-  |f| and |finv| are functorial over |.->|.
+\begin{definition}[Isomorphism of information-flow control languages]
+  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
+  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
+  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
+  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
+  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
+  $l$-equivalences and |.->|.
 \end{definition}
+
+\Red{In some cases, this restriction can be weakened, where |finv| does
+not have to be functorial over |.->|}
 

### 2014-02-27 paper/formal.tex
more

@@
 }
-%
 The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
@@
 from the task's message queue that are more sensitive than |il|.
-
-We note that the definition of |erasef il| precisely captures the IFC
-language's attacker model.  For instance, in our case, by removing sensitive
-tasks and messages from the system, we assume that that the attacker cannot
-observe the number of sensitive tasks or messages.
-%
 %}
@@
 \end{align*}
-\caption{
-Erasure function for tasks, queue maps, message queues, and configurations.
-In all other cases, including target-language constructs, |erasef il| is
-applied homomorphically.
-\label{fig:erasure}
-}
+\caption{ Erasure function for tasks, queue maps, message queues, and
+configurations.  In all other cases, including target-language constructs,
+|erasef il| is applied homomorphically.  \label{fig:erasure} }
 \end{figure}
 
-\begin{definition}[$l$-equivalence]
+We note that the definition of |erasef il| precisely captures the IFC
+language's attacker model. 
+%
+For instance, in our case, by removing sensitive tasks and messages from the
+system, we assume that that the attacker cannot observe the number of sensitive
+tasks or messages.
+%
+While such assumptions are standard~\tocite{}, our defintions allow for
+stronger attackers that may be able to inspect resource usage.\footnote{
+  We belive that we can extend |specLang alpha (targetLang nop)| to
+  such models using the resource limits techniqes of~\tocite{}.
+  %
+  We leave this extension to future work.
+}
+
+Non-inteference relies on the defintion of an attacker's observational power at
+security level |l|, which is typically defined as an equivalence
+relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
+distinguish two configurations that are |l|-equivlaent.
+%
+Since our erasure function captures attacker mode, we simply define this
+equivalance as the syntactic-equivalence of erased configurations.
+%
+\begin{definition}[|l|-equivalence]
     In a language |(C, .->, erasef l)|, two machine configurations
@@
 \end{definition}
+%
 

### 2014-02-27 paper/concrete.tex
rm some unused stuff

--- 2014-02-27 paper/concrete.tex
@@
 
-The operational semantics we have derived in the previous section
-constitutes an abstract \emph{specification}: a semantics for which
-non-interference is (obviously) true.  This specification can guide the
-design of an information-flow calculus which would not be directly
-derivable from our procedure, but is related to some such derivation.
-For example, in our mini-ML language, the combined semantics requires
-each thread to have a separate ML heap.  In an actual implementation, we
-might like to only have a single heap and disallow the passing of
-references between threads.  This restriction maintains a correspondence
-between the abstract multiple heaps and the concrete single heap.  We might
-hope that we can prove noninterference for this new system by reusing
-noninterference for the old system.
-
 However, modifying operational rules poses a distinct problem for
@@
 \end{figure}
-
-The approach we will take is in two steps.  First, we sidestep the
-restriction problem by demanding that the concrete implementation be
-\emph{isomorphic} to the abstract specification, but perhaps having a different
-runtime representation (a single heap) and some well-formedness
-condition (every item on the heap only contains pointers from a single
-location).  Isomorphism will preserve nonintereference, but it will also means all
-transitions in the abstract language have to be implemented, including
-undesirable transitions such as sending a pointer to another thread makes
-the pointer dangling.  Next, we define a desugaring into this language
-which adds dynamic checks, eliminating the possibility for these undesirable
-transitions to be exercised.
 

### 2014-02-27 paper/formal.tex

@@
 list if its label does not flow to the attacker observation level |il|;
-otherwsie, we apply the erasure function homomorphically and remove any message
+otherwise, we apply the erasure function homomorphically and remove any message
 from the task's message queue that are more sensitive than |il|.
@@
 %
-While such assumptions are standard~\tocite{}, our defintions allow for
+While such assumptions are standard~\tocite{}, our definitions allow for
 stronger attackers that may be able to inspect resource usage.\footnote{
-  We belive that we can extend |specLang alpha (targetLang nop)| to
-  such models using the resource limits techniqes of~\tocite{}.
+  We believe that we can extend |specLang alpha (targetLang nop)| to
+  such models using the resource limits techniques of~\tocite{}.
   %
@@
 
-Non-inteference relies on the defintion of an attacker's observational power at
+Non-interference relies on the definition of an attacker's observational power at
 security level |l|, which is typically defined as an equivalence
 relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
-distinguish two configurations that are |l|-equivlaent.
+distinguish two configurations that are |l|-equivalent.
 %
-Since our erasure function captures attacker mode, we simply define this
-equivalance as the syntactic-equivalence of erased configurations.
+Since our erasure function captures the attacker model, we simply define this
+equivalence as the syntactic-equivalence of erased configurations.
 %

### 2014-02-27 paper/formal.tex
more

@@
 
+Intuitively, we can now state that a language satisfies non-interference if an
+attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
+configurations.
+%
+This precise NI property is called termination sensitive non-interference
+(TSNI), since it considers runs of programs, and thus does not allow for leaks
+due termination or internal timing behavior.
+%
+Formally, we define TSNI as follows.
+
 \begin{definition}[Termination Sensitive Non-Interference (TSNI)]

### 2014-02-27 paper/concrete.tex
Finish proof.

@@
     In |ic2|, we can first take some number of steps until |it2| moves
-    to the front of the list (\Red{Say more precisely why
-      (basically because we require the scheduling policy to do that)}).
+    to the front of the list.
+    This is the case regardless of any additional side conditions $P$ on
+    rules, because for all of these tasks, it can either take an actual
+    step, or it gets dropped by \textsc{I-noStep} (which is always
+    possible, as there cannot be an additional side condition on this
+    rule).  All tasks that didn't get dropped are still at a label
+    that isn't below |il| and thus get erased.
 
-    \alphacondition{The scheduling policy must eventually let any task in
-      the task list evaluate.  In particular, it cannot get stuck when the
-      first task gets stuck, or keep executing a small number of tasks
-      exclusively forever (e.g. just execute the first task all the time
-      if it gets into an infinite loop).}
+%    \alphacondition{The scheduling policy must eventually let any task in
+%      the task list evaluate.  In particular, it cannot get stuck when the
+%      first task gets stuck, or keep executing a small number of tasks
+%      exclusively forever (e.g. just execute the first task all the time
+%      if it gets into an infinite loop).}
 
     Therefore, after |ic2| has potentially executed some number of steps
-    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
-    get erased and are thus equivalent.
-    The task |it2| can now take exactly the same step as |it1|;  we only
+    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
+    respectively, don't get erased and are thus equivalent.
+    The task |it2| can now take exactly the same step as |it1|;  this
+    is true even with arbitrary additional premises $P$ that follow
+    the condition in Definition~\ref{def:npri}, since those
+    predicates only depend on |erase il ic1|, which is equivalent
+    to |erase il ic2|, and thus those predicates evaluate in the same way.
+    Thus, we only
     need to argue that the potential differences in |iS1| and |iS2| cannot
@@
     |il| equivalent).
-    Again, only send and receive will change |iS|, so we consider all
-    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
-    a message is sent, then the message is added to the same queue.  This
+    Again, only sending and receiving will depend on, or change |iS|,
+    so we consider all these cases.
+    \begin{description}
+      \item[Case \textsc{I-send}]
+      Here, the task |it2| will send the same message to the same
+      receiver queue. This
       queue is either completely erased, or it is |il| equivalent.  In both
       cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
+      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
       When the tasks are receiving a message, then by the reduction rules
-    we know that they first filter the queue by the label of |it1|.  We
+      we know that they first filter the queue by the label
+      |lcurr| of |it1|.  We
       also know that the queues are equivalent when filtered by the less
@@
       queue are equivalent.
+    \end{description}
   \end{itemize}

### 2014-02-27 paper/formal.tex
Add missing label.

--- 2014-02-27 paper/formal.tex
@@
 
-\begin{theorem}[Concurrent specification language is TSNI]
+\begin{theorem}[Concurrent specification language is TSNI].
+  \label{thm:rr-tsni}
 For any target language |targetLang nop|, |specLang roundrobinf

### 2014-02-28 paper/formal.tex
switching cafe

@@
 \end{definition}
+%
+In other words if we take two |l|-equivalent configurations, then for every
+intermediate step taken by the first configuration, there is a corresponding
+step that the second configuration can take to result in a configuration that
+is |l|-equivalent to the first resultant configuration.
+\Red{TODO: Do we want a commutative diagram to illustrate this?}
+
+\begin{figure}
+  Round robin:
+\begin{code}
+  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
+  roundrobin D (it1, it2, ldots)     = it2, ldots
+  roundrobin N (it1, it2, ldots)     = it2, ldots
+  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
+\end{code}
+  Sequential:
+\begin{code}
+  seq step (it1, it2, ldots)     = it1, it2, ldots
+  seq N (it1, it2, ldots)        = it1, it2, ldots
+  seq D (it)                     = it
+  seq D (it1, it2, ldots)        = it2, ldots
+  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
+\end{code}
+\caption{Round robin and sequential scheduling policies.\label{fig:scheduler}}
+\end{figure}
+
+Directly, we now show that our IFC language satisfies TSNI under a particular
+scheduling policy.
+%
+Specifically, we consider the language under the round-robin scheduler
+|roundrobinf| given in Figure~\ref{fig:scheduler}.
 
@@
 \end{theorem}
+
+In general TSNI will not hold for an arbitrary scheduler |alpha|.
+%
+For example, |specLang alpha (targetLang nop)| with a scheduler that inspects a
+sensitive threads current state when deciding which thread to schedule next
+will clearly not satisfy TSNI.
+%
+In Section~\toref{} we detail the preceise scheduler for which our
+specification language is TSNI.
+%
+Here, we simply remark that even non-adversairal schedulers are not always safe.
+
+Consider the sequential scheduling policy |seqf| given in
+Figure~\ref{fig:scheduler}.
+%
+It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
+TSNI.
+%
+\Red{HERE}
 

### 2014-02-28 paper/formal.tex
rm done state from scheduler since we it's captured by nostep

@@
   roundrobin step (it1, it2, ldots)  = it2, ldots, it1
-  roundrobin D (it1, it2, ldots)     = it2, ldots
   roundrobin N (it1, it2, ldots)     = it2, ldots
@@
   seq N (it1, it2, ldots)        = it1, it2, ldots
-  seq D (it)                     = it
-  seq D (it1, it2, ldots)        = it2, ldots
+  seq N (it)                     = it
   seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots

### 2014-02-28 paper/formal.tex
fix

@@
 intermediate step taken by the first configuration, there is a corresponding
-step that the second configuration can take to result in a configuration that
-is |l|-equivalent to the first resultant configuration.
+number of steps that the second configuration can take to result in a
+configuration that is |l|-equivalent to the first resultant configuration.
 \Red{TODO: Do we want a commutative diagram to illustrate this?}

### 2014-02-28 paper/extensions.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff
Comments about type safety
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \label{sec:extensions}
+\cut{
 
@@
 language to provide IFC-aware versions of target language features.
+
+}
+
+\subsection{Type safety}
+
+One important consideration for any new language feature is whether
+or not it preserves type safety.  If implementations are allowed to
+have undefined behavior when the system gets stuck, concerns of type
+safety can be directly applicable to security.
+
+In our presentation, we have demanded that implementations \emph{not}
+have undefined behavior when getting stuck: in such situations, the
+\textsc{I-noStep} rule applies, where the stuck thread should be dropped
+from execution.  Our combined language will be not get stuck, even if
+the target language could get stuck.  This sort of guarantee can be
+achieved at a coarse granularity for languages like C by using hard
+isolation.  However, for many other languages, this is too stringent a
+requirement.
+
+A possible way to relax this requirement is to drop the \textsc{I-noStep}
+rule, and instead demand type-safety of the combined language.  This
+depends on the type system of the target language, so it is difficult to
+make any general statements about how one would go about doing this.  However,
+there are few general remarks to be made:
+
+\begin{itemize}
+    \item In Matthews and Findlers original
+        paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
+        on using type boundaries to mediate between the type systems of
+        the two languages, i.e. handling conversions of values from
+        one language to the other.  These techniques are directly applicable here.
+
+    \item In the case of mini-ML, type safety proceeds by a preservation theorem
+        that refers to well-typed stores.  In our setting, there are now multiple
+        stores, and expressions may move from being interpreted with one store
+        to another (e.g. when an address is sent from one thread to
+        another); a clear violation of type safety.  In this case, operations
+        such as \textbf{send} have their typing rules require
+        the expressions being sent be typeable in an arbitrary well-typed store,
+        statically disallowing the sending of addresses, or any types which
+        may contain addresses.  In practice, this may be further restricted to
+        types which can be easily marshalled, e.g. strings.
+
+    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
+        influences the difficulty of the type-safety proof for
+        \textbf{fork} when the target language has a store.  When
+        $\kappa$ is identity, most expressions can be allowed, since the store
+        remains the same; if $\kappa$ drops the store, however, only closed expressions
+        can be forked.
+\end{itemize}

### 2014-02-28 paper/monad.tex
Drop the cite.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 monad can depend on the order in which the monad transformers are
-applied. \Red{cite} The canonical example of this phenomenon is the
+applied. The canonical example of this phenomenon is the
 composition of the state monad and the error monad: depending on the

### 2014-02-28 paper/monad.tex
Minor changes to monad.tex.

@@
 language with information flow control.  In this section, we present
-a more abstract view of what is going on, phrased in the language of monads
+a more abstract view of the situation, phrased in the language of monads
 and monad transformers.  The key idea is that the computational effects
 of the target language should be thought of as a \emph{monad transformer}
-on top of the information-flow control base monad.  Readers who are not
+on top of the information flow control base monad.  Readers who are not
 familiar with monads should feel free to skip this section.
@@
 computational effects of a target language with information flow control
-\emph{without} compromising noninterference.  When the base monad is
+\emph{without} compromising non-interference.  When the base monad is
 kept abstract (in the style of a restricted IO monad~\cite{Terei:2012:SH:2364506.2364524}),
-there is an easy argument why any monad transformer must also preserve noninterference:
+there is an easy argument why any monad transformer must also preserve non-interference:
 the monad transformer could have been implemented simply as a \emph{pure} interpreter, and
@@
 developing the relationship between concrete semantics and abstract
-semantics in \ref{sec:concrete} relates to the question of monad
-isomorphisms in the presence of data abstraction.  We leave
-investigating this connection in more detail to future work.
+semantics in Section~\ref{sec:concrete} relates to the question of monad
+isomorphisms in the presence of data abstraction.  We leave the
+investigation of this connection in more detail to future work.

### 2014-02-28 paper/formal.tex
formal done; releasing lock

@@
 
-Consider the sequential scheduling policy |seqf| given in
+Consider, for example, the sequential scheduling policy |seqf| given in
 Figure~\ref{fig:scheduler}.
@@
 %
-\Red{HERE}
+Concretely, consider a target language similar to |targetLang ML| with an
+additional expression terminal |diverge| that denotes a divergent computation,
+i.e., |diverge| always reduces to |diverge| and a a simple label lattice |{pub,
+sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|, we can write the
+following program in the specification language:
+\begin{code}
+ic1 = iS ; fullconf 1 sec tS1 (IT(when false diverge)),  fullconf 2 pub tS1 ie
+ic2 = iS ; fullconf 1 sec tS1 (IT(when true diverge)),   fullconf 2 pub tS2 ie
+\end{code}
+These two configurations are |pub|-equivalent, however |ic1| will reduce (in two
+steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
+any progress.
+%
+Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
+Though we do not model labeled channels, extending the calculus with such a
+feature is straight forward, see Setion~\ref{}.
+} then the |sec| thread's decision to diverge or not is directly leaked to a
+public entitiy.
 
+In certain cases, however, a TSNI-safe concurrent scheduling policy such as
+|roundrobinf| cannot be considered without imposig a non-trivial burden on the
+concrete implementation.
+%
+(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
+target language.)
+%
+Hence, we consider an alternative NI property---called termination insensitive
+non-interference---that can also be upheld by sequential languages at the cost
+of leaking one bit through (non)-termination.
+%
 \begin{definition}[Termination Insensitive Non-Interference (TINI)]
@@
 
+TSNI states that if we take two |l|-equivalent configurations, and both
+configurations reduce to terminal configuration states (for which there are no
+possible further transitions), then the end configurations are also
+|l|-equivalent.
+%
+We highlight that this statement is much weaker than TSNI: it only states that
+terminating programs do not leak sensitive data.
+
+Nevertheless, we believe TINI to be a useful for many scenariors and thus we
+show that our IFC language with the sequential scheduling policy |seqf|
+satisfies TINI.
+%
 \begin{theorem}[Sequential specification language is TINI]

### 2014-02-28 paper/retrofit.tex
rm formal from retrofit.tex
Minor formatting updates.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-02-27 paper/retrofit.tex
@@
 tv   ::= \tx.te | true | false | ta
-tty   ::= bool | tty -> tty | ref tty
 te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
@@
 \end{code}
-
-\Red{Suggestion: Only give the rules for references, because otherwise this is all standard.}
 
@@
 \inferrule[T-ref]
-{| tS' = tS [ ta mapsto tv ] | } 
-{| conf tS (ref tv) -> conf tS' ta |}
-{| fresh (ta) |}
+{ }
+{| conf tS (ref tv) -> conf (tS [ ta mapsto tv ]) ta |}
+{| fresh ta |}
 
@@
 \inferrule[T-deref]
-{| tv = tS(ta) |}
-{| conf tS (!ta) -> conf tS tv |}
+{ }
+{| conf tS (!ta) -> conf tS (ap ts ta) |}
 
@@
 \inferrule[T-ass]
-{| tS' = tS [ ta mapsto tv ] |} 
-{| conf tS (ta := tv) -> conf tS' tv |}
+{ }
+{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}
 \end{mathpar}

### 2014-02-28 paper/concrete.tex
checkpoint.

@@
 The operational semantics we have defined in the previous section
-satisfy termination sensitive non-interference by design.
+satisfy non-interference by design.
 We achieve this general statement that works for a large class of
@@
 language by reusing existing infrastructure.  In the running example,
-a concrete implementation might use a single global heap, and ensure
-that references do not cross task boundaries, and thus preserving
-non-interference.
+a concrete implementation might use a single global heap.
+More precisely, instead of using a configuration of the form
+\[|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|\]
+we would like a single global heap as in
+|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
+
+If the operational rules are adapted na\"ively to this new setting,
+then non-interference can be violated.  In particular, it is not
+sound to share references to a heap cell between different tasks
+in general.  Otherwise, information can be trivially leaked by copying
+secret data into a reference in one task, and then
+read again by a another task with a lower label.
+Clearly, we cannot
+modify the semantics in arbitrary ways if we are hoping to preserve
+non-interference, but how can we know if our changes to the abstract
+semantics preserve non-interference?
+The intention of our single heap implementation was to be more efficient
+by using one global heap, but conceptually maintain isolation between
+task by not allowing sharing of references between tasks.
+This intuition of having a different (potentially more efficient)
+concrete semantics that behave like the abstract semantics
+can be formalized by the following definition:
+
+\begin{definition}[Isomorphism of information-flow control languages]
+  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
+  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
+  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
+  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
+  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
+  $l$-equivalences and |.->|.
+
+  If we weaken this restriction such that |finv| does
+  not have to be functorial over |.->|, we call the
+  language \con{|(C, .->, erasef l)|} \textit{weakly isomorphic} to
+  \abs{|(iC, .->, erasef l)|}.
+\end{definition}
+
+Providing an isomorphism between the two languages allows us to
+preserve (termination sensitive or insensitive) non-interference
+as the following two theorems state.
+
+\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
+  \tar{L} satisfies TSNI.
+\end{theorem}
+
+\begin{proof}
+  Shown by transporting configurations and reduction derivations from
+  \tar{L} to \ifc{L}, applying TSNI, and then transporting the
+  resulting configuration, $l$-equivalence and multi-step derivation back.
+\end{proof}
+
+\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
+  If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
+  satisfies TINI, then \con{L} satisfies TINI.
+\end{theorem}
+
+\begin{proof}
+  Shown by transporting configurations and reduction derivations
+  from \con{L} to \abs{L}, applying TINI and transporting the resulting
+  equivalence back using functoriality of |finv| over $l$-equivalences.
+\end{proof}
+
+A na\"ive attempt at our single heap semantics
+will not allow us to construct an isomorphism
+with the abstract language |specLangML alpha|, and instead highlights
+where things will go wrong.
 
@@
 
-Instead of using a configuration of the form
-\[|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|\]
-as is done in |specLangML alpha|
-where every task has its
-own ML heap, we would like a single global heap as in
-|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
 To keep up a fictional separation between the portions

### 2014-02-28 paper/retrofit.tex

@@
 
-While we would like to add information flow control to \emph{any}
-language, we will have to make some assumptions about the form of the
-target language.  We consider languages whose semantics can be expressed
-in the form of abstract machines |(tS, tE, te, tv, ->)|, where |tS| is the
-global machine state, |tE| is an evaluation context, |te| is an
-expression in the language, |tv| is the set of values, and |->| is the reduction relation on such
-configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
-\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
-target language have been colored red.
+Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
+operational semantics and combine it with an \textit{{\color{blue} information
+flow control language}}.  For concreteness, we use a simple, untyped,
+ML-like language with mutable references as our target language.
+However, our technique will be indifferent to the actual target language
+chosen: it need only be prepared for interoperability by being expressed
+in the style of Matthews and
+Findler~\cite{Matthews:2007:OSM:1190216.1190220}.  This procedure will
+equip the target language with primitives for implementing dynamic
+information control in the style of LIO~\cite{lio}, which we will
+describe in more detail shortly.
 
-In Figure~\ref{fig:ml}, we give an example of a standard ML-like
-language with mutable references.  These semantics have been prepared
-for interoperability in the style of Matthews and Findler~\Red{XXX}; in
-particular, the evaluation rules have been expressed in terms of an
-evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
-this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
-when we perform the embedding, we will reinterpret the meaning
-of this evaluation context, lifting these semantics to an IFC setting.
+We have typeset nonterminals of the target language using \textbf{{\color{red}
+bold font}} while the nonterminals of the IFC language have been typeset
+with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
+a color copy of this paper, where target language nonterminals are colored red
+while IFC language nonterminals are colored blue.
+
+\subsection{Target language: Mini-ML}
+
+In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
+mutable references \Red{and errors}, prepared for combination with an
+information flow control language.  The presentation is standard, but it
+is worth paying some attention to the Felleisen-Hieb reduction
+semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
+operational semantics of the system.  Our language defines an evaluation
+context |tE|; however, the evaluation rules have been expressed in terms
+of a different evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  To
+derive the usual operational semantics for this language, the evaluation
+context merely needs to be defined as |conf tS te @= tS, tE[ te ]|.
+However, when we combine this language with an IFC language, we must
+reinterpret the meaning of this evaluation context.
+In general, we require that a target language be expressed in terms
+of some global machine state |tS|, some evaluation context |tE|,
+some expressions |te|, some set of values |tv| and a reduction
+relations on full configurations $|tS| \times |tE| \times |te|$.
 
@@
 
-Next, we describe the IFC language.  \Red{Description of the IFC language as
-a standard floating label system, or backwards reference to the
-background section.}  In Figure~\ref{fig:ifc}, we describe the syntax
-of the language, and provide rules for all operations which operate on a single
-thread.  \Red{One could imagine these rules giving the definition of a very
-boring information flow control language, by defining |niconf iS id il ie| appropriately
-and providing an appropriate erasure function.}
+\subsection{IFC language}
 
-We use the notation |filter il Q| to indicate a filter function which removes message whose labels do not
+Information flow control seeks to enforce a security policy known as
+\emph{noninterference}: public results must not depend on secret inputs.
+Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
+with data, which encodes a policy of whether or not data tagged with one
+label can flow to |canflowto| another label.  Since our embedding is agnostic
+to the choice of labeling scheme, we simply represent labels with the metavariable
+$l$, but do not discuss them in more detail.
+
+In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
+evaluation rules for a minimal information-flow control language.  The
+evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
+of the current thread which is running, including on the right-hand side
+the current label $l$ (which protects the program counter of the thread)
+and the thread ID $i$.
+
+Ordinarily, information flow control languages are defined by directly
+stating a base language plus information flow control operators.  In
+contrast, our language is purposely minimal: it does not have sequencing
+operations, control flow, or other constructs.  However, it contains
+support for the following core information flow control features:
+
+\begin{itemize}
+    \item First-class labels, with label values $l$ as well as operations for computing on
+labels (|canflowto|, |lub| and |glb|),
+    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the thread (note a thread can only increase its label, and not decrease it),
+    \item Operations for non-blocking inter-thread communication (\textbf{send} and \textbf{recv}),
+        which interact with the global store of per-thread message queues |iS|, and
+    \item A forking operation, which will be described in more detail in the next section.
+\end{itemize}
+
+The form of \textbf{send}/\textbf{recv} are inspired by methods of inter-worker communication
+in web browser APIs \Red{cite}, however in Section~\ref{sec:extensions} we
+discuss other possible choices for information flow control aware communication
+primitives.  Their rules are non-standard and worth commenting on: when a thread places
+a message on the message queue of the thread it is sending to, it also adds the current
+label when it sent the message.  When the recipient reads out messages from its queue,
+it filters out (notated using |filter il Q|) messages whose labels do not
 flow to |il|. Specifically, if |Q| is the empty list |nil|, the

### 2014-02-28 paper/concrete.tex
checkpoint.

@@
 where things will go wrong.
+To successfully construct an isomorphism, our concrete semantics need
+to mirror the behavior of the abstract semantics, most importantly
+in the case where tasks interact.  Namely, at a fork and when sending
+or receiving messages, we take an expression from one task and
+execute it in the context of another task.  In the abstract semantics
+the fork rule
 

### 2014-02-28 paper/concrete.tex
checkpoint.

@@
 \begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+  \label{thm:iso-tsni}
   If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
@@
 \begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
+  \label{thm:iso-tini}
   If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
@@
 execute it in the context of another task.  In the abstract semantics
-the fork rule
+the fork rule is parameterized by the strategy |klone| which defines
+what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
+we have motivated two choices}, namely the identity (to effectively
+clone the heap), or to start with an empty heap.
+In the latter case, this effectively means that existing addresses
+in the forked expression |ie| are no longer valid and the
+task gets stuck (and then removed by \textsc{I-noStep}).
+\todo{}{Is this actually true?  Currently the semantics are unclear.}
+To get the isomorphic behavior in the concrete semantics with a
+single heap, we would have to change the forked expression |ie| in
+such a way that all addresses get rewritten to fresh addresses
+that are guaranteed to not occur in the global heap.  Similarly,
+sending a memory address should take a similar approach, as addresses
+for sent references will not exist in the receiving task.
+
+If |klone| is the identity function, then the abstract semantics
+effectively clone the heap on a fork.  To get an isomorphic
+behavior in the concrete, we would have to create a copy of everything
+reachable from the forked expression (not just the values for
+the memory addresses in the expression), and replace all addresses
+correspondingly.  Even worse, the behavior of sending a memory address
+now depends on whether that address existed at the time the receiving
+task was forked;  if it did, then the address should be rewritten to the
+new one, otherwise to a fresh address.
+Such a complicated behavior is contradictory to our initial motivation
+of implementing a single heap for efficiency.  But also the
+behavior of the simpler case where |klone| returns an empty heap is
+undesirable:  We rewrite addresses to fresh addresses, which will
+result in a stuck task whenever such an address is dereferenced.
+
+\subsection{Restricting the IFC Language}
+
+As a better solution we could forbid forked expressions as well
+as messages sent to other tasks to contain memory addresses in the
+first place.  In a statically typed language, the type system could
+prevent this from happening, and we talk more about how our
+approach integrates with typed languages in
+Section~\ref{sec:extensions:types}.
+In a dynamically type languages such as |targetLangML|, we might
+restrict the transition for |fork| and |send| to only allow expressions
+without memory addresses.
+
+Again we are modifying the IFC language semantics in a non-trivial way,
+which begs the question whether non-interference is preserved.
+Note that restricting the transitions in an information flow control
+system in general is not non-interference preserving as the following
+minimal example illustrates.
+Consider a trivial state machine as shown
+in Figure~\ref{fig:trivial-sm}, whose second projection is classified
+secret.  With all three transitions, this language fulfills
+termination sensitive non-interference.  Furthermore, if the
+dashed transition
+is removed, the language continues to satisfy TSNI.  However, if any
+solid line is removed, the language fails TSNI.
+
+\begin{figure}
+  States: $(x,y)$ for $x,y \in \{0,1\}$ \\
+  Erasure function: $f(x,y) = (x,\bullet)$
+
+  \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
+    \node (A) {$(1,1)$};
+    \node (B) [right of=A] {$(1,0)$};
+    \node (C) [below of=A] {$(0,1)$};
+    \node (D) [right of=C] {$(0,0)$};
+    \draw[->] (A) to node {} (B);
+    \draw[->] (C) to node {} (D);
+    \draw[->, dashed] (B) to node {} (D);
+    \end{tikzpicture}\end{center}
+
+  \label{fig:trivial-sm}
+  \caption{A trivial state machine}
+\end{figure}
+
+To remedy this issue, we give a definition that gives a condition
+under which it is safe to restrict the abstract IFC language
+|specLang alpha targetLang|, such that non-interference is preserved.
+
+\begin{definition}[Restricted IFC language]
+  \label{def:npri}
+  For a family of predicates $\mathcal P$ (one for every reduction
+  rule), we call
+  |restrictedLang alpha targetLang| a restricted IFC language
+  if its definition is equivalent to the abstract language
+  |specLang alpha targetLang|, with the following exception:
+  The reduction rules are restricted
+  by adding a predicate $P$ from $\mathcal P$ to the premise of
+  any rule other than \textsc{I-noStep}.  Furthermore, the predicate $P$
+  can depend only on the \textit{erased} configuration
+  |erase il ic|, where |il| is the label of the first task
+  in the task list and |ic| the full configuration.
+\end{definition}
+
+By the following theorem, the restricted IFC language with an
+appropriate scheduling policy is non-interfering.
+
+\begin{theorem}
+  \label{thm:restricted}
+  For any target language |targetLang| and family of predicates
+  $\mathcal{P}$, the IFC language |restrictedLang roundrobinf targetLang|
+  is TSNI.  Furthermore, the IFC language
+  |restrictedLang seqf targetLang| is TSNI.
+\end{theorem}
+
+\subsection{IFC language with a single heap}
+
+We are now ready to make our single heap IFC language precise and
+ensure its non-interference using the techniques presented.
+First, we can construct the restricted language
+|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
+the family of always valid predicates, except for the ones for
+\textsc{I-fork} and \textsc{I-send}, which we define as
+\[ P = \text{|ie| does not contain any address |ta|} \]
+Since $P$ only depends on |ie|, which is part of the current
+task and thus never erased w.r.t.\ the label of the first task,
+this language satisfies non-interference by Theorem~\ref{thm:restricted}.
+
+The essential parts of the semantics for the concrete language
+with a single heap are given in Figure~\Red{X}.  Most rules are
+straight-forward translations of the rules in Figures~\ref{fig:ifc}
+and~\ref{fig:embedding} but for a single heap.  For conciseness, we
+only show the interesting ones.
+Now, we can show an isomorphism between this language and
+|restrictedLangNoRef alpha targetLangML|, which
+(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
+non-interference for an appropriate scheduling policy |alpha|.
+
+\Red{Show the isomorphism.}
+
+\subsection{Old Stuff}
 

### 2014-02-28 paper/concrete.tex
concrete

@@
 languages by having different task execute completely isolated from
-each other, such that every task has it's own state.
+each other, such that every task has its own state.
 In some cases, this strong separation is desirable, or even necessary.
-Languages like C provide direct access to the addresses without
+Languages like C provide direct access to memory locations without
 mechanisms in the language to achieve a separation of the heap.
-However, for other languages this isolation of tasks can be
+On the other hand, for other languages this
+strong isolation of tasks can be
 undesirable, e.g., for performance reasons.
-For instance, for the mini-ML language, our presentation so far
+For instance, for the language |targetLangML|, our presentation so far
 requires a separate heap per task, which is not very practical.
@@
 we would like a single global heap as in
-|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
+\[|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|\]
 
@@
 then non-interference can be violated.  In particular, it is not
-sound to share references to a heap cell between different tasks
-in general.  Otherwise, information can be trivially leaked by copying
+sound to share references to a heap cell between different tasks.
+Otherwise, information can be trivially leaked by copying
 secret data into a reference in one task, and then
-read again by a another task with a lower label.
+reading it again by a another task with a lower label.
 Clearly, we cannot
@@
 
+\Red{We really should not use red/blue here.  I suggest we just use primes instead of colors here.}
 \begin{definition}[Isomorphism of information-flow control languages]
@@
 execute it in the context of another task.  In the abstract semantics
-the fork rule is parameterized by the strategy |klone| which defines
+the fork rule is parameterized by the strategy |klone|, which defines
 what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
@@
 Note that restricting the transitions in an information flow control
-system in general is not non-interference preserving as the following
+system in general does not preserve non-interference as the following
 minimal example illustrates.
@@
   by adding a predicate $P$ from $\mathcal P$ to the premise of
-  any rule other than \textsc{I-noStep}.  Furthermore, the predicate $P$
+  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
   can depend only on the \textit{erased} configuration
@@
 \[ P = \text{|ie| does not contain any address |ta|} \]
+That is, we do not restrict any rules except for \textsc{I-fork}
+and \textsc{I-send}.
 Since $P$ only depends on |ie|, which is part of the current
@@
 
+\begin{figure}
+
+  \begin{mathpar}
+    \inferrule[C-fork]
+    {
+      \text{|ie| does not contain any |ta|}\\
+      |iS' = iS [ id' mapsto nil ]|\\
+      |it1 = oneheapfullconf id il (iniE id')|\\
+      |itnew = oneheapfullconf id' il (TI ie)|\\
+      |fresh (id')|
+    }
+    {|
+      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
+      .->
+      iS'; tS; sched F (it1, ldots, itnew)
+    |}
+    \and
+    \inferrule[C-send]
+    {
+      \text{|ie| does not contain any |ta|}\\
+      |il canFlowTo il'|\\
+      |iS(id') = Q|\\
+      |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
+    }
+    {|
+      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
+      ->
+      iS; tS; sched step (oneheapfullconf id il unit, ldots)
+    |}
+  \end{mathpar}
+
+  \caption{A selection of the reduction rules for |concreteLangMl alpha|.}
+  \label{fig:concrete}
+\end{figure}
+
 The essential parts of the semantics for the concrete language
-with a single heap are given in Figure~\Red{X}.  Most rules are
+with a single heap,
+which we call |concreteLangMl alpha|,
+are given in Figure~\ref{fig:concrete}.  Most rules are
 straight-forward translations of the rules in Figures~\ref{fig:ifc}
@@
 
-\subsection{Old Stuff}
+\section{Proofs}
+\label{sec:proofs}
 
-In this section, we will detail an approach that allows one to implement
-a concrete system guided conceptually by the ideas in the previous
-section but making different choice for ease of implementation or
-performance, and give conditions for when such a system preserves
-non-interference.
-We first explain the idea for the single heap mini-ML language, and then
-generalize to arbitrary languages.
-
-\subsection{IFC-Mini-ML with a Single Heap}
-
-To keep up a fictional separation between the portions
-of the global heap that tasks can use, we forbid references to
-cross task boundaries.  To achieve such a system, we can
-adapt most of the operational rules easily to work with these
-new configurations.  In the abstract system, the \textsc{I-fork}
-rule created a fresh heap for the new task to execute in.  Since we
-want to forbid references to cross task boundaries, we do not modify
-the global heap and instead add an additional premise that the forked
-expression |ie| must not contain any references.
-Finally, we add the same condition to the \textsc{I-send} rule.
-Tasks that try to fork or send an expression that contains a
-reference will now get stuck, and will stop executing by the
-\textsc{I-noStep} rule.
-We call this family of languages |concreteLangMl alpha|, which
-is still parametrized by the scheduling policy |alpha|.
-
-\Red{Show the key rules here.}
-
-In |concreteLangMl alpha| we
-effectively restrict the abstract semantics in some cases (namely
-to not allow the passing of references) as well as using a different
-way to represent the heap.  How can we be sure that these
-new, \textit{concrete semantics} for our system still satisfy
-non-interference?
-
-We will use two techniques to ensure non-interference.  First,
-we require some form of isomorphism to the abstract language
-|specLangML alpha| that ensures that the concrete system behaves
-in a similar way.  Secondly, we pose conditions on what kind
-of restrictions the concrete language is allowed to make
-on the abstract language.
-
-Intuitively, there are two scenarios in which non-interference
-can be violated when restricting the transition relation:
-\begin{itemize}
-  \item Adding an additional premise to one of the rules that inspects
-  information which is above the security label of the task currently
-  executing.  This would allow another task to observe the termination
-  of the other if both are at the same security level, and thus observe
-  the secret information that was used in the additional
-  premise of the rule.
-  \item Adding additional restrictions to transition rules can
-  also cause the whole configuration to get stuck, which can leak
-  information through the termination channel (which is only
-  of interest for TSNI, but not TINI, of course).
-\end{itemize}
-
-Next, we will make these two intuitions precise and give a general
-definition for how non-interference can be preserved.  Then, we
-show that the language |concreteLangMl alpha| satisfies these
-conditions.
-
-\Red{Should we give an example why removing transitions in general
-  is not OK?  Edward has already typeset one that we could
-  use.}
-
-%This isn't trivial, as it is not sound to add arbitrary additional
-%conditions on evaluation rules.  To see this, consider a contrived
-%concrete system where we add a premise to a reduction rule that
-%stops a task based on secret information.  Such a system will
-%not satisfy non-interference, as it allows other tasks on the
-%same level to observe the termination of that task and thus the
-%secret information which was used to decide if the task terminates
-%or not.
-
-\subsection{Correctness of Concrete Semantics}
-
-To formalize the conditions under which we can show the concrete
-semantics preserve non-interference, we require some notation:
-
-\begin{definition}[Isomorphism of information-flow control languages]
-  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
-  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
-  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
-  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
-  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
-  $l$-equivalences and |.->|.
-\end{definition}
-
-\Red{In some cases, this restriction can be weakened, where |finv| does
-not have to be functorial over |.->|}
-
-Now, we can propose the following two-step process to ensure that
-non-interference is preserved:
-\Red{We should find a better name for this, or not use a name, or something.}
-\begin{definition}[Non-interference preserving, restricted isomorphism (NPRI)]
-  \label{def:npri}
-  We call an IFC language
-  |concreteLang alpha targetLang| (the concrete language for a given
-  target language |targetLang| and scheduling policy |alpha|)
-  a \textit{non-intereference preserving,
-  restricted isomorphism} with regard to the IFC language
-  |specLang alpha targetLang|
-  (the abstract language) if the following
-  two conditions hold:
-  \begin{enumerate}
-    \item Any of the reduction rules of the abstract
-    semantics |specLang alpha targetLang|
-    presented in Section~\ref{sec:retrofit} can
-    be restricted by adding a predicate $P$ to the premise of
-    any rule other than \textsc{I-noStep}.  The predicate $P$
-    can depend only on the \textit{erased} configuration
-    |erase il ic|, where |il| is the label of the first task
-    in the task list and |ic| the full configuration.
-    \item The concrete language
-    |concreteLang alpha targetLang|
-    must be isomorphic to the abstract semantics |specLang alpha targetLang|
-    with the additional predicates $P$ on the rules.
-  \end{enumerate}
-\end{definition}
-
-\begin{theorem}[NPRI implies non-interference]
-  \label{thm:npri}
-  If a language |concreteLang alpha targetLang| is a NPRI, and |alpha|
-  is a scheduling policy that makes |specLang alpha targetLang| satisfy
-  TINI or TSNI, then also
-  |concreteLang alpha targetLang| satisfies TINI, or TSNI, respectively.
-\end{theorem}
-
-Before we give the proof of this theorem in Section~\ref{sec:proofs},
-let's consider our single-heap ML-like IFC language and
-show that it is in fact NPRI, and thus non-interfering.
-
-\begin{theorem}
-  The language |concreteLangMl alpha| is a NPRI.
-\end{theorem}
-As a trivial corollary, it follows that |concreteLangMl roundrobinf| is
-TSNI, and |concreteLangMl seqf| is TINI.
-
-\begin{proof}
-  It is easy to see that condition (1) of NPRI is satisfied, since
-  we only add a side condition to the rules \textsc{I-fork} and
-  \textsc{I-send}, and the condition only inspects the expression
-  of the current task, which is by the definition of |erasef il| not
-  erased.
-
-  This leaves us to give an isomorphism between |concreteLangMl alpha|
-  and |concreteLang alpha targetLangMl|, which we do as follows.
-  \Red{Actually give an isomorphism.}
-\end{proof}
-
-\subsection{Proof of Theorem~\ref{thm:npri}}
-\label{sec:proofs}
+\Red{Adapt some of this text.}
 
@@
 \end{proof}
-
-\subsection{\Red{Previous Stuff (to be merged/removed as necessary)}}
-
-However, modifying operational rules poses a distinct problem for
-preserving non-interference.  Consider a trivial state machine as shown
-in Figure~\ref{fig:trivial-sm}, whose second projection is classified
-secret.  With all three transitions, this language fulfills
-termination-sensitive noninterference.  Furthermore, if the dashed line
-is removed, the language continues to satisfy TSNI.  However, if any
-solid line is removed, however, the language fails TSNI.
-
-\begin{figure}
-    States: $(x,y)$ for $x,y \in \{0,1\}$ \\
-    Erasure function: $f(x,y) = (x,\bullet)$
-
-    \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
-        \node (A) {$(1,1)$};
-        \node (B) [right of=A] {$(1,0)$};
-        \node (C) [below of=A] {$(0,1)$};
-        \node (D) [right of=C] {$(0,0)$};
-        \draw[->] (A) to node {} (B);
-        \draw[->] (C) to node {} (D);
-        \draw[->, dashed] (B) to node {} (D);
-    \end{tikzpicture}\end{center}
-
-    \label{fig:trivial-sm}
-    \caption{A trivial state machine}
-\end{figure}
-
-Before we show isomorphism preserves termination sensitive
-non-interference, we'd like to remark that one can safely remove transitions
-and preserve termination \emph{insensitive} interference:
-
-\begin{figure}
-
-\begin{mathpar}
-\inferrule[I-stepT]
-{|
-conf tS (te) -> conf tS' te'
-|}
-{|
-coconf iS tS (cconf id il (iniE (IT te)), ldots)
-.->
-iS ; tS' ; sched step (cconf id il (iniE (IT te')), ldots)
-|}
-
-\and
-% This rule is not complete, needs the FV condition
-\inferrule[C-fork]
-{ 
-|iS' = iS [ id' mapsto nil ]|\\
-|it1 = cconf id il (iniE id')|\\
-|itnew = cconf id' il (TI ie)|\\
-|fresh (id')|
-}
-{|
-coconf iS tS (lconf id il (iniE (fork ie)), ldots)
-.->
-iS'; tS; sched fork (it1, ldots, itnew)
-|}
-\end{mathpar}
-
-\caption{ML with a single heap}
-\label{fig:comb}
-\end{figure}

### 2014-02-28 paper/real.tex

@@
 \label{sec:real}
+
+In this section we consider the application of our embedding to 
+real world target languages.
+%
+To illustrate the flexibility of our system and challenges in the
+embedding we chose three mainstream languages---C, Haskell, and
+JavaScript---that have vastly different features and properties.
+%
+We remark that we have implemented variants of our Haskell and
+JavaScript embeddings, which are used in the Hails~\tocite{} and
+SWAPI~\tocite{} systems; we leave the implementation of the IFC system
+for C, as describe below, to future work.
+
+\subsection{C}
+\label{sec:real:c}
+
+\subsection{Haskell}
+\label{sec:real:hs}
+While the C embedding closely resembles the specification language of
+Section~\ref{sec:retrofit}, in our Haskell IFC embedding we leverage
+Haskell's strong data abstraction and static type system, monadic
+approach to effects, and lightweight concurrency to implement the
+embedding in a more efficient manner, as library.
+
+To this end, we define a new monad, |LIO|, that wraps Haskell's |IO|
+monad---which allows for arbitrary effects---to associate labels with
+threads (tasks) and restrict computational effects according to the
+semantics of Section~\ref{sec:retrofit}.
+%
+The precise restrictions encode our IFC system as computations in the
+|LIO| monad.
+%
+By wrapping |IO|, we can use Haskell's efficient implementation of
+threads, channels, etc. (e.g., we use Haskell's \texttt{forkIO} to
+fork a lightweight thread in the case of |fork|), in contrast to
+defining them in a pure fashion (see Section~\ref{sec:monad}).
+
+Importantly, this concrete implementation approach also directly
+corresponds to the specification language.
+%
+Specifically, it is |specLang alpha targetLangHS|, for $|alpha| \in
+|{roundrobinf, seqf}|$, with the pure subset of Haskell as to target
+language |targetLangHS|, the subset of Haskell that additionally
+contains the |LIO| monad (and corresponding |LIO| computations
+encoding the language) as the IFC language.
+%
+Of course since our IFC system is implemented as a library in Haskell,
+we must ensure that these languages are indeed the subsets of Haskell
+we claim, i.e., while the concrete language is all of Haskell, we must
+ensure that we can restrict programs to our subset of Haskell that
+encodes the combined language.
+%
+
+To this end, we rely Haskell's strong data abstraction and type system
+(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
+ensure that arbitrary |IO| actions cannot be lifted into
+|LIO|.\footnote{
+Of course, our IFC guarantees only extend insofar as the program is
+written as a computation in the |LIO| monad; a program written
+directly in the |IO| monad can trivially violate information flow
+control.
+}
+%
+In other words, assuming |LIO| is implemented correctly, programs
+written in the |LIO| monad cannot perform arbitrary |IO| actions
+without breaking abstraction.
+
+We refer the interested reader to~\tocite{icfp,haskellsymp} for
+additional details on the various implementations of this system.
+%
+Finally, we remark that in this work unifies these systems and
+presents in addition to proving NI fo such systems with asynchronous
+communication primitives.
+
+\subsection{JavaScript}
+\label{sec:real:js}
+
 \cut{

### 2014-02-28 paper/retrofit.tex
Examples
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
-mutable references \Red{and errors}, prepared for combination with an
+mutable references and errors, prepared for combination with an
 information flow control language.  The presentation is standard, but it
@@
 \begin{code}
-tv   ::= \tx.te | true | false | ta
-te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
+tv   ::= \tx.te | true | false | ta | unit
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fail
 tE   ::= tHole | tE te | tv tE | if tE then te else te
@@
 { }
-{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}
+{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) unit |}
+
+\and
+\inferrule[T-fail]
+{ }
+{| conf tS ( tE [ fail ] ) -> conf tS fail |}
 \end{mathpar}
@@
 with data, which encodes a policy of whether or not data tagged with one
-label can flow to |canflowto| another label.  Since our embedding is agnostic
+label can flow to |canFlowTo| another label.  Since our embedding is agnostic
 to the choice of labeling scheme, we simply represent labels with the metavariable
@@
     \item First-class labels, with label values $l$ as well as operations for computing on
-labels (|canflowto|, |lub| and |glb|),
-    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the thread (note a thread can only increase its label, and not decrease it),
+labels (|canFlowTo|, |lub| and |glb|),
+    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the thread (a thread can only increase its label, and not decrease it),
     \item Operations for non-blocking inter-thread communication (\textbf{send} and \textbf{recv}),
@@
 
+\subsection{The embedding}
+
 Finally, in Figure~\ref{fig:embedding},
-we provide all of the rules responsible for actually carrying out the embedding:
-
-\begin{itemize}
-    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-\Red{For now, we defer discussion on how these boundaries mediate between the type systems of the two languages.}
-    \item We reinterpret |CE| to be evaluation contexts on threadpools.  By assumption, only the first thread in the threadpool executes.
-    \item We define |->|, operation on a single thread, in terms of |.->|, operation on thread pools.
-The correspondence is simple: a thread executes a step, and then is rescheduled in the thread pool according to schedule policy $\alpha$.
-\Red{More on schedule policies later}
-    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
-\Red{As written, these rules will not preserve type-safety of the underyling language, but it is easy to adjust them to ensure they do so.}
-\end{itemize}
-
-The fork rule is of particular interest; it is defined in terms of a function $\kappa$.
-Conservatively, $\kappa$ may be simply thought of as the identity function, in which
-case the semantics of fork are such that the state of the target language is \emph{cloned}
-when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
-to remove entries from the state.  \Red{For more information about when this is not the
-fork semantics you want, see the concrete implementation section.}
+we provide all of the rules responsible for actually carrying out the embedding.
+The most important feature of this embedding is that every thread maintains its own
+copy of the target language global state and evaluation context, thus
+enforcing isolation between various threads.  In more detail:
 
@@
 \begin{code}
-ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
+ix1, ix2 <= brecv . ie @=
+tab tab tab IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
 conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
@@
 
-\Red{When both languages have booleans, it is relatively simple to define
-a natural embedding which preserves booleans across boundaries.}
-\begin{mathpar}
-\inferrule[I-bool]
-{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-\and
-\inferrule[T-bool]
-{ |b member {true, false}| } {| intE (TI b) -> intE b |}
-\end{mathpar}
-
 \begin{figure}
@@
 \caption{Scheduling policies}
+\label{fig:schedule}
 \end{figure}
 
-\subsection{Generalizing further}
-
 \begin{itemize}
-\item Label transition systems.
-\item Non-deterministic reduction.
-\item Arbitrary scheduling policies $\alpha$
+    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
+    \item We reinterpret |CE| to be evaluation contexts on threadpools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.
+These rules only operate on the first thread in the threadpool, which by convention, is the only thread executing.
+    \item We reinterpret |->|, an operation on a single thread, in terms of |.->|, operation on thread pools.
+The correspondence is simple: a thread executes a step and then is rescheduled in the thread pool according to schedule policy $\alpha$.
+Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:schedule}.
+    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
 \end{itemize}
 
+The \textsc{I-fork} rule is of particular interest, as it is intended to allow users
+to create new threads.  When a new thread is created, there is a question of what the
+global state of the new thread should be; this is defined in terms of a function $\kappa$.
+Conservatively, $\kappa$ may be simply thought of as the identity function, in which
+case the semantics of fork are such that the state of the target language is \emph{cloned}
+when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
+to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
+discussion of the implications of the choice of $\kappa$.
+
+\subsection{Examples}
+
+To get a feeling for how these operational semantics operate, we'd like to
+describe a few sample programs, and what their outputs are.
+
+\paragraph{Sending mutable references}  As each thread maintains its own
+global state for the target language, one might reasonably wonder what would
+happen if you attempted to send a reference to another thread.
+
+\begin{align*}
+    & |let i = TI (fork (x, i' <= brecv . (IT (!(TI x)))))| \\
+    & |in TI (send (IT (ref true)))|
+\end{align*}
+
+It would be a violation of information flow if such an operation actually
+resulted in references being shared between two threads.  In fact, the address
+will be received by the forked thread, but it will be a dangling pointer; the
+thread will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
+who are curious whether or not a static discipline could be enforced to
+prevent these dangling pointers should check Section~\ref{sec:extensions}.)
+
+\paragraph{Status of the heap after a fork}  Here is a program whose
+semantics depends on the definition of $\kappa$:
+
+\begin{align*}
+    & |let x = ref true| \\
+    & |in TI (fork (IT (!x; !x))); x := false|
+\end{align*}
+
+When $\kappa$ is the identity, the forked thread successfully dereferences
+the contents of the reference to be true twice (recall that references
+are cloned into the new global state).  When $\kappa$ is the constant function
+to the empty store, $x$ becomes a dangling pionter.
+
+\paragraph{Exceptions}  One language feature that has caused difficulty
+for many information flow control systems is handling
+exceptions.~\cite{Hritcu:2013:YIB:2497621.2498098}  The key difficulty
+appears when an exception must cross a stack boundary where the current
+label reverts back, i.e. across a \textbf{toLabeled} operator.~\cite{lio}
+If the exception crosses this boundary, it can leak information about the
+inner sensitive computation.
+
+At first glance, it does not appear that our system has any such operator;
+there are only threads, and the correct behavior for a thread throwing
+an exception is self-evident: it should simply be removed from the scheduler.
+However, under a \emph{sequential scheduler}, the behavior of \textbf{fork}
+can be used to model the behavior of \textbf{toLabeled}:
+
+\begin{align*}
+    & |toLabeled l te @= | \\
+    & |tab let pid = threadId; | \\
+    & |tab let i = TI (fork (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
+    & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
+\end{align*}
+
+When the sequential scheduler is used, the forked thread runs to
+completion before returning to the thread that forked it.  Thus,
+a threadpool should rather be interpreted as a number of information-flow
+aware stack frames.  To read the result of a |toLabeled| operation
+(which is communicated via message passing), the parent thread must raise
+its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-thread
+channel, we might mix up our messages.  Indeed, a proper development requires
+the ability to allocate fresh channels; for purposes of simplicity, this
+has been omitted.}
+
+%   \Red{When both languages have booleans, it is relatively simple to define
+%   a natural embedding which preserves booleans across boundaries.}
+%   \begin{mathpar}
+%   \inferrule[I-bool]
+%   { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
+%   \and
+%   \inferrule[T-bool]
+%   { |b member {true, false}| } {| intE (TI b) -> intE b |}
+%   \end{mathpar}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-02-28 paper/formal.tex
one scheduler; rule D is back, rm from formal;

@@
 
-\begin{figure}
-  Round robin:
-\begin{code}
-  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
-  roundrobin N (it1, it2, ldots)     = it2, ldots
-  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
-\end{code}
-  Sequential:
-\begin{code}
-  seq step (it1, it2, ldots)     = it1, it2, ldots
-  seq N (it1, it2, ldots)        = it1, it2, ldots
-  seq N (it)                     = it
-  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
-\end{code}
-\caption{Round robin and sequential scheduling policies.\label{fig:scheduler}}
-\end{figure}
-
 Directly, we now show that our IFC language satisfies TSNI under a particular

### 2014-02-28 paper/retrofit.tex
Fixup.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
one scheduler; rule D is back, rm from formal;

@@
 \caption{Scheduling policies}
-\label{fig:schedule}
+\label{fig:scheduler}
 \end{figure}
@@
 The correspondence is simple: a thread executes a step and then is rescheduled in the thread pool according to schedule policy $\alpha$.
-Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:schedule}.
+Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
     \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
@@
 
+In this setting, it is also clear that exceptions should not cross boundaries,
+as seen in |toLabeled l fail; true|, which evaluates to |true| no matter even in
+the event of an exception inside of the |toLabeled| block:
+
 %   \Red{When both languages have booleans, it is relatively simple to define

### 2014-02-28 paper/retrofit.tex
todos for me

@@
 
+\Red{TODO[ds]:
+  - move the async recv to text and out of the figure
+  - clarify discussion on exceptions
+  - fix the toLabled
+  - add threadId to ruls
+}
 Finally, in Figure~\ref{fig:embedding},
@@
 ix1, ix2 <= brecv . ie @=
-tab tab tab IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
+tab tab tab (IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx))
 conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)

### 2014-02-28 paper/concrete.tex
Update proof section.

@@
 \begin{definition}[Restricted IFC language]
-  \label{def:npri}
+  \label{def:restricted}
   For a family of predicates $\mathcal P$ (one for every reduction
@@
 
-\Red{Adapt some of this text.}
+In this section we will prove all theorems we have stated so far.
+We observe that the non-interference claims for the languages
+|specLang seqf targetLang| and |specLang roundrobin targetLang|
+in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
+from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
+respectively, about restricted IFC languages where the set
+of predicates is the set of always valid predicates.
 
-Before we give the actual proof, we state and proof some properties
-of isomorphisms.
-
-\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
-  If a language \con{L} is included in a language \abs{L}, and \abs{L}
-  satisfies TINI, then \con{L} satisfies TINI.
-\end{theorem}
-
-\begin{proof}
-  Shown by transporting configurations and reduction derivations
-  from \con{L} to \abs{L}, applying TINI and transporting the resulting
-  equivalence back using functoriality of |finv| over $l$-equivalences.
-\end{proof}
-
-\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
-  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
-  \tar{L} satisfies TSNI.
-\end{theorem}
-
-\begin{proof}
-  Shown by transporting configurations and reduction derivations from
-  \tar{L} to \ifc{L}, applying TSNI, and then transporting the
-  resulting configuration, $l$-equivalence and multi-step derivation back.
-\end{proof}
-
-For the proof of Theorem~\ref{thm:npri}, we first show that the
-abstract language, potentially augmented with predicates as described
-in the first point of Definition~\ref{def:npri}, satisfies
-non-interference.  Combining this result with the isomorphism theorems
-will prove the goal as desired.
-
-\begin{theorem}
-  \label{thm:rr-tsni-general}
-  For any target language |targetLang|,
-  the language |specLang roundrobinf targetLang| where predicates $P$
-  have potentially been added to the reduction rules as described in
-  Definition~\ref{def:npri} satisfies TSNI.
-\end{theorem}
-
-Theorem~\ref{thm:rr-tsni} is a simple consequence of this
-(for the case where without any additional predicates).
-Before we proceed with the proof of this theorem, we state a
-lemma we will use.
+Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
+we state a lemma we will use.
 
@@
   We consider, for any target language |targetLang|,
-  the information-flow control
-  language |specLang roundrobinf targetLang| where a predicate $P$
-  has potentially been added to the reduction rules as described in
-  Definition~\ref{def:npri}.  Then,
+  the restricted IFC language |restrictedLang alpha targetLang|
+  (according to Definition~\ref{def:restricted}).
+  Then,
   for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
@@
 
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
   We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
@@
 \end{proof}
+
+The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
+in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
+some cases are simpler due to the fact termination is not an issue
+(cf.~\tocite{} for a TINI proof of a similar system).

### 2014-02-28 paper/formal.tex
Update proof section.

@@
 \begin{theorem}[Sequential specification language is TINI]
+  \label{thm:seq-tini}
 For any target language |targetLang nop|, |specLang seqf (targetLang

### 2014-02-28 paper/real.tex
wip

@@
 %
-Finally, we remark that in this work unifies these systems and
-presents in addition to proving NI fo such systems with asynchronous
+Here, we lastly remark that our work unifies these systems and
+presents a proof of NI for such systems with asynchronous
 communication primitives.
@@
 \label{sec:real:js}
+
+JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
+built-in functionality for I/O.
+%
+Consequently, and in contrast to our C and Haskell embeddings, for
+which we must eliminate external effects, the embedding for JS is
+trivial.
+%
+Hence, as a first step, we implement the IFC language functionality in the
+JS runtime and expose the new functions, e.g., |fork|, by attaching
+them to the JS global object.
+%
+Importantly, each task runs a separate instances of this runtime.
+
+Indeed this coarse-grained approach is already used by browsers in the
+Worker API~\tocite{}, which provides client-side JS with primitives
+for executing code in a separate thread, called a Worker.
+%
+Each Worker has a separate runtime with a fresh global object.
+%
+In turn, exchanging information between runtimes is accomplished with
+message-passing, i.e., \texttt{postMessage}.
+%
+The message-passing approach is, in part, due to ECMAScript's lack
+of well-defined semantics for concurrency.
+%
+Hence sharing and accessing objects such as the DOM across threads is
+undefined.
+%
+
+Hence, our implementation provides
+
+\begin{itemize}
+\item not completely unrealist; workers provide a similar world; we
+  provide labeled workers
+
+\item actual embeddings of JS have external effects; consider the browser
+  case as in SWAPI
+\begin{itemize}
+   \item associate label with browsing context ~ task
+   \item use CSP and sandbox flags to control external effects
+   \item mediate communication by interposing on on postMessage
+   argue that browsers already have to provide isolation guarantees
+   between different compartments
+\end{itemize}
+
+\item talk about SWAPI's attach object feature that makes the concrete
+  implementation more interesting
+\end{itemize}
+
+Of course, applications, such as browsers, that embed JavaScript
+expose various features that perform external effects (again by
+attaching them as objects to the JS global object).
+%
 

### 2014-02-28 paper/retrofit.tex
Minor changes to retrofit.

@@
 { }
-{| conf tS (!ta) -> conf tS (ap ts ta) |}
+{| conf tS (!ta) -> conf tS (ap tS ta) |}
 
@@
 Information flow control seeks to enforce a security policy known as
-\emph{noninterference}: public results must not depend on secret inputs.
+\emph{non-interference}: public results must not depend on secret inputs.
 Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
 with data, which encodes a policy of whether or not data tagged with one
-label can flow to |canFlowTo| another label.  Since our embedding is agnostic
+label can flow to another label (written as |canFlowTo|).
+Since our embedding is agnostic
 to the choice of labeling scheme, we simply represent labels with the metavariable
@@
 evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
-of the current thread which is running, including on the right-hand side
-the current label $l$ (which protects the program counter of the thread)
-and the thread ID $i$.
+of the current task which is running, including on the right-hand side
+the current label $l$ (which protects the program counter of the task)
+and the task ID $i$.
 
@@
 labels (|canFlowTo|, |lub| and |glb|),
-    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the thread (a thread can only increase its label, and not decrease it),
-    \item Operations for non-blocking inter-thread communication (\textbf{send} and \textbf{recv}),
-        which interact with the global store of per-thread message queues |iS|, and
-    \item A forking operation, which will be described in more detail in the next section.
+    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
+    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
+        which interact with the global store of per-task message queues |iS|, and
+    \item a forking operation allowing to spawn new tasks, which will be described in more detail in the next section.
 \end{itemize}
 
-The form of \textbf{send}/\textbf{recv} are inspired by methods of inter-worker communication
-in web browser APIs \Red{cite}, however in Section~\ref{sec:extensions} we
+The form of \textbf{send}/\textbf{recv} are \Red{inspired by methods of inter-worker communication
+in web browser APIs} \Red{cite}, however in Section~\ref{sec:extensions} we
 discuss other possible choices for information flow control aware communication
-primitives.  Their rules are non-standard and worth commenting on: when a thread places
-a message on the message queue of the thread it is sending to, it also adds the current
-label when it sent the message.  When the recipient reads out messages from its queue,
-it filters out (notated using |filter il Q|) messages whose labels do not
-flow to |il|. Specifically, if |Q| is the empty list |nil|, the
+primitives.  Their rules are different from non-IFC systems
+and worth commenting on: when a task places
+a message on the message queue of receiving task, it also labels that
+message with a label |il'| (which must be above the tasks current label |il|)
+When the recipient reads out messages from its queue,
+messages whose labels do not
+flow to |il| are filtered out (denoted by |filter il Q|).
+Specifically, if |Q| is the empty list |nil|, the
 function is simply the identity function, i.e.,
@@
 \]
+This ensures that tasks cannot receive messages that are more secret
+than their current label would allow.
 
@@
 \end{mathpar}
-\caption{IFC language, single-thread operations}
+\caption{IFC language with all single-threaded operations}
 \label{fig:ifc}
@@
   - fix the toLabled
-  - add threadId to ruls
+  - add taskIDs to ruls
 }
@@
 we provide all of the rules responsible for actually carrying out the embedding.
-The most important feature of this embedding is that every thread maintains its own
+The most important feature of this embedding is that every task maintains its own
 copy of the target language global state and evaluation context, thus
-enforcing isolation between various threads.  In more detail:
+enforcing isolation between various tasks.  In more detail:
 
@@
     \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-    \item We reinterpret |CE| to be evaluation contexts on threadpools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.
-These rules only operate on the first thread in the threadpool, which by convention, is the only thread executing.
-    \item We reinterpret |->|, an operation on a single thread, in terms of |.->|, operation on thread pools.
-The correspondence is simple: a thread executes a step and then is rescheduled in the thread pool according to schedule policy $\alpha$.
+    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.
+These rules only operate on the first task in the task pool, which by convention, is the only task executing.
+    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.
+The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.
 Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
-    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
+    \item Finally, we define some rules for scheduling, handling forking tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
 \end{itemize}
@@
 The \textsc{I-fork} rule is of particular interest, as it is intended to allow users
-to create new threads.  When a new thread is created, there is a question of what the
-global state of the new thread should be; this is defined in terms of a function $\kappa$.
+to create new tasks.  When a new task is created, there is a question of what the
+global state of the new task should be; this is defined in terms of a function $\kappa$.
 Conservatively, $\kappa$ may be simply thought of as the identity function, in which
@@
 
-\paragraph{Sending mutable references}  As each thread maintains its own
+\paragraph{Sending mutable references}  As each task maintains its own
 global state for the target language, one might reasonably wonder what would
-happen if you attempted to send a reference to another thread.
+happen if you attempted to send a reference to another task.
 
@@
 It would be a violation of information flow if such an operation actually
-resulted in references being shared between two threads.  In fact, the address
-will be received by the forked thread, but it will be a dangling pointer; the
-thread will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
+resulted in references being shared between two tasks.  In fact, the address
+will be received by the forked task, but it will be a dangling pointer; the
+task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
 who are curious whether or not a static discipline could be enforced to
@@
 
-When $\kappa$ is the identity, the forked thread successfully dereferences
+When $\kappa$ is the identity, the forked task successfully dereferences
 the contents of the reference to be true twice (recall that references
@@
 At first glance, it does not appear that our system has any such operator;
-there are only threads, and the correct behavior for a thread throwing
+there are only tasks, and the correct behavior for a task throwing
 an exception is self-evident: it should simply be removed from the scheduler.
@@
     & |toLabeled l te @= | \\
-    & |tab let pid = threadId; | \\
+    & |tab let pid = taskId; | \\
     & |tab let i = TI (fork (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
@@
 
-When the sequential scheduler is used, the forked thread runs to
-completion before returning to the thread that forked it.  Thus,
-a threadpool should rather be interpreted as a number of information-flow
+When the sequential scheduler is used, the forked task runs to
+completion before returning to the task that forked it.  Thus,
+a task pool should rather be interpreted as a number of information-flow
 aware stack frames.  To read the result of a |toLabeled| operation
-(which is communicated via message passing), the parent thread must raise
-its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-thread
+(which is communicated via message passing), the parent task must raise
+its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
 channel, we might mix up our messages.  Indeed, a proper development requires

### 2014-02-28 paper/formal.tex

@@
 %
-Concretely, we show that an IFC langauge, |specLang alpha (targetLang
-nop)|, satisfies non-interference(NI)~\tocite{}.
+Concretely, we show that an IFC langauge, |specLang alpha targetLang)|, satisfies non-interference~\tocite{}, without making any reference to properties of |targetLang|.
 %
-Intuitively, non-interference states that secret values cannot be
-leaked by programs written in the language.
+As it turns out, the precise scheduling policy |alpha| dictates
+whether or not the guarantee holds for programs with diverging tasks.
+For a sequential scheduler, we will only be able to show
+\emph{termination-insensitive non-interference}, where a program
+may diverge based on secret data; with the concurrent schedule,
+we can show a stronger result, \emph{termination-sensitive non-interference},
+where termination attacks cannot leak information.
+
+How does one characterize what the \emph{secret inputs} of a program
+are?  Like other work,~\tocite{} we show specify and prove
+noninterference using \emph{term erasure}.
 %
-As we show below, the precise scheduling policy |alpha| dictates
-whether or not the guarantee holds for programs with diverging tasks.
-
-We prove non-interference for |specLang alpha (targetLang nop)| using
-the \emph{term erasure} technique of~\tocite{}.
-%
-Intuitively the term erasure technique allows us to show that a an
+Intuitively, term erasure allows us to show that a an
 attacker does not learn any sensitive information from a program
-written in a NI language, if the program behaves identically to the
+written in a non-interference language, if the program behaves identically to the
 same program with all sensitive data ``erased.''
@@
 %
-Directly, we can now give a precise definition for the kinds of
-languages we wish to prove NI.
+We can generally characterize what features a language must have
+in order for the statement of non-interference to be well-posed:
 
@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
+In our case, |specLang alpha (targetLang nop) = (ifc C, ifc
 V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
-$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
+$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
 type for tasks whose expressions have been reduced to
@@
 %
-This precise NI property is called termination sensitive non-interference
+This precise non-interference property is called termination sensitive non-interference
 (TSNI), since it considers runs of programs, and thus does not allow for leaks
@@
 
-\begin{theorem}[Concurrent specification language is TSNI].
+\begin{theorem}[Concurrent specification language is TSNI]
   \label{thm:rr-tsni}
@@
 %
-Hence, we consider an alternative NI property---called termination insensitive
+Hence, we consider an alternative non-interference property---called termination insensitive
 non-interference---that can also be upheld by sequential languages at the cost

### 2014-02-28 paper/formal.tex
More small fixes.

@@
 %
-Concretely, we show that an IFC langauge, |specLang alpha targetLang)|, satisfies non-interference~\tocite{}, without making any reference to properties of |targetLang|.
+Concretely, we show that |specLang alpha targetLang| for an appropriate
+scheduler, satisfies non-interference~\tocite{},
+without making any reference to properties of |targetLang|.
 %
@@
 \emph{termination-insensitive non-interference}, where a program
-may diverge based on secret data; with the concurrent schedule,
-we can show a stronger result, \emph{termination-sensitive non-interference},
+may diverge based on secret data; this allows attackers to observe
+secrets by observing the termination of tasks.
+For the concurrent round-robin schedule,
+we can show a stronger result known as
+\emph{termination-sensitive non-interference},
 where termination attacks cannot leak information.

### 2014-02-28 paper/concrete.tex

@@
 reading it again by a another task with a lower label.
-Clearly, we cannot
-modify the semantics in arbitrary ways if we are hoping to preserve
-non-interference, but how can we know if our changes to the abstract
-semantics preserve non-interference?
+What we would like is a way of characterizing safe modifications to
+the semantics which preserve non-interference.
 The intention of our single heap implementation was to be more efficient
@@
 
-\Red{We really should not use red/blue here.  I suggest we just use primes instead of colors here.}
+% con no-prime red target
+% abs prime blue ifc
+
 \begin{definition}[Isomorphism of information-flow control languages]
-  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
-  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
-  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
-  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
-  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
+  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
+  language |(C', tarrow', erasefp l)| if there exist total functions |f
+  : C -> C'| and |finv : C' -> C'| such that |f .. finv = idf C| |finv
+  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
+  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
   $l$-equivalences and |.->|.
@@
   not have to be functorial over |.->|, we call the
-  language \con{|(C, .->, erasef l)|} \textit{weakly isomorphic} to
-  \abs{|(iC, .->, erasef l)|}.
+  language |(C, .->, erasef l)| \textit{weakly isomorphic} to
+  |(C', tarrow', erasefp l)|.
 \end{definition}

### 2014-03-01 paper/formal.tex
notational changes, improvements to erasure, etc.

@@
 
-How does one characterize what the \emph{secret inputs} of a program
-are?  Like other work,~\tocite{} we show specify and prove
-noninterference using \emph{term erasure}.
+How can we characterize what the \emph{secret inputs} of a program
+are?  Like other work,~\tocite{} we specify and prove
+non-interference using \emph{term erasure}.
 %
+Intuitively, in this approach we proving that an attacker does not learn
+any sensitive information from a program by 
 Intuitively, term erasure allows us to show that a an
-attacker does not learn any sensitive information from a program
-written in a non-interference language, if the program behaves identically to the
-same program with all sensitive data ``erased.''
+attacker does not learn any sensitive information from a program if the
+program behaves identically to a program with all sensitive data ``erased''.
 %
 To accommodate for this, we extend our formalism to account for
-programs with erased configurations and a function |erasef l| that
+programs with erased configurations and a function |erasef il| that
 performs erasures, usually by rewriting (parts of) configurations that
-are more sensitive than |l| to a new syntactic construct |bullet|.
+are more sensitive than |il| to a new syntactic construct |bullet|.
 %
-We can generally characterize what features a language must have
-in order for the statement of non-interference to be well-posed:
+We can characterize the types of languages for which one can state
+a non-interference claim.
 
-\begin{definition}[Information-flow control language]
-    An information-flow control language |L| is a tuple |(C, .->,
-    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
+\begin{definition}[Information flow control language]
+    An information flow control language |L| is a tuple |(C, .->,
+    erasef l)|, where $|C|$ is the type of machine configurations (members
+    of which are usually denoted by the meta-variable |c|), |.->| is a
     reduction relation between machine configurations and |erasef l : C -> tyerase C|
     is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  For sequential languages, the
-    language is augmented with a set of terminal configuration states $V
+    configurations |tyerase C|.  This tuple is sometimes
+    augmented with a set of terminal configuration states $V
     \subseteq |C|$ for which there are no possible further transitions.
@@
 containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
-our erasure function.
+our erasure function |erasef il|.
 %
@@
     |bullet| & |il' cantFlowTo il| \\
-    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
+    |fullconf id il' tS ie| & \text{otherwise}
   \end{cases} \\
@@
     In a language |(C, .->, erasef l)|, two machine configurations
-    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
-    if |erase l c = erase l c'|.
+    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
+    if |erase l c = erase il c'|.
 \end{definition}
@@
 
-Directly, we now show that our IFC language satisfies TSNI under a particular
+We now show that our IFC language satisfies TSNI under a particular
 scheduling policy.
@@
 %
-For example, |specLang alpha (targetLang nop)| with a scheduler that inspects a
+For example, |specLang alpha targetLang| with a scheduler that inspects a
 sensitive threads current state when deciding which thread to schedule next
@@
 %
-It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
+It is easy to show that |specLang seqf targetLang| does not satisfy
 TSNI.
 %
-Concretely, consider a target language similar to |targetLang ML| with an
+Concretely, consider a target language similar to |targetLangML| with an
 additional expression terminal |diverge| that denotes a divergent computation,
-i.e., |diverge| always reduces to |diverge| and a a simple label lattice |{pub,
-sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|, we can write the
+i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
+sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.  We can write the
 following program in the specification language:
@@
 feature is straight forward, see Setion~\ref{}.
-} then the |sec| thread's decision to diverge or not is directly leaked to a
+} then the |sec| tasks's decision to diverge or not is directly leaked to a
 public entitiy.
@@
 %
-\begin{definition}[Termination Insensitive Non-Interference (TINI)]
+\begin{definition}[Termination insensitive non-interference (TINI)]
   A language |(C, V, .->, erasef l)| is termination

### 2014-03-01 paper/retrofit.tex
More small fixes.
notational changes, improvements to erasure, etc.

@@
 \begin{code}
-tv   ::= \tx.te | true | false | ta | unit
-te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fail
+tv   ::= \tx.te | true | false | ta
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
 tE   ::= tHole | tE te | tv tE | if tE then te else te
@@
 \inferrule[T-ass]
-{ }
-{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) unit |}
+{ |(ta, tv) in tS| }
+{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}
 
-\and
-\inferrule[T-fail]
-{ }
-{| conf tS ( tE [ fail ] ) -> conf tS fail |}
+%\and
+%\inferrule[T-fail]
+%{ }
+%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
 \end{mathpar}
@@
         which interact with the global store of per-task message queues |iS|, and
-    \item a forking operation allowing to spawn new tasks, which will be described in more detail in the next section.
+    \item a sandboxing operation allowing to spawn new
+    isolated tasks, which will be described in more detail in the
+    next section.
 \end{itemize}
@@
 ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
-       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
-iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
+       |  sandbox ie | send ie ie ie | ix1, ix2 <= recv. ie ie
+iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE 
        |  send iE ie ie | send iv iE ie | send iv iv iE
@@
 \begin{mathpar}
-\inferrule[I-fork]
+\inferrule[I-sandbox]
 { 
@@
 {|
-iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
+iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
 .->
@@
   roundrobin step (it1, it2, ldots)  = it2, ldots, it1
-  roundrobin D (it1, it2, ldots)     = it2, ldots
-  roundrobin N (it1, it2, ldots)     = it2, ldots
-  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
+  roundrobin done (it1, it2, ldots)     = it2, ldots
+  roundrobin nostep (it1, it2, ldots)     = it2, ldots
+  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
 \end{code}
@@
   seq step (it1, it2, ldots)     = it1, it2, ldots
-  seq N (it1, it2, ldots)        = it1, it2, ldots
-  seq D (it)                     = it
-  seq D (it1, it2, ldots)        = it2, ldots
-  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
+  seq nostep (it1, it2, ldots)        = it1, it2, ldots
+  seq done (it)                     = it
+  seq done (it1, it2, ldots)        = it2, ldots
+  seq box (it1, it2, ldots, itn)   = itn, it1, it2, ldots
 \end{code}
@@
 Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
-    \item Finally, we define some rules for scheduling, handling forking tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
+    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
 \end{itemize}
 
-The \textsc{I-fork} rule is of particular interest, as it is intended to allow users
+The \textsc{I-sandbox} rule is of particular interest, as it is intended to allow users
 to create new tasks.  When a new task is created, there is a question of what the
@@
 Conservatively, $\kappa$ may be simply thought of as the identity function, in which
-case the semantics of fork are such that the state of the target language is \emph{cloned}
-when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
+case the semantics of sandbox are such that the state of the target language is \emph{cloned}
+when sandboxing occurs.  However, this is not necessary: it is also valid for $\kappa$
 to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
 discussion of the implications of the choice of $\kappa$.
+
+For any target language |targetLang| and scheduling policy |alpha|, this
+embedding defines an information flow control language, which we will
+refer to as |specLang alpha targetLang|.
 
@@
 \begin{align*}
-    & |let i = TI (fork (x, i' <= brecv . (IT (!(TI x)))))| \\
+    & |let i = TI (sandbox (x, i' <= brecv . (IT (!(TI x)))))| \\
     & |in TI (send (IT (ref true)))|
@@
 resulted in references being shared between two tasks.  In fact, the address
-will be received by the forked task, but it will be a dangling pointer; the
+will be received by the sandboxed task, but it will be a dangling pointer; the
 task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
@@
 
-\paragraph{Status of the heap after a fork}  Here is a program whose
+\paragraph{Status of the heap after a sandbox}  Here is a program whose
 semantics depends on the definition of $\kappa$:
@@
     & |let x = ref true| \\
-    & |in TI (fork (IT (!x; !x))); x := false|
+    & |in TI (sandbox (IT (!x; !x))); x := false|
 \end{align*}
 
-When $\kappa$ is the identity, the forked task successfully dereferences
+When $\kappa$ is the identity, the sandboxed task successfully dereferences
 the contents of the reference to be true twice (recall that references
@@
 an exception is self-evident: it should simply be removed from the scheduler.
-However, under a \emph{sequential scheduler}, the behavior of \textbf{fork}
+However, under a \emph{sequential scheduler}, the behavior of |sandbox|
 can be used to model the behavior of \textbf{toLabeled}:
@@
     & |tab let pid = taskId; | \\
-    & |tab let i = TI (fork (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
+    & |tab let i = TI (sandbox (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
     & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
@@
 
-When the sequential scheduler is used, the forked task runs to
-completion before returning to the task that forked it.  Thus,
+When the sequential scheduler is used, the sandboxed task runs to
+completion before returning to the task that sandboxed it.  Thus,
 a task pool should rather be interpreted as a number of information-flow

### 2014-03-01 paper/concrete.tex

@@
   language |(C', tarrow', erasefp l)| if there exist total functions |f
-  : C -> C'| and |finv : C' -> C'| such that |f .. finv = idf C| |finv
+  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| |finv
   .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
@@
   \label{thm:iso-tsni}
-  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
-  \tar{L} satisfies TSNI.
+  If L is isomorphic to L' and L' satisfies TSNI, then
+  L satisfies TSNI.
 \end{theorem}
@@
   Shown by transporting configurations and reduction derivations from
-  \tar{L} to \ifc{L}, applying TSNI, and then transporting the
+  L to L', applying TSNI, and then transporting the
   resulting configuration, $l$-equivalence and multi-step derivation back.
@@
   \label{thm:iso-tini}
-  If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
-  satisfies TINI, then \con{L} satisfies TINI.
+  If a language L is weakly isomorphic to a language L', and L'
+  satisfies TINI, then L satisfies TINI.
 \end{theorem}
@@
   Shown by transporting configurations and reduction derivations
-  from \con{L} to \abs{L}, applying TINI and transporting the resulting
+  from L to L', applying TINI and transporting the resulting
   equivalence back using functoriality of |finv| over $l$-equivalences.

### 2014-03-01 paper/real.tex

@@
 %
-Consequently, and in contrast to our C and Haskell embeddings, for
-which we must eliminate external effects, the embedding for JS is
+Consequently, and in contrast to our C and Haskell embeddings---for
+which we must eliminate external effects---the embedding for JS is
 trivial.
 %
-Hence, as a first step, we implement the IFC language functionality in the
-JS runtime and expose the new functions, e.g., |fork|, by attaching
-them to the JS global object.
+As a first step, we directly implement |specLangJS roundrobinf| by
+running multiple instances of the JS runtime, i.e., |targetLangJS|, in
+separate OS-level threads.
+
+Specifically, we implement the IFC language functionality in the JS
+runtime, much like browser layout engines implement the DOM, and
+expose the new functions, e.g., |fork|, by attaching them to the JS
+global object.
 %
-Importantly, each task runs a separate instances of this runtime.
+Importantly, each task created with |fork| is execute in a separate
+thread, running a separate, fresh instance of our modified JS runtime.
+%
+In the context of our formalism, this amounts to using |klone(tS) =
+tS0|, where |tS0| is the global object corresponding to the standard
+JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
+etc.).
+
+Since this implementation approach relies on multiple runtimes of the
+language, sending arbitrary objects between tasks can result in
+unexpected behavior, e.g., when the object contains reference.
+%
+Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
+to expressions that can be marshalled as strings, i.e., structurally
+clonable objects~\tocite{}.
+%
+In our formalization this amounts to restricting the IFC language rule
+for |send| as follows:
+  \Red{HERE: typeof!!!}
 

### 2014-03-01 paper/real.tex
Wip

@@
 In our formalization this amounts to restricting the IFC language rule
-for |send| as follows:
-  \Red{HERE: typeof!!!}
+for |send| such that only strings can be shared:
+%{
+\newcommand{\str}{"string"}
+%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
+%format ttrue = "\texttt{true}"
+\begin{mathpar}
+\inferrule[JS-send]
+{
+|il canFlowTo il'|\\
+|iS(id') = Q|\\
+|iS' = iS [ id' mapsto (il', id,  ie') , Q ]|\\
+|ie = IT te|\\
+|conf tS (tOf te) -> conf tS ttrue|
+}
+{|
+iconf iS (fullconf id il tS (iniEi (send id' il' ie)), ldots)
+.->
+iS'; sched S (fullconf id il tS (iniEi unit), ldots)
+|}
+\end{mathpar}
+%}
+We remark that this is similar to the existing
+\texttt{postMessage} API used for iframe and Worker
+communications~\tocite{}.
+%
+Insomuch, that the SWAPI implementation provides an IFC version of
+\texttt{postMessage}, defined in terms of |send|, that additionally
+takes a label argument.
 
-Indeed this coarse-grained approach is already used by browsers in the
-Worker API~\tocite{}, which provides client-side JS with primitives
-for executing code in a separate thread, called a Worker.
+Unsurprisingly, our coarse-grained combined language approach has been
+inspired by existing browser (security) architectures.
 %
-Each Worker has a separate runtime with a fresh global object.
+Browsers, for example, isolate pages of different origins by running
+them in separate runtimes.
 %
-In turn, exchanging information between runtimes is accomplished with
-message-passing, i.e., \texttt{postMessage}.
+Similarly, they provide the Worker JS object~\tocite{}, which allows
+JavaScript to execute code in separate threads with separate JS
+runtimes (and fresh global objects).
 %
+In both cases, code relies on the \texttt{postMessage} message-passing
+API for communication.\footnote{
   The message-passing approach is, in part, due to ECMAScript's lack
@@
   %
-Hence sharing and accessing objects such as the DOM across threads is
-undefined.
-%
+  Hence sharing and accessing objects such as the DOM across Worker
+  threads is undefined.
+}
+
+\Red{HERE}
+Our |specLangJS roundrobinf| implementation builds on the existing
+Worker implementat
 

### 2014-03-01 paper/real.tex
js, almost done

@@
 In both cases, code relies on the \texttt{postMessage} message-passing
-API for communication.\footnote{
+API for communication, similar to our system.\footnote{
   The message-passing approach is, in part, due to ECMAScript's lack
@@
 
-\Red{HERE}
-Our |specLangJS roundrobinf| implementation builds on the existing
-Worker implementat
-
-Hence, our implementation provides
-
-\begin{itemize}
-\item not completely unrealist; workers provide a similar world; we
-  provide labeled workers
-
-\item actual embeddings of JS have external effects; consider the browser
-  case as in SWAPI
-\begin{itemize}
-   \item associate label with browsing context ~ task
-   \item use CSP and sandbox flags to control external effects
-   \item mediate communication by interposing on on postMessage
-   argue that browsers already have to provide isolation guarantees
-   between different compartments
-\end{itemize}
-
-\item talk about SWAPI's attach object feature that makes the concrete
-  implementation more interesting
-\end{itemize}
-
-Of course, applications, such as browsers, that embed JavaScript
-expose various features that perform external effects (again by
-attaching them as objects to the JS global object).
+More interestingly, the SWAPI implementation directly leverages these
+mechanisms to implement the semantics of |specLangJS roundrobinf|
+without modifying the JS runtime or intrusively changing the browser
+layout engine~\tocite{}.
+%
+However, a simple implementation of just associating a label with
+Workers and browsing context (iframes and top-level pages) to enforce
+IFC on the executing JavaScript is not sufficient.
+%
+The initial global object of a Worker contains the
+\texttt{XMLHttpRequest} (XHR) object, while the global object of a
+browsing context additionally contains the DOM, i.e., the global
+object in a browser JS runtime is not simply |tS0|, above, and thus,
+in both cases, JS code can trivially leak information (e.g., to the
+network with XHR or persistent storage using the DOM).
 %
 
-\cut{
-
-\subsection{Example: JavaScript}
-\label{sec:real:javascript}
-
-(NB:\ the JS spec refers to execution context and state; when we refer to
-execution context, we refer to both the context AND the state)
-
-(Some background on JavaScript versus ECMAScript, since ECMAScript
-constitutes the semantics we're actually going to combine with
-IFC;\ everything else has to be locked down or made IFC-specific).
-
-(Lay out how ECMAScript semantics work. Execution context and syntax.
-Don't go into too much detail.  Point out that the execution context/state
-corresponds implementation-wise to a JavaEngine)
-g
-(Minimal IFC fragment.  Actually, this wants to be in the general section.
-So specialize this some more?)
-
-(Combined ECMAScript and IFC. Talk about serialization. Draw parallel to web
-workers, note the similarity.)
+To address this we use content security policy (CSP) and (iframe)
+sandbox~\tocite{} to restrict external effects according to the label
+of a task (Worker or browsing context), as describe
+in~\tocite{}.
+%
+Of course, simply disallowing all external effects for all browsing
+contexts would break most of the Web.
+%
+Hence SWAPI only enforces IFC, and thus restricts external effects,
+when the JS code uses the new API.\footnote{
+  Once a piece of code ``opts-in'' to use our IFC API, in addition to
+  restricting external effects we interpose ``standard''
+  \texttt{postMessage} communication to ensure that no information is
+  leaked between contexts that have opted-in and those that have not.
 }
+%
+Moreover, rather than disallowing all external effects, SWAPI allows
+controlled network communication by leveraging the fact that web
+pages already have an accompanying security policy: the same origin
+policy.
+%
+Hence, for example, a Worker that has read data only sensitive to
+\texttt{http://bank.ch} can communicate with this domain; only once
+\texttt{http://aws.com} data is also included in the context will all
+network requests be blocked.
+%
+Of course, this requires that we use a concrete label format to
+express the policies; we refer the interested reader to~\tocite{} for
+more details.

### 2014-03-01 paper/real.tex
bigass footnote

@@
 running multiple instances of the JS runtime, i.e., |targetLangJS|, in
-separate OS-level threads.
+separate OS-level threads.\footnote{
+ The Firefox implementation of SWAPI also considers the case where
+ tasks share the JavaScript runtime event-loop, but the heap and
+ execution context of each task is disjoint. This is similar to the
+ single-heap language of Section~\ref{sec:concrete}.  However, since the heap
+ separation is provided by the browser the browser, we do not discuss
+ this further. The interested reader is referred to~\tocite{} for more
+ details.
+}
 
@@
 %
-Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
+As discussed in Section~\ref{sec:concrete} we thus restrict |send|
 to expressions that can be marshalled as strings, i.e., structurally
@@
 
-To address this we use content security policy (CSP) and (iframe)
-sandbox~\tocite{} to restrict external effects according to the label
-of a task (Worker or browsing context), as describe
+To address this, we additionally use content security policy (CSP) and
+(iframe) sandbox~\tocite{} to restrict external effects according to
+the label of a task (Worker or browsing context), as describe
 in~\tocite{}.

### 2014-03-01 paper/related.tex
First pass at related work section.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \label{sec:related}
+
+Our paper follows a long tradition of papers on information flow
+control.  Our information flow control system is mostly closely related
+to the coarse-grained information systems used in operating systems such
+as Asbestos~\cite{efstathopoulos:asbestos} and
+HiStar~\cite{Zeldovich:2006}, as well as language-level
+\emph{floating-label IFC systems} such as LIO~\cite{lio},
+Breeze~\cite{Hritcu:2013:YIB:2497621.2498098}, where there is a label
+associated with threads of execution which increases monotonically.
+Our treatment of termination-sensitive and termination-insensitive interference
+originates from Smith and Volpano~\cite{Smith:Volpano:MultiThreaded,Volpano:1997:ECF:794197.795081}.
+While this work often considers the interaction of information flow
+control with respect to various language features (e.g.,
+exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}), none of these
+systems attempt to be generic in the choice of target language.
+
+One of the primary motivations behind this paper is constructing a
+practical information flow control system for JavaScript.  Some of
+these systems attempt to perform fine-grained information flow of
+JavaScript, e.g. Hedin and Sabelfield's work~\cite{Hedin:2012} on JSFlow~\cite{JSFlow}
+and \Red{some other stuff here}.  While fine-grained information flow
+control can result in very precise analysis of legacy code, it comes
+at the cost of high theoretical complexity (the system must accomodate
+the entirety of JavaScript's semantics) and runtime performance cost.
+There are attempts to overcome this performance barrier by various means:
+Austin and Flanagan~\cite{Austin:Flanagan:PLAS09} handle this problem
+by using a \emph{sparse information labeling} scheme which reduces the
+cost of managing labels when they are not needed, while FlowFox~\cite{DeGroef:2012}
+uses an entirely different technique of \emph{secure multi-execution} to
+enforce non-interference. \Red{Probably more stuff here.}
+
+The constructs in our IFC language, as well as the behavior of
+inter-thread communication, is reminiscent of distributed systems
+like Erlang.~\cite{Armstrong03makingreliable}  There is a close
+correspondence: in distributed systems, isolation is required due to
+physical constraints; in information flow control, isolation is
+required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
+built an information flow control system on top of Erlang which is quite
+similar to ours.  However, they do not use a floating label system (processes
+can find out when sending a message failed due to a forbidden information flow),
+and they include no security proofs.
+
+There appears to be limited literature in general techniques for
+retrofitting information flow control to arbitrary languages; however,
+one time-honored technique is defining a fundamental calculus, for which
+other languages can be desugared into.  Abadi et al.~\cite{abadi+:core}
+motivate their core calculus of dependency by showing how various
+previous systems can be encoded in it; Tse and
+Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus
+can be encoded in System F via parametricity.  However, this work is
+primarily focused on static information flow control systems.
+
+Our definition of isomorphism of information flow control languages in
+Section~\ref{sec:concrete} is closely related to the idea of
+\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
+although as our system is deterministic, we do not use the theory in any
+deep way.
+
+It has long been observed that information flow control and monads are
+closely related.  This observation has been used by Abadi et
+al.~\cite{abadi+:core} to structure access to private data by protecting
+it using a lattice of monads, one per security level.  Our system uses
+monads in a conceptually different manner, where there is a single monad
+representing the information flow control computational effects; this
+is inline with the use of monads in other systems.~\cite{Harrison05,lio,Devriese:2011}.
+Devriese and Piessens~\cite{Devriese:2011} utilized monad
+transformers as an essential component in their work.  However, their use
+of monad transformers is to explain when extra constraints on a non-information
+flow control aware base monad should be applied (i.e., during lifting).
+Harrison and Hook~\cite{Harrison05} define a notion of \emph{atomic noninterference},
+which is preserved through monad transformer application.  However, it is not
+clear what the relationship between this notion and traditional noninterference is,
+and in their paper they prove only a weaker property of no write down.
+
+\cut{
+\begin{itemize}
+    \item Monads and IFC (Abadi~\cite{Abadi+:Core}, Tse~\cite{Tse:Zdancewic:ICFP04}, Harrison-Hook~\cite{Harrison05}, Crary~\cite{Crary:2005}, Devriese-Piessens~\cite{Devriese:2011})
+    \item \Red{Operating systems approaches to IFC, which use coarse grained (Asbestos~\cite{efstathopoulos:asbestos}, HiStar~\cite{Zeldovich:2006})}
+    \item \Red{Floating-label IFC systems, look at LIO paper (LIO~\cite{lio}, Breeze~\cite{Hritcu:2013:YIB:2497621.2498098})}
+    \item JavaScript IFC related work, look at BrowBound.
+(ADSafe, xBook \Red{needs lookup})  Classify approaches into fine-grained (Hedin-Sabelfield~\cite{Hedin:2012}+JSFlow~\cite{JSFlow}, FlowFox~\cite{DeGroef:2012}, ConDOM~\cite{ConDOM}, Austin-Flanagan (sparse information labeling)~\cite{Austin:Flanagan:PLAS09}) or coarse-grained (BFlow~\cite{Yip:2009:PBS}, see Deian)
+\item Secure multi-execution (FlowFox~\cite{DeGroef:2012}, Russo~\cite{Jaskelioff:SME})
+\item Distributed programming languages (Cloud Haskell) plus IFC (Erlang (they check IFC when sending messages, no security proofs, assumes true isolation, not a floating labels)~\cite{Papagiannis_enforcinguser})
+\end{itemize}
 
@@
 Gotta talk about secure multi-execution
+}

### 2014-03-01 paper/real.tex
First pass at related work section.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
typofix
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-We refer the interested reader to~\tocite{icfp,haskellsymp} for
+We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
 additional details on the various implementations of this system.
@@
 Here, we lastly remark that our work unifies these systems and
-presents a proof of NI for such systems with asynchronous
+presents a proof of non-interference for such systems with asynchronous
 communication primitives.

### 2014-03-01 paper/real.tex
fix comparison w/ c in haskell subsection

@@
 \label{sec:real:hs}
-While the C embedding closely resembles the specification language of
-Section~\ref{sec:retrofit}, in our Haskell IFC embedding we leverage
-Haskell's strong data abstraction and static type system, monadic
-approach to effects, and lightweight concurrency to implement the
-embedding in a more efficient manner, as library.
+While the C embedding relies on hardware protection mechanisms to
+implement the embedding of Section~\ref{sec:retrofit}, in our Haskell
+IFC embedding we leverage Haskell's strong data abstraction and static
+type system, monadic approach to effects, and lightweight concurrency
+to implement the embedding in a more efficient manner, as library.
 

### 2014-03-01 paper/real.tex
wip

@@
 \label{sec:real:c}
+%
+Within the confine of a process, C program can execute arbitrary
+(machine) code, access arbitrary memory, and perform arbitrary
+syscalls.
+%
+C code is only confined to degree imposed by by underlying OS and
+hardware.
+%
+Hence implementing an IFC system according to the specification
+language of Section~\ref{sec:retrofit} must address these concerns.
+
+Nevertheless, we believe that an implementation that adheres to our
+specification under the |roundrobinf| scheduler can be achieved
+without too much effort.
+%
+(Our proposed approach, below, is very similar to a simpler version of
+Wedge~\tocite{}, with an IFC policy.)
+%
+Specifically, we propose a system, HIPStar, that uses hardware
+protection mechanisms to isolate untrusted code according to an IFC
+policy (implemented by a small runtime) in user-space, with
+Dune~\tocite{}.
+%
+Using pages tables, our (trusted) IFC runtime ensures that each task,
+implemented as a lightweight process can only access the memory it
+allocates--tasks do not have access to any shared memory.
+%
+In addition, we use ring protection to intercept syscalls performed by
+a task and only permit those corresponding to our IFC language (e.g.,
+|getLabel|, |send|).
+%
+
+Although other sandboxing mechanisms can be used in place of Dune, we
+believe Dune's hardware protection mechanism allow us to provide a 
+concrete implementation that is simpler to reason about.
+%
+To this end, the combined language of Section~\ref{sec:retrofict}
+corresponds to C with the additional IFC syscalls.
+%
+Creating a new task with the |fork| syscall ensures that no memory is
+shared, by defining |kappa(tS) = tS0|, where |tS0| is the set of pages
+we copy to bootstrap the lightweight process.
+%
+Similarly, sending a message with |send| results in a copying the
+pages to our (trusted) runtime, and, then the (untrusted) receiver.
+%
+Of course, a more efficient message-passing approach, such as that of
+Singularity~\tocite{}, which simply passes a pointer to data the
+receiver at the cost of revoking the sender's access to the pages is
+also possible.
 

### 2014-03-01 paper/real.tex
last c paragraph

@@
 %
-To this end, the combined language of Section~\ref{sec:retrofict}
-corresponds to C with the additional IFC syscalls.
+The ability to provide a new syscall interface allows us to precisely
+define combined language of Section~\ref{sec:retrofit} as C with only
+IFC syscalls.
 %
-Creating a new task with the |fork| syscall ensures that no memory is
-shared, by defining |kappa(tS) = tS0|, where |tS0| is the set of pages
-we copy to bootstrap the lightweight process.
+Page tables limits what memory a task can access; hence, we can ensure
+that new task created with the |fork| syscall will no have any shared
+memory, i.e., we can effectively define |kappa(tS) = tS0|, where |tS0|
+is the set of pages necessary in bootstrap a lightweight process.
 %
-Similarly, sending a message with |send| results in a copying the
-pages to our (trusted) runtime, and, then the (untrusted) receiver.
+Similarly, control over page tables and protection bits allows us to
+define a |send| syscall that satisfies the concrete/abstract
+isomorphism.
+%
+Specifically, we can implement a |send| that copies pages to our
+(trusted) runtime queue; and, correspondingly, a |recv| that copies
+the pages from the runtime queue to the (untrusted) receiver.
 %
@@
 also possible.
+%
+However, since we do not consider the isomorphism condition for this,
+we do not discuss it further.
 

### 2014-03-01 paper/real.tex
minor

@@
 The ability to provide a new syscall interface allows us to precisely
-define combined language of Section~\ref{sec:retrofit} as C with only
-IFC syscalls.
+define the combined language of Section~\ref{sec:retrofit} as C with
+with (only) IFC syscalls.
 %

### 2014-03-01 paper/real.tex
minor

--- 2014-03-01 paper/real.tex
@@
 %
-To this end, the combined language of Section~\ref{sec:retrofict}
-corresponds to C with the additional IFC syscalls.
+The ability to provide a new syscall interface allows us to precisely
+define the combined language of Section~\ref{sec:retrofit} as C with
+(only) IFC syscalls.
 %
-Creating a new task with the |fork| syscall ensures that no memory is
-shared, by defining |kappa(tS) = tS0|, where |tS0| is the set of pages
-we copy to bootstrap the lightweight process.
+Page tables limits what memory a task can access; hence, we can ensure
+that new task created with the |fork| syscall will not have any shared
+memory, i.e., we effectively define |kappa(tS) = tS0|, where |tS0| is
+the set of pages necessary in bootstrap a lightweight process.
 %
-Similarly, sending a message with |send| results in a copying the
-pages to our (trusted) runtime, and, then the (untrusted) receiver.
+Similarly, control over page tables and protection bits allows us to
+define a |send| syscall that copies pages to our
+(trusted) runtime queue; and, correspondingly, a |recv| that copies
+the pages from the runtime queue to the (untrusted) receiver.
+%
+Since C is not memory safe, conditions on these syscalls are
+meaningless.
 %

### 2014-03-01 paper/intro.tex
lhs makefile; put new outline
TODO: add notation for lhs stuff
Introduction.

--- 2014-01-22 intro.tex
@@
 \label{sec:intro}
+
+Information flow control (IFC) is a promising technique to enforce
+security policies by tracking the flow of sensitive data through
+a system.  The idea is to prevent the leaking of secret or sensitive
+data into public channels by enforcing the notion of non-interference.
+Significant research has been devoted to adding various
+forms of IFC to different kinds of programming languages and system,
+both static and dynamic in nature.  In this paper we are interested
+in the latter, where an execution monitor ensure at runtime that secret
+information is not revealed through public outputs.
+A key challenge in the design of these dynamic systems has been the
+performance cost incurred by additional security checks.
+Particularly when retrofitting an existing programming language with
+IFC it is tempting to track information flow at a fine-grained level,
+e.g., per value in the system.  This can lead to impractical
+runtime overheads even for ordinary operations.
+
+An alternative to this is a more \textit{coarse-grained} approach
+to IFC by trading off precision for efficiency.  Here, computational
+units are associated with a floating label which protects all data
+in this unit.
+A recent example dubbed SWAPI adds IFC to the web by extending
+Javascript with coarse-grained IFC by identifying web workers as
+an existing computational unit.  Communication between workers can
+efficiently be mediated in an IFC aware way to ensure a notation
+non-interference, where sensitive workers cannot influence the
+computations in less sensitive workers.
+
+This coarse-grained approach as employed by SWAPI provides a number
+of advantages; (1) reduced runtime overhead because checks need only
+be performed at isolation boundaries, (2) minimal changes to an
+existing programming language when adding IFC, which (3) allows
+the reuse of existing programs.  Finally, (4) the simplicity
+of a single security label per computational unit facilitates
+understanding and easy reasoning about the correctness of the
+system, in particular without having to reason about all the
+technical details of the semantics of the programming language
+at hand.
+
+The recognition of the simplicity of this coarse-grained approach
+to IFC allows us to generalize it to a large class of programming
+languages.  In this paper we identify the key concepts of coarse-grained
+dynamic IFC and show how these can be combined with a programming
+language, which we will call the target language.  We achieve this
+by using an embedding that combines the operational semantics
+of the core IFC calculus and the target language.
+At the core of our IFC system we use a sandboxing operation that allows
+the execution of potentially sensitive computations in isolation,
+while communicating through clearly specified interfaces with other
+sandboxed operations.
+We formally state and prove the non-interference guarantees that our
+system gives, independently of the choice of the target language.
+
+One challenge in the design of such a general IFC calculus that
+is supposed to work for a large class of programming languages is
+that the stated semantics might not correspond well to the
+semantics of a concrete implementation for a particular choice
+of target language.  We address this issue by using the notation
+of isomorphism to characterize a condition that guarantees
+non-interference of the concrete system without having to prove
+this property manually.
+
+Our key contributions can be summarized as follows:
+\begin{itemize}
+  \item We give formal semantics for a core IFC language that
+  captures the essence of coarse-grained information flow control.
+  \item We show how a large class of target languages can be combined
+  with this IFC language and prove that the resulting system provides
+  non-interference.
+%  \item We show how to extend the Matthews-Findler method from just
+%  languages that are not simply expressions evaluating to values,
+%  but may be collections of threads executing nondeterministically.
+  \item We provide a proof technique to show the non-interference
+  of a concrete semantics for a potentially optimized IFC language
+  by means of an isomorphism, and show a class of restrictions on
+  the IFC calculus that preserves non-interference.
+  \item We sketch how the core IFC language can be enriched with
+  more advanced concepts such as labeled values, privileges or a
+  notation of clearance.
+  \item We connect our formal semantics to real implementations of
+  coarse-grained IFC systems for Javascript and Haskell, and explain
+  how our system could be used to enforce IFC in C.
+  \item We informally connect our results to a monadic interpretation
+  of IFC which guided our design.
+\end{itemize}
+
+\cut{
 
@@
 apply the procedure to a number of systems.
+}

### 2014-03-01 paper/real.tex

@@
 
-In this section we consider the application of our embedding to 
-real world target languages.
+In the introduction, we stated that the original motivation behind
+developing this embedding was in order to formally specify a
+coarse-grained information flow control language for JavaScript.
 %
-To illustrate the flexibility of our system and challenges in the
-embedding we chose three mainstream languages---C, Haskell, and
-JavaScript---that have vastly different features and properties.
+In Section~\ref{sec:retrofit}, however, we used only a simplified
+language as an example target language.
 %
-We remark that we have implemented variants of our Haskell and
-JavaScript embeddings, which are used in the Hails~\tocite{} and
-SWAPI~\tocite{} systems; we leave the implementation of the IFC system
-for C, as describe below, to future work.
+In this section, we consider the application of our embedding to
+JavaScript and two other real world target languages, C and Haskell.
+%
+Our goal is to show the flexibility of the embedding in settings with
+vastly different features and properties, as well as discuss the
+semantic gap that must be overcome in some cases to apply our formalism
+to other systems.
+%
+Two of the systems we describe have been implemented: the Haskell
+system~\cite{lio} and the SWAPI~\tocite{} system; we leave the
+implementation of the IFC system for C to future work.
 
@@
 %
-Within the confine of a process, C program can execute arbitrary
-(machine) code, access arbitrary memory, and perform arbitrary
-syscalls.
+C programs are able to execute arbitrary (machine) code, access
+arbitrary memory, and perform arbitrary syscalls.
 %
-C code is only confined to degree imposed by by underlying OS and
-hardware.
+Thus, the confinement of C programs must be imposed by the underlying OS
+and hardware.
 %
-Hence implementing an IFC system according to the specification
-language of Section~\ref{sec:retrofit} must address these concerns.
-
-Nevertheless, we believe that an implementation that adheres to our
-specification under the |roundrobinf| scheduler can be achieved
-without too much effort.
+This isolation can be achieved using hardware protection
+mechanisms~\cite{Belay:2012:DSU:2387880.2387913} (similar to a simpler
+version of Wedge~\cite{Bittau:2008:WSA:1387589.1387611} with an
+information flow control policy).
 %
-(Our proposed approach, below, is very similar to a simpler version of
-Wedge~\tocite{}, with an IFC policy.)
-%
-Specifically, we propose a system, HIPStar, that uses hardware
-protection mechanisms to isolate untrusted code according to an IFC
-policy (implemented by a small runtime) in user-space, with
-Dune~\tocite{}.
-%
-Using pages tables, our (trusted) IFC runtime ensures that each task,
-implemented as a lightweight process can only access the memory it
+Using pages tables, a (trusted) IFC runtime could ensure that each task,
+implemented as a lightweight process, can only access the memory it
 allocates--tasks do not have access to any shared memory.
 %
-In addition, we use ring protection to intercept syscalls performed by
+In addition, ring protection could be used to intercept syscalls performed by
 a task and only permit those corresponding to our IFC language (e.g.,
@@
 %
+Although other sandboxing mechanisms can be used in place of Dune, we
+believe Dune's hardware protection mechanism would allow us to provide a 
+concrete implementation that is more efficient and simpler to reason about.
 
-Although other sandboxing mechanisms can be used in place of Dune, we
-believe Dune's hardware protection mechanism allow us to provide a 
-concrete implementation that is simpler to reason about.
+In this setting, the combined language of Section~\ref{sec:retrofit}
+can be interpreted in the following way: calling from the target
+language to the IFC language corresponds to invoking a syscall.
 %
-The ability to provide a new syscall interface allows us to precisely
-define the combined language of Section~\ref{sec:retrofit} as C with
-(only) IFC syscalls.
-%
-Page tables limits what memory a task can access; hence, we can ensure
-that new task created with the |fork| syscall will not have any shared
-memory, i.e., we effectively define |kappa(tS) = tS0|, where |tS0| is
-the set of pages necessary in bootstrap a lightweight process.
+Creating a new task with the |sandbox| syscall is corresponds to
+\emph{forking} a process.  Here, page tables limit what memory
+a task can access: we can ensure there will be no memory (effectively
+defining |klone(tS)
+= tS0|, where |tS0| is the set of pages necessary to bootstrap a
+lightweight process.)
 %
@@
 %
+\Red{
+EZY: Suggest chopping
+
     Of course, a more efficient message-passing approach, such as that of
@@
 However, since we do not consider the isomorphism condition for this,
-we do not discuss it further.
+we do not discuss it further.}
 
@@
 \label{sec:real:hs}
-While the C embedding relies on hardware protection mechanisms to
-implement the embedding of Section~\ref{sec:retrofit}, in our Haskell
-IFC embedding we leverage Haskell's strong data abstraction and static
-type system, monadic approach to effects, and lightweight concurrency
-to implement the embedding in a more efficient manner, as library.
+In contrast with the C embedding which relies on hardware protection
+mechanisms, a Haskell implementation can leverage Haskell's strong data
+abstraction and static type system, monadic approach to effects, and
+lightweight concurrency to implement the embedding in a more lightweight
+manner.  We briefly describe one such system, LIO,~\cite{lio} which
+implements IFC as a library.
 
-To this end, we define a new monad, |LIO|, that wraps Haskell's |IO|
-monad---which allows for arbitrary effects---to associate labels with
-threads (tasks) and restrict computational effects according to the
-semantics of Section~\ref{sec:retrofit}.
+LIO is implemented by defining a new monad, \verb|LIO|, which wraps Haskell's \verb|IO|
+monad.
 %
-The precise restrictions encode our IFC system as computations in the
-|LIO| monad.
+The purpose of this monad is twofold: it restricts the use of
+arbitrary effects that would ordinarily be allowed by the \verb|IO| monad,
+and it associates labels with threads (tasks).
 %
-By wrapping |IO|, we can use Haskell's efficient implementation of
+Computations in the \verb|LIO|
+monad can be thought to be operating within the IFC system.
+%
+One important aspect of using \verb|IO| as the base for this
+implementation is that it allows use of Haskell's efficient implementation of
 threads, channels, etc. (e.g., we use Haskell's \texttt{forkIO} to
 fork a lightweight thread in the case of |fork|), in contrast to
-defining them in a pure fashion (see Section~\ref{sec:monad}).
+defining them in a completely pure fashion (as suggested in Section~\ref{sec:monad}).
 
-Importantly, this concrete implementation approach also directly
-corresponds to the specification language.
+What is the interpretation of this system as per Section~\ref{sec:retrofit}?
 %
-Specifically, it is |specLang alpha targetLangHS|, for $|alpha| \in
-|{roundrobinf, seqf}|$, with the pure subset of Haskell as to target
-language |targetLangHS|, the subset of Haskell that additionally
-contains the |LIO| monad (and corresponding |LIO| computations
-encoding the language) as the IFC language.
+Here, the \emph{pure subset} of Haskell is the target language
+|targetLangHS|, while the monadic subset of Haskell in the \verb|LIO|
+monad is the IFC language.
 %
-Of course since our IFC system is implemented as a library in Haskell,
-we must ensure that these languages are indeed the subsets of Haskell
+Crucially, the lack of unrestricted mutation in the pure fragment of
+Haskell prevents direct communication between tasks, even when memory is
+shared between them.\footnote{However, lazy evaluation can still produce
+a covert channel.}
+
+Since this IFC system is implemented as a library in Haskell,
+implementation-wise, we must ensure that these languages are indeed the subsets of Haskell
 we claim, i.e., while the concrete language is all of Haskell, we must
@@
 %
-
-To this end, we rely Haskell's strong data abstraction and type system
+To this end, \verb|LIO| relies on Haskell's strong data abstraction and type system
 (as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
-ensure that arbitrary |IO| actions cannot be lifted into
-|LIO|.\footnote{
-Of course, our IFC guarantees only extend insofar as the program is
-written as a computation in the |LIO| monad; a program written
-directly in the |IO| monad can trivially violate information flow
-control.
-}
+ensure that arbitrary \verb|IO| actions cannot be lifted into
+\verb|LIO|.
 %
-In other words, assuming |LIO| is implemented correctly, programs
-written in the |LIO| monad cannot perform arbitrary |IO| actions
+In other words, assuming \verb|LIO| is implemented correctly, programs
+written in the \verb|LIO| monad cannot perform arbitrary \verb|IO| actions
 without breaking abstraction.
@@
 We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
-additional details on the various implementations of this system.
-%
-Here, we lastly remark that our work unifies these systems and
-presents a proof of non-interference for such systems with asynchronous
-communication primitives.
+additional details on the various implementations of this system.\footnote{It's worth noting that the proofs of non-interference we have given for asynchronous communication primitives are new and not in the original presentation of LIO.}
 
@@
 JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
-built-in functionality for I/O.
+built-in functionality for I/O. (Capabilities such as the ability to
+mutate the DOM and read user input are APIs defined on top of the ECMAScript
+specification.)
 %
@@
 trivial.
+
+We describe SWAPI,~\tocite{} an implementation of this system for JavaScript.
 %
-As a first step, we directly implement |specLangJS roundrobinf| by
-running multiple instances of the JS runtime, i.e., |targetLangJS|, in
+The direct approach for implementing the embedded language |specLangJS roundrobinf| is
+by running multiple instances of the JS runtime, i.e., |targetLangJS|, in
 separate OS-level threads.\footnote{
@@
 
-Specifically, we implement the IFC language functionality in the JS
+From here, the IFC language functionality is implemented in the JS
 runtime, much like browser layout engines implement the DOM, and
-expose the new functions, e.g., |fork|, by attaching them to the JS
+expose the new functions, e.g., |sandbox|, by attaching them to the JS
 global object.
 %
-Importantly, each task created with |fork| is execute in a separate
-thread, running a separate, fresh instance of our modified JS runtime.
+To avoid termination timing attacks, each task created with |sandbox| is
+executed in a separate thread, running a separate, \emph{fresh} instance of our
+modified JS runtime.
 %
-In the context of our formalism, this amounts to using |klone(tS) =
+Formally, \verb|sandbox| is defined with |klone(tS) =
 tS0|, where |tS0| is the global object corresponding to the standard
@@
 language, sending arbitrary objects between tasks can result in
-unexpected behavior, e.g., when the object contains reference.
+unexpected behavior, e.g., when the object contains references.
 %
-As discussed in Section~\ref{sec:concrete} we thus restrict |send|
+As discussed in Section~\ref{sec:concrete}, we need to restrict |send|
 to expressions that can be marshalled as strings, i.e., structurally
-clonable objects~\tocite{}.
+clonable objects.
 %
-In our formalization this amounts to restricting the IFC language rule
+In our formalization, this amounts to restricting the IFC language rule
 for |send| such that only strings can be shared:
@@
 \texttt{postMessage} API used for iframe and Worker
-communications~\tocite{}.
+communications~\cite{webworkers}.
 %
-Insomuch, that the SWAPI implementation provides an IFC version of
+Thus, the SWAPI implementation provides an IFC version of
 \texttt{postMessage}, defined in terms of |send|, that additionally
@@
 %
-Similarly, they provide the Worker JS object~\tocite{}, which allows
+Similarly, they provide the Worker JS object~\cite{webworkers}, which allows
 JavaScript to execute code in separate threads with separate JS
@@
 }
-
-More interestingly, the SWAPI implementation directly leverages these
+%
+As suggested by our formal semantics, SWAPI can directly leverage these
 mechanisms to implement the semantics of |specLangJS roundrobinf|
 without modifying the JS runtime or intrusively changing the browser
-layout engine~\tocite{}.
-%
+layout engine.
+
 However, a simple implementation of just associating a label with
 Workers and browsing context (iframes and top-level pages) to enforce
-IFC on the executing JavaScript is not sufficient.
+IFC on the executing JavaScript is not sufficient, as APIs which
+introduce extra computational effects must be manually made aware of information flow
+control.
 %
-The initial global object of a Worker contains the
+For example, the initial global object of a Worker contains the
 \texttt{XMLHttpRequest} (XHR) object, while the global object of a
-browsing context additionally contains the DOM, i.e., the global
-object in a browser JS runtime is not simply |tS0|, above, and thus,
-in both cases, JS code can trivially leak information (e.g., to the
+browsing context additionally contains the DOM.
+%
+In both cases, JS code can trivially leak information (e.g., to the
 network with XHR or persistent storage using the DOM).
 %
+To address this, SWAPI additionally uses content security policy (CSP) and
+(iframe) sandboxes~\tocite{} to restrict external effects according to
+the label of a task (worker or browsing context).  Accomodating these
+features lies outside the purview of our formalism.
 
-To address this, we additionally use content security policy (CSP) and
-(iframe) sandbox~\tocite{} to restrict external effects according to
-the label of a task (Worker or browsing context), as describe
-in~\tocite{}.
-%
+\Red{
+EZY:  This seems like useless detail about the SWAPI implementation
+that is not relevant to this paper.
+
 Of course, simply disallowing all external effects for all browsing
@@
 express the policies; we refer the interested reader to~\tocite{} for
-more details.
+more details.}

### 2014-03-01 paper/formal.tex
Improvements to formal.

@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-In our case, |specLang alpha (targetLang nop) = (ifc C, ifc
-V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
+Our language |specLang alpha (targetLang nop)| can be
+represented as |(ifc C, ifc V, .->, erasef il)|, such that
+$|ifc C| = |iS| \times \prod |it|$ and
 $|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
@@
 The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
-containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
+containing |bullet|, and Figure~\ref{fig:erasure} gives the precise definition for
 our erasure function |erasef il|.
@@
 A task and its corresponding message queue is completely removed from the task
-list if its label does not flow to the attacker observation level |il|;
-otherwise, we apply the erasure function homomorphically and remove any message
+list if its label does not flow to the attacker observation level |il|.
+Otherwise, we apply the erasure function homomorphically and remove any message
 from the task's message queue that are more sensitive than |il|.
@@
 
-We note that the definition of |erasef il| precisely captures the IFC
+We note that the definition of |erasef il| captures the IFC
 language's attacker model. 
 %
-For instance, in our case, by removing sensitive tasks and messages from the
-system, we assume that that the attacker cannot observe the number of sensitive
-tasks or messages.
+In our case, we assume that the attacker cannot observe sensitive tasks or
+messages, or even just the number of such entities.
 %
@@
 security level |l|, which is typically defined as an equivalence
-relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
+relation---called |l|-equivalence---on configurations.  An attacker
+at level |l| cannot
 distinguish two configurations that are |l|-equivalent.
@@
 This precise non-interference property is called termination sensitive non-interference
-(TSNI), since it considers runs of programs, and thus does not allow for leaks
-due termination or internal timing behavior.
+(TSNI).  Besides the obvious requirement to not leak secret information
+to public channels, this definition also requires the termination
+of public tasks to be independent of secret tasks.
 %
@@
 
-\begin{theorem}[Concurrent specification language is TSNI]
+\begin{theorem}[Concurrent IFC language is TSNI]
   \label{thm:rr-tsni}
-For any target language |targetLang nop|, |specLang roundrobinf
-(targetLang nop)| satisfies TSNI.
+For any target language |targetLang|, |specLang roundrobinf
+targetLang| satisfies TSNI.
 \end{theorem}
@@
 sensitive threads current state when deciding which thread to schedule next
-will clearly not satisfy TSNI.
+will in general not satisfy TSNI.
 %
-In Section~\toref{} we detail the preceise scheduler for which our
-specification language is TSNI.
+%In Section~\toref{} we detail the preceise scheduler for which our
+%specification language is TSNI.
 %
-Here, we simply remark that even non-adversairal schedulers are not always safe.
 
+However, even non-adversairal schedulers are not always safe.
 Consider, for example, the sequential scheduling policy |seqf| given in
@@
 i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
-sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.  We can write the
-following program in the specification language:
+sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
+Consider the following two configurations in this language:
 \begin{code}
@@
 \end{code}
-These two configurations are |pub|-equivalent, however |ic1| will reduce (in two
+These two configurations are |pub|-equivalent, but |ic1| will reduce (in two
 steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
@@
 Though we do not model labeled channels, extending the calculus with such a
-feature is straight forward, see Setion~\ref{}.
-} then the |sec| tasks's decision to diverge or not is directly leaked to a
+feature is straight forward, see Setion~\ref{sec:extensions}.}
+then the |sec| tasks's decision to diverge or not is directly leaked to a
 public entitiy.
 
-In certain cases, however, a TSNI-safe concurrent scheduling policy such as
-|roundrobinf| cannot be considered without imposig a non-trivial burden on the
-concrete implementation.
+% sheule: I feel like this forward reference is not useful here.
+%In certain cases, however, a TSNI-safe concurrent scheduling policy such as
+%|roundrobinf| cannot be considered without imposing a non-trivial burden on the
+%concrete implementation.
+%(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
+%target language.)
 %
-(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
-target language.)
-%
-Hence, we consider an alternative non-interference property---called termination insensitive
-non-interference---that can also be upheld by sequential languages at the cost
+To accomodate for sequential languages, or cases where a weaker guarantee
+is sufficient, we consider an alternative non-interference property called termination insensitive
+non-interference (TINI).  This property can also be upheld by sequential languages at the cost
 of leaking one bit through (non)-termination.
@@
   insensitive non-interfering if for any label |l|, and configurations
-  |c1, c2 member C| and |c1', c2' member V| if
-   $|c1| \approx_{|l|} |c2|$,
-   $|c1| |.->|^* |c1'|$, and
-   $|c2| |.->|^* |c2'|$, then
-   $|c1'| \approx_{|l|} |c2'|$.
+  |c1, c2 member C| and |c1', c2' member V|, it holds that
+  \[
+    (|c1| \approx_{|l|} |c2|
+    \;\;\land\;\;
+    |c1| |.->|^* |c1'|
+    \;\;\land\;\;
+    |c2| |.->|^* |c2'|)
+    \implies
+    |c1'| \approx_{|l|} |c2'|
+  \]
 \end{definition}
@@
 TSNI states that if we take two |l|-equivalent configurations, and both
-configurations reduce to terminal configuration states (for which there are no
+configurations reduce to final configurations (i.e.,
+configurations for which there are no
 possible further transitions), then the end configurations are also
@@
 We highlight that this statement is much weaker than TSNI: it only states that
-terminating programs do not leak sensitive data.
+terminating programs do not leak sensitive data, but makes no statement
+about non-terminating programs.
 
-Nevertheless, we believe TINI to be a useful for many scenariors and thus we
+Nevertheless, we believe TINI to be a useful for many scenarios and thus we
 show that our IFC language with the sequential scheduling policy |seqf|
@@
 %
-\begin{theorem}[Sequential specification language is TINI]
+\begin{theorem}[Sequential IFC language is TINI]
   \label{thm:seq-tini}
-For any target language |targetLang nop|, |specLang seqf (targetLang
-nop)| satisfies TINI.
+For any target language |targetLang|, |specLang seqf targetLang| satisfies TINI.
 \end{theorem}

### 2014-03-01 paper/concrete.tex
notation fixes.

@@
       \text{|ie| does not contain any |ta|}\\
-      |iS' = iS [ id' mapsto nil ]|\\
+      |iS' = iS [ mapsto id' nil ]|\\
       |it1 = oneheapfullconf id il (iniE id')|\\
@@
       |iS(id') = Q|\\
-      |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
+      |iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
     }

### 2014-03-01 paper/formal.tex
notation fixes.

@@
   &|erase il emptyset = emptyset|\\
-  &|erase il (iS [id mapsto Q]) =| \begin{cases}
+  &|erase il (iS [mapsto id Q]) =| \begin{cases}
     |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
     & \text{the label of thread |id|} \\
-    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
+    |(erase il iS) [mapsto id (erase il Q)]| & \text{otherwise}
   \end{cases} \\

### 2014-03-01 paper/retrofit.tex
notation fixes.

@@
 { }
-{| conf tS (ref tv) -> conf (tS [ ta mapsto tv ]) ta |}
+{| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}
 {| fresh ta |}
@@
 { |(ta, tv) in tS| }
-{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}
+{| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}
 
@@
 Q    ::=  nil | io , Q
-iS   ::=  emptyset | iS [ id mapsto Q ]
+iS   ::=  emptyset | iS [ mapsto id Q ]
 \end{code}
@@
 |iS(id') = Q|\\
-|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
+|iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
 }
@@
 | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
-| iS' = iS[id mapsto io1 , ... , iok]|\\
+| iS' = iS[mapsto id (io1 , ... , iok)]|\\
 }
@@
 | filter il (iS(id)) = nil|\\
-| iS' = iS[id mapsto nil]|
+| iS' = iS[mapsto id nil]|
 }
@@
 { 
-|iS' = iS [ id' mapsto nil ]|\\
+|iS' = iS [ mapsto id' nil ]|\\
 |tS' = klone(tS)|\\

### 2014-03-01 paper/retrofit.tex
More notation fixes.

@@
 \inferrule[T-ref]
-{ }
+{ | ap fresh ta | }
 {| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}
-{| fresh ta |}
 
@@
 \inferrule[T-deref]
-{ }
-{| conf tS (!ta) -> conf tS (ap tS ta) |}
+{ |(ta, tv) in tS| }
+{| conf tS (!ta) -> conf tS (tv) |}
 
@@
 \inferrule[T-ass]
-{ |(ta, tv) in tS| }
+{ }
 {| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}
@@
 |itnew = fullconf id' il tS' (TI ie)|\\
-|fresh (id')|
+|ap fresh id'|
 }

### 2014-03-01 paper/concrete.tex
More notation fixes.

@@
       \text{|ie| does not contain any |ta|}\\
-      |iS' = iS [ mapsto id' nil ]|\\
+      |iS' = bracket iS (mapsto id' nil)|\\
       |it1 = oneheapfullconf id il (iniE id')|\\
@@
       |iS(id') = Q|\\
-      |iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
+      |iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
     }

### 2014-03-01 paper/formal.tex
More notation fixes.

@@
   &|erase il emptyset = emptyset|\\
-  &|erase il (iS [mapsto id Q]) =| \begin{cases}
+  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
     |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
     & \text{the label of thread |id|} \\
-    |(erase il iS) [mapsto id (erase il Q)]| & \text{otherwise}
+    |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
   \end{cases} \\

### 2014-03-01 paper/retrofit.tex
More notation fixes.

@@
 { | ap fresh ta | }
-{| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}
+{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
 
@@
 { }
-{| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}
+{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}
 
@@
 Q    ::=  nil | io , Q
-iS   ::=  emptyset | iS [ mapsto id Q ]
+iS   ::=  emptyset | bracket iS (mapsto id Q)
 \end{code}
@@
 |iS(id') = Q|\\
-|iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
+|iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
 }
@@
 | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
-| iS' = iS[mapsto id (io1 , ... , iok)]|\\
+| iS' = bracket iS (mapsto id (io1 , ... , iok))|\\
 }
@@
 | filter il (iS(id)) = nil|\\
-| iS' = iS[mapsto id nil]|
+| iS' = bracket iS (mapsto id nil)|
 }
@@
 { 
-|iS' = iS [ mapsto id' nil ]|\\
+|iS' = bracket iS (mapsto id' nil)|\\
 |tS' = klone(tS)|\\

### 2014-03-01 paper/extensions.tex
Examples
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
points
scheduling policies

@@
-\section{Extensions to the IFC language}
+\section{Extensions and Limitations}
 \label{sec:extensions}
-\cut{
 
-The good thing about our approach is that we are indifferent to the
-functionality implemented in the IFC language: as long as you can
-prove termination sensitive non-interference with the IFC language
-\Red{What is the IFC language? Make sure it is written down}, you
-can combine it with another target language.  In this section,
-we briefly review various extensions you can make to the base IFC
-language to provide IFC-aware versions of target language features.
+In this section we consider several extensions to our IFC system.
+%
+Specifically, we discuss how the specification language can be
+extended to consider other IFC-aware features (e.g., fine-grained
+labeled values), a static type system, or more complex scheduling
+policies.
+%
+When considering these extensions we also highlight some limitations
+of our approach.
 
-}
+\subsection{IFC-aware language features}
+\label{sec:extensions:labeled}
+
+\subsubsection{Labeled objects}
+
+\paragraph{Labeled values}
+\paragraph{Labeled references}
+\paragraph{Labeled synchronization primitives}
+\subsubsection{Privileges}
+\subsubsection{Clearance}
 
 \subsection{Type safety}
+\label{sec:extensions:types}
 
@@
 \end{itemize}
+
+\subsection{Safe scheduling policies}
+Our specification language is parametrized by a scheduling policy
+|alpha|, which maps a task list to a potentially different task list.
+%
+As previously discussed, the precise definition of |alpha|
+dictates whether the language is TSNI, TINI, or neither.
+%
+For simplicity we considered two popular policies |roundrobinf| and
+|seqf| for which we showed TSNI and TINI, respectively.
+%
+However, our definitions allow for other scheduling policies that only
+rely on the current task list.
+%
+For example, this allows us to implement the scheduler of~\tocite{}
+that always schedules less sensitive threads first; this can be
+employed to address external timing covert channels where an attacker
+can measure the delay between output events.\footnote{
+  When considering a label lattice that is not totally ordered, e.g.,
+  DCLabels~\tocite{}, this scheduling policy is considerably more
+  complex. See~\tocite{}.
+}
+%
+More generally, we belove that deterministic schedulers that always
+make ``low-progress,'' i.e., if a task whose label is not above the
+current task's label will will eventually run, and do not decide which
+low tasks to schedule according to data more sensitive than the tasks'
+label, i.e., the scheduler does not schedule one public thread over
+another according to sensitive data, to be safe.
+%
+We leave the proof of this claim to future work.
+%
+
+Despite allowing a number of practical schedulers to be expressed, our
+scheduler parametrization is limited.
+%
+For instance, since |alpha| is a map on task lists, schedulers
+that rely on the global state |iS|, or previous task configurations
+cannot be expressed.
+%
+Though, we do not belove this to be a fundamental limitation, our
+current formalization cannot directly be applied to more-powerful, but
+safe, scheduling policies, as considered in~\tocite{}.
+
+\subsection{Other target languages}
+
+\subsubsection{External effects}
+\label{sec:extensions:external}
+Application specific, use XHR as driving example.
+General way to think of safety is internalize and treat as a labeled
+object; or message to thread that has access to unsafe API, but
+exposes labeled safe messaging API.
+
+\cut{
+
+The good thing about our approach is that we are indifferent to the
+functionality implemented in the IFC language: as long as you can
+prove termination sensitive non-interference with the IFC language
+\Red{What is the IFC language? Make sure it is written down}, you
+can combine it with another target language.  In this section,
+we briefly review various extensions you can make to the base IFC
+language to provide IFC-aware versions of target language features.
+
+}
+\begin{itemize}
+\item Label transition systems.
+\item Non-deterministic reduction.
+\end{itemize}

### 2014-03-01 paper/extensions.tex
note on non-deterministic schedulers

@@
 %
-More generally, we belove that deterministic schedulers that always
+More generally, we believe that deterministic schedulers that always
 make ``low-progress,'' i.e., if a task whose label is not above the
@@
 %
-For instance, since |alpha| is a map on task lists, schedulers
-that rely on the global state |iS|, or previous task configurations
-cannot be expressed.
+For instance, since |alpha| is a map on task lists, schedulers that
+rely on the global state |iS| or previous task configurations cannot
+be expressed.
 %
-Though, we do not belove this to be a fundamental limitation, our
+Though, we do not believe this to be a fundamental limitation, our
 current formalization cannot directly be applied to more-powerful, but
 safe, scheduling policies, as considered in~\tocite{}.
+%
+More fundamentally, our definitions rely on deterministic relations,
+and thus extending the system to consider non-deterministic schedulers
+is non-trivial.
+%
+For instance, this may potentially require the security condition to
+consider \emph{low-determinism}, which states that a program is secure
+only if |l|-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers
 

### 2014-03-01 paper/extensions.tex
I don't think we can consider langs with non-derministic relations, in general
external effects

@@
 
-\subsection{Safe scheduling policies}
+\subsection{Scheduling policies}
 Our specification language is parametrized by a scheduling policy
@@
 
+\subsubsection{External effects}
+\label{sec:extensions:external}
+Our embedding assumes that the target language not have any
+primitives that can external-world effects.
+%
+Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
+when considering real languages is precisely imposing this restriction
+on the concrete implementation.
+%
+Yet, external effects are crucial when implementing more complex
+real-world applications.
+%
+For example, code in our modified IFC browser must load resources or
+perform XHR to be useful.
+
+Like labeled references, features with external effects must be
+modeled in the IFC language; we must reason about the precise security
+implications of features that otherwise inherently leak data.
+%
+Previous approaches have modeled external effects by internalizing the
+effects as writes/reads to labeled channels/references~\tocite{}.
+%
+An alternative approach is to model such effects as messages to/from
+certain labeled tasks.
+%
+These ``special'' tasks are trusted with access to the unlabeled
+primitives that can be used to perform the external effects; since the
+interface to these tasks is already part of the IFC language, the
+proof only requires showing that this task does not leak information.
+%
+This latter approach of wrapping unsafe primitives is, for example,
+used in SWAPI to allow for controlled network communication.
+%
+By wrapping the default XHR object, for example, we can allow code
+to communicate with hosts according to the task's current label.
+
 \subsection{Other target languages}
 
-\subsubsection{External effects}
-\label{sec:extensions:external}
-Application specific, use XHR as driving example.
-General way to think of safety is internalize and treat as a labeled
-object; or message to thread that has access to unsafe API, but
-exposes labeled safe messaging API.
+Non-deterministic reduction.
 
@@
 }
-\begin{itemize}
-\item Label transition systems.
-\item Non-deterministic reduction.
-\end{itemize}

### 2014-03-01 paper/real.tex
external effects

@@
 
-\Red{
-EZY:  This seems like useless detail about the SWAPI implementation
-that is not relevant to this paper.
-
-Of course, simply disallowing all external effects for all browsing
-contexts would break most of the Web.
-%
-Hence SWAPI only enforces IFC, and thus restricts external effects,
-when the JS code uses the new API.\footnote{
-  Once a piece of code ``opts-in'' to use our IFC API, in addition to
-  restricting external effects we interpose ``standard''
-  \texttt{postMessage} communication to ensure that no information is
-  leaked between contexts that have opted-in and those that have not.
-}
-%
-Moreover, rather than disallowing all external effects, SWAPI allows
-controlled network communication by leveraging the fact that web
-pages already have an accompanying security policy: the same origin
-policy.
-%
-Hence, for example, a Worker that has read data only sensitive to
-\texttt{http://bank.ch} can communicate with this domain; only once
-\texttt{http://aws.com} data is also included in the context will all
-network requests be blocked.
-%
-Of course, this requires that we use a concrete label format to
-express the policies; we refer the interested reader to~\tocite{} for
-more details.}
+%% \Red{
+%% EZY:  This seems like useless detail about the SWAPI implementation
+%% that is not relevant to this paper.
+%% 
+%% Of course, simply disallowing all external effects for all browsing
+%% contexts would break most of the Web.
+%% %
+%% Hence SWAPI only enforces IFC, and thus restricts external effects,
+%% when the JS code uses the new API.\footnote{
+%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
+%%   restricting external effects we interpose ``standard''
+%%   \texttt{postMessage} communication to ensure that no information is
+%%   leaked between contexts that have opted-in and those that have not.
+%% }
+%% %
+%% Moreover, rather than disallowing all external effects, SWAPI allows
+%% controlled network communication by leveraging the fact that web
+%% pages already have an accompanying security policy: the same origin
+%% policy.
+%% %
+%% Hence, for example, a Worker that has read data only sensitive to
+%% \texttt{http://bank.ch} can communicate with this domain; only once
+%% \texttt{http://aws.com} data is also included in the context will all
+%% network requests be blocked.
+%% %
+%% Of course, this requires that we use a concrete label format to
+%% express the policies; we refer the interested reader to~\tocite{} for
+%% more details.}

### 2014-03-01 paper/related.tex
I don't think we can consider langs with non-derministic relations, in general
Related work, pass

@@
 
-Our paper follows a long tradition of papers on information flow
-control.  Our information flow control system is mostly closely related
+% Local Variables:
+% TeX-master: "main.lhs.tex"
+% TeX-command-default: "Make"
+% End:
+
+%Our paper follows a long tradition of papers on information flow
+%control.  
+Our information flow control system is closely related
 to the coarse-grained information systems used in operating systems such
-as Asbestos~\cite{efstathopoulos:asbestos} and
-HiStar~\cite{Zeldovich:2006}, as well as language-level
+as Asbestos~\cite{efstathopoulos:asbestos}, 
+HiStar~\cite{Zeldovich:2006}, and Flume~\cite{krohn:flume}, as well as language-based
 \emph{floating-label IFC systems} such as LIO~\cite{lio},
-Breeze~\cite{Hritcu:2013:YIB:2497621.2498098}, where there is a label
-associated with threads of execution which increases monotonically.
+and Breeze~\cite{Hritcu:2013:YIB:2497621.2498098}, where there is a
+monotonically increased label
+associated with threads of execution.
 Our treatment of termination-sensitive and termination-insensitive interference
 originates from Smith and Volpano~\cite{Smith:Volpano:MultiThreaded,Volpano:1997:ECF:794197.795081}.
-While this work often considers the interaction of information flow
-control with respect to various language features (e.g.,
-exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}), none of these
-systems attempt to be generic in the choice of target language.
+%While this work often considers the interaction of information flow
+%control with respect to various language features (e.g.,
+%exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}), none of these
+%systems attempt to be generic in the choice of target language.
 
-One of the primary motivations behind this paper is constructing a
-practical information flow control system for JavaScript.  Some of
-these systems attempt to perform fine-grained information flow of
-JavaScript, e.g. Hedin and Sabelfield's work~\cite{Hedin:2012} on JSFlow~\cite{JSFlow}
-and \Red{some other stuff here}.  While fine-grained information flow
-control can result in very precise analysis of legacy code, it comes
-at the cost of high theoretical complexity (the system must accomodate
-the entirety of JavaScript's semantics) and runtime performance cost.
-There are attempts to overcome this performance barrier by various means:
-Austin and Flanagan~\cite{Austin:Flanagan:PLAS09} handle this problem
-by using a \emph{sparse information labeling} scheme which reduces the
-cost of managing labels when they are not needed, while FlowFox~\cite{DeGroef:2012}
-uses an entirely different technique of \emph{secure multi-execution} to
-enforce non-interference. \Red{Probably more stuff here.}
+Designed to target legacy code, secure multi-execution (SME) is a black-box
+technique to enforce information-flow control~\cite{Devriese:2010}. It runs
+multiple copies of the program, one per security level, where the semantics of
+I/O interactions is altered. Besides its black-box nature, authors often present
+it considering one specific programming
+language~\cite{KULeuven-350547,Rafnson:2013}. Differently, Bielova
+al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
+details of the underlying language is hidden.  Zanarini et
+al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
+interaction trees~\cite{jacobs-tutorial}, which threats programs as black-boxes
+about which nothing is known except what is inferred from their I/O interactions
+with the environment. Similar to SME, our approach only mediates some I/O
+operations; differently, it runs the program once.
+
+One of the primary motivations behind this paper is constructing a practical
+information flow control system for JavaScript.  Some of these systems attempt
+to perform fine-grained information flow of
+JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
+control can result in less false alarms and target legacy code, it comes at the
+cost of complexity (the system must accomodate the entirety of JavaScript's
+semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
+higher than 100\%!\cite{JSFlow}.  Alternatively, coarse-grained approaches have
+also been proposed for the web
+scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. Different
+from them, we rely on programming level abstraction to isolate
+computations.
+
+%There are attempts to overcome this performance barrier by various means:
+%Austin and Flanagan~\cite{Austin:Flanagan:PLAS09} handle this problem
+%by using a \emph{sparse information labeling} scheme which reduces the
+%cost of managing labels when they are not needed, while FlowFox~\cite{DeGroef:2012}
+%uses an entirely different technique of \emph{secure multi-execution} to
+%enforce non-interference. \Red{Probably more stuff here.}
+%\todo{ds}{SME works for arbitrary language (kind of).}
 
@@
 inter-thread communication, is reminiscent of distributed systems
-like Erlang.~\cite{Armstrong03makingreliable}  There is a close
+like Erlang~\cite{Armstrong03makingreliable}.  There is a close
 correspondence: in distributed systems, isolation is required due to
@@
 
-There appears to be limited literature in general techniques for
-retrofitting information flow control to arbitrary languages; however,
-one time-honored technique is defining a fundamental calculus, for which
-other languages can be desugared into.  Abadi et al.~\cite{abadi+:core}
-motivate their core calculus of dependency by showing how various
-previous systems can be encoded in it; Tse and
-Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus
-can be encoded in System F via parametricity.  However, this work is
-primarily focused on static information flow control systems.
+There appears to be limited literature in general techniques for retrofitting
+information flow control to arbitrary languages; however, one time-honored
+technique is defining a fundamental calculus, for which other languages can be
+desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
+dependency by showing how various previous systems can be encoded in it; Tse and
+Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
+encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
+encodes several IFC systems into Paralocks.  However, this line of work is
+primarily focused on static enforcements. 
+%information flow control systems.
 
@@
 al.~\cite{abadi+:core} to structure access to private data by protecting
-it using a lattice of monads, one per security level.  Our system uses
+it using a lattice of monads, one per security level. Russo et. al.~\cite{Russo+:Haskell08} extend this 
+idea to languages with side-effects. Our system uses
 monads in a conceptually different manner, where there is a single monad
 representing the information flow control computational effects; this
-is inline with the use of monads in other systems.~\cite{Harrison05,lio,Devriese:2011}.
-Devriese and Piessens~\cite{Devriese:2011} utilized monad
+is inline with the use of monads in other systems~\cite{Harrison05,lio,Devriese:2011}.
+Devriese and Piessens~\cite{Devriese:2011} utilize monad
 transformers as an essential component in their work.  However, their use
@@
 which is preserved through monad transformer application.  However, it is not
-clear what the relationship between this notion and traditional noninterference is,
-and in their paper they prove only a weaker property of no write down.
+clear what is the relationship between this notion and traditional noninterference,
+and their paper only proves a weaker property of no write down.
 

### 2014-03-02 paper/formal.tex
pass over section 3

@@
 %
-Concretely, we show that |specLang alpha targetLang| for an appropriate
-scheduler, satisfies non-interference~\tocite{},
+Concretely, we show that |specLang alpha targetLang| for, appropriate
+scheduler, satisfies non-interference~\cite{Goguen82},
 without making any reference to properties of |targetLang|.
 %
-As it turns out, the precise scheduling policy |alpha| dictates
-whether or not the guarantee holds for programs with diverging tasks.
-For a sequential scheduler, we will only be able to show
+%As it turns out, 
+The precise scheduling policy |alpha| dictates
+the guarantee holding for programs with diverging tasks.
+For a sequential scheduler |seqf|, we will only be able to show
 \emph{termination-insensitive non-interference}, where a program
@@
 secrets by observing the termination of tasks.
-For the concurrent round-robin schedule,
+For the concurrent round-robin schedule |roundrobinf|,
 we can show a stronger result known as
@@
 
-How can we characterize what the \emph{secret inputs} of a program
-are?  Like other work,~\tocite{} we specify and prove
-non-interference using \emph{term erasure}.
+How can we characterize what the \emph{secret inputs} of a program are?  Like
+other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
+we specify and prove non-interference using \emph{term erasure}.
 %
-Intuitively, in this approach we proving that an attacker does not learn
-any sensitive information from a program by 
-Intuitively, term erasure allows us to show that a an
-attacker does not learn any sensitive information from a program if the
-program behaves identically to a program with all sensitive data ``erased''.
+%Intuitively, we prove that an attacker does not learn
+%any sensitive information from a program by 
+Intuitively, term erasure allows us to show that a an attacker does not learn
+any sensitive information from a program if the program behaves identically
+(from the attacker point of view) to a program with all sensitive data
+``erased''.
 %
@@
 
+\Red{should be the environment colored in the definition?}
 \begin{definition}[Information flow control language]
@@
     \subseteq |C|$ for which there are no possible further transitions.
+    \Red{It is a bit odd to extend a tuple ``sometimes'' and a |V| appears like from
+      nowhere. What about saying: Sometimes, we refer as |V| to set of 
+     terminal configurations in |C|, i.e., configurations states where
+     no further transitions are possible. If you agree, then the next sentence
+     where you said |V = ...| must be removed.}
 \end{definition}
@@
 Since our erasure function captures the attacker model, we simply define this
-equivalence as the syntactic-equivalence of erased configurations.
+equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
 %
@@
 configuration that is |l|-equivalent to the first resultant configuration.
-\Red{TODO: Do we want a commutative diagram to illustrate this?}
+\Red{TODO: Do we want a commutative diagram to illustrate this? Ale: I don't
+  think so, it is quite standard}
 
-We now show that our IFC language satisfies TSNI under a particular
-scheduling policy.
+We now show that our IFC language satisfies TSNI %under a particular
+%scheduling policy.
 %
-Specifically, we consider the language under the round-robin scheduler
+%Specifically, we consider the language 
+under the round-robin scheduler
 |roundrobinf| given in Figure~\ref{fig:scheduler}.
@@
 sensitive threads current state when deciding which thread to schedule next
-will in general not satisfy TSNI.
+will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
 %
@@
 \begin{code}
-ic1 = iS ; fullconf 1 sec tS1 (IT(when false diverge)),  fullconf 2 pub tS1 ie
-ic2 = iS ; fullconf 1 sec tS1 (IT(when true diverge)),   fullconf 2 pub tS2 ie
+ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
+ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
 \end{code}
-These two configurations are |pub|-equivalent, but |ic1| will reduce (in two
-steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
+\Red{Ale: |when| was not defined, so I changed it to if-then-else}
+These two configurations are |pub|-equivalent, but |ic1| will reduce 
+(in two steps) 
+to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
 any progress.
@@
 non-interference (TINI).  This property can also be upheld by sequential languages at the cost
-of leaking one bit through (non)-termination.
+of leaking through (non)-termination~\cite{Askarov:2008}.
 %
@@
 
-Nevertheless, we believe TINI to be a useful for many scenarios and thus we
-show that our IFC language with the sequential scheduling policy |seqf|
-satisfies TINI.
+As shown by compilers~\cite{jif,FlowCaml}, interpreters~\cite{JSFlow}, and
+libraries~\cite{Russo+:Haskell08,lio}, TINI is useful for sequential
+settings. We show that our IFC language with the sequential scheduling policy
+|seqf| satisfies TINI.
 %
@@
 \end{theorem}
+
+% Local Variables:
+% TeX-master: "main.tex"
+% TeX-command-default: "Make"
+% End:

### 2014-03-02 paper/related.tex

@@
 
-Designed to target legacy code, secure multi-execution (SME) is a black-box
-technique to enforce information-flow control~\cite{Devriese:2010}. It runs
+One information flow control technique designed to handle legacy code is
+secure multi-execution (SME)~\cite{Devriese:2010}. It runs
 multiple copies of the program, one per security level, where the semantics of
-I/O interactions is altered. Besides its black-box nature, authors often present
-it considering one specific programming
-language~\cite{KULeuven-350547,Rafnson:2013}. Differently, Bielova
+I/O interactions is altered. Authors often present
+SME considering one specific programming
+language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova
 al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
@@
 al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
-interaction trees~\cite{jacobs-tutorial}, which threats programs as black-boxes
+interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
 about which nothing is known except what is inferred from their I/O interactions
-with the environment. Similar to SME, our approach only mediates some I/O
-operations; differently, it runs the program once.
+with the environment. Similar to SME, our approach mediates I/O
+operations; however, our approach only runs the program once.
 
@@
 semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
-higher than 100\%!\cite{JSFlow}.  Alternatively, coarse-grained approaches have
+higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
 also been proposed for the web
-scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. Different
+scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. \Red{Different
 from them, we rely on programming level abstraction to isolate
-computations.
+computations.}
 

### 2014-03-02 paper/abstract.tex
Abstract
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{abstract}
    Many important security problems in JavaScript, including extension
    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
    XXX~\tocite{}, could be solved with a implementation
    of information flow control.  However, designing an IFC system which
    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
    we formally describe a coarse-grained IFC system which fulfills this
    criterion.  The key idea is that an efficient IFC system must not
    depend too much on the details of the language it is integrated
    with.  The result is a general method for adding IFC to existing
    languages which is indifferent to the choice of language.
    Additionally, we describe how to relate concrete implementations
    with the IFC systems produced by our technique and show how various
    proposed and existing IFC systems fit into our formal framework.
\end{abstract}

### 2014-03-02 paper/intro.tex
Abstract
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
+\Red{
+    \begin{itemize}
+        \item Complex software systems are composed of modules of different provenance
+        \item Web applications have profilerated..components reuse libraries but also network accessible components
+        \item IFC is a promising approach to preserving confidentiality
+        \item Covert channels arise when programming features are misused to leak information
+    \end{itemize}
+
+Information flow control (IFC) has been shown to be useful in a variety
+of settings, with applicability to web applications~\tocite{}, operating systems~\tocite{},
+machine architectures~\tocite{}, and other contexts.  To this end, signifant research
+has been devoted to adding IFC to various programming languages and systems.
+}
+
 Information flow control (IFC) is a promising technique to enforce
 security policies by tracking the flow of sensitive data through
-a system.  The idea is to prevent the leaking of secret or sensitive
+a system.  The usual policy one enforces prevent the leaking of secret or sensitive
 data into public channels by enforcing the notion of non-interference.

### 2014-03-02 paper/extensions.tex
wip

@@
 \subsubsection{Privileges}
+Decentralized IFC extends IFC with the decentralized label model of
+Myers and Liskov~\cite{myers:dlm} to allow for more general
+applications, including systems consisting of mutually distrustful
+parties.  In a decentralized system, a computation is executed with a
+set of \emph{privileges}, which, when exercised, allow the computation
+to declassify data (e.g., by lowering the current label).
+%
+Practical IFC systems
+(e.g.,~\cite{Zeldovich:2006, lio,
+Hritcu:2013:YIB:2497621.2498098,myers:jif}) rely on privileges to
+implement many applications.
+
+Both the LIO and SWAPI implementations already support such features.
+%
+Extending our calculus to consider privileges
+%
+The challenge with such an extension, however, lies in the precise
+security guarantees that must be proved.
+%
+
 \subsubsection{Clearance}

### 2014-03-02 paper/abstract.tex
Italics.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
mashup
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
-    XXX~\tocite{}, could be solved with a implementation
+    mash-up security~\tocite{}, could be solved with a implementation
     of information flow control.  However, designing an IFC system which
@@
     depend too much on the details of the language it is integrated
-    with.  The result is a general method for adding IFC to existing
-    languages which is indifferent to the choice of language.
+    with.  The result is a \emph{general} method for adding IFC to existing
+    languages which is \emph{indifferent} to the choice of language.
     Additionally, we describe how to relate concrete implementations

### 2014-03-02 paper/extensions.tex
privs

@@
 (e.g.,~\cite{Zeldovich:2006, lio,
-Hritcu:2013:YIB:2497621.2498098,myers:jif}) rely on privileges to
+Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
 implement many applications.
-
-Both the LIO and SWAPI implementations already support such features.
 %
-Extending our calculus to consider privileges
+Since both the LIO and SWAPI implementations already support such features,
+we believe that extending our calculus to consider privileges is
+straight forward.
 %
-The challenge with such an extension, however, lies in the precise
+However, the challenge with such an extension lies in the precise
 security guarantees that must be proved.
 %
+Addressing this problem is a natural direction for this work.
 

### 2014-03-02 paper/extensions.tex
non-deterministic langs

@@
 and thus extending the system to consider non-deterministic schedulers
-is non-trivial.
+(or even non-deterministic target languages) is non-trivial.
 %
@@
 to communicate with hosts according to the task's current label.
-
-\subsection{Other target languages}
-
-Non-deterministic reduction.
-
-\cut{
-
-The good thing about our approach is that we are indifferent to the
-functionality implemented in the IFC language: as long as you can
-prove termination sensitive non-interference with the IFC language
-\Red{What is the IFC language? Make sure it is written down}, you
-can combine it with another target language.  In this section,
-we briefly review various extensions you can make to the base IFC
-language to provide IFC-aware versions of target language features.
-
-}

### 2014-03-02 paper/extensions.tex
clearance

@@
 \paragraph{Labeled synchronization primitives}
-\subsubsection{Privileges}
+
+\paragraph{Privileges}
 Decentralized IFC extends IFC with the decentralized label model of
@@
 
-\subsubsection{Clearance}
+\paragraph{Clearance}
+%
+LIO, SWAPI, and Breeze additionally provide a discretionary access
+control mechanism---called \emph{clearance}---at the language
+level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}; this mechanisms is
+used to restrict a computation from accessing data (or communicating
+with entities) above a specified label, the clearance.
+%
+For simplicity, we omitted clearance from our formalism.
+%
+We only remark that the mechanism generalizes beyond these IFC systems
+in a straight forward manner and does not affect our definitions or
+proofs in any meaningful way.
 

### 2014-03-02 paper/intro.tex
More intro stuff
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-01 paper/intro.tex
@@
 
-Information flow control (IFC) is a promising technique to enforce
-security policies by tracking the flow of sensitive data through
-a system.  The idea is to prevent the leaking of secret or sensitive
-data into public channels by enforcing the notion of non-interference.
-Significant research has been devoted to adding various
-forms of IFC to different kinds of programming languages and system,
-both static and dynamic in nature.  In this paper we are interested
-in the latter, where an execution monitor ensure at runtime that secret
-information is not revealed through public outputs.
-A key challenge in the design of these dynamic systems has been the
-performance cost incurred by additional security checks.
-Particularly when retrofitting an existing programming language with
-IFC it is tempting to track information flow at a fine-grained level,
-e.g., per value in the system.  This can lead to impractical
-runtime overheads even for ordinary operations.
+A defining aspect of web platforms is the combinability of many
+components of various providence.  This pattern shows up in browser
+extensions, which run JavaScript code alongside third-party website
+code, web applications, which include possibly untrusted third-party
+libraries, and mash-up websites, which combine code and data from
+websites which may not even be aware of each other's existence.  While
+this combinability has offered great flexibility, it also poses a set of
+unique security challenges: in particular, maintaining the privacy of
+data in these settings is difficult, if not impossible.
+
+Information flow control (IFC) is a promising technique for addressing these
+problems, by tracking the flow of sensitive data through a system and
+confining untrusted code so that it cannot exfiltrate data, except as
+per a information flow policy.  Significant research has been devoted to
+adding various forms of IFC to different kinds of programming languages
+and systems.  In the context of the web, however, there is a strong
+motivation to preserve the language JavaScript, and retrofit information
+flow control on top of it.  A key challenge in the design of these
+systems is ensuring they can be implemented efficiently: when the
+semantics specify that information flow must be tracked at a
+fine-grained level, e.g., per value in the system,  it can lead to
+impractical runtime overheads even for ordinary operations.
 

### 2014-03-02 paper/intro.tex
Flow it
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 and systems.  In the context of the web, however, there is a strong
-motivation to preserve the language JavaScript, and retrofit information
+motivation to preserve the language JavaScript, and retrofit dynamic information
 flow control on top of it.  A key challenge in the design of these
@@
 
-An alternative to this is a more \textit{coarse-grained} approach
-to IFC by trading off precision for efficiency.  Here, computational
-units are associated with a floating label which protects all data
-in this unit.
-A recent example dubbed SWAPI adds IFC to the web by extending
-Javascript with coarse-grained IFC by identifying web workers as
-an existing computational unit.  Communication between workers can
-efficiently be mediated in an IFC aware way to ensure a notation
-non-interference, where sensitive workers cannot influence the
-computations in less sensitive workers.
+One alternative is a \textit{coarse-grained} approach to IFC.  Here,
+computational units are associated with a floating label which protects
+all data in this unit.  A recent system named SWAPI adds IFC to the
+browser by identifying \emph{web workers} as an existing computational
+unit.  Communication between workers can efficiently be mediated in an
+IFC aware way to ensure non-interference, where sensitive workers cannot
+influence the computations in less sensitive workers.
 

### 2014-03-02 paper/intro.tex
wc
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
paren
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-A defining aspect of web platforms is the combinability of many
-components of various providence.  This pattern shows up in browser
-extensions, which run JavaScript code alongside third-party website
-code, web applications, which include possibly untrusted third-party
-libraries, and mash-up websites, which combine code and data from
-websites which may not even be aware of each other's existence.  While
+A defining aspect of web platforms is the combinability of
+components of differing providence.  This pattern shows up in browser
+extensions (which run JavaScript code alongside third-party website
+code), web applications (which include possibly untrusted third-party
+libraries), and mash-up websites (which combine code and data from
+websites which may not even be aware of each other's existence.)  While
 this combinability has offered great flexibility, it also poses a set of

### 2014-03-02 paper/retrofit.tex
Fix many notational issues and other things in retrofit.

@@
 in the style of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220}.  This procedure will
+Findler~\cite{Matthews:2007:OSM:1190216.1190220},
+and for simplicity, we require the semantics to be deterministic.
+This procedure will
 equip the target language with primitives for implementing dynamic
@@
 with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
-a color copy of this paper, where target language nonterminals are colored red
-while IFC language nonterminals are colored blue.
+a color copy of this paper, where target language nonterminals are colored \textbf{{\color{red} red}}
+while IFC language nonterminals are colored \textit{{\color{blue} blue}}.
 
@@
 In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
-mutable references and errors, prepared for combination with an
+mutable references, prepared for combination with an
 information flow control language.  The presentation is standard, but it
@@
 context |tE|; however, the evaluation rules have been expressed in terms
-of a different evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  To
+of a different evaluation context |curlyRedE|,
+following the approach of Matthews and
+Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
+semantics of multiple languages.  To
 derive the usual operational semantics for this language, the evaluation
-context merely needs to be defined as |conf tS te @= tS, tE[ te ]|.
+context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
 However, when we combine this language with an IFC language, we must
@@
 of some global machine state |tS|, some evaluation context |tE|,
-some expressions |te|, some set of values |tv| and a reduction
-relations on full configurations $|tS| \times |tE| \times |te|$.
+some expressions |te|, some set of values |tv| and a deterministic
+reduction relation on full configurations $|tS| \times |tE| \times |te|$.
 
@@
 
-\and
 \inferrule[T-app]
@@
 \inferrule[T-deref]
-{ |(ta, tv) in tS| }
+{ |memberf (ta, tv) tS| }
 {| conf tS (!ta) -> conf tS (tv) |}
@@
 with data, which encodes a policy of whether or not data tagged with one
-label can flow to another label (written as |canFlowTo|).
-Since our embedding is agnostic
-to the choice of labeling scheme, we simply represent labels with the metavariable
+label |l1| can flow to another label |l2| (written as |canFlowTo2 l1 l2|).
+Our embedding is agnostic to the choice of labeling scheme; we only
+require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
+with the partial order |canFlowTo|.
+In this paper, we simply represent labels with the metavariable
 $l$, but do not discuss them in more detail.
@@
 evaluation rules for a minimal information-flow control language.  The
-evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
+evaluation context |curlyBlueE| represents the context
 of the current task which is running, including on the right-hand side
-the current label $l$ (which protects the program counter of the task)
-and the task ID $i$.
+the current label |il| (which protects the program counter of the task)
+and the task ID |id|.
 
@@
 
-The form of \textbf{send}/\textbf{recv} are \Red{inspired by methods of inter-worker communication
-in web browser APIs} \Red{cite}, however in Section~\ref{sec:extensions} we
-discuss other possible choices for information flow control aware communication
-primitives.  Their rules are different from non-IFC systems
-and worth commenting on: when a task places
-a message on the message queue of receiving task, it also labels that
-message with a label |il'| (which must be above the tasks current label |il|)
-When the recipient reads out messages from its queue,
-messages whose labels do not
-flow to |il| are filtered out (denoted by |filter il Q|).
-Specifically, if |Q| is the empty list |nil|, the
+We consider asynchronous communication primitives that allow different
+tasks to exchange messages.
+When a task is sending a message using |send|, it also labels that
+message with a label |il'| (which must be above the tasks current label |il|).
+Now, messages can only be received by a task if its current label is
+at least as high as the label of the message.
+
+Specifically, receiving a message using
+\[ |recvf ix1 ix2 ie1 ie2| \]
+binds the senders task identifier and the message
+to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
+Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
+and that tasks continues its execution with |ie2|.
+We denote the filtering of the message queue by |filter il Q|,
+which is defined as follows.
+If |Q| is the empty list |nil|, the
 function is simply the identity function, i.e.,
@@
 than their current label would allow.
+
+The particular choice of communication primitives has been motivated by
+inter-worker communication in web browser APIs~\Red{cite}, but
+other choices such as blocking communication or labeled channels
+would also be possible.
 
@@
 iv   ::=  id | il | true | false | unit
-ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
-       |  sandbox ie | send ie ie ie | ix1, ix2 <= recv. ie ie
+ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie | getTaskId
+       |  sandbox ie | send ie ie ie | recvf ix ix ie ie
 iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE
        |  send iE ie ie | send iv iE ie | send iv iv iE
-       |  ix1, ix2 <= recv. ie ie
 io   ::=  (il, id ie)
@@
 \begin{mathpar}
+
+\inferrule[I-getTaskId]
+{ }
+{|
+niconf iS id il getTaskId
+->
+niconf iS id il id
+|}
 
@@
 |iS(id') = Q|\\
-|iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
+|iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
 }
 {|
-niconf iS  id il (send id' il' ie)
+niconf iS  id il (send id' il' iv)
 ->
@@
 {
-| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
+| (filter il (iS(id))) = io1 , ... , iok , (il', id', iv)|\\
 | iS' = bracket iS (mapsto id (io1 , ... , iok))|\\
@@
 {|
-niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
+niconf iS  id il (recvf ix1 ix2 ie1 ie2)
 ->
-niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
+niconf iS' id il ({iv/ix1,id'/ix2} ie1)
 |}
@@
 {|
-niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
+niconf iS  id il (recvf ix1 ix2 ie1 ie2)
 ->
@@
   - fix the toLabled
-  - add taskIDs to ruls
 }
@@
 .->
-iS'; sched F (it1, ldots, itnew)
+iS'; sched box (it1, ldots, itnew)
 |}
@@
 .->
-iS ; sched D (fullconf id il tS iv, ldots)
+iS ; sched done (fullconf id il tS iv, ldots)
 |}
@@
 .->
-iS ; sched N (it, ldots)
+iS ; sched nostep (it, ldots)
 |}
@@
     \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.
-These rules only operate on the first task in the task pool, which by convention, is the only task executing.
+    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for |curlyRedE| and |curlyBlueE|.
+These rules only operate on the first task in the task pool, which by convention is the only task executing.
     \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.
-The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.
-Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
-    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
+The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy |alpha|.
+Not all schedulers preserve non-interference, and we provide two specific schedules in Figure~\ref{fig:scheduler}.
+    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
+    primitives for asynchronously communicating between
+    tasks and intermediating between the borders of the two languages.
 \end{itemize}
 
-The \textsc{I-sandbox} rule is of particular interest, as it is intended to allow users
-to create new tasks.  When a new task is created, there is a question of what the
-global state of the new task should be; this is defined in terms of a function $\kappa$.
-Conservatively, $\kappa$ may be simply thought of as the identity function, in which
+The \textsc{I-sandbox} rule allows to create a new isolated task that
+executes separately from the existing tasks (and can be communicated
+with via |send| and |recv|).  When the new task is created, there
+is the question of what the target language state of the new task should
+be.  Our rule is stated generically in terms of a function |klone|.
+Conservatively, |klone| may be simply thought of as the identity
+function, in which
 case the semantics of sandbox are such that the state of the target language is \emph{cloned}
-when sandboxing occurs.  However, this is not necessary: it is also valid for $\kappa$
+when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
 to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
-discussion of the implications of the choice of $\kappa$.
+discussion of the implications of the choice of |klone|, but all our
+non-interference claims will hold regardless of the choice of |klone|.
 

### 2014-03-02 paper/concrete.tex
Fix notation in concrete.

@@
       \text{|ie| does not contain any |ta|}\\
-      |il canFlowTo il'|\\
+      |canFlowTo2 il il'|\\
       |iS(id') = Q|\\

### 2014-03-02 paper/concrete.tex
Comments on section 4, small changes

--- 2014-03-01 paper/concrete.tex
@@
 We achieve this general statement that works for a large class of
-languages by having different task execute completely isolated from
+languages by having different tasks executing completely isolated from
 each other, such that every task has its own state.
@@
 by using one global heap, but conceptually maintain isolation between
-task by not allowing sharing of references between tasks.
+task by not allowing sharing of references between them.
 This intuition of having a different (potentially more efficient)
@@
 
+\Red{the next paragraph needs some rephrasing. We should say that if we 
+condense everything into one environment, then we need to ``simulate'' 
+the different policies. A bit more intro}
 A na\"ive attempt at our single heap semantics
@@
 
-Again we are modifying the IFC language semantics in a non-trivial way,
+Again, we are modifying the IFC language semantics in a non-trivial way,
 which begs the question whether non-interference is preserved.
-Note that restricting the transitions in an information flow control
+Restricting the transitions in an information flow control
 system in general does not preserve non-interference as the following
-minimal example illustrates.
+minimal example illustrates. \Red{Ale: I am not sure that the example is clear,
+  too abstract, at least, I don't get it. Propose to remove it, and just say 
+the top level idea: ``the restriction should not be based on secret data!''} 
 Consider a trivial state machine as shown
@@
   The reduction rules are restricted
-  by adding a predicate $P$ from $\mathcal P$ to the premise of
+  by adding a predicate $P \in \mathcal P$ to the premise of
   all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
@@
   For any target language |targetLang| and family of predicates
-  $\mathcal{P}$, the IFC language |restrictedLang roundrobinf targetLang|
+  $\mathcal{P}$, the restricted IFC language |restrictedLang roundrobinf targetLang|
   is TSNI.  Furthermore, the IFC language
-  |restrictedLang seqf targetLang| is TSNI.
+  |restrictedLang seqf targetLang| is TINI.
 \end{theorem}
@@
 \textsc{I-fork} and \textsc{I-send}, which we define as
-\[ P = \text{|ie| does not contain any address |ta|} \]
+\[ P(e) = \text{|ie| does not contain any address |ta|} \]
 That is, we do not restrict any rules except for \textsc{I-fork}

### 2014-03-02 paper/intro.tex

@@
 Information flow control (IFC) is a promising technique for addressing these
-problems, by tracking the flow of sensitive data through a system and
-confining untrusted code so that it cannot exfiltrate data, except as
-per a information flow policy.  Significant research has been devoted to
+problems by tracking the flow of sensitive data through a system. Untrusted
+code is confined so that it cannot exfiltrate data, except as
+per an information flow policy.  Significant research has been devoted to
 adding various forms of IFC to different kinds of programming languages

### 2014-03-02 paper/jcm.tex

\documentclass{sigplanconf}
%% ODER: format ==         = "\mathrel{==}"
%% ODER: format /=         = "\neq "
%
%
\makeatletter
\@ifundefined{lhs2tex.lhs2tex.sty.read}%
  {\@namedef{lhs2tex.lhs2tex.sty.read}{}%
   \newcommand\SkipToFmtEnd{}%
   \newcommand\EndFmtInput{}%
   \long\def\SkipToFmtEnd#1\EndFmtInput{}%
  }\SkipToFmtEnd

\newcommand\ReadOnlyOnce[1]{\@ifundefined{#1}{\@namedef{#1}{}}\SkipToFmtEnd}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\DeclareFontFamily{OT1}{cmtex}{}
\DeclareFontShape{OT1}{cmtex}{m}{n}
  {<5><6><7><8>cmtex8
   <9>cmtex9
   <10><10.95><12><14.4><17.28><20.74><24.88>cmtex10}{}
\DeclareFontShape{OT1}{cmtex}{m}{it}
  {<-> ssub * cmtt/m/it}{}
\newcommand{\texfamily}{\fontfamily{cmtex}\selectfont}
\DeclareFontShape{OT1}{cmtt}{bx}{n}
  {<5><6><7><8>cmtt8
   <9>cmbtt9
   <10><10.95><12><14.4><17.28><20.74><24.88>cmbtt10}{}
\DeclareFontShape{OT1}{cmtex}{bx}{n}
  {<-> ssub * cmtt/bx/n}{}
\newcommand{\tex}[1]{\text{\texfamily#1}}	% NEU

\newcommand{\Sp}{\hskip.33334em\relax}

\newcommand{\Conid}[1]{\mathit{#1}}
\newcommand{\Varid}[1]{\mathit{#1}}
\newcommand{\anonymous}{\kern0.06em \vbox{\hrule\@width.5em}}
\newcommand{\plus}{\mathbin{+\!\!\!+}}
\newcommand{\bind}{\mathbin{>\!\!\!>\mkern-6.7mu=}}
\newcommand{\rbind}{\mathbin{=\mkern-6.7mu<\!\!\!<}}% suggested by Neil Mitchell
\newcommand{\sequ}{\mathbin{>\!\!\!>}}
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\usepackage{polytable}

%mathindent has to be defined
\@ifundefined{mathindent}%
  {\newdimen\mathindent\mathindent\leftmargini}%
  {}%

\def\resethooks{%
  \global\let\SaveRestoreHook\empty
  \global\let\ColumnHook\empty}
\newcommand*{\savecolumns}[1][default]%
  {\g@addto@macro\SaveRestoreHook{\savecolumns[#1]}}
\newcommand*{\restorecolumns}[1][default]%
  {\g@addto@macro\SaveRestoreHook{\restorecolumns[#1]}}
\newcommand*{\aligncolumn}[2]%
  {\g@addto@macro\ColumnHook{\column{#1}{#2}}}

\resethooks

\newcommand{\onelinecommentchars}{\quad-{}- }
\newcommand{\commentbeginchars}{\enskip\{-}
\newcommand{\commentendchars}{-\}\enskip}

\newcommand{\visiblecomments}{%
  \let\onelinecomment=\onelinecommentchars
  \let\commentbegin=\commentbeginchars
  \let\commentend=\commentendchars}

\newcommand{\invisiblecomments}{%
  \let\onelinecomment=\empty
  \let\commentbegin=\empty
  \let\commentend=\empty}

\visiblecomments

\newlength{\blanklineskip}
\setlength{\blanklineskip}{0.66084ex}

\newcommand{\hsindent}[1]{\quad}% default is fixed indentation
\let\hspre\empty
\let\hspost\empty
\newcommand{\NB}{\textbf{NB}}
\newcommand{\Todo}[1]{$\langle$\textbf{To do:}~#1$\rangle$}

\EndFmtInput
\makeatother
%
%
%
%
%
%
% This package provides two environments suitable to take the place
% of hscode, called "plainhscode" and "arrayhscode". 
%
% The plain environment surrounds each code block by vertical space,
% and it uses \abovedisplayskip and \belowdisplayskip to get spacing
% similar to formulas. Note that if these dimensions are changed,
% the spacing around displayed math formulas changes as well.
% All code is indented using \leftskip.
%
% Changed 19.08.2004 to reflect changes in colorcode. Should work with
% CodeGroup.sty.
%
\ReadOnlyOnce{polycode.fmt}%
\makeatletter

\newcommand{\hsnewpar}[1]%
  {{\parskip=0pt\parindent=0pt\par\vskip #1\noindent}}

% can be used, for instance, to redefine the code size, by setting the
% command to \small or something alike
\newcommand{\hscodestyle}{}

% The command \sethscode can be used to switch the code formatting
% behaviour by mapping the hscode environment in the subst directive
% to a new LaTeX environment.

\newcommand{\sethscode}[1]%
  {\expandafter\let\expandafter\hscode\csname #1\endcsname
   \expandafter\let\expandafter\endhscode\csname end#1\endcsname}

% "compatibility" mode restores the non-polycode.fmt layout.

\newenvironment{compathscode}%
  {\par\noindent
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \let\hspre\(\let\hspost\)%
   \pboxed}%
  {\endpboxed\)%
   \par\noindent
   \ignorespacesafterend}

\newcommand{\compaths}{\sethscode{compathscode}}

% "plain" mode is the proposed default.
% It should now work with \centering.
% This required some changes. The old version
% is still available for reference as oldplainhscode.

\newenvironment{plainhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\hspre\(\let\hspost\)%
   \pboxed}%
  {\endpboxed%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

\newenvironment{oldplainhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \(\pboxed}%
  {\endpboxed\)%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

% Here, we make plainhscode the default environment.

\newcommand{\plainhs}{\sethscode{plainhscode}}
\newcommand{\oldplainhs}{\sethscode{oldplainhscode}}
\plainhs

% The arrayhscode is like plain, but makes use of polytable's
% parray environment which disallows page breaks in code blocks.

\newenvironment{arrayhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \(\parray}%
  {\endparray\)%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

\newcommand{\arrayhs}{\sethscode{arrayhscode}}

% The mathhscode environment also makes use of polytable's parray 
% environment. It is supposed to be used only inside math mode 
% (I used it to typeset the type rules in my thesis).

\newenvironment{mathhscode}%
  {\parray}{\endparray}

\newcommand{\mathhs}{\sethscode{mathhscode}}

% texths is similar to mathhs, but works in text mode.

\newenvironment{texthscode}%
  {\(\parray}{\endparray\)}

\newcommand{\texths}{\sethscode{texthscode}}

% The framed environment places code in a framed box.

\def\codeframewidth{\arrayrulewidth}
\RequirePackage{calc}

\newenvironment{framedhscode}%
  {\parskip=\abovedisplayskip\par\noindent
   \hscodestyle
   \arrayrulewidth=\codeframewidth
   \tabular{@{}|p{\linewidth-2\arraycolsep-2\arrayrulewidth-2pt}|@{}}%
   \hline\framedhslinecorrect\\{-1.5ex}%
   \let\endoflinesave=\\
   \let\\=\@normalcr
   \(\pboxed}%
  {\endpboxed\)%
   \framedhslinecorrect\endoflinesave{.5ex}\hline
   \endtabular
   \parskip=\belowdisplayskip\par\noindent
   \ignorespacesafterend}

\newcommand{\framedhslinecorrect}[2]%
  {#1[#2]}

\newcommand{\framedhs}{\sethscode{framedhscode}}

% The inlinehscode environment is an experimental environment
% that can be used to typeset displayed code inline.

\newenvironment{inlinehscode}%
  {\(\def\column##1##2{}%
   \let\>\undefined\let\<\undefined\let\\\undefined
   \newcommand\>[1][]{}\newcommand\<[1][]{}\newcommand\\[1][]{}%
   \def\fromto##1##2##3{##3}%
   \def\nextline{}}{\) }%

\newcommand{\inlinehs}{\sethscode{inlinehscode}}

% The joincode environment is a separate environment that
% can be used to surround and thereby connect multiple code
% blocks.

\newenvironment{joincode}%
  {\let\orighscode=\hscode
   \let\origendhscode=\endhscode
   \def\endhscode{\def\hscode{\endgroup\def\@currenvir{hscode}\\}\begingroup}
   %\let\SaveRestoreHook=\empty
   %\let\ColumnHook=\empty
   %\let\resethooks=\empty
   \orighscode\def\hscode{\endgroup\def\@currenvir{hscode}}}%
  {\origendhscode
   \global\let\hscode=\orighscode
   \global\let\endhscode=\origendhscode}%

\makeatother
\EndFmtInput
%

\usepackage{array, amssymb, amsthm, amsmath, mathpartir,thmtools}
\usepackage[usenames,dvipsnames]{color}
\usepackage{tikz}
\newcommand{\Red}[1]{{\color{red} #1}}
\newcommand{\todo}[2]{\Red{\textbf{TODO[}#1\textbf{]:} #2}} % chktex 9
%\newcommand{\todo}[2]{}
\newcommand{\cut}[1]{}
\newcommand{\alphacondition}[1]{{\color{green}Condition for $\alpha$: #1}}

\usepackage{wrapfig}
\usepackage[square,numbers,sort&compress]{natbib}

\newcommand{\tocite}[1]{\Red{\cite{#1}}}
\newcommand{\toref}[1]{\Red{\ref{#1}}}

\usepackage{float}
\newfloat{listing}{htbp}{lop} \floatname{listing}{Listing}

\declaretheorem{theorem}
\declaretheorem[name=Lemma]{lemma}
\declaretheorem[name=Corollary]{corollary}
\declaretheorem[name=Proposition]{proposition}
% thmstyle: definition
\declaretheorem[name=Definition, style=definition]{definition}
\declaretheorem[name=Example, style=definition]{example}
% thmstyle: remark
\declaretheorem[name=Proof sketch, style=remark]{proofsketch}

\begin{document}

% label operation related:
\newcommand{\flows}{\sqsubseteq}
\newcommand{\lub}{\sqcup}
\newcommand{\glb}{\sqcap}

\newcommand{\ifc}[1]{\ensuremath{{\color{blue} #1}}}
\newcommand{\lcurr}{\ensuremath{\ifc{l_{\textrm{cur}}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% state, eval ctx, expression

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% IFC state, eval ctx, expression

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TARGET state, eval ctx, expression
\newcommand{\tar}[1]{\ensuremath{\mathbf{\color{red} #1}}}

%formtt tty'
%formtt tty''
%formtt ttyi = tty"_"i
%formtt ttyi' = tty'"_"i
%formtt ttyi'' = tty''"_"i
%formtt tty1
%formtt tty2
%formtt tty3
%formtt tty1'
%formtt tty2'
%formtt tty3'
%formtt tty1''
%formtt tty2''
%formtt tty3''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% language
\newcommand{\Coloneqq}{::=} % txfonts

%% misc
\newcommand{\dom}[1]{\ensuremath{{\textrm{dom}} #1}}
\newcommand{\fresh}[1]{\ensuremath{\textrm{fresh}(#1)}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Combined state, eval ctx, expression

% Going to use S

%%%%%
%% LANGUAGES

%%%%%
%% From concrete

% ----------
%% \conferenceinfo{ICFP'14,} {September 1--3, 2013, Gothenburg, Sweden.}
%% \CopyrightYear{2014}
%% \copyrightdata{XXX-X-XXXX-XXXX-X/XX/XX}
% ----------

\title{
Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control
}
%   Generic, Efficient, Coarse-grained Information Flow Control
%   IFC For Me
%   Who knew adding IFC could be us easy?
%   Language-polymorphic schemes of dynamic information flow control
%   Target language and IFC language: shake to mix
%   1. Target language, 2. IFC language, 3. ... 4. Profit!!!
%   Just add IFC

\authorinfo{
  Stefan Heule \and
  Deian Stefan \and
  Edward Z. Yang \and
  John C. Mitchell \and
  Alejandro Russo
}{Stanford University, Chalmers University}{
\text{\tt \char123{}sheule\char44{}deian\char44{}ezyang\char44{}mitchell\char125{}\char64{}cs\char46{}stanford\char46{}edu}, \text{\tt russo\char64{}chalmers\char46{}se}
}

\maketitle

\input{abstract}
\input{intro}

\section{Retrofitting languages with IFC}
\label{sec:retrofit}

Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
operational semantics and combine it with an \textit{{\color{blue} information
flow control language}}.  For concreteness, we use a simple, untyped,
ML-like language with mutable references as our target language.
However, our technique will be indifferent to the actual target language
chosen: it need only be prepared for interoperability by being expressed
in the style of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220}.  This procedure will
equip the target language with primitives for implementing dynamic
information control in the style of LIO~\cite{lio}, which we will
describe in more detail shortly.

We have typeset nonterminals of the target language using \textbf{{\color{red}
bold font}} while the nonterminals of the IFC language have been typeset
with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
a color copy of this paper, where target language nonterminals are colored red
while IFC language nonterminals are colored blue.

\subsection{Target language: Mini-ML}

In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
mutable references and errors, prepared for combination with an
information flow control language.  The presentation is standard, but it
is worth paying some attention to the Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
operational semantics of the system.  Our language defines an evaluation
context \ensuremath{\tar{E}}; however, the evaluation rules have been expressed in terms
of a different evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as \ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\tar{\Sigma},\tar{E}\;[\mskip1.5mu \tar{e}\mskip1.5mu]}.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state \ensuremath{\tar{\Sigma}}, some evaluation context \ensuremath{\tar{E}},
some expressions \ensuremath{\tar{e}}, some set of values \ensuremath{\tar{v}} and a reduction
relations on full configurations $\ensuremath{\tar{\Sigma}} \times \ensuremath{\tar{E}} \times \ensuremath{\tar{e}}$.

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\tar{v}{}\<[6]%
\>[6]{}\Coloneqq\lambda \tar{x}.\tar{e}\mid \mathbf{true}\mid \mathbf{false}\mid \tar{a}{}\<[E]%
\\
\>[B]{}\tar{e}{}\<[6]%
\>[6]{}\Coloneqq\tar{v}\mid \tar{x}\mid \tar{e}\;\tar{e}\mid \mathbf{if}\;\tar{e}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}\mid \mathbf{ref}\;\tar{e}\mid \mathbin{!}\tar{e}\mid \tar{e}\mathbin{:=}\tar{e}{}\<[E]%
\\
\>[B]{}\tar{E}{}\<[6]%
\>[6]{}\Coloneqq\tar{[\cdot ]_T}\mid \tar{E}\;\tar{e}\mid \tar{v}\;\tar{E}\mid \mathbf{if}\;\tar{E}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid \mathbf{ref}\;\tar{E}\mid \mathbin{!}\tar{E}\mid \tar{E}\mathbin{:=}\tar{e}\mid \tar{v}\mathbin{:=}\tar{E}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\tar{e}_{1};\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}\;{}\<[40]%
\>[40]{}\mathbf{where}\;{}\<[47]%
\>[47]{}\tar{x}\;\not\in\;\mathcal{FV}\;(\tar{e}_{2}){}\<[E]%
\\
\>[B]{}\mathbf{let}\;\tar{x}\mathrel{=}\tar{e}_{1}\;\mathbf{in}\;\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{mathpar}

\and
\inferrule[T-app]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[(\lambda \Varid{x}.\tar{e})\;\tar{v}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\{\mskip1.5mu \tar{v}\mathbin{/}\Varid{x}\mskip1.5mu\}\;\tar{e}\right]}}

\and
\inferrule[T-ifTrue]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\;\mathbf{if}\;\mathbf{true}\;\mathbf{then}\;\tar{e}_{1}\;\mathbf{else}\;\tar{e}_{2}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}_{1}\right]}}

\and
\inferrule[T-ifFalse]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\;\mathbf{if}\;\mathbf{false}\;\mathbf{then}\;\tar{e}_{1}\;\mathbf{else}\;\tar{e}_{2}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}_{2}\right]}}

\and
\inferrule[T-ref]
{ \ensuremath{\textrm{fresh}(\tar{a})} }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbf{ref}\;\tar{v}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}\left[\tar{a}\mapsto{}\tar{v}\right]}\left[\tar{a}\right]}}

\and
\inferrule[T-deref]
{ \ensuremath{(\tar{a},\tar{v})\;\mathbf{in}\;\tar{\Sigma}} }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbin{!}\tar{a}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{v}\right]}}

\and
\inferrule[T-ass]
{ }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{a}\mathbin{:=}\tar{v}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}\left[\tar{a}\mapsto{}\tar{v}\right]}\left[\tar{v}\right]}}

%\and
%\inferrule[T-fail]
%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
\end{mathpar}

\caption{Simple ML-like language \ensuremath{\Red{\lambda_{\text{ML}}}}}
\label{fig:ml}
\end{figure}

\subsection{IFC language}

Information flow control seeks to enforce a security policy known as
\emph{non-interference}: public results must not depend on secret inputs.
Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
with data, which encodes a policy of whether or not data tagged with one
label can flow to another label (written as \ensuremath{\flows}).
Since our embedding is agnostic
to the choice of labeling scheme, we simply represent labels with the metavariable
$l$, but do not discuss them in more detail.

In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
evaluation rules for a minimal information-flow control language.  The
evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
of the current task which is running, including on the right-hand side
the current label $l$ (which protects the program counter of the task)
and the task ID $i$.

Ordinarily, information flow control languages are defined by directly
stating a base language plus information flow control operators.  In
contrast, our language is purposely minimal: it does not have sequencing
operations, control flow, or other constructs.  However, it contains
support for the following core information flow control features:

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (\ensuremath{\flows}, \ensuremath{\lub} and \ensuremath{\glb}),
    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues \ensuremath{\ifc{\Sigma}}, and
    \item a sandboxing operation allowing to spawn new
    isolated tasks, which will be described in more detail in the
    next section.
\end{itemize}

The form of \textbf{send}/\textbf{recv} are \Red{inspired by methods of inter-worker communication
in web browser APIs} \Red{cite}, however in Section~\ref{sec:extensions} we
discuss other possible choices for information flow control aware communication
primitives.  Their rules are different from non-IFC systems
and worth commenting on: when a task places
a message on the message queue of receiving task, it also labels that
message with a label \ensuremath{\ifc{\Varid{l}}'} (which must be above the tasks current label \ensuremath{\ifc{\Varid{l}}})
When the recipient reads out messages from its queue,
messages whose labels do not
flow to \ensuremath{\ifc{\Varid{l}}} are filtered out (denoted by \ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}}).
Specifically, if \ensuremath{\ifc{\Theta}} is the empty list \ensuremath{\epsilon}, the
function is simply the identity function, i.e.,
\ensuremath{\epsilon\preceq\ifc{\Varid{l}}\mathrel{=}\epsilon}; otherwise:
\[
\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} = \left\{
\begin{array}{l l}
\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{if \ensuremath{\ifc{\Varid{l}}'\;\flows\;\ifc{\Varid{l}}}}\\
\ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more secret
than their current label would allow.

%   \begin{figure}
%   Typing judgment: $|tyrule tG tS te tty|$
%   \begin{mathpar}
%   \inferrule[T-ty-address]
%   {}
%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
%   \end{mathpar}

%   \caption{Selected typing rules for ML-like language}
%   \label{fig:ml-typing}
%   \end{figure}

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}c<{\hspost}@{}}%
\column{6E}{@{}l@{}}%
\column{8}{@{}>{\hspre}c<{\hspost}@{}}%
\column{8E}{@{}l@{}}%
\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\otimes{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\flows\mid \lub\mid \glb{}\<[E]%
\\
\>[B]{}\ifc{\Varid{v}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{i}}\mid \ifc{\Varid{l}}\mid \mathbf{true}\mid \mathbf{false}\mid \langle\rangle{}\<[E]%
\\
\>[B]{}\ifc{\Varid{e}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{v}}\mid \ifc{\Varid{x}}\mid \ifc{\Varid{e}}\;\otimes\;\ifc{\Varid{e}}\mid \mathbf{getLabel}\mid \mathbf{setLabel}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{sandbox}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[B]{}\ifc{E}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{[\cdot ]_I}\mid \ifc{E}\;\otimes\;\ifc{\Varid{e}}\mid \ifc{\Varid{v}}\;\otimes\;\ifc{E}\mid \mathbf{setLabel}\;\ifc{E}\mid \mathbf{sandbox}\;\ifc{E}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{send}\;\ifc{E}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{E}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{\Varid{v}}\;\ifc{E}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[B]{}\ifc{\theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}(\ifc{\Varid{l}},\ifc{\Varid{i}}\;\ifc{\Varid{e}}){}\<[E]%
\\
\>[B]{}\ifc{\Theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\epsilon\mid \ifc{\theta},\ifc{\Theta}{}\<[E]%
\\
\>[B]{}\ifc{\Sigma}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\emptyset\mid \ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right]{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{mathpar}

\and
\inferrule[I-getLabel]
{ }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{getLabel}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{l}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\and
\inferrule[I-setLabel]
{ \ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'} }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{setLabel}\;\ifc{\Varid{l}}'\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}}}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
\ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
}
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\and
\inferrule[I-recv]
{
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{\Varid{l}}\mathrel{=}\ifc{\theta}_{1},\mathbin{...},\ifc{\theta}_\Varid{k},(\ifc{\Varid{l}}',\ifc{\Varid{i}}',\ifc{\Varid{e}}')}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}(\ifc{\theta}_{1},\mathbin{...},\ifc{\theta}_\Varid{k})\right]}\\
}
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}_{1}\;\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\{\mskip1.5mu \ifc{\Varid{e}}'\mathbin{/}\ifc{\Varid{x}}_{1},\ifc{\Varid{i}}'\mathbin{/}\ifc{\Varid{x}}_{2}\mskip1.5mu\}\;\ifc{\Varid{e}}_{1}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\and
\inferrule[I-noRecv]
{
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{\Varid{l}}\mathrel{=}\epsilon}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\epsilon\right]}
}
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}_{1}\;\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\inferrule[I-labelOp]
{ \ensuremath{\llbracket \ifc{\Varid{l}}_{1}\;\otimes\;\ifc{\Varid{l}}_{2}\rrbracket\mathrel{=}\ifc{\Varid{v}}}}
{ \ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{l}}_{1}\;\otimes\;\ifc{\Varid{l}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{v}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}} }
\end{mathpar}
\caption{IFC language with all single-threaded operations}
\label{fig:ifc}
\end{figure}

\subsection{The embedding}

\Red{TODO[ds]:
  - move the async recv to text and out of the figure
  - clarify discussion on exceptions
  - fix the toLabled
  - add taskIDs to ruls
}
Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.22\textwidth}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\ifc{\Varid{v}}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \ifc{^{\textrm{IT}}\lceil}\tar{v}\ifc{\rceil}{}\<[E]%
\\
\>[B]{}\ifc{\Varid{e}}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}{}\<[E]%
\\
\>[B]{}\ifc{E}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \ifc{^{\textrm{IT}}\lceil}\tar{E}\ifc{\rceil}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\end{minipage} &
\begin{minipage}{.22\textwidth}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\tar{v}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{v}}\tar{\rfloor}{}\<[E]%
\\
\>[B]{}\tar{e}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}{}\<[E]%
\\
\>[B]{}\tar{E}{}\<[5]%
\>[5]{}\Coloneqq\cdots\mid \tar{_{\textrm{TI}}\lfloor}\ifc{E}\tar{\rfloor}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\end{minipage}
\end{tabular}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{53}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}_{\infty}.\ifc{\Varid{e}}\triangleq{}{}\<[E]%
\\
\>[B]{}\ \ \;\ \ \;\ \ \;\ifc{^{\textrm{IT}}\lceil}\;\mathbf{let}\;\tar{x}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;{}\<[53]%
\>[53]{}\ifc{^{\textrm{IT}}\lceil}\tar{x}\ifc{\rceil}\tar{\rfloor}\;\mathbf{in}\;\tar{x}\ifc{\rceil}{}\<[E]%
\\
\>[B]{}\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\tar{e}\ifc{]}_\tar{T}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots{}\<[E]%
\\
\>[B]{}\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots{}\<[E]%
\\
\>[B]{}\mathcal{E}\;[\mskip1.5mu \Varid{e}\mskip1.5mu]\rightarrow\ifc{\Sigma};\ifc{\Varid{t}},\ldots\triangleq{}\mathcal{E}\;[\mskip1.5mu \Varid{e}\mskip1.5mu]\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{mathpar}
\inferrule[I-sandbox]
{ 
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}\epsilon\right]}\\
\ensuremath{\tar{\Sigma}'\mathrel{=}\kappa\;(\tar{\Sigma})}\\
\ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}\\
\ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{\Sigma}', \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{\Varid{l}}}}\\
\ensuremath{\textrm{fresh}(\ifc{\Varid{i}}')}
}
{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Conid{F}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}

\and
\inferrule[I-done]
{\ensuremath{}}
{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\Conid{D}}}}(\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}

\and
\inferrule[I-noStep]
{\ensuremath{\ifc{\Sigma};\ifc{\Varid{t}},\ldots\not\overset{\alpha}{\hookrightarrow}}}
{\ensuremath{\ifc{\Sigma};\ifc{\Varid{t}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\Conid{N}}}}(\ifc{\Varid{t}},\ldots)}}

\and
\inferrule[I-border]
{ }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\ifc{\rceil}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\and
\inferrule[T-border]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{_{\textrm{TI}}\lfloor}\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}\tar{\rfloor}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]}}
\end{mathpar}
\caption{The embedding \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda}\;\!\!)}, where
\ensuremath{\Red{\lambda}\;\!\!\mathrel{=}(\tar{\Sigma},\tar{E},\tar{e},\tar{v},\rightarrow)}}
\label{fig:embedding}
\end{figure}

\begin{figure}
  Concurrent, round robin:
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
\column{41}{@{}>{\hspre}l<{\hspost}@{}}%
\column{43}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}\textsc{RR}_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[38]%
\>[38]{}\mathrel{=}\ifc{\Varid{t}}_{2},\ldots,\ifc{\Varid{t}}_{1}{}\<[E]%
\\
\>[3]{}\textsc{RR}_{{\tiny\mathrm{\text{done}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[41]%
\>[41]{}\mathrel{=}\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\\
\>[3]{}\textsc{RR}_{{\tiny\mathrm{\text{noStep}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[43]%
\>[43]{}\mathrel{=}\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\\
\>[3]{}\textsc{RR}_{{\tiny\mathrm{\text{sandbox}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[40]%
\>[40]{}\mathrel{=}\ifc{\Varid{t}}_{2},\ldots,\ifc{\Varid{t}}_{1}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
  Sequential:
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{34}{@{}>{\hspre}l<{\hspost}@{}}%
\column{36}{@{}>{\hspre}l<{\hspost}@{}}%
\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
\column{39}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}\textsc{Seq}_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[34]%
\>[34]{}\mathrel{=}\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\\
\>[3]{}\textsc{Seq}_{{\tiny\mathrm{\text{noStep}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[39]%
\>[39]{}\mathrel{=}\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\\
\>[3]{}\textsc{Seq}_{{\tiny\mathrm{\text{done}}}}(\ifc{\Varid{t}}){}\<[37]%
\>[37]{}\mathrel{=}\ifc{\Varid{t}}{}\<[E]%
\\
\>[3]{}\textsc{Seq}_{{\tiny\mathrm{\text{done}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots){}\<[37]%
\>[37]{}\mathrel{=}\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\\
\>[3]{}\textsc{Seq}_{{\tiny\mathrm{\text{sandbox}}}}(\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots,\ifc{\Varid{t}}_\Varid{n}){}\<[36]%
\>[36]{}\mathrel{=}\ifc{\Varid{t}}_\Varid{n},\ifc{\Varid{t}}_{1},\ifc{\Varid{t}}_{2},\ldots{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\caption{Scheduling policies}
\label{fig:scheduler}
\end{figure}

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret \ensuremath{\mathcal{E}} to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.  These rules only operate on the first task in the task pool, which by convention, is the only task executing.
    \item We reinterpret \ensuremath{\rightarrow}, an operation on a single task, in terms of \ensuremath{\hookrightarrow}, operation on task pools.  The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.  Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
\end{itemize}

The \textsc{I-sandbox} rule is of particular interest, as it is intended to allow users
to create new tasks.  When a new task is created, there is a question of what the
global state of the new task should be; this is defined in terms of a function $\kappa$.
Conservatively, $\kappa$ may be simply thought of as the identity function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for $\kappa$
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of $\kappa$.

For any target language \ensuremath{\Red{\lambda}} and scheduling policy \ensuremath{\alpha}, this
embedding defines an information flow control language, which we will
refer to as \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}.

\subsection{Examples}

To get a feeling for how these operational semantics operate, we'd like to
describe a few sample programs, and what their outputs are.

\paragraph{Sending mutable references}  As each task maintains its own
global state for the target language, one might reasonably wonder what would
happen if you attempted to send a reference to another task.

\begin{align*}
    & \ensuremath{\mathbf{let}\;\Varid{i}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;(\Varid{x},\Varid{i'}\Leftarrow\mathbf{recv}_{\infty}.\ifc{^{\textrm{IT}}\lceil}\mathbin{!}\tar{_{\textrm{TI}}\lfloor}\Varid{x}\tar{\rfloor}\ifc{\rceil})\tar{\rfloor}} \\
    & \ensuremath{\mathbf{in}\;\tar{_{\textrm{TI}}\lfloor}\mathbf{send}\;\ifc{^{\textrm{IT}}\lceil}\mathbf{ref}\;\mathbf{true}\ifc{\rceil}\tar{\rfloor}}
\end{align*}

It would be a violation of information flow if such an operation actually
resulted in references being shared between two tasks.  In fact, the address
will be received by the sandboxed task, but it will be a dangling pointer; the
task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
who are curious whether or not a static discipline could be enforced to
prevent these dangling pointers should check Section~\ref{sec:extensions}.)

\paragraph{Status of the heap after a sandbox}  Here is a program whose
semantics depends on the definition of $\kappa$:

\begin{align*}
    & \ensuremath{\mathbf{let}\;\Varid{x}\mathrel{=}\mathbf{ref}\;\mathbf{true}} \\
    & \ensuremath{\mathbf{in}\;\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;\ifc{^{\textrm{IT}}\lceil}\mathbin{!}\Varid{x};\mathbin{!}\Varid{x}\ifc{\rceil}\tar{\rfloor};\Varid{x}\mathbin{:=}\mathbf{false}}
\end{align*}

When $\kappa$ is the identity, the sandboxed task successfully dereferences
the contents of the reference to be true twice (recall that references
are cloned into the new global state).  When $\kappa$ is the constant function
to the empty store, $x$ becomes a dangling pionter.

\paragraph{Exceptions}  One language feature that has caused difficulty
for many information flow control systems is handling
exceptions.~\cite{Hritcu:2013:YIB:2497621.2498098}  The key difficulty
appears when an exception must cross a stack boundary where the current
label reverts back, i.e. across a \textbf{toLabeled} operator.~\cite{lio}
If the exception crosses this boundary, it can leak information about the
inner sensitive computation.

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler}, the behavior of \ensuremath{\mathbf{sandbox}}
can be used to model the behavior of \textbf{toLabeled}:

\begin{align*}
    & \ensuremath{\mathbf{toLabeled}\;\Varid{l}\;\tar{e}\triangleq{}} \\
    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{pid}\mathrel{=}\mathbf{taskId};} \\
    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{i}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;\Varid{l}\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\mathbf{send}\;\Varid{pid}\;\Varid{l}\;\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}\tar{\rfloor}\ifc{\rceil}\tar{\rfloor}} \\
    & \ensuremath{\ \ \;\mathbf{in}\;(\lambda \anonymous .\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;\Varid{l}\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\Varid{x},\anonymous \Leftarrow\mathbf{recv}.\Varid{x}\tar{\rfloor})} \\
\end{align*}

When the sequential scheduler is used, the sandboxed task runs to
completion before returning to the task that sandboxed it.  Thus,
a task pool should rather be interpreted as a number of information-flow
aware stack frames.  To read the result of a \ensuremath{\mathbf{toLabeled}} operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}

In this setting, it is also clear that exceptions should not cross boundaries,
as seen in \ensuremath{\mathbf{toLabeled}\;\Varid{l}\;\mathbf{fail};\mathbf{true}}, which evaluates to \ensuremath{\mathbf{true}} no matter even in
the event of an exception inside of the \ensuremath{\mathbf{toLabeled}} block:

%   \Red{When both languages have booleans, it is relatively simple to define
%   a natural embedding which preserves booleans across boundaries.}
%   \begin{mathpar}
%   \inferrule[I-bool]
%   { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
%   \and
%   \inferrule[T-bool]
%   { |b member {true, false}| } {| intE (TI b) -> intE b |}
%   \end{mathpar}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Security guarantees}
\label{sec:formal}

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})} for, appropriate
scheduler, satisfies non-interference~\cite{Goguen82},
without making any reference to properties of \ensuremath{\Red{\lambda}}.
%
%As it turns out, 
The precise scheduling policy \ensuremath{\alpha} dictates
the guarantee holding for programs with diverging tasks.
For a sequential scheduler \ensuremath{\textsc{Seq}}, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; this allows attackers to observe
secrets by observing the termination of tasks.
For the concurrent round-robin schedule \ensuremath{\textsc{RR}},
we can show a stronger result known as
\emph{termination-sensitive non-interference},
where termination attacks cannot leak information.

How can we characterize what the \emph{secret inputs} of a program are?  Like
other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
we specify and prove non-interference using \emph{term erasure}.
%
%Intuitively, we prove that an attacker does not learn
%any sensitive information from a program by 
Intuitively, term erasure allows us to show that a an attacker does not learn
any sensitive information from a program if the program behaves identically
(from the attacker point of view) to a program with all sensitive data
``erased''.
%
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than \ensuremath{\ifc{\Varid{l}}} to a new syntactic construct \ensuremath{\bullet}.
%
We can characterize the types of languages for which one can state
a non-interference claim.

\Red{should be the environment colored in the definition?}
\begin{definition}[Information flow control language]
    An information flow control language \ensuremath{\textbf{L}} is a tuple \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})}, where $\ensuremath{\Delta}$ is the type of machine configurations (members
    of which are usually denoted by the meta-variable \ensuremath{c}), \ensuremath{\hookrightarrow} is a
    reduction relation between machine configurations and \ensuremath{\varepsilon_{\Varid{l}}\mathbin{:}\Delta\rightarrow\varepsilon(\Delta)}
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations \ensuremath{\varepsilon(\Delta)}.  This tuple is sometimes
    augmented with a set of terminal configuration states $V
    \subseteq \ensuremath{\Delta}$ for which there are no possible further transitions.
    \Red{It is a bit odd to extend a tuple ``sometimes'' and a \ensuremath{V} appears like from
      nowhere. What about saying: Sometimes, we refer as \ensuremath{V} to set of 
     terminal configurations in \ensuremath{\Delta}, i.e., configurations states where
     no further transitions are possible. If you agree, then the next sentence
     where you said \ensuremath{V\mathrel{=}\mathbin{...}} must be removed.}
\end{definition}

Our language \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda}\;\!\!)} can be
represented as \ensuremath{(\ifc{\Delta},\ifc{V},\overset{\alpha}{\hookrightarrow},\varepsilon_{\ifc{\Varid{l}}})}, such that
$\ensuremath{\ifc{\Delta}} = \ensuremath{\ifc{\Sigma}} \times \prod \ensuremath{\ifc{\Varid{t}}}$ and
$\ensuremath{\ifc{V}} = \ensuremath{\ifc{\Sigma}} \times \ensuremath{\ifc{\Varid{t}}}_V$, where $\ensuremath{\ifc{\Varid{t}}}_V \subset \ensuremath{\ifc{\Varid{t}}}$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., \ensuremath{\ifc{\Varid{t}}} for the type of
  task.
}
The erased configuration \ensuremath{\varepsilon(\ifc{\Delta})} extends \ensuremath{\ifc{\Delta}} with configurations
containing \ensuremath{\bullet}, and Figure~\ref{fig:erasure} gives the precise definition for
our erasure function \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level \ensuremath{\ifc{\Varid{l}}}.
Otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than \ensuremath{\ifc{\Varid{l}}}.

\begin{figure} % fig:erasure
\begin{align*}
  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma};\ifc{\Varid{ts}})\mathrel{=}\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma});\text{filter}\;(\lambda \ifc{\Varid{t}}.\ifc{\Varid{t}}\mathrel{=}\bullet)\;(\text{map}\;\varepsilon_{\ifc{\Varid{l}}}\;\ifc{\Varid{ts}})}\\
  &\ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}} \begin{cases}
    \ensuremath{\bullet} & \ensuremath{\ifc{\Varid{l}}'\;\not\flows\;\ifc{\Varid{l}}} \\
    \ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}} & \text{otherwise}
  \end{cases} \\
  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\emptyset)\mathrel{=}\emptyset}\\
  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right])\mathrel{=}} \begin{cases}
    \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma})} & \text{\ensuremath{\ifc{\Varid{l}}'\;\not\flows\;\ifc{\Varid{l}}}, where \ensuremath{\ifc{\Varid{l}}'} is}\\
    & \text{the label of thread \ensuremath{\ifc{\Varid{i}}}} \\
    \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma})\left[\ifc{\Varid{i}}\mapsto{}\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Theta})\right]} & \text{otherwise}
  \end{cases} \\
  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Theta})\mathrel{=}\ifc{\Theta}\preceq\ifc{\Varid{l}}}\\
  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\Varid{v})\mathrel{=}\Varid{v}}
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
\ensuremath{\varepsilon_{\ifc{\Varid{l}}}} is applied homomorphically.  \label{fig:erasure} }
\end{figure}

We note that the definition of \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} captures the IFC
language's attacker model. 
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even just the number of such entities.
%
While such assumptions are standard~\tocite{}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda}\;\!\!)} to
  such models using the resource limits techniques of~\tocite{}.
  %
  We leave this extension to future work.
}

Non-interference relies on the definition of an attacker's observational power at
security level \ensuremath{\Varid{l}}, which is typically defined as an equivalence
relation---called \ensuremath{\Varid{l}}-equivalence---on configurations.  An attacker
at level \ensuremath{\Varid{l}} cannot
distinguish two configurations that are \ensuremath{\Varid{l}}-equivalent.
%
Since our erasure function captures the attacker model, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[\ensuremath{\Varid{l}}-equivalence]
    In a language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})}, two machine configurations
    \ensuremath{c,c'\in\Delta} are considered $l$-equivalent, written as \ensuremath{c\approx_lc'},
    if \ensuremath{\varepsilon_{\Varid{l}}(c)\mathrel{=}\varepsilon_{\ifc{\Varid{l}}}(c')}.
\end{definition}
%

Intuitively, we can now state that a language satisfies non-interference if an
attacker at level \ensuremath{\Varid{l}} cannot distinguish the runs of any two \ensuremath{\Varid{l}}-equivalent
configurations.
%
This precise non-interference property is called termination sensitive non-interference
(TSNI).  Besides the obvious requirement to not leak secret information
to public channels, this definition also requires the termination
of public tasks to be independent of secret tasks.
%
Formally, we define TSNI as follows.

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} is termination
  sensitive non-interfering if for any label \ensuremath{\Varid{l}}, and configurations
  \ensuremath{c_{1},c_{1}',c_{2}\;\in\;\Delta}, if
  \begin{equation} \label{eq:tsni-lhs}
    \ensuremath{c_{1}} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}}
    \qquad \text{and} \qquad
    \ensuremath{c_{1}} \ensuremath{\hookrightarrow}^* \ensuremath{c_{1}'}
  \end{equation}
  then there exists a configuration \ensuremath{c_{2}'\;\in\;\Delta} such that
  \begin{equation} \label{eq:tsni-rhs}
    \ensuremath{c_{1}'} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}'}
     \qquad \text{and} \qquad
    \ensuremath{c_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{c_{2}'}
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words if we take two \ensuremath{\Varid{l}}-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
number of steps that the second configuration can take to result in a
configuration that is \ensuremath{\Varid{l}}-equivalent to the first resultant configuration.
\Red{TODO: Do we want a commutative diagram to illustrate this? Ale: I don't
  think so, it is quite standard}

We now show that our IFC language satisfies TSNI %under a particular
%scheduling policy.
%
%Specifically, we consider the language 
under the round-robin scheduler
\ensuremath{\textsc{RR}} given in Figure~\ref{fig:scheduler}.

\begin{theorem}[Concurrent IFC language is TSNI]
  \label{thm:rr-tsni}
For any target language \ensuremath{\Red{\lambda}}, \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda})} satisfies TSNI.
\end{theorem}

In general TSNI will not hold for an arbitrary scheduler \ensuremath{\alpha}.
%
For example, \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})} with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%

However, even non-adversairal schedulers are not always safe.
Consider, for example, the sequential scheduling policy \ensuremath{\textsc{Seq}} given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that \ensuremath{L_\text{IFC}(\textsc{Seq},\Red{\lambda})} does not satisfy
TSNI.
%
Concretely, consider a target language similar to \ensuremath{\Red{\lambda_{\text{ML}}}} with an
additional expression terminal \ensuremath{\tar{\Uparrow}} that denotes a divergent computation,
i.e., \ensuremath{\tar{\Uparrow}} always reduces to \ensuremath{\tar{\Uparrow}} and a simple label lattice \ensuremath{\{\mskip1.5mu \mathsf{pub},\mathsf{sec}\mskip1.5mu\}} such that \ensuremath{\mathsf{pub}\;\flows\;\mathsf{sec}}, but \ensuremath{\mathsf{sec}\;\not\flows\;\mathsf{pub}}.
Consider the following two configurations in this language:
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{71}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\ifc{c}_{1}\mathrel{=}\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{^{\textrm{IT}}\lceil}\;\mathbf{if}\;\mathbf{false}\;\mathbf{then}\;\tar{\Uparrow}\;\mathbf{else}\;\mathbf{true}\ifc{\rceil}\rangle^{\mathrm{1}}_{\mathsf{sec}},{}\<[71]%
\>[71]{}\langle \tar{\Sigma}_{1}, \ifc{\Varid{e}}\rangle^{\mathrm{2}}_{\mathsf{pub}}{}\<[E]%
\\
\>[B]{}\ifc{c}_{2}\mathrel{=}\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{^{\textrm{IT}}\lceil}\;\mathbf{if}\;\mathbf{true}\;\mathbf{then}\;\tar{\Uparrow}\;\mathbf{else}\;\mathbf{true}\ifc{\rceil}\rangle^{\mathrm{1}}_{\mathsf{sec}},{}\<[71]%
\>[71]{}\langle \tar{\Sigma}_{2}, \ifc{\Varid{e}}\rangle^{\mathrm{2}}_{\mathsf{pub}}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\Red{Ale: \ensuremath{\mathbf{when}} was not defined, so I changed it to if-then-else}
These two configurations are \ensuremath{\mathsf{pub}}-equivalent, but \ensuremath{\ifc{c}_{1}} will reduce 
(in two steps) 
to \ensuremath{\ifc{c}_{1}\mathrel{=}\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{^{\textrm{IT}}\lceil}\mathbf{true}\ifc{\rceil}\rangle^{\mathrm{2}}_{\mathsf{pub}}}, whereas \ensuremath{\ifc{c}_{2}} will not make
any progress.
%
Suppose that \ensuremath{\ifc{\Varid{e}}} is a computation that writes to a \ensuremath{\mathsf{pub}} channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the \ensuremath{\mathsf{sec}} tasks's decision to diverge or not is directly leaked to a
public entitiy.

% sheule: I feel like this forward reference is not useful here.
%In certain cases, however, a TSNI-safe concurrent scheduling policy such as
%|roundrobinf| cannot be considered without imposing a non-trivial burden on the
%concrete implementation.
%(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
%target language.)
%
To accomodate for sequential languages, or cases where a weaker guarantee
is sufficient, we consider an alternative non-interference property called termination insensitive
non-interference (TINI).  This property can also be upheld by sequential languages at the cost
of leaking through (non)-termination~\cite{Askarov:2008}.
%
\begin{definition}[Termination insensitive non-interference (TINI)]
  A language \ensuremath{(\Delta,V,\hookrightarrow,\varepsilon_{\Varid{l}})} is termination
  insensitive non-interfering if for any label \ensuremath{\Varid{l}}, and configurations
  \ensuremath{c_{1},c_{2}\;\in\;\Delta} and \ensuremath{c_{1}',c_{2}'\;\in\;V}, it holds that
  \[
    (\ensuremath{c_{1}} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}}
    \;\;\land\;\;
    \ensuremath{c_{1}} \ensuremath{\hookrightarrow}^* \ensuremath{c_{1}'}
    \;\;\land\;\;
    \ensuremath{c_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{c_{2}'})
    \implies
    \ensuremath{c_{1}'} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}'}
  \]
\end{definition}

TSNI states that if we take two \ensuremath{\Varid{l}}-equivalent configurations, and both
configurations reduce to final configurations (i.e.,
configurations for which there are no
possible further transitions), then the end configurations are also
\ensuremath{\Varid{l}}-equivalent.
%
We highlight that this statement is much weaker than TSNI: it only states that
terminating programs do not leak sensitive data, but makes no statement
about non-terminating programs.

As shown by compilers~\cite{jif,FlowCaml}, interpreters~\cite{JSFlow}, and
libraries~\cite{Russo+:Haskell08,lio}, TINI is useful for sequential
settings. We show that our IFC language with the sequential scheduling policy
\ensuremath{\textsc{Seq}} satisfies TINI.
%
\begin{theorem}[Sequential IFC language is TINI]
  \label{thm:seq-tini}
For any target language \ensuremath{\Red{\lambda}}, \ensuremath{L_\text{IFC}(\textsc{Seq},\Red{\lambda})} satisfies TINI.
\end{theorem}

% Local Variables:
% TeX-master: "main.tex"
% TeX-command-default: "Make"
% End:
\section{Concrete implementation}
\label{sec:concrete}

\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}

The operational semantics we have defined in the previous section
satisfy non-interference by design.
We achieve this general statement that works for a large class of
languages by having different task execute completely isolated from
each other, such that every task has its own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to memory locations without
mechanisms in the language to achieve a separation of the heap.
On the other hand, for other languages this
strong isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the language \ensuremath{\Red{\lambda_{\text{ML}}}}, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap.
More precisely, instead of using a configuration of the form
\[\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\langle \tar{\Sigma}_{2}, \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{\Varid{l}}_{2}}\;\ldots}\]
we would like a single global heap as in
\[\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\langle \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{\Varid{l}}_{2}},\ldots}\]

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated.  In particular, it is not
sound to share references to a heap cell between different tasks.
Otherwise, information can be trivially leaked by copying
secret data into a reference in one task, and then
reading it again by a another task with a lower label.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation was to be more efficient
by using one global heap, but conceptually maintain isolation between
task by not allowing sharing of references between tasks.
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

% con no-prime red target
% abs prime blue ifc

\begin{definition}[Isomorphism of information-flow control languages]
  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} is \textit{isomorphic} to a
  language \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{\Varid{l}})} if there exist total functions \ensuremath{\Varid{f}\mathbin{:}\Delta\rightarrow\Delta'} and \ensuremath{\Varid{f}^{-1}\mathbin{:}\Delta'\rightarrow\Delta} such that \ensuremath{\Varid{f}\circ\Varid{f}^{-1}\mathrel{=}id_{\Delta}} \ensuremath{\Varid{f}^{-1}\circ\Varid{f}\mathrel{=}id_{\Delta'}}.  Furthermore, \ensuremath{\Varid{f}} and \ensuremath{\Varid{f}^{-1}} are functorial (e.g. if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and \ensuremath{\hookrightarrow}.

  If we weaken this restriction such that \ensuremath{\Varid{f}^{-1}} does
  not have to be functorial over \ensuremath{\hookrightarrow}, we call the
  language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} \textit{weakly isomorphic} to
  \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{\Varid{l}})}.
\end{definition}

Providing an isomorphism between the two languages allows us to
preserve (termination sensitive or insensitive) non-interference
as the following two theorems state.

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
  \label{thm:iso-tsni}
  If L is isomorphic to L' and L' satisfies TSNI, then
  L satisfies TSNI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations from
  L to L', applying TSNI, and then transporting the
  resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
  \label{thm:iso-tini}
  If a language L is weakly isomorphic to a language L', and L'
  satisfies TINI, then L satisfies TINI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations
  from L to L', applying TINI and transporting the resulting
  equivalence back using functoriality of \ensuremath{\Varid{f}^{-1}} over $l$-equivalences.
\end{proof}

A na\"ive attempt at our single heap semantics
will not allow us to construct an isomorphism
with the abstract language \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda_{\text{ML}}})}, and instead highlights
where things will go wrong.
To successfully construct an isomorphism, our concrete semantics need
to mirror the behavior of the abstract semantics, most importantly
in the case where tasks interact.  Namely, at a fork and when sending
or receiving messages, we take an expression from one task and
execute it in the context of another task.  In the abstract semantics
the fork rule is parameterized by the strategy \ensuremath{\kappa}, which defines
what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
we have motivated two choices}, namely the identity (to effectively
clone the heap), or to start with an empty heap.
In the latter case, this effectively means that existing addresses
in the forked expression \ensuremath{\ifc{\Varid{e}}} are no longer valid and the
task gets stuck (and then removed by \textsc{I-noStep}).
\todo{}{Is this actually true?  Currently the semantics are unclear.}
To get the isomorphic behavior in the concrete semantics with a
single heap, we would have to change the forked expression \ensuremath{\ifc{\Varid{e}}} in
such a way that all addresses get rewritten to fresh addresses
that are guaranteed to not occur in the global heap.  Similarly,
sending a memory address should take a similar approach, as addresses
for sent references will not exist in the receiving task.

If \ensuremath{\kappa} is the identity function, then the abstract semantics
effectively clone the heap on a fork.  To get an isomorphic
behavior in the concrete, we would have to create a copy of everything
reachable from the forked expression (not just the values for
the memory addresses in the expression), and replace all addresses
correspondingly.  Even worse, the behavior of sending a memory address
now depends on whether that address existed at the time the receiving
task was forked;  if it did, then the address should be rewritten to the
new one, otherwise to a fresh address.
Such a complicated behavior is contradictory to our initial motivation
of implementing a single heap for efficiency.  But also the
behavior of the simpler case where \ensuremath{\kappa} returns an empty heap is
undesirable:  We rewrite addresses to fresh addresses, which will
result in a stuck task whenever such an address is dereferenced.

\subsection{Restricting the IFC Language}

As a better solution we could forbid forked expressions as well
as messages sent to other tasks to contain memory addresses in the
first place.  In a statically typed language, the type system could
prevent this from happening, and we talk more about how our
approach integrates with typed languages in
Section~\ref{sec:extensions:types}.
In a dynamically type languages such as \ensuremath{\Red{\lambda_{\text{ML}}}}, we might
restrict the transition for \ensuremath{\mathbf{sandbox}} and \ensuremath{\mathbf{send}} to only allow expressions
without memory addresses.

Again we are modifying the IFC language semantics in a non-trivial way,
which begs the question whether non-interference is preserved.
Note that restricting the transitions in an information flow control
system in general does not preserve non-interference as the following
minimal example illustrates.
Consider a trivial state machine as shown
in Figure~\ref{fig:trivial-sm}, whose second projection is classified
secret.  With all three transitions, this language fulfills
termination sensitive non-interference.  Furthermore, if the
dashed transition
is removed, the language continues to satisfy TSNI.  However, if any
solid line is removed, the language fails TSNI.

\begin{figure}
  States: $(x,y)$ for $x,y \in \{0,1\}$ \\
  Erasure function: $f(x,y) = (x,\bullet)$

  \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
    \node (A) {$(1,1)$};
    \node (B) [right of=A] {$(1,0)$};
    \node (C) [below of=A] {$(0,1)$};
    \node (D) [right of=C] {$(0,0)$};
    \draw[->] (A) to node {} (B);
    \draw[->] (C) to node {} (D);
    \draw[->, dashed] (B) to node {} (D);
    \end{tikzpicture}\end{center}

  \label{fig:trivial-sm}
  \caption{A trivial state machine}
\end{figure}

To remedy this issue, we give a definition that gives a condition
under which it is safe to restrict the abstract IFC language
\ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}, such that non-interference is preserved.

\begin{definition}[Restricted IFC language]
  \label{def:restricted}
  For a family of predicates $\mathcal P$ (one for every reduction
  rule), we call
  \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\alpha,\Red{\lambda})} a restricted IFC language
  if its definition is equivalent to the abstract language
  \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}, with the following exception:
  The reduction rules are restricted
  by adding a predicate $P$ from $\mathcal P$ to the premise of
  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
  can depend only on the \textit{erased} configuration
  \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c})}, where \ensuremath{\ifc{\Varid{l}}} is the label of the first task
  in the task list and \ensuremath{\ifc{c}} the full configuration.
\end{definition}

By the following theorem, the restricted IFC language with an
appropriate scheduling policy is non-interfering.

\begin{theorem}
  \label{thm:restricted}
  For any target language \ensuremath{\Red{\lambda}} and family of predicates
  $\mathcal{P}$, the IFC language \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\textsc{RR},\Red{\lambda})}
  is TSNI.  Furthermore, the IFC language
  \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\textsc{Seq},\Red{\lambda})} is TSNI.
\end{theorem}

\subsection{IFC language with a single heap}

We are now ready to make our single heap IFC language precise and
ensure its non-interference using the techniques presented.
First, we can construct the restricted language
\ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P}_\text{norefs},\alpha,\Red{\lambda_{\text{ML}}})}, where \ensuremath{\mathcal{P}_\text{norefs}} is
the family of always valid predicates, except for the ones for
\textsc{I-fork} and \textsc{I-send}, which we define as
\[ P = \text{\ensuremath{\ifc{\Varid{e}}} does not contain any address \ensuremath{\tar{a}}} \]
That is, we do not restrict any rules except for \textsc{I-fork}
and \textsc{I-send}.
Since $P$ only depends on \ensuremath{\ifc{\Varid{e}}}, which is part of the current
task and thus never erased w.r.t.\ the label of the first task,
this language satisfies non-interference by Theorem~\ref{thm:restricted}.

\begin{figure}

  \begin{mathpar}
    \inferrule[C-fork]
    {
      \text{\ensuremath{\ifc{\Varid{e}}} does not contain any \ensuremath{\tar{a}}}\\
      \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}\epsilon\right]}\\
      \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}\\
      \ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{\Varid{l}}}}\\
      \ensuremath{\textrm{fresh}\;(\ifc{\Varid{i}}')}
    }
    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\ldots\hookrightarrow\ifc{\Sigma}';\tar{\Sigma};\alpha_{{\tiny\mathrm{\Conid{F}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}
    \and
    \inferrule[C-send]
    {
      \text{\ensuremath{\ifc{\Varid{e}}} does not contain any \ensuremath{\tar{a}}}\\
      \ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
      \ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
      \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
    }
    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\rightarrow\ifc{\Sigma};\tar{\Sigma};\alpha_{{\tiny\mathrm{\text{step}}}}(\langle \langle\rangle\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}
  \end{mathpar}

  \caption{A selection of the reduction rules for \ensuremath{L_\text{IFC}^{\Red{\text{Heap}}}(\alpha)}.}
  \label{fig:concrete}
\end{figure}

The essential parts of the semantics for the concrete language
with a single heap,
which we call \ensuremath{L_\text{IFC}^{\Red{\text{Heap}}}(\alpha)},
are given in Figure~\ref{fig:concrete}.  Most rules are
straight-forward translations of the rules in Figures~\ref{fig:ifc}
and~\ref{fig:embedding} but for a single heap.  For conciseness, we
only show the interesting ones.
Now, we can show an isomorphism between this language and
\ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P}_\text{norefs},\alpha,\Red{\lambda_{\text{ML}}})}, which
(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
non-interference for an appropriate scheduling policy \ensuremath{\alpha}.

\Red{Show the isomorphism.}

\section{Proofs}
\label{sec:proofs}

In this section we will prove all theorems we have stated so far.
We observe that the non-interference claims for the languages
\ensuremath{L_\text{IFC}(\textsc{Seq},\Red{\lambda})} and \ensuremath{L_\text{IFC}(\textsc{RR}_{{\tiny\mathrm{\cdot }}}(\cdot ),\Red{\lambda})}
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
respectively, about restricted IFC languages where the set
of predicates is the set of always valid predicates.

Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
we state a lemma we will use.

\begin{lemma}
  \label{lemma:rr-tsni-general}
  We consider, for any target language \ensuremath{\Red{\lambda}},
  the restricted IFC language \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\alpha,\Red{\lambda})}
  (according to Definition~\ref{def:restricted}).
  Then,
  for any configurations \ensuremath{\ifc{c}_{1}}, \ensuremath{\ifc{c}_{1}'}, \ensuremath{\ifc{c}_{2}}, and label \ensuremath{\ifc{\Varid{l}}} where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  \ensuremath{\ifc{c}_{1}} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}}
  \qquad \text{and} \qquad
  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}'}
  \end{equation}
  there exists a configuration \ensuremath{\ifc{c}_{2}'} such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}'}
  \qquad \text{and} \qquad
  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $\ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}}$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}
  \]
  for some configuration \ensuremath{\ifc{c}_{1}''}.  By Lemma~\ref{lemma:rr-tsni-general}, we get
  \ensuremath{\ifc{c}''} with
  \begin{equation} \label{eq:tsni-proof-1}
  \ensuremath{\ifc{c}_{1}''} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}''}
  \qquad \text{and} \qquad
  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}''}
  \end{equation}
  Applying the induction hypothesis to
  $\ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}$, we get \ensuremath{\ifc{c}_{2}'} with
  \begin{equation} \label{eq:tsni-proof-2}
  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}'}
  \qquad \text{and} \qquad
  \ensuremath{\ifc{c}_{2}''} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us the right-hand side of the implication in the TSNI
  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in \ensuremath{\ifc{c}_{1}}, otherwise
  it could not take a step.  Thus, \ensuremath{\ifc{c}_{1}} is of the form
  \ensuremath{\ifc{\Sigma}_{1};\ifc{\Varid{t}}_{1},\ifc{\Varid{ts}}_{1}}.  Consider two cases:
  \begin{itemize}
    \item $\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Varid{t}}_{1})}=\ensuremath{\bullet}$.
    By the definition of \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}, we know that \ensuremath{\ifc{\Varid{l}}\;\flows\;\lcurr}
    where \ensuremath{\lcurr} is the label of \ensuremath{\ifc{\Varid{t}}_{1}}.
    In this case, we do not need to take a step for
    \ensuremath{\ifc{c}_{2}}, because \ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}} will already be \ensuremath{\ifc{\Varid{l}}}-equivalent to \ensuremath{\ifc{c}_{1}'}.
    To see that, note that the tasks \ensuremath{\ifc{\Varid{ts}}_{1}} in \ensuremath{\ifc{c}_{1}} are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task \ensuremath{\ifc{\Varid{t}}_{1}} either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task \ensuremath{\ifc{\Varid{t}}_{1}'} as well as potentially spawning a new
    task \ensuremath{\ifc{\Varid{t}}_{1}''}.  Since both \ensuremath{\ifc{\Varid{t}}_{1}'} and \ensuremath{\ifc{\Varid{t}}_{1}''} have a label that is
    at least as high as the label of \ensuremath{\ifc{\Varid{t}}_{1}} (can be seen
    by inspecting all reduction rules), they will get filtered
    by \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} in \ensuremath{\ifc{c}_{1}'}.  Therefore, the \ensuremath{\ifc{\Varid{l}}} equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to \ensuremath{\ifc{\Sigma}_{1}}:
    Only three reduction rules change \ensuremath{\ifc{\Sigma}_{1}},
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label \ensuremath{\ifc{\Varid{l}}'} gets added to the message
      queue of the receiving thread.  However, since \ensuremath{\lcurr\;\flows\;\ifc{\Varid{l}}'},
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task \ensuremath{\ifc{\Varid{t}}_{1}} can change, which gets erased.
    \end{description}
    This ensures that $\ensuremath{\ifc{c}_{1}'}\approx_{\ensuremath{\ifc{\Varid{l}}}}\ensuremath{\ifc{c}_{2}'}=\ensuremath{\ifc{c}_{2}}$.
%    \alphacondition{We need all scheduling policies to not change the order
%      of any tasks (except for the first one).  Newly spawned task can appear
%      anywhere in the list.}
    \item $\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Varid{t}}_{1})}\neq\ensuremath{\bullet}$.
    Here, there must be a corresponding
    task \ensuremath{\ifc{\Varid{t}}_{2}} in \ensuremath{\ifc{c}_{2}},
    such that \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\ifc{\Varid{t}}_{2}} (otherwise \ensuremath{\ifc{c}_{1}} and
    \ensuremath{\ifc{c}_{2}} could not be \ensuremath{\ifc{\Varid{l}}} equivalent).
    However, \ensuremath{\ifc{\Varid{t}}_{2}} might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}.
    In \ensuremath{\ifc{c}_{2}}, we can first take some number of steps until \ensuremath{\ifc{\Varid{t}}_{2}} moves
    to the front of the list.
    This is the case regardless of any additional side conditions $P$ on
    rules, because for all of these tasks, it can either take an actual
    step, or it gets dropped by \textsc{I-noStep} (which is always
    possible, as there cannot be an additional side condition on this
    rule).  All tasks that didn't get dropped are still at a label
    that isn't below \ensuremath{\ifc{\Varid{l}}} and thus get erased.

%    \alphacondition{The scheduling policy must eventually let any task in
%      the task list evaluate.  In particular, it cannot get stuck when the
%      first task gets stuck, or keep executing a small number of tasks
%      exclusively forever (e.g. just execute the first task all the time
%      if it gets into an infinite loop).}

    Therefore, after \ensuremath{\ifc{c}_{2}} has potentially executed some number of steps
    to arrive at \ensuremath{\ifc{c}_{2}''}, we are now in the situation where $\ensuremath{\ifc{c}_{1}}\approx_{\ensuremath{\ifc{\Varid{l}}}}\ensuremath{\ifc{c}_{2}''}$, and the first tasks \ensuremath{\ifc{\Varid{t}}_{1}} and \ensuremath{\ifc{\Varid{t}}_{2}},
    respectively, don't get erased and are thus equivalent.
    The task \ensuremath{\ifc{\Varid{t}}_{2}} can now take exactly the same step as \ensuremath{\ifc{\Varid{t}}_{1}};  this
    is true even with arbitrary additional premises $P$ that follow
    the condition in Definition~\ref{def:npri}, since those
    predicates only depend on \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c}_{1})}, which is equivalent
    to \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c}_{2})}, and thus those predicates evaluate in the same way.
    Thus, we only
    need to argue that the potential differences in \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} cannot
    have an influence on the execution (and we know \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} are
    \ensuremath{\ifc{\Varid{l}}} equivalent).
    Again, only sending and receiving will depend on, or change \ensuremath{\ifc{\Sigma}},
    so we consider all these cases.
    \begin{description}
      \item[Case \textsc{I-send}]
      Here, the task \ensuremath{\ifc{\Varid{t}}_{2}} will send the same message to the same
      receiver queue. This
      queue is either completely erased, or it is \ensuremath{\ifc{\Varid{l}}} equivalent.  In both
      cases, \ensuremath{\ifc{\Varid{l}}} equivalence of \ensuremath{\ifc{\Sigma}_{1}'} and \ensuremath{\ifc{\Sigma}_{2}'} is preserved.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      When the tasks are receiving a message, then by the reduction rules
      we know that they first filter the queue by the label
      \ensuremath{\lcurr} of \ensuremath{\ifc{\Varid{t}}_{1}}.  We
      also know that the queues are equivalent when filtered by the less
      restrictive label \ensuremath{\ifc{\Varid{l}}}, thus the messages received (or dropped) from the
      queue are equivalent.
    \end{description}
  \end{itemize}
\end{proof}

The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\tocite{} for a TINI proof of a similar system).

\section{The monadic interpretation}
\label{sec:monad}

In the previous sections, we have been primarily concerned with the
combination of operational semantics in order to automatically augment a
language with information flow control.  In this section, we present
a more abstract view of the situation, phrased in the language of monads
and monad transformers.  The key idea is that the computational effects
of the target language should be thought of as a \emph{monad transformer}
on top of the information flow control base monad.  Readers who are not
familiar with monads should feel free to skip this section.

Monads were originally proposed as a method for organizing computational
effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
of interest was how to modularly build more complex computational
effects out of simpler ones.  One particular approach, the
\emph{incremental
approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
monad transformers, which add an extra computation feature to a
pre-existing monad.  In the past, this approach has been criticized for
a number of failings, including the fact that the order in meaning of a
monad can depend on the order in which the monad transformers are
applied. The canonical example of this phenomenon is the
composition of the state monad and the error monad: depending on the
ordering of the two monad transformers, state is preserved or thrown away
upon an error.

These problems can be viewed as defects in a setting where we are
simply interested in combining effects.  However, in the setting of information
flow control, we are primarily interested in augmenting the
computational effects of a target language with information flow control
\emph{without} compromising non-interference.  When the base monad is
kept abstract (in the style of a restricted IO monad~\cite{Terei:2012:SH:2364506.2364524}),
there is an easy argument why any monad transformer must also preserve non-interference:
the monad transformer could have been implemented simply as a \emph{pure} interpreter, and
the pure interpreter is just another program like any other that may run on top of
a restricted IO monad.

Now, one shouldn't simply force an interpreter to be reimplemented on
top of a language supporting information flow control.  As suggested by
Filinski et al~\cite{Filinski:2010:MA:1707801.1706354}, we should use
pure implementations of computational effects to understand
computational effects when built into information flow languages: they
give a good hint what the operational rules should be.  This intuition
backed the development of Section~\ref{sec:retrofit}.  Furthermore,
developing the relationship between concrete semantics and abstract
semantics in Section~\ref{sec:concrete} relates to the question of monad
isomorphisms in the presence of data abstraction.  We leave the
investigation of this connection in more detail to future work.
\section{Real world languages}
\label{sec:real}

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the SWAPI~\tocite{} system; we leave the
implementation of the IFC system for C to future work.

\subsection{C}
\label{sec:real:c}
%
C programs are able to execute arbitrary (machine) code, access
arbitrary memory, and perform arbitrary syscalls.
%
Thus, the confinement of C programs must be imposed by the underlying OS
and hardware.
%
This isolation can be achieved using Dune's hardware protection
mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
version of Wedge~\cite{Belay:2012:DSU:2387880.2387913,
Bittau:2008:WSA:1387589.1387611} with an information flow control
policy.
%
Using pages tables, a (trusted) IFC runtime could ensure that each task,
implemented as a lightweight process, can only access the memory it
allocates--tasks do not have access to any shared memory.
%
In addition, ring protection could be used to intercept syscalls performed by
a task and only permit those corresponding to our IFC language (e.g.,
\ensuremath{\mathbf{getLabel}}, \ensuremath{\mathbf{send}}).
%
Although other sandboxing mechanisms can be used in place of Dune, we
believe Dune's hardware protection mechanism would allow us to provide a 
concrete implementation that is more efficient and simpler to reason about.

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a syscall.
%
Creating a new task with the \ensuremath{\mathbf{sandbox}} syscall is corresponds to
\emph{forking} a process.  Here, page tables limit what memory
a task can access: we can ensure there will be no memory (effectively
defining \ensuremath{\kappa\;(\tar{\Sigma})\mathrel{=}\tar{\Sigma}_{0}}, where \ensuremath{\tar{\Sigma}_{0}} is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a \ensuremath{\mathbf{send}} syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a \ensuremath{\mathbf{recv}} that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these syscalls are
meaningless.

\subsection{Haskell}
\label{sec:real:hs}
In contrast with the C embedding which relies on hardware protection
mechanisms, a Haskell implementation can leverage Haskell's strong data
abstraction and static type system, monadic approach to effects, and
lightweight concurrency to implement the embedding in a more lightweight
manner.  We briefly describe one such system, LIO~\cite{lio}, which
implements IFC as a library.

LIO is implemented by defining a new monad, \text{\tt LIO}, which wraps Haskell's \text{\tt IO}
monad.
%
The purpose of this monad is twofold: it restricts the use of
arbitrary effects that would ordinarily be allowed by the \text{\tt IO} monad,
and it associates labels with tasks.
%
Computations in the \text{\tt LIO}
monad can be thought to be operating within the IFC system.
%
One important aspect of using \text{\tt IO} as the base for this
implementation is that it allows use of Haskell's efficient
implementation of threads, channels, etc. (e.g., in the concurrent
version of LIO, we use Haskell's \texttt{forkIO} to fork a lightweight
thread in the case of \ensuremath{\mathbf{sandbox}}~\cite{stefan:addressing-covert}), in
contrast to defining them in a completely pure fashion (as suggested
in Section~\ref{sec:monad}).

What is the interpretation of this system as per Section~\ref{sec:retrofit}?
%
Here, the \emph{pure subset} of Haskell is the target language, while
the monadic subset of Haskell in the \text{\tt LIO} monad is the IFC
language.
%
Crucially, the lack of unrestricted mutation in the pure fragment of
Haskell prevents direct communication between tasks, even when memory is
shared between them.\footnote{However, lazy evaluation can still produce
a covert channel.}

Since this IFC system is implemented as a library in Haskell,
implementation-wise, we must ensure that these languages are indeed the subsets of Haskell
we claim, i.e., while the concrete language is all of Haskell, we must
ensure that we can restrict programs to our subset of Haskell that
encodes the combined language.
%
To this end, \text{\tt LIO} relies on Haskell's strong data abstraction and type system
(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
ensure that arbitrary \text{\tt IO} actions cannot be lifted into
\text{\tt LIO}.
%
In other words, assuming \text{\tt LIO} is implemented correctly, programs
written in the \text{\tt LIO} monad cannot perform arbitrary \text{\tt IO} actions
without breaking abstraction.

We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
additional details on the various implementations of this system.\footnote{It's worth noting that the proofs of non-interference we have given for asynchronous communication primitives are new and not in the original presentation of LIO.}

\subsection{JavaScript}
\label{sec:real:js}

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O. (Capabilities such as the ability to
mutate the DOM and read user input are APIs defined on top of the ECMAScript
specification.)
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.

We describe SWAPI~\tocite{}, an implementation of this system for JavaScript.
%
The direct approach for implementing the embedded language \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})} is
by running multiple instances of the JS runtime, i.e., \ensuremath{\Red{\lambda_{\text{JS}}}}, in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\tocite{} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \text{\tt getElementById}, by attaching them to
the global JS object.
%
In turn, each task created with \ensuremath{\mathbf{sandbox}} is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, \ensuremath{\mathbf{sandbox}} is defined with \ensuremath{\kappa\;(\tar{\Sigma})\mathrel{=}\tar{\Sigma}_{0}}, where \ensuremath{\tar{\Sigma}_{0}} is the global object corresponding to the standard
JS library (e.g., \ensuremath{\tar{\Sigma}_{0}} contains \texttt{Object}, \texttt{Array},
etc.).

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict \ensuremath{\mathbf{send}}
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for \ensuremath{\mathbf{send}} such that only strings can be shared:
\newcommand{\str}{"string"}
\begin{mathpar}
\inferrule[JS-send]
{
\ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\;[\mskip1.5mu \ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}'),\ifc{\Theta}\mskip1.5mu]}\\
\ensuremath{\ifc{\Varid{e}}\mathrel{=}\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}}\\
\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\texttt{typeOf}(\tar{e})\texttt{ === \str}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\texttt{true}\right]}
}
{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\hookrightarrow\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Sigma}}}(\langle \tar{\Sigma}, \ifc{E}\ifc{[}\langle\rangle\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}
\end{mathpar}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and Worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of \ensuremath{\mathbf{send}}, that additionally
takes a label argument.

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the Worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across Worker
  threads is undefined.
}
%
As suggested by our formal semantics, SWAPI can directly leverage these
mechanisms to implement the semantics of \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})}
without modifying the JS runtime or intrusively changing the browser
layout engine.

However, a simple implementation of just associating a label with
Workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a Worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\tocite{} to restrict external effects according to
the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the SWAPI implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence SWAPI only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, SWAPI allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a Worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}
\section{Extensions and Limitations}
\label{sec:extensions}

In this section we consider several extensions to our IFC system.
%
Specifically, we discuss how the specification language can be
extended to consider other IFC-aware features (e.g., fine-grained
labeled values), a static type system, or more complex scheduling
policies.
%
When considering these extensions we also highlight some limitations
of our approach.

\subsection{IFC language features}
\label{sec:extensions:labeled}

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

\paragraph{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and SWAPI implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
Addressing this problem is a natural direction for this work.

\paragraph{Clearance}
%
LIO, SWAPI, and Breeze additionally provide a discretionary access
control mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}; this mechanisms is
used to restrict a computation from accessing data (or communicating
with entities) above a specified label, the clearance.
%
For simplicity, we omitted clearance from our formalism.
%
We only remark that the mechanism generalizes beyond these IFC systems
in a straight forward manner and does not affect our definitions or
proofs in any meaningful way.

\subsection{Type safety}
\label{sec:extensions:types}

One important consideration for any new language feature is whether
or not it preserves type safety.  If implementations are allowed to
have undefined behavior when the system gets stuck, concerns of type
safety can be directly applicable to security.

In our presentation, we have demanded that implementations \emph{not}
have undefined behavior when getting stuck: in such situations, the
\textsc{I-noStep} rule applies, where the stuck thread should be dropped
from execution.  Our combined language will be not get stuck, even if
the target language could get stuck.  This sort of guarantee can be
achieved at a coarse granularity for languages like C by using hard
isolation.  However, for many other languages, this is too stringent a
requirement.

A possible way to relax this requirement is to drop the \textsc{I-noStep}
rule, and instead demand type-safety of the combined language.  This
depends on the type system of the target language, so it is difficult to
make any general statements about how one would go about doing this.  However,
there are few general remarks to be made:

\begin{itemize}
    \item In Matthews and Findlers original
        paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
        on using type boundaries to mediate between the type systems of
        the two languages, i.e. handling conversions of values from
        one language to the other.  These techniques are directly applicable here.

    \item In the case of mini-ML, type safety proceeds by a preservation theorem
        that refers to well-typed stores.  In our setting, there are now multiple
        stores, and expressions may move from being interpreted with one store
        to another (e.g. when an address is sent from one thread to
        another); a clear violation of type safety.  In this case, operations
        such as \textbf{send} have their typing rules require
        the expressions being sent be typeable in an arbitrary well-typed store,
        statically disallowing the sending of addresses, or any types which
        may contain addresses.  In practice, this may be further restricted to
        types which can be easily marshalled, e.g. strings.

    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
        influences the difficulty of the type-safety proof for
        \textbf{fork} when the target language has a store.  When
        $\kappa$ is identity, most expressions can be allowed, since the store
        remains the same; if $\kappa$ drops the store, however, only closed expressions
        can be forked.
\end{itemize}

\subsection{Scheduling policies}
Our specification language is parametrized by a scheduling policy
\ensuremath{\alpha}, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of \ensuremath{\alpha}
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies \ensuremath{\textsc{RR}} and
\ensuremath{\textsc{Seq}} for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\tocite{}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\tocite{}, this scheduling policy is considerably more
  complex. See~\tocite{}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%
We leave the proof of this claim to future work.
%

Despite allowing a number of practical schedulers to be expressed, our
scheduler parametrization is limited.
%
For instance, since \ensuremath{\alpha} is a map on task lists, schedulers that
rely on the global state \ensuremath{\ifc{\Sigma}} or previous task configurations cannot
be expressed.
%
Though, we do not believe this to be a fundamental limitation, our
current formalization cannot directly be applied to more-powerful, but
safe, scheduling policies, as considered in~\tocite{}.
%
More fundamentally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
(or even non-deterministic target languages) is non-trivial.
%
For instance, this may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if \ensuremath{\Varid{l}}-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers

\subsection{External effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\tocite{}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
This latter approach of wrapping unsafe primitives is, for example,
used in SWAPI to allow for controlled network communication.
%
By wrapping the default XHR object, for example, we can allow code
to communicate with hosts according to the task's current label.
\section{Related work}
\label{sec:related}

% Local Variables:
% TeX-master: "main.lhs.tex"
% TeX-command-default: "Make"
% End:

%Our paper follows a long tradition of papers on information flow
%control.  
Our information flow control system is closely related
to the coarse-grained information systems used in operating systems such
as Asbestos~\cite{efstathopoulos:asbestos}, 
HiStar~\cite{Zeldovich:2006}, and Flume~\cite{krohn:flume}, as well as language-based
\emph{floating-label IFC systems} such as LIO~\cite{lio},
and Breeze~\cite{Hritcu:2013:YIB:2497621.2498098}, where there is a
monotonically increased label
associated with threads of execution.
Our treatment of termination-sensitive and termination-insensitive interference
originates from Smith and Volpano~\cite{Smith:Volpano:MultiThreaded,Volpano:1997:ECF:794197.795081}.
%While this work often considers the interaction of information flow
%control with respect to various language features (e.g.,
%exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}), none of these
%systems attempt to be generic in the choice of target language.

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accomodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. \Red{Different
from them, we rely on programming level abstraction to isolate
computations.}

%There are attempts to overcome this performance barrier by various means:
%Austin and Flanagan~\cite{Austin:Flanagan:PLAS09} handle this problem
%by using a \emph{sparse information labeling} scheme which reduces the
%cost of managing labels when they are not needed, while FlowFox~\cite{DeGroef:2012}
%uses an entirely different technique of \emph{secure multi-execution} to
%enforce non-interference. \Red{Probably more stuff here.}
%\todo{ds}{SME works for arbitrary language (kind of).}

The constructs in our IFC language, as well as the behavior of
inter-thread communication, is reminiscent of distributed systems
like Erlang~\cite{Armstrong03makingreliable}.  There is a close
correspondence: in distributed systems, isolation is required due to
physical constraints; in information flow control, isolation is
required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
built an information flow control system on top of Erlang which is quite
similar to ours.  However, they do not use a floating label system (processes
can find out when sending a message failed due to a forbidden information flow),
and they include no security proofs.

There appears to be limited literature in general techniques for retrofitting
information flow control to arbitrary languages; however, one time-honored
technique is defining a fundamental calculus, for which other languages can be
desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
dependency by showing how various previous systems can be encoded in it; Tse and
Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
encodes several IFC systems into Paralocks.  However, this line of work is
primarily focused on static enforcements. 
%information flow control systems.

Our definition of isomorphism of information flow control languages in
Section~\ref{sec:concrete} is closely related to the idea of
\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
although as our system is deterministic, we do not use the theory in any
deep way.

It has long been observed that information flow control and monads are
closely related.  This observation has been used by Abadi et
al.~\cite{abadi+:core} to structure access to private data by protecting
it using a lattice of monads, one per security level. Russo et. al.~\cite{Russo+:Haskell08} extend this 
idea to languages with side-effects. Our system uses
monads in a conceptually different manner, where there is a single monad
representing the information flow control computational effects; this
is inline with the use of monads in other systems~\cite{Harrison05,lio,Devriese:2011}.
Devriese and Piessens~\cite{Devriese:2011} utilize monad
transformers as an essential component in their work.  However, their use
of monad transformers is to explain when extra constraints on a non-information
flow control aware base monad should be applied (i.e., during lifting).
Harrison and Hook~\cite{Harrison05} define a notion of \emph{atomic noninterference},
which is preserved through monad transformer application.  However, it is not
clear what is the relationship between this notion and traditional noninterference,
and their paper only proves a weaker property of no write down.

\cut{
\begin{itemize}
    \item Monads and IFC (Abadi~\cite{Abadi+:Core}, Tse~\cite{Tse:Zdancewic:ICFP04}, Harrison-Hook~\cite{Harrison05}, Crary~\cite{Crary:2005}, Devriese-Piessens~\cite{Devriese:2011})
    \item \Red{Operating systems approaches to IFC, which use coarse grained (Asbestos~\cite{efstathopoulos:asbestos}, HiStar~\cite{Zeldovich:2006})}
    \item \Red{Floating-label IFC systems, look at LIO paper (LIO~\cite{lio}, Breeze~\cite{Hritcu:2013:YIB:2497621.2498098})}
    \item JavaScript IFC related work, look at BrowBound. (ADSafe, xBook \Red{needs lookup})  Classify approaches into fine-grained (Hedin-Sabelfield~\cite{Hedin:2012}+JSFlow~\cite{JSFlow}, FlowFox~\cite{DeGroef:2012}, ConDOM~\cite{ConDOM}, Austin-Flanagan (sparse information labeling)~\cite{Austin:Flanagan:PLAS09}) or coarse-grained (BFlow~\cite{Yip:2009:PBS}, see Deian)
\item Secure multi-execution (FlowFox~\cite{DeGroef:2012}, Russo~\cite{Jaskelioff:SME})
\item Distributed programming languages (Cloud Haskell) plus IFC (Erlang (they check IFC when sending messages, no security proofs, assumes true isolation, not a floating labels)~\cite{Papagiannis_enforcinguser})
\end{itemize}

\Red{
Monads and IFC:

Basically, monads and IFC go together like toads and holes, or pigs and blankets, etc.  But the role the monad plays varies widely.  First, you have static systems (Abadi, Tse-Zdancewic), which utilize a lattice of monads: if a value is in a monad with a label that's too high, you're not allowed to unpeel it and look at the value inside.  Next, you have dynamic systems.  It seems pretty clear that making the IFC TCB be in a monad is a good idea, and the cluster of papers around LIO are all about that. Some of these papers talk about monad transformers: Devriese/Piessens focuses on how you might implement something like LIO by applying a monad transformer to some base monad to run the appropriate restrictions; Harrison/Hook do some more close to what we're doing, where they actually try to say something like "transformers do not interfere." But I can't tell if they're actually doing what we're doing, and their work has a number of unrelated technical restrictions.

In more detail:

Information Flow Enforcement in Monadic Libraries (Devriese/Piessens): Talks about how to use a monad transformer to take a non-IFC base monad and turn it into a IFC monad, namely the lifting operation should enforce extra constraints.  We take closely related ideas, and apply it to settings where there are not any monads.  Devriese/Piessens doesn't note the idea that untrusted monad transformers can be applied to add extra effects.

Achieving information flow security through monadic control of effects (Harrison/Hook): separation kernel is the basic idea behind our constructed (everything is partioned).  Notion of atomic noninterference between layers of effects, ``sufficient condition for atomic noninterference to be inherited through monad transformer application''.  But atomic noninterference is not proper noninterference as we've defined here! No proof of separation of kernels, instead prove weaker property no write down.

A Core Calculus of Dependency (Abadi et al): define a calculus, which calculi you want to prove IFC secure can be translated into.  It's a static system.  Why do they use monads?  Something about that
}

IFC for any language:

Gotta talk about secure multi-execution
}

\input{conclusion}

%{\frenchspacing\scriptsize
%\setlength{\bibsep}{2pt}
\bibliographystyle{abbrvnat}
\bibliography{local}

\end{document}

% Local Variables:
% TeX-master: "main.lhs.tex"
% TeX-command-default: "Make"
% End:

### 2014-03-02 paper/real.tex

@@
 %
-This isolation can be achieved using hardware protection
-mechanisms~\cite{Belay:2012:DSU:2387880.2387913} (similar to a simpler
-version of Wedge~\cite{Bittau:2008:WSA:1387589.1387611} with an
-information flow control policy).
+This isolation can be achieved using Dune's hardware protection
+mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
+version of Wedge~\cite{Belay:2012:DSU:2387880.2387913,
+Bittau:2008:WSA:1387589.1387611} with an information flow control
+policy.
 %
@@
 meaningless.
-%
-\Red{
-EZY: Suggest chopping
-
-    Of course, a more efficient message-passing approach, such as that of
-Singularity~\tocite{}, which simply passes a pointer to data the
-receiver at the cost of revoking the sender's access to the pages is
-also possible.
-%
-However, since we do not consider the isomorphism condition for this,
-we do not discuss it further.}
 
@@
 lightweight concurrency to implement the embedding in a more lightweight
-manner.  We briefly describe one such system, LIO,~\cite{lio} which
+manner.  We briefly describe one such system, LIO~\cite{lio}, which
 implements IFC as a library.
@@
 arbitrary effects that would ordinarily be allowed by the \verb|IO| monad,
-and it associates labels with threads (tasks).
+and it associates labels with tasks.
 %
@@
 One important aspect of using \verb|IO| as the base for this
-implementation is that it allows use of Haskell's efficient implementation of
-threads, channels, etc. (e.g., we use Haskell's \texttt{forkIO} to
-fork a lightweight thread in the case of |fork|), in contrast to
-defining them in a completely pure fashion (as suggested in Section~\ref{sec:monad}).
+implementation is that it allows use of Haskell's efficient
+implementation of threads, channels, etc. (e.g., in the concurrent
+version of LIO, we use Haskell's \texttt{forkIO} to fork a lightweight
+thread in the case of |fork|~\cite{stefan:addressing-covert}), in
+contrast to defining them in a completely pure fashion (as suggested
+in Section~\ref{sec:monad}).
 
@@
 %
-Here, the \emph{pure subset} of Haskell is the target language
-|targetLangHS|, while the monadic subset of Haskell in the \verb|LIO|
-monad is the IFC language.
+Here, the \emph{pure subset} of Haskell is the target language, while
+the monadic subset of Haskell in the \verb|LIO| monad is the IFC
+language.
 %
@@
 
-We describe SWAPI,~\tocite{} an implementation of this system for JavaScript.
+We describe SWAPI~\tocite{}, an implementation of this system for JavaScript.
 %
@@
  The Firefox implementation of SWAPI also considers the case where
- tasks share the JavaScript runtime event-loop, but the heap and
- execution context of each task is disjoint. This is similar to the
- single-heap language of Section~\ref{sec:concrete}.  However, since the heap
- separation is provided by the browser the browser, we do not discuss
- this further. The interested reader is referred to~\tocite{} for more
- details.
+ tasks share the JavaScript runtime (and are cooperatively scheduled
+ on the event-loop), but the heap and execution context of each task
+ is disjoint. This is similar to the single-heap language of
+ Section~\ref{sec:concrete}.  However, since the heap separation is
+ provided by the browser the browser, we do not discuss this further.
+ The interested reader is referred to~\tocite{} for more details.
 }
-
-From here, the IFC language functionality is implemented in the JS
-runtime, much like browser layout engines implement the DOM, and
-expose the new functions, e.g., |sandbox|, by attaching them to the JS
-global object.
 %
-To avoid termination timing attacks, each task created with |sandbox| is
+In SWAPI, the IFC language functionality is implemented in the JS
+runtime much like browser layout engines implement the DOM, and expose
+the new functions, e.g., \verb|getElementById|, by attaching them to
+the global JS object.
+%
+In turn, each task created with |sandbox| is
 executed in a separate thread, running a separate, \emph{fresh} instance of our
@@
 %
-Formally, \verb|sandbox| is defined with |klone(tS) =
+Formally, |sandbox| is defined with |klone(tS) =
 tS0|, where |tS0| is the global object corresponding to the standard
@@
 |iS(id') = Q|\\
-|iS' = iS [ id' mapsto (il', id,  ie') , Q ]|\\
+|iS' = iS [ mapsto id' (il', id,  ie') , Q ]|\\
 |ie = IT te|\\

### 2014-03-02 paper/retrofit.tex
notation in retrofit.

@@
 would also be possible.
+We note, however, that blocking receive can be implemented using
+our asynchronous primitives as follows:
+\begin{code}
+  brecvf ix1 ix2 ie @=
+  tab tab tab (IT (let tx = TI (recvf ix1 ix2 ie (IT tx)) in tx))
+\end{code}
 
@@
 \Red{TODO[ds]:
-  - move the async recv to text and out of the figure
   - clarify discussion on exceptions
@@
 \begin{code}
-ix1, ix2 <= brecv . ie @=
-tab tab tab (IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx))
 conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
@@
 \begin{align*}
-    & |let i = TI (sandbox (x, i' <= brecv . (IT (!(TI x)))))| \\
+    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))| \\
     & |in TI (send (IT (ref true)))|
@@
     & |toLabeled l te @= | \\
-    & |tab let pid = taskId; | \\
-    & |tab let i = TI (sandbox (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
-    & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
+    & |tab let i = taskId; | \\
+    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))| \\
 \end{align*}

### 2014-03-02 paper/concrete.tex
No hissy fits please
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     is true even with arbitrary additional premises $P$ that follow
-    the condition in Definition~\ref{def:npri}, since those
+    the condition in \Red{Definition (EZY: NPRI is missing)}, since those
     predicates only depend on |erase il ic1|, which is equivalent

### 2014-03-02 paper/concrete.tex
rephase of some paragraphs

--- 2014-03-02 paper/concrete.tex
@@
 The intention of our single heap implementation was to be more efficient
-by using one global heap, but conceptually maintain isolation between
-task by not allowing sharing of references between them.
+by using one global heap, but \emph{conceptually maintain isolation between
+task by not allowing sharing of references between them}.
 This intuition of having a different (potentially more efficient)
@@
 
-\Red{the next paragraph needs some rephrasing. We should say that if we 
-condense everything into one environment, then we need to ``simulate'' 
-the different policies. A bit more intro}
-A na\"ive attempt at our single heap semantics
-will not allow us to construct an isomorphism
-with the abstract language |specLangML alpha|, and instead highlights
-where things will go wrong.
-To successfully construct an isomorphism, our concrete semantics need
-to mirror the behavior of the abstract semantics, most importantly
-in the case where tasks interact.  Namely, at a fork and when sending
-or receiving messages, we take an expression from one task and
-execute it in the context of another task.  In the abstract semantics
-the fork rule is parameterized by the strategy |klone|, which defines
-what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
-we have motivated two choices}, namely the identity (to effectively
-clone the heap), or to start with an empty heap.
-In the latter case, this effectively means that existing addresses
-in the forked expression |ie| are no longer valid and the
-task gets stuck (and then removed by \textsc{I-noStep}).
-\todo{}{Is this actually true?  Currently the semantics are unclear.}
-To get the isomorphic behavior in the concrete semantics with a
-single heap, we would have to change the forked expression |ie| in
-such a way that all addresses get rewritten to fresh addresses
-that are guaranteed to not occur in the global heap.  Similarly,
-sending a memory address should take a similar approach, as addresses
+To obtain an isomorphism with our single heap semantics, we need to mimic the
+behavior of several heaps into one. The interesting cases are when forking and
+sending or receiving messages. These rules (see Section~\ref{sec:retrofit}) are
+parameterized by the strategy |klone|, which defines what heap the new task
+should execute with.  We have motivated two choices, namely the identity (to
+effectively clone the heap), or to start with an empty heap.
+
+In the first choice, the concrete semantics should essentially implement several
+heaps into one. For that, it creates a copy of everything reachable from the
+forked expression (not just the values for the memory addresses in the
+expression \Red{Ale:why not only the addresses?}), and replace all addresses
+correspondingly.  behavior of sending a memory address now depends on whether
+that address existed at the time the receiving task was forked; if it did, then
+the address should be rewritten to the new one, otherwise to a fresh one.
+
+In the latter case, this effectively means that the concrete semantics must
+change the forked expression |ie| in such a way that all addresses get rewritten
+to fresh addresses that are guaranteed to not occur in the global heap. As a
+consequence, existing addresses in the forked expression |ie| are no longer
+valid and the task gets stuck (and then removed by \textsc{I-noStep}).
+%\todo{}{Is this actually true?  Currently the semantics are unclear.}
+%To get the isomorphic behavior in the concrete semantics with a
+%single heap, we would have to change the forked expression |ie| in
+%such a way that all addresses get rewritten to fresh addresses
+%that are guaranteed to not occur in the global heap.  
+Similarly, sending a memory address should take a similar approach, as addresses
 for sent references will not exist in the receiving task.
 
-If |klone| is the identity function, then the abstract semantics
-effectively clone the heap on a fork.  To get an isomorphic
-behavior in the concrete, we would have to create a copy of everything
-reachable from the forked expression (not just the values for
-the memory addresses in the expression), and replace all addresses
-correspondingly.  Even worse, the behavior of sending a memory address
-now depends on whether that address existed at the time the receiving
-task was forked;  if it did, then the address should be rewritten to the
-new one, otherwise to a fresh address.
-Such a complicated behavior is contradictory to our initial motivation
-of implementing a single heap for efficiency.  But also the
-behavior of the simpler case where |klone| returns an empty heap is
-undesirable:  We rewrite addresses to fresh addresses, which will
-result in a stuck task whenever such an address is dereferenced.
+% A na\"ive attempt at our single heap semantics
+% will not allow us to construct an isomorphism
+% with the abstract language |specLangML alpha|, and instead highlights
+% where things will go wrong.
+% To successfully construct an isomorphism, our concrete semantics need
+% to mirror the behavior of the abstract semantics, most importantly
+% in the case where tasks interact.  Namely, at a fork and when sending
+% or receiving messages, we take an expression from one task and
+% execute it in the context of another task.  In the abstract semantics
+% the fork rule is parameterized by the strategy |klone|, which defines
+% what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
+% we have motivated two choices}, namely the identity (to effectively
+% clone the heap), or to start with an empty heap.
+% In the latter case, this effectively means that existing addresses
+% in the forked expression |ie| are no longer valid and the
+% task gets stuck (and then removed by \textsc{I-noStep}).
+% \todo{}{Is this actually true?  Currently the semantics are unclear.}
+% To get the isomorphic behavior in the concrete semantics with a
+% single heap, we would have to change the forked expression |ie| in
+% such a way that all addresses get rewritten to fresh addresses
+% that are guaranteed to not occur in the global heap.  Similarly,
+% sending a memory address should take a similar approach, as addresses
+% for sent references will not exist in the receiving task.
+
+% If |klone| is the identity function, then the abstract semantics
+% effectively clone the heap on a fork.  To get an isomorphic
+% behavior in the concrete, we would have to create a copy of everything
+% reachable from the forked expression (not just the values for
+% the memory addresses in the expression), and replace all addresses
+% correspondingly.  Even worse, the behavior of sending a memory address
+% now depends on whether that address existed at the time the receiving
+% task was forked;  if it did, then the address should be rewritten to the
+% new one, otherwise to a fresh address.
+% Such a complicated behavior is contradictory to our initial motivation
+% of implementing a single heap for efficiency.  But also the
+% behavior of the simpler case where |klone| returns an empty heap is
+% undesirable:  We rewrite addresses to fresh addresses, which will
+% result in a stuck task whenever such an address is dereferenced.
 
@@
 
-Again, we are modifying the IFC language semantics in a non-trivial way,
-which begs the question whether non-interference is preserved.
-Restricting the transitions in an information flow control
-system in general does not preserve non-interference as the following
-minimal example illustrates. \Red{Ale: I am not sure that the example is clear,
-  too abstract, at least, I don't get it. Propose to remove it, and just say 
-the top level idea: ``the restriction should not be based on secret data!''} 
-Consider a trivial state machine as shown
-in Figure~\ref{fig:trivial-sm}, whose second projection is classified
-secret.  With all three transitions, this language fulfills
-termination sensitive non-interference.  Furthermore, if the
-dashed transition
-is removed, the language continues to satisfy TSNI.  However, if any
-solid line is removed, the language fails TSNI.
+Generally speaking, we are modifying the IFC language semantics in a non-trivial
+way, which begs the question whether non-interference is preserved.  With this
+in mind, we device a general condition under which restrictions on transitions
+preserve non-interference. We require semantic rules to get restricted only
+based on information observable by the task triggering them. In that manner, the
+restriction does not depend on confidential information---a possible risk to
+jeopardize security. Below, the formal definition of such conditions for the
+abstract IFC language |specLang alpha targetLang|.
 
-\begin{figure}
-  States: $(x,y)$ for $x,y \in \{0,1\}$ \\
-  Erasure function: $f(x,y) = (x,\bullet)$
+%, such that non-interference is preserved.
 
-  \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
-    \node (A) {$(1,1)$};
-    \node (B) [right of=A] {$(1,0)$};
-    \node (C) [below of=A] {$(0,1)$};
-    \node (D) [right of=C] {$(0,0)$};
-    \draw[->] (A) to node {} (B);
-    \draw[->] (C) to node {} (D);
-    \draw[->, dashed] (B) to node {} (D);
-    \end{tikzpicture}\end{center}
+%system in general does not preserve non-interference as the following
+%minimal example illustrates.
 
-  \label{fig:trivial-sm}
-  \caption{A trivial state machine}
-\end{figure}
+% Again, we are modifying the IFC language semantics in a non-trivial way,
+% which begs the question whether non-interference is preserved.
+% Restricting the transitions in an information flow control
+% system in general does not preserve non-interference as the following
+% minimal example illustrates. \Red{Ale: I am not sure that the example is clear,
+%   too abstract, at least, I don't get it. Propose to remove it, and just say 
+% the top level idea: ``the restriction should not be based on secret data!''} 
+% Consider a trivial state machine as shown
+% in Figure~\ref{fig:trivial-sm}, whose second projection is classified
+% secret.  With all three transitions, this language fulfills
+% termination sensitive non-interference.  Furthermore, if the
+% dashed transition
+% is removed, the language continues to satisfy TSNI.  However, if any
+% solid line is removed, the language fails TSNI.
 
-To remedy this issue, we give a definition that gives a condition
-under which it is safe to restrict the abstract IFC language
-|specLang alpha targetLang|, such that non-interference is preserved.
+% \begin{figure}
+%   States: $(x,y)$ for $x,y \in \{0,1\}$ \\
+%   Erasure function: $f(x,y) = (x,\bullet)$
+
+%   \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
+%     \node (A) {$(1,1)$};
+%     \node (B) [right of=A] {$(1,0)$};
+%     \node (C) [below of=A] {$(0,1)$};
+%     \node (D) [right of=C] {$(0,0)$};
+%     \draw[->] (A) to node {} (B);
+%     \draw[->] (C) to node {} (D);
+%     \draw[->, dashed] (B) to node {} (D);
+%     \end{tikzpicture}\end{center}
+
+%   \label{fig:trivial-sm}
+%   \caption{A trivial state machine}
+% \end{figure}
+
+%To remedy this issue,
 

### 2014-03-02 paper/intro.tex

@@
 influence the computations in less sensitive workers.
-
-This coarse-grained approach as employed by SWAPI provides a number
-of advantages; (1) reduced runtime overhead because checks need only
+This coarse-grained approach provides a number
+of advantages: (1) reduced runtime overhead because checks need only
 be performed at isolation boundaries, (2) minimal changes to an
@@
 
-The recognition of the simplicity of this coarse-grained approach
+In fact, the simplicity of this coarse-grained approach
 to IFC allows us to generalize it to a large class of programming
-languages.  In this paper we identify the key concepts of coarse-grained
-dynamic IFC and show how these can be combined with a programming
-language, which we will call the target language.  We achieve this
+languages.  In this paper, we identify the key concepts of coarse-grained
+dynamic IFC and show how these can be combined with \emph{any} programming
+language.  We achieve this
 by using an embedding that combines the operational semantics
@@
 
-One challenge in the design of such a general IFC calculus that
-is supposed to work for a large class of programming languages is
-that the stated semantics might not correspond well to the
-semantics of a concrete implementation for a particular choice
-of target language.  We address this issue by using the notation
-of isomorphism to characterize a condition that guarantees
-non-interference of the concrete system without having to prove
-this property manually.
+One challenge in the design of our system is that the semantics for the
+retrofitted IFC language may not reflect the actual implementation in a
+particular choice of target language.  We partially address this issue
+by characterizing isomorphisms between the operational semantics of our
+defined language and a concrete implementation, showing that if this
+relationship holds, then noninterference in the abstract specification
+carries over to the concrete specification.
 
@@
       captures the essence of coarse-grained information flow control.
-  \item We show how a large class of target languages can be combined
+  We then show how a large class of target languages can be combined
   with this IFC language and prove that the resulting system provides
-  non-interference.
+  non-interference. (Section~\ref{sec:retrofit})
 %  \item We show how to extend the Matthews-Findler method from just
@@
   by means of an isomorphism, and show a class of restrictions on
-  the IFC calculus that preserves non-interference.
+  the IFC calculus that preserves non-interference. (Section~\ref{sec:formal})
   \item We sketch how the core IFC language can be enriched with
   more advanced concepts such as labeled values, privileges or a
-  notation of clearance.
+  notation of clearance. (Section~\ref{sec:extensions})
   \item We connect our formal semantics to real implementations of
   coarse-grained IFC systems for Javascript and Haskell, and explain
-  how our system could be used to enforce IFC in C.
+  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
   \item We informally connect our results to a monadic interpretation
-  of IFC which guided our design.
+      of IFC which guided our design. (Section~\ref{sec:monad})
 \end{itemize}

### 2014-03-02 paper/retrofit.tex
Finish pass over retrofit.

@@
 message with a label |il'| (which must be above the tasks current label |il|).
-Now, messages can only be received by a task if its current label is
+Messages can only be received by a task if its current label is
 at least as high as the label of the message.
-
 Specifically, receiving a message using
 \[ |recvf ix1 ix2 ie1 ie2| \]
-binds the senders task identifier and the message
+binds the message and the senders task identifier
 to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
@@
 Finally, in Figure~\ref{fig:embedding},
-we provide all of the rules responsible for actually carrying out the embedding.
+we provide all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
 The most important feature of this embedding is that every task maintains its own
@@
     \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
-    primitives for asynchronously communicating between
-    tasks and intermediating between the borders of the two languages.
+    and intermediating between the borders of the two languages.
 \end{itemize}
@@
 
+We note that it is possible to add rules for a natuaral embedding of
+expressions that occur in both languages.  In our specific example
+with |targetLangML|, we can choose to preserve booleans across
+language boundaries as follows:
+\begin{mathpar}
+\inferrule[I-bool]
+{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
+\and
+\inferrule[T-bool]
+{ |b member {true, false}| } {| intE (TI b) -> intE b |}
+\end{mathpar}
+
 For any target language |targetLang| and scheduling policy |alpha|, this
@@
 
-To get a feeling for how these operational semantics operate, we'd like to
+To get a feeling for how these operational semantics operate, we
+would like to
 describe a few sample programs, and what their outputs are.
@@
 happen if you attempted to send a reference to another task.
-
 \begin{align*}
@@
 \end{align*}
-
 It would be a violation of information flow if such an operation actually
@@
 will be received by the sandboxed task, but it will be a dangling pointer; the
-task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
+task will become stuck and removed from execution by \textsc{I-noStep}.  Readers
 who are curious whether or not a static discipline could be enforced to
-prevent these dangling pointers should check Section~\ref{sec:extensions}.)
+prevent these dangling pointers should check Section~\ref{sec:extensions}.
 
 \paragraph{Status of the heap after a sandbox}  Here is a program whose
-semantics depends on the definition of $\kappa$:
-
+semantics depends on the definition of |klone|:
 \begin{align*}
@@
 \end{align*}
-
-When $\kappa$ is the identity, the sandboxed task successfully dereferences
+When |klone| is the identity, the sandboxed task successfully dereferences
 the contents of the reference to be true twice (recall that references
@@
 for many information flow control systems is handling
-exceptions.~\cite{Hritcu:2013:YIB:2497621.2498098}  The key difficulty
+exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}.  The key difficulty
 appears when an exception must cross a stack boundary where the current
-label reverts back, i.e. across a \textbf{toLabeled} operator.~\cite{lio}
+label reverts back, i.e. across a |toLabeled| operator~\cite{lio}.
 If the exception crosses this boundary, it can leak information about the
@@
 an exception is self-evident: it should simply be removed from the scheduler.
-However, under a \emph{sequential scheduler}, the behavior of |sandbox|
-can be used to model the behavior of \textbf{toLabeled}:
-
+However, under a \emph{sequential scheduler} (such as |seqf|),
+the behavior of |sandbox|
+can be used to model the behavior of such an operator:
 \begin{align*}
@@
     & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
-    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))| \\
+    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
 \end{align*}
-
 When the sequential scheduler is used, the sandboxed task runs to
 completion before returning to the task that sandboxed it.  Thus,
-a task pool should rather be interpreted as a number of information-flow
+a task pool should rather be interpreted as a number of information flow
 aware stack frames.  To read the result of a |toLabeled| operation
@@
 the event of an exception inside of the |toLabeled| block:
+\todo{sh}{leaving this to ds, who wanted to finish the example}
 

### 2014-03-02 paper/formal.tex
Pass
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-In this section we present the formal security guarantees provided by
+In this section, we present the formal security guarantees provided by
 our embedding.
 %
-Concretely, we show that |specLang alpha targetLang| for, appropriate
-scheduler, satisfies non-interference~\cite{Goguen82},
+Concretely, we show that |specLang alpha targetLang|, with an appropriate
+scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
 without making any reference to properties of |targetLang|.
 %
-%As it turns out, 
-The precise scheduling policy |alpha| dictates
-the guarantee holding for programs with diverging tasks.
+The precise scheduling policy dictates
+what guarantee we can achieve for programs with diverging tasks.
 For a sequential scheduler |seqf|, we will only be able to show
@@
 %
-%Intuitively, we prove that an attacker does not learn
-%any sensitive information from a program by 
-Intuitively, term erasure allows us to show that a an attacker does not learn
+Intuitively, term erasure allows us to show that an attacker does not learn
 any sensitive information from a program if the program behaves identically
@@
 %
-To accommodate for this, we extend our formalism to account for
-programs with erased configurations and a function |erasef il| that
-performs erasures, usually by rewriting (parts of) configurations that
-are more sensitive than |il| to a new syntactic construct |bullet|.
+To accommodate for this, we extend our formalism with a function |erasef l| that
+performs erasures by mapping configurations to erased configurations,
+usually by rewriting (parts of) configurations that are more sensitive
+than |l| to a new syntactic construct |bullet|.
 %
-We can characterize the types of languages for which one can state
-a non-interference claim.
+In order for us to state non-interference, a language needs to include an
+erasure function:
 
-\Red{should be the environment colored in the definition?}
+%\Red{should be the environment colored in the definition?}
+%EZY: No, I don't think so.
 \begin{definition}[Information flow control language]
@@
     is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  This tuple is sometimes
-    augmented with a set of terminal configuration states $V
-    \subseteq |C|$ for which there are no possible further transitions.
-    \Red{It is a bit odd to extend a tuple ``sometimes'' and a |V| appears like from
-      nowhere. What about saying: Sometimes, we refer as |V| to set of 
+    configurations |tyerase C|.  Sometimes, we refer as |V| to set of
      terminal configurations in |C|, i.e., configurations states where
-     no further transitions are possible. If you agree, then the next sentence
-     where you said |V = ...| must be removed.}
+     no further transitions are possible.
 \end{definition}
@@
 Our language |specLang alpha (targetLang nop)| can be
-represented as |(ifc C, ifc V, .->, erasef il)|, such that
-$|ifc C| = |iS| \times \prod |it|$ and
+represented as |(ifc C, .->, erasef il)|, such that
+$|ifc C| = |iS| \times \prod |it|$.  Here,
 $|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
@@
 
-We note that the definition of |erasef il| captures the IFC
-language's attacker model. 
+The definition of |erasef il| is quite important, as it captures the IFC
+language's attacker model: elements that are erased cannot be observed
+by the attacker.
 %
 In our case, we assume that the attacker cannot observe sensitive tasks or
-messages, or even just the number of such entities.
+messages, or even the number of such entities.
 %
@@
 configuration that is |l|-equivalent to the first resultant configuration.
-\Red{TODO: Do we want a commutative diagram to illustrate this? Ale: I don't
-  think so, it is quite standard}
 

### 2014-03-02 paper/concrete.tex
typo.

@@
 We observe that the non-interference claims for the languages
-|specLang seqf targetLang| and |specLang roundrobin targetLang|
+|specLang seqf targetLang| and |specLang roundrobinf targetLang|
 in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly

### 2014-03-02 paper/concrete.tex
Move proofs and monads to the end.

--- 2014-03-02 paper/concrete.tex
@@
 \Red{Show the isomorphism.}
-
-\section{Proofs}
-\label{sec:proofs}
-
-In this section we will prove all theorems we have stated so far.
-We observe that the non-interference claims for the languages
-|specLang seqf targetLang| and |specLang roundrobin targetLang|
-in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
-from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
-respectively, about restricted IFC languages where the set
-of predicates is the set of always valid predicates.
-
-Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
-we state a lemma we will use.
-
-\begin{lemma}
-  \label{lemma:rr-tsni-general}
-  We consider, for any target language |targetLang|,
-  the restricted IFC language |restrictedLang alpha targetLang|
-  (according to Definition~\ref{def:restricted}).
-  Then,
-  for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
-  \begin{equation} \label{eq:tsni-lemma-lhs}
-  |ic1| \approx_{|il|} |ic2|
-  \qquad \text{and} \qquad
-  |ic1| |.->| |ic1'|
-  \end{equation}
-  there exists a configuration |ic2'| such that
-  \begin{equation} \label{eq:tsni-lemma-rhs}
-  |ic1'| \approx_{|il|} |ic2'|
-  \qquad \text{and} \qquad
-  |ic2| |.->|^* |ic2'|
-  \ \text{.}
-  \end{equation}
-\end{lemma}
-
-\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
-  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
-  The base case for derivations
-  of length 0 is trivial, allowing
-  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
-  the theorem holds for derivation sequences of length up to $n$, and show that it also
-  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
-  \[
-  |ic1| |.->| |ic1''| |.->|^n |ic1'|
-  \]
-  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
-  |ic''| with
-  \begin{equation} \label{eq:tsni-proof-1}
-  |ic1''| \approx_{|il|} |ic2''|
-  \qquad \text{and} \qquad
-  |ic2| |.->|^* |ic2''|
-  \end{equation}
-  Applying the induction hypothesis to
-  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
-  \begin{equation} \label{eq:tsni-proof-2}
-  |ic1'| \approx_{|il|} |ic2'|
-  \qquad \text{and} \qquad
-  |ic2''| |.->|^* |ic2'|
-  \end{equation}
-  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
-  us the right-hand side of the implication in the TSNI
-  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
-\end{proof}
-\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
-  First, we observe there must be at least one task in |ic1|, otherwise
-  it could not take a step.  Thus, |ic1| is of the form
-  |iconf iS1 (it1, its1)|.  Consider two cases:
-  \begin{itemize}
-    \item $|erase il it1|=|bullet|$.
-    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
-    where |lcurr| is the label of |it1|.
-    In this case, we do not need to take a step for
-    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
-    To see that, note that the tasks |its1| in |ic1| are left in the
-    same order and unmodified (the scheduling policy only
-    modifies the first task). The task |it1| either
-    gets dropped (by \textsc{I-noStep}), or
-    transforms into a task |it1'| as well as potentially spawning a new
-    task |it1''|.  Since both |it1'| and |it1''| have a label that is
-    at least as high as the label of |it1| (can be seen
-    by inspecting all reduction rules), they will get filtered
-    by |erasef il| in |ic1'|.  Therefore, the |il| equivalence of the
-    task list is guaranteed.
-    Lets consider the possible changes to |iS1|:
-    Only three reduction rules change |iS1|,
-    thus it suffices to consider these cases:
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      A new message triple with label |il'| gets added to the message
-      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
-      the triple will get erased.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      In this case, only the queue of
-      task |it1| can change, which gets erased.
-    \end{description}
-    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
-%    \alphacondition{We need all scheduling policies to not change the order
-%      of any tasks (except for the first one).  Newly spawned task can appear
-%      anywhere in the list.}
-    \item $|erase il it1|\neq|bullet|$.
-    Here, there must be a corresponding
-    task |it2| in |ic2|,
-    such that |it1=it2| (otherwise |ic1| and
-    |ic2| could not be |il| equivalent).
-    However, |it2| might not be at the beginning of the task list yet, but
-    all tasks occurring before it must get erased by |erasef il|.
-    In |ic2|, we can first take some number of steps until |it2| moves
-    to the front of the list.
-    This is the case regardless of any additional side conditions $P$ on
-    rules, because for all of these tasks, it can either take an actual
-    step, or it gets dropped by \textsc{I-noStep} (which is always
-    possible, as there cannot be an additional side condition on this
-    rule).  All tasks that didn't get dropped are still at a label
-    that isn't below |il| and thus get erased.
-
-%    \alphacondition{The scheduling policy must eventually let any task in
-%      the task list evaluate.  In particular, it cannot get stuck when the
-%      first task gets stuck, or keep executing a small number of tasks
-%      exclusively forever (e.g. just execute the first task all the time
-%      if it gets into an infinite loop).}
-
-    Therefore, after |ic2| has potentially executed some number of steps
-    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
-    respectively, don't get erased and are thus equivalent.
-    The task |it2| can now take exactly the same step as |it1|;  this
-    is true even with arbitrary additional premises $P$ that follow
-    the condition in Definition~\ref{def:npri}, since those
-    predicates only depend on |erase il ic1|, which is equivalent
-    to |erase il ic2|, and thus those predicates evaluate in the same way.
-    Thus, we only
-    need to argue that the potential differences in |iS1| and |iS2| cannot
-    have an influence on the execution (and we know |iS1| and |iS2| are
-    |il| equivalent).
-    Again, only sending and receiving will depend on, or change |iS|,
-    so we consider all these cases.
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      Here, the task |it2| will send the same message to the same
-      receiver queue. This
-      queue is either completely erased, or it is |il| equivalent.  In both
-      cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      When the tasks are receiving a message, then by the reduction rules
-      we know that they first filter the queue by the label
-      |lcurr| of |it1|.  We
-      also know that the queues are equivalent when filtered by the less
-      restrictive label |il|, thus the messages received (or dropped) from the
-      queue are equivalent.
-    \end{description}
-  \end{itemize}
-\end{proof}
-
-The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
-in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
-some cases are simpler due to the fact termination is not an issue
-(cf.~\tocite{} for a TINI proof of a similar system).

### 2014-03-02 paper/proofs.tex
Move proofs and monads to the end.

\section{Proofs}
\label{sec:proofs}

In this section we will prove all theorems we have stated so far.
We observe that the non-interference claims for the languages
|specLang seqf targetLang| and |specLang roundrobinf targetLang|
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
respectively, about restricted IFC languages where the set
of predicates is the set of always valid predicates.

Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
we state a lemma we will use.

\begin{lemma}
  \label{lemma:rr-tsni-general}
  We consider, for any target language |targetLang|,
  the restricted IFC language |restrictedLang alpha targetLang|
  (according to Definition~\ref{def:restricted}).
  Then,
  for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us the right-hand side of the implication in the TSNI
  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$.
    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
    where |lcurr| is the label of |it1|.
    In this case, we do not need to take a step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1| (can be seen
    by inspecting all reduction rules), they will get filtered
    by |erasef il| in |ic1'|.  Therefore, the |il| equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to |iS1|:
    Only three reduction rules change |iS1|,
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label |il'| gets added to the message
      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task |it1| can change, which gets erased.
    \end{description}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
    %    \alphacondition{We need all scheduling policies to not change the order
    %      of any tasks (except for the first one).  Newly spawned task can appear
    %      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.
    Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il| equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list.
    This is the case regardless of any additional side conditions $P$ on
    rules, because for all of these tasks, it can either take an actual
    step, or it gets dropped by \textsc{I-noStep} (which is always
    possible, as there cannot be an additional side condition on this
    rule).  All tasks that didn't get dropped are still at a label
    that isn't below |il| and thus get erased.

    %    \alphacondition{The scheduling policy must eventually let any task in
    %      the task list evaluate.  In particular, it cannot get stuck when the
    %      first task gets stuck, or keep executing a small number of tasks
    %      exclusively forever (e.g. just execute the first task all the time
    %      if it gets into an infinite loop).}

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
    respectively, don't get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  this
    is true even with arbitrary additional premises $P$ that follow
    the condition in \Red{Definition (EZY: NPRI is missing)}, since those
    predicates only depend on |erase il ic1|, which is equivalent
    to |erase il ic2|, and thus those predicates evaluate in the same way.
    Thus, we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il| equivalent).
    Again, only sending and receiving will depend on, or change |iS|,
    so we consider all these cases.
    \begin{description}
      \item[Case \textsc{I-send}]
      Here, the task |it2| will send the same message to the same
      receiver queue. This
      queue is either completely erased, or it is |il| equivalent.  In both
      cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      When the tasks are receiving a message, then by the reduction rules
      we know that they first filter the queue by the label
      |lcurr| of |it1|.  We
      also know that the queues are equivalent when filtered by the less
      restrictive label |il|, thus the messages received (or dropped) from the
      queue are equivalent.
    \end{description}
  \end{itemize}
\end{proof}

The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\tocite{} for a TINI proof of a similar system).

### 2014-03-02 paper/extensions.tex
minor
hmm.
wip

@@
 
-\subsection{IFC-aware language features}
+\subsection{IFC language features}
 \label{sec:extensions:labeled}
 
-\subsubsection{Labeled objects}
+\paragraph{Labeled values}
+%{
+%format unlabel = "\mathbf{unlabel}"
+%format label = "\mathbf{label}"
+%format labelOf = "\mathbf{labelOf}"
+In traditional language-based dynamic IFC systems, a label is
+associated with values.
+%
+Hence, a program that, for example, simply writes labeled messages to
+a labeled log can operate on both public and sensitive values.
+%
+In its simplest form, our coarse grained system requires that the
+current label of a task be at least at the level of the sensitive data
+to reflect the fact that such data is in scope.
 
-\paragraph{Labeled values}
+Thus, an extension that allows supports such fine-grained explicitly
+labeled values is essential.
+%
+While both LIO and Breeze have such values built-in, our IFC calculus
+can be used to encode the labeled values in terms of the |toLabeled|
+construct presented in Section~\ref{sec:retrofit}.
+%
+However, to allow for the inspection of the label of such values (as
+in LIO and Breeze) we assume, for simplicity, that the target
+language, e.g., the ML-like language from Figure~\ref{fig:ml},
+contains pairs: |te  ::= cdots inlinesep (te, te) inlinesep proji te|.
+%
+Directly, we can define constructs for labeling a value (|label|),
+inspecting the label of such values (|labelOf|), and inspecting the
+protected value (|unlabel|):
+\begin{code}
+label il te  @= let x = te in (il, toLabeled il x)
+labelOf te   @= proj1 te
+unlabel te   @= (proj2 te) (TI unit)
+\end{code}
+Here, the first projection of the pair contains the label, which is
+effectively public (to the task), while the second contains the
+``wrapped'' value.
+%
+Note that |label| first reduces to a values and then wraps it by
+sending it to task whose sole role is to protect the value with its
+current label (|il|).
+%
+The latter task protects the value with the supplied label by ensuring
+that any task that wishes to inspect the ```labeled value'' must 
+raise their current label before calling |unlabel|.
+% 
+We remark that this simply gives an encoding for labeled values; 
+a concrete implementation would likely rely on constructs that are
+cheaper than tasks, e.g., abstract data types.
+%}
+
 \paragraph{Labeled references}
@@
 
-\subsubsection{External effects}
+\subsection{External effects}
 \label{sec:extensions:external}

### 2014-03-02 paper/retrofit.tex
rm useless stuff.
retrofit updates
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 operational semantics and combine it with an \textit{{\color{blue} information
-flow control language}}.  For concreteness, we use a simple, untyped,
-ML-like language with mutable references as our target language.
-However, our technique will be indifferent to the actual target language
-chosen: it need only be prepared for interoperability by being expressed
+flow control language}}.  While our technique will be indifferent to the
+actual target language, for concreteness we give a simple, untyped,
+ML-like language to illustrate some examples, as well as express
+how the language should be prepared for interoperability
 in the style of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220},
-and for simplicity, we require the semantics to be deterministic.
-This procedure will
-equip the target language with primitives for implementing dynamic
+Findler~\cite{Matthews:2007:OSM:1190216.1190220}.
+We then equip this target language with primitives for implementing dynamic
 information control in the style of LIO~\cite{lio}, which we will
@@
 of some global machine state |tS|, some evaluation context |tE|,
-some expressions |te|, some set of values |tv| and a deterministic
+some expressions |te|, some set of values |tv| and a \emph{deterministic}
 reduction relation on full configurations $|tS| \times |tE| \times |te|$.
@@
 \inferrule[T-deref]
-{ |memberf (ta, tv) tS| }
+{ |memberf ((ta, tv)) tS| }
 {| conf tS (!ta) -> conf tS (tv) |}
@@
 evaluation context |curlyBlueE| represents the context
-of the current task which is running, including on the right-hand side
+of the current task which is running, which has three important pieces
+of state: the global message queues |iS|,
 the current label |il| (which protects the program counter of the task)
@@
 \todo{sh}{leaving this to ds, who wanted to finish the example}
-
-%   \Red{When both languages have booleans, it is relatively simple to define
-%   a natural embedding which preserves booleans across boundaries.}
-%   \begin{mathpar}
-%   \inferrule[I-bool]
-%   { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-%   \and
-%   \inferrule[T-bool]
-%   { |b member {true, false}| } {| intE (TI b) -> intE b |}
-%   \end{mathpar}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-03-02 paper/real.tex
pass over real.

@@
 %
-This isolation can be achieved using Dune's hardware protection
+For instance, this isolation can be achieved using Dune's hardware protection
 mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
@@
 %
-Using pages tables, a (trusted) IFC runtime could ensure that each task,
+Using page tables, a (trusted) IFC runtime could ensure that each task,
 implemented as a lightweight process, can only access the memory it
@@
 In addition, ring protection could be used to intercept syscalls performed by
-a task and only permit those corresponding to our IFC language (e.g.,
-|getLabel|, |send|).
+a task and only permit those corresponding to our IFC language (such as
+|getLabel| or |send|).
 %
-Although other sandboxing mechanisms can be used in place of Dune, we
-believe Dune's hardware protection mechanism would allow us to provide a 
-concrete implementation that is more efficient and simpler to reason about.
+Dunes hardware protection mechanism allows us to provide a concrete
+implementation that is efficient and relatively simple to reason
+about, but other sandboxing mechanisms could be used in place of Dune.
 
@@
 JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
-built-in functionality for I/O. (Capabilities such as the ability to
+built-in functionality for I/O. Capabilities such as the ability to
 mutate the DOM and read user input are APIs defined on top of the ECMAScript
-specification.)
+specification.
 %
@@
 
-We describe SWAPI~\tocite{}, an implementation of this system for JavaScript.
+We describe SWAPI~\tocite{}, an implementation of this system for JavaScript
+(which we here denote by |targetLangJS|).
 %
 The direct approach for implementing the embedded language |specLangJS roundrobinf| is
-by running multiple instances of the JS runtime, i.e., |targetLangJS|, in
+by running multiple instances of the JS runtime, i.e., in
 separate OS-level threads.\footnote{
@@
 |iS(id') = Q|\\
-|iS' = iS [ mapsto id' (il', id,  ie') , Q ]|\\
+|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
 |ie = IT te|\\
@@
 {|
-iconf iS (fullconf id il tS (iniEi (send id' il' ie)), ldots)
+iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
 .->
@@
 We remark that this is similar to the existing
-\texttt{postMessage} API used for iframe and Worker
+\texttt{postMessage} API used for iframe and worker
 communications~\cite{webworkers}.
@@
 %
-Similarly, they provide the Worker JS object~\cite{webworkers}, which allows
+Similarly, they provide the worker JS object~\cite{webworkers}, which allows
 JavaScript to execute code in separate threads with separate JS
@@
   %
-  Hence sharing and accessing objects such as the DOM across Worker
+  Hence sharing and accessing objects such as the DOM across worker
   threads is undefined.
@@
 However, a simple implementation of just associating a label with
-Workers and browsing context (iframes and top-level pages) to enforce
+workers and browsing context (iframes and top-level pages) to enforce
 IFC on the executing JavaScript is not sufficient, as APIs which
@@
 %
-For example, the initial global object of a Worker contains the
+For example, the initial global object of a worker contains the
 \texttt{XMLHttpRequest} (XHR) object, while the global object of a
@@
 %% %
-%% Hence, for example, a Worker that has read data only sensitive to
+%% Hence, for example, a worker that has read data only sensitive to
 %% \texttt{http://bank.ch} can communicate with this domain; only once

### 2014-03-02 paper/extensions.tex

--- 2014-03-02 paper/extensions.tex
@@
 
-\subsection{IFC-aware language features}
+\subsection{IFC language features}
 \label{sec:extensions:labeled}
 
-\subsubsection{Labeled objects}
+\paragraph{Labeled values}
+%{
+%format Lb = "\textbf{Labeled}"
+In traditional language-based dynamic IFC systems, a label is
+associated with values.
+%
+Hence, a program that, for example, simply writes labeled messages to
+a labeled log can operate on both public and sensitive values.
+%
+In its simplest form, our coarse grained system requires that the
+current label of a task be at least at the level of the sensitive data
+to reflect the fact that such data is in scope.
 
-\paragraph{Labeled values}
+Thus, an extension that allows supports such fine-grained explicitly
+labeled values is essential.
+%
+To this end, we extend the IFC calculus with explicitly labeled
+values, much like those of LIO and
+Breeze~\cite{Hritcu:2013:YIB:2497621.2498098, lio}: |tv ::= cdots
+inlinesep Lb il tv|.
+%
+Following LIO, we say that the value |tv| is protected by label |il|,
+while the label |il| itself is protected by the task's current label.
+%
+%
+Directly, the label of such values can be inspected the task without
+requiring the current label to be raised.
+%
+However, when a task wishes to inspect the protected value |tv|, it
+must first raise it label to at least |il| to reflect that it is
+incorporating data at such sensitivity level in its scope.
+%
+Similarly, when creating labeled values the label |il| must be above
+the current label; otherwise |il| cannot be said to protect the value.
+%
+(Importantly, we assumes that the |Lb| constructor cannot be accessed
+directly to construct or destruct such values without label checks.)
+%
+We omit the reduction rules for labeled values since they closely
+follow those presented in~\cite{lio}.
+%}
+
 \paragraph{Labeled references}

### 2014-03-02 paper/retrofit.tex

@@
 flow control language}}. While our technique will be indifferent to the
-actual target language, for concreteness we give a simple, untyped,
-ML-like language to illustrate some examples, as well as express
+actual target language, for concreteness we give a simple, untyped lambda calculus to illustrate some examples, as well as express
 how the language should be prepared for interoperability
@@
 
-\subsection{Target language: Mini-ML}
+\subsection{Target language: Mini-ES}
 
-In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
+In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
 mutable references, prepared for combination with an
@@
 
-\caption{Simple ML-like language |targetLangML|}
+\caption{Simple untyped lambda calculus |targetLangML|}
 \label{fig:ml}
@@
 \end{code}
-
-%   \begin{figure}
-%   Typing judgment: $|tyrule tG tS te tty|$
-%   \begin{mathpar}
-%   \inferrule[T-ty-address]
-%   {}
-%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
-%   \end{mathpar}
-
-%   \caption{Selected typing rules for ML-like language}
-%   \label{fig:ml-typing}
-%   \end{figure}
 

### 2014-03-02 paper/retrofit.tex
More pushing through retrofit
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
-operational semantics and combine it with an \textit{{\color{blue} information
-flow control language}}. While our technique will be indifferent to the
-actual target language, for concreteness we give a simple, untyped lambda calculus to illustrate some examples, as well as express
-how the language should be prepared for interoperability
-in the style of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220}.
-We then equip this target language with primitives for implementing dynamic
-information control in the style of LIO~\cite{lio}, which we will
-describe in more detail shortly.
+Our overall plan will be to take a \textbf{{\color{red} target
+language}} with a formal operational semantics and combine it with an
+\textit{{\color{blue} information flow control language}}.  For example,
+taking ECMAScript as the target language and combining it with our IFC
+language should produce the formal semantics for SWAPI.  In this
+presentation, we use a simple, untyped lambda calculus with mutable
+references in place of ECMAScript, to demonstrate some of the key
+properties without having too much detail; we discuss the proper
+embedding in more detail in Section~\ref{sec:real}.
 
@@
 mutable references, prepared for combination with an
-information flow control language.  The presentation is standard, but it
-is worth paying some attention to the Felleisen-Hieb reduction
-semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
+information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
+semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
 operational semantics of the system.  Our language defines an evaluation

### 2014-03-02 paper/extensions.tex
lb

@@
 %format Lb = "\textbf{Labeled}"
+%format label = "\textbf{label}"
 In traditional language-based dynamic IFC systems, a label is
@@
 values, much like those of LIO and
-Breeze~\cite{Hritcu:2013:YIB:2497621.2498098, lio}: |tv ::= cdots
+Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
 inlinesep Lb il tv|.
@@
 %
-Similarly, when creating labeled values the label |il| must be above
-the current label; otherwise |il| cannot be said to protect the value.
+When creating labeled values the label |il| must be above
+the current label; otherwise it cannot be said that protection has
+been transferred from the current label to |il|.
 %
-(Importantly, we assumes that the |Lb| constructor cannot be accessed
-directly to construct or destruct such values without label checks.)
+(For these rules, we assume that the |Lb| constructor is not part of
+the surface syntax and thus cannot be accessed directly to construct
+or destruct such values without label checks.)
 % 
@@
 follow those presented in~\cite{lio}.
+%
+Here, we lastly remark that that---albeit in a straight forward
+way---the TSNI proof must account for this new construct, since it
+appears in the IFC calculus.
 %}

### 2014-03-02 paper/extensions.tex
intro to labeled object shit

@@
 \label{sec:extensions:labeled}
+
+Different concrete IFC implementations may wish to extend our minimal
+system with labeled constructs appropriate for their envisioned
+applications.
+%
+For example, SWAPI provides a labeled version of the XHR object, while
+LIO implements a labeled file system, use in severer-side web
+applications~\cite{hails}.
+%
+However, since proving non-interference for a concrete implementation
+follows by isomorphism to the specification language, below we
+consider the addition of several labeled constructs to the latter.
+%
+We remark that that the non-interference proofs must account for the
+new constructs, since they amend the IFC calculus semantics (usually
+by addition).
 
@@
 follow those presented in~\cite{lio}.
-%
-Here, we lastly remark that that---albeit in a straight forward
-way---the TSNI proof must account for this new construct, since it
-appears in the IFC calculus.
 %}
 
-\paragraph{Labeled references}
-\paragraph{Labeled synchronization primitives}
+\paragraph{Labeled mutable references/variables/channels}
+%
+In a similar manner, extending the
 

### 2014-03-02 paper/retrofit.tex
Fixpoint
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 presentation, we use a simple, untyped lambda calculus with mutable
-references in place of ECMAScript, to demonstrate some of the key
+references and fixpoint in place of ECMAScript, to demonstrate some of the key
 properties without having too much detail; we discuss the proper
@@
 In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
-mutable references, prepared for combination with an
+mutable references and fixpoint, prepared for combination with an
 information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
@@
 tv   ::= \tx.te | true | false | ta
-te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
+te   ::= tv | tx | te te | if te then te else te
+       | ref te | !te | te := te | fix e
 tE   ::= tHole | tE te | tv tE | if tE then te else te
-       | ref tE | !tE | tE := te | tv := tE
+       | ref tE | !tE | tE := te | tv := tE | fix E
 
@@
 
+\and
+\inferrule[T-fix]
+{ }
+{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}
+
 %\and
@@
 
-Information flow control seeks to enforce a security policy known as
-\emph{non-interference}: public results must not depend on secret inputs.
-Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
-with data, which encodes a policy of whether or not data tagged with one
+Most modern, dynamic information flow control languages encode
+policy by associating a \emph{label}
+with data, which encodes whether or not data tagged with one
 label |l1| can flow to another label |l2| (written as |canFlowTo2 l1 l2|).
@@
 In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
-evaluation rules for a minimal information-flow control language.  The
-evaluation context |curlyBlueE| represents the context
-of the current task which is running, which has three important pieces
-of state: the global message queues |iS|,
-the current label |il| (which protects the program counter of the task)
-and the task ID |id|.
-
+evaluation rules for a minimal information-flow control language.  
 Ordinarily, information flow control languages are defined by directly
@@
 labels (|canFlowTo|, |lub| and |glb|),
-    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
-    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
+    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
+    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
         which interact with the global store of per-task message queues |iS|, and
-    \item a sandboxing operation allowing to spawn new
+    \item A sandboxing operation allowing to spawn new
     isolated tasks, which will be described in more detail in the
@@
 
-We consider asynchronous communication primitives that allow different
-tasks to exchange messages.
-When a task is sending a message using |send|, it also labels that
+While the first two bullet points are essentially universal to all
+floating-label systems, our choice of communication primitives is motivated
+by inter-worker communication in web browser APIs~\cite{webworkers}, but
+other choices such as blocking communication or labeled channels are possible.
+We describe some of the alternate possibilities in Section~\ref{sec:extensions}.
+These operations are all defined with respect to an evaluation context |curlyBlueE| represents the context
+of the current task which is running, which has three important pieces
+of state: the global message queues |iS|,
+the current label |il| (which protects the program counter of the task)
+and the task ID |id|.
+
+Our asynchronous communication primitives are worth some further
+discussion.  When a task is sending a message using |send|, it also labels that
 message with a label |il'| (which must be above the tasks current label |il|).
@@
 
-The particular choice of communication primitives has been motivated by
-inter-worker communication in web browser APIs~\Red{cite}, but
-other choices such as blocking communication or labeled channels
-would also be possible.
-We note, however, that blocking receive can be implemented using
+As a final remark, blocking receive can be (inefficiently) implemented using
 our asynchronous primitives as follows:
@@
   brecvf ix1 ix2 ie @=
-  tab tab tab (IT (let tx = TI (recvf ix1 ix2 ie (IT tx)) in tx))
+  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
 \end{code}

### 2014-03-02 paper/formal.tex
sp
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-However, even non-adversairal schedulers are not always safe.
+However, even non-adversarial schedulers are not always safe.
 Consider, for example, the sequential scheduling policy |seqf| given in
@@
 then the |sec| tasks's decision to diverge or not is directly leaked to a
-public entitiy.
+public entity.
 

### 2014-03-02 paper/extensions.tex
donezo with the extensions

@@
 %
-In a similar manner, extending the
+Extending the calculus with other labeled features, such as
+references, mutable variables (MVars)~\tocite{CH96}, or channels,
+follows in a similar way.
+%
+In these cases, however, we must keep track of the additional state
+(as opposed to the labeled value case which requires no additional
+bookkeeping).
+%
+While we can modify the IFC calculus to add such labeled state to each
+individual task, adding it to the system state |iS| leads to more
+interesting use cases.
+%
+Specifically, by amending |iS|, as in~\cite{lio,
+stefan;addressing-covert}, we can allow threads to use these
+constructs to synchronize, or communicate with constructs other than
+|send|/|recv| in a safe manner.
+%
+For example, when extending the calculus with labeled references, |iS|
+additionally contains a store that maps addresses to |(il, tv)| pairs
+which can be read and written to by different tasks through a labeled
+|ref| implementations.
+%
+Since such labeled constructs have also been considered before in other
+concurrent systems, we do not discuss them further.
 

### 2014-03-02 paper/extensions.tex
fix tocite

@@
 Extending the calculus with other labeled features, such as
-references, mutable variables (MVars)~\tocite{CH96}, or channels,
+references, mutable variables (MVars)~\cite{CH96}, or channels,
 follows in a similar way.

### 2014-03-02 paper/extensions.tex
some refs

@@
 %
-For example, this allows us to implement the scheduler of~\tocite{}
+For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
 that always schedules less sensitive threads first; this can be
@@
   When considering a label lattice that is not totally ordered, e.g.,
-  DCLabels~\tocite{}, this scheduling policy is considerably more
-  complex. See~\tocite{}.
+  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
+  considerably more complex. See~\cite{Kashyap:2011}.
 }
@@
 current formalization cannot directly be applied to more-powerful, but
-safe, scheduling policies, as considered in~\tocite{}.
+safe, scheduling policies, as considered by~\cite{russo2006securing}.
 %
@@
 consider \emph{low-determinism}, which states that a program is secure
-only if |l|-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers
+only if |l|-equivalent results are deterministic~\cite{Zdancewic:Myers:CSFW03,
+sabelfeld2003language}.
 

### 2014-03-02 paper/extensions.tex
Fix it
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 %
-When considering these extensions we also highlight some limitations
+When considering these extensions we also discuss some limitations
 of our approach.
@@
 For example, SWAPI provides a labeled version of the XHR object, while
-LIO implements a labeled file system, use in severer-side web
+LIO implements a labeled file system, use in server-side web
 applications~\cite{hails}.
 %
-However, since proving non-interference for a concrete implementation
-follows by isomorphism to the specification language, below we
-consider the addition of several labeled constructs to the latter.
+Below we
+consider the addition of several labeled constructs to the abstract specification.
 %

### 2014-03-02 paper/formal.tex
more refs

@@
   We believe that we can extend |specLang alpha (targetLang nop)| to
-  such models using the resource limits techniques of~\tocite{}.
+  such models using the resource limits techniques of~\cite{yangresource}.
   %

### 2014-03-02 paper/concrete.tex
Pass on concrete.

@@
 Otherwise, information can be trivially leaked by copying
-secret data into a reference in one task, and then
+secret data to a shared reference in one task, and then
 reading it again by a another task with a lower label.
@@
 To obtain an isomorphism with our single heap semantics, we need to mimic the
-behavior of several heaps into one. The interesting cases are when forking and
-sending or receiving messages. These rules (see Section~\ref{sec:retrofit}) are
-parameterized by the strategy |klone|, which defines what heap the new task
+behavior of several heaps with a single actual heap.
+The interesting cases are when we sandbox
+an expression, and when messages are sent and received.
+The rule for sandboxing is
+parameterized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
+which defines what heap the new task
 should execute with.  We have motivated two choices, namely the identity (to
@@
 
+{\color{red}
 In the first choice, the concrete semantics should essentially implement several
@@
 valid and the task gets stuck (and then removed by \textsc{I-noStep}).
-%\todo{}{Is this actually true?  Currently the semantics are unclear.}
 %To get the isomorphic behavior in the concrete semantics with a
@@
 for sent references will not exist in the receiving task.
+}
 
-% A na\"ive attempt at our single heap semantics
-% will not allow us to construct an isomorphism
-% with the abstract language |specLangML alpha|, and instead highlights
-% where things will go wrong.
-% To successfully construct an isomorphism, our concrete semantics need
-% to mirror the behavior of the abstract semantics, most importantly
-% in the case where tasks interact.  Namely, at a fork and when sending
-% or receiving messages, we take an expression from one task and
-% execute it in the context of another task.  In the abstract semantics
-% the fork rule is parameterized by the strategy |klone|, which defines
-% what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
-% we have motivated two choices}, namely the identity (to effectively
-% clone the heap), or to start with an empty heap.
-% In the latter case, this effectively means that existing addresses
-% in the forked expression |ie| are no longer valid and the
-% task gets stuck (and then removed by \textsc{I-noStep}).
-% \todo{}{Is this actually true?  Currently the semantics are unclear.}
-% To get the isomorphic behavior in the concrete semantics with a
-% single heap, we would have to change the forked expression |ie| in
-% such a way that all addresses get rewritten to fresh addresses
-% that are guaranteed to not occur in the global heap.  Similarly,
-% sending a memory address should take a similar approach, as addresses
-% for sent references will not exist in the receiving task.
+{\color{blue}
+In the latter case, this effectively means that existing addresses
+in the forked expression |ie| are no longer valid and the
+task gets stuck (and then removed by \textsc{I-noStep}).
+To get the isomorphic behavior in the concrete semantics with a
+single heap, we would have to change the forked expression |ie| in
+such a way that all addresses get rewritten to fresh addresses
+that are guaranteed to not occur in the heap.  Similarly,
+sending a memory address should take a similar approach, as addresses
+for sent references will not exist in the receiving task.
 
-% If |klone| is the identity function, then the abstract semantics
-% effectively clone the heap on a fork.  To get an isomorphic
-% behavior in the concrete, we would have to create a copy of everything
-% reachable from the forked expression (not just the values for
-% the memory addresses in the expression), and replace all addresses
-% correspondingly.  Even worse, the behavior of sending a memory address
-% now depends on whether that address existed at the time the receiving
-% task was forked;  if it did, then the address should be rewritten to the
-% new one, otherwise to a fresh address.
-% Such a complicated behavior is contradictory to our initial motivation
-% of implementing a single heap for efficiency.  But also the
-% behavior of the simpler case where |klone| returns an empty heap is
-% undesirable:  We rewrite addresses to fresh addresses, which will
-% result in a stuck task whenever such an address is dereferenced.
+If |klone| is the identity function, then the abstract semantics
+effectively clone the heap on a fork.  To get an isomorphic
+behavior in the concrete, we would have to create a copy of everything
+reachable from the forked expression (not just the values for
+the memory addresses in the expression), and replace all addresses
+correspondingly.  Even worse, the behavior of sending a memory address
+now depends on whether that address existed at the time the receiving
+task was forked;  if it did, then the address should be rewritten to the
+new one, otherwise to a fresh address.
+
+Such a complicated behavior is contradictory to our initial motivation
+of implementing a single heap for efficiency.  But even the
+behavior of the simpler case where |klone| returns an empty heap is
+undesirable:  We rewrite addresses to fresh addresses, which will
+result in a stuck task whenever such an address is dereferenced.
+}
 
@@
 
-Generally speaking, we are modifying the IFC language semantics in a non-trivial
-way, which begs the question whether non-interference is preserved.  With this
-in mind, we device a general condition under which restrictions on transitions
-preserve non-interference. We require semantic rules to get restricted only
-based on information observable by the task triggering them. In that manner, the
-restriction does not depend on confidential information---a possible risk to
-jeopardize security. Below, the formal definition of such conditions for the
+Again, we are modifying the IFC language semantics in a non-trivial way,
+which begs the question whether non-interference is preserved.
+Restricting the transitions in an information flow control
+system in general does not preserve non-interference.  Intuitively
+if the restriction depends on secret data, then a public thread
+can observe if some other task terminates or not, and by that obtain
+information about the secret data that was used to restrict the
+transition.
+With this in mind, we require semantic rules to get restricted only
+based on information observable by the task triggering them.
+This ensures that non-interference is preserved, as the
+restriction does not depend on confidential information.
+Below, we give the formal definition of this condition for the
 abstract IFC language |specLang alpha targetLang|.
-
-%, such that non-interference is preserved.
 
@@
 \textsc{I-fork} and \textsc{I-send}, which we define as
-\[ P(e) = \text{|ie| does not contain any address |ta|} \]
+\[ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) \]
+where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
 That is, we do not restrict any rules except for \textsc{I-fork}
@@
     {
-      \text{|ie| does not contain any |ta|}\\
+      \mathcal{AV}(|ie|) = \emptyset{}\\
       |iS' = bracket iS (mapsto id' nil)|\\
@@
     {
-      \text{|ie| does not contain any |ta|}\\
+      \mathcal{AV}(|ie|) = \emptyset{}\\
       |canFlowTo2 il il'|\\

### 2014-03-02 paper/proofs.tex
Minor change in proofs.

@@
 
-In this section we will prove all theorems we have stated so far.
-We observe that the non-interference claims for the languages
+In this section we prove all theorems we have stated.
+We first observe that the non-interference claims for the languages
 |specLang seqf targetLang| and |specLang roundrobinf targetLang|
@@
 from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
-respectively, about restricted IFC languages where the set
+respectively, where the set
 of predicates is the set of always valid predicates.

### 2014-03-02 paper/extensions.tex

@@
 Specifically, by amending |iS|, as in~\cite{lio,
-stefan;addressing-covert}, we can allow threads to use these
+stefan:addressing-covert}, we can allow threads to use these
 constructs to synchronize, or communicate with constructs other than

### 2014-03-02 paper/proofs.tex
more

@@
 some cases are simpler due to the fact termination is not an issue
-(cf.~\tocite{} for a TINI proof of a similar system).
+(cf.~\cite{lio} for a TINI proof of a similar system).

### 2014-03-02 paper/real.tex
more refs

@@
 Two of the systems we describe have been implemented: the Haskell
-system~\cite{lio} and the SWAPI~\tocite{} system; we leave the
+system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
 implementation of the IFC system for C to future work.
@@
 
-JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
+JavaScript (JS), as specified by ECMAScript~\cite{ecma}, does not have any
 built-in functionality for I/O. Capabilities such as the ability to
@@
 
-We describe SWAPI~\tocite{}, an implementation of this system for JavaScript
+We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
 (which we here denote by |targetLangJS|).
@@
  provided by the browser the browser, we do not discuss this further.
- The interested reader is referred to~\tocite{} for more details.
+ The interested reader is referred to~\cite{swapi} for more details.
 }
@@
 To address this, SWAPI additionally uses content security policy (CSP) and
-(iframe) sandboxes~\tocite{} to restrict external effects according to
-the label of a task (worker or browsing context).  Accomodating these
+(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
+to the label of a task (worker or browsing context).  Accomodating these
 features lies outside the purview of our formalism.

### 2014-03-02 paper/jcm.tex
file for jcm

@@
 
+\usepackage{url}
+
 \begin{document}
@@
 \title{
-Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control
+IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control
 }
@@
 \maketitle
-
 \input{abstract}
@@
 
-Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
-operational semantics and combine it with an \textit{{\color{blue} information
-flow control language}}.  For concreteness, we use a simple, untyped,
-ML-like language with mutable references as our target language.
-However, our technique will be indifferent to the actual target language
-chosen: it need only be prepared for interoperability by being expressed
-in the style of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220}.  This procedure will
-equip the target language with primitives for implementing dynamic
-information control in the style of LIO~\cite{lio}, which we will
-describe in more detail shortly.
+Our overall plan will be to take a \textbf{{\color{red} target
+language}} with a formal operational semantics and combine it with an
+\textit{{\color{blue} information flow control language}}.  For example,
+taking ECMAScript as the target language and combining it with our IFC
+language should produce the formal semantics for SWAPI.  In this
+presentation, we use a simple, untyped lambda calculus with mutable
+references and fixpoint in place of ECMAScript, to demonstrate some of the key
+properties without having too much detail; we discuss the proper
+embedding in more detail in Section~\ref{sec:real}.
 
@@
 with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
-a color copy of this paper, where target language nonterminals are colored red
-while IFC language nonterminals are colored blue.
-
-\subsection{Target language: Mini-ML}
-
-In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
-mutable references and errors, prepared for combination with an
-information flow control language.  The presentation is standard, but it
-is worth paying some attention to the Felleisen-Hieb reduction
-semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
+a color copy of this paper, where target language nonterminals are colored \textbf{{\color{red} red}}
+while IFC language nonterminals are colored \textit{{\color{blue} blue}}.
+
+\subsection{Target language: Mini-ES}
+
+In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
+mutable references and fixpoint, prepared for combination with an
+information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
+semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
 operational semantics of the system.  Our language defines an evaluation
 context \ensuremath{\tar{E}}; however, the evaluation rules have been expressed in terms
-of a different evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  To
+of a different evaluation context \ensuremath{\mathcal{E}_{\tar{\Sigma}}},
+following the approach of Matthews and
+Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
+semantics of multiple languages.  To
 derive the usual operational semantics for this language, the evaluation
-context merely needs to be defined as \ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\tar{\Sigma},\tar{E}\;[\mskip1.5mu \tar{e}\mskip1.5mu]}.
+context merely needs to be defined as \ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\tar{\Sigma},\tar{E}\left[\tar{e}\right]}.
 However, when we combine this language with an IFC language, we must
@@
 of some global machine state \ensuremath{\tar{\Sigma}}, some evaluation context \ensuremath{\tar{E}},
-some expressions \ensuremath{\tar{e}}, some set of values \ensuremath{\tar{v}} and a reduction
-relations on full configurations $\ensuremath{\tar{\Sigma}} \times \ensuremath{\tar{E}} \times \ensuremath{\tar{e}}$.
+some expressions \ensuremath{\tar{e}}, some set of values \ensuremath{\tar{v}} and a \emph{deterministic}
+reduction relation on full configurations $\ensuremath{\tar{\Sigma}} \times \ensuremath{\tar{E}} \times \ensuremath{\tar{e}}$.
 
@@
 \>[B]{}\tar{e}{}\<[6]%
-\>[6]{}\Coloneqq\tar{v}\mid \tar{x}\mid \tar{e}\;\tar{e}\mid \mathbf{if}\;\tar{e}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}\mid \mathbf{ref}\;\tar{e}\mid \mathbin{!}\tar{e}\mid \tar{e}\mathbin{:=}\tar{e}{}\<[E]%
+\>[6]{}\Coloneqq\tar{v}\mid \tar{x}\mid \tar{e}\;\tar{e}\mid \mathbf{if}\;\tar{e}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}{}\<[E]%
+\\
+\>[6]{}\hsindent{2}{}\<[8]%
+\>[8]{}\mid \mathbf{ref}\;\tar{e}\mid \mathbin{!}\tar{e}\mid \tar{e}\mathbin{:=}\tar{e}\mid \mathbf{fix}\;\Varid{e}{}\<[E]%
 \\
@@
 \>[6]{}\hsindent{2}{}\<[8]%
-\>[8]{}\mid \mathbf{ref}\;\tar{E}\mid \mathbin{!}\tar{E}\mid \tar{E}\mathbin{:=}\tar{e}\mid \tar{v}\mathbin{:=}\tar{E}{}\<[E]%
+\>[8]{}\mid \mathbf{ref}\;\tar{E}\mid \mathbin{!}\tar{E}\mid \tar{E}\mathbin{:=}\tar{e}\mid \tar{v}\mathbin{:=}\tar{E}\mid \mathbf{fix}\;E{}\<[E]%
 \\[\blanklineskip]%
@@
 \inferrule[T-deref]
-{ \ensuremath{(\tar{a},\tar{v})\;\mathbf{in}\;\tar{\Sigma}} }
+{ \ensuremath{(\tar{a},\tar{v})\in\tar{\Sigma}} }
 {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbin{!}\tar{a}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{v}\right]}}
@@
 
+\and
+\inferrule[T-fix]
+{ }
+{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbf{fix}\;(\lambda \Varid{x}.\Varid{e})\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\{\mskip1.5mu \mathbf{fix}\;(\lambda \Varid{x}.\Varid{e})\mathbin{/}\Varid{x}\mskip1.5mu\}\;\Varid{e}\right]}}
+
 %\and
@@
 
-\caption{Simple ML-like language \ensuremath{\Red{\lambda_{\text{ML}}}}}
+\caption{Simple untyped lambda calculus \ensuremath{\Red{\lambda_{\text{ES}}}}}
 \label{fig:ml}
@@
 
-Information flow control seeks to enforce a security policy known as
-\emph{non-interference}: public results must not depend on secret inputs.
-Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
-with data, which encodes a policy of whether or not data tagged with one
-label can flow to another label (written as \ensuremath{\flows}).
-Since our embedding is agnostic
-to the choice of labeling scheme, we simply represent labels with the metavariable
+Most modern, dynamic information flow control languages encode
+policy by associating a \emph{label}
+with data, which encodes whether or not data tagged with one
+label \ensuremath{l_{1}} can flow to another label \ensuremath{l_{2}} (written as \ensuremath{l_{1}\flows{}l_{2}}).
+Our embedding is agnostic to the choice of labeling scheme; we only
+require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
+with the partial order \ensuremath{\flows{}}.
+In this paper, we simply represent labels with the metavariable
 $l$, but do not discuss them in more detail.
@@
 In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
-evaluation rules for a minimal information-flow control language.  The
-evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
-of the current task which is running, including on the right-hand side
-the current label $l$ (which protects the program counter of the task)
-and the task ID $i$.
-
+evaluation rules for a minimal information-flow control language.  
 Ordinarily, information flow control languages are defined by directly
@@
     \item First-class labels, with label values $l$ as well as operations for computing on
-labels (\ensuremath{\flows}, \ensuremath{\lub} and \ensuremath{\glb}),
-    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
-    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
+labels (\ensuremath{\flows{}}, \ensuremath{\lub} and \ensuremath{\glb}),
+    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
+    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
         which interact with the global store of per-task message queues \ensuremath{\ifc{\Sigma}}, and
-    \item a sandboxing operation allowing to spawn new
+    \item A sandboxing operation allowing to spawn new
     isolated tasks, which will be described in more detail in the
@@
 
-The form of \textbf{send}/\textbf{recv} are \Red{inspired by methods of inter-worker communication
-in web browser APIs} \Red{cite}, however in Section~\ref{sec:extensions} we
-discuss other possible choices for information flow control aware communication
-primitives.  Their rules are different from non-IFC systems
-and worth commenting on: when a task places
-a message on the message queue of receiving task, it also labels that
-message with a label \ensuremath{\ifc{\Varid{l}}'} (which must be above the tasks current label \ensuremath{\ifc{\Varid{l}}})
-When the recipient reads out messages from its queue,
-messages whose labels do not
-flow to \ensuremath{\ifc{\Varid{l}}} are filtered out (denoted by \ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}}).
-Specifically, if \ensuremath{\ifc{\Theta}} is the empty list \ensuremath{\epsilon}, the
+While the first two bullet points are essentially universal to all
+floating-label systems, our choice of communication primitives is motivated
+by inter-worker communication in web browser APIs~\cite{webworkers}, but
+other choices such as blocking communication or labeled channels are possible.
+We describe some of the alternate possibilities in Section~\ref{sec:extensions}.
+These operations are all defined with respect to an evaluation context \ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}} represents the context
+of the current task which is running, which has three important pieces
+of state: the global message queues \ensuremath{\ifc{\Sigma}},
+the current label \ensuremath{\ifc{l}} (which protects the program counter of the task)
+and the task ID \ensuremath{\ifc{\Varid{i}}}.
+
+Our asynchronous communication primitives are worth some further
+discussion.  When a task is sending a message using \ensuremath{\mathbf{send}}, it also labels that
+message with a label \ensuremath{\ifc{l}'} (which must be above the tasks current label \ensuremath{\ifc{l}}).
+Messages can only be received by a task if its current label is
+at least as high as the label of the message.
+Specifically, receiving a message using
+\[ \ensuremath{\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}_{1}\ \mathbf{else}\ \ifc{\Varid{e}}_{2}} \]
+binds the message and the senders task identifier
+to local variables \ensuremath{\ifc{\Varid{x}}_{1}} and \ensuremath{\ifc{\Varid{x}}_{2}}, respectively, and then executes \ensuremath{\ifc{\Varid{e}}_{1}}.
+Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
+and that tasks continues its execution with \ensuremath{\ifc{\Varid{e}}_{2}}.
+We denote the filtering of the message queue by \ensuremath{\ifc{\Theta}\preceq\ifc{l}},
+which is defined as follows.
+If \ensuremath{\ifc{\Theta}} is the empty list \ensuremath{\epsilon}, the
 function is simply the identity function, i.e.,
-\ensuremath{\epsilon\preceq\ifc{\Varid{l}}\mathrel{=}\epsilon}; otherwise:
+\ensuremath{\epsilon\preceq\ifc{l}\mathrel{=}\epsilon}; otherwise:
 \[
-\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} = \left\{
+\ensuremath{(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{l}} = \left\{
 \begin{array}{l l}
-\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{if \ensuremath{\ifc{\Varid{l}}'\;\flows\;\ifc{\Varid{l}}}}\\
-\ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{otherwise}
+\ensuremath{(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{l}} & \quad \text{if \ensuremath{\ifc{l}'\;\flows{}\;\ifc{l}}}\\
+\ensuremath{\ifc{\Theta}\preceq\ifc{l}} & \quad \text{otherwise}
 \end{array} \right.
@@
 
-%   \begin{figure}
-%   Typing judgment: $|tyrule tG tS te tty|$
-%   \begin{mathpar}
-%   \inferrule[T-ty-address]
-%   {}
-%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
-%   \end{mathpar}
-
-%   \caption{Selected typing rules for ML-like language}
-%   \label{fig:ml-typing}
-%   \end{figure}
+As a final remark, blocking receive can be (inefficiently) implemented using
+our asynchronous primitives as follows:
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\mathbf{blockingRecv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}\triangleq{}{}\<[E]%
+\\
+\>[3]{}\ \ \;\ \ \;\ \ \;\ifc{^{\textrm{IT}}\lceil}\mathbf{fix}\;(\lambda \Varid{k}.\tar{_{\textrm{TI}}\lfloor}\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}\ \mathbf{else}\ \ifc{^{\textrm{IT}}\lceil}\Varid{k}\ifc{\rceil}\tar{\rfloor})\ifc{\rceil}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
 
@@
 \>[6]{}\Coloneqq{}\<[6E]%
-\>[11]{}\flows\mid \lub\mid \glb{}\<[E]%
+\>[11]{}\flows{}\mid \lub\mid \glb{}\<[E]%
 \\
@@
 \>[6]{}\Coloneqq{}\<[6E]%
-\>[11]{}\ifc{\Varid{i}}\mid \ifc{\Varid{l}}\mid \mathbf{true}\mid \mathbf{false}\mid \langle\rangle{}\<[E]%
+\>[11]{}\ifc{\Varid{i}}\mid \ifc{l}\mid \mathbf{true}\mid \mathbf{false}\mid \langle\rangle{}\<[E]%
 \\
@@
 \>[6]{}\Coloneqq{}\<[6E]%
-\>[11]{}\ifc{\Varid{v}}\mid \ifc{\Varid{x}}\mid \ifc{\Varid{e}}\;\otimes\;\ifc{\Varid{e}}\mid \mathbf{getLabel}\mid \mathbf{setLabel}\;\ifc{\Varid{e}}{}\<[E]%
+\>[11]{}\ifc{\Varid{v}}\mid \ifc{\Varid{x}}\mid \ifc{\Varid{e}}\;\otimes\;\ifc{\Varid{e}}\mid \mathbf{getLabel}\mid \mathbf{setLabel}\;\ifc{\Varid{e}}\mid \mathbf{taskId}{}\<[E]%
 \\
@@
 \>[8]{}\mid {}\<[8E]%
-\>[11]{}\mathbf{sandbox}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
+\>[11]{}\mathbf{sandbox}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \mathbf{recv}\ \ifc{\Varid{x}},\ifc{\Varid{x}}\;\mathbf{in}\;\ifc{\Varid{e}}\ \mathbf{else}\ \ifc{\Varid{e}}{}\<[E]%
 \\
@@
 \\
-\>[6]{}\hsindent{2}{}\<[8]%
-\>[8]{}\mid {}\<[8E]%
-\>[11]{}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
-\\
 \>[B]{}\ifc{\theta}{}\<[6]%
 \>[6]{}\Coloneqq{}\<[6E]%
-\>[11]{}(\ifc{\Varid{l}},\ifc{\Varid{i}}\;\ifc{\Varid{e}}){}\<[E]%
+\>[11]{}(\ifc{l},\ifc{\Varid{i}}\;\ifc{\Varid{e}}){}\<[E]%
 \\
@@
 
+\inferrule[I-getTaskId]
+{ }
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{taskId}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{i}}\right]}}
+
 \and
@@
 { }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{getLabel}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{l}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{getLabel}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{l}\right]}}
 
@@
 \inferrule[I-setLabel]
-{ \ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'} }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{setLabel}\;\ifc{\Varid{l}}'\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}}}
+{ \ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'} }
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{setLabel}\;\ifc{l}'\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}'}\left[\langle\rangle\right]}}
 %{|fresh (id')|}
@@
 {
-\ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
+\ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'}\\
 \ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
-\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
+\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{v}}),\ifc{\Theta}\right]}
 }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{v}}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}'}^{\ifc{\Varid{i}},\ifc{l}}\left[\langle\rangle\right]}}
 
@@
 {
-\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{\Varid{l}}\mathrel{=}\ifc{\theta}_{1},\mathbin{...},\ifc{\theta}_\Varid{k},(\ifc{\Varid{l}}',\ifc{\Varid{i}}',\ifc{\Varid{e}}')}\\
+\ensuremath{(\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{l})\mathrel{=}\ifc{\theta}_{1},\mathbin{...},\ifc{\theta}_\Varid{k},(\ifc{l}',\ifc{\Varid{i}}',\ifc{\Varid{v}})}\\
 \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}(\ifc{\theta}_{1},\mathbin{...},\ifc{\theta}_\Varid{k})\right]}\\
 }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}_{1}\;\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\{\mskip1.5mu \ifc{\Varid{e}}'\mathbin{/}\ifc{\Varid{x}}_{1},\ifc{\Varid{i}}'\mathbin{/}\ifc{\Varid{x}}_{2}\mskip1.5mu\}\;\ifc{\Varid{e}}_{1}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}_{1}\ \mathbf{else}\ \ifc{\Varid{e}}_{2}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}'}^{\ifc{\Varid{i}},\ifc{l}}\left[\{\mskip1.5mu \ifc{\Varid{v}}\mathbin{/}\ifc{\Varid{x}}_{1},\ifc{\Varid{i}}'\mathbin{/}\ifc{\Varid{x}}_{2}\mskip1.5mu\}\;\ifc{\Varid{e}}_{1}\right]}}
 
@@
 {
-\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{\Varid{l}}\mathrel{=}\epsilon}\\
+\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}})\preceq\ifc{l}\mathrel{=}\epsilon}\\
 \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\epsilon\right]}
 }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}_{1}\;\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\ifc{\Varid{e}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}_{1}\ \mathbf{else}\ \ifc{\Varid{e}}_{2}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}'}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{e}}_{2}\right]}}
 
 \inferrule[I-labelOp]
-{ \ensuremath{\llbracket \ifc{\Varid{l}}_{1}\;\otimes\;\ifc{\Varid{l}}_{2}\rrbracket\mathrel{=}\ifc{\Varid{v}}}}
-{ \ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{l}}_{1}\;\otimes\;\ifc{\Varid{l}}_{2}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{v}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}} }
+{ \ensuremath{\llbracket \ifc{l}_{1}\;\otimes\;\ifc{l}_{2}\rrbracket\mathrel{=}\ifc{\Varid{v}}}}
+{ \ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{l}_{1}\;\otimes\;\ifc{l}_{2}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{v}}\right]} }
 \end{mathpar}
@@
 \Red{TODO[ds]:
-  - move the async recv to text and out of the figure
   - clarify discussion on exceptions
   - fix the toLabled
-  - add taskIDs to ruls
 }
 Finally, in Figure~\ref{fig:embedding},
-we provide all of the rules responsible for actually carrying out the embedding.
+we provide all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
 The most important feature of this embedding is that every task maintains its own
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{53}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}_{\infty}.\ifc{\Varid{e}}\triangleq{}{}\<[E]%
-\\
-\>[B]{}\ \ \;\ \ \;\ \ \;\ifc{^{\textrm{IT}}\lceil}\;\mathbf{let}\;\tar{x}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;{}\<[53]%
-\>[53]{}\ifc{^{\textrm{IT}}\lceil}\tar{x}\ifc{\rceil}\tar{\rfloor}\;\mathbf{in}\;\tar{x}\ifc{\rceil}{}\<[E]%
-\\
-\>[B]{}\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\tar{e}\ifc{]}_\tar{T}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots{}\<[E]%
-\\
-\>[B]{}\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots{}\<[E]%
+\>[B]{}\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\tar{e}\ifc{]}_\tar{T}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots{}\<[E]%
+\\
+\>[B]{}\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{e}}\right]\triangleq{}\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots{}\<[E]%
 \\
@@
 \ensuremath{\tar{\Sigma}'\mathrel{=}\kappa\;(\tar{\Sigma})}\\
-\ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}\\
-\ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{\Sigma}', \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{\Varid{l}}}}\\
+\ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \tar{\Sigma}, \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}}}\\
+\ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{\Sigma}', \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{l}}}\\
 \ensuremath{\textrm{fresh}(\ifc{\Varid{i}}')}
 }
-{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Conid{F}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}
+{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\text{sandbox}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}
 
@@
 {\ensuremath{}}
-{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\Conid{D}}}}(\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}
+{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\text{done}}}}(\langle \tar{\Sigma}, \ifc{\Varid{v}}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots)}}
 
@@
 {\ensuremath{\ifc{\Sigma};\ifc{\Varid{t}},\ldots\not\overset{\alpha}{\hookrightarrow}}}
-{\ensuremath{\ifc{\Sigma};\ifc{\Varid{t}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\Conid{N}}}}(\ifc{\Varid{t}},\ldots)}}
+{\ensuremath{\ifc{\Sigma};\ifc{\Varid{t}},\ldots\overset{\alpha}{\hookrightarrow}\ifc{\Sigma};\alpha_{{\tiny\mathrm{\text{noStep}}}}(\ifc{\Varid{t}},\ldots)}}
 
@@
 { }
-{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\ifc{\rceil}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}
+{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\ifc{\rceil}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{e}}\right]}}
 
@@
     \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-    \item We reinterpret \ensuremath{\mathcal{E}} to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.
-These rules only operate on the first task in the task pool, which by convention, is the only task executing.
+    \item We reinterpret \ensuremath{\mathcal{E}} to be evaluation contexts on task pools, providing definitions for \ensuremath{\mathcal{E}_{\tar{\Sigma}}} and \ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}}.
+These rules only operate on the first task in the task pool, which by convention is the only task executing.
     \item We reinterpret \ensuremath{\rightarrow}, an operation on a single task, in terms of \ensuremath{\hookrightarrow}, operation on task pools.
-The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.
-Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
-    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
+The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy \ensuremath{\alpha}.
+Not all schedulers preserve non-interference, and we provide two specific schedules in Figure~\ref{fig:scheduler}.
+    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
+    and intermediating between the borders of the two languages.
 \end{itemize}
 
-The \textsc{I-sandbox} rule is of particular interest, as it is intended to allow users
-to create new tasks.  When a new task is created, there is a question of what the
-global state of the new task should be; this is defined in terms of a function $\kappa$.
-Conservatively, $\kappa$ may be simply thought of as the identity function, in which
+The \textsc{I-sandbox} rule allows to create a new isolated task that
+executes separately from the existing tasks (and can be communicated
+with via \ensuremath{\mathbf{send}} and \ensuremath{\mathbf{recv}}).  When the new task is created, there
+is the question of what the target language state of the new task should
+be.  Our rule is stated generically in terms of a function \ensuremath{\kappa}.
+Conservatively, \ensuremath{\kappa} may be simply thought of as the identity
+function, in which
 case the semantics of sandbox are such that the state of the target language is \emph{cloned}
-when sandboxing occurs.  However, this is not necessary: it is also valid for $\kappa$
+when sandboxing occurs.  However, this is not necessary: it is also valid for \ensuremath{\kappa}
 to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
-discussion of the implications of the choice of $\kappa$.
+discussion of the implications of the choice of \ensuremath{\kappa}, but all our
+non-interference claims will hold regardless of the choice of \ensuremath{\kappa}.
+
+We note that it is possible to add rules for a natural embedding of
+expressions that occur in both languages.  In our specific example
+with \ensuremath{\Red{\lambda_{\text{ES}}}}, we can choose to preserve booleans across
+language boundaries as follows:
+\begin{mathpar}
+\inferrule[I-bool]
+{ \ensuremath{\Varid{b}\;\in\;\{\mskip1.5mu \mathbf{true},\mathbf{false}\mskip1.5mu\}}  } {\ensuremath{\ifc{E}\ifc{[}\ifc{^{\textrm{IT}}\lceil}\Varid{b}\ifc{\rceil}\ifc{]}\rightarrow\ifc{E}\ifc{[}\Varid{b}\ifc{]}}}
+\and
+\inferrule[T-bool]
+{ \ensuremath{\Varid{b}\;\in\;\{\mskip1.5mu \mathbf{true},\mathbf{false}\mskip1.5mu\}} } {\ensuremath{\tar{E}\tar{[}\tar{_{\textrm{TI}}\lfloor}\Varid{b}\tar{\rfloor}\tar{]}\rightarrow\tar{E}\tar{[}\Varid{b}\tar{]}}}
+\end{mathpar}
 
@@
 happen if you attempted to send a reference to another task.
-
 \begin{align*}
-    & \ensuremath{\mathbf{let}\;\Varid{i}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;(\Varid{x},\Varid{i'}\Leftarrow\mathbf{recv}_{\infty}.\ifc{^{\textrm{IT}}\lceil}\mathbin{!}\tar{_{\textrm{TI}}\lfloor}\Varid{x}\tar{\rfloor}\ifc{\rceil})\tar{\rfloor}} \\
+    & \ensuremath{\mathbf{let}\;\Varid{i}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;(\mathbf{blockingRecv}\ \Varid{x},\Varid{i'}\;\mathbf{in}\;\ifc{^{\textrm{IT}}\lceil}\mathbin{!}\tar{_{\textrm{TI}}\lfloor}\Varid{x}\tar{\rfloor}\ifc{\rceil})\tar{\rfloor}} \\
     & \ensuremath{\mathbf{in}\;\tar{_{\textrm{TI}}\lfloor}\mathbf{send}\;\ifc{^{\textrm{IT}}\lceil}\mathbf{ref}\;\mathbf{true}\ifc{\rceil}\tar{\rfloor}}
 \end{align*}
-
 It would be a violation of information flow if such an operation actually
@@
 will be received by the sandboxed task, but it will be a dangling pointer; the
-task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
+task will become stuck and removed from execution by \textsc{I-noStep}.  Readers
 who are curious whether or not a static discipline could be enforced to
-prevent these dangling pointers should check Section~\ref{sec:extensions}.)
+prevent these dangling pointers should check Section~\ref{sec:extensions}.
 
 \paragraph{Status of the heap after a sandbox}  Here is a program whose
-semantics depends on the definition of $\kappa$:
-
+semantics depends on the definition of \ensuremath{\kappa}:
 \begin{align*}
@@
 \end{align*}
-
-When $\kappa$ is the identity, the sandboxed task successfully dereferences
+When \ensuremath{\kappa} is the identity, the sandboxed task successfully dereferences
 the contents of the reference to be true twice (recall that references
@@
 for many information flow control systems is handling
-exceptions.~\cite{Hritcu:2013:YIB:2497621.2498098}  The key difficulty
+exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}.  The key difficulty
 appears when an exception must cross a stack boundary where the current
-label reverts back, i.e. across a \textbf{toLabeled} operator.~\cite{lio}
+label reverts back, i.e. across a \ensuremath{\mathbf{toLabeled}} operator~\cite{lio}.
 If the exception crosses this boundary, it can leak information about the
@@
 an exception is self-evident: it should simply be removed from the scheduler.
-However, under a \emph{sequential scheduler}, the behavior of \ensuremath{\mathbf{sandbox}}
-can be used to model the behavior of \textbf{toLabeled}:
-
+However, under a \emph{sequential scheduler} (such as \ensuremath{\textsc{Seq}}),
+the behavior of \ensuremath{\mathbf{sandbox}}
+can be used to model the behavior of such an operator:
 \begin{align*}
-    & \ensuremath{\mathbf{toLabeled}\;\Varid{l}\;\tar{e}\triangleq{}} \\
-    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{pid}\mathrel{=}\mathbf{taskId};} \\
-    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{i}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;\Varid{l}\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\mathbf{send}\;\Varid{pid}\;\Varid{l}\;\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}\tar{\rfloor}\ifc{\rceil}\tar{\rfloor}} \\
-    & \ensuremath{\ \ \;\mathbf{in}\;(\lambda \anonymous .\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;\Varid{l}\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\Varid{x},\anonymous \Leftarrow\mathbf{recv}.\Varid{x}\tar{\rfloor})} \\
+    & \ensuremath{\mathbf{toLabeled}\;l\;\tar{e}\triangleq{}} \\
+    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{i}\mathrel{=}\mathbf{taskId};} \\
+    & \ensuremath{\ \ \;\mathbf{let}\;\Varid{j}\mathrel{=}\tar{_{\textrm{TI}}\lfloor}\mathbf{sandbox}\;\ifc{^{\textrm{IT}}\lceil}\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;l\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\mathbf{send}\;\Varid{i}\;l\;\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}\tar{\rfloor}\ifc{\rceil}\tar{\rfloor}} \\
+    & \ensuremath{\ \ \;\mathbf{in}\;(\lambda \anonymous .\tar{_{\textrm{TI}}\lfloor}\mathbf{setLabel}\;l\tar{\rfloor};\tar{_{\textrm{TI}}\lfloor}\mathbf{recv}\ \Varid{x},\anonymous \;\mathbf{in}\;\Varid{x}\ \mathbf{else}\ \langle\rangle\tar{\rfloor})}
 \end{align*}
-
 When the sequential scheduler is used, the sandboxed task runs to
 completion before returning to the task that sandboxed it.  Thus,
-a task pool should rather be interpreted as a number of information-flow
+a task pool should rather be interpreted as a number of information flow
 aware stack frames.  To read the result of a \ensuremath{\mathbf{toLabeled}} operation
@@
 In this setting, it is also clear that exceptions should not cross boundaries,
-as seen in \ensuremath{\mathbf{toLabeled}\;\Varid{l}\;\mathbf{fail};\mathbf{true}}, which evaluates to \ensuremath{\mathbf{true}} no matter even in
+as seen in \ensuremath{\mathbf{toLabeled}\;l\;\mathbf{fail};\mathbf{true}}, which evaluates to \ensuremath{\mathbf{true}} no matter even in
 the event of an exception inside of the \ensuremath{\mathbf{toLabeled}} block:
-
-%   \Red{When both languages have booleans, it is relatively simple to define
-%   a natural embedding which preserves booleans across boundaries.}
-%   \begin{mathpar}
-%   \inferrule[I-bool]
-%   { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-%   \and
-%   \inferrule[T-bool]
-%   { |b member {true, false}| } {| intE (TI b) -> intE b |}
-%   \end{mathpar}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{sh}{leaving this to ds, who wanted to finish the example}
+
 \section{Security guarantees}
@@
 
-In this section we present the formal security guarantees provided by
+In this section, we present the formal security guarantees provided by
 our embedding.
 %
-Concretely, we show that \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})} for, appropriate
-scheduler, satisfies non-interference~\cite{Goguen82},
+Concretely, we show that \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}, with an appropriate
+scheduler \ensuremath{\alpha}, satisfies non-interference~\cite{Goguen82},
 without making any reference to properties of \ensuremath{\Red{\lambda}}.
 %
-%As it turns out, 
-The precise scheduling policy \ensuremath{\alpha} dictates
-the guarantee holding for programs with diverging tasks.
+The precise scheduling policy dictates
+what guarantee we can achieve for programs with diverging tasks.
 For a sequential scheduler \ensuremath{\textsc{Seq}}, we will only be able to show
@@
 %
-To accommodate for this, we extend our formalism to account for
-programs with erased configurations and a function \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} that
-performs erasures, usually by rewriting (parts of) configurations that
-are more sensitive than \ensuremath{\ifc{\Varid{l}}} to a new syntactic construct \ensuremath{\bullet}.
-%
-We can characterize the types of languages for which one can state
-a non-interference claim.
-
-\Red{should be the environment colored in the definition?}
+To accommodate for this, we extend our formalism with a function \ensuremath{\varepsilon_{l}} that
+performs erasures by mapping configurations to erased configurations,
+usually by rewriting (parts of) configurations that are more sensitive
+than \ensuremath{l} to a new syntactic construct \ensuremath{\bullet}.
+%
+In order for us to state non-interference, a language needs to include an
+erasure function:
+
+%\Red{should be the environment colored in the definition?}
+%EZY: No, I don't think so.
 \begin{definition}[Information flow control language]
-    An information flow control language \ensuremath{\textbf{L}} is a tuple \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})}, where $\ensuremath{\Delta}$ is the type of machine configurations (members
+    An information flow control language \ensuremath{\textbf{L}} is a tuple \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{l})}, where $\ensuremath{\Delta}$ is the type of machine configurations (members
     of which are usually denoted by the meta-variable \ensuremath{c}), \ensuremath{\hookrightarrow} is a
-    reduction relation between machine configurations and \ensuremath{\varepsilon_{\Varid{l}}\mathbin{:}\Delta\rightarrow\varepsilon(\Delta)}
+    reduction relation between machine configurations and \ensuremath{\varepsilon_{l}\mathbin{:}\Delta\rightarrow\varepsilon(\Delta)}
     is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations \ensuremath{\varepsilon(\Delta)}.  This tuple is sometimes
-    augmented with a set of terminal configuration states $V
-    \subseteq \ensuremath{\Delta}$ for which there are no possible further transitions.
-    \Red{It is a bit odd to extend a tuple ``sometimes'' and a \ensuremath{V} appears like from
-      nowhere. What about saying: Sometimes, we refer as \ensuremath{V} to set of 
+    configurations \ensuremath{\varepsilon(\Delta)}.  Sometimes, we refer as \ensuremath{V} to set of
      terminal configurations in \ensuremath{\Delta}, i.e., configurations states where
-     no further transitions are possible. If you agree, then the next sentence
-     where you said \ensuremath{V\mathrel{=}\mathbin{...}} must be removed.}
+     no further transitions are possible.
 \end{definition}
@@
 Our language \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda}\;\!\!)} can be
-represented as \ensuremath{(\ifc{\Delta},\ifc{V},\overset{\alpha}{\hookrightarrow},\varepsilon_{\ifc{\Varid{l}}})}, such that
-$\ensuremath{\ifc{\Delta}} = \ensuremath{\ifc{\Sigma}} \times \prod \ensuremath{\ifc{\Varid{t}}}$ and
+represented as \ensuremath{(\ifc{\Delta},\overset{\alpha}{\hookrightarrow},\varepsilon_{\ifc{l}})}, such that
+$\ensuremath{\ifc{\Delta}} = \ensuremath{\ifc{\Sigma}} \times \prod \ensuremath{\ifc{\Varid{t}}}$.  Here,
 $\ensuremath{\ifc{V}} = \ensuremath{\ifc{\Sigma}} \times \ensuremath{\ifc{\Varid{t}}}_V$, where $\ensuremath{\ifc{\Varid{t}}}_V \subset \ensuremath{\ifc{\Varid{t}}}$ is the
@@
 containing \ensuremath{\bullet}, and Figure~\ref{fig:erasure} gives the precise definition for
-our erasure function \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}.
+our erasure function \ensuremath{\varepsilon_{\ifc{l}}}.
 %
 A task and its corresponding message queue is completely removed from the task
-list if its label does not flow to the attacker observation level \ensuremath{\ifc{\Varid{l}}}.
+list if its label does not flow to the attacker observation level \ensuremath{\ifc{l}}.
 Otherwise, we apply the erasure function homomorphically and remove any message
-from the task's message queue that are more sensitive than \ensuremath{\ifc{\Varid{l}}}.
+from the task's message queue that are more sensitive than \ensuremath{\ifc{l}}.
 
@@
 \begin{align*}
-  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma};\ifc{\Varid{ts}})\mathrel{=}\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma});\text{filter}\;(\lambda \ifc{\Varid{t}}.\ifc{\Varid{t}}\mathrel{=}\bullet)\;(\text{map}\;\varepsilon_{\ifc{\Varid{l}}}\;\ifc{\Varid{ts}})}\\
-  &\ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}} \begin{cases}
-    \ensuremath{\bullet} & \ensuremath{\ifc{\Varid{l}}'\;\not\flows\;\ifc{\Varid{l}}} \\
-    \ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}} & \text{otherwise}
+  &\ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Sigma};\ifc{\Varid{ts}})\mathrel{=}\varepsilon_{\ifc{l}}(\ifc{\Sigma});\text{filter}\;(\lambda \ifc{\Varid{t}}.\ifc{\Varid{t}}\mathrel{=}\bullet)\;(\text{map}\;\varepsilon_{\ifc{l}}\;\ifc{\Varid{ts}})}\\
+  &\ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}'}} \begin{cases}
+    \ensuremath{\bullet} & \ensuremath{\ifc{l}'\;\not\flows{}\;\ifc{l}} \\
+    \ensuremath{\langle \tar{\Sigma}, \ifc{\Varid{e}}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}'}} & \text{otherwise}
   \end{cases} \\
-  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\emptyset)\mathrel{=}\emptyset}\\
-  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right])\mathrel{=}} \begin{cases}
-    \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma})} & \text{\ensuremath{\ifc{\Varid{l}}'\;\not\flows\;\ifc{\Varid{l}}}, where \ensuremath{\ifc{\Varid{l}}'} is}\\
+  &\ensuremath{\varepsilon_{\ifc{l}}(\emptyset)\mathrel{=}\emptyset}\\
+  &\ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right])\mathrel{=}} \begin{cases}
+    \ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Sigma})} & \text{\ensuremath{\ifc{l}'\;\not\flows{}\;\ifc{l}}, where \ensuremath{\ifc{l}'} is}\\
     & \text{the label of thread \ensuremath{\ifc{\Varid{i}}}} \\
-    \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Sigma})\left[\ifc{\Varid{i}}\mapsto{}\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Theta})\right]} & \text{otherwise}
+    \ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Sigma})\left[\ifc{\Varid{i}}\mapsto{}\varepsilon_{\ifc{l}}(\ifc{\Theta})\right]} & \text{otherwise}
   \end{cases} \\
-  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Theta})\mathrel{=}\ifc{\Theta}\preceq\ifc{\Varid{l}}}\\
-  &\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\Varid{v})\mathrel{=}\Varid{v}}
+  &\ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Theta})\mathrel{=}\ifc{\Theta}\preceq\ifc{l}}\\
+  &\ensuremath{\varepsilon_{\ifc{l}}(\Varid{v})\mathrel{=}\Varid{v}}
 \end{align*}
@@
 configurations.  In all other cases, including target-language constructs,
-\ensuremath{\varepsilon_{\ifc{\Varid{l}}}} is applied homomorphically.  \label{fig:erasure} }
+\ensuremath{\varepsilon_{\ifc{l}}} is applied homomorphically.  \label{fig:erasure} }
 \end{figure}
 
-We note that the definition of \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} captures the IFC
-language's attacker model. 
+The definition of \ensuremath{\varepsilon_{\ifc{l}}} is quite important, as it captures the IFC
+language's attacker model: elements that are erased cannot be observed
+by the attacker.
 %
 In our case, we assume that the attacker cannot observe sensitive tasks or
-messages, or even just the number of such entities.
-%
-While such assumptions are standard~\tocite{}, our definitions allow for
+messages, or even the number of such entities.
+%
+While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
+stefan:addressing-covert}, our definitions allow for
 stronger attackers that may be able to inspect resource usage.\footnote{
   We believe that we can extend \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda}\;\!\!)} to
-  such models using the resource limits techniques of~\tocite{}.
+  such models using the resource limits techniques of~\cite{yangresource}.
   %
@@
 Non-interference relies on the definition of an attacker's observational power at
-security level \ensuremath{\Varid{l}}, which is typically defined as an equivalence
-relation---called \ensuremath{\Varid{l}}-equivalence---on configurations.  An attacker
-at level \ensuremath{\Varid{l}} cannot
-distinguish two configurations that are \ensuremath{\Varid{l}}-equivalent.
+security level \ensuremath{l}, which is typically defined as an equivalence
+relation---called \ensuremath{l}-equivalence---on configurations.  An attacker
+at level \ensuremath{l} cannot
+distinguish two configurations that are \ensuremath{l}-equivalent.
 %
@@
 %
-\begin{definition}[\ensuremath{\Varid{l}}-equivalence]
-    In a language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})}, two machine configurations
+\begin{definition}[\ensuremath{l}-equivalence]
+    In a language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{l})}, two machine configurations
     \ensuremath{c,c'\in\Delta} are considered $l$-equivalent, written as \ensuremath{c\approx_lc'},
-    if \ensuremath{\varepsilon_{\Varid{l}}(c)\mathrel{=}\varepsilon_{\ifc{\Varid{l}}}(c')}.
+    if \ensuremath{\varepsilon_{l}(c)\mathrel{=}\varepsilon_{\ifc{l}}(c')}.
 \end{definition}
@@
 Intuitively, we can now state that a language satisfies non-interference if an
-attacker at level \ensuremath{\Varid{l}} cannot distinguish the runs of any two \ensuremath{\Varid{l}}-equivalent
+attacker at level \ensuremath{l} cannot distinguish the runs of any two \ensuremath{l}-equivalent
 configurations.
@@
 \begin{definition}[Termination Sensitive Non-Interference (TSNI)]
-  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} is termination
-  sensitive non-interfering if for any label \ensuremath{\Varid{l}}, and configurations
+  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{l})} is termination
+  sensitive non-interfering if for any label \ensuremath{l}, and configurations
   \ensuremath{c_{1},c_{1}',c_{2}\;\in\;\Delta}, if
   \begin{equation} \label{eq:tsni-lhs}
-    \ensuremath{c_{1}} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}}
+    \ensuremath{c_{1}} \approx_{\ensuremath{l}} \ensuremath{c_{2}}
     \qquad \text{and} \qquad
@@
   \begin{equation} \label{eq:tsni-rhs}
-    \ensuremath{c_{1}'} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}'}
+    \ensuremath{c_{1}'} \approx_{\ensuremath{l}} \ensuremath{c_{2}'}
      \qquad \text{and} \qquad
@@
 %
-In other words if we take two \ensuremath{\Varid{l}}-equivalent configurations, then for every
+In other words if we take two \ensuremath{l}-equivalent configurations, then for every
 intermediate step taken by the first configuration, there is a corresponding
 number of steps that the second configuration can take to result in a
-configuration that is \ensuremath{\Varid{l}}-equivalent to the first resultant configuration.
-\Red{TODO: Do we want a commutative diagram to illustrate this? Ale: I don't
-  think so, it is quite standard}
+configuration that is \ensuremath{l}-equivalent to the first resultant configuration.
 
@@
 
-However, even non-adversairal schedulers are not always safe.
+However, even non-adversarial schedulers are not always safe.
 Consider, for example, the sequential scheduling policy \ensuremath{\textsc{Seq}} given in
@@
 %
-Concretely, consider a target language similar to \ensuremath{\Red{\lambda_{\text{ML}}}} with an
+Concretely, consider a target language similar to \ensuremath{\Red{\lambda_{\text{ES}}}} with an
 additional expression terminal \ensuremath{\tar{\Uparrow}} that denotes a divergent computation,
-i.e., \ensuremath{\tar{\Uparrow}} always reduces to \ensuremath{\tar{\Uparrow}} and a simple label lattice \ensuremath{\{\mskip1.5mu \mathsf{pub},\mathsf{sec}\mskip1.5mu\}} such that \ensuremath{\mathsf{pub}\;\flows\;\mathsf{sec}}, but \ensuremath{\mathsf{sec}\;\not\flows\;\mathsf{pub}}.
+i.e., \ensuremath{\tar{\Uparrow}} always reduces to \ensuremath{\tar{\Uparrow}} and a simple label lattice \ensuremath{\{\mskip1.5mu \mathsf{pub},\mathsf{sec}\mskip1.5mu\}} such that \ensuremath{\mathsf{pub}\;\flows{}\;\mathsf{sec}}, but \ensuremath{\mathsf{sec}\;\not\flows{}\;\mathsf{pub}}.
 Consider the following two configurations in this language:
@@
 then the \ensuremath{\mathsf{sec}} tasks's decision to diverge or not is directly leaked to a
-public entitiy.
+public entity.
 
@@
 \begin{definition}[Termination insensitive non-interference (TINI)]
-  A language \ensuremath{(\Delta,V,\hookrightarrow,\varepsilon_{\Varid{l}})} is termination
-  insensitive non-interfering if for any label \ensuremath{\Varid{l}}, and configurations
+  A language \ensuremath{(\Delta,V,\hookrightarrow,\varepsilon_{l})} is termination
+  insensitive non-interfering if for any label \ensuremath{l}, and configurations
   \ensuremath{c_{1},c_{2}\;\in\;\Delta} and \ensuremath{c_{1}',c_{2}'\;\in\;V}, it holds that
   \[
-    (\ensuremath{c_{1}} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}}
+    (\ensuremath{c_{1}} \approx_{\ensuremath{l}} \ensuremath{c_{2}}
     \;\;\land\;\;
@@
     \implies
-    \ensuremath{c_{1}'} \approx_{\ensuremath{\Varid{l}}} \ensuremath{c_{2}'}
+    \ensuremath{c_{1}'} \approx_{\ensuremath{l}} \ensuremath{c_{2}'}
   \]
@@
 
-TSNI states that if we take two \ensuremath{\Varid{l}}-equivalent configurations, and both
+TSNI states that if we take two \ensuremath{l}-equivalent configurations, and both
 configurations reduce to final configurations (i.e.,
@@
 possible further transitions), then the end configurations are also
-\ensuremath{\Varid{l}}-equivalent.
+\ensuremath{l}-equivalent.
 %
@@
 undesirable, e.g., for performance reasons.
-For instance, for the language \ensuremath{\Red{\lambda_{\text{ML}}}}, our presentation so far
+For instance, for the language \ensuremath{\Red{\lambda_{\text{ES}}}}, our presentation so far
 requires a separate heap per task, which is not very practical.
@@
 More precisely, instead of using a configuration of the form
-\[\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\langle \tar{\Sigma}_{2}, \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{\Varid{l}}_{2}}\;\ldots}\]
+\[\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}_{1}, \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{l}_{1}},\langle \tar{\Sigma}_{2}, \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{l}_{2}}\;\ldots}\]
 we would like a single global heap as in
-\[\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\langle \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{\Varid{l}}_{2}},\ldots}\]
+\[\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{\Varid{e}}_{1}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{l}_{1}},\langle \ifc{\Varid{e}}_{2}\rangle^{\ifc{\Varid{i}}_{2}}_{\ifc{l}_{2}},\ldots}\]
 
@@
 The intention of our single heap implementation was to be more efficient
-by using one global heap, but conceptually maintain isolation between
-task by not allowing sharing of references between tasks.
+by using one global heap, but \emph{conceptually maintain isolation between
+task by not allowing sharing of references between them}.
 This intuition of having a different (potentially more efficient)
@@
 \begin{definition}[Isomorphism of information-flow control languages]
-  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} is \textit{isomorphic} to a
-  language \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{\Varid{l}})} if there exist total functions \ensuremath{\Varid{f}\mathbin{:}\Delta\rightarrow\Delta'} and \ensuremath{\Varid{f}^{-1}\mathbin{:}\Delta'\rightarrow\Delta} such that \ensuremath{\Varid{f}\circ\Varid{f}^{-1}\mathrel{=}id_{\Delta}} \ensuremath{\Varid{f}^{-1}\circ\Varid{f}\mathrel{=}id_{\Delta'}}.
+  A language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{l})} is \textit{isomorphic} to a
+  language \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{l})} if there exist total functions \ensuremath{\Varid{f}\mathbin{:}\Delta\rightarrow\Delta'} and \ensuremath{\Varid{f}^{-1}\mathbin{:}\Delta'\rightarrow\Delta} such that \ensuremath{\Varid{f}\circ\Varid{f}^{-1}\mathrel{=}id_{\Delta}} \ensuremath{\Varid{f}^{-1}\circ\Varid{f}\mathrel{=}id_{\Delta'}}.
 Furthermore, \ensuremath{\Varid{f}} and \ensuremath{\Varid{f}^{-1}} are functorial (e.g.
@@
   not have to be functorial over \ensuremath{\hookrightarrow}, we call the
-  language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{\Varid{l}})} \textit{weakly isomorphic} to
-  \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{\Varid{l}})}.
+  language \ensuremath{(\Delta,\hookrightarrow,\varepsilon_{l})} \textit{weakly isomorphic} to
+  \ensuremath{(\Delta',\hookrightarrow',\varepsilon'_{l})}.
 \end{definition}
@@
 
-A na\"ive attempt at our single heap semantics
-will not allow us to construct an isomorphism
-with the abstract language \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda_{\text{ML}}})}, and instead highlights
-where things will go wrong.
-To successfully construct an isomorphism, our concrete semantics need
-to mirror the behavior of the abstract semantics, most importantly
-in the case where tasks interact.  Namely, at a fork and when sending
-or receiving messages, we take an expression from one task and
-execute it in the context of another task.  In the abstract semantics
-the fork rule is parameterized by the strategy \ensuremath{\kappa}, which defines
-what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
-we have motivated two choices}, namely the identity (to effectively
-clone the heap), or to start with an empty heap.
+To obtain an isomorphism with our single heap semantics, we need to mimic the
+behavior of several heaps with a single actual heap.
+The interesting cases are when we sandbox
+an expression, and when messages are sent and received.
+The rule for sandboxing is
+parameterized by the strategy \ensuremath{\kappa} (cf.\ Section~\ref{sec:retrofit}),
+which defines what heap the new task
+should execute with.  We have motivated two choices, namely the identity (to
+effectively clone the heap), or to start with an empty heap.
+
+{\color{red}
+In the first choice, the concrete semantics should essentially implement several
+heaps into one. For that, it creates a copy of everything reachable from the
+forked expression (not just the values for the memory addresses in the
+expression \Red{Ale:why not only the addresses?}), and replace all addresses
+correspondingly.  behavior of sending a memory address now depends on whether
+that address existed at the time the receiving task was forked; if it did, then
+the address should be rewritten to the new one, otherwise to a fresh one.
+
+In the latter case, this effectively means that the concrete semantics must
+change the forked expression \ensuremath{\ifc{\Varid{e}}} in such a way that all addresses get rewritten
+to fresh addresses that are guaranteed to not occur in the global heap. As a
+consequence, existing addresses in the forked expression \ensuremath{\ifc{\Varid{e}}} are no longer
+valid and the task gets stuck (and then removed by \textsc{I-noStep}).
+%To get the isomorphic behavior in the concrete semantics with a
+%single heap, we would have to change the forked expression |ie| in
+%such a way that all addresses get rewritten to fresh addresses
+%that are guaranteed to not occur in the global heap.  
+Similarly, sending a memory address should take a similar approach, as addresses
+for sent references will not exist in the receiving task.
+}
+
+{\color{blue}
 In the latter case, this effectively means that existing addresses
@@
 task gets stuck (and then removed by \textsc{I-noStep}).
-\todo{}{Is this actually true?  Currently the semantics are unclear.}
 To get the isomorphic behavior in the concrete semantics with a
@@
 such a way that all addresses get rewritten to fresh addresses
-that are guaranteed to not occur in the global heap.  Similarly,
+that are guaranteed to not occur in the heap.  Similarly,
 sending a memory address should take a similar approach, as addresses
@@
 new one, otherwise to a fresh address.
+
 Such a complicated behavior is contradictory to our initial motivation
-of implementing a single heap for efficiency.  But also the
+of implementing a single heap for efficiency.  But even the
 behavior of the simpler case where \ensuremath{\kappa} returns an empty heap is
@@
 result in a stuck task whenever such an address is dereferenced.
+}
 
@@
 Section~\ref{sec:extensions:types}.
-In a dynamically type languages such as \ensuremath{\Red{\lambda_{\text{ML}}}}, we might
+In a dynamically type languages such as \ensuremath{\Red{\lambda_{\text{ES}}}}, we might
 restrict the transition for \ensuremath{\mathbf{sandbox}} and \ensuremath{\mathbf{send}} to only allow expressions
@@
 
-Again we are modifying the IFC language semantics in a non-trivial way,
+Again, we are modifying the IFC language semantics in a non-trivial way,
 which begs the question whether non-interference is preserved.
-Note that restricting the transitions in an information flow control
-system in general does not preserve non-interference as the following
-minimal example illustrates.
-Consider a trivial state machine as shown
-in Figure~\ref{fig:trivial-sm}, whose second projection is classified
-secret.  With all three transitions, this language fulfills
-termination sensitive non-interference.  Furthermore, if the
-dashed transition
-is removed, the language continues to satisfy TSNI.  However, if any
-solid line is removed, the language fails TSNI.
-
-\begin{figure}
-  States: $(x,y)$ for $x,y \in \{0,1\}$ \\
-  Erasure function: $f(x,y) = (x,\bullet)$
-
-  \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
-    \node (A) {$(1,1)$};
-    \node (B) [right of=A] {$(1,0)$};
-    \node (C) [below of=A] {$(0,1)$};
-    \node (D) [right of=C] {$(0,0)$};
-    \draw[->] (A) to node {} (B);
-    \draw[->] (C) to node {} (D);
-    \draw[->, dashed] (B) to node {} (D);
-    \end{tikzpicture}\end{center}
-
-  \label{fig:trivial-sm}
-  \caption{A trivial state machine}
-\end{figure}
-
-To remedy this issue, we give a definition that gives a condition
-under which it is safe to restrict the abstract IFC language
-\ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}, such that non-interference is preserved.
+Restricting the transitions in an information flow control
+system in general does not preserve non-interference.  Intuitively
+if the restriction depends on secret data, then a public thread
+can observe if some other task terminates or not, and by that obtain
+information about the secret data that was used to restrict the
+transition.
+With this in mind, we require semantic rules to get restricted only
+based on information observable by the task triggering them.
+This ensures that non-interference is preserved, as the
+restriction does not depend on confidential information.
+Below, we give the formal definition of this condition for the
+abstract IFC language \ensuremath{L_\text{IFC}(\alpha,\Red{\lambda})}.
+
+%system in general does not preserve non-interference as the following
+%minimal example illustrates.
+
+% Again, we are modifying the IFC language semantics in a non-trivial way,
+% which begs the question whether non-interference is preserved.
+% Restricting the transitions in an information flow control
+% system in general does not preserve non-interference as the following
+% minimal example illustrates. \Red{Ale: I am not sure that the example is clear,
+%   too abstract, at least, I don't get it. Propose to remove it, and just say 
+% the top level idea: ``the restriction should not be based on secret data!''} 
+% Consider a trivial state machine as shown
+% in Figure~\ref{fig:trivial-sm}, whose second projection is classified
+% secret.  With all three transitions, this language fulfills
+% termination sensitive non-interference.  Furthermore, if the
+% dashed transition
+% is removed, the language continues to satisfy TSNI.  However, if any
+% solid line is removed, the language fails TSNI.
+
+% \begin{figure}
+%   States: $(x,y)$ for $x,y \in \{0,1\}$ \\
+%   Erasure function: $f(x,y) = (x,\bullet)$
+
+%   \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
+%     \node (A) {$(1,1)$};
+%     \node (B) [right of=A] {$(1,0)$};
+%     \node (C) [below of=A] {$(0,1)$};
+%     \node (D) [right of=C] {$(0,0)$};
+%     \draw[->] (A) to node {} (B);
+%     \draw[->] (C) to node {} (D);
+%     \draw[->, dashed] (B) to node {} (D);
+%     \end{tikzpicture}\end{center}
+
+%   \label{fig:trivial-sm}
+%   \caption{A trivial state machine}
+% \end{figure}
+
+%To remedy this issue,
 
@@
   rule), we call
-  \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\alpha,\Red{\lambda})} a restricted IFC language
+  \ensuremath{L_\text{IFC}^{\mathcal{P}}(\alpha,\Red{\lambda})} a restricted IFC language
   if its definition is equivalent to the abstract language
@@
   The reduction rules are restricted
-  by adding a predicate $P$ from $\mathcal P$ to the premise of
+  by adding a predicate $P \in \mathcal P$ to the premise of
   all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
   can depend only on the \textit{erased} configuration
-  \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c})}, where \ensuremath{\ifc{\Varid{l}}} is the label of the first task
+  \ensuremath{\varepsilon_{\ifc{l}}(\ifc{c})}, where \ensuremath{\ifc{l}} is the label of the first task
   in the task list and \ensuremath{\ifc{c}} the full configuration.
@@
   For any target language \ensuremath{\Red{\lambda}} and family of predicates
-  $\mathcal{P}$, the IFC language \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\textsc{RR},\Red{\lambda})}
+  $\mathcal{P}$, the restricted IFC language \ensuremath{L_\text{IFC}^{\mathcal{P}}(\textsc{RR},\Red{\lambda})}
   is TSNI.  Furthermore, the IFC language
-  \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\textsc{Seq},\Red{\lambda})} is TSNI.
+  \ensuremath{L_\text{IFC}^{\mathcal{P}}(\textsc{Seq},\Red{\lambda})} is TINI.
 \end{theorem}
@@
 First, we can construct the restricted language
-\ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P}_\text{norefs},\alpha,\Red{\lambda_{\text{ML}}})}, where \ensuremath{\mathcal{P}_\text{norefs}} is
+\ensuremath{L_\text{IFC}^{\mathcal{P}_\text{norefs}}(\alpha,\Red{\lambda_{\text{ES}}})}, where \ensuremath{\mathcal{P}_\text{norefs}} is
 the family of always valid predicates, except for the ones for
 \textsc{I-fork} and \textsc{I-send}, which we define as
-\[ P = \text{\ensuremath{\ifc{\Varid{e}}} does not contain any address \ensuremath{\tar{a}}} \]
+\[ P(\ensuremath{\ifc{\Varid{e}}}) = (\mathcal{AV}(\ensuremath{\ifc{\Varid{e}}}) = \emptyset{}) \]
+where $\mathcal{AV}(\ensuremath{\ifc{\Varid{e}}})$ denotes the set of address variables in \ensuremath{\ifc{\Varid{e}}}.
 That is, we do not restrict any rules except for \textsc{I-fork}
@@
     {
-      \text{\ensuremath{\ifc{\Varid{e}}} does not contain any \ensuremath{\tar{a}}}\\
+      \mathcal{AV}(\ensuremath{\ifc{\Varid{e}}}) = \emptyset{}\\
       \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}\epsilon\right]}\\
-      \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}\\
-      \ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{\Varid{l}}}}\\
+      \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\langle \ifc{E}\ifc{[}\ifc{\Varid{i}}'\ifc{]}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}}}\\
+      \ensuremath{\ifc{\Varid{t}}_\textrm{new}\mathrel{=}\langle \tar{_{\textrm{TI}}\lfloor}\ifc{\Varid{e}}\tar{\rfloor}\rangle^{\ifc{\Varid{i}}'}_{\ifc{l}}}\\
       \ensuremath{\textrm{fresh}\;(\ifc{\Varid{i}}')}
     }
-    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{\Varid{l}}_{1}},\ldots\hookrightarrow\ifc{\Sigma}';\tar{\Sigma};\alpha_{{\tiny\mathrm{\Conid{F}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}
+    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{sandbox}\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}_{1}}_{\ifc{l}_{1}},\ldots\hookrightarrow\ifc{\Sigma}';\tar{\Sigma};\alpha_{{\tiny\mathrm{\Conid{F}}}}(\ifc{\Varid{t}}_{1},\ldots,\ifc{\Varid{t}}_\textrm{new})}}
     \and
@@
     {
-      \text{\ensuremath{\ifc{\Varid{e}}} does not contain any \ensuremath{\tar{a}}}\\
-      \ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
+      \mathcal{AV}(\ensuremath{\ifc{\Varid{e}}}) = \emptyset{}\\
+      \ensuremath{\ifc{l}\flows{}\ifc{l}'}\\
       \ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
-      \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
+      \ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
     }
-    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\rightarrow\ifc{\Sigma};\tar{\Sigma};\alpha_{{\tiny\mathrm{\text{step}}}}(\langle \langle\rangle\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}
+    {\ensuremath{\ifc{\Sigma};\tar{\Sigma};\langle \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\rightarrow\ifc{\Sigma};\tar{\Sigma};\alpha_{{\tiny\mathrm{\text{step}}}}(\langle \langle\rangle\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots)}}
   \end{mathpar}
@@
 Now, we can show an isomorphism between this language and
-\ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P}_\text{norefs},\alpha,\Red{\lambda_{\text{ML}}})}, which
+\ensuremath{L_\text{IFC}^{\mathcal{P}_\text{norefs}}(\alpha,\Red{\lambda_{\text{ES}}})}, which
 (by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
@@
 
-\section{Proofs}
-\label{sec:proofs}
-
-In this section we will prove all theorems we have stated so far.
-We observe that the non-interference claims for the languages
-\ensuremath{L_\text{IFC}(\textsc{Seq},\Red{\lambda})} and \ensuremath{L_\text{IFC}(\textsc{RR}_{{\tiny\mathrm{\cdot }}}(\cdot ),\Red{\lambda})}
-in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
-from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
-respectively, about restricted IFC languages where the set
-of predicates is the set of always valid predicates.
-
-Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
-we state a lemma we will use.
-
-\begin{lemma}
-  \label{lemma:rr-tsni-general}
-  We consider, for any target language \ensuremath{\Red{\lambda}},
-  the restricted IFC language \ensuremath{L_\text{IFC}^{\text{-}}(\mathcal{P},\alpha,\Red{\lambda})}
-  (according to Definition~\ref{def:restricted}).
-  Then,
-  for any configurations \ensuremath{\ifc{c}_{1}}, \ensuremath{\ifc{c}_{1}'}, \ensuremath{\ifc{c}_{2}}, and label \ensuremath{\ifc{\Varid{l}}} where
-  \begin{equation} \label{eq:tsni-lemma-lhs}
-  \ensuremath{\ifc{c}_{1}} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}}
-  \qquad \text{and} \qquad
-  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}'}
-  \end{equation}
-  there exists a configuration \ensuremath{\ifc{c}_{2}'} such that
-  \begin{equation} \label{eq:tsni-lemma-rhs}
-  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}'}
-  \qquad \text{and} \qquad
-  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
-  \ \text{.}
-  \end{equation}
-\end{lemma}
-
-\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
-  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
-  The base case for derivations
-  of length 0 is trivial, allowing
-  us to simple chose $\ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}}$.  In the step case, we assume
-  the theorem holds for derivation sequences of length up to $n$, and show that it also
-  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
-  \[
-  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}
-  \]
-  for some configuration \ensuremath{\ifc{c}_{1}''}.  By Lemma~\ref{lemma:rr-tsni-general}, we get
-  \ensuremath{\ifc{c}''} with
-  \begin{equation} \label{eq:tsni-proof-1}
-  \ensuremath{\ifc{c}_{1}''} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}''}
-  \qquad \text{and} \qquad
-  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}''}
-  \end{equation}
-  Applying the induction hypothesis to
-  $\ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}$, we get \ensuremath{\ifc{c}_{2}'} with
-  \begin{equation} \label{eq:tsni-proof-2}
-  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{\Varid{l}}}} \ensuremath{\ifc{c}_{2}'}
-  \qquad \text{and} \qquad
-  \ensuremath{\ifc{c}_{2}''} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
-  \end{equation}
-  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
-  us the right-hand side of the implication in the TSNI
-  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
-\end{proof}
-\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
-  First, we observe there must be at least one task in \ensuremath{\ifc{c}_{1}}, otherwise
-  it could not take a step.  Thus, \ensuremath{\ifc{c}_{1}} is of the form
-  \ensuremath{\ifc{\Sigma}_{1};\ifc{\Varid{t}}_{1},\ifc{\Varid{ts}}_{1}}.  Consider two cases:
-  \begin{itemize}
-    \item $\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Varid{t}}_{1})}=\ensuremath{\bullet}$.
-    By the definition of \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}, we know that \ensuremath{\ifc{\Varid{l}}\;\flows\;\lcurr}
-    where \ensuremath{\lcurr} is the label of \ensuremath{\ifc{\Varid{t}}_{1}}.
-    In this case, we do not need to take a step for
-    \ensuremath{\ifc{c}_{2}}, because \ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}} will already be \ensuremath{\ifc{\Varid{l}}}-equivalent to \ensuremath{\ifc{c}_{1}'}.
-    To see that, note that the tasks \ensuremath{\ifc{\Varid{ts}}_{1}} in \ensuremath{\ifc{c}_{1}} are left in the
-    same order and unmodified (the scheduling policy only
-    modifies the first task). The task \ensuremath{\ifc{\Varid{t}}_{1}} either
-    gets dropped (by \textsc{I-noStep}), or
-    transforms into a task \ensuremath{\ifc{\Varid{t}}_{1}'} as well as potentially spawning a new
-    task \ensuremath{\ifc{\Varid{t}}_{1}''}.  Since both \ensuremath{\ifc{\Varid{t}}_{1}'} and \ensuremath{\ifc{\Varid{t}}_{1}''} have a label that is
-    at least as high as the label of \ensuremath{\ifc{\Varid{t}}_{1}} (can be seen
-    by inspecting all reduction rules), they will get filtered
-    by \ensuremath{\varepsilon_{\ifc{\Varid{l}}}} in \ensuremath{\ifc{c}_{1}'}.  Therefore, the \ensuremath{\ifc{\Varid{l}}} equivalence of the
-    task list is guaranteed.
-    Lets consider the possible changes to \ensuremath{\ifc{\Sigma}_{1}}:
-    Only three reduction rules change \ensuremath{\ifc{\Sigma}_{1}},
-    thus it suffices to consider these cases:
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      A new message triple with label \ensuremath{\ifc{\Varid{l}}'} gets added to the message
-      queue of the receiving thread.  However, since \ensuremath{\lcurr\;\flows\;\ifc{\Varid{l}}'},
-      the triple will get erased.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      In this case, only the queue of
-      task \ensuremath{\ifc{\Varid{t}}_{1}} can change, which gets erased.
-    \end{description}
-    This ensures that $\ensuremath{\ifc{c}_{1}'}\approx_{\ensuremath{\ifc{\Varid{l}}}}\ensuremath{\ifc{c}_{2}'}=\ensuremath{\ifc{c}_{2}}$.
-%    \alphacondition{We need all scheduling policies to not change the order
-%      of any tasks (except for the first one).  Newly spawned task can appear
-%      anywhere in the list.}
-    \item $\ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{\Varid{t}}_{1})}\neq\ensuremath{\bullet}$.
-    Here, there must be a corresponding
-    task \ensuremath{\ifc{\Varid{t}}_{2}} in \ensuremath{\ifc{c}_{2}},
-    such that \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\ifc{\Varid{t}}_{2}} (otherwise \ensuremath{\ifc{c}_{1}} and
-    \ensuremath{\ifc{c}_{2}} could not be \ensuremath{\ifc{\Varid{l}}} equivalent).
-    However, \ensuremath{\ifc{\Varid{t}}_{2}} might not be at the beginning of the task list yet, but
-    all tasks occurring before it must get erased by \ensuremath{\varepsilon_{\ifc{\Varid{l}}}}.
-    In \ensuremath{\ifc{c}_{2}}, we can first take some number of steps until \ensuremath{\ifc{\Varid{t}}_{2}} moves
-    to the front of the list.
-    This is the case regardless of any additional side conditions $P$ on
-    rules, because for all of these tasks, it can either take an actual
-    step, or it gets dropped by \textsc{I-noStep} (which is always
-    possible, as there cannot be an additional side condition on this
-    rule).  All tasks that didn't get dropped are still at a label
-    that isn't below \ensuremath{\ifc{\Varid{l}}} and thus get erased.
-
-%    \alphacondition{The scheduling policy must eventually let any task in
-%      the task list evaluate.  In particular, it cannot get stuck when the
-%      first task gets stuck, or keep executing a small number of tasks
-%      exclusively forever (e.g. just execute the first task all the time
-%      if it gets into an infinite loop).}
-
-    Therefore, after \ensuremath{\ifc{c}_{2}} has potentially executed some number of steps
-    to arrive at \ensuremath{\ifc{c}_{2}''}, we are now in the situation where $\ensuremath{\ifc{c}_{1}}\approx_{\ensuremath{\ifc{\Varid{l}}}}\ensuremath{\ifc{c}_{2}''}$, and the first tasks \ensuremath{\ifc{\Varid{t}}_{1}} and \ensuremath{\ifc{\Varid{t}}_{2}},
-    respectively, don't get erased and are thus equivalent.
-    The task \ensuremath{\ifc{\Varid{t}}_{2}} can now take exactly the same step as \ensuremath{\ifc{\Varid{t}}_{1}};  this
-    is true even with arbitrary additional premises $P$ that follow
-    the condition in Definition~\ref{def:npri}, since those
-    predicates only depend on \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c}_{1})}, which is equivalent
-    to \ensuremath{\varepsilon_{\ifc{\Varid{l}}}(\ifc{c}_{2})}, and thus those predicates evaluate in the same way.
-    Thus, we only
-    need to argue that the potential differences in \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} cannot
-    have an influence on the execution (and we know \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} are
-    \ensuremath{\ifc{\Varid{l}}} equivalent).
-    Again, only sending and receiving will depend on, or change \ensuremath{\ifc{\Sigma}},
-    so we consider all these cases.
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      Here, the task \ensuremath{\ifc{\Varid{t}}_{2}} will send the same message to the same
-      receiver queue. This
-      queue is either completely erased, or it is \ensuremath{\ifc{\Varid{l}}} equivalent.  In both
-      cases, \ensuremath{\ifc{\Varid{l}}} equivalence of \ensuremath{\ifc{\Sigma}_{1}'} and \ensuremath{\ifc{\Sigma}_{2}'} is preserved.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      When the tasks are receiving a message, then by the reduction rules
-      we know that they first filter the queue by the label
-      \ensuremath{\lcurr} of \ensuremath{\ifc{\Varid{t}}_{1}}.  We
-      also know that the queues are equivalent when filtered by the less
-      restrictive label \ensuremath{\ifc{\Varid{l}}}, thus the messages received (or dropped) from the
-      queue are equivalent.
-    \end{description}
-  \end{itemize}
-\end{proof}
-
-The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
-in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
-some cases are simpler due to the fact termination is not an issue
-(cf.~\tocite{} for a TINI proof of a similar system).
-
-\section{The monadic interpretation}
-\label{sec:monad}
-
-In the previous sections, we have been primarily concerned with the
-combination of operational semantics in order to automatically augment a
-language with information flow control.  In this section, we present
-a more abstract view of the situation, phrased in the language of monads
-and monad transformers.  The key idea is that the computational effects
-of the target language should be thought of as a \emph{monad transformer}
-on top of the information flow control base monad.  Readers who are not
-familiar with monads should feel free to skip this section.
-
-Monads were originally proposed as a method for organizing computational
-effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
-of interest was how to modularly build more complex computational
-effects out of simpler ones.  One particular approach, the
-\emph{incremental
-approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
-monad transformers, which add an extra computation feature to a
-pre-existing monad.  In the past, this approach has been criticized for
-a number of failings, including the fact that the order in meaning of a
-monad can depend on the order in which the monad transformers are
-applied. The canonical example of this phenomenon is the
-composition of the state monad and the error monad: depending on the
-ordering of the two monad transformers, state is preserved or thrown away
-upon an error.
-
-These problems can be viewed as defects in a setting where we are
-simply interested in combining effects.  However, in the setting of information
-flow control, we are primarily interested in augmenting the
-computational effects of a target language with information flow control
-\emph{without} compromising non-interference.  When the base monad is
-kept abstract (in the style of a restricted IO monad~\cite{Terei:2012:SH:2364506.2364524}),
-there is an easy argument why any monad transformer must also preserve non-interference:
-the monad transformer could have been implemented simply as a \emph{pure} interpreter, and
-the pure interpreter is just another program like any other that may run on top of
-a restricted IO monad.
-
-Now, one shouldn't simply force an interpreter to be reimplemented on
-top of a language supporting information flow control.  As suggested by
-Filinski et al~\cite{Filinski:2010:MA:1707801.1706354}, we should use
-pure implementations of computational effects to understand
-computational effects when built into information flow languages: they
-give a good hint what the operational rules should be.  This intuition
-backed the development of Section~\ref{sec:retrofit}.  Furthermore,
-developing the relationship between concrete semantics and abstract
-semantics in Section~\ref{sec:concrete} relates to the question of monad
-isomorphisms in the presence of data abstraction.  We leave the
-investigation of this connection in more detail to future work.
 \section{Real world languages}
@@
 In addition, ring protection could be used to intercept syscalls performed by
-a task and only permit those corresponding to our IFC language (e.g.,
-\ensuremath{\mathbf{getLabel}}, \ensuremath{\mathbf{send}}).
-%
-Although other sandboxing mechanisms can be used in place of Dune, we
-believe Dune's hardware protection mechanism would allow us to provide a 
-concrete implementation that is more efficient and simpler to reason about.
+a task and only permit those corresponding to our IFC language (such as
+\ensuremath{\mathbf{getLabel}} or \ensuremath{\mathbf{send}}).
+%
+Dunes hardware protection mechanism allows us to provide a concrete
+implementation that is efficient and relatively simple to reason
+about, but other sandboxing mechanisms could be used in place of Dune.
 
@@
 
-JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
-built-in functionality for I/O. (Capabilities such as the ability to
+JavaScript (JS), as specified by ECMAScript~\cite{ecma}, does not have any
+built-in functionality for I/O. Capabilities such as the ability to
 mutate the DOM and read user input are APIs defined on top of the ECMAScript
-specification.)
+specification.
 %
@@
 
-We describe SWAPI~\tocite{}, an implementation of this system for JavaScript.
+We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
+(which we here denote by \ensuremath{\Red{\lambda_{\text{JS}}}}).
 %
 The direct approach for implementing the embedded language \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})} is
-by running multiple instances of the JS runtime, i.e., \ensuremath{\Red{\lambda_{\text{JS}}}}, in
+by running multiple instances of the JS runtime, i.e., in
 separate OS-level threads.\footnote{
@@
 {
-\ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
+\ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'}\\
 \ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
-\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\;[\mskip1.5mu \ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}'),\ifc{\Theta}\mskip1.5mu]}\\
+\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\;[\mskip1.5mu \ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{v}}),\ifc{\Theta}\mskip1.5mu]}\\
 \ensuremath{\ifc{\Varid{e}}\mathrel{=}\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}}\\
@@
 }
-{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots\hookrightarrow\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Sigma}}}(\langle \tar{\Sigma}, \ifc{E}\ifc{[}\langle\rangle\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}},\ldots)}}
+{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{v}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\hookrightarrow\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Sigma}}}(\langle \tar{\Sigma}, \ifc{E}\ifc{[}\langle\rangle\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots)}}
 \end{mathpar}
 We remark that this is similar to the existing
-\texttt{postMessage} API used for iframe and Worker
+\texttt{postMessage} API used for iframe and worker
 communications~\cite{webworkers}.
@@
 
+Different concrete IFC implementations may wish to extend our minimal
+system with labeled constructs appropriate for their envisioned
+applications.
+%
+For example, SWAPI provides a labeled version of the XHR object, while
+LIO implements a labeled file system, use in server-side web
+applications~\cite{hails}.
+%
+Below we
+consider the addition of several labeled constructs to the abstract specification.
+%
+We remark that that the non-interference proofs must account for the
+new constructs, since they amend the IFC calculus semantics (usually
+by addition).
+
 \paragraph{Labeled values}
-\paragraph{Labeled references}
-\paragraph{Labeled synchronization primitives}
+In traditional language-based dynamic IFC systems, a label is
+associated with values.
+%
+Hence, a program that, for example, simply writes labeled messages to
+a labeled log can operate on both public and sensitive values.
+%
+In its simplest form, our coarse grained system requires that the
+current label of a task be at least at the level of the sensitive data
+to reflect the fact that such data is in scope.
+
+Thus, an extension that allows supports such fine-grained explicitly
+labeled values is essential.
+%
+To this end, we extend the IFC calculus with explicitly labeled
+values, much like those of LIO and
+Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: \ensuremath{\tar{v}\Coloneqq\cdots\;|\;\textbf{Labeled}\;\ifc{l}\;\tar{v}}.
+%
+Following LIO, we say that the value \ensuremath{\tar{v}} is protected by label \ensuremath{\ifc{l}},
+while the label \ensuremath{\ifc{l}} itself is protected by the task's current label.
+%
+%
+The label of such values can be inspected the task without
+requiring the current label to be raised.
+%
+However, when a task wishes to inspect the protected value \ensuremath{\tar{v}}, it
+must first raise it label to at least \ensuremath{\ifc{l}} to reflect that it is
+incorporating data at such sensitivity level in its scope.
+%
+When creating labeled values the label \ensuremath{\ifc{l}} must be above
+the current label; otherwise it cannot be said that protection has
+been transferred from the current label to \ensuremath{\ifc{l}}.
+%
+(For these rules, we assume that the \ensuremath{\textbf{Labeled}} constructor is not part of
+the surface syntax and thus cannot be accessed directly to construct
+or destruct such values without label checks.)
+% 
+We omit the reduction rules for labeled values since they closely
+follow those presented in~\cite{lio}.
+
+\paragraph{Labeled mutable references/variables/channels}
+%
+Extending the calculus with other labeled features, such as
+references, mutable variables (MVars)~\cite{CH96}, or channels,
+follows in a similar way.
+%
+In these cases, however, we must keep track of the additional state
+(as opposed to the labeled value case which requires no additional
+bookkeeping).
+%
+While we can modify the IFC calculus to add such labeled state to each
+individual task, adding it to the system state \ensuremath{\ifc{\Sigma}} leads to more
+interesting use cases.
+%
+Specifically, by amending \ensuremath{\ifc{\Sigma}}, as in~\cite{lio,
+stefan:addressing-covert}, we can allow threads to use these
+constructs to synchronize, or communicate with constructs other than
+\ensuremath{\mathbf{send}}/\ensuremath{\mathbf{recv}} in a safe manner.
+%
+For example, when extending the calculus with labeled references, \ensuremath{\ifc{\Sigma}}
+additionally contains a store that maps addresses to \ensuremath{(\ifc{l},\tar{v})} pairs
+which can be read and written to by different tasks through a labeled
+\ensuremath{\mathbf{ref}} implementations.
+%
+Since such labeled constructs have also been considered before in other
+concurrent systems, we do not discuss them further.
 
@@
 %
-Addressing this problem is a natural direction for this work.
+%Addressing this problem is a natural direction for this work.
 
@@
 %
-We leave the proof of this claim to future work.
-%
 
@@
 consider \emph{low-determinism}, which states that a program is secure
-only if \ensuremath{\Varid{l}}-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers
+only if \ensuremath{l}-equivalent results are deterministic~\cite{Zdancewic:Myers:CSFW03,
+sabelfeld2003language}.
 
@@
 to communicate with hosts according to the task's current label.
+\section{Proofs}
+\label{sec:proofs}
+
+In this section we prove all theorems we have stated.
+We first observe that the non-interference claims for the languages
+\ensuremath{L_\text{IFC}(\textsc{Seq},\Red{\lambda})} and \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda})}
+in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
+from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
+respectively, where the set
+of predicates is the set of always valid predicates.
+
+Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
+we state a lemma we will use.
+
+\begin{lemma}
+  \label{lemma:rr-tsni-general}
+  We consider, for any target language \ensuremath{\Red{\lambda}},
+  the restricted IFC language \ensuremath{L_\text{IFC}^{\mathcal{P}}(\alpha,\Red{\lambda})}
+  (according to Definition~\ref{def:restricted}).
+  Then,
+  for any configurations \ensuremath{\ifc{c}_{1}}, \ensuremath{\ifc{c}_{1}'}, \ensuremath{\ifc{c}_{2}}, and label \ensuremath{\ifc{l}} where
+  \begin{equation} \label{eq:tsni-lemma-lhs}
+  \ensuremath{\ifc{c}_{1}} \approx_{\ensuremath{\ifc{l}}} \ensuremath{\ifc{c}_{2}}
+  \qquad \text{and} \qquad
+  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}'}
+  \end{equation}
+  there exists a configuration \ensuremath{\ifc{c}_{2}'} such that
+  \begin{equation} \label{eq:tsni-lemma-rhs}
+  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{l}}} \ensuremath{\ifc{c}_{2}'}
+  \qquad \text{and} \qquad
+  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
+  \ \text{.}
+  \end{equation}
+\end{lemma}
+
+\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
+  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+  The base case for derivations
+  of length 0 is trivial, allowing
+  us to simple chose $\ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}}$.  In the step case, we assume
+  the theorem holds for derivation sequences of length up to $n$, and show that it also
+  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
+  \[
+  \ensuremath{\ifc{c}_{1}} \ensuremath{\hookrightarrow} \ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}
+  \]
+  for some configuration \ensuremath{\ifc{c}_{1}''}.  By Lemma~\ref{lemma:rr-tsni-general}, we get
+  \ensuremath{\ifc{c}''} with
+  \begin{equation} \label{eq:tsni-proof-1}
+  \ensuremath{\ifc{c}_{1}''} \approx_{\ensuremath{\ifc{l}}} \ensuremath{\ifc{c}_{2}''}
+  \qquad \text{and} \qquad
+  \ensuremath{\ifc{c}_{2}} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}''}
+  \end{equation}
+  Applying the induction hypothesis to
+  $\ensuremath{\ifc{c}_{1}''} \ensuremath{\hookrightarrow}^n \ensuremath{\ifc{c}_{1}'}$, we get \ensuremath{\ifc{c}_{2}'} with
+  \begin{equation} \label{eq:tsni-proof-2}
+  \ensuremath{\ifc{c}_{1}'} \approx_{\ensuremath{\ifc{l}}} \ensuremath{\ifc{c}_{2}'}
+  \qquad \text{and} \qquad
+  \ensuremath{\ifc{c}_{2}''} \ensuremath{\hookrightarrow}^* \ensuremath{\ifc{c}_{2}'}
+  \end{equation}
+  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
+  us the right-hand side of the implication in the TSNI
+  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
+\end{proof}
+\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
+  First, we observe there must be at least one task in \ensuremath{\ifc{c}_{1}}, otherwise
+  it could not take a step.  Thus, \ensuremath{\ifc{c}_{1}} is of the form
+  \ensuremath{\ifc{\Sigma}_{1};\ifc{\Varid{t}}_{1},\ifc{\Varid{ts}}_{1}}.  Consider two cases:
+  \begin{itemize}
+    \item $\ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Varid{t}}_{1})}=\ensuremath{\bullet}$.
+    By the definition of \ensuremath{\varepsilon_{\ifc{l}}}, we know that \ensuremath{\ifc{l}\;\flows{}\;\lcurr}
+    where \ensuremath{\lcurr} is the label of \ensuremath{\ifc{\Varid{t}}_{1}}.
+    In this case, we do not need to take a step for
+    \ensuremath{\ifc{c}_{2}}, because \ensuremath{\ifc{c}_{2}'\mathrel{=}\ifc{c}_{2}} will already be \ensuremath{\ifc{l}}-equivalent to \ensuremath{\ifc{c}_{1}'}.
+    To see that, note that the tasks \ensuremath{\ifc{\Varid{ts}}_{1}} in \ensuremath{\ifc{c}_{1}} are left in the
+    same order and unmodified (the scheduling policy only
+    modifies the first task). The task \ensuremath{\ifc{\Varid{t}}_{1}} either
+    gets dropped (by \textsc{I-noStep}), or
+    transforms into a task \ensuremath{\ifc{\Varid{t}}_{1}'} as well as potentially spawning a new
+    task \ensuremath{\ifc{\Varid{t}}_{1}''}.  Since both \ensuremath{\ifc{\Varid{t}}_{1}'} and \ensuremath{\ifc{\Varid{t}}_{1}''} have a label that is
+    at least as high as the label of \ensuremath{\ifc{\Varid{t}}_{1}} (can be seen
+    by inspecting all reduction rules), they will get filtered
+    by \ensuremath{\varepsilon_{\ifc{l}}} in \ensuremath{\ifc{c}_{1}'}.  Therefore, the \ensuremath{\ifc{l}} equivalence of the
+    task list is guaranteed.
+    Lets consider the possible changes to \ensuremath{\ifc{\Sigma}_{1}}:
+    Only three reduction rules change \ensuremath{\ifc{\Sigma}_{1}},
+    thus it suffices to consider these cases:
+    \begin{description}
+      \item[Case \textsc{I-send}]
+      A new message triple with label \ensuremath{\ifc{l}'} gets added to the message
+      queue of the receiving thread.  However, since \ensuremath{\lcurr\;\flows{}\;\ifc{l}'},
+      the triple will get erased.
+      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
+      In this case, only the queue of
+      task \ensuremath{\ifc{\Varid{t}}_{1}} can change, which gets erased.
+    \end{description}
+    This ensures that $\ensuremath{\ifc{c}_{1}'}\approx_{\ensuremath{\ifc{l}}}\ensuremath{\ifc{c}_{2}'}=\ensuremath{\ifc{c}_{2}}$.
+    %    \alphacondition{We need all scheduling policies to not change the order
+    %      of any tasks (except for the first one).  Newly spawned task can appear
+    %      anywhere in the list.}
+    \item $\ensuremath{\varepsilon_{\ifc{l}}(\ifc{\Varid{t}}_{1})}\neq\ensuremath{\bullet}$.
+    Here, there must be a corresponding
+    task \ensuremath{\ifc{\Varid{t}}_{2}} in \ensuremath{\ifc{c}_{2}},
+    such that \ensuremath{\ifc{\Varid{t}}_{1}\mathrel{=}\ifc{\Varid{t}}_{2}} (otherwise \ensuremath{\ifc{c}_{1}} and
+    \ensuremath{\ifc{c}_{2}} could not be \ensuremath{\ifc{l}} equivalent).
+    However, \ensuremath{\ifc{\Varid{t}}_{2}} might not be at the beginning of the task list yet, but
+    all tasks occurring before it must get erased by \ensuremath{\varepsilon_{\ifc{l}}}.
+    In \ensuremath{\ifc{c}_{2}}, we can first take some number of steps until \ensuremath{\ifc{\Varid{t}}_{2}} moves
+    to the front of the list.
+    This is the case regardless of any additional side conditions $P$ on
+    rules, because for all of these tasks, it can either take an actual
+    step, or it gets dropped by \textsc{I-noStep} (which is always
+    possible, as there cannot be an additional side condition on this
+    rule).  All tasks that didn't get dropped are still at a label
+    that isn't below \ensuremath{\ifc{l}} and thus get erased.
+
+    %    \alphacondition{The scheduling policy must eventually let any task in
+    %      the task list evaluate.  In particular, it cannot get stuck when the
+    %      first task gets stuck, or keep executing a small number of tasks
+    %      exclusively forever (e.g. just execute the first task all the time
+    %      if it gets into an infinite loop).}
+
+    Therefore, after \ensuremath{\ifc{c}_{2}} has potentially executed some number of steps
+    to arrive at \ensuremath{\ifc{c}_{2}''}, we are now in the situation where $\ensuremath{\ifc{c}_{1}}\approx_{\ensuremath{\ifc{l}}}\ensuremath{\ifc{c}_{2}''}$, and the first tasks \ensuremath{\ifc{\Varid{t}}_{1}} and \ensuremath{\ifc{\Varid{t}}_{2}},
+    respectively, don't get erased and are thus equivalent.
+    The task \ensuremath{\ifc{\Varid{t}}_{2}} can now take exactly the same step as \ensuremath{\ifc{\Varid{t}}_{1}};  this
+    is true even with arbitrary additional premises $P$ that follow
+    the condition in \Red{Definition (EZY: NPRI is missing)}, since those
+    predicates only depend on \ensuremath{\varepsilon_{\ifc{l}}(\ifc{c}_{1})}, which is equivalent
+    to \ensuremath{\varepsilon_{\ifc{l}}(\ifc{c}_{2})}, and thus those predicates evaluate in the same way.
+    Thus, we only
+    need to argue that the potential differences in \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} cannot
+    have an influence on the execution (and we know \ensuremath{\ifc{\Sigma}_{1}} and \ensuremath{\ifc{\Sigma}_{2}} are
+    \ensuremath{\ifc{l}} equivalent).
+    Again, only sending and receiving will depend on, or change \ensuremath{\ifc{\Sigma}},
+    so we consider all these cases.
+    \begin{description}
+      \item[Case \textsc{I-send}]
+      Here, the task \ensuremath{\ifc{\Varid{t}}_{2}} will send the same message to the same
+      receiver queue. This
+      queue is either completely erased, or it is \ensuremath{\ifc{l}} equivalent.  In both
+      cases, \ensuremath{\ifc{l}} equivalence of \ensuremath{\ifc{\Sigma}_{1}'} and \ensuremath{\ifc{\Sigma}_{2}'} is preserved.
+      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
+      When the tasks are receiving a message, then by the reduction rules
+      we know that they first filter the queue by the label
+      \ensuremath{\lcurr} of \ensuremath{\ifc{\Varid{t}}_{1}}.  We
+      also know that the queues are equivalent when filtered by the less
+      restrictive label \ensuremath{\ifc{l}}, thus the messages received (or dropped) from the
+      queue are equivalent.
+    \end{description}
+  \end{itemize}
+\end{proof}
+
+The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
+in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
+some cases are simpler due to the fact termination is not an issue
+(cf.~\cite{lio} for a TINI proof of a similar system).
+\section{The monadic interpretation}
+\label{sec:monad}
+
+In the previous sections, we have been primarily concerned with the
+combination of operational semantics in order to automatically augment a
+language with information flow control.  In this section, we present
+a more abstract view of the situation, phrased in the language of monads
+and monad transformers.  The key idea is that the computational effects
+of the target language should be thought of as a \emph{monad transformer}
+on top of the information flow control base monad.  Readers who are not
+familiar with monads should feel free to skip this section.
+
+Monads were originally proposed as a method for organizing computational
+effects~\cite{Moggi:1991:NCM:116981.116984}.  One of the key questions
+of interest was how to modularly build more complex computational
+effects out of simpler ones.  One particular approach, the
+\emph{incremental
+approach}~\cite{Benton00monadsand,Liang95monadtransformers}, utilizes
+monad transformers, which add an extra computation feature to a
+pre-existing monad.  In the past, this approach has been criticized for
+a number of failings, including the fact that the order in meaning of a
+monad can depend on the order in which the monad transformers are
+applied. The canonical example of this phenomenon is the
+composition of the state monad and the error monad: depending on the
+ordering of the two monad transformers, state is preserved or thrown away
+upon an error.
+
+These problems can be viewed as defects in a setting where we are
+simply interested in combining effects.  However, in the setting of information
+flow control, we are primarily interested in augmenting the
+computational effects of a target language with information flow control
+\emph{without} compromising non-interference.  When the base monad is
+kept abstract (in the style of a restricted IO monad~\cite{Terei:2012:SH:2364506.2364524}),
+there is an easy argument why any monad transformer must also preserve non-interference:
+the monad transformer could have been implemented simply as a \emph{pure} interpreter, and
+the pure interpreter is just another program like any other that may run on top of
+a restricted IO monad.
+
+Now, one shouldn't simply force an interpreter to be reimplemented on
+top of a language supporting information flow control.  As suggested by
+Filinski et al~\cite{Filinski:2010:MA:1707801.1706354}, we should use
+pure implementations of computational effects to understand
+computational effects when built into information flow languages: they
+give a good hint what the operational rules should be.  This intuition
+backed the development of Section~\ref{sec:retrofit}.  Furthermore,
+developing the relationship between concrete semantics and abstract
+semantics in Section~\ref{sec:concrete} relates to the question of monad
+isomorphisms in the presence of data abstraction.  We leave the
+investigation of this connection in more detail to future work.
 \section{Related work}

### 2014-03-02 paper/proofs.tex
fix proofs.

--- 2014-03-02 paper/proofs.tex
@@
 respectively, where the set
-of predicates is the set of always valid predicates.
+of predicates is the set of always valid predicates (i.e., no restriction).
 
@@
     by inspecting all reduction rules), they will get filtered
-    by |erasef il| in |ic1'|.  Therefore, the |il| equivalence of the
+    by |erasef il| in |ic1'|.  Therefore, the |il|-equivalence of the
     task list is guaranteed.
     Lets consider the possible changes to |iS1|:
-    Only three reduction rules change |iS1|,
+    Only three reduction interact with |iS1|,
     thus it suffices to consider these cases:
@@
     such that |it1=it2| (otherwise |ic1| and
-    |ic2| could not be |il| equivalent).
+    |ic2| could not be |il|-equivalent).
     However, |it2| might not be at the beginning of the task list yet, but
@@
     is true even with arbitrary additional premises $P$ that follow
-    the condition in \Red{Definition (EZY: NPRI is missing)}, since those
+    the condition in Definition~\ref{def:restricted}, since those
     predicates only depend on |erase il ic1|, which is equivalent
@@
     have an influence on the execution (and we know |iS1| and |iS2| are
-    |il| equivalent).
+    |il|-equivalent).
     Again, only sending and receiving will depend on, or change |iS|,
@@
       receiver queue. This
-      queue is either completely erased, or it is |il| equivalent.  In both
-      cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
+      queue is either completely erased, or it is |il|-equivalent.  In both
+      cases, |il|-equivalence of |iS1'| and |iS2'| is preserved.
       \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
@@
 \end{proof}
-
 The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely

### 2014-03-02 paper/extensions.tex

@@
 %
-Directly, the label of such values can be inspected the task without
+The label of such values can be inspected the task without
 requiring the current label to be raised.

### 2014-03-02 paper/formal.tex

--- 2014-03-02 paper/formal.tex
@@
 %
-While such assumptions are standard~\tocite{}, our definitions allow for
+While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
+stefan:addressing-covert}, our definitions allow for
 stronger attackers that may be able to inspect resource usage.\footnote{
   We believe that we can extend |specLang alpha (targetLang nop)| to
-  such models using the resource limits techniques of~\tocite{}.
+  such models using the resource limits techniques of~\cite{yangresource}.
   %

### 2014-03-02 paper/retrofit.tex
first subsection

@@
 
+\paragraph{Notation}
 We have typeset nonterminals of the target language using \textbf{{\color{red}
@@
 following the approach of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
+Findler~\cite{Matthews:2007:OSM:1190216.1190220} to simplify combining
 semantics of multiple languages.  To
@@
 context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
-However, when we combine this language with an IFC language, we must
+However, when we combine this language with an IFC language, we
 reinterpret the meaning of this evaluation context.
@@
 require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
-with the partial order |canFlowTo|.
+with the partial order |canFlowTo|, join |lub|, and meet |glb|.
 In this paper, we simply represent labels with the metavariable
@@
     \item A sandboxing operation allowing to spawn new
-    isolated tasks, which will be described in more detail in the
+    isolated tasks, described in more detail in the
     next section.
@@
 
-While the first two bullet points are essentially universal to all
-floating-label systems, our choice of communication primitives is motivated
-by inter-worker communication in web browser APIs~\cite{webworkers}, but
-other choices such as blocking communication or labeled channels are possible.
-We describe some of the alternate possibilities in Section~\ref{sec:extensions}.
-These operations are all defined with respect to an evaluation context |curlyBlueE| represents the context
-of the current task which is running, which has three important pieces
-of state: the global message queues |iS|,
-the current label |il| (which protects the program counter of the task)
-and the task ID |id|.
+These operations are all defined with respect to an evaluation context
+|curlyBlueE| represents the context of the current task which is running, which
+has three important pieces of state: the global message queues |iS|, the
+current label |il| and the task ID |id|.
+
+At a high level, the semantics define a coarse-grained floating-label IFC
+system~\cite{Zeldovich:2006, lio}, i.e., a system in which the current label of
+the task can be raised to protect everything in scope.
+%
+We note that while first class labels and operations for inspecting the current
+label are are essentially universal to all floating-label systems, our choice
+of communication and isolation primitives is motivated by those present in
+browsers, namely \texttt{postMessage} and Workers~\cite{webworkers,webmessaging}.
+%
+Of course, other choices such as blocking communication or labeled channels are
+possible and further discussed in Section~\ref{sec:extensions}.
+%
+Though motivated by Web Workers, our notion of a task generalizes previous
+primitives considered by floating-label dynamic IFC
+systems~\cite{Zeldovich:2006, lio, stefan:addressing-covert,
+Hritcu:2013:YIB:2497621.2498098}.
 
@@
 \]
-This ensures that tasks cannot receive messages that are more secret
+This ensures that tasks cannot receive messages that are more sensitive
 than their current label would allow.
 
+\Red{MOVE:}
 As a final remark, blocking receive can be (inefficiently) implemented using
@@
 
-We note that it is possible to add rules for a natuaral embedding of
+We note that it is possible to add rules for a natural embedding of
 expressions that occur in both languages.  In our specific example

### 2014-03-02 paper/concrete.tex
Structure up the text.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
+Unfortunately, an isomorphism is often too strong of a requirement.
 To obtain an isomorphism with our single heap semantics, we need to mimic the
@@
 The interesting cases are when we sandbox
-an expression, and when messages are sent and received.
+an expression and when messages are sent and received.
 The rule for sandboxing is
@@
 which defines what heap the new task
-should execute with.  We have motivated two choices, namely the identity (to
-effectively clone the heap), or to start with an empty heap.
+should execute with.  We have considered two choices:
 
-{\color{red}
-In the first choice, the concrete semantics should essentially implement several
-heaps into one. For that, it creates a copy of everything reachable from the
-forked expression (not just the values for the memory addresses in the
-expression \Red{Ale:why not only the addresses?}), and replace all addresses
-correspondingly.  behavior of sending a memory address now depends on whether
-that address existed at the time the receiving task was forked; if it did, then
-the address should be rewritten to the new one, otherwise to a fresh one.
+\begin{itemize}
+    \item When we sandbox into an empty heap, existing addresses
+in the forked expression are no longer valid and the
+task will get stuck (and then removed by \textsc{I-noStep}).
+Thus, we must rewrite the forked expression so that
+all addresses point to fresh addresses
+guaranteed to not occur in the heap.  Similarly,
+sending a memory address should be rewritten.
 
-In the latter case, this effectively means that the concrete semantics must
-change the forked expression |ie| in such a way that all addresses get rewritten
-to fresh addresses that are guaranteed to not occur in the global heap. As a
-consequence, existing addresses in the forked expression |ie| are no longer
-valid and the task gets stuck (and then removed by \textsc{I-noStep}).
-%To get the isomorphic behavior in the concrete semantics with a
-%single heap, we would have to change the forked expression |ie| in
-%such a way that all addresses get rewritten to fresh addresses
-%that are guaranteed to not occur in the global heap.  
-Similarly, sending a memory address should take a similar approach, as addresses
-for sent references will not exist in the receiving task.
-}
-
-{\color{blue}
-In the latter case, this effectively means that existing addresses
-in the forked expression |ie| are no longer valid and the
-task gets stuck (and then removed by \textsc{I-noStep}).
-To get the isomorphic behavior in the concrete semantics with a
-single heap, we would have to change the forked expression |ie| in
-such a way that all addresses get rewritten to fresh addresses
-that are guaranteed to not occur in the heap.  Similarly,
-sending a memory address should take a similar approach, as addresses
-for sent references will not exist in the receiving task.
-
-If |klone| is the identity function, then the abstract semantics
-effectively clone the heap on a fork.  To get an isomorphic
-behavior in the concrete, we would have to create a copy of everything
+\item When we clone the heap, we have to create a copy of everything
 reachable from the forked expression (not just the values for
@@
 new one, otherwise to a fresh address.
+\end{itemize}
 
-Such a complicated behavior is contradictory to our initial motivation
-of implementing a single heap for efficiency.  But even the
-behavior of the simpler case where |klone| returns an empty heap is
-undesirable:  We rewrite addresses to fresh addresses, which will
-result in a stuck task whenever such an address is dereferenced.
-}
+This complicated behavior is counter to our initial motivation
+of implementing a single heap for efficiency.
 
@@
 
-As a better solution we could forbid forked expressions as well
+A better solution is to forbid forked expressions as well
 as messages sent to other tasks to contain memory addresses in the
@@
 
-Again, we are modifying the IFC language semantics in a non-trivial way,
-which begs the question whether non-interference is preserved.
-Restricting the transitions in an information flow control
-system in general does not preserve non-interference.  Intuitively
+While this sounds plausible, it is worth noting that we are modifying the IFC language semantics,
+which raises the question whether non-interference is preserved.
+This question can be subtle: it is easy to remove a transition from
+a language and invalidate TSNI.  Intuitively
 if the restriction depends on secret data, then a public thread

### 2014-03-02 paper/concrete.tex
isomophism

--- 2014-03-02 paper/concrete.tex
@@
 
-\Red{Show the isomorphism.}
+To this end, we represent addresses in the concrete language as
+pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
+address in the abstract system\footnote{Note that this does
+  not make the isomorphism trivial, as in the single heap, there
+  is nothing preventing task 1 to access an address (2,|ta|).
+  Furthermore, it is common to represent addresses in this way
+  for efficient garbage collection of dead tasks.}.
+We also formulate the following well-formedness condition for
+configurations:
+\[
+  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
+  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
+\]
+Essentially, every address in a given task must have the correct
+identifier as the first part of the address.  It is easy to
+see that the initial configuration satisfies this condition, and
+any step in the concrete semantics preserves the condition.
+Therefore, we only need to consider well-formed configurations,
+which allows us to give the two required functions
+|f| and |finv| for the isomorphism.  For conciseness, we informally
+give their definition and leave the straight-forward proof that they
+actually provide an isomorphism.
+\begin{itemize}
+  \item Addresses can be directly translated with
+  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
+  an address |ta| that occurs in task |id|.
+  \item |f| splits the single heap into multiple heaps based on
+  the |id| of the addresses.  |finv| produces a single heap
+  by translating the addresses and collapsing everything to a single
+  store.
+\end{itemize}

### 2014-03-02 paper/abstract.tex

--- 2014-03-02 paper/abstract.tex
@@
 \begin{abstract}
-    Many important security problems in JavaScript, including extension
-    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
-    XXX~\tocite{}, could be solved with a implementation
-    of information flow control.  However, designing an IFC system which
-    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
-    we formally describe a coarse-grained IFC system which fulfills this
-    criterion.  The key idea is that an efficient IFC system must not
-    depend too much on the details of the language it is integrated
-    with.  The result is a general method for adding IFC to existing
-    languages which is indifferent to the choice of language.
-    Additionally, we describe how to relate concrete implementations
-    with the IFC systems produced by our technique and show how various
-    proposed and existing IFC systems fit into our formal framework.
+    Many important security problems in JavaScript, such as browser extension
+    security~\tocite{}, untrusted JavaScript libraries~\tocite{} and
+    safe integration of mutually distrustful websites (mash-ups)~\tocite{}, may be effectively addressed using an efficient implementation
+    of information flow control.
+We present a coarse-grained IFC system that
+can be implemented  non-intrusively, resulting in
+much greater implementation efficiency than previous finer-grained approaches.
+The central concept is an isolation mechanism whose operation does not
+depend too much on the details of the programming language used.
+We thus present a \emph{general} method for adding IFC to existing
+languages that is largely \emph{indifferent} to the choice of language.
+Additionally, we describe how to relate optimized concrete implementations
+to the IFC systems produced by our technique and show how various
+proposed and existing IFC systems conform to our formal framework
+and therefore enjoy the semantic properties we prove.
 \end{abstract}

### 2014-03-02 paper/formal.tex

@@
 
-In this section, we present the formal security guarantees provided by
-our embedding.
-%
-Concretely, we show that |specLang alpha targetLang|, with an appropriate
+We are interested in proving non-interference about many programming
+languages.  This requires an appropriate definition of this notion
+that is language agnostic, so in this section, we present a few
+general definitions for what an information flow control language is
+and what non-interference properties it may have.  We also state
+theorems about our system which we prove in Section~\ref{sec:proofs}.
+In particular, we show that |specLang alpha targetLang|, with an appropriate
 scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
 without making any reference to properties of |targetLang|.
-%
+
+\cut{
 The precise scheduling policy dictates
@@
 where termination attacks cannot leak information.
+}
 
-How can we characterize what the \emph{secret inputs} of a program are?  Like
+\subsection{Erasure function}
+
+When defining the security guarantees of an information flow control,
+we must characterize what the \emph{secret inputs} of a program.  Like
 other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
@@
 %
-To accommodate for this, we extend our formalism with a function |erasef l| that
+To interpret a language under information flow control, we define a function |erasef l| that
 performs erasures by mapping configurations to erased configurations,
 usually by rewriting (parts of) configurations that are more sensitive
-than |l| to a new syntactic construct |bullet|.
-%
-In order for us to state non-interference, a language needs to include an
-erasure function:
+than |l| to a new syntactic construct |bullet|.  We can the define
+an information flow control language as follows:
 
-%\Red{should be the environment colored in the definition?}
-%EZY: No, I don't think so.
 \begin{definition}[Information flow control language]
@@
 %format .->  = "\overset{\alpha}{\hookrightarrow}"
-Our language |specLang alpha (targetLang nop)| can be
-represented as |(ifc C, .->, erasef il)|, such that
-$|ifc C| = |iS| \times \prod |it|$.  Here,
-$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
+Our language |specLang alpha (targetLang nop)| fulfills
+this definition as|(ifc C, .->, erasef il)|, where
+$|ifc C| = |iS| \times \prod |it|$.  The set of terminal conditions
+$|ifc V|$ is $|iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
 type for tasks whose expressions have been reduced to
@@
 %
-A task and its corresponding message queue is completely removed from the task
+Essentially, a task and its corresponding message queue is completely erased from the task
 list if its label does not flow to the attacker observation level |il|.
@@
 
-The definition of |erasef il| is quite important, as it captures the IFC
-language's attacker model: elements that are erased cannot be observed
-by the attacker.
+The definition of an erasure function is quite important: it captures
+the attack model, stating what can and cannot be observed by the attacker.
 %
@@
 
-Non-interference relies on the definition of an attacker's observational power at
-security level |l|, which is typically defined as an equivalence
-relation---called |l|-equivalence---on configurations.  An attacker
-at level |l| cannot
-distinguish two configurations that are |l|-equivalent.
+\subsection{Non-interference}
+
+Given an information flow-control language, we can now define non-interference.
+Intuitively, we want to make statements about the attacker's observational
+power at some security level |l|.  This is done by defining an equivalence
+relation called |l|-equivalence on configurations: an attacker should
+not be able to distinguish two configuration that are |l|-equivalent.
 %
-Since our erasure function captures the attacker model, we simply define this
+Since our erasure function captures what an attacker can or cannot observe, we simply define this
 equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
@@
 
-Intuitively, we can now state that a language satisfies non-interference if an
+We can now state that a language satisfies non-interference if an
 attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
@@
 %
-This precise non-interference property is called termination sensitive non-interference
+This particular property is called termination sensitive non-interference
 (TSNI).  Besides the obvious requirement to not leak secret information
@@
 %
-Formally, we define TSNI as follows.
+Formally, we define TSNI as follows:
 
 \begin{definition}[Termination Sensitive Non-Interference (TSNI)]
-  A language |(C, .->, erasef l)| is termination
-  sensitive non-interfering if for any label |l|, and configurations
+  A language |(C, .->, erasef l)| satisfies termination
+  sensitive non-interference if for any label |l|, and configurations
   |c1, c1', c2 member C|, if
@@
 
-We now show that our IFC language satisfies TSNI %under a particular
+Our IFC language satisfies TSNI %under a particular
 %scheduling policy.
@@
 
-In general TSNI will not hold for an arbitrary scheduler |alpha|.
+In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
 %
@@
 It is easy to show that |specLang seqf targetLang| does not satisfy
-TSNI.
+TSNI:
 %
-Concretely, consider a target language similar to |targetLangML| with an
+consider a target language similar to |targetLangML| with an
 additional expression terminal |diverge| that denotes a divergent computation,
@@
 \end{code}
-\Red{Ale: |when| was not defined, so I changed it to if-then-else}
 These two configurations are |pub|-equivalent, but |ic1| will reduce 
@@
 libraries~\cite{Russo+:Haskell08,lio}, TINI is useful for sequential
-settings. We show that our IFC language with the sequential scheduling policy
+settings. In our case, we show that our IFC language with the sequential scheduling policy
 |seqf| satisfies TINI.

### 2014-03-02 paper/retrofit.tex

@@
 labels (|canFlowTo|, |lub| and |glb|),
-    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
+    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (since the current label's role is to protect everything in the task, the task can only increase its label),
     \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
@@
 system~\cite{Zeldovich:2006, lio}, i.e., a system in which the current label of
-the task can be raised to protect everything in scope.
+the task can be raised to protect everything in scope;
+%
+this is different from traditional fine-grained language-based IFC systems that
+associate labels with values~\cite{sabelfeld2003language,Austin:Flanagan:PLAS09}.
 %
@@
 \subsection{The embedding}
-
-\Red{TODO[ds]:
-  - clarify discussion on exceptions
-  - fix the toLabled
-}
-Finally, in Figure~\ref{fig:embedding},
-we provide all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
+Figure~\ref{fig:embedding}
+provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
 The most important feature of this embedding is that every task maintains its own
@@
 
+\begin{itemize}
+    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
+    %
+In the target language, an IFC expression appears as |TI ie| (``target-outside,
+IFC-inside''); in the IFC language, a target language expression appears as |IT
+te| ( ``IFC-outside, target-inside'').
+    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.
+These rules only operate on the first task in the task list, which by convention is the only task executing.
+    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.
+The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|;
+    Figure~\ref{fig:scheduler} defines two concrete schedulers.
+    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
+    and intermediating between the borders of the two languages.
+\end{itemize}
+
 \begin{figure}
@@
 
-\begin{itemize}
-    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
-    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for |curlyRedE| and |curlyBlueE|.
-These rules only operate on the first task in the task pool, which by convention is the only task executing.
-    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.
-The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy |alpha|.
-Not all schedulers preserve non-interference, and we provide two specific schedules in Figure~\ref{fig:scheduler}.
-    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
-    and intermediating between the borders of the two languages.
-\end{itemize}
-
-The \textsc{I-sandbox} rule allows to create a new isolated task that
+The \textsc{I-sandbox} rule is used to create a new isolated task that
 executes separately from the existing tasks (and can be communicated
@@
 
+%
+As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
+\textsc{I-border} define the syntactic boundaries between the IFC and target
+languages.
+%
+Intuitively, the boundaries respectively correspond to an upcall into and
+downcall from the IFC runtime.
+%
+
 We note that it is possible to add rules for a natural embedding of
@@
 \begin{mathpar}
-\inferrule[I-bool]
+\inferrule
 { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
 \and
-\inferrule[T-bool]
+\inferrule
 { |b member {true, false}| } {| intE (TI b) -> intE b |}
@@
 For any target language |targetLang| and scheduling policy |alpha|, this
-embedding defines an information flow control language, which we will
+embedding defines an IFC language, which we will
 refer to as |specLang alpha targetLang|.
@@
 To get a feeling for how these operational semantics operate, we
-would like to
-describe a few sample programs, and what their outputs are.
+describe a few sample programs, and their corresponding outputs.
 
@@
 completion before returning to the task that sandboxed it.  Thus,
-a task pool should rather be interpreted as a number of information flow
+a task list should rather be interpreted as a number of information flow
 aware stack frames.  To read the result of a |toLabeled| operation

### 2014-03-02 paper/extensions.tex
capitalize titles.

@@
 
-\subsection{IFC language features}
+\subsection{IFC Language Features}
 \label{sec:extensions:labeled}
@@
 
-\subsection{Type safety}
+\subsection{Type Safety}
 \label{sec:extensions:types}
@@
 
-\subsection{Scheduling policies}
+\subsection{Scheduling Policies}
 Our specification language is parametrized by a scheduling policy
@@
 
-\subsection{External effects}
+\subsection{External Effects}
 \label{sec:extensions:external}

### 2014-03-02 paper/retrofit.tex
capitalize titles.

@@
-\section{Retrofitting languages with IFC}
+\section{Retrofitting Languages with IFC}
 \label{sec:retrofit}
@@
 
-\subsection{Target language: Mini-ES}
+\subsection{Target Language: Mini-ES}
 
@@
 
-\subsection{IFC language}
+\subsection{IFC Language}
 
@@
 
-\subsection{The embedding}
+\subsection{The Embedding}
 Figure~\ref{fig:embedding}

### 2014-03-02 paper/intro.tex
John's stuff
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-A defining aspect of web platforms is the combinability of
-components of differing providence.  This pattern shows up in browser
-extensions (which run JavaScript code alongside third-party website
-code), web applications (which include possibly untrusted third-party
-libraries), and mash-up websites (which combine code and data from
-websites which may not even be aware of each other's existence.)  While
-this combinability has offered great flexibility, it also poses a set of
-unique security challenges: in particular, maintaining the privacy of
-data in these settings is difficult, if not impossible.
+Modern web content is rendered using a potentially large number of
+different components with differing provenance.
+Disparate and untrusting components may arise from browser
+extensions (whose JavaScript code runs alongside website
+code), web applications (with possibly untrusted third-party
+libraries), and mashups (which combine code and data from
+websites that may not even be aware of each other's existence.)
+While just-in-time combination of untrusting components
+offers great flexibility, it also poses complex security challenges.
+In particular, maintaining data privacy in the face of malicious
+extensions, libraries, and mashup components has been difficult,
+and in general effectively impossible.
 
-Information flow control (IFC) is a promising technique for addressing these
-problems by tracking the flow of sensitive data through a system. Untrusted
-code is confined so that it cannot exfiltrate data, except as
+Information flow control (IFC) is a promising technique
+that provides security
+by tracking the flow of sensitive data through a system.
+Untrusted code is confined so that it cannot exfiltrate data, except as
 per an information flow policy.  Significant research has been devoted to
@@
 motivation to preserve the language JavaScript, and retrofit dynamic information
-flow control on top of it.  A key challenge in the design of these
-systems is ensuring they can be implemented efficiently: when the
-semantics specify that information flow must be tracked at a
-fine-grained level, e.g., per value in the system,  it can lead to
-impractical runtime overheads even for ordinary operations.
+flow control on top of it.  A key challenge in dynamic information
+flow control is implementation efficiency: when
+information flow is tracked at a fine-grained level,
+e.g., per value in the system, systems may incur
+impractical runtime overhead.
 
-One alternative is a \textit{coarse-grained} approach to IFC.  Here,
-computational units are associated with a floating label which protects
-all data in this unit.  A recent system named SWAPI adds IFC to the
+In the alternative \textit{coarse-grained} approach to IFC,
+a system is divided into relatively course computational units,
+each with a single label dictating its security policy.
+Only
+communication between isolated computational units must be tracked.
+A recent system named SWAPI adds IFC to the
 browser by identifying \emph{web workers} as an existing computational
-unit.  Communication between workers can efficiently be mediated in an
-IFC aware way to ensure non-interference, where sensitive workers cannot
-influence the computations in less sensitive workers.
-This coarse-grained approach provides a number
-of advantages: (1) reduced runtime overhead because checks need only
+unit.  Communication between workers is mediated using
+IFC to ensure non-interference, preventing sensitive workers from
+influencing the computation of less sensitive workers.
+This coarse-grained approach provides a number of advantages:
+(1) reduced runtime overhead because checks need only
 be performed at isolation boundaries, (2) minimal changes to an
 existing programming language when adding IFC, which (3) allows
-the reuse of existing programs.  Finally, (4) the simplicity
-of a single security label per computational unit facilitates
+the reuse of existing programs.  Finally, (4) associating
+a single security label with the entire computational unit simplifies
 understanding and easy reasoning about the correctness of the
-system, in particular without having to reason about all the
-technical details of the semantics of the programming language
-at hand.
+system, without information-flow reasoning about the
+technical details of the semantics of the programming language.
 
-In fact, the simplicity of this coarse-grained approach
-to IFC allows us to generalize it to a large class of programming
-languages.  In this paper, we identify the key concepts of coarse-grained
-dynamic IFC and show how these can be combined with \emph{any} programming
-language.  We achieve this
-by using an embedding that combines the operational semantics
-of the core IFC calculus and the target language.
-At the core of our IFC system we use a sandboxing operation that allows
-the execution of potentially sensitive computations in isolation,
-while communicating through clearly specified interfaces with other
-sandboxed operations.
-We formally state and prove the non-interference guarantees that our
-system gives, independently of the choice of the target language.
+A further benefit of the coarse-grained approach
+is that a single IFC design and semantics can be generalized
+to a large class of programming languages.
+Leveraging this insight, we define a general form of coarse-grained
+dynamic IFC and show how IFC can be combined with \emph{any} programming
+language conforming to a general semantic framework.
+At the core of our IFC system is a sandboxing construct that isolates
+potentially sensitive computations, allowing them to
+communicate only through clearly specified interfaces.
+Based on a framework for combining the operational semantics
+of our core IFC calculus with the operational semantics of any target language,
+we formally state and prove non-interference guarantees that are
+independent of the choice of specific target language.
 
 One challenge in the design of our system is that the semantics for the
-retrofitted IFC language may not reflect the actual implementation in a
-particular choice of target language.  We partially address this issue
+retrofitted IFC language may not accurately correspond to the optimized
+implementation details of a particular target language.
+We discuss and partially address this issue
 by characterizing isomorphisms between the operational semantics of our
@@
 
-Our key contributions can be summarized as follows:
+Our contributions can be summarized as follows:
 \begin{itemize}
-  \item We give formal semantics for a core IFC language that
-      captures the essence of coarse-grained information flow control.
+  \item We give formal semantics for a core coarse-grained
+  information flow control language.
   We then show how a large class of target languages can be combined
-  with this IFC language and prove that the resulting system provides
+  with this IFC language and prove that the result provides
   non-interference. (Section~\ref{sec:retrofit})
@@
   by means of an isomorphism, and show a class of restrictions on
-  the IFC calculus that preserves non-interference. (Section~\ref{sec:formal})
-  \item We sketch how the core IFC language can be enriched with
-  more advanced concepts such as labeled values, privileges or a
+  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
+  \item We briefly describe ways to enrich the core IFC language with
+  more advanced concepts such as labeled values, privileges, or a
   notation of clearance. (Section~\ref{sec:extensions})
@@
   how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
-  \item We informally connect our results to a monadic interpretation
+  \item We informally relate our results to a monadic interpretation
       of IFC which guided our design. (Section~\ref{sec:monad})     

### 2014-03-02 paper/abstract.tex
Remove tocites
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
     Many important security problems in JavaScript, such as browser extension
-    security~\tocite{}, untrusted JavaScript libraries~\tocite{} and
-    safe integration of mutually distrustful websites (mash-ups)~\tocite{}, may be effectively addressed using an efficient implementation
+    security, untrusted JavaScript libraries and
+    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
     of information flow control.

### 2014-03-02 paper/retrofit.tex
more text

@@
 
-\caption{Simple untyped lambda calculus |targetLangML|}
+\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
+mutable references and general recursion. |FV(te)| returns the set of free
+variables in express |te|.}
 \label{fig:ml}
@@
         which interact with the global store of per-task message queues |iS|, and
-    \item A sandboxing operation allowing to spawn new
-    isolated tasks, described in more detail in the
-    next section.
+    \item A sandboxing operation used to spawn new isolated tasks. In
+    concurrent settings |fork| corresponds to a fork-lie primitive; in a
+    sequential setting, it more closely resembles the LIO's
+    |toLabeled|~\cite{lio}, and the Breeze
+    bracket~\cite{Hritcu:2013:YIB:2497621.2498098}.
 \end{itemize}
@@
 than their current label would allow.
-
-\Red{MOVE:}
-As a final remark, blocking receive can be (inefficiently) implemented using
-our asynchronous primitives as follows:
-\begin{code}
-  brecvf ix1 ix2 ie @=
-  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
-\end{code}
 
@@
 %
+As an example, taking |targetLangML| as the target languge, we can now define a
+blocking receive (inefficiently) in terms of the asynchronous |recv| as series
+of cross-language calls:
+\begin{code}
+  brecvf ix1 ix2 ie @=
+  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
+\end{code}
 
-We note that it is possible to add rules for a natural embedding of
-expressions that occur in both languages.  In our specific example
-with |targetLangML|, we can choose to preserve booleans across
-language boundaries as follows:
+We note that our embedding corresponds to the lump embedding
+of~\cite{Matthews:2007:OSM:1190216.1190220}, terms in one language are
+treated opaquely in the other.
+%
+Indeed since our embedding is defined for an arbitrary language |targetLang|,
+we cannot do better.
+%
+However, when we have more information about the target language, it is
+possible to add rules for a natural embedding of expressions that occur in both
+languages.  In our specific example with |targetLangML|, we can choose to
+preserve booleans across language boundaries as follows:
 \begin{mathpar}

### 2014-03-02 paper/conclusion.tex
John's conclusion
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\cut{
\section{Conclusion}
\label{sec:conclusion}

In this paper, we develop a general coarse-grained approach to IFC
based on dividing a system into relatively course computational units
and tracking only communication between these isolated units.
We give formal semantics for the core coarse-grained
information flow control language and show how a large class of target languages
can be combined with it to achieve provable
non-interference.
We then give a proof technique for showing  non-interference
of a concrete semantics for a potentially optimized IFC language
by means of an isomorphism, and identify a class of IFC language restrictions
that preserves non-interference.
We briefly describe ways to enrich the core IFC language with
more advanced concepts such as labeled values, privileges, or a
notation of clearance and
connect our formal semantics to real implementations of
coarse-grained IFC systems for Javascript, Haskell, and
(in less detail) enforcing IFC in C.
Leaving more detailed presentation to later work,
we informally relate our results to a monadic interpretation
of IFC which guided our design.
}

### 2014-03-02 paper/formal.tex
capitalize titles.
nits.

@@
-\section{Security guarantees}
+\section{Security Guarantees}
 \label{sec:formal}
@@
 
-\subsection{Erasure function}
+\subsection{Erasure Function}
 
 When defining the security guarantees of an information flow control,
-we must characterize what the \emph{secret inputs} of a program.  Like
+we must characterize what the \emph{secret inputs} of a program are.  Like
 other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
@@
 any sensitive information from a program if the program behaves identically
-(from the attacker point of view) to a program with all sensitive data
+(from the attackers point of view) to a program with all sensitive data
 ``erased''.
@@
     erasef l)|, where $|C|$ is the type of machine configurations (members
-    of which are usually denoted by the meta-variable |c|), |.->| is a
+    of which are usually denoted by the metavariable |c|), |.->| is a
     reduction relation between machine configurations and |erasef l : C -> tyerase C|
     is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
-    configurations |tyerase C|.  Sometimes, we refer as |V| to set of
-     terminal configurations in |C|, i.e., configurations states where
+    configurations |tyerase C|.  Sometimes, we use |V| to refer to set of
+     terminal configurations in |C|, i.e., configurations where
      no further transitions are possible.
@@
 Our language |specLang alpha (targetLang nop)| fulfills
-this definition as|(ifc C, .->, erasef il)|, where
-$|ifc C| = |iS| \times \prod |it|$.  The set of terminal conditions
+this definition as |(ifc C, .->, erasef il)|, where
+$|ifc C| = |iS| \times \operatorname{List}(|it|)$.  The set of terminal conditions
 $|ifc V|$ is $|iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
@@
 
-\subsection{Non-interference}
+\subsection{Non-Interference}
 
-Given an information flow-control language, we can now define non-interference.
+Given an information flow control language, we can now define non-interference.
 Intuitively, we want to make statements about the attacker's observational
@@
   sensitive non-interference if for any label |l|, and configurations
-  |c1, c1', c2 member C|, if
+  $|c1, c1', c2|\in|C|$, if
   \begin{equation} \label{eq:tsni-lhs}
@@
   \end{equation}
-  then there exists a configuration |c2' member C| such that
+  then there exists a configuration $|c2'|\in|C|$ such that
   \begin{equation} \label{eq:tsni-rhs}
@@
 For example, |specLang alpha targetLang| with a scheduler that inspects a
-sensitive threads current state when deciding which thread to schedule next
+sensitive tasks current state when deciding which task to schedule next
 will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
@@
 i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
-sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
+sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
 Consider the following two configurations in this language:
@@
 %
-To accomodate for sequential languages, or cases where a weaker guarantee
+To accommodate for sequential languages, or cases where a weaker guarantee
 is sufficient, we consider an alternative non-interference property called termination insensitive
@@
   insensitive non-interfering if for any label |l|, and configurations
-  |c1, c2 member C| and |c1', c2' member V|, it holds that
+  $|c1, c2|\in|C|$ and $|c1', c2'|\in|V|$, it holds that
   \[

### 2014-03-02 paper/formal.tex
Fix dupe
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-02 paper/formal.tex
@@
 
-\subsection{Erasure function}
+\subsection{Erasure Function}
 
@@
 
-\subsection{Non-interference}
+\subsection{Non-Interference}
 
@@
 sensitive threads current state when deciding which thread to schedule next
-will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
+will in general break non-interference~\cite{russo2006securing,BartheRRS07}.
 %

### 2014-03-02 paper/intro.tex
intro pass

@@
 e.g., per value in the system, systems may incur
-impractical runtime overhead.
+impractical runtime overhead~\cite{JSFlow}.
+%
+Moreover, the task of adding fine-grained IFC event to a simple language is
+non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
+such as JavaScript, this challenge is becomes almost insurmountable.
 
@@
 A recent system named SWAPI adds IFC to the
-browser by identifying \emph{web workers} as an existing computational
-unit.  Communication between workers is mediated using
+browser by identifying \emph{Web workers} as an existing computational
+unit~\cite{swapi}.  Communication between workers is mediated using
 IFC to ensure non-interference, preventing sensitive workers from
@@
   the IFC language that preserves non-interference. (Section~\ref{sec:formal})
+  \item We connect our formal semantics to real implementations of
+  coarse-grained IFC systems for Javascript and Haskell, and explain
+  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
   \item We briefly describe ways to enrich the core IFC language with
@@
   notation of clearance. (Section~\ref{sec:extensions})
-  \item We connect our formal semantics to real implementations of
-  coarse-grained IFC systems for Javascript and Haskell, and explain
-  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
   \item We informally relate our results to a monadic interpretation

### 2014-03-02 paper/intro.tex
typo

@@
 non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
-such as JavaScript, this challenge is becomes almost insurmountable.
+such as JavaScript, this challenge becomes almost insurmountable.
 

### 2014-03-02 paper/concrete.tex
capitalize titles.
remove outdated terminology.

@@
-\section{Concrete implementation}
+\section{Isomorphisms and Restrictions}
 \label{sec:concrete}
@@
     \item When we sandbox into an empty heap, existing addresses
-in the forked expression are no longer valid and the
+in the sandboxed expression are no longer valid and the
 task will get stuck (and then removed by \textsc{I-noStep}).
-Thus, we must rewrite the forked expression so that
+Thus, we must rewrite the sandboxed expression so that
 all addresses point to fresh addresses
@@
 \item When we clone the heap, we have to create a copy of everything
-reachable from the forked expression (not just the values for
+reachable from the sandboxed expression (not just the values for
 the memory addresses in the expression), and replace all addresses
@@
 now depends on whether that address existed at the time the receiving
-task was forked;  if it did, then the address should be rewritten to the
+task was sandboxed;  if it did, then the address should be rewritten to the
 new one, otherwise to a fresh address.
@@
 
-A better solution is to forbid forked expressions as well
+A better solution is to forbid sandboxed expressions as well
 as messages sent to other tasks to contain memory addresses in the
@@
 In a dynamically type languages such as |targetLangML|, we might
-restrict the transition for |fork| and |send| to only allow expressions
+restrict the transition for |sandbox| and |send| to only allow expressions
 without memory addresses.
@@
 
-\subsection{IFC language with a single heap}
+\subsection{IFC Language with a Single Heap}
 
@@
 the family of always valid predicates, except for the ones for
-\textsc{I-fork} and \textsc{I-send}, which we define as
+\textsc{I-sandbox} and \textsc{I-send}, which we define as
 \[ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) \]
 where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
-That is, we do not restrict any rules except for \textsc{I-fork}
+That is, we do not restrict any rules except for \textsc{I-sandbox}
 and \textsc{I-send}.
@@
   \begin{mathpar}
-    \inferrule[C-fork]
+    \inferrule[C-sandbox]
     {
@@
     {|
-      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
+      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
       .->
@@
       |iS(id') = Q|\\
-      |iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
+      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
     }
     {|
-      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
+      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
       ->

### 2014-03-02 paper/extensions.tex
more outdated terminology.

@@
         another); a clear violation of type safety.  In this case, operations
-        such as \textbf{send} have their typing rules require
+        such as |send| have their typing rules require
         the expressions being sent be typeable in an arbitrary well-typed store,
@@
         influences the difficulty of the type-safety proof for
-        \textbf{fork} when the target language has a store.  When
+        |sandbox| when the target language has a store.  When
         $\kappa$ is identity, most expressions can be allowed, since the store
         remains the same; if $\kappa$ drops the store, however, only closed expressions
-        can be forked.
+        can be sandboxed.
 \end{itemize}

### 2014-03-02 paper/formal.tex

--- 2014-03-02 paper/formal.tex
@@
 sensitive tasks current state when deciding which task to schedule next
-will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
+will in general break non-interference~\cite{russo2006securing,BartheRRS07}.
 %

### 2014-03-02 paper/proofs.tex
safe space in proof.

@@
   of length 0 is trivial, allowing
-  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
-  the theorem holds for derivation sequences of length up to $n$, and show that it also
-  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
+  us to simple chose $|ic2'=ic2|$.  In the step case,
+  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
   \[
@@
   \]
-  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
-  |ic''| with
-  \begin{equation} \label{eq:tsni-proof-1}
-  |ic1''| \approx_{|il|} |ic2''|
-  \qquad \text{and} \qquad
-  |ic2| |.->|^* |ic2''|
-  \end{equation}
-  Applying the induction hypothesis to
-  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
-  \begin{equation} \label{eq:tsni-proof-2}
-  |ic1'| \approx_{|il|} |ic2'|
-  \qquad \text{and} \qquad
-  |ic2''| |.->|^* |ic2'|
-  \end{equation}
-  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
-  us the right-hand side of the implication in the TSNI
-  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
+  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
+  the first step and
+  the induction hypothesis to the rest of the derivation sequence,
+  we directly get the desired property.
+  % long version
+%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+%  The base case for derivations
+%  of length 0 is trivial, allowing
+%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
+%  the theorem holds for derivation sequences of length up to $n$, and show that it also
+%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
+%  \[
+%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
+%  \]
+%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
+%  |ic''| with
+%  \begin{equation} \label{eq:tsni-proof-1}
+%  |ic1''| \approx_{|il|} |ic2''|
+%  \qquad \text{and} \qquad
+%  |ic2| |.->|^* |ic2''|
+%  \end{equation}
+%  Applying the induction hypothesis to
+%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
+%  \begin{equation} \label{eq:tsni-proof-2}
+%  |ic1'| \approx_{|il|} |ic2'|
+%  \qquad \text{and} \qquad
+%  |ic2''| |.->|^* |ic2'|
+%  \end{equation}
+%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
+%  us the right-hand side of the implication in the TSNI
+%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
 \end{proof}

### 2014-03-02 paper/intro.tex
typo.

@@
 %
-Moreover, the task of adding fine-grained IFC event to a simple language is
+Moreover, the task of adding fine-grained IFC even to a simple language is
 non-trivial~\cite{hritcu2013testing}; when considering a real-world language,

### 2014-03-02 paper/intro.tex
typo

@@
 In the alternative \textit{coarse-grained} approach to IFC,
-a system is divided into relatively course computational units,
+a system is divided into relatively coarse computational units,
 each with a single label dictating its security policy.
@@
 A recent system named SWAPI adds IFC to the
-browser by identifying \emph{Web workers} as an existing computational
+browser by identifying \emph{web workers} as an existing computational
 unit~\cite{swapi}.  Communication between workers is mediated using
@@
 a single security label with the entire computational unit simplifies
-understanding and easy reasoning about the correctness of the
-system, without information-flow reasoning about the
+understanding and reasoning about the correctness of the
+system, without information flow reasoning about the
 technical details of the semantics of the programming language.
@@
 defined language and a concrete implementation, showing that if this
-relationship holds, then noninterference in the abstract specification
+relationship holds, then non-interference in the abstract specification
 carries over to the concrete specification.

### 2014-03-02 paper/intro.tex
caps
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-02 paper/intro.tex
@@
   \item We connect our formal semantics to real implementations of
-  coarse-grained IFC systems for Javascript and Haskell, and explain
+  coarse-grained IFC systems for JavaScript and Haskell, and explain
   how our system could be used to enforce IFC in C. (Section~\ref{sec:real})

### 2014-03-02 paper/retrofit.tex
sec 2

@@
 mutable references and fixpoint, prepared for combination with an
-information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
+information flow control language.  The presentation is mostly standard, and utilizes Felleisen-Hieb reduction
 semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
-operational semantics of the system.  Our language defines an evaluation
-context |tE|; however, the evaluation rules have been expressed in terms
-of a different evaluation context |curlyRedE|,
-following the approach of Matthews and
-Findler~\cite{Matthews:2007:OSM:1190216.1190220} to simplify combining
-semantics of multiple languages.  To
-derive the usual operational semantics for this language, the evaluation
+operational semantics of the system.  One peculiarity is that our language
+defines an evaluation context |tE|, but, the evaluation rules have been
+expressed in terms of a different evaluation context |curlyRedE|;
+Here, we following the approach of Matthews and
+Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining
+semantics of multiple languages. 
+To derive the usual operational semantics for this language, the evaluation
 context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
@@
 reinterpret the meaning of this evaluation context.
+
 In general, we require that a target language be expressed in terms
@@
 
-In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
+Different from more traditional fine-grained language-based IFC systems that
+associate labels with values~\cite{sabelfeld2003language,
+Austin:Flanagan:PLAS09}, we follow~\cite{Zeldovich:2006, lio} in taking a
+coarse-grained floating-label approach and associating labels with
+\emph{tasks}.
+%
+The task label---we refer to the label of the currently executing task as the
+\emph{current label}---serves to protect everything in the task's scope;
+all data in a task shares this common label.
+%
+Hence before performing a reads or a write, the IFC monitor inspects the
+current label to decide whether the operation is permitted.
+%
+A task can only write to entities that are at least as sensitive.
+%
+Similarly, it can only read from entities that are less sensitive.
+%
+However, as in other floating-label systems, this current label can be raised
+to allow the task to read from more sensitive entities at the cost of giving up
+the ability to write to certain entities.
+
+In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-task}
 evaluation rules for a minimal information-flow control language.  
@@
     \item First-class labels, with label values $l$ as well as operations for computing on
-labels (|canFlowTo|, |lub| and |glb|),
-    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (since the current label's role is to protect everything in the task, the task can only increase its label),
-    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
-        which interact with the global store of per-task message queues |iS|, and
+labels (|canFlowTo|, |lub| and |glb|).
+    \item Operations for inspecting (\textbf{getLabel}) and modifying
+    (\textbf{setLabel}) the current label of the task (a task can only increase its label),
+    \item Operations for non-blocking inter-task communication (\textbf{send}
+    and \textbf{recv}), which interact with the global store of per-task
+    message queues |iS|, and
+%%     Labels are associated with message at the time of
+%%     the send; the label on a message must always be at least as sensitive as that
+%%     of the sending thread, since, conceptually, once a message is put on a
+%%     message queue it is no longer protected by the current label, rather it is
+%%     protected by the message label.
+%%     Dually, when reading a message with |recv| the current label of the
+%%     receiver must be at least as high as the message label.
     \item A sandboxing operation used to spawn new isolated tasks. In
-    concurrent settings |fork| corresponds to a fork-lie primitive; in a
+    concurrent settings |fork| corresponds to a fork-like primitive; in a
     sequential setting, it more closely resembles the LIO's
@@
 These operations are all defined with respect to an evaluation context
-|curlyBlueE| represents the context of the current task which is running, which
-has three important pieces of state: the global message queues |iS|, the
-current label |il| and the task ID |id|.
+|curlyBlueE| that represents the context of the current task which, by
+conventions is running; the evaluation context has three important pieces of
+state: the global message queues |iS|, the current label |il| and the task ID |id|.
 
-At a high level, the semantics define a coarse-grained floating-label IFC
-system~\cite{Zeldovich:2006, lio}, i.e., a system in which the current label of
-the task can be raised to protect everything in scope;
+We note that first class labels, tasks (albeit named differently), and
+operations for inspecting the current label are are essentially universal to
+all floating-label systems.
 %
-this is different from traditional fine-grained language-based IFC systems that
-associate labels with values~\cite{sabelfeld2003language,Austin:Flanagan:PLAS09}.
+However, our choice of communication primitives is motivated by
+those present in browsers, namely \texttt{postMessage}~\cite{webmessaging}.
 %
-We note that while first class labels and operations for inspecting the current
-label are are essentially universal to all floating-label systems, our choice
-of communication and isolation primitives is motivated by those present in
-browsers, namely \texttt{postMessage} and Workers~\cite{webworkers,webmessaging}.
+Of course, other choices, such as blocking communication or labeled channels,
+are possible (see Section~\ref{sec:extensions}).
 %
-Of course, other choices such as blocking communication or labeled channels are
-possible and further discussed in Section~\ref{sec:extensions}.
-%
-Though motivated by Web Workers, our notion of a task generalizes previous
-primitives considered by floating-label dynamic IFC
-systems~\cite{Zeldovich:2006, lio, stefan:addressing-covert,
-Hritcu:2013:YIB:2497621.2498098}.
 
-Our asynchronous communication primitives are worth some further
+These asynchronous communication primitives are worth further
 discussion.  When a task is sending a message using |send|, it also labels that
@@
 discussion of the implications of the choice of |klone|, but all our
-non-interference claims will hold regardless of the choice of |klone|.
+security claims will hold regardless of the choice of |klone|.
 

### 2014-03-02 paper/concrete.tex
Spelling
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 The rule for sandboxing is
-parameterized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
+parametrized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
 which defines what heap the new task
@@
 which allows us to give the two required functions
-|f| and |finv| for the isomorphism.  For conciseness, we informally
-give their definition and leave the straight-forward proof that they
+|f| and |finv| for the isomorphism.  For conciseness, we only give
+the interesting parts of their definition,
+and leave the straight-forward proof that they
 actually provide an isomorphism.

### 2014-03-02 paper/retrofit.tex
typo.

@@
 defines an evaluation context |tE|, but, the evaluation rules have been
-expressed in terms of a different evaluation context |curlyRedE|;
-Here, we following the approach of Matthews and
+expressed in terms of a different evaluation context |curlyRedE|.
+We follow the approach of Matthews and
 Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining
@@
 %
-Hence before performing a reads or a write, the IFC monitor inspects the
+Hence before performing a read or a write, the IFC monitor inspects the
 current label to decide whether the operation is permitted.

### 2014-03-02 paper/formal.tex

@@
 Though we do not model labeled channels, extending the calculus with such a
-feature is straight forward, see Setion~\ref{sec:extensions}.}
-then the |sec| tasks's decision to diverge or not is directly leaked to a
+feature is straight forward, see Section~\ref{sec:extensions}.}
+then the |sec| task's decision to diverge or not is directly leaked to a
 public entity.

### 2014-03-02 paper/related.tex
rm dead text
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
capitalize titles.

@@
-\section{Related work}
+\section{Related Work}
 \label{sec:related}
@@
 control can result in less false alarms and target legacy code, it comes at the
-cost of complexity (the system must accomodate the entirety of JavaScript's
+cost of complexity (the system must accommodate the entirety of JavaScript's
 semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
@@
 also been proposed for the web
-scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. \Red{Different
-from them, we rely on programming level abstraction to isolate
-computations.}
+scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
 

### 2014-03-02 paper/intro.tex
condensation
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 Leveraging this insight, we define a general form of coarse-grained
-dynamic IFC and show how IFC can be combined with \emph{any} programming
+dynamic IFC and show how it can be combined with \emph{any} programming
 language conforming to a general semantic framework.
@@
 communicate only through clearly specified interfaces.
-Based on a framework for combining the operational semantics
-of our core IFC calculus with the operational semantics of any target language,
+Using the Matthews-Findler approach~\cite{Matthews:2007:OSM:1190216.1190220}
+for combining operational semantics,
 we formally state and prove non-interference guarantees that are

### 2014-03-02 paper/extensions.tex
Fix broken
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 Our embedding assumes that the target language not have any
-primitives that can external-world effects.
+primitives that can induce external-world effects.
 %
-Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
-when considering real languages is precisely imposing this restriction
-on the concrete implementation.
+As discussed in Section~\ref{sec:real}, imposing this restriction
+can be challenging.
 %
@@
 %
-For example, code in our modified IFC browser must load resources or
+For example, code in an IFC browser must load resources or
 perform XHR to be useful.

### 2014-03-02 paper/extensions.tex
typo

--- 2014-03-02 paper/extensions.tex
@@
 For example, SWAPI provides a labeled version of the XHR object, while
-LIO implements a labeled file system, use in server-side web
+LIO implements a labeled file system, used in server-side web
 applications~\cite{hails}.

### 2014-03-02 paper/retrofit.tex

@@
 \end{mathpar}
-\caption{IFC language with all single-threaded operations}
+\caption{IFC language with all single-task operations.}
 \label{fig:ifc}
@@
 
+Rules \textsc{I-done} and \textsc{I-noStep} define the behavior of the system
+when the current thread has reduced to a value, or gotten stuck, respectively.
+%
+While these definitions simply rely on the underlying scheduling policy,
+|alpha|, to modify the task list, as we describe in Sections~\ref{sec:formal}
+and~\ref{sec:extensions}, these rules (notably, \textsc{I-noStep}) are crucial
+to proving our security guarantees.
+%
+For instance, it is unsafe for the whole system to get stuck if a particular
+task gets stuck, since a sensitive thread may then leverage this to leak
+information through the termination channel.
+%
+Instead, as our example |roundrobinf| scheduler shows, such tasks should simply
+be removed from the task list.
+
 %

### 2014-03-02 paper/proofs.tex
Move full proof to appendix.

@@
 \end{proof}
-\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
-  First, we observe there must be at least one task in |ic1|, otherwise
-  it could not take a step.  Thus, |ic1| is of the form
-  |iconf iS1 (it1, its1)|.  Consider two cases:
+\begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
+  For space reasons, we only sketch the structure of the proof here,
+  and refer the interested reader to the appendix where we give the
+  full proof.
+  The proof distinguishes two cases:
   \begin{itemize}
-    \item $|erase il it1|=|bullet|$.
-    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
-    where |lcurr| is the label of |it1|.
-    In this case, we do not need to take a step for
-    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
-    To see that, note that the tasks |its1| in |ic1| are left in the
-    same order and unmodified (the scheduling policy only
-    modifies the first task). The task |it1| either
-    gets dropped (by \textsc{I-noStep}), or
-    transforms into a task |it1'| as well as potentially spawning a new
-    task |it1''|.  Since both |it1'| and |it1''| have a label that is
-    at least as high as the label of |it1| (can be seen
-    by inspecting all reduction rules), they will get filtered
-    by |erasef il| in |ic1'|.  Therefore, the |il|-equivalence of the
-    task list is guaranteed.
-    Lets consider the possible changes to |iS1|:
-    Only three reduction interact with |iS1|,
-    thus it suffices to consider these cases:
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      A new message triple with label |il'| gets added to the message
-      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
-      the triple will get erased.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      In this case, only the queue of
-      task |it1| can change, which gets erased.
-    \end{description}
-    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
-    %    \alphacondition{We need all scheduling policies to not change the order
-    %      of any tasks (except for the first one).  Newly spawned task can appear
-    %      anywhere in the list.}
-    \item $|erase il it1|\neq|bullet|$.
-    Here, there must be a corresponding
-    task |it2| in |ic2|,
-    such that |it1=it2| (otherwise |ic1| and
-    |ic2| could not be |il|-equivalent).
-    However, |it2| might not be at the beginning of the task list yet, but
-    all tasks occurring before it must get erased by |erasef il|.
-    In |ic2|, we can first take some number of steps until |it2| moves
-    to the front of the list.
-    This is the case regardless of any additional side conditions $P$ on
-    rules, because for all of these tasks, it can either take an actual
-    step, or it gets dropped by \textsc{I-noStep} (which is always
-    possible, as there cannot be an additional side condition on this
-    rule).  All tasks that didn't get dropped are still at a label
-    that isn't below |il| and thus get erased.
-
-    %    \alphacondition{The scheduling policy must eventually let any task in
-    %      the task list evaluate.  In particular, it cannot get stuck when the
-    %      first task gets stuck, or keep executing a small number of tasks
-    %      exclusively forever (e.g. just execute the first task all the time
-    %      if it gets into an infinite loop).}
-
-    Therefore, after |ic2| has potentially executed some number of steps
-    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
-    respectively, don't get erased and are thus equivalent.
-    The task |it2| can now take exactly the same step as |it1|;  this
-    is true even with arbitrary additional premises $P$ that follow
-    the condition in Definition~\ref{def:restricted}, since those
-    predicates only depend on |erase il ic1|, which is equivalent
-    to |erase il ic2|, and thus those predicates evaluate in the same way.
-    Thus, we only
-    need to argue that the potential differences in |iS1| and |iS2| cannot
-    have an influence on the execution (and we know |iS1| and |iS2| are
-    |il|-equivalent).
-    Again, only sending and receiving will depend on, or change |iS|,
-    so we consider all these cases.
-    \begin{description}
-      \item[Case \textsc{I-send}]
-      Here, the task |it2| will send the same message to the same
-      receiver queue. This
-      queue is either completely erased, or it is |il|-equivalent.  In both
-      cases, |il|-equivalence of |iS1'| and |iS2'| is preserved.
-      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
-      When the tasks are receiving a message, then by the reduction rules
-      we know that they first filter the queue by the label
-      |lcurr| of |it1|.  We
-      also know that the queues are equivalent when filtered by the less
-      restrictive label |il|, thus the messages received (or dropped) from the
-      queue are equivalent.
-    \end{description}
+    \item If the task |it1| executed in |ic1| is erased, then there is no
+    need to take a step in |ic2|, as the computation in |ic1| does
+    not have any visible effects after erasure.
+    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
+    it can take exactly the same reduction step as the task in |ic1|.
+    The only difficulty is that there might be secret tasks executing
+    before |it2|, but it can be shown that these do not influence the
+    computation after erasure.
   \end{itemize}

### 2014-03-02 paper/conclusion.tex

@@
-\cut{
+%\cut{
 \section{Conclusion}
@@
 
-In this paper, we develop a general coarse-grained approach to IFC
-based on dividing a system into relatively course computational units
-and tracking only communication between these isolated units.
-We give formal semantics for the core coarse-grained
-information flow control language and show how a large class of target languages
-can be combined with it to achieve provable
-non-interference.
-We then give a proof technique for showing  non-interference
-of a concrete semantics for a potentially optimized IFC language
-by means of an isomorphism, and identify a class of IFC language restrictions
-that preserves non-interference.
-We briefly describe ways to enrich the core IFC language with
-more advanced concepts such as labeled values, privileges, or a
-notation of clearance and
-connect our formal semantics to real implementations of
-coarse-grained IFC systems for Javascript, Haskell, and
-(in less detail) enforcing IFC in C.
-Leaving more detailed presentation to later work,
-we informally relate our results to a monadic interpretation
-of IFC which guided our design.
-}
+We present a formal semantics which describes how to extend arbitrary languages
+with language-based coarse-grained IFC. We provably show the security guarantees
+TSNI and TINI non-interference, where the proof technique is parametrized on the
+target language, and it is developed for two ubiquitous scheduling policies. In
+addition, we provide conditions to securely refine our formal semantics to
+consider optimizations required in practice. Finally, we describe extensions to
+the core IFC language with more advanced concepts like labeled values, privileges,
+and a notation of clearance, and therefore connecting it with existing
+IFC implementations for Javascript, Haskell, and (in
+less detail) proposing IFC for C.
+
+With this work, we set a global framework which describes how ideas from
+OS can be systematically applied in programming languages.
+
+% In this paper, we develop a general coarse-grained approach to IFC
+% based on dividing a system into relatively course computational units
+% and tracking only communication between these isolated units.
+% We give formal semantics for the core coarse-grained
+% information flow control language and show how a large class of target languages
+% can be combined with it to achieve provable
+% non-interference.
+% We then give a proof technique for showing  non-interference
+% of a concrete semantics for a potentially optimized IFC language
+% by means of an isomorphism, and identify a class of IFC language restrictions
+% that preserves non-interference.
+% We briefly describe ways to enrich the core IFC language with
+% more advanced concepts such as labeled values, privileges, or a
+% notation of clearance and
+% connect our formal semantics to real implementations of
+% coarse-grained IFC systems for Javascript, Haskell, and
+% (in less detail) enforcing IFC in C.
+% Leaving more detailed presentation to later work,
+% we informally relate our results to a monadic interpretation
+% of IFC which guided our design.
+% }

### 2014-03-02 paper/conclusion.tex
slice up
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-We present a formal semantics which describes how to extend arbitrary languages
-with language-based coarse-grained IFC. We provably show the security guarantees
-TSNI and TINI non-interference, where the proof technique is parametrized on the
-target language, and it is developed for two ubiquitous scheduling policies. In
-addition, we provide conditions to securely refine our formal semantics to
-consider optimizations required in practice. Finally, we describe extensions to
+We presented a formal semantics which describes how to extend arbitrary languages
+with language-based coarse-grained IFC. We prove the security guarantees
+TSNI and TINI, where the proof technique is parametrized on the
+target language, for two scheduling policies. In
+addition, we provided conditions on how to securely refine our formal semantics to
+consider optimizations required in practice. Finally, we described extensions to
 the core IFC language with more advanced concepts like labeled values, privileges,
@@
 less detail) proposing IFC for C.
-
-With this work, we set a global framework which describes how ideas from
-OS can be systematically applied in programming languages.
 

### 2014-03-02 paper/conclusion.tex
nit on conclusions

--- 2014-03-02 paper/conclusion.tex
@@
 addition, we provide conditions to securely refine our formal semantics to
-consider optimizations required in practice. Finally, we describe extensions to
-the core IFC language with more advanced concepts like labeled values, privileges,
-and a notation of clearance, and therefore connecting it with existing
-IFC implementations for Javascript, Haskell, and (in
-less detail) proposing IFC for C.
-
-With this work, we set a global framework which describes how ideas from
-OS can be systematically applied in programming languages.
+consider optimizations often required in practice. Finally, we describe
+extensions to the core IFC language with more advanced concepts like labeled
+values, privileges, and a notation of clearance, which allows us to draw
+connections to existing IFC implementations for Javascript, Haskell, and (in
+less detail) proposing IFC for C. With this work, we aim to expose how ideas
+from IFC in OS can be systematically applied in programming languages.
 

### 2014-03-02 paper/appendix.tex

\appendix
\section{Full Non-Interference Proof}
\label{sec:appendix}

In the main body of the paper we have only sketched the proof structure
for Lemma~\ref{lemma:rr-tsni-general}.  Here we give it with full
details.

\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$.
    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
    where |lcurr| is the label of |it1|.
    In this case, we do not need to take a step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1| (can be seen
    by inspecting all reduction rules), they will get filtered
    by |erasef il| in |ic1'|.  Therefore, the |il|-equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to |iS1|:
    Only three reduction interact with |iS1|,
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label |il'| gets added to the message
      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task |it1| can change, which gets erased.
    \end{description}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
    %    \alphacondition{We need all scheduling policies to not change the order
    %      of any tasks (except for the first one).  Newly spawned task can appear
    %      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.
    Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il|-equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list.
    This is the case regardless of any additional side conditions $P$ on
    rules, because for all of these tasks, it can either take an actual
    step, or it gets dropped by \textsc{I-noStep} (which is always
    possible, as there cannot be an additional side condition on this
    rule).  All tasks that didn't get dropped are still at a label
    that isn't below |il| and thus get erased.

    %    \alphacondition{The scheduling policy must eventually let any task in
    %      the task list evaluate.  In particular, it cannot get stuck when the
    %      first task gets stuck, or keep executing a small number of tasks
    %      exclusively forever (e.g. just execute the first task all the time
    %      if it gets into an infinite loop).}

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
    respectively, don't get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  this
    is true even with arbitrary additional premises $P$ that follow
    the condition in Definition~\ref{def:restricted}, since those
    predicates only depend on |erase il ic1|, which is equivalent
    to |erase il ic2|, and thus those predicates evaluate in the same way.
    Thus, we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il|-equivalent).
    Again, only sending and receiving will depend on, or change |iS|,
    so we consider all these cases.
    \begin{description}
      \item[Case \textsc{I-send}]
      Here, the task |it2| will send the same message to the same
      receiver queue. This
      queue is either completely erased, or it is |il|-equivalent.  In both
      cases, |il|-equivalence of |iS1'| and |iS2'| is preserved.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      When the tasks are receiving a message, then by the reduction rules
      we know that they first filter the queue by the label
      |lcurr| of |it1|.  We
      also know that the queues are equivalent when filtered by the less
      restrictive label |il|, thus the messages received (or dropped) from the
      queue are equivalent.
    \end{description}
  \end{itemize}
\end{proof}

### 2014-03-02 paper/proofs.tex
wording
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
-  For space reasons, we only sketch the structure of the proof here,
-  and refer the interested reader to the appendix where we give the
-  full proof.
+  For space reasons, we only sketch the structure of the proof here.
+  We refer the interested reader to the Appendix for a full proof.
   The proof distinguishes two cases:

### 2014-03-02 paper/retrofit.tex

--- 2014-03-02 paper/retrofit.tex
@@
 To get a feeling for how these operational semantics operate, we
-describe a few sample programs, and their corresponding outputs.
+describe a few sample programs, and their corresponding behavior.
 
@@
 \begin{align*}
-    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))| \\
-    & |in TI (send (IT (ref true)))|
+    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))|\\
+    & |in TI (send (IT i) getLabel (IT (ref true)))|
 \end{align*}
@@
 will be received by the sandboxed task, but it will be a dangling pointer; the
-task will become stuck and removed from execution by \textsc{I-noStep}.  Readers
+task will get stuck (under the |roundrobinf| scheduler the \textsc{I-noStep} will in turn remove it from the task list).  Readers
 who are curious whether or not a static discipline could be enforced to
@@
 
-\paragraph{Status of the heap after a sandbox}  Here is a program whose
+\paragraph{Status of the heap after a sandbox}  Consider a program whose
 semantics depends on the definition of |klone|:
@@
 When |klone| is the identity, the sandboxed task successfully dereferences
-the contents of the reference to be true twice (recall that references
-are cloned into the new global state).  When $\kappa$ is the constant function
-to the empty store, $x$ becomes a dangling pionter.
+the contents of the reference to be |true| twice (recall that references
+are cloned into the new global state).  When |klone| is the constant function
+to the empty store, |x| is a dangling pointer.
 
-\paragraph{Exceptions}  One language feature that has caused difficulty
-for many information flow control systems is handling
-exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}.  The key difficulty
-appears when an exception must cross a stack boundary where the current
-label reverts back, i.e. across a |toLabeled| operator~\cite{lio}.
+\paragraph{Exceptions}  One language feature that has caused difficulty for
+many information flow control systems is handling exceptions.
+%
+The key difficulty appears when considering the propagation of exceptions
+across stack boundaries where the current label is restored, e.g., from secret
+to public, as done by LIO's |toLabeled| and Breeze's
+brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
+%
 If the exception crosses this boundary, it can leak information about the
-inner sensitive computation.
+inner secret computation into a public computation.
 

### 2014-03-02 paper/retrofit.tex
small fixes + explain I-noStep

@@
     \item A sandboxing operation used to spawn new isolated tasks. In
-    concurrent settings |fork| corresponds to a fork-like primitive; in a
+    concurrent settings |fork| corresponds to a fork-like primitive,
+    whereas in a
     sequential setting, it more closely resembles the LIO's
@@
 |curlyBlueE| that represents the context of the current task which, by
-conventions is running; the evaluation context has three important pieces of
+conventions is running. The evaluation context has three important pieces of
 state: the global message queues |iS|, the current label |il| and the task ID |id|.
@@
 function is simply the identity function, i.e.,
-|filter il nil = nil|; otherwise:
+|filter il nil = nil|, and otherwise:
 \[
@@
     \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.
-The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|;
+The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
     Figure~\ref{fig:scheduler} defines two concrete schedulers.
@@
 security claims will hold regardless of the choice of |klone|.
+
+The rule \textsc{I-noStep} says something about configurations for which
+it is not possible to take a transition.  The notation
+$|ic|\not\overset{\alpha}{\hookrightarrow}$ in the premise
+is meant to be understood as
+follows:  If the configuration |ic| cannot take a step by any rule other
+than \textsc{I-noStep}, then \textsc{I-noStep} applies and the
+stuck task gets removed.
 

### 2014-03-02 paper/retrofit.tex
minor

@@
 We note that our embedding corresponds to the lump embedding
-of~\cite{Matthews:2007:OSM:1190216.1190220}, terms in one language are
+of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
 treated opaquely in the other.

### 2014-03-02 paper/retrofit.tex
grammar
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-02 paper/retrofit.tex
@@
 expressed in terms of a different evaluation context |curlyRedE|;
-Here, we following the approach of Matthews and
+Here, we follow the approach of Matthews and
 Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining

### 2014-03-02 paper/retrofit.tex
nit
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-Different from more traditional fine-grained language-based IFC systems that
+As opposed to more traditional fine-grained language-based IFC systems that
 associate labels with values~\cite{sabelfeld2003language,

### 2014-03-02 paper/retrofit.tex

@@
 \begin{itemize}
-    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
+    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.~\cite{Matthews:2007:OSM:1190216.1190220}
     %

### 2014-03-02 paper/retrofit.tex
yo

@@
 If the exception crosses this boundary, it can leak information about the
-inner secret computation into a public computation.
+inner secret computation into a public computation; hence, both systems
+explicitly ensure that |toLabeled| does not propagate exceptions.
 
-At first glance, it does not appear that our system has any such operator;
-there are only tasks, and the correct behavior for a task throwing
-an exception is self-evident: it should simply be removed from the scheduler.
-However, under a \emph{sequential scheduler} (such as |seqf|),
-the behavior of |sandbox|
-can be used to model the behavior of such an operator:
+Our general embedding approach provides these semantics by construction.
+%
+To show this, consider, first, the encoding of the sequential |toLabeled|
+construct in our framework:
 \begin{align*}
@@
 \end{align*}
-When the sequential scheduler is used, the sandboxed task runs to
-completion before returning to the task that sandboxed it.  Thus,
-a task list should rather be interpreted as a number of information flow
-aware stack frames.  To read the result of a |toLabeled| operation
+When using the sequential scheduler |seqf|, the sandboxed task runs to
+completion before returning to the task that sandboxed it. 
+(Here, a task list can be interpreted as a number of information flow aware
+stack frames.)
+To read the result of a |toLabeled| operation
 (which is communicated via message passing), the parent task must raise
-its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
-channel, we might mix up our messages.  Indeed, a proper development requires
-the ability to allocate fresh channels; for purposes of simplicity, this
-has been omitted.}
+its label; otherwise the label will get dropped, as per the \textsc{I-recv}
+rule.\footnote{A keen reader may note that with a single, per-task channel, we
+might mix up our messages.  Indeed, a proper development requires the ability
+to allocate fresh channels; for purposes of simplicity, this has been omitted.}
 
-In this setting, it is also clear that exceptions should not cross boundaries,
-as seen in |toLabeled l fail; true|, which evaluates to |true| no matter even in
-the event of an exception inside of the |toLabeled| block:
-\todo{sh}{leaving this to ds, who wanted to finish the example}
+Second, suppose that our |targetLangML| is extended with a single exception
+expression |fail|, which reduces to |fail|, removing all containing |tE|
+evaluation contexts, i.e., it propagates up to a |IT (-)| boundary.
+%
+In this setting, it is clear that exceptions cannot cross boundaries.
+%
+For instance, 
+\begin{code}
+TI(toLabeled l (IT (if te then fail else true))); true
+\end{code}
+always evaluates to |true|, regardless of the value of |te|.
+%
+As in both LIO and Breeze, however, only when calling |recv| on such messages
+will the exception be propagated.
+%
+This of course, is not a leak since the current label must be raised before
+receiving sensitive message, regardless of their content.

### 2014-03-02 paper/retrofit.tex
simple
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 %
-To show this, consider, first, the encoding of the sequential |toLabeled|
+To show this, we first define an encoding of the sequential |toLabeled|
 construct in our framework:
@@
 
-Second, suppose that our |targetLangML| is extended with a single exception
+Now suppose that our |targetLangML| is extended with a single exception
 expression |fail|, which reduces to |fail|, removing all containing |tE|
@@
 %
-As in both LIO and Breeze, however, only when calling |recv| on such messages
+Just like in both LIO and Breeze, however, only when calling |recv| on such messages
 will the exception be propagated.

### 2014-03-02 paper/extensions.tex
typo

@@
 
-    \item In the case of mini-ML, type safety proceeds by a preservation theorem
+    \item In the case of mini-ES, type safety proceeds by a preservation theorem
         that refers to well-typed stores.  In our setting, there are now multiple
@@
 Previous approaches have modeled external effects by internalizing the
-effects as writes/reads to labeled channels/references~\tocite{}.
+effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
 %

### 2014-03-02 paper/conclusion.tex
yo

--- 2014-03-02 paper/conclusion.tex
@@
 the core IFC language with more advanced concepts like labeled values, privileges,
-and a notation of clearance, and therefore connecting it with existing
-IFC implementations for Javascript, Haskell, and (in
-less detail) proposing IFC for C.
+and a notion of clearance, and therefore connecting it with existing
+IFC implementations for JavaScript, Haskell, and (in
+less detail) proposing IFC for C. With this work, we aim to expose how ideas
+from IFC in OS can be systematically applied in programming languages.
 

### 2014-03-02 paper/intro.tex
cite
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
grammar
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
notation is not notion

@@
 communication between isolated computational units must be tracked.
-A recent system named SWAPI adds IFC to the
+A recent system named SWAPI~\cite{swapi} adds IFC to the
 browser by identifying \emph{web workers} as an existing computational
-unit~\cite{swapi}.  Communication between workers is mediated using
+unit.  Communication between workers is mediated using
 IFC to ensure non-interference, preventing sensitive workers from
@@
   more advanced concepts such as labeled values, privileges, or a
-  notation of clearance. (Section~\ref{sec:extensions})
+  notion of clearance. (Section~\ref{sec:extensions})
   \item We informally relate our results to a monadic interpretation

### 2014-03-08 paper/retrofit.tex
Fix color in lambda_ES.

@@
 te   ::= tv | tx | te te | if te then te else te
-       | ref te | !te | te := te | fix e
+       | ref te | !te | te := te | fix te
 tE   ::= tHole | tE te | tv tE | if tE then te else te
-       | ref tE | !tE | tE := te | tv := tE | fix E
+       | ref tE | !tE | tE := te | tv := tE | fix tE
 

### 2014-04-11 paper/retrofit.tex
Fix two bugs pointed out by Stefan (sandbox should not evaluate e, and we don't need a barrier)
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-02 paper/retrofit.tex
@@
        |  sandbox ie | send ie ie ie | recvf ix ix ie ie
-iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE
+iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE
        |  send iE ie ie | send iv iE ie | send iv iv iE
@@
 |it1 = fullconf id il tS (iniE id')|\\
-|itnew = fullconf id' il tS' (TI ie)|\\
+|itnew = fullconf id' il tS' ie|\\
 |ap fresh id'|

### 2014-04-24 paper/rebuttal.txt
Rebuttal draft.

We would like to thank all reviewers for their feedback and suggestions.  We will first reply to high-level comments and then reply to specific questions in the reviews.

High-level comments
-------------------

Several reviewers raised questions about the generality as well as the practical scalability of our approach, in particular with regards to external effects.  We note that as a first step our framework assumes the target language to be free of external effects.  The problem of adding IFC even to such languages is non-trivial and error-prone (e.g., see [29]).  Furthermore, some practical languages like ECMAScript are of this form, and external effects such as XMLHttpRequest are added as extensions to it in browsers to arrive at JavaScript.
Devising a general mechanism to deal with external effects is challenging and requires a formal definition of the external effects, which can vary widely across systems.  Soundly dealing with such external effects requires these effects to be internalized into the IFC language, and for XMLHttpRequest in SWAPI we show how do exactly that.

Another point raised by the reviewers is the missing connection between the real-world examples and the formal framework, and that it feels like we are trying to shoe-horn two previous one-off retrofittings into a unified framework.  This is not the case, in fact, the cause-and-effect relationship is the other way around.  The general framework for IFC presented in this paper has influenced both SWAPI as well as LIO, helping to decide what a non-interfering implementation needs to provide.  For example, mumble mumble exceptions.

Reviewer 1 asks about the extension section, and whether these are speculative ideas or not.  Extensions to the IFC language are largely orthogonal to the core contribution of combining coarse-grained IFC with a target language.  To keep the presentation in earlier clean of orthogonal distractions, we only present more advanced IFC features in the extension section.  However, these extensions have been worked out, and are also part of the JavaScript or Haskell implementation, or both.
W.r.t. the comment about labeled references not being amenable to Matthews-Findler-style semantics, we note that in a coarse-grained approach like ours, the labeled references are part of the IFC state and the references are distinct from the native references a target language might have.  For this reason, there is no conflict with the approach of Matthews and Findler.

Specific questions
------------------

Reviewer 1 ask why we have not developed our formalism with a monad.  One of our motivations was to formalize an IFC system for JavaScript, whose semantics are typically not presented in a stratified way by distinguishing a monadic and a pure fragment.  A non-monadic approach enables a more natural formalism for a large class of languages, including JavaScript.

Reviewer 2 ask about the proof strategy for Theorem 3.  Performing induction on the length of the derivation sequence followed by induction on the derivation tree is standard for small-step operational semantics.  This is isomorphic to induction on the structure of the derivation for ->*.

Reviewer 1 ask about the soundness of the JS-send rule.  While omitted in the paper, this rule can be proven to be non-interfering.  Intuitively, for an attacker at level L, the additional premise evaluates regardless of secrets at a level above L, thus ensuring that no secrets can be observed.

Reviewer 2 correctly points out that on page 6 the second \Sigma_1 in c_1 should be \Sigma_2.

Reviewer 3 asks about shared mutable references:  It is correct that a different design choice might allow shared mutable references in this way.  However, because native references are protected by the current label, this would effectively be a fine-grained IFC system, requiring checks for all reference reads and writes.  This would be against our goal of a coarse-grained system.  We will improve the unfortunate phrase in our paper.

Reviewer 3 asks about the values sent across channels in SWAPI.  For simplicity, we require them to be strings in the paper, thought any structurally cloned object (as well as labeled blobs) are allowed in the actual implementation.

As reviewer 3 points out, the reference about SWAPI does not include an URL.  It is available at http://deian.net/swapi.pdf and currently not indexed by search engines because the paper is under anonymous review.  We apologize for the mistake.

### 2014-04-25 paper/rebuttal.txt
rebuttal

@@
-We would like to thank all reviewers for their feedback and suggestions.  We will first reply to high-level comments and then reply to specific questions in the reviews.
+# Generality and novelty of the system
 
-High-level comments
--------------------
+A reviewer raised the question of the generality of the framework and
+asks how does our work scales in practice -- indeed if there is clear
+path to retrofitting real languages with IFC or did we just shoe-horn
+SWAPI and LIO into a "unified framework".
 
-Several reviewers raised questions about the generality as well as the practical scalability of our approach, in particular with regards to external effects.
-We note that as a first step our framework assumes the target language to be free of external effects.
-The problem of adding IFC even to such languages is non-trivial and error-prone (e.g., see [29]).
-Furthermore, some practical languages like ECMAScript are of this form, and external effects such as XMLHttpRequest are added as extensions to it in browsers to arrive at JavaScript.
-Devising a general mechanism to deal with external effects is challenging and requires a formal definition of the external effects, which can vary widely across systems.
-Soundly dealing with such external effects requires these effects to be internalized into the IFC language, and for XMLHttpRequest in SWAPI we show how do exactly that.
+First, we note that our framework assumes that the target language
+must not have external effects. In section 6 we show how real-world
+languages can be constrained to achieve this. For C we use Dune, for
+Haskell we use types, and for browser-JS we use CSP. Unfortunately due
+to space restrictions we left the discussion of the mapping to the
+formalism as informal discussion (doing this at the cost of section 8
+seems natural).
 
-Another point raised by the reviewers is the missing connection between the real-world examples and the formal framework, and that it feels like we are trying to shoe-horn two previous one-off retrofittings into a unified framework.
-This is not the case, in fact, the cause-and-effect relationship is the other way around.
-The general framework for IFC presented in this paper has influenced both SWAPI as well as LIO, helping to decide what a non-interfering implementation needs to provide.
-For example, mumble mumble exceptions.
+We do not claim that our work is general enough to handle languages
+where effects cannot be tamed (we will emphasize this on revision).
+Yet some languages can be tamed (as we discuss) and others don't even
+have external effects.  For example, our work is directly applicable
+to "vanilla" JS (EcmaScript), which does not have any external effects
+-- indeed, under one lens, one can see our work as presenting an
+alternative (to [25]) IFC semantics for JS.  Indeed the motivation
+behind this work was to address the question of how to build an
+efficient, non-intrusive IFC system for JS.
 
-Reviewer 1 asks about the extension section, and whether these are speculative ideas or not.
-Extensions to the IFC language are largely orthogonal to the core contribution of combining coarse-grained IFC with a target language.
-To keep the presentation in earlier clean of orthogonal distractions, we only present more advanced IFC features in the extension section.
-However, these extensions have been worked out, and are also part of the JavaScript or Haskell implementation, or both.
-W.r.t.
-the comment about labeled references not being amenable to Matthews-Findler-style semantics, we note that in a coarse-grained approach like ours, the labeled references are part of the IFC state and the references are distinct from the native references a target language might have.
-For this reason, there is no conflict with the approach of Matthews and Findler.
+While our language uses ideas from LIO and SWAPI, we note that the
+current (and at the time of the writing) versions of these systems are
+using the concepts of this paper. It is not the case that "the
+framework didn't come first". For instance, in LIO [53] (and Breeze
+[28]) exceptions were original treated in a rather complex fashion; as
+we discuss in the paper, exceptions are internal effects and thus the
+security concern becomes trivial; LIO now uses this approach (and
+regular Haskell exceptions vs. labeled exceptions).
 
-Specific questions
-------------------
+Addressing the first reviewer's concern that the IFC system presented
+is a rehash prior work, we remark that this approach of dealing with
+internal effects and our asynchronous communication primitives is
+novel. Moreover, we believe that the formalization serves as a
+stepping stone for reasoning about IFC OS work.
+
+# Extensions
+
+The reviewers asked if we actually worked out the extensions to
+language. We chose to present the core ideas separate from extensions
+for simplicity and because the features largely depend on the
+embedding. For example, labeled MVars are natural to Haskell, but
+not JS. Nevertheless, these extensions have been formalized and are
+implemented in LIO and/or SWAPI. (The only extension common
+to both system systems are labeled values.) The main points on how
+to extend the system with such features follows from the discussion:
+they must be added to the IFC language and the no sharing
+"sandbox-local pointers" rule (of send) must be used.  For example,
+in the labeled references case we amend the IFC language state to
+contain a labeled reference store; these labeled references are
+distinct from the native references a target language might have and
+all access abides by IFC.  (For this reason, there is also no
+conflict with the approach of Matthews and Findler as brought up by
+the first reviewer.)
+
+# External effects
+
+The reviewers are concerned that our treatment of external effects
+makes the work incomplete. We remark that like other IFC systems [A
+XXXX Z], external effects can be handled by internalizing them into
+the IFC language. In practice and as in the XMLHttpRequest (as used in
+SWAPI) case this amounts to wrapping the "native" unsafe code. While
+we can extend the language with a general external effect primitive
+(e.g., 'out') we do not think this add much value, formally or
+practically. Finally, and most importantly, the treatment of external
+effects is very much application specific. For instance, the HTTP
+client in SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both
+wrap the native code with label checks, but the semantics differ
+(simply because of the different use cases: browser vs. server).
+While important for (certain) practical applications, we believe that
+general treatment of such effects is an open problem and complementary
+to this work.
+
+# Other questions
+
+Reviewer 3 asks about shared mutable references:  It is correct that a
+different design choice might allow shared mutable references in this
+way.  However, because native references are protected by the current
+label, this would effectively be a fine-grained IFC system, requiring
+checks for all reference reads and writes.  This would be against our
+goal of a coarse-grained system.  We will improve the unfortunate
+phrasing.
+
+Reviewer 3 asks about the values sent across channels in SWAPI.  For
+simplicity, we require them to be strings in the paper, thought any
+structurally cloned object (as well as labeled blobs) are actually
+permitted.
 
 Reviewer 1 ask why we have not developed our formalism with a monad.
-One of our motivations was to formalize an IFC system for JavaScript, whose semantics are typically not presented in a stratified way by distinguishing a monadic and a pure fragment.
-A non-monadic approach enables a more natural formalism for a large class of languages, including JavaScript.
+One of our motivations was to formalize an IFC system for JavaScript,
+whose semantics are typically not presented in a stratified way by
+distinguishing a monadic and a pure fragment.  A non-monadic approach
+enables a more natural formalism for a large class of languages,
+including JavaScript.
 
-Reviewer 2 ask about the proof strategy for Theorem 3.
-Performing induction on the length of the derivation sequence followed by induction on the derivation tree is standard for small-step operational semantics.
-This is isomorphic to induction on the structure of the derivation for ->*.
+Reviewer 2 ask about the proof strategy for Theorem 3.  Performing
+induction on the length of the derivation sequence followed by
+induction on the derivation tree is standard for small-step
+operational semantics.  This is isomorphic to induction on the
+structure of the derivation for ->*.
 
-Reviewer 1 ask about the soundness of the JS-send rule.
-While omitted in the paper, this rule can be proven to be non-interfering.
-Intuitively, for an attacker at level L, the additional premise evaluates regardless of secrets at a level above L, thus ensuring that no secrets can be observed.
+Reviewer 1 ask about the soundness of the JS-send rule.  While omitted
+in the paper, this rule can be proven to be non-interfering.
+Intuitively, for an attacker at level L, the additional premise
+evaluates regardless of secrets at a level above L, thus ensuring that
+no secrets can be observed.
 
-Reviewer 2 correctly points out that on page 6 the second \Sigma_1 in c_1 should be \Sigma_2.
-
-Reviewer 3 asks about shared mutable references:  It is correct that a different design choice might allow shared mutable references in this way.
-However, because native references are protected by the current label, this would effectively be a fine-grained IFC system, requiring checks for all reference reads and writes.
-This would be against our goal of a coarse-grained system.
-We will improve the unfortunate phrase in our paper.
-
-Reviewer 3 asks about the values sent across channels in SWAPI.
-For simplicity, we require them to be strings in the paper, thought any structurally cloned object (as well as labeled blobs) are allowed in the actual implementation.
-
-As reviewer 3 points out, the reference about SWAPI does not include an URL.
-It is available at http://deian.net/swapi.pdf and currently not indexed by search engines because the paper is under anonymous review.
-We apologize for the mistake.
+As reviewer 3 points out, the reference about SWAPI does not include
+an URL.  It is available at http://deian.net/swapi.pdf and currently
+not indexed by search engines because the paper is being anonymously
+submitted.  We apologize for the mistake.

### 2014-04-25 paper/rebuttal.txt
First section edits
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-A reviewer raised the question of the generality of the framework and
-asks how does our work scales in practice -- indeed if there is clear
-path to retrofitting real languages with IFC or did we just shoe-horn
-SWAPI and LIO into a "unified framework".
-
-First, we note that our framework assumes that the target language
-must not have external effects. In section 6 we show how real-world
-languages can be constrained to achieve this. For C we use Dune, for
-Haskell we use types, and for browser-JS we use CSP. Unfortunately due
-to space restrictions we left the discussion of the mapping to the
-formalism as informal discussion (doing this at the cost of section 8
-seems natural).
+A reviewer asked if our system really applies to real-world languages,
+pointing to our inability to deal with external effects.  It is true
+that our framework assumes that the target language must not have
+external effects.  However, this is not an unreasonable constraint: in
+Section 6, we discussed how real-world languages can be constrained to
+achieve this.  Unfortunately due to space restrictions we left the
+discussion of the mapping to the formalism as informal discussion (doing
+this at the cost of section 8 seems natural).
 
@@
 
-While our language uses ideas from LIO and SWAPI, we note that the
-current (and at the time of the writing) versions of these systems are
-using the concepts of this paper. It is not the case that "the
-framework didn't come first". For instance, in LIO [53] (and Breeze
-[28]) exceptions were original treated in a rather complex fashion; as
-we discuss in the paper, exceptions are internal effects and thus the
-security concern becomes trivial; LIO now uses this approach (and
-regular Haskell exceptions vs. labeled exceptions).
+Similarly, there was a comment that this work simply shoe-horned SWAPI
+and LIO into a "unified framework".  While our language uses ideas from
+LIO and SWAPI, we note that the current (and at the time of the writing)
+versions of these systems are using the concepts of this paper. It is
+not the case that "the framework didn't come first". For instance, in
+LIO [53] (and Breeze [28]) exceptions were originally treated in a rather
+complex fashion; as we discuss in the paper, exceptions are internal
+effects and thus the security concern becomes trivial; LIO was modified to
+adopt this new approach.
 
-Addressing the first reviewer's concern that the IFC system presented
-is a rehash prior work, we remark that this approach of dealing with
+As for the first reviewer's concern that the IFC system presented
+is simply a rehash of prior work, we claim the approach of dealing with
 internal effects and our asynchronous communication primitives is
 novel. Moreover, we believe that the formalization serves as a
-stepping stone for reasoning about IFC OS work.
+stepping stone for formal reasoning about IFC OS work.
 

### 2014-04-25 paper/rebuttal.txt
Minor changes.
changes after chatting with ale

@@
-# Generality and novelty of the system
+Generality and novelty of the system
+------------------------------------
 
@@
 -- indeed, under one lens, one can see our work as presenting an
-alternative (to [25]) IFC semantics for JS.  Indeed the motivation
-behind this work was to address the question of how to build an
-efficient, non-intrusive IFC system for JS.
+alternative (to [25]) coarse-grained IFC system for JS.  Indeed the
+motivation behind this work was to address the question of how to
+build an efficient, non-intrusive IFC system for JS.
 
@@
 
-As for the first reviewer's concern that the IFC system presented
-is simply a rehash of prior work, we claim the approach of dealing with
+As for the first reviewer's concern that the IFC system presented is
+simply a rehash of prior work, we claim the approach of dealing with
 internal effects and our asynchronous communication primitives is
-novel. Moreover, we believe that the formalization serves as a
-stepping stone for formal reasoning about IFC OS work.
+novel. To our knowledge this is the first language-based dynamic IFC
+system to use such asynchronous primitives and work on both concurrent
+and sequential schedulers. (While simple, the checks performed by our
+asynchronous communication primitives imply a more flexible
+system---synchronous primitives effectively impose that the end-points
+have the same label.) Moreover, we believe that our formalization
+serves as a stepping stone for formal reasoning about IFC OS work.
 
-# Extensions
+Extensions
+----------
 
@@
 
-# External effects
+External effects
+----------------
 
@@
 client in SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both
-wrap the native code with label checks, but the semantics differ
-(simply because of the different use cases: browser vs. server).
-While important for (certain) practical applications, we believe that
-general treatment of such effects is an open problem and complementary
-to this work.
+wrap the native code with label checks, but the actual label checks
+differ simply because of the different setting and attacker models:
+browser vs. server.  While important for (certain) practical
+applications, we believe that general treatment of such effects is an
+open problem and complementary to this work.
 
-# Other questions
+Other questions
+---------------
+
+As reviewer 3 points out, the reference about SWAPI does not include
+an URL.  It is available at http://deian.net/swapi.pdf and currently
+not indexed by search engines because the paper is being anonymously
+submitted.  We apologize for the mistake.
+
+Reviewer 1 ask why we have not developed our formalism with a monad.
+One of our motivations was to formalize an IFC system for JavaScript,
+whose semantics are typically not presented in a stratified way by
+distinguishing a monadic and a pure fragment.  A non-monadic approach
+enables a more natural formalism for a large class of languages,
+including JavaScript.
+
+Reviewer 2 ask about the proof strategy for Theorem 3.  Performing
+induction on the length of the derivation sequence followed by
+induction on the derivation tree is standard for small-step
+operational semantics.  This is isomorphic to induction on the
+structure of the derivation for ->*.
 
@@
 
-Reviewer 1 ask why we have not developed our formalism with a monad.
-One of our motivations was to formalize an IFC system for JavaScript,
-whose semantics are typically not presented in a stratified way by
-distinguishing a monadic and a pure fragment.  A non-monadic approach
-enables a more natural formalism for a large class of languages,
-including JavaScript.
-
-Reviewer 2 ask about the proof strategy for Theorem 3.  Performing
-induction on the length of the derivation sequence followed by
-induction on the derivation tree is standard for small-step
-operational semantics.  This is isomorphic to induction on the
-structure of the derivation for ->*.
-
 Reviewer 1 ask about the soundness of the JS-send rule.  While omitted
@@
 no secrets can be observed.
-
-As reviewer 3 points out, the reference about SWAPI does not include
-an URL.  It is available at http://deian.net/swapi.pdf and currently
-not indexed by search engines because the paper is being anonymously
-submitted.  We apologize for the mistake.

### 2014-04-25 paper/rebuttal.txt
References for external effects and examples on JPmail, Paragon, and JSFlow

@@
 
-The reviewers are concerned that our treatment of external effects
-makes the work incomplete. We remark that like other IFC systems [A
-XXXX Z], external effects can be handled by internalizing them into
-the IFC language. In practice and as in the XMLHttpRequest (as used in
-SWAPI) case this amounts to wrapping the "native" unsafe code. While
-we can extend the language with a general external effect primitive
-(e.g., 'out') we do not think this add much value, formally or
-practically. Finally, and most importantly, the treatment of external
-effects is very much application specific. For instance, the HTTP
-client in SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both
-wrap the native code with label checks, but the actual label checks
-differ simply because of the different setting and attacker models:
-browser vs. server.  While important for (certain) practical
-applications, we believe that general treatment of such effects is an
-open problem and complementary to this work.
+The reviewers are concerned that our treatment of external effects makes the
+work incomplete. We remark that like other IFC systems, external effects can be
+handled by internalizing them (manually) into the IFC language. For instance,
+JPMail (a secure mail agent) [1] essentially re-implements the primitives with
+external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
+internalizes external effects by wrapping the corresponding primitives to be
+IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
+effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
+amounts to wrapping the "native" unsafe code. While we can extend the language
+with a general external effect primitive (e.g., 'out'), we do not think this add
+much value, formally or practically. This is because the treatment of external
+effects is very much application specific. For instance, the HTTP client in
+SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
+to make IFC-aware, but the actual label checks differ simply because of the
+different setting and attacker models: browser (client) vs. server.  While
+important for pushing IFC into practice, we believe that general treatment of
+external effects is an open problem and complementary to this work.
 
@@
 no secrets can be observed.
+
+References
+----------
+
+[1] Boniface Hicks, Kiyan Ahmadizadeh, and Patrick McDaniel. Understanding
+practical application development in security-typed languages. In 22nd Annual
+Computer Security Applications Conference (ACSAC), Miami, Fl, December 2006.
+
+[2] Paragon for Practical Programming with Information-Flow Control Niklas
+Broberg, Bart van Delft and David Sands Asian Symposium on Programming Languages
+and Systems (APLAS) 2013, Springer
+
+[3] http://www.cse.chalmers.se/research/group/paragon/?p=Case%20Studies

### 2014-04-25 paper/rebuttal.txt
Small edits
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Reorder, pending changes
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
+External effects
+----------------
+
+# is the system general?
+#
+# true, we can't handle external effects
+
+The reviewers are concerned that our treatment of external effects makes the
+work incomplete. We remark that like other IFC systems, external effects can be
+handled by internalizing them (manually) into the IFC language. For instance,
+JPMail (a secure mail agent) [1] essentially re-implements the primitives with
+external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
+internalizes external effects by wrapping the corresponding primitives to be
+IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
+effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
+amounts to wrapping the "native" unsafe code. While we can extend the language
+with a general external effect primitive (e.g., 'out'), we do not think this add
+much value, formally or practically. This is because the treatment of external
+effects is very much application specific. For instance, the HTTP client in
+SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
+to make IFC-aware, but the actual label checks differ simply because of the
+different setting and attacker models: browser (client) vs. server.  While
+important for pushing IFC into practice, we believe that general treatment of
+external effects is an open problem and complementary to this work.
+
 Generality and novelty of the system
 ------------------------------------
+
+# that doesn't make it not real
 
@@
 Section 6, we discussed how real-world languages can be constrained to
-achieve this.  Unfortunately due to space restrictions we left the
-discussion of the mapping to the formalism as informal discussion (doing
-this at the cost of section 8 seems natural).
+achieve this.  Unfortunately, due to space restrictions, we left the
+discussion of the mapping to the formalism as informal discussion.
 
@@
 the first reviewer.)
-
-External effects
-----------------
-
-The reviewers are concerned that our treatment of external effects makes the
-work incomplete. We remark that like other IFC systems, external effects can be
-handled by internalizing them (manually) into the IFC language. For instance,
-JPMail (a secure mail agent) [1] essentially re-implements the primitives with
-external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
-internalizes external effects by wrapping the corresponding primitives to be
-IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
-effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
-amounts to wrapping the "native" unsafe code. While we can extend the language
-with a general external effect primitive (e.g., 'out'), we do not think this add
-much value, formally or practically. This is because the treatment of external
-effects is very much application specific. For instance, the HTTP client in
-SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
-to make IFC-aware, but the actual label checks differ simply because of the
-different setting and attacker models: browser (client) vs. server.  While
-important for pushing IFC into practice, we believe that general treatment of
-external effects is an open problem and complementary to this work.
 

### 2014-04-25 paper/rebuttal.txt
Update extension rebuttal based on discussion.

@@
-External effects
-----------------
-
-# is the system general?
-#
-# true, we can't handle external effects
-
-The reviewers are concerned that our treatment of external effects makes the
-work incomplete. We remark that like other IFC systems, external effects can be
-handled by internalizing them (manually) into the IFC language. For instance,
-JPMail (a secure mail agent) [1] essentially re-implements the primitives with
-external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
-internalizes external effects by wrapping the corresponding primitives to be
-IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
-effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
-amounts to wrapping the "native" unsafe code. While we can extend the language
-with a general external effect primitive (e.g., 'out'), we do not think this add
-much value, formally or practically. This is because the treatment of external
-effects is very much application specific. For instance, the HTTP client in
-SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
-to make IFC-aware, but the actual label checks differ simply because of the
-different setting and attacker models: browser (client) vs. server.  While
-important for pushing IFC into practice, we believe that general treatment of
-external effects is an open problem and complementary to this work.
-
 Generality and novelty of the system
 ------------------------------------
-
-# that doesn't make it not real
 
@@
 
-The reviewers asked if we actually worked out the extensions to
-language. We chose to present the core ideas separate from extensions
-for simplicity and because the features largely depend on the
-embedding. For example, labeled MVars are natural to Haskell, but
-not JS. Nevertheless, these extensions have been formalized and are
-implemented in LIO and/or SWAPI. (The only extension common
-to both system systems are labeled values.) The main points on how
-to extend the system with such features follows from the discussion:
-they must be added to the IFC language and the no sharing
-"sandbox-local pointers" rule (of send) must be used.  For example,
-in the labeled references case we amend the IFC language state to
-contain a labeled reference store; these labeled references are
-distinct from the native references a target language might have and
-all access abides by IFC.  (For this reason, there is also no
-conflict with the approach of Matthews and Findler as brought up by
-the first reviewer.)
+Reviewer 1 asks about the extension section, and whether we actually
+worked out these ideas or not. We chose to present the core ideas
+separately from extensions for simplicity. However, the IFC language
+extensions described in Section 6 have been formally worked out, and
+are also part of the JavaScript or Haskell implementation, or both.
+W.r.t. the comment about labeled references not being amenable to
+Matthews-Findler-style semantics, we note that labeled references
+are part of the IFC state and are distinct from the native references
+a target language might have. For this reason, there is no conflict
+with the approach of Matthews and Findler.
+
+External effects
+----------------
+
+The reviewers are concerned that our treatment of external effects makes the
+work incomplete. We remark that like other IFC systems, external effects can be
+handled by internalizing them (manually) into the IFC language. For instance,
+JPMail (a secure mail agent) [1] essentially re-implements the primitives with
+external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
+internalizes external effects by wrapping the corresponding primitives to be
+IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
+effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
+amounts to wrapping the "native" unsafe code. While we can extend the language
+with a general external effect primitive (e.g., 'out'), we do not think this add
+much value, formally or practically. This is because the treatment of external
+effects is very much application specific. For instance, the HTTP client in
+SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
+to make IFC-aware, but the actual label checks differ simply because of the
+different setting and attacker models: browser (client) vs. server.  While
+important for pushing IFC into practice, we believe that general treatment of
+external effects is an open problem and complementary to this work.
 

### 2014-04-25 paper/rebuttal.txt
Reorg
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
-Generality and novelty of the system
-------------------------------------
+Reviewer 2 asks whether or not our method actually scales in practice,
+pointing to our inability to deal with external effects as a mark
+against it.  It is true that dealing with external effects is important
+for pushing IFC into practice, and our work is not primarily concerned
+with addressing this issue.  However, this problem is endemic to all
+information flow control systems: for instance, JPMail [1] re-implements
+primitives with external effects in Jif; Paragon [2] internalizes
+external effects by wrapping the corresponding primitives to be
+IFC-aware [3]; JSFlow [25] manually wraps JavaScript primitives with
+external effects.  This is not to say that the systems we have
+implemented do not deal with external effects: e.g. XMLHttpRequest as
+used in SWAPI essential wraps the "native" unsafe code. While we could
+have formally modeled these effects with an external effect primitive
+(e.g., 'out'), we do not think this add much value, formally or
+practically. This is because the treatment of external effects is very
+much application specific.
 
-A reviewer asked if our system really applies to real-world languages,
-pointing to our inability to deal with external effects.  It is true
-that our framework assumes that the target language must not have
-external effects.  However, this is not an unreasonable constraint: in
-Section 6, we discussed how real-world languages can be constrained to
-achieve this.  Unfortunately, due to space restrictions, we left the
-discussion of the mapping to the formalism as informal discussion.
+Thus, the generality of our system does not come from a treatment of
+external effects; rather, assuming that external effects are taken care
+of (Section 6), it comes from our ability to accomodate arbitrarily
+complex internal semantics.  For example, our work is directly
+applicable to "vanilla" JS (EcmaScript), which does not have any
+external effects.  As opposed to existing IFC systems [25] which incur
+tremendous overhead, we show that you can build an efficient,
+non-intrusive IFC system for JavaScript, or any other language which can
+be isolated.
 
-We do not claim that our work is general enough to handle languages
-where effects cannot be tamed (we will emphasize this on revision).
-Yet some languages can be tamed (as we discuss) and others don't even
-have external effects.  For example, our work is directly applicable
-to "vanilla" JS (EcmaScript), which does not have any external effects
--- indeed, under one lens, one can see our work as presenting an
-alternative (to [25]) coarse-grained IFC system for JS.  Indeed the
-motivation behind this work was to address the question of how to
-build an efficient, non-intrusive IFC system for JS.
+# about shoehorning
 
@@
 with the approach of Matthews and Findler.
-
-External effects
-----------------
-
-The reviewers are concerned that our treatment of external effects makes the
-work incomplete. We remark that like other IFC systems, external effects can be
-handled by internalizing them (manually) into the IFC language. For instance,
-JPMail (a secure mail agent) [1] essentially re-implements the primitives with
-external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
-internalizes external effects by wrapping the corresponding primitives to be
-IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
-effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
-amounts to wrapping the "native" unsafe code. While we can extend the language
-with a general external effect primitive (e.g., 'out'), we do not think this add
-much value, formally or practically. This is because the treatment of external
-effects is very much application specific. For instance, the HTTP client in
-SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
-to make IFC-aware, but the actual label checks differ simply because of the
-different setting and attacker models: browser (client) vs. server.  While
-important for pushing IFC into practice, we believe that general treatment of
-external effects is an open problem and complementary to this work.
 

### 2014-04-25 paper/rebuttal.txt
Fix up
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-# about shoehorning
+It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
+"unified framework".  While our language uses ideas from LIO and SWAPI,
+we note that the current (and at the time of the writing) versions of
+these systems coevolved with the concepts in the paper.  For instance,
+in LIO [53] (and Breeze [28]) exceptions were originally treated in a
+rather complex fashion. As we discuss in the paper, when you consider
+exceptions as part of the internal semantics of the language, the
+appropriate semantics for exceptions becomes trivial.  In fact, LIO was
+modified to adopt this new approach.
 
-Similarly, there was a comment that this work simply shoe-horned SWAPI
-and LIO into a "unified framework".  While our language uses ideas from
-LIO and SWAPI, we note that the current (and at the time of the writing)
-versions of these systems are using the concepts of this paper. It is
-not the case that "the framework didn't come first". For instance, in
-LIO [53] (and Breeze [28]) exceptions were originally treated in a rather
-complex fashion; as we discuss in the paper, exceptions are internal
-effects and thus the security concern becomes trivial; LIO was modified to
-adopt this new approach.
-
+# I haven't fixed this
 As for the first reviewer's concern that the IFC system presented is

### 2014-04-25 paper/rebuttal.txt
Smallish updates to first three paragraphs.

@@
 implemented do not deal with external effects: e.g. XMLHttpRequest as
-used in SWAPI essential wraps the "native" unsafe code. While we could
-have formally modeled these effects with an external effect primitive
-(e.g., 'out'), we do not think this add much value, formally or
-practically. This is because the treatment of external effects is very
-much application specific.
+used in SWAPI essential wraps the "native" unsafe code. However, the treatment
+of external effects is very much application specific, and finding a
+general solution is an open problem.
 
@@
 external effects; rather, assuming that external effects are taken care
-of (Section 6), it comes from our ability to accomodate arbitrarily
+of (Section 6), it comes from our ability to accommodate arbitrarily
 complex internal semantics.  For example, our work is directly
-applicable to "vanilla" JS (EcmaScript), which does not have any
-external effects.  As opposed to existing IFC systems [25] which incur
+applicable to "vanilla" JavaScript (ECMAScript), which does not have any
+external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
 tremendous overhead, we show that you can build an efficient,
@@
 "unified framework".  While our language uses ideas from LIO and SWAPI,
-we note that the current (and at the time of the writing) versions of
+we note that the current versions of
 these systems coevolved with the concepts in the paper.  For instance,
@@
 rather complex fashion. As we discuss in the paper, when you consider
-exceptions as part of the internal semantics of the language, the
-appropriate semantics for exceptions becomes trivial.  In fact, LIO was
-modified to adopt this new approach.
+exceptions as part of the internal semantics of the target language, the
+appropriate semantics for exceptions fall out naturally in our framework.
+In fact, LIO was modified to adopt this new, simpler approach.
 

### 2014-04-25 paper/rebuttal.txt
rename references.

@@
 with addressing this issue.  However, this problem is endemic to all
-information flow control systems: for instance, JPMail [1] re-implements
-primitives with external effects in Jif; Paragon [2] internalizes
+information flow control systems: for instance, JPMail [A] re-implements
+primitives with external effects in Jif; Paragon [B] internalizes
 external effects by wrapping the corresponding primitives to be
-IFC-aware [3]; JSFlow [25] manually wraps JavaScript primitives with
+IFC-aware [C]; JSFlow [25] manually wraps JavaScript primitives with
 external effects.  This is not to say that the systems we have
@@
 
-[1] Boniface Hicks, Kiyan Ahmadizadeh, and Patrick McDaniel. Understanding
+[A] Boniface Hicks, Kiyan Ahmadizadeh, and Patrick McDaniel. Understanding
 practical application development in security-typed languages. In 22nd Annual
@@
 
-[2] Paragon for Practical Programming with Information-Flow Control Niklas
+[B] Paragon for Practical Programming with Information-Flow Control Niklas
 Broberg, Bart van Delft and David Sands Asian Symposium on Programming Languages
@@
 
-[3] http://www.cse.chalmers.se/research/group/paragon/?p=Case%20Studies
+[C] http://www.cse.chalmers.se/research/group/paragon/?p=Case%20Studies

### 2014-04-26 paper/rebuttal.txt
Done
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-# I haven't fixed this
-As for the first reviewer's concern that the IFC system presented is
-simply a rehash of prior work, we claim the approach of dealing with
-internal effects and our asynchronous communication primitives is
-novel. To our knowledge this is the first language-based dynamic IFC
-system to use such asynchronous primitives and work on both concurrent
-and sequential schedulers. (While simple, the checks performed by our
-asynchronous communication primitives imply a more flexible
-system---synchronous primitives effectively impose that the end-points
-have the same label.) Moreover, we believe that our formalization
-serves as a stepping stone for formal reasoning about IFC OS work.
+Reviewer 1 was concerned that many aspects of our IFC system were simply
+rehashes of prior work.  We believe that our core IFC language's support
+for both concurrent and sequential scheduling through asynchronous
+communication primitives is novel.  (Notice that a primitive which may
+block cannot work in a sequential setting).  This is an old idea from IFC
+OS work, but formally reasoning about this idea is new.
 
-Extensions
-----------
-
-Reviewer 1 asks about the extension section, and whether we actually
-worked out these ideas or not. We chose to present the core ideas
-separately from extensions for simplicity. However, the IFC language
-extensions described in Section 6 have been formally worked out, and
-are also part of the JavaScript or Haskell implementation, or both.
-W.r.t. the comment about labeled references not being amenable to
-Matthews-Findler-style semantics, we note that labeled references
-are part of the IFC state and are distinct from the native references
-a target language might have. For this reason, there is no conflict
-with the approach of Matthews and Findler.
+Reviewer 1 also asks whether or not the ideas in the extension section
+were actually worked out.  The IFC language features and external effect
+systems mentioned have been implemented for Haskell and JavaScript, and,
+in the case of LIO, have had properties formally proven, while the
+scheduling policies and type safety extensions are more speculative.
+The treatment of mutable references was explicitly called out as
+unworkable: we would like to clarify an important distinction between
+mutable references in the IFC language and mutable references internally
+supported in the target language.  The naive addition of IFC references
+results in two *different* types of references: this is a feature,
+not a bug, since it avoids the need of adding expensive checks to
+existing references which, in all likelihood, are local to an IFC thread.
 

### 2014-04-26 paper/rebuttal.txt
rebuttal
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 supported in the target language.  The naive addition of IFC references
-results in two *different* types of references: this is a feature,
-not a bug, since it avoids the need of adding expensive checks to
-existing references which, in all likelihood, are local to an IFC thread.
+results in two *different* types of references: this is a feature, not a
+bug, since it absolves us of the responsibility of integrating the two
+semantics.  Furthermore, existing code using old references does not
+usually need to communicate over IFC boundaries, so code being written
+to take advantage of the new IFC support can be written to explicitly use
+IFC references.  This approach of adding features to the core IFC
+calculus extends to our other proposed extensions, and their security
+proofs are generalizable to our setting in the same way.
 

### 2014-04-26 paper/rebuttal.txt
minor

@@
 pointing to our inability to deal with external effects as a mark
-against it.  It is true that dealing with external effects is important
-for pushing IFC into practice, and our work is not primarily concerned
-with addressing this issue.  However, this problem is endemic to all
-information flow control systems: for instance, JPMail [A] re-implements
-primitives with external effects in Jif; Paragon [B] internalizes
-external effects by wrapping the corresponding primitives to be
-IFC-aware [C]; JSFlow [25] manually wraps JavaScript primitives with
-external effects.  This is not to say that the systems we have
-implemented do not deal with external effects: e.g. XMLHttpRequest as
-used in SWAPI essential wraps the "native" unsafe code. However, the treatment
-of external effects is very much application specific, and finding a
-general solution is an open problem.
+against it.  It is true that dealing with external effects is
+important for pushing IFC into practice, and our work is not primarily
+concerned with addressing this issue.  However, this problem is
+endemic to all information flow control systems: for instance, JPMail
+[A] re-implements primitives with external effects in Jif; Paragon [B]
+internalizes external effects by wrapping the corresponding primitives
+to be IFC-aware [C]; JSFlow [25.26] manually wraps JavaScript
+primitives with external effects.  This is not to say that the systems
+we have implemented do not deal with external effects: e.g.
+XMLHttpRequest as used in SWAPI essential wraps the "native" unsafe
+code. However, the treatment of external effects is very much
+application specific, and finding a general solution is an open
+problem.
 
 Thus, the generality of our system does not come from a treatment of
-external effects; rather, assuming that external effects are taken care
-of (Section 6), it comes from our ability to accommodate arbitrarily
-complex internal semantics.  For example, our work is directly
-applicable to "vanilla" JavaScript (ECMAScript), which does not have any
-external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
-tremendous overhead, we show that you can build an efficient,
-non-intrusive IFC system for JavaScript, or any other language which can
-be isolated.
+external effects; rather, assuming that external effects are taken
+care of (Section 6), it comes from our ability to accommodate
+arbitrarily complex internal semantics.  For example, our work is
+directly applicable to "vanilla" JavaScript (ECMAScript), which does
+not have any external effects.  As opposed to existing IFC systems
+(e.g., [25]) which incur tremendous overhead, we show that you can
+build an efficient, non-intrusive IFC system for JavaScript, or any
+other language which can be isolated.
 
-It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
-"unified framework".  While our language uses ideas from LIO and SWAPI,
-we note that the current versions of
-these systems coevolved with the concepts in the paper.  For instance,
-in LIO [53] (and Breeze [28]) exceptions were originally treated in a
-rather complex fashion. As we discuss in the paper, when you consider
-exceptions as part of the internal semantics of the target language, the
-appropriate semantics for exceptions fall out naturally in our framework.
-In fact, LIO was modified to adopt this new, simpler approach.
+It's worth stating that we did not simply shoe-horn SWAPI and LIO into
+a "unified framework".  While our language uses ideas from LIO and
+SWAPI, we note that the current versions of these systems coevolved
+with the concepts in the paper.  For instance, in LIO [53] (and Breeze
+[28]) exceptions were originally treated in a rather complex fashion.
+As we discuss in the paper, when you consider exceptions as part of
+the internal semantics of the target language, the appropriate
+semantics for exceptions fall out naturally in our framework.  In
+fact, LIO was modified to adopt this new, simpler approach.
 
-Reviewer 1 was concerned that many aspects of our IFC system were simply
-rehashes of prior work.  We believe that our core IFC language's support
-for both concurrent and sequential scheduling through asynchronous
-communication primitives is novel.  (Notice that a primitive which may
-block cannot work in a sequential setting).  This is an old idea from IFC
-OS work, but formally reasoning about this idea is new.
+Reviewer 1 was concerned that many aspects of our IFC system were
+simply rehashes of prior work.  We believe that our core IFC
+language's support for both concurrent and sequential scheduling
+through asynchronous communication primitives is novel.  (Notice that
+a primitive which may block cannot work in a sequential setting).
+This is an old idea from IFC OS work, but formally reasoning about
+this idea is new.
 
 Reviewer 1 also asks whether or not the ideas in the extension section
-were actually worked out.  The IFC language features and external effect
-systems mentioned have been implemented for Haskell and JavaScript, and,
-in the case of LIO, have had properties formally proven, while the
-scheduling policies and type safety extensions are more speculative.
-The treatment of mutable references was explicitly called out as
-unworkable: we would like to clarify an important distinction between
-mutable references in the IFC language and mutable references internally
-supported in the target language.  The naive addition of IFC references
-results in two *different* types of references: this is a feature, not a
-bug, since it absolves us of the responsibility of integrating the two
-semantics.  Furthermore, existing code using old references does not
-usually need to communicate over IFC boundaries, so code being written
-to take advantage of the new IFC support can be written to explicitly use
-IFC references.  This approach of adding features to the core IFC
-calculus extends to our other proposed extensions, and their security
-proofs are generalizable to our setting in the same way.
+were actually worked out.  The IFC language features and external
+effect systems mentioned have been implemented for Haskell and
+JavaScript, and, in the case of LIO, have had properties formally
+proven, while the scheduling policies and type safety extensions are
+more speculative.  The treatment of mutable references was explicitly
+called out as unworkable: we would like to clarify an important
+distinction between mutable references in the IFC language and mutable
+references internally supported in the target language.  The naive
+addition of IFC references results in two *different* types of
+references: this is a feature, not a bug, since it absolves us of the
+responsibility of integrating the two semantics.  Furthermore,
+existing code using old references does not usually need to
+communicate over IFC boundaries, so code being written to take
+advantage of the new IFC support can be written to explicitly use IFC
+references.  This approach of adding features to the core IFC calculus
+extends to our other proposed extensions, and their security proofs
+are generalizable to our setting in the same way.
 

### 2014-04-26 paper/rebuttal.txt
Last minor changes.

--- 2014-04-26 paper/rebuttal.txt
@@
+We would like to thank all reviewers for their feedback and suggestions.
+We will first reply to high-level comments and then reply to specific
+questions in the reviews.
+
 Reviewer 2 asks whether or not our method actually scales in practice,
 pointing to our inability to deal with external effects as a mark
-against it.  It is true that dealing with external effects is important
-for pushing IFC into practice, and our work is not primarily concerned
-with addressing this issue.  However, this problem is endemic to all
-information flow control systems: for instance, JPMail [A] re-implements
-primitives with external effects in Jif; Paragon [B] internalizes
-external effects by wrapping the corresponding primitives to be
-IFC-aware [C]; JSFlow [25] manually wraps JavaScript primitives with
-external effects.  This is not to say that the systems we have
-implemented do not deal with external effects: e.g. XMLHttpRequest as
-used in SWAPI essential wraps the "native" unsafe code. However, the treatment
-of external effects is very much application specific, and finding a
-general solution is an open problem.
+against it.  It is true that dealing with external effects is
+important for pushing IFC into practice, and our work is not primarily
+concerned with addressing this issue.  However, this problem is
+endemic to all information flow control systems: for instance, JPMail [A]
+re-implements primitives with external effects in Jif; Paragon [B]
+internalizes external effects by wrapping the corresponding primitives
+to be IFC-aware [C]; JSFlow [25,26] manually wraps JavaScript
+primitives with external effects.  This is not to say that the systems
+we have implemented do not deal with external effects: e.g.
+XMLHttpRequest as used in SWAPI essential wraps the "native" unsafe
+code. However, the treatment of external effects is very much
+application specific, and finding a general solution is an open
+problem.
 
 Thus, the generality of our system does not come from a treatment of
-external effects; rather, assuming that external effects are taken care
-of (Section 6), it comes from our ability to accommodate arbitrarily
-complex internal semantics.  For example, our work is directly
-applicable to "vanilla" JavaScript (ECMAScript), which does not have any
-external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
-tremendous overhead, we show that you can build an efficient,
-non-intrusive IFC system for JavaScript, or any other language which can
-be isolated.
+external effects; rather, assuming that external effects are taken
+care of (Section 6), it comes from our ability to accommodate
+arbitrarily complex internal semantics.  For example, our work is
+directly applicable to "vanilla" JavaScript (ECMAScript), which does
+not have any external effects.  As opposed to existing IFC systems
+(e.g., [25]) which incur tremendous overhead, we show that you can
+build an efficient, non-intrusive IFC system for JavaScript, or any
+other language which can be isolated.
 
-It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
-"unified framework".  While our language uses ideas from LIO and SWAPI,
-we note that the current versions of
-these systems coevolved with the concepts in the paper.  For instance,
-in LIO [53] (and Breeze [28]) exceptions were originally treated in a
-rather complex fashion. As we discuss in the paper, when you consider
-exceptions as part of the internal semantics of the target language, the
-appropriate semantics for exceptions fall out naturally in our framework.
-In fact, LIO was modified to adopt this new, simpler approach.
+It's worth stating that we did not simply shoe-horn SWAPI and LIO into
+a "unified framework".  While our language uses ideas from LIO and
+SWAPI, we note that the current versions of these systems coevolved
+with the concepts in the paper.  For instance, in LIO [53] (and Breeze
+[28]) exceptions were originally treated in a rather complex fashion.
+As we discuss in the paper, when you consider exceptions as part of
+the internal semantics of the target language, the appropriate
+semantics for exceptions fall out naturally in our framework.  In
+fact, LIO was modified to adopt this new, simpler approach.
 
-Reviewer 1 was concerned that many aspects of our IFC system were simply
-rehashes of prior work.  We believe that our core IFC language's support
-for both concurrent and sequential scheduling through asynchronous
-communication primitives is novel.  (Notice that a primitive which may
-block cannot work in a sequential setting).  This is an old idea from IFC
-OS work, but formally reasoning about this idea is new.
+Reviewer 1 was concerned that many aspects of our IFC system were
+simply rehashes of prior work.  We believe that our core IFC
+language's support for both concurrent and sequential scheduling
+through asynchronous communication primitives is novel.  (Notice that
+a primitive which may block cannot work in a sequential setting).
+This is an old idea from IFC OS work, but formally reasoning about
+this idea is new.
 
 Reviewer 1 also asks whether or not the ideas in the extension section
-were actually worked out.  The IFC language features and external effect
-systems mentioned have been implemented for Haskell and JavaScript, and,
-in the case of LIO, have had properties formally proven, while the
-scheduling policies and type safety extensions are more speculative.
-The treatment of mutable references was explicitly called out as
-unworkable: we would like to clarify an important distinction between
-mutable references in the IFC language and mutable references internally
-supported in the target language.  The naive addition of IFC references
-results in two *different* types of references: this is a feature, not a
-bug, since it absolves us of the responsibility of integrating the two
-semantics.  Furthermore, existing code using old references does not
-usually need to communicate over IFC boundaries, so code being written
-to take advantage of the new IFC support can be written to explicitly use
-IFC references.  This approach of adding features to the core IFC
-calculus extends to our other proposed extensions, and their security
-proofs are generalizable to our setting in the same way.
+were actually worked out.  The IFC language features and external
+effect systems mentioned have been implemented for Haskell and
+JavaScript, and, in the case of LIO, have had properties formally
+proven, while the scheduling policies and type safety extensions are
+more speculative.  The treatment of mutable references was explicitly
+called out as unworkable: we would like to clarify an important
+distinction between mutable references in the IFC language and mutable
+references internally supported in the target language.  The naive
+addition of IFC references results in two *different* types of
+references: this is a feature, not a bug, since it absolves us of the
+responsibility of integrating the two semantics.  Furthermore,
+existing code using old references does not usually need to
+communicate over IFC boundaries, so code being written to take
+advantage of the new IFC support can be written to explicitly use IFC
+references.  This approach of adding features to the core IFC calculus
+extends to our other proposed extensions, and their security proofs
+are generalizable to our setting in the same way.
 
-Other questions
----------------
+Specific questions
+------------------
 

### 2014-05-09 paper/appendix.tex
Start formalizing some of the extensions.

@@
 \appendix
+
+\section{Formal Extensions}
+
+\begin{figure}
+  %{
+  %format .->  = "\overset{\alpha}{\hookrightarrow}"
+  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
+  \begin{code}
+    iv  ::= cdots | Labeled il ie
+    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
+    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
+  \end{code}
+
+  \begin{mathpar}
+    \inferrule[I-label]
+    {|
+      il canFlowTo il'
+    |}
+    {|
+      niconf iS id il (label il' ie)
+      ->
+      niconf iS id il (Labeled il' ie)
+    |}
+    \and
+    \inferrule[I-unlabel]
+    {|
+      il''=il lub il'
+    |}
+    {|
+      niconf iS id il (unlabel (Labeled il' ie))
+      ->
+      niconf iS id (il'') ie
+    |}
+    \and
+    \inferrule[I-labelOf]
+    {|
+    |}
+    {|
+      niconf iS id il (labelOf (Labeled il' ie))
+      ->
+      niconf iS id il (il')
+    |}
+  \end{mathpar}
+  \caption{}
+  \label{fig:labeled-vals}
+  %}
+\end{figure}
+
+\begin{figure}
+  %{
+  %format .->  = "\overset{\alpha}{\hookrightarrow}"
+  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
+  \begin{code}
+    iv  ::= cdots | ial
+    ie  ::= cdots | new ie ie | read ie | write ie ie
+    iE  ::= cdots | new iE ie | new il iE | read E
+                  | write iE ie | write ial iE
+  \end{code}
+
+  \begin{mathpar}
+    \inferrule[I-new]
+    {
+      |il canFlowTo il'| \\
+      |fresh ia|
+    }
+    {|
+      niconf iS id il (new il' iv)
+      ->
+      niconf iS id il (iall il')
+      |}
+    \and
+    \inferrule[I-read]
+    {|
+      il canFlowTo il'
+      |}
+    {|
+      niconf iS id il (label il' ie)
+      ->
+      niconf iS id il (Labeled il' ie)
+      |}
+    \and
+    \inferrule[I-write]
+    {|
+      il canFlowTo il'
+      |}
+    {|
+      niconf iS id il (label il' ie)
+      ->
+      niconf iS id il (Labeled il' ie)
+      |}
+    \and
+    \inferrule[I-labelOf2]
+    {|
+      il canFlowTo il'
+      |}
+    {|
+      niconf iS id il (label il' ie)
+      ->
+      niconf iS id il (Labeled il' ie)
+      |}
+  \end{mathpar}
+  \caption{}
+  \label{fig:labeled-refs}
+  %}
+\end{figure}
+
 \section{Full Non-Interference Proof}

### 2014-05-09 paper/concrete.tex
Fix notation issues with fresh.

@@
       |itnew = oneheapfullconf id' il (TI ie)|\\
-      |fresh (id')|
+      |fresh id'|
     }

### 2014-05-09 paper/retrofit.tex
Fix notation issues with fresh.

@@
 \inferrule[T-ref]
-{ | ap fresh ta | }
+{ | fresh ta | }
 {| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
@@
 |}
-%{|fresh (id')|}
 
@@
 |itnew = fullconf id' il tS' ie|\\
-|ap fresh id'|
+|fresh id'|
 }

### 2014-05-11 paper/appendix.tex
More on extention formalism.

@@
   \end{code}
-
   \begin{mathpar}
@@
       |il canFlowTo il'| \\
-      |fresh ia|
+      |fresh ia|\\
+      |iS'= bracket iS (mapsto (iall il') iv)|
     }
@@
       ->
-      niconf iS id il (iall il')
+      niconf iS' id il (iall il')
       |}
@@
     \inferrule[I-read]
+    {}
     {|
-      il canFlowTo il'
-      |}
-    {|
-      niconf iS id il (label il' ie)
+      niconf iS id il (read ial')
       ->
-      niconf iS id il (Labeled il' ie)
+      niconf iS id (il lub il') (readState iS (iall il'))
       |}
@@
     \inferrule[I-write]
+    {
+      |il canFlowTo il'|\\
+      |iS'= bracket iS (mapsto (iall il') iv)|
+    }
     {|
-      il canFlowTo il'
-      |}
-    {|
-      niconf iS id il (label il' ie)
+      niconf iS id il (write ial' iv)
       ->
-      niconf iS id il (Labeled il' ie)
+      niconf iS' id il (unit)
       |}
@@
     \inferrule[I-labelOf2]
+    {}
     {|
-      il canFlowTo il'
-      |}
-    {|
-      niconf iS id il (label il' ie)
+      niconf iS id il (labelOf ial')
       ->
-      niconf iS id il (Labeled il' ie)
+      niconf iS id il (il')
       |}
@@
   %}
+\end{figure}
+
+\begin{figure}
+  \begin{align*}
+  &|erase il (iconf iS its) =
+  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
+  &|fullconf id il' tS ie| \begin{cases}
+  |bullet| & |il' cantFlowTo il| \\
+  |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
+  \end{cases} \\
+  &|erase il emptyset = emptyset|\\
+  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
+  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
+  & \text{the label of thread |id|} \\
+  |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
+  \end{cases} \\
+  &|erase il Q = filter il Q|\\
+  &|erase il v = v|
+  \end{align*}
+  \caption{Erasure function for the full IFC language, with all extensions.
+    In all not specified (including target-language constructs),
+    |erasef il| is applied homomorphically.}
+  \label{fig:erasure2}
 \end{figure}

### 2014-05-11 paper/retrofit.tex
Improve notation.

@@
 |il canFlowTo il'|\\
-|iS(id') = Q|\\
+|readState iS (id') = Q|\\
 |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
@@
 {
-| (filter il (iS(id))) = io1 , ... , iok , (il', id', iv)|\\
+| (filter il (readState iS id)) = io1 , ... , iok , (il', id', iv)|\\
 | iS' = bracket iS (mapsto id (io1 , ... , iok))|\\
@@
 {
-| filter il (iS(id)) = nil|\\
+| filter il (readState iS (id)) = nil|\\
 | iS' = bracket iS (mapsto id nil)|

### 2014-05-11 paper/appendix.tex
Update erasure function for extentions.

@@
                   | write iE ie | write ial iE
+    iS  ::=  cdots | bracket iS (mapsto ial iv)
   \end{code}
@@
   \end{cases} \\
+  &|erase il (Labeled il' ie)|= \begin{cases}
+  |Labeled il' bullet| & |il' cantFlowTo il| \\
+  |Labeled il' ie| & \text{otherwise}
+  \end{cases} \\
   &|erase il emptyset = emptyset|\\
@@
   \end{cases} \\
-  &|erase il Q = filter il Q|\\
-  &|erase il v = v|
+  &|erase il (bracket iS (mapsto (iall il') iv)) =| \begin{cases}
+  |bracket (erase il iS) (mapsto (iall il') bullet)| & \text{|il' cantFlowTo il|}\\
+  |bracket (erase il iS) (mapsto (iall il') (erase il iv))| & \text{otherwise}
+  \end{cases} \\
+  &|erase il Q = filter il Q|
   \end{align*}
   \caption{Erasure function for the full IFC language, with all extensions.
-    In all not specified (including target-language constructs),
-    |erasef il| is applied homomorphically.}
+    In all cases not specified (including target-language constructs),
+    |erasef il| is applied homomorphically.
+    This definition replaces the one from Figure~\ref{fig:erasure}, which
+    is for the IFC language without extensions.}
   \label{fig:erasure2}

### 2014-07-05 paper/formal.tex
Remove invalid case in erasure function.
minor bugs and nits

@@
 usually by rewriting (parts of) configurations that are more sensitive
-than |l| to a new syntactic construct |bullet|.  We can the define
+than |l| to a new syntactic construct |bullet|.  We define
 an information flow control language as follows:
@@
   iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
-  &|fullconf id il' tS ie| \begin{cases}
+  &|erase il (fullconf id il' tS ie) =| \begin{cases}
     |bullet| & |il' cantFlowTo il| \\
@@
   \end{cases} \\
-  &|erase il Q = filter il Q|\\
-  &|erase il v = v|
+  &|erase il Q = filter il Q|
 \end{align*}

### 2014-07-05 paper/retrofit.tex
minor bugs and nits

@@
 require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
-with the partial order |canFlowTo|, join |lub|, and meet |glb|.
+with the partial order $\sqsubseteq$, join |lub|, and meet |glb|.
 In this paper, we simply represent labels with the metavariable
@@
     \item Operations for inspecting (\textbf{getLabel}) and modifying
-    (\textbf{setLabel}) the current label of the task (a task can only increase its label),
+    (\textbf{setLabel}) the current label of the task (a task can only increase its label).
     \item Operations for non-blocking inter-task communication (\textbf{send}
     and \textbf{recv}), which interact with the global store of per-task
-    message queues |iS|, and
+    message queues |iS|.
 %%     Labels are associated with message at the time of
@@
     whereas in a
-    sequential setting, it more closely resembles the LIO's
-    |toLabeled|~\cite{lio}, and the Breeze
-    bracket~\cite{Hritcu:2013:YIB:2497621.2498098}.
+    sequential setting, it more closely resembles the LIO
+    |toLabeled|~\cite{lio} and Breeze
+    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.
 \end{itemize}
@@
 \begin{itemize}
-    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.~\cite{Matthews:2007:OSM:1190216.1190220}
+    \item We extend the values, expressions and evaluation contexts of
+      both languages to allow for embeddings terms in one language to
+      be embedded in the other, as
+      in~\cite{Matthews:2007:OSM:1190216.1190220}.
     %
@@
 %
-Instead, as our example |roundrobinf| scheduler shows, such tasks should simply
-be removed from the task list.
+Instead, as our example round-robin (|roundrobinf|) scheduler shows,
+such tasks should simply be removed from the task list.
 
@@
 \begin{align*}
-    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))|\\
+    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
     & |in TI (send (IT i) getLabel (IT (ref true)))|
@@
     & |toLabeled l te @= | \\
-    & |tab let i = taskId; | \\
-    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+    & |tab let i = taskId in| \\
+%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
@@
 %
-Just like in both LIO and Breeze, however, only when calling |recv| on such messages
+Just like in LIO and Breeze, however, only when calling |recv| on such messages
 will the exception be propagated.
@@
 receiving sensitive message, regardless of their content.
+\Red{TODO: note that if the target language allows inspecting if
+  result is exception we can implement Breeze's NAV (vs. just
+propagating)}

### 2014-07-05 paper/formal.tex
nit

@@
     |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
-    if |erase l c = erase il c'|.
+    if |erase l c = erase l c'|.
 \end{definition}
@@
 For example, |specLang alpha targetLang| with a scheduler that inspects a
-sensitive tasks current state when deciding which task to schedule next
+sensitive task's current state when deciding which task to schedule next
 will in general break non-interference~\cite{russo2006securing,BartheRRS07}.

### 2014-07-05 paper/concrete.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 the semantics which preserve non-interference.
-The intention of our single heap implementation was to be more efficient
-by using one global heap, but \emph{conceptually maintain isolation between
-task by not allowing sharing of references between them}.
+The intention of our single heap implementation is to permit
+efficient execution while \emph{conceptually maintaining isolation between
+tasks} (by not allowing sharing of references between them).
 This intuition of having a different (potentially more efficient)
@@
 Section~\ref{sec:extensions:types}.
-In a dynamically type languages such as |targetLangML|, we might
+In dynamically typed languages such as |targetLangML|, we might
 restrict the transition for |sandbox| and |send| to only allow expressions
@@
 the interesting parts of their definition,
-and leave the straight-forward proof that they
+and leave out the straight-forward proof that they
 actually provide an isomorphism.

### 2014-07-05 paper/extensions.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-Thus, an extension that allows supports such fine-grained explicitly
+Thus, an extension that supports such fine-grained explicitly
 labeled values is essential.
@@
 \begin{itemize}
-    \item In Matthews and Findlers original
+    \item In Matthews and Findler's original
         paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was

### 2014-07-05 paper/formal.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 usually by rewriting (parts of) configurations that are more sensitive
-than |l| to a new syntactic construct |bullet|.  We define
+than |l| to a new syntactic construct |bullet|.  We can then define
 an information flow control language as follows:
@@
     |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
-    if |erase l c = erase l c'|.
+    if |erase l c = erase il c'|.
 \end{definition}
@@
 \begin{code}
-ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
+ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS2 ie
 ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie

### 2014-07-05 paper/proofs.tex
conditionally build extended version
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
-  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+  We prove the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
   The base case for derivations
   of length 0 is trivial, allowing
-  us to simple chose $|ic2'=ic2|$.  In the step case,
+  us to simply chose $|ic2'=ic2|$.  In the step case,
   we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
@@
   For space reasons, we only sketch the structure of the proof here.
-  We refer the interested reader to the Appendix for a full proof.
+  We refer the interested reader to the Appendix
+  \ifextended
+  \else
+  of the extended version (which we provide at
+  \url{http://www.scs.stanford.edu/~deian/ifc-inside_extended.pdf})
+  \fi
+  for a full proof.
   The proof distinguishes two cases:

### 2014-07-05 paper/retrofit.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-05-11 paper/retrofit.tex
@@
 mutable references and general recursion. |FV(te)| returns the set of free
-variables in express |te|.}
+variables in expression |te|.}
 \label{fig:ml}
@@
 %
-As an example, taking |targetLangML| as the target languge, we can now define a
+As an example, taking |targetLangML| as the target language, we can now define a
 blocking receive (inefficiently) in terms of the asynchronous |recv| as series

### 2014-07-05 paper/real.tex
capitalize titles.
Spelling
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
-\section{Real world languages}
+\section{Real World Languages}
 \label{sec:real}
@@
 %
-Creating a new task with the |sandbox| syscall is corresponds to
+Creating a new task with the |sandbox| syscall corresponds to
 \emph{forking} a process.  Here, page tables limit what memory
@@
  Section~\ref{sec:concrete}.  However, since the heap separation is
- provided by the browser the browser, we do not discuss this further.
+ provided by the browser, we do not discuss this further.
  The interested reader is referred to~\cite{swapi} for more details.
@@
 (iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
-to the label of a task (worker or browsing context).  Accomodating these
+to the label of a task (worker or browsing context).  Accommodating these
 features lies outside the purview of our formalism.

### 2014-07-06 paper/appendix.tex
Some changes towards updating the proof.

@@
 for Lemma~\ref{lemma:rr-tsni-general}.  Here we give it with full
-details.
+details, and first state and proof another lemma that will be used in that
+proof.
+
+%\begin{lemma}
+%  For any task lists |its|, |its'|, and tasks |it|, |it'| we have that
+%  if
+%  \begin{enumerate}
+%    \item |iconf iS (it1, its) .-> iconf iS' (its')|
+%    \item $|erase il it1|=|bullet|$
+%  \end{enumerate}
+%  then
+%\end{lemma}
+
+\begin{lemma}
+  \label{lemma:high-not-blocking}
+  For any task |it|, task lists |its|, store |iS|, and label |il|, if
+  $|erase il it|=|bullet|$, then there exists a task list
+  |its'| and a store |iS'| such that
+  \[
+    |iconf iS (it, its)| |.->| |iconf iS' (its, its')|
+    \qquad
+    |erase il its'|=|nil|
+    \qquad
+    |erase il iS'|=|erase il iS|
+  \]
+\end{lemma}
+\begin{proof}
+  TODO (consideration of all rules that could be applied)
+\end{proof}
+
+%\begin{lemma}
+%  \label{lemma:erase-context}
+%  For any expressions |ie1|, |ie2|, |ie1'|, context |iE1| as well as
+%  label |il|, if
+%  \[ |ie1= iHole2 iE1 ie1'| \quad \land \quad |erase il ie1 = erase il ie2| \]
+%  then there exist |iE2|, |ie2'| such that
+%  \[ |ie2= iHole2 iE2 ie2'| \quad \land \quad
+%  |erase il ie1' = erase il ie2'|\neq|bullet| \]
+%  Similarly, for any
+%  expressions |ie1|, |ie2|, |te1'|, context |iE1| as well as
+%  label |il|, if
+%  \[ |ie1= tHole2 iE1 te1'| \quad \land \quad |erase il ie1 = erase il ie2| \]
+%  then there exist |iE2|, |te2'| such that
+%  \[ |ie2= tHole2 iE2 te2'| \quad \land \quad
+%  |erase il te1' = erase il te2'|\neq|bullet| \]
+%\end{lemma}
+%\begin{proof}
+%  TODO
+%\end{proof}
 
@@
   it could not take a step.  Thus, |ic1| is of the form
-  |iconf iS1 (it1, its1)|.  Consider two cases:
+  |iconf iS1 (it1, its1)|.
+  Furthermore, let |ic2| be |iconf iS2 its2|.
+  Consider two cases:
   \begin{itemize}
@@
     |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
-    To see that, note that the tasks |its1| in |ic1| are left in the
+    To show this, note that the tasks |its1| in |ic1| are left in the
     same order and unmodified (the scheduling policy only
@@
     Lets consider the possible changes to |iS1|:
-    Only three reduction interact with |iS1|,
+    Only five reduction interact with |iS1|,
     thus it suffices to consider these cases:
@@
       task |it1| can change, which gets erased.
+      \item[Case \textsc{I-new}] The newly allocated address has to be at a
+      label at least as high as |lcurr|, and will thus be erased.
+      \item[Case \textsc{I-write}] Only addresses with a label |il'| above
+      |lcurr| can be written, thus the change in |iS1| will get erased.
     \end{description}
-    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
+    This ensures that $|ic1'|\approx_{|il|}|ic2'|$, as well as
+    $|ic2| |.->|^* |ic2'|$ (in zero steps), as claimed.
     %    \alphacondition{We need all scheduling policies to not change the order
@@
     \item $|erase il it1|\neq|bullet|$.
-    Here, there must be a corresponding
-    task |it2| in |ic2|,
-    such that |it1=it2| (otherwise |ic1| and
-    |ic2| could not be |il|-equivalent).
-    However, |it2| might not be at the beginning of the task list yet, but
-    all tasks occurring before it must get erased by |erasef il|.
-    In |ic2|, we can first take some number of steps until |it2| moves
-    to the front of the list.
-    This is the case regardless of any additional side conditions $P$ on
-    rules, because for all of these tasks, it can either take an actual
-    step, or it gets dropped by \textsc{I-noStep} (which is always
-    possible, as there cannot be an additional side condition on this
-    rule).  All tasks that didn't get dropped are still at a label
-    that isn't below |il| and thus get erased.
+    By the definition of |erasef il|, the task list |its2|
+    in |ic2| must be of the
+    form |its2', it2, its2''| (for some task lists |its2'|, |its2''| and
+    some task |it2|)
+    where
+    \begin{align}
+    |erase il its2'| = |nil| \\
+    |erase il it2| = |erase il it1| \\
+    |erase il its2''| = |erase il its1|
+    \end{align}
+    (where |nil| is the empty list of tasks).
+    Now, intuitively we will first execute a number of steps to process
+    the tasks in |its2'| (execute them one step and move them to the back
+    of the task list, or drop them if they are done or stuck).  Then, the task
+    |it2| can take the same step as |it1|, which will result in a configuration
+    |ic2'|
+    with the desired properties.
+    More formally, we can proceed as follows:
 
-    %    \alphacondition{The scheduling policy must eventually let any task in
-    %      the task list evaluate.  In particular, it cannot get stuck when the
-    %      first task gets stuck, or keep executing a small number of tasks
-    %      exclusively forever (e.g. just execute the first task all the time
-    %      if it gets into an infinite loop).}
+    First, we can apply Lemma~\ref{lemma:high-not-blocking} continuously
+    for all the task in |its2'|,
+    until we reach a configuration |ic2''=iconf iS2' (it2, its2'', its2''')|
+    for some |its2'''| such
+    that |erase il its2''' = nil| and |erase il iS2| = |erase il iS2'|.
+    We note that |erase il ic1 = erase il ic2''| (by the definition of
+    |erasef il|).
 
-    Therefore, after |ic2| has potentially executed some number of steps
-    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
-    respectively, don't get erased and are thus equivalent.
-    The task |it2| can now take exactly the same step as |it1|;  this
-    is true even with arbitrary additional premises $P$ that follow
-    the condition in Definition~\ref{def:restricted}, since those
+    Now, the first task |it2| in |ic2''| is |il|-equivalent to the task |it1|.
+    This implies that the two tasks must have the same id, label and
+    can only differ in the expression or store if some subexpression
+    is of the form |Labeled il' ie|.  In this case, the expression |ie| could
+    be different in the two threads if |lcurr canFlowTo il'|.  However, none of the reduction rules
+    depend on an expression in that position, and there is never a
+    hole in that position
+    where evaluation could take place.  Thus, the same rules will syntactically
+    match for both task, and we are left to argue that all premises
+    evaluate to the same values for |it1| and |it2|, as well as that
+    the resulting states |iS1'| and
+    |iS2''| are |il|-equivalent.
+    The additional premises $P$ that follow
+    the condition in Definition~\ref{def:restricted} are not a problem,
+    since those
     predicates only depend on |erase il ic1|, which is equivalent
-    to |erase il ic2|, and thus those predicates evaluate in the same way.
-    Thus, we only
-    need to argue that the potential differences in |iS1| and |iS2| cannot
-    have an influence on the execution (and we know |iS1| and |iS2| are
-    |il|-equivalent).
-    Again, only sending and receiving will depend on, or change |iS|,
-    so we consider all these cases.
+    to |erase il ic2''|, and thus those predicates evaluate in the same way.
+    All other premises are either on the threads labels (which are the same),
+    or on the state |iS1|, or |iS2'|, respectively.  Because
+    |erase il iS1=erase il iS2'|, all of these also evaluate in the same way,
+    as can be seen by simply considering all rules that involve or
+    change the state:
     \begin{description}
@@
       queue are equivalent.
+      \item[Case \textsc{I-new}] The newly allocated address can be the same
+      for both |it1| and |it2|, thus resulting in |il|-equivalent states.
+      \item[Case \textsc{I-write}] By |erase il it1=earse il it2| both tasks
+      write the same value, and therefore the resulting states will still
+      be |il|-equivalent.
     \end{description}
+
   \end{itemize}

### 2014-07-06 paper/retrofit.tex
First stab at swivel
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 \label{sec:retrofit}
+
+Before delving into the formal operational semantics in earnest, we'd
+like to first demonstrate some examples where a dynamic information flow
+control system can either be thought of as the execution of a single
+language or a collection of communicating, isolated tasks.
+
+\Red{(need to describe the correspondence)}
+
+\paragraph{Language restrictions versus isolated sandboxes}  If you want
+to create a standard programming language with information-flow control,
+the usual technique is to build in restrictions (dynamic or static)
+which allow noninterference to be proved.  While this is fine for toy
+languages, if the language in question is an existing language, these
+modifications can often require extremely intrusive, both in terms of
+semantic changes and implementation changes, and it is easy to get things
+wrong and permit a subtle implicit flow between different security levels.
+
+The alternative method is to start with complete isolation between
+different security levels: literally seperate instances of the
+``language runtime'' for each traditional IFC thread.  For languages
+which already have isolated implementations, such as JavaScript and C
+with access to hardware privilege separation, this is a far more
+practical starting point.  From here, the line between the isolated
+instances can be blurred, but the `completely isolated'' semantics
+are a helpful guidepost for what can be done safely.
+
+As an example, imagine a program which attempts to send a mutable
+reference from a low security level to a high security level:
+\begin{align*}
+    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
+    & |in TI (send (IT i) getLabel (IT (ref true)))|
+\end{align*}
+
+For now, ignore the |TI| and |IT| annotations: this code creates a new
+sandboxed thread $i$ which waits for a message, and then sends the
+thread a mutable cell containing the value true.  If this mutable cell
+is actually shared between the two tasks, it would be a violation of
+information flow if such an operation actually resulted in references
+being shared between two tasks.  However, since these are isolated
+tasks, the address received by the sandboxed task is actually a dangling
+pointer.  We can use a static discipline to avoid this situation
+entirely or dynamically copy the mutable cell into the destination
+context; in any case, the isolation makes it clear what semantics can
+be safely supported.
+
+While this is a very simple example, the elaborations of this principle
+can actually be quite non-obvious for more interesting language
+features.
+
+\paragraph{Stack frames versus scheduling}  A feature that is supported
+by some information flow control systems is the ability to temporarily
+raise one's label in order to do computation on data.  Once the
+computation is finished, the label is lowered back to the original
+label---a stack discipline.  Care must be taken to ensure that
+information doesn't leak when the label is lowered (for example, the
+parent is not allowed to inspect the result of the computation). In
+fact, systems with this feature generally only achieve
+termination-insensitive noninterference: if the high secrecy section
+doesn't terminate, this is observable by the halted execution of the low
+secrecy section.
+
+In this paper, we will instead say that the allocation of a new
+stack frame with a raised label corresponds to the creation of a
+new isolated task; a sample encoding using our language is
+shown in Figure~\ref{toLabeled}.
+
+\begin{figure}
+\begin{align*}
+    & |toLabeled l te @= | \\
+    & |tab let i = taskId in| \\
+%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
+    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
+\end{align*}
+\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
+\end{figure}
+
+The sequential processing of these
+tasks corresponds to a specific \emph{scheduling policy} of these
+threads.  This change of perspective to scheduling highlights the
+essential differents between termination-insensitive and termination-sensitive
+noninterference.
+
+\paragraph{Exceptions versus message passing}
+A language feature that has caused difficulty for
+many information flow control systems is handling exceptions.
+%
+The key difficulty appears when considering the propagation of exceptions
+across stack boundaries where the current label is restored, e.g., from secret
+to public, as done by LIO's |toLabeled| and Breeze's
+brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
+%
+If the exception crosses this boundary, it can leak information about the
+inner secret computation into a public computation; hence, both systems
+explicitly ensure that |toLabeled| does not propagate exceptions.
+
+When stack frames are treated as isolated tasks, the correct semantics
+are achieved automatically.
+%
+The only way for the stack frame to communicate information is by
+initiating inter-task message passing; in its absence, the ``parent
+frame'' will operate as if no exception had occurred.
+%
+For instance, 
+\begin{code}
+TI(toLabeled l (IT (if te then fail else true))); true
+\end{code}
+always evaluates to |true|, regardless of the value of |te|.
+%
+Of course, when communication is performed, there is no leak,
+because all of the necessary information flow checks needed to
+communicate between tasks are also performed here.
+\Red{TODO: note that if the target language allows inspecting if
+  result is exception we can implement Breeze's NAV (vs. just
+propagating)}
+
+\subsection{Preliminaries}
 
@@
 refer to as |specLang alpha targetLang|.
-
-\subsection{Examples}
-
-To get a feeling for how these operational semantics operate, we
-describe a few sample programs, and their corresponding behavior.
-
-\paragraph{Sending mutable references}  As each task maintains its own
-global state for the target language, one might reasonably wonder what would
-happen if you attempted to send a reference to another task.
-\begin{align*}
-    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
-    & |in TI (send (IT i) getLabel (IT (ref true)))|
-\end{align*}
-It would be a violation of information flow if such an operation actually
-resulted in references being shared between two tasks.  In fact, the address
-will be received by the sandboxed task, but it will be a dangling pointer; the
-task will get stuck (under the |roundrobinf| scheduler the \textsc{I-noStep} will in turn remove it from the task list).  Readers
-who are curious whether or not a static discipline could be enforced to
-prevent these dangling pointers should check Section~\ref{sec:extensions}.
-
-\paragraph{Status of the heap after a sandbox}  Consider a program whose
-semantics depends on the definition of |klone|:
-\begin{align*}
-    & |let x = ref true| \\
-    & |in TI (sandbox (IT (!x; !x))); x := false|
-\end{align*}
-When |klone| is the identity, the sandboxed task successfully dereferences
-the contents of the reference to be |true| twice (recall that references
-are cloned into the new global state).  When |klone| is the constant function
-to the empty store, |x| is a dangling pointer.
-
-\paragraph{Exceptions}  One language feature that has caused difficulty for
-many information flow control systems is handling exceptions.
-%
-The key difficulty appears when considering the propagation of exceptions
-across stack boundaries where the current label is restored, e.g., from secret
-to public, as done by LIO's |toLabeled| and Breeze's
-brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
-%
-If the exception crosses this boundary, it can leak information about the
-inner secret computation into a public computation; hence, both systems
-explicitly ensure that |toLabeled| does not propagate exceptions.
-
-Our general embedding approach provides these semantics by construction.
-%
-To show this, we first define an encoding of the sequential |toLabeled|
-construct in our framework:
-\begin{align*}
-    & |toLabeled l te @= | \\
-    & |tab let i = taskId in| \\
-%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
-    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
-    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
-\end{align*}
-When using the sequential scheduler |seqf|, the sandboxed task runs to
-completion before returning to the task that sandboxed it. 
-(Here, a task list can be interpreted as a number of information flow aware
-stack frames.)
-To read the result of a |toLabeled| operation
-(which is communicated via message passing), the parent task must raise
-its label; otherwise the label will get dropped, as per the \textsc{I-recv}
-rule.\footnote{A keen reader may note that with a single, per-task channel, we
-might mix up our messages.  Indeed, a proper development requires the ability
-to allocate fresh channels; for purposes of simplicity, this has been omitted.}
-
-Now suppose that our |targetLangML| is extended with a single exception
-expression |fail|, which reduces to |fail|, removing all containing |tE|
-evaluation contexts, i.e., it propagates up to a |IT (-)| boundary.
-%
-In this setting, it is clear that exceptions cannot cross boundaries.
-%
-For instance, 
-\begin{code}
-TI(toLabeled l (IT (if te then fail else true))); true
-\end{code}
-always evaluates to |true|, regardless of the value of |te|.
-%
-Just like in LIO and Breeze, however, only when calling |recv| on such messages
-will the exception be propagated.
-%
-This of course, is not a leak since the current label must be raised before
-receiving sensitive message, regardless of their content.
-\Red{TODO: note that if the target language allows inspecting if
-  result is exception we can implement Breeze's NAV (vs. just
-propagating)}

### 2014-07-07 paper/appendix.tex
Finish proof of helper lemma.

@@
   |its'| and a store |iS'| such that
-  \[
-    |iconf iS (it, its)| |.->| |iconf iS' (its, its')|
-    \qquad
-    |erase il its'|=|nil|
-    \qquad
-    |erase il iS'|=|erase il iS|
-  \]
+  \begin{align}
+  |iconf iS (it, its)| |.->| |iconf iS' (its, its')| \label{eq:hnb-1} \\
+  |erase il its'|=|nil| \label{eq:hnb-2}\\
+  |erase il iS'|=|erase il iS| \label{eq:hnb-3}
+  \end{align}
 \end{lemma}
 \begin{proof}
-  TODO (consideration of all rules that could be applied)
+  From $|erase il it|=|bullet|$ we know that the current label |lcurr| of |it|
+  must be above |il|.  Furthermore, tasks can always take a step (if no
+  regular rule applies, then \textsc{I-noStep} can be used), and thus
+  we consider all rules that could be applied to execute |it|.
+  \begin{description}
+    \item[Case \textsc{I-noStep} and \textsc{I-done}]
+    In this case, the task |it| is dropped,
+    and thus |its'=nil| and |iS'=iS| satisfy
+    conditions~\eqref{eq:hnb-2} and~\eqref{eq:hnb-3}.
+    \item[Case \textsc{I-sandbox}]
+    The newly created task has a label of at least |lcurr|, and will thus be
+    erased, as required by condition~\eqref{eq:hnb-2}.  Furthermore, the
+    state only changes for the newly created thread, and thus the state
+    change is erased, showing~\eqref{eq:hnb-3}.
+  \end{description}
+  In all other rules, no new tasks are created, and thus |its'| consists of just
+  the one task |it'|, to which |it| executed.  Since the tasks label can
+  only increase, |it'| is still erased, showing condition~\eqref{eq:hnb-2}.
+  We are left to show condition~\eqref{eq:hnb-3} for the remaining rules.
+  \begin{description}
+    \item[Case \textsc{I-send}]
+    A new message triple with label |il'| gets added to the message
+    queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
+    the triple will get erased.
+    \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
+    In this case, only the queue of
+    task |it| can change, which gets erased.
+    \item[Case \textsc{I-new}] The newly allocated address has to be at a
+    label at least as high as |lcurr|, and will thus be erased.
+    \item[Case \textsc{I-write}] Only addresses with a label |il'| above
+    |lcurr| can be written, thus the change in |iS1| will get erased.
+    \item[Otherwise.]  None of the other rules modify the state |iS|, and
+    thus |iS'=iS| will trivially satisfy condition~\eqref{eq:hnb-3}.
+  \end{description}
 \end{proof}
@@
     \end{description}
-
+    After |it2| has taken a step, we finally arrive in the desired
+    configuration |ic2'=iconf iS2'' (its2'', its2''', its2'''')|, where
+    |its2''''| contains the task resulting from executing |it2| (and
+    might contain, zero (if the task was done or stuck), one (for most steps) or two tasks if a new task was launched).
+    As required, we have
+    \[ |ic2| |.->|^* |ic2''| |.->| |ic2'|
+    \quad \land \quad |ic1'| \approx_{|il|} |ic2'| \text{.}\]
   \end{itemize}

### 2014-07-07 paper/appendix.tex
Minor updates about proofs, and some numbering fixes when referring to theorems.

@@
 \section{Formal Extensions}
+\label{sec:appendix-extensions}
+
+Here we formally define the syntax and semantics of the extensions
+sketched in Section~\ref{sec:extensions}.
+In Figure~\ref{fig:labeled-vals} we show how labeled values can be added,
+while Figure~\ref{fig:labeled-refs} details labeled references formally.
+These changes to the semantics require us to update the erasure function
+|erasef il|, which is shown in Figure~\ref{fig:erasure2}.
+Note that the soundness proof in Appendix~\ref{sec:appendix}
+is done for the fully extended language with labeled values and
+labeled references.
 

### 2014-07-07 paper/proofs.tex
Minor updates about proofs, and some numbering fixes when referring to theorems.

@@
 
-In this section we prove all theorems we have stated.
+In this section we prove the theorems we have stated, or give a proof
+sketch and refer to the extended version for the full proof.
 We first observe that the non-interference claims for the languages
@@
 in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
-from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
-respectively, where the set
+from Theorem~\ref{thm:restricted}, where the set
 of predicates is the set of always valid predicates (i.e., no restriction).
 
-Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
+Before we proceed with the proof of Theorem~\ref{thm:restricted},
 we state a lemma we will use.
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
+\begin{proof}[Proof of Theorem~\ref{thm:restricted}, TSNI]
   We prove the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
@@
   For space reasons, we only sketch the structure of the proof here.
-  We refer the interested reader to the Appendix
+  We refer the interested reader to Appendix~\ref{sec:appendix}
   \ifextended
@@
 \end{proof}
-The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
-in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
+The proof of Theorem~\ref{thm:restricted} about TINI proceeds largely
+in the same fashion as for TSNI, except that
 some cases are simpler due to the fact termination is not an issue

### 2014-07-07 paper/appendix.tex
Various small improvements, including a revision of extensions.txt (first part).

@@
 while Figure~\ref{fig:labeled-refs} details labeled references formally.
+For labeled values, we assume that the constructor |Labeled| is not part
+of the surface syntax, but rather an internal construct.
 These changes to the semantics require us to update the erasure function
-|erasef il|, which is shown in Figure~\ref{fig:erasure2}.
+|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
 Note that the soundness proof in Appendix~\ref{sec:appendix}
@@
   \end{mathpar}
-  \caption{}
+  \caption{Syntax and semantics for labeled values.  These rules are
+    understood to be an addition to the existing rules given earlier.}
   \label{fig:labeled-vals}
@@
   \end{mathpar}
-  \caption{}
+  \caption{Syntax and semantics for labeled references.  These rules are
+    understood to be an addition to the existing rules given earlier.}
   \label{fig:labeled-refs}
@@
   \caption{Erasure function for the full IFC language, with all extensions.
-    In all cases not specified (including target-language constructs),
-    |erasef il| is applied homomorphically.
+    In all cases that are not specified, including target-language constructs,
+    |erasef il| is applied homomorphically
+    (e.g., |erase il (setLabel e) = setLabel (erase il e)|).
     This definition replaces the one from Figure~\ref{fig:erasure}, which

### 2014-07-07 paper/extensions.tex
Various small improvements, including a revision of extensions.txt (first part).

@@
 
-Different concrete IFC implementations may wish to extend our minimal
-system with labeled constructs appropriate for their envisioned
-applications.
-%
+While the IFC language presented thus far provides the basic
+information flow primitives, actual IFC implementations
+may wish to extend the minimal system with more specialized
+constructs.
+%Different concrete IFC implementations may wish to extend our minimal
+%system with labeled constructs appropriate for their envisioned
+%applications.
+%%
 For example, SWAPI provides a labeled version of the XHR object, while
@@
 applications~\cite{hails}.
+%%
+%Below we
+%consider the addition of several labeled constructs to the abstract specification.
+Below we show how to extend the language with several such constructs,
+and highlight some other possible extensions as well.
 %
-Below we
-consider the addition of several labeled constructs to the abstract specification.
-%
-We remark that that the non-interference proofs must account for the
-new constructs, since they amend the IFC calculus semantics (usually
-by addition).
+%We remark that that the non-interference proofs must account for the
+%new constructs, since they amend the IFC calculus semantics (usually
+%by addition).
 
@@
 a labeled log can operate on both public and sensitive values.
+Similarly, a task that receives a sensitive value and forwards it
+to another task does not have be be at a sensitive level, if the
+value is not inspected.
 %
@@
 
-Thus, an extension that supports such fine-grained explicitly
-labeled values is essential.
+If such fine-grained labeling of values is required, our base IFC
+system can be extended with explicitly labeled
+values, much like those of LIO and
+Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
+inlinesep Labeled il ie|.
 %
-To this end, we extend the IFC calculus with explicitly labeled
-values, much like those of LIO and
-Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
-inlinesep Lb il tv|.
-%
-Following LIO, we say that the value |tv| is protected by label |il|,
+Following LIO, we say that the expression |ie| is protected by label |il|,
 while the label |il| itself is protected by the task's current label.
@@
 %
-However, when a task wishes to inspect the protected value |tv|, it
-must first raise it label to at least |il| to reflect that it is
+However, when a task wishes to inspect the protected value |ie|, it
+must first raise its label to at least |il| to reflect that it is
 incorporating data at such sensitivity level in its scope.
@@
 %
-(For these rules, we assume that the |Lb| constructor is not part of
-the surface syntax and thus cannot be accessed directly to construct
-or destruct such values without label checks.)
-% 
-We omit the reduction rules for labeled values since they closely
-follow those presented in~\cite{lio}.
+
+Full details with formal reduction rules can be found
+in \appendixext{}.
 %}
@@
 references, mutable variables (MVars)~\cite{CH96}, or channels,
-follows in a similar way.
+can be done in a similar manner.
 %
@@
 %
-While we can modify the IFC calculus to add such labeled state to each
-individual task, adding it to the system state |iS| leads to more
-interesting use cases.
+%While we can modify the IFC calculus to add such labeled state to each
+%individual task, adding it to the system state |iS| leads to more
+%interesting use cases.
 %
@@
 For example, when extending the calculus with labeled references, |iS|
-additionally contains a store that maps addresses to |(il, tv)| pairs
+additionally contains a store that maps addresses to a value
+and a label
 which can be read and written to by different tasks through a labeled
-|ref| implementations.
-%
-Since such labeled constructs have also been considered before in other
-concurrent systems, we do not discuss them further.
+reference implementations.
+Again, we omit details here and refer the interested reader
+to \appendixext{}, where this extension has been fully worked out.
 
@@
 %
-Since both the LIO and SWAPI implementations already support such features,
-we believe that extending our calculus to consider privileges is
-straight forward.
+%Since both the LIO and SWAPI implementations already support such features,
+%we believe that extending our calculus to consider privileges is
+%straight forward.
 %
-However, the challenge with such an extension lies in the precise
-security guarantees that must be proved.
+The challenge with such an extension lies in the precise
+security guarantees that must be proved, which to the best of our
+knowledge is an open research problem.
 %
@@
 control mechanism---called \emph{clearance}---at the language
-level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}; this mechanisms is
+level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
+This mechanisms is
 used to restrict a computation from accessing data (or communicating

### 2014-07-07 paper/formal.tex
Various small improvements, including a revision of extensions.txt (first part).

@@
     |bullet| & |il' cantFlowTo il| \\
-    |fullconf id il' tS ie| & \text{otherwise}
+    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
   \end{cases} \\
@@
 configurations.  In all other cases, including target-language constructs,
-|erasef il| is applied homomorphically.  \label{fig:erasure} }
+|erasef il| is applied homomorphically.
+Note that |erase il ie| is always equal to |ie| (and similar for |tS|)
+in this simple setting.  However,
+when the IFC language is extended with more constructs as shown in
+Section~\ref{sec:extensions}, then this will no longer be the case.
+\label{fig:erasure} }
 \end{figure}

### 2014-07-07 paper/concrete.tex
nit

@@
   language |(C', tarrow', erasefp l)| if there exist total functions |f
-  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| |finv
-  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
+  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| and |finv
+  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g., if
   $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
@@
   \label{thm:iso-tsni}
-  If L is isomorphic to L' and L' satisfies TSNI, then
-  L satisfies TSNI.
+  If $L$ is isomorphic to $L'$ and $L'$ satisfies TSNI, then
+  $L$ satisfies TSNI.
 \end{theorem}
@@
   Shown by transporting configurations and reduction derivations from
-  L to L', applying TSNI, and then transporting the
+  $L$ to $L'$, applying TSNI, and then transporting the
   resulting configuration, $l$-equivalence and multi-step derivation back.
@@
 
+\Red{TODO: intuition for why weakly is enough for TINI}
+
 \begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
   \label{thm:iso-tini}
-  If a language L is weakly isomorphic to a language L', and L'
-  satisfies TINI, then L satisfies TINI.
+  If a language $L$ is weakly isomorphic to a language $L'$, and $L'$
+  satisfies TINI, then $L$ satisfies TINI.
 \end{theorem}
@@
   Shown by transporting configurations and reduction derivations
-  from L to L', applying TINI and transporting the resulting
+  from $L$ to $L'$, applying TINI and transporting the resulting
   equivalence back using functoriality of |finv| over $l$-equivalences.
@@
   by adding a predicate $P \in \mathcal P$ to the premise of
-  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
+  any rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
   can depend only on the \textit{erased} configuration
@@
       .->
-      iS'; tS; sched F (it1, ldots, itnew)
+      iS'; tS; sched box (it1, ldots, itnew)
     |}

### 2014-07-07 paper/concrete.tex
Revert "nit"
This reverts commit 728f38e11206d90ddcd2288bf6529db18a108f6b.

@@
   by adding a predicate $P \in \mathcal P$ to the premise of
-  any rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
+  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
   can depend only on the \textit{erased} configuration

### 2014-07-07 paper/appendix.tex
minor
a_l is not in surface syntax

@@
 For labeled values, we assume that the constructor |Labeled| is not part
-of the surface syntax, but rather an internal construct.
+of the surface syntax, but rather an internal construct.  Similarly,
+the construct |ial| is internal in the labeled reference implementation.
 These changes to the semantics require us to update the erasure function
@@
     \inferrule[I-unlabel]
-    {|
-      il''=il lub il'
-    |}
+    {}
     {|
@@
       ->
-      niconf iS id (il'') ie
+      niconf iS id (il  lub il' ) ie
     |}

### 2014-07-07 paper/extensions.tex
clearance fix

@@
 LIO, SWAPI, and Breeze additionally provide a discretionary access
-control mechanism---called \emph{clearance}---at the language
+control (DAC) mechanism---called \emph{clearance}---at the language
 level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
-This mechanisms is
-used to restrict a computation from accessing data (or communicating
-with entities) above a specified label, the clearance.
 %
-For simplicity, we omitted clearance from our formalism.
+This mechanisms is used to restrict a computation from allocating and
+accessing data (or communicating with entities) above a specified
+label, the clearance.
 %
-We only remark that the mechanism generalizes beyond these IFC systems
-in a straight forward manner and does not affect our definitions or
-proofs in any meaningful way.
+Amending our IFC language with clearance is mostly straight forward,
+and, in particular, does not not affect our definitions or proofs in
+any meaningful way.
+%
+To this end, we first extend tasks to track a clearance label
+alongside the current label, and amend the core IFC language with two
+new terminals for retrieving and setting this value (see
+Appendix~\ref{sec:appendix-extensions}).
+%
+Since this extension simply adds a per-task global mutable variable,
+our security guarantees hold trivially.
+%
+Of course this also does not provide any notion of DAC.
+%
+To do so we restrict the language with $\mathcal{P}_\text{clearance}$,
+the family of always valid predicates, except for the ones for
+rules that raise the current label (e.g., \textsc{I-setLabel}) or
+perform allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}).
+%
+The predicate for \textsc{I-setLabel} is: $P = |il canFlowTo il'|$,
+where |il'| is the clearance and |il| is the current label.
+%
+As further discussed in Appendix~\ref{sec:appendix-extensions},
+similar predicates are used in some of the rules of the calculus
+extended with labeled values and references.
 

### 2014-07-07 paper/extensions.tex
clearance clarify

@@
 alongside the current label, and amend the core IFC language with two
-new terminals for retrieving and setting this value (see
-Appendix~\ref{sec:appendix-extensions}).
+new terminals for retrieving and setting this value.
 %
@@
 %
-Of course this also does not provide any notion of DAC.
+However, this does not implement any DAC mechanism.
 %
-To do so we restrict the language with $\mathcal{P}_\text{clearance}$,
-the family of always valid predicates, except for the ones for
-rules that raise the current label (e.g., \textsc{I-setLabel}) or
-perform allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}).
+To do so, we must restrict the language with
+$\mathcal{P}_\text{clearance}$.
 %
-The predicate for \textsc{I-setLabel} is: $P = |il canFlowTo il'|$,
-where |il'| is the clearance and |il| is the current label.
+This family contains always valid predicates, except for rules that
+raise the current label (e.g., \textsc{I-setLabel}), perform
+allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
+clearance (clearance should not be arbitrarily raised).
 %
-As further discussed in Appendix~\ref{sec:appendix-extensions},
-similar predicates are used in some of the rules of the calculus
-extended with labeled values and references.
+These predicates use the clearance to impose DAC.
+%
+For instance, the predicate for \textsc{I-setLabel} prevents the
+current label from being raised above the clearance (and thus permit
+reads above the clearance); this predicate is given by $P = |il
+canFlowTo il'|$, where |il'| is the clearance and |il| is the current
+label.
+%
+The otters predicates are defined in a similar way and omitted for
+clarity.
 

### 2014-07-07 paper/extensions.tex
scheduling

@@
   When considering a label lattice that is not totally ordered, e.g.,
-  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
-  considerably more complex. See~\cite{Kashyap:2011}.
+  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
+  considerably more complex.
 }
 %
-More generally, we believe that deterministic schedulers that always
-make ``low-progress,'' i.e., if a task whose label is not above the
-current task's label will will eventually run, and do not decide which
-low tasks to schedule according to data more sensitive than the tasks'
-label, i.e., the scheduler does not schedule one public thread over
-another according to sensitive data, to be safe.
+Our formalism generalizes to a class of stateless, deterministic
+schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
+modify (or create) tasks; 2) \emph{non-interfering at level |l|}, the
+greatest lower bound of all the labels on the task labels,\footnote{
+  The label on a task's current label is the current label of the
+  parent at the time of creation, i.e., the initial current label of
+  the task.
+} i.e., they do not depends on a sensitive task's state; and, 3) make
+\emph{low-progress}, i.e., if there is a task in the task list whose
+label is below (or incomparable to) the label of another task, this
+task (or another one at the same level) must eventually run.
 %
+The last condition is required for TSNI; languages relying on
+schedulers, such as |seqf|, that do not satisfy the low-progress
+condition can at most satisfy TINI.
+%
+For simplicity, we do treat this, more-general class of schedulers;
+doing so would require modifying our calculus to keep track of the
+label on the current label of tasks and complicate the
+non-interference proofs.
 
-Despite allowing a number of practical schedulers to be expressed, our
-scheduler parametrization is limited.
+More fundamentally, our scheduler parametrization is limited in being
+stateless and deterministic.
 %
-For instance, since |alpha| is a map on task lists, schedulers that
-rely on the global state |iS| or previous task configurations cannot
-be expressed.
+For instance,  we do not consider  schedulers that, among other, rely
+on the global state |iS| or previous task configurations, as treated
+in~\cite{russo2006securing}.
 %
-Though, we do not believe this to be a fundamental limitation, our
-current formalization cannot directly be applied to more-powerful, but
-safe, scheduling policies, as considered by~\cite{russo2006securing}.
-%
-More fundamentally, our definitions rely on deterministic relations,
+Additionally, our definitions rely on deterministic relations,
 and thus extending the system to consider non-deterministic schedulers
@@
 %
-For instance, this may potentially require the security condition to
+Such extensions may potentially require the security condition to
 consider \emph{low-determinism}, which states that a program is secure
-only if |l|-equivalent results are deterministic~\cite{Zdancewic:Myers:CSFW03,
-sabelfeld2003language}.
+only if |l|-equivalent results are
+deterministic~\cite{Zdancewic:Myers:CSFW03, sabelfeld2003language}.
 

### 2014-07-07 paper/extensions.tex
Minor fixes, and minor revision of clearance.

@@
 
-Full details with formal reduction rules can be found
-in \appendixext{}.
+Full details with formal reduction rules are provided
+in \appendixext{}, but omitted here for space reasons.
 %}
@@
 %
-LIO, SWAPI, and Breeze additionally provide a discretionary access
+Systems like LIO, SWAPI, and Breeze additionally provide a discretionary access
 control (DAC) mechanism---called \emph{clearance}---at the language
@@
 %
-Amending our IFC language with clearance is mostly straight forward,
-and, in particular, does not not affect our definitions or proofs in
-any meaningful way.
+Amending our IFC language with clearance is straight forward,
+and, can be done using our notation of a restricted language.
 %
@@
 %
-Since this extension simply adds a per-task global mutable variable,
-our security guarantees hold trivially.
+Since this extension only adds a per-task mutable variable whose value
+has no influence on the system, all security guarantees still
+hold, by essentially the same proofs.
 %
-However, this does not implement any DAC mechanism.
+However, this does not implement any DAC mechanism yet.
 %
-To do so, we must restrict the language with
-$\mathcal{P}_\text{clearance}$.
-%
-This family contains always valid predicates, except for rules that
+To do so, we can restrict the language with a family of predicates
+$\mathcal{P}_\text{clearance}$:
+All rules that
 raise the current label (e.g., \textsc{I-setLabel}), perform
 allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
-clearance (clearance should not be arbitrarily raised).
-%
-These predicates use the clearance to impose DAC.
+clearance (clearance should not be arbitrarily raised), a predicate
+that uses the clearance to impose DAC is used.
 %
@@
 current label from being raised above the clearance (and thus permit
-reads above the clearance); this predicate is given by $P = |il
-canFlowTo il'|$, where |il'| is the clearance and |il| is the current
+reads above the clearance).  The predicate $P := |il
+canFlowTo il'|$ achieves this restriction, where |il'| is the
+clearance and |il| is the current
 label.
 %
-The otters predicates are defined in a similar way and omitted for
-clarity.
+The other predicates are defined in a similar way and omitted for
+brevity.
+
+TODO: provide them in the appendix, and refer to them here.
 

### 2014-07-07 paper/retrofit.tex
Minor fixes, and minor revision of clearance.

@@
 the usual technique is to build in restrictions (dynamic or static)
-which allow noninterference to be proved.  While this is fine for toy
+which allow non-interference to be proved.  While this is fine for toy
 languages, if the language in question is an existing language, these
@@
 fact, systems with this feature generally only achieve
-termination-insensitive noninterference: if the high secrecy section
+termination-insensitive non-interference: if the high secrecy section
 doesn't terminate, this is observable by the halted execution of the low
@@
 new isolated task; a sample encoding using our language is
-shown in Figure~\ref{toLabeled}.
+shown in Figure~\ref{fig:toLabeled}.
 
@@
 essential differents between termination-insensitive and termination-sensitive
-noninterference.
+non-interference.
 

### 2014-07-07 paper/retrofit.tex
OK I think I socked the new intro
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-07-05 paper/retrofit.tex
@@
 
-Our overall plan will be to take a \textbf{{\color{red} target
+Information flow control systems operate by associating data with \emph{labels},
+which specify whether or not data tagged with one label |l1| can flow to another
+label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
+security policy (for example, confidential information should not flow to
+a public channel), and the work of specifying the semantics of an information
+flow language involves demonstrating that impermissible flows cannot happen,
+a property called \emph{noninterference}.
+
+Supporting fine-grained labeling of data in a programming language often
+requires extremely intrusive modifications to its semantics and
+implementation.  In this paper, we advocate applying coarse-grained
+labeling~\cite{Zeldovich:2006, lio} to its extreme: our starting point
+is multiple instances of completely isolated language runtimes or \emph{tasks}, with
+information flow control applied between their communication.  For
+languages which are implemented with isolation, such as JavaScript or C
+with access to hardware privilege separation, systems along these lines
+are far more easily implementable and require minimal semantic changes.
+
+Why is this setting more interesting than ``traditional
+coarse-grained information flow control system on isolated
+threads?''  First, although completely separate tasks
+are semantically easy to reason about, real-world implementations often blur the
+lines between tasks in the name of efficiency.  Characterizing what optimizations
+are permissible is a problem we address in Section~\ref{sec:concrete}, and
+it is quite subtle, since removing transitions from the operational semantics
+of a language can break noninterference.  Second, even though the underlying
+semantic model involves communicating tasks, these tasks can be coordinated
+together in ways that simulate traditional features in monolithic languages.
+In fact, it is a very useful design tool for discovering what variants of the
+features are permissible and which are not.
+
+A very simple example is a low security task sending a high security
+task a mutable reference:
+\begin{align*}
+    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
+    & |in TI (send (IT i) getLabel (IT (ref true)))|
+\end{align*}
+
+For now, ignore |TI| and |IT|: roughly, this code creates a new
+|sandbox|ed thread $i$ which waits (\textbf{blockingRecv}) for a
+message, and then \textbf{send}s the thread a mutable reference to (|ref
+true|).  If this operation actually shared the mutable cell, this cell
+could be used to violate information flow control.  When working with
+isolated tasks which each have their own heaps, the isolation is obviously true:
+the sandboxed task receives a dangling pointer.
+
+While this is a very simple example, we can still ask: given the
+obviously safe formulation with separate heaps, can this fact be useful
+for showing the safety of an semantics which only has a single heap
+(Yes: see Section~\ref{sec:single-heap})?  Furthermore, the ``raw''
+semantics violates expectations about how inter-thread communication
+works on a shared heap: it strongly suggests, for example, that which
+types of data may be passed between tasks should be restricted (for
+example, in JavaScript, one might only allow JSON objects to be passed
+between tasks).
+
+Before moving on to the formal treatment of our system, we'd like to give
+two more examples of language features which have an interesting interpretation
+when viewed in the setting of multiple tasks.
+
+\paragraph{Stack frames versus scheduling}  One feature which is
+supported by some information flow control systems is the ability to
+temporarily raise the current label in order to do computation on data
+(as done by LIO's |toLabeled| and Breeze's
+brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
+stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
+enforcing a stack discipline.  This is the trickiest part of the feature: care must be taken to ensure that information doesn't leak when
+the label is lowered. In fact, systems with this feature generally only
+achieve termination-insensitive non-interference: if the high secrecy
+section doesn't terminate, this is observable by the non-execution of
+the defunct public continuation.
+
+\begin{figure}
+\begin{align*}
+    & |toLabeled l te @= | \\
+    & |tab let i = taskId in| \\
+%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
+    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
+\end{align*}
+\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
+\end{figure}
+
+When considering tasks, we will instead say that the allocation of a new
+stack frame with a raised label corresponds to the creation of a new
+isolated task; a sample encoding using our language is shown in
+Figure~\ref{fig:toLabeled}.
+However, this is not enough: in a stack discipline, one generally
+expects stack entries to be processed in order, rather than in parallel
+as would be suggested by isolated tasks.  The sequential processing of
+the task queue corresponds to a specific \emph{scheduling policy} of
+these threads.  The recasting of the problem to one of scheduling
+highlights the essential difference between termination-insensitive and
+termination-sensitive non-interference.
+
+\paragraph{Exceptions versus message passing}
+Another language feature that has caused difficulty for
+many information flow control systems is exceptions handling,
+when built on top of this stack discipline.
+%
+The key difficulty appears when considering the propagation of exceptions
+across stack boundaries where the current label is restored.
+%
+If the exception crosses this boundary, it can leak information about the
+inner secret computation into a public computation; hence, one must
+explicitly ensure that |toLabeled| does not propagate exceptions.
+
+When stack frames are treated as isolated tasks, the correct semantics
+are achieved automatically.
+%
+Exceptions simply stop when the hit the top-level of a task:
+the only way for the frame to communicate information is by
+initiating inter-task message passing.
+%
+For instance, 
+\begin{code}
+TI(toLabeled l (IT (if te then fail else true))); true
+\end{code}
+always evaluates to |true|, regardless of the value of |te|.
+\Red{TODO: note that if the target language allows inspecting if
+  result is exception we can implement Breeze's NAV (vs. just
+propagating)}
+
+\subsection{Preliminaries}
+
+Our goal now is to
+describe how to take a \textbf{{\color{red} target
 language}} with a formal operational semantics and combine it with an
@@
 references and fixpoint in place of ECMAScript, to demonstrate some of the key
-properties without having too much detail; we discuss the proper
+properties without having too much detail (and because the embedding really
+doesn't care about what, exactly, is in the target language); we discuss the proper
 embedding in more detail in Section~\ref{sec:real}.
@@
 
-Most modern, dynamic information flow control languages encode
-policy by associating a \emph{label}
-with data, which encodes whether or not data tagged with one
-label |l1| can flow to another label |l2| (written as |canFlowTo2 l1 l2|).
-Our embedding is agnostic to the choice of labeling scheme; we only
-require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
-with the partial order $\sqsubseteq$, join |lub|, and meet |glb|.
-In this paper, we simply represent labels with the metavariable
-$l$, but do not discuss them in more detail.
+As mentioned previously, most modern, dynamic information flow control
+languages encode policy by associating a label with data.  Our
+embedding is agnostic to the choice of labeling scheme; we only require
+the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056} with
+the partial order $\sqsubseteq$, join |lub|, and meet |glb|.  In this
+paper, we simply represent labels with the metavariable $l$, but do not
+discuss them in more detail.
 
-As opposed to more traditional fine-grained language-based IFC systems that
-associate labels with values~\cite{sabelfeld2003language,
-Austin:Flanagan:PLAS09}, we follow~\cite{Zeldovich:2006, lio} in taking a
-coarse-grained floating-label approach and associating labels with
-\emph{tasks}.
+In our coarse-grained floating-label approach, labels are associated with tasks.
 %

### 2014-07-07 paper/real.tex
new approach, wip

@@
 In this section, we consider the application of our embedding to
-JavaScript and two other real world target languages, C and Haskell.
+JavaScript, and two other real world target languages, Haskell, and C.
 %
@@
 %
-Two of the systems we describe have been implemented: the Haskell
-system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
-implementation of the IFC system for C to future work.
-
-\subsection{C}
-\label{sec:real:c}
-%
-C programs are able to execute arbitrary (machine) code, access
-arbitrary memory, and perform arbitrary syscalls.
-%
-Thus, the confinement of C programs must be imposed by the underlying OS
-and hardware.
-%
-For instance, this isolation can be achieved using Dune's hardware protection
-mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
-version of Wedge~\cite{Belay:2012:DSU:2387880.2387913,
-Bittau:2008:WSA:1387589.1387611} with an information flow control
-policy.
-%
-Using page tables, a (trusted) IFC runtime could ensure that each task,
-implemented as a lightweight process, can only access the memory it
-allocates--tasks do not have access to any shared memory.
-%
-In addition, ring protection could be used to intercept syscalls performed by
-a task and only permit those corresponding to our IFC language (such as
-|getLabel| or |send|).
-%
-Dunes hardware protection mechanism allows us to provide a concrete
-implementation that is efficient and relatively simple to reason
-about, but other sandboxing mechanisms could be used in place of Dune.
-
-In this setting, the combined language of Section~\ref{sec:retrofit}
-can be interpreted in the following way: calling from the target
-language to the IFC language corresponds to invoking a syscall.
-%
-Creating a new task with the |sandbox| syscall corresponds to
-\emph{forking} a process.  Here, page tables limit what memory
-a task can access: we can ensure there will be no memory (effectively
-defining |klone(tS)
-= tS0|, where |tS0| is the set of pages necessary to bootstrap a
-lightweight process.)
-%
-Similarly, control over page tables and protection bits allows us to
-define a |send| syscall that copies pages to our
-(trusted) runtime queue; and, correspondingly, a |recv| that copies
-the pages from the runtime queue to the (untrusted) receiver.
-%
-Since C is not memory safe, conditions on these syscalls are
-meaningless.
-
-\subsection{Haskell}
-\label{sec:real:hs}
-In contrast with the C embedding which relies on hardware protection
-mechanisms, a Haskell implementation can leverage Haskell's strong data
-abstraction and static type system, monadic approach to effects, and
-lightweight concurrency to implement the embedding in a more lightweight
-manner.  We briefly describe one such system, LIO~\cite{lio}, which
-implements IFC as a library.
-
-LIO is implemented by defining a new monad, \verb|LIO|, which wraps Haskell's \verb|IO|
-monad.
-%
-The purpose of this monad is twofold: it restricts the use of
-arbitrary effects that would ordinarily be allowed by the \verb|IO| monad,
-and it associates labels with tasks.
-%
-Computations in the \verb|LIO|
-monad can be thought to be operating within the IFC system.
-%
-One important aspect of using \verb|IO| as the base for this
-implementation is that it allows use of Haskell's efficient
-implementation of threads, channels, etc. (e.g., in the concurrent
-version of LIO, we use Haskell's \texttt{forkIO} to fork a lightweight
-thread in the case of |fork|~\cite{stefan:addressing-covert}), in
-contrast to defining them in a completely pure fashion (as suggested
-in Section~\ref{sec:monad}).
-
-What is the interpretation of this system as per Section~\ref{sec:retrofit}?
-%
-Here, the \emph{pure subset} of Haskell is the target language, while
-the monadic subset of Haskell in the \verb|LIO| monad is the IFC
-language.
-%
-Crucially, the lack of unrestricted mutation in the pure fragment of
-Haskell prevents direct communication between tasks, even when memory is
-shared between them.\footnote{However, lazy evaluation can still produce
-a covert channel.}
-
-Since this IFC system is implemented as a library in Haskell,
-implementation-wise, we must ensure that these languages are indeed the subsets of Haskell
-we claim, i.e., while the concrete language is all of Haskell, we must
-ensure that we can restrict programs to our subset of Haskell that
-encodes the combined language.
-%
-To this end, \verb|LIO| relies on Haskell's strong data abstraction and type system
-(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
-ensure that arbitrary \verb|IO| actions cannot be lifted into
-\verb|LIO|.
-%
-In other words, assuming \verb|LIO| is implemented correctly, programs
-written in the \verb|LIO| monad cannot perform arbitrary \verb|IO| actions
-without breaking abstraction.
-
-We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
-additional details on the various implementations of this system.\footnote{It's worth noting that the proofs of non-interference we have given for asynchronous communication primitives are new and not in the original presentation of LIO.}
+%% Two of the systems we describe have been implemented: the Haskell
+%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
+%% implementation of the IFC system for C to future work.
 
@@
 
-JavaScript (JS), as specified by ECMAScript~\cite{ecma}, does not have any
-built-in functionality for I/O. Capabilities such as the ability to
-mutate the DOM and read user input are APIs defined on top of the ECMAScript
-specification.
+An interesting aspect of JavaScript, as specified by
+ECMAScript~\cite{ecma}, is that it does not have any built-in
+functionality for I/O.
 %
-Consequently, and in contrast to our C and Haskell embeddings---for
-which we must eliminate external effects---the embedding for JS is
-trivial.
+(We denote this language as |targetLangJS|.)
+%
+Instead, when embedding a JavaScript engine, browser layout engines,
+such as Gecko, and server-side platforms, such as Node.js, expose APIs
+such as the DOM and filesystem as part of the runtime system.
+%
+In a similar manner, we can directly implement the embedded language
+|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
+of the runtime and running multiple instances of the JavaScript VM in
+separate OS-level threads.\footnote{
+  We, indeed, do this for the Gecko implementation when considering
+  Web Workers that run operate OS threads.
+}
+%
+Unfortunately, this becomes very costly when an application relies on
+many tasks.
+%
+(Consider, for instance, a server-side web application that wishes to
+create a new task for each HTTP request.)
+
+This issue of performance and JavaScript isolation is not unique to
+our work. 
+%
+In particular, browser layout engines rely on the isolation of content
+from different origins (e.g., two iframes of different origins) to
+implement the \emph{same-origin policy}.
+%
+Since creating an OS thread for each iframe is expensive, both V8 and
+SpiderMonkey provide a means for running JavaScript code in isolation,
+on disjoint sub-heaps of the same OS thread.
+%
+In V8 this unit of isolation is called a \emph{context}~\tocite{}, in
+SpiderMonkey, it called a \emph{compartment}~\tocite{}.
+%
+(We will use these terms and ``task'' interchangeably.)
+%
+Each context/compartment is associated with a global object, which
+implements the JavaScript standard library (e.g., \verb|Object|,
+\verb|Array|, etc.).
+%
+It is this global object that is extended with feature such as the
+DOM and filesystem.
+
+\Red{HERE}
 
@@
 .->
-iS'; sched S (fullconf id il tS (iniEi unit), ldots)
+iS'; sched step (fullconf id il tS (iniEi unit), ldots)
 |}
@@
 %% more details.}
+
+\subsection{Haskell}
+\label{sec:real:hs}
+In contrast with the C embedding which relies on hardware protection
+mechanisms, a Haskell implementation can leverage Haskell's strong data
+abstraction and static type system, monadic approach to effects, and
+lightweight concurrency to implement the embedding in a more lightweight
+manner.  We briefly describe one such system, LIO~\cite{lio}, which
+implements IFC as a library.
+
+LIO is implemented by defining a new monad, \verb|LIO|, which wraps Haskell's \verb|IO|
+monad.
+%
+The purpose of this monad is twofold: it restricts the use of
+arbitrary effects that would ordinarily be allowed by the \verb|IO| monad,
+and it associates labels with tasks.
+%
+Computations in the \verb|LIO|
+monad can be thought to be operating within the IFC system.
+%
+One important aspect of using \verb|IO| as the base for this
+implementation is that it allows use of Haskell's efficient
+implementation of threads, channels, etc. (e.g., in the concurrent
+version of LIO, we use Haskell's \texttt{forkIO} to fork a lightweight
+thread in the case of |fork|~\cite{stefan:addressing-covert}), in
+contrast to defining them in a completely pure fashion (as suggested
+in Section~\ref{sec:monad}).
+
+What is the interpretation of this system as per Section~\ref{sec:retrofit}?
+%
+Here, the \emph{pure subset} of Haskell is the target language, while
+the monadic subset of Haskell in the \verb|LIO| monad is the IFC
+language.
+%
+Crucially, the lack of unrestricted mutation in the pure fragment of
+Haskell prevents direct communication between tasks, even when memory is
+shared between them.\footnote{However, lazy evaluation can still produce
+a covert channel.}
+
+Since this IFC system is implemented as a library in Haskell,
+implementation-wise, we must ensure that these languages are indeed the subsets of Haskell
+we claim, i.e., while the concrete language is all of Haskell, we must
+ensure that we can restrict programs to our subset of Haskell that
+encodes the combined language.
+%
+To this end, \verb|LIO| relies on Haskell's strong data abstraction and type system
+(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
+ensure that arbitrary \verb|IO| actions cannot be lifted into
+\verb|LIO|.
+%
+In other words, assuming \verb|LIO| is implemented correctly, programs
+written in the \verb|LIO| monad cannot perform arbitrary \verb|IO| actions
+without breaking abstraction.
+
+We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
+additional details on the various implementations of this system.\footnote{It's worth noting that the proofs of non-interference we have given for asynchronous communication primitives are new and not in the original presentation of LIO.}
+
+\subsection{C}
+\label{sec:real:c}
+%
+C programs are able to execute arbitrary (machine) code, access
+arbitrary memory, and perform arbitrary syscalls.
+%
+Thus, the confinement of C programs must be imposed by the underlying OS
+and hardware.
+%
+For instance, this isolation can be achieved using Dune's hardware protection
+mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
+version of Wedge~\cite{Belay:2012:DSU:2387880.2387913,
+Bittau:2008:WSA:1387589.1387611} with an information flow control
+policy.
+%
+Using page tables, a (trusted) IFC runtime could ensure that each task,
+implemented as a lightweight process, can only access the memory it
+allocates--tasks do not have access to any shared memory.
+%
+In addition, ring protection could be used to intercept syscalls performed by
+a task and only permit those corresponding to our IFC language (such as
+|getLabel| or |send|).
+%
+Dunes hardware protection mechanism allows us to provide a concrete
+implementation that is efficient and relatively simple to reason
+about, but other sandboxing mechanisms could be used in place of Dune.
+
+In this setting, the combined language of Section~\ref{sec:retrofit}
+can be interpreted in the following way: calling from the target
+language to the IFC language corresponds to invoking a syscall.
+%
+Creating a new task with the |sandbox| syscall corresponds to
+\emph{forking} a process.  Here, page tables limit what memory
+a task can access: we can ensure there will be no memory (effectively
+defining |klone(tS)
+= tS0|, where |tS0| is the set of pages necessary to bootstrap a
+lightweight process.)
+%
+Similarly, control over page tables and protection bits allows us to
+define a |send| syscall that copies pages to our
+(trusted) runtime queue; and, correspondingly, a |recv| that copies
+the pages from the runtime queue to the (untrusted) receiver.
+%
+Since C is not memory safe, conditions on these syscalls are
+meaningless.

### 2014-07-07 paper/extensions.tex

@@
 \subsection{Scheduling Policies}
-Our specification language is parametrized by a scheduling policy
-|alpha|, which maps a task list to a potentially different task list.
+Our specification language is parametrized by a scheduling policy |alpha|, which
+maps a task list to a potentially different task list, i.e.,
+$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
 %
@@
 %
-For simplicity we considered two popular policies |roundrobinf| and
+We described two popular policies |roundrobinf| and
 |seqf| for which we showed TSNI and TINI, respectively.
 %
-However, our definitions allow for other scheduling policies that only
-rely on the current task list.
+However, our definitions allow for other scheduling policies based on the
+current task list---in fact, our formalism can be easily 
+extended to consider history~\cite{BartheRRS07}.
 %
-For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
-that always schedules less sensitive threads first; this can be
+As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
+which always schedules less sensitive threads first; this can be
 employed to address external timing covert channels where an attacker
@@
 %
-Our formalism generalizes to a class of stateless, deterministic
+More precisely, our calculus generalizes to a class of deterministic
 schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
-modify (or create) tasks; 2) \emph{non-interfering at level |l|}, the
-greatest lower bound of all the labels on the task labels,\footnote{
-  The label on a task's current label is the current label of the
-  parent at the time of creation, i.e., the initial current label of
-  the task.
-} i.e., they do not depends on a sensitive task's state; and, 3) make
-\emph{low-progress}, i.e., if there is a task in the task list whose
-label is below (or incomparable to) the label of another task, this
-task (or another one at the same level) must eventually run.
+modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
+%greatest lower bound of all the labels on the task labels,\footnote{
+%  The label on a task's current label is the current label of the
+%  parent at the time of creation, i.e., the initial current label of
+%  the task.
+%} 
+scheduling decisions on public tasks do not depend on a sensitive task's
+state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
+is a task in the task list whose label is below (or incomparable to) the label
+of another task, this task (or another one at the same level) must eventually
+run.
 %
@@
 More fundamentally, our scheduler parametrization is limited in being
-stateless and deterministic.
+deterministic, and thus extending the system to consider non-deterministic
+schedulers (or even non-deterministic target languages) is non-trivial.
 %
-For instance,  we do not consider  schedulers that, among other, rely
-on the global state |iS| or previous task configurations, as treated
-in~\cite{russo2006securing}.
+%For instance,  we do not consider  schedulers that, among other, rely
+%on the global state |iS| or previous task configurations, as treated
+%in~\cite{russo2006securing}.
 %
-Additionally, our definitions rely on deterministic relations,
-and thus extending the system to consider non-deterministic schedulers
-(or even non-deterministic target languages) is non-trivial.
+%Additionally, our definitions rely on deterministic relations,
 %
-Such extensions may potentially require the security condition to
-consider \emph{low-determinism}, which states that a program is secure
-only if |l|-equivalent results are
-deterministic~\cite{Zdancewic:Myers:CSFW03, sabelfeld2003language}.
+Such extensions often apply security conditions which suffer 
+from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
+adapt non-trivial definitions as
+\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
+which states that a program is secure only if |l|-equivalent results are
+deterministic.
 

### 2014-07-08 paper/retrofit.tex
typo

@@
 obviously safe formulation with separate heaps, can this fact be useful
-for showing the safety of an semantics which only has a single heap
+for showing the safety of a semantics which only has a single heap
 (Yes: see Section~\ref{sec:single-heap})?  Furthermore, the ``raw''

### 2014-07-08 paper/real.tex
fig for node

@@
 
-This issue of performance and JavaScript isolation is not unique to
-our work. 
+However, this issue of performance and JavaScript isolation is not
+unique to our work. 
 %
@@
 %
-In V8 this unit of isolation is called a \emph{context}~\tocite{}, in
+In V8, this unit of isolation is called a \emph{context}~\tocite{}, in
 SpiderMonkey, it called a \emph{compartment}~\tocite{}.
 %
-(We will use these terms and ``task'' interchangeably.)
+Each context/compartment is associated with a global object, which, by
+default, implements the JavaScript standard library (e.g.,
+\verb|Object|, \verb|Array|, etc.).
 %
-Each context/compartment is associated with a global object, which
-implements the JavaScript standard library (e.g., \verb|Object|,
-\verb|Array|, etc.).
+(Gecko and Node.js expose features such as the DOM and
+filesystem by extending this global object.)
 %
-It is this global object that is extended with feature such as the
-DOM and filesystem.
 
-\Red{HERE}
+We leverage contexts to implement |specLangJS seqf| for Node.js.
+%
+Our implementation provides a library for creating new tasks, i.e.,
+contexts whose global object only contains the standard JavaScript
+library and our IFC primitives (|send|, |sandbox|, etc.).
+%
+In turn, these tasks can create new tasks with |sandbox|.
+%
+Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
+the global object corresponding to the standard JavaScript library and
+our IFC primitives.
 
-We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
-(which we here denote by |targetLangJS|).
+\begin{figure}
+\centerline{\includegraphics[width=\columnwidth]{figs/node}}
+\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
+This example shows how our trusted monitor (left) is used to mediate
+communication between two tasks.}
+\end{figure}
+As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
+by the trusted library code (the main Node.js context), that tracks
+the current label, messages, etc. of each task.
 %
-The direct approach for implementing the embedded language |specLangJS roundrobinf| is
-by running multiple instances of the JS runtime, i.e., in
-separate OS-level threads.\footnote{
- The Firefox implementation of SWAPI also considers the case where
- tasks share the JavaScript runtime (and are cooperatively scheduled
- on the event-loop), but the heap and execution context of each task
- is disjoint. This is similar to the single-heap language of
- Section~\ref{sec:concrete}.  However, since the heap separation is
- provided by the browser, we do not discuss this further.
- The interested reader is referred to~\cite{swapi} for more details.
-}
+While V8 provides a means for sharing objects between contexts that
+share a security token (in the case of Blink this is used by pages of
+the same origin), our API (conservatively) restricts the kinds of
+messages that can be exchanged.
 %
-In SWAPI, the IFC language functionality is implemented in the JS
-runtime much like browser layout engines implement the DOM, and expose
-the new functions, e.g., \verb|getElementById|, by attaching them to
-the global JS object.
-%
-In turn, each task created with |sandbox| is
-executed in a separate thread, running a separate, \emph{fresh} instance of our
-modified JS runtime.
-%
-Formally, |sandbox| is defined with |klone(tS) =
-tS0|, where |tS0| is the global object corresponding to the standard
-JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
-etc.).
-
-Since this implementation approach relies on multiple runtimes of the
-language, sending arbitrary objects between tasks can result in
-unexpected behavior, e.g., when the object contains references.
-%
-As discussed in Section~\ref{sec:concrete}, we need to restrict |send|
-to expressions that can be marshalled as strings, i.e., structurally
-clonable objects.
+More concretely, and as mentioned in Section~\ref{sec:concrete}, we
+restrict |send| (and |sandbox|) to sending string values.
 %
@@
 %}
+%
+However, our implementation is accompanied by a library that provides
+a more flexible standard library, which, among other things,
+automatically marshalls JSON objects to/from strings on each
+|send|/|recv|.
+
+\Red{HERE}
+
 We remark that this is similar to the existing
@@
 takes a label argument.
+
+%
+In turn, each task created with |sandbox| is
+executed in a separate thread, running a separate, \emph{fresh} instance of our
+modified JS runtime.
+%
+Formally, |sandbox| is defined with |klone(tS) =
+tS0|, where |tS0| is the global object corresponding to the standard
+JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
+etc.).
 

### 2014-07-08 paper/retrofit.tex
Minor changes to retrofit.tex

@@
 Information flow control systems operate by associating data with \emph{labels},
-which specify whether or not data tagged with one label |l1| can flow to another
+and specifying whether or not data tagged with one label |l1| can flow
+to another
 label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
@@
 flow language involves demonstrating that impermissible flows cannot happen,
-a property called \emph{noninterference}.
+a property called \emph{non-interference}.
 
@@
 it is quite subtle, since removing transitions from the operational semantics
-of a language can break noninterference.  Second, even though the underlying
+of a language can in general break non-interference.
+Second, even though the underlying
 semantic model involves communicating tasks, these tasks can be coordinated
@@
 \end{align*}
-
-For now, ignore |TI| and |IT|: roughly, this code creates a new
-|sandbox|ed thread $i$ which waits (\textbf{blockingRecv}) for a
-message, and then \textbf{send}s the thread a mutable reference to (|ref
-true|).  If this operation actually shared the mutable cell, this cell
-could be used to violate information flow control.  When working with
+For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
+|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}) for a
+message, and then \textbf{send}s the task a mutable reference to |(ref
+true)|.  If this operation actually shared the mutable cell, this cell
+could be used to violate information flow control, by leaking
+information from the high security task to the low security task.
+When working with
 isolated tasks which each have their own heaps, the isolation is obviously true:
@@
 for showing the safety of a semantics which only has a single heap
-(Yes: see Section~\ref{sec:single-heap})?  Furthermore, the ``raw''
-semantics violates expectations about how inter-thread communication
+(we answer this question positively in Section~\ref{sec:single-heap})?
+Furthermore, the na\"ive
+semantics violates expectations about how inter-task communication
 works on a shared heap: it strongly suggests, for example, that which
@@
 example, in JavaScript, one might only allow JSON objects to be passed
-between tasks).
+between tasks, rather than general object structures).
 
@@
 the task queue corresponds to a specific \emph{scheduling policy} of
-these threads.  The recasting of the problem to one of scheduling
+these tasks.  The recasting of the problem to one of scheduling
 highlights the essential difference between termination-insensitive and
-termination-sensitive non-interference.
+termination-sensitive non-interference, and we will show how different
+scheduling policies give different security guarantees.
 

### 2014-07-08 paper/real.tex
capture
minor

@@
 
-An interesting aspect of JavaScript, as specified by
-ECMAScript~\cite{ecma}, is that it does not have any built-in
-functionality for I/O.
+JavaScript as specified by
+ECMAScript~\cite{ecma}, does not have any built-in
+functionality for I/O
+(we denote this language as |targetLangJS|).
 %
-(We denote this language as |targetLangJS|.)
-%
-Instead, when embedding a JavaScript engine, browser layout engines,
-such as Gecko, and server-side platforms, such as Node.js, expose APIs
-such as the DOM and filesystem as part of the runtime system.
+When JavaScript is embedded in web browser engines such as
+Gecko or Blink, or in server-side platforms such as Node.js, additional
+APIs such as the Document Object Model (DOM) or the file system
+get exposed as part of the runtime system.
 %
@@
 This example shows how our trusted monitor (left) is used to mediate
-communication between two tasks.}
+communication between two tasks for which IFC is enforced(left).}
 \end{figure}

### 2014-07-08 paper/extensions.tex
nits

@@
 %
-For simplicity, we do treat this, more-general class of schedulers;
+For simplicity, we do not treat this, more-general class of schedulers;
 doing so would require modifying our calculus to keep track of the

### 2014-07-08 paper/real.tex
nits

@@
 
-JavaScript as specified by
+JavaScript, as specified by
 ECMAScript~\cite{ecma}, does not have any built-in
@@
 
-We leverage contexts to implement |specLangJS seqf| for Node.js.
+\subsubsection{Server-side embedding for Node.js}
+
+Using contexts as the unit of isolation, we implemented
+|specLangJS seqf| for Node.js.
 %

### 2014-07-08 paper/extensions.tex
rearrange extensions as dicussed

--- 2014-07-07 paper/extensions.tex
@@
-\section{Extensions and Limitations}
+\section{Extensions}
 \label{sec:extensions}
+\label{sec:extensions:labeled}
 
-In this section we consider several extensions to our IFC system.
-%
-Specifically, we discuss how the specification language can be
-extended to consider other IFC-aware features (e.g., fine-grained
-labeled values), a static type system, or more complex scheduling
-policies.
-%
-When considering these extensions we also discuss some limitations
-of our approach.
-
-\subsection{IFC Language Features}
-\label{sec:extensions:labeled}
+%In this section we consider several extensions to our IFC system.
+%%
+%Specifically, we discuss how the specification language can be
+%extended to consider other IFC-aware features (e.g., fine-grained
+%labeled values), and talk about a static type system, as well as
+%more complex scheduling policies.
+%%
+%When considering these extensions we also discuss some limitations
+%of our approach.
 
@@
 %consider the addition of several labeled constructs to the abstract specification.
-Below we show how to extend the language with several such constructs,
-and highlight some other possible extensions as well.
+In this section we show how to extend the language with several such
+constructs.
 %
@@
 
-\paragraph{Labeled values}
+\subsection{Labeled values}
 %{
@@
 
-\paragraph{Labeled mutable references/variables/channels}
+\subsection{Labeled mutable references/variables/channels}
 %
@@
 
-\paragraph{Privileges}
-Decentralized IFC extends IFC with the decentralized label model of
-Myers and Liskov~\cite{myers:dlm} to allow for more general
-applications, including systems consisting of mutually distrustful
-parties.  In a decentralized system, a computation is executed with a
-set of \emph{privileges}, which, when exercised, allow the computation
-to declassify data (e.g., by lowering the current label).
-%
-Practical IFC systems
-(e.g.,~\cite{Zeldovich:2006, lio,
-Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
-implement many applications.
-%
-%Since both the LIO and SWAPI implementations already support such features,
-%we believe that extending our calculus to consider privileges is
-%straight forward.
-%
-The challenge with such an extension lies in the precise
-security guarantees that must be proved, which to the best of our
-knowledge is an open research problem.
-%
-%Addressing this problem is a natural direction for this work.
-
-\paragraph{Clearance}
+\subsection{Clearance}
 %
@@
 TODO: provide them in the appendix, and refer to them here.
+
+\subsection{Privileges}
+Decentralized IFC extends IFC with the decentralized label model of
+Myers and Liskov~\cite{myers:dlm} to allow for more general
+applications, including systems consisting of mutually distrustful
+parties.  In a decentralized system, a computation is executed with a
+set of \emph{privileges}, which, when exercised, allow the computation
+to declassify data (e.g., by lowering the current label).
+%
+Practical IFC systems
+(e.g.,~\cite{Zeldovich:2006, lio,
+  Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
+implement many applications.
+%
+%Since both the LIO and SWAPI implementations already support such features,
+%we believe that extending our calculus to consider privileges is
+%straight forward.
+%
+The challenge with such an extension lies in the precise
+security guarantees that must be proved, which to the best of our
+knowledge is an open research problem.
+
+Our implementation for Node.js and SWAPI both provide privileges, but
+we have not formalized this part any further.
+%
+%Addressing this problem is a natural direction for this work.
+
+\section{Limitations and Future Directions}
+
+In this section we state some limitations of the current system, and
+outline potential future directions to alleviate these limitations.
 

### 2014-07-08 paper/real.tex
node

@@
 %
-In Section~\ref{sec:retrofit}, however, we used only a simplified
-language as an example target language.
+Indeed, this work serves as the theoretical foundation for the
+JavaScript IFC systems built atop Node.js and Gecko layout engine.
 %
 In this section, we consider the application of our embedding to
-JavaScript, and two other real world target languages, Haskell, and C.
+JavaScript for these two platforms, and two other real world target
+languages, Haskell, and C.
 %
@@
 %
-When JavaScript is embedded in web browser engines such as
-Gecko or Blink, or in server-side platforms such as Node.js, additional
-APIs such as the Document Object Model (DOM) or the file system
-get exposed as part of the runtime system.
+When JavaScript is embedded in web browser engines, such as Google's
+Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
+additional APIs such as the Document Object Model (DOM) or the file
+system get exposed as part of the runtime system.
 %
@@
 separate OS-level threads.\footnote{
-  We, indeed, do this for the Gecko implementation when considering
-  Web Workers that run operate OS threads.
+  Indeed, the Gecko implementation of this work does this for Web
+  Workers that run operate OS threads~\cite{cowl}.
 }
@@
 %
-In particular, browser layout engines rely on the isolation of content
-from different origins (e.g., two iframes of different origins) to
+In particular, layout engines rely on the isolation of content from
+different origins (e.g., two iframes of different origins) to
 implement the \emph{same-origin policy}.
 %
-Since creating an OS thread for each iframe is expensive, both V8 and
-SpiderMonkey provide a means for running JavaScript code in isolation,
-on disjoint sub-heaps of the same OS thread.
+Since creating an OS thread for each iframe is expensive, both
+Google's V8 and Mozilla's SpiderMonkey provide a means for running
+JavaScript code in isolation, on disjoint sub-heaps of the same OS
+thread.
 %
-In V8, this unit of isolation is called a \emph{context}~\tocite{}, in
+In V8, this unit of isolation is called a \emph{context}~\tocite{}; in
 SpiderMonkey, it called a \emph{compartment}~\tocite{}.
@@
 (Gecko and Node.js expose features such as the DOM and
-filesystem by extending this global object.)
+file system by extending this global object.)
 %
+Naturally, our notion of a task for JavaScript directly corresponds to
+a context/compartment.
+%
+Below we describe some of the implementation details specific to
+Node.js and Gecko.
 
-\subsubsection{Server-side embedding for Node.js}
+\subsubsection{Server-side embedding: Node.js}
 
-Using contexts as the unit of isolation, we implemented
-|specLangJS seqf| for Node.js.
+We implemented |specLangJS seqf| for Node.js in the form of a module
+(library), which does not modify the Node.js or V8 code-base in any
+way.
 %
@@
 %
-Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
-the global object corresponding to the standard JavaScript library and
-our IFC primitives.
+In our formal treatement, |sandbox| is defined with |klone(tS) = tS0|,
+where |tS0| is the global object corresponding to the standard
+JavaScript library and our IFC primitives.
 
@@
 \end{figure}
+%
 As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
@@
 %
-While V8 provides a means for sharing objects between contexts that
-share a security token (in the case of Blink this is used by pages of
-the same origin), our API (conservatively) restricts the kinds of
-messages that can be exchanged.
+(This task is part of the trusted computing base (TCB) and has access
+to the full Node.js API.)
 %
-More concretely, and as mentioned in Section~\ref{sec:concrete}, we
+While V8 provides a means for sharing objects between contexts (used
+by same-origin contexts in Blink), our system conservatively restricts
+the kinds of messages that can be exchanged by tasks.
+%
+Concretely, and as mentioned in Section~\ref{sec:concrete}, we
 restrict |send| (and |sandbox|) to sending string values.
@@
 %
-However, our implementation is accompanied by a library that provides
+Our implementation, however, is accompanied by a library that provides
 a more flexible standard library, which, among other things,
@@
 
+\subsubsection{Client-side embedding: Gecko}
 \Red{HERE}

### 2014-07-08 paper/abstract.tex
jcmnew intro

--- 2014-03-02 paper/abstract.tex
@@
 \begin{abstract}
-    Many important security problems in JavaScript, including extension
-    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
-    mash-up security~\tocite{}, could be solved with a implementation
-    of information flow control.  However, designing an IFC system which
-    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
-    we formally describe a coarse-grained IFC system which fulfills this
-    criterion.  The key idea is that an efficient IFC system must not
-    depend too much on the details of the language it is integrated
-    with.  The result is a \emph{general} method for adding IFC to existing
-    languages which is \emph{indifferent} to the choice of language.
-    Additionally, we describe how to relate concrete implementations
-    with the IFC systems produced by our technique and show how various
-    proposed and existing IFC systems fit into our formal framework.
+Many important security problems in JavaScript, such as browser extension
+security, untrusted JavaScript libraries and
+safe integration of mutually distrustful websites (mash-ups), 
+may be effectively addressed using an efficient implementation
+of course-grained information flow control.
+Using JavaScript as a motivating and illustrative example, 
+we formally specify a coarse-grained IFC system that
+can be implemented non-intrusively in a variety of language contexts, 
+resulting in
+much greater implementation efficiency than previous finer-grained approaches.
+The main advance involves identifying isolation mechanisms
+that allow IFC to track interaction between program
+components whose internal operation is not tracked
+because the entire component has the same label.
+By presenting other language examples, we suggest that this 
+is a general method for adding IFC to existing
+languages,
+provided an appropriate isolation mechanism can be identified.
+We also describe how to relate optimized concrete implementations
+to the IFC systems produced by our technique.
 \end{abstract}

### 2014-07-08 paper/intro.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
jcmnew intro

@@
 
-Modern web content is rendered using a potentially large number of
-different components with differing provenance.
-Disparate and untrusting components may arise from browser
-extensions (whose JavaScript code runs alongside website
-code), web applications (with possibly untrusted third-party
-libraries), and mashups (which combine code and data from
-websites that may not even be aware of each other's existence.)
+The way modern web content is rendered, using a potentially large number of
+different components with differing provenance, illustrates the need for 
+general methods to track data provenance and use in complex software systems.
+Disparate and untrusting software components may arise from browser
+extensions whose JavaScript code runs alongside website
+code, web applications with possibly untrusted third-party
+libraries, and mashups which combine code and data from
+websites that may not even be aware of each other's existence.
 While just-in-time combination of untrusting components
@@
 extensions, libraries, and mashup components has been difficult,
-and in general effectively impossible.
+with no previous comprehensive principled solution.
 
 Information flow control (IFC) is a promising technique
-that provides security
+that provides confidentiality (and integrity, as desired)
 by tracking the flow of sensitive data through a system.
 Untrusted code is confined so that it cannot exfiltrate data, except as
-per an information flow policy.  Significant research has been devoted to
+permitted by an explicit information flow policy.  
+Significant research has been devoted to
 adding various forms of IFC to different kinds of programming languages
 and systems.  In the context of the web, however, there is a strong
-motivation to preserve the language JavaScript, and retrofit dynamic information
-flow control on top of it.  A key challenge in dynamic information
-flow control is implementation efficiency: when
-information flow is tracked at a fine-grained level,
-e.g., per value in the system, systems may incur
+motivation to preserve the language, JavaScript, and retrofit dynamic information
+flow control on top of it.  
+However, adding fine-grained IFC even to a simple language is
+non-trivial~\cite{hritcu2013testing} and 
+tracking fine-grained information flow for each
+value in the system may incur
 impractical runtime overhead~\cite{JSFlow}.
-%
-Moreover, the task of adding fine-grained IFC even to a simple language is
-non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
-such as JavaScript, this challenge becomes almost insurmountable.
 
-In the alternative \textit{coarse-grained} approach to IFC,
-a system is divided into relatively coarse computational units,
+In an alternative \textit{coarse-grained} approach to IFC we advance 
+in this paper, a system is divided into relatively coarse computational units,
 each with a single label dictating its security policy.
-Only
-communication between isolated computational units must be tracked.
+It is only necessary to track
+communication between isolated computational units.
 A recent system named SWAPI~\cite{swapi} adds IFC to the
@@
 
-A further benefit of the coarse-grained approach
-is that a single IFC design and semantics can be generalized
-to a large class of programming languages.
-Leveraging this insight, we define a general form of coarse-grained
-dynamic IFC and show how it can be combined with \emph{any} programming
-language conforming to a general semantic framework.
-At the core of our IFC system is a sandboxing construct that isolates
+We show how a coarse-grained approach suggested by
+SWAPI can be applied generally to the JavaScript language and 
+similarly generalized to a large class of programming languages
+that provide a suitable isolation mechanism.
+At the core of our coarse-grained IFC system is a sandboxing construct that isolates
 potentially sensitive computations, allowing them to
@@
 independent of the choice of specific target language.
-
-One challenge in the design of our system is that the semantics for the
+While the semantics for the
 retrofitted IFC language may not accurately correspond to the optimized
-implementation details of a particular target language.
-We discuss and partially address this issue
-by characterizing isomorphisms between the operational semantics of our
-defined language and a concrete implementation, showing that if this
-relationship holds, then non-interference in the abstract specification
-carries over to the concrete specification.
+implementation details of a particular target language, 
+we discuss and partially address this issue
+by characterizing isomorphisms that imply non-interference for the concrete specification.
 
@@
   notion of clearance. (Section~\ref{sec:extensions})
-  \item We informally relate our results to a monadic interpretation
-      of IFC which guided our design. (Section~\ref{sec:monad})     
 \end{itemize}
+
+The systems we have implemented allow and appropriately track
+external effects. For example, SWAPI treats XMLHttpRequest by
+wrapping the ``native'' unsafe code. 
+However, general treatment of external effects difficult and
+current information flow control systems suffer limitations.
+For instance, JPMail [A] re-implements primitives with external effects in Jif; 
+Paragon [B] internalizes external effects by wrapping the corresponding primitives
+to be IFC-aware [C]; JSFlow [25,26] manually wraps JavaScript primitives with external effects.
 
@@
 }
+
+\cut{DM had some very good comments on how to make this sound less
+  like a pitch for LIO. Outline for something more compelling (not
+  necessarily in this order):
+\begin{itemize}
+  \item Motivate IFC
+  \item Coarse grained IFC is easy
+  \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
+  \item We have the right API and it's language-agnostic; proof is also language independent
+  \item You can ``drop it in''
+\end{itemize}
+}

### 2014-07-08 paper/abstract.tex
Revert "jcmnew intro"
This reverts commit 0888d98c8975a3bc3aaef3250801c285cfadedd4.

--- 2014-03-02 paper/abstract.tex
@@
     of information flow control.
-We present a coarse-grained IFC system that
+We formally specify a coarse-grained IFC system that
 can be implemented  non-intrusively, resulting in
@@
 depend too much on the details of the programming language used.
-We thus present a \emph{general} method for adding IFC to existing
+Thus, we have a \emph{general} method for adding IFC to existing
 languages that is largely \emph{indifferent} to the choice of language.

### 2014-07-08 paper/intro.tex
Revert "jcmnew intro"
This reverts commit 0888d98c8975a3bc3aaef3250801c285cfadedd4.

--- 2014-03-02 paper/intro.tex
@@
 \label{sec:intro}
+\Red{DM had some very good comments on how to make this sound less
+  like a pitch for LIO. Outline for something more compelling (not
+  necessarily in this order):
+\begin{itemize}
+  \item Motivate IFC
+  \item Coarse grained IFC is easy
+  \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
+  \item We have the right API and it's language-agnostic; proof is also language independent
+  \item You can ``drop it in''
+\end{itemize}
+}
 
@@
   notion of clearance. (Section~\ref{sec:extensions})
-  \item We informally relate our results to a monadic interpretation
-      of IFC which guided our design. (Section~\ref{sec:monad})     
 \end{itemize}

### 2014-07-08 paper/retrofit.tex
Fix up retrofit
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 implementation.  In this paper, we advocate applying coarse-grained
-labeling~\cite{Zeldovich:2006, lio} to its extreme: our starting point
+labeling~\cite{Zeldovich:2006, lio} at its most extreme: our starting point
 is multiple instances of completely isolated language runtimes or \emph{tasks}, with
@@
 with access to hardware privilege separation, systems along these lines
-are far more easily implementable and require minimal semantic changes.
+are far more easily implementable and require fewer semantic changes.
 
-Why is this setting more interesting than ``traditional
-coarse-grained information flow control system on isolated
-threads?''  First, although completely separate tasks
-are semantically easy to reason about, real-world implementations often blur the
-lines between tasks in the name of efficiency.  Characterizing what optimizations
-are permissible is a problem we address in Section~\ref{sec:concrete}, and
-it is quite subtle, since removing transitions from the operational semantics
-of a language can in general break non-interference.
-Second, even though the underlying
-semantic model involves communicating tasks, these tasks can be coordinated
-together in ways that simulate traditional features in monolithic languages.
-In fact, it is a very useful design tool for discovering what variants of the
-features are permissible and which are not.
+What distinguishes this setting from previous coarse-grained IFC
+systems?
+%
+First, even though the underlying semantic model involves communicating
+tasks, these tasks can be coordinated together in ways that simulate
+traditional features in monolithic languages.  In fact, simulating
+features in this way is a very useful \emph{design tool} for discovering
+what variants of the features are permissible and which are not.
+%
+Second, although completely separate tasks are semantically easy to
+reason about, real-world implementations often blur the lines between
+tasks in the name of efficiency (Section~\ref{sec:concrete}).
+Characterizing what optimizations are permissible is subtle, since
+removing transitions from the operational semantics of a language can
+break non-interference.
 
-A very simple example is a low security task sending a high security
+To give a simple example, here is a low security task sending a high security
 task a mutable reference:
@@
     & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
-    & |in TI (send (IT i) getLabel (IT (ref true)))|
+    & |in TI (send (IT i) l (IT (ref true)))|
 \end{align*}
@@
 |sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}) for a
-message, and then \textbf{send}s the task a mutable reference to |(ref
-true)|.  If this operation actually shared the mutable cell, this cell
+message, and then \textbf{send}s the task a mutable reference |(ref
+true)| which is labeled $l$.  If this operation actually shared the mutable cell, this cell
 could be used to violate information flow control, by leaking
 information from the high security task to the low security task.
-When working with
-isolated tasks which each have their own heaps, the isolation is obviously true:
-the sandboxed task receives a dangling pointer.
 
-While this is a very simple example, we can still ask: given the
-obviously safe formulation with separate heaps, can this fact be useful
-for showing the safety of a semantics which only has a single heap
-(we answer this question positively in Section~\ref{sec:single-heap})?
-Furthermore, the na\"ive
-semantics violates expectations about how inter-task communication
-works on a shared heap: it strongly suggests, for example, that which
-types of data may be passed between tasks should be restricted (for
-example, in JavaScript, one might only allow JSON objects to be passed
-between tasks, rather than general object structures).
+This example demonstrates both of our design principles.  When working
+with isolated tasks, each of which have their own heaps, the isolation
+is obviously true: the sandboxed task receives a dangling pointer.  From
+there, we can further ask: given the obviously safe formulation with
+separate heaps, can this fact be useful for showing the safety of a
+semantics which only has a single heap (we answer this question
+positively in Section~\ref{sec:single-heap})?  Finally, this na\"ive
+semantics violates expectations about how inter-task communication works
+on a shared heap, and strongly suggests one should restrict the types of
+data which may be passed between tasks (for example, in JavaScript, one
+might only allow JSON objects to be passed between tasks, rather than
+general object structures).
 

### 2014-07-08 paper/real.tex
nit
wip, pulling

@@
 This example shows how our trusted monitor (left) is used to mediate
-communication between two tasks for which IFC is enforced(left).}
+communication between two tasks for which IFC is enforced (right).}
 \end{figure}
@@
 |send|/|recv|.
+
+While the described system implements |specLangJS seqf|, Node.js
+applications may require access to the file system, HTTP server, HTTP
+client, etc.
 
@@
 
+\Red{TODO: note that if the target language allows inspecting if
+  result is exception we can implement Breeze's NAV (vs. just
+propagating)}
+
 \subsection{C}

### 2014-07-08 paper/intro.tex

@@
 motivation to preserve the language JavaScript, and retrofit dynamic information
-flow control on top of it.  A key challenge in dynamic information
-flow control is implementation efficiency: when
-information flow is tracked at a fine-grained level,
-e.g., per value in the system, systems may incur
-impractical runtime overhead~\cite{JSFlow}.
+flow control on top of it.
+
+Systems that track information flow at a fine-grained level, e.g. per
+value in the system, offer great flexibility.  However, they
+require deep integration with the programming language and modify
+the semantics in non-trivial ways.  This makes fine-grained systems
+less suitable in contexts where preserving an existing language
+is important.
 %
@@
 communication between isolated computational units must be tracked.
-A recent system named SWAPI~\cite{swapi} adds IFC to the
-browser by identifying \emph{web workers} as an existing computational
-unit.  Communication between workers is mediated using
-IFC to ensure non-interference, preventing sensitive workers from
-influencing the computation of less sensitive workers.
+%A recent system named SWAPI~\cite{swapi} adds IFC to the
+%browser by identifying \emph{web workers} as an existing computational
+%unit.  Communication between workers is mediated using
+%IFC to ensure non-interference, preventing sensitive workers from
+%influencing the computation of less sensitive workers.
 This coarse-grained approach provides a number of advantages:
-(1) reduced runtime overhead because checks need only
-be performed at isolation boundaries, (2) minimal changes to an
-existing programming language when adding IFC, which (3) allows
-the reuse of existing programs.  Finally, (4) associating
+(1) minimal changes to an
+existing programming language when adding IFC, which (2) allows
+the reuse of existing programs.  Furthermore, (3)
+reduced runtime overhead because checks need only
+be performed at isolation boundaries, compared to fine-grained
+systems were the runtime overhead can be impractical~\cite{JSFlow}.
+Finally, (4) associating
 a single security label with the entire computational unit simplifies
@@
 to a large class of programming languages.
-Leveraging this insight, we define a general form of coarse-grained
-dynamic IFC and show how it can be combined with \emph{any} programming
-language conforming to a general semantic framework.
+Leveraging this insight, we define a form of coarse-grained
+dynamic IFC and show how it can be combined with any programming
+language for which external effects can be controlled.
 At the core of our IFC system is a sandboxing construct that isolates
@@
 communicate only through clearly specified interfaces.
-Using the Matthews-Findler approach~\cite{Matthews:2007:OSM:1190216.1190220}
+Using an approach by Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220}
 for combining operational semantics,
@@
 relationship holds, then non-interference in the abstract specification
-carries over to the concrete specification.
+carries over to the concrete implementation.
 
@@
   \item We give formal semantics for a core coarse-grained
-  information flow control language.
+  information flow control language free of non-IFC constructs.
   We then show how a large class of target languages can be combined
@@
   non-interference. (Section~\ref{sec:retrofit})
+  \item We provide a proof technique to show the non-interference
+  of a concrete semantics for a potentially optimized IFC language
+  by means of an isomorphism, and show a class of restrictions on
+  the IFC language that preserves non-interference. (Section~\ref{sec:formal}
+  and~\ref{sec:concrete})
+  \item We have implemented an IFC system based on these semantics
+  for Node.js, and we connect our formalism to another implementation
+  based on this work
+  for client-side JavaScript in Gecko~\cite{swapi}.
+  Furthermore, we outline an implementation for the C programming
+  language.
+  (Section~\ref{sec:real})
 %  \item We show how to extend the Matthews-Findler method from just
@@
 %  but may be collections of threads executing nondeterministically.
-  \item We provide a proof technique to show the non-interference
-  of a concrete semantics for a potentially optimized IFC language
-  by means of an isomorphism, and show a class of restrictions on
-  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
-  \item We connect our formal semantics to real implementations of
-  coarse-grained IFC systems for JavaScript and Haskell, and explain
-  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
-  \item We briefly describe ways to enrich the core IFC language with
-  more advanced concepts such as labeled values, privileges, or a
+  \item We describe ways to enrich the core IFC language with
+  more advanced concepts such as labeled values, labeled references, or a
   notion of clearance. (Section~\ref{sec:extensions})

### 2014-07-08 paper/real.tex
locking

@@
 
-While the described system implements |specLangJS seqf|, Node.js
+\Red{LOCK:deian}
+While the described system implements |specLangJS seqf|, server-side
 applications may require access to the file system, HTTP server, HTTP
 client, etc.
+%
+Unfortunately, our formalism does not capture such external effects
+and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
+%
+Hence, we instead implement libraries such as the file system as
+message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
+in Figure~\ref{fig:node}) and main Node.js task taht 
+%
+This is in part because how external effects 
+%
+Hence, our implementation of l
+%This is, in part, because the handling of such effect
 

### 2014-07-08 paper/real.tex
wip external

@@
 %
-Hence, we instead implement libraries such as the file system as
+We, instead, implement libraries such as a labeled file system as
 message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
-in Figure~\ref{fig:node}) and main Node.js task taht 
+in Figure~\ref{fig:node}) and the main Node.js task that implements
+our IFC monitor.\footnote{
+  Importantly, our libraries provide mostly-identical interfaces to
+  the standard Node.js libraries, hiding the underlying
+  message-passing implementations.
+}
 %
-This is in part because how external effects 
+This task is trusted to ensures that, for instance, labels are
+propagated to files and that tasks are tainted when reading sensitive
+files, as to preserve non-interference.
 %
-Hence, our implementation of l
-%This is, in part, because the handling of such effect
+\Red{go into how this is app specific and it's not a huge limitation
+  that our system does not capture this; e.g., even for fs semantics
+  can vary: are labels serialized or not. later let's us change policy
+more easily, the other is better for persistence}
 

### 2014-07-08 paper/intro.tex

@@
 \label{sec:intro}
-\Red{DM had some very good comments on how to make this sound less
-  like a pitch for LIO. Outline for something more compelling (not
-  necessarily in this order):
-\begin{itemize}
-  \item Motivate IFC
-  \item Coarse grained IFC is easy
-  \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
-  \item We have the right API and it's language-agnostic; proof is also language independent
-  \item You can ``drop it in''
-\end{itemize}
-}
+%   \Red{DM had some very good comments on how to make this sound less
+%     like a pitch for LIO. Outline for something more compelling (not
+%     necessarily in this order):
+%   \begin{itemize}
+%     \item Motivate IFC
+%     \item Coarse grained IFC is easy
+%     \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
+%     \item We have the right API and it's language-agnostic; proof is also language independent
+%     \item You can ``drop it in''
+%   \end{itemize}
+%   }
 
@@
 and systems.  In the context of the web, however, there is a strong
-motivation to preserve the language JavaScript, and retrofit dynamic information
-flow control on top of it.
+motivation to preserve JavaScript's semantics while retrofitting it with dynamic information
+flow control.
 
-Systems that track information flow at a fine-grained level, e.g. per
-value in the system, offer great flexibility.  However, they
+One approach to information flow control is fine-grained tracking,
+which offers great flexibility.
+However, these systems
 require deep integration with the programming language and modify
@@
 
-A further benefit of the coarse-grained approach
-is that a single IFC design and semantics can be generalized
-to a large class of programming languages.
-Leveraging this insight, we define a form of coarse-grained
-dynamic IFC and show how it can be combined with any programming
-language for which external effects can be controlled.
-At the core of our IFC system is a sandboxing construct that isolates
-potentially sensitive computations, allowing them to
-communicate only through clearly specified interfaces.
-Using an approach by Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220}
-for combining operational semantics,
-we formally state and prove non-interference guarantees that are
-independent of the choice of specific target language.
+In this paper, we take coarse-grained labeling~\cite{Zeldovich:2006,
+lio} to its logical extreme: an information flow control system should
+be thought of as multiple instances of completely isolated language
+runtimes or \emph{tasks}, with information flow control applied to
+inter-task communication.  We describe a formal system in which an IFC
+system can be designed once and then applied to any programming language
+which has control over external effects (e.g., JavaScript or C with
+access to hardware privilege separation).  We formalize this system
+using an approach by
+Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
+operational semantics and prove non-interference guarantees
+that are independent of the choice of specific target language.
 
-One challenge in the design of our system is that the semantics for the
-retrofitted IFC language may not accurately correspond to the optimized
-implementation details of a particular target language.
-We discuss and partially address this issue
+What distinguishes this setting from previous coarse-grained IFC
+systems?
+%
+First, even though the underlying semantic model involves communicating
+tasks, these tasks can be coordinated together in ways that simulate
+traditional features in monolithic languages.  In fact, simulating
+features in this way is a very useful \emph{design tool} for discovering
+what variants of the features are permissible and which are not.
+%
+Second, although completely separate tasks are semantically easy to
+reason about, real-world implementations often blur the lines between
+tasks in the name of efficiency.
+Characterizing what optimizations are permissible is subtle, since
+removing transitions from the operational semantics of a language can
+break non-interference.  We partially address this issue
 by characterizing isomorphisms between the operational semantics of our
@@
   \item We give formal semantics for a core coarse-grained
-  information flow control language free of non-IFC constructs.
+  dynamic information flow control language free of non-IFC constructs.
   We then show how a large class of target languages can be combined

### 2014-07-08 paper/retrofit.tex
wip, pulling

@@
 \label{sec:retrofit}
+
+Before moving on to the formal treatment of our system, we'd like to give
+a brief primer of information flow control and describe some example programs
+in our system, emphasizing the parallel between their implementation
+in a multi-task setting, and the traditional, ``monolithic'' programming
+language feature they simulate.
 
@@
 a property called \emph{non-interference}.
+%
+In our coarse-grained floating-label approach, labels are associated with tasks.
+%
+The task label---we refer to the label of the currently executing task as the
+\emph{current label}---serves to protect everything in the task's scope;
+all data in a task shares this common label.
 
-Supporting fine-grained labeling of data in a programming language often
-requires extremely intrusive modifications to its semantics and
-implementation.  In this paper, we advocate applying coarse-grained
-labeling~\cite{Zeldovich:2006, lio} at its most extreme: our starting point
-is multiple instances of completely isolated language runtimes or \emph{tasks}, with
-information flow control applied between their communication.  For
-languages which are implemented with isolation, such as JavaScript or C
-with access to hardware privilege separation, systems along these lines
-are far more easily implementable and require fewer semantic changes.
-
-What distinguishes this setting from previous coarse-grained IFC
-systems?
-%
-First, even though the underlying semantic model involves communicating
-tasks, these tasks can be coordinated together in ways that simulate
-traditional features in monolithic languages.  In fact, simulating
-features in this way is a very useful \emph{design tool} for discovering
-what variants of the features are permissible and which are not.
-%
-Second, although completely separate tasks are semantically easy to
-reason about, real-world implementations often blur the lines between
-tasks in the name of efficiency (Section~\ref{sec:concrete}).
-Characterizing what optimizations are permissible is subtle, since
-removing transitions from the operational semantics of a language can
-break non-interference.
-
-To give a simple example, here is a low security task sending a high security
-task a mutable reference:
+For our first example, here is a program which spawns a new isolated task,
+and then sends it a mutable reference:
 \begin{align*}
@@
 For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
-|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}) for a
+|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
 message, and then \textbf{send}s the task a mutable reference |(ref
-true)| which is labeled $l$.  If this operation actually shared the mutable cell, this cell
-could be used to violate information flow control, by leaking
-information from the high security task to the low security task.
+true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
+could be used to violate information flow control if the tasks had differing labels.
 
-This example demonstrates both of our design principles.  When working
-with isolated tasks, each of which have their own heaps, the isolation
-is obviously true: the sandboxed task receives a dangling pointer.  From
+While simple, this example demonstrates some of our general design principles.  When these
+constructs are treated as isolated tasks, each of which have their own heaps, it
+is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  From
 there, we can further ask: given the obviously safe formulation with
 separate heaps, can this fact be useful for showing the safety of a
-semantics which only has a single heap (we answer this question
-positively in Section~\ref{sec:single-heap})?  Finally, this na\"ive
+semantics which only has a single heap? (We answer this question
+positively in Section~\ref{sec:single-heap}.)  Finally, this na\"ive
 semantics violates expectations about how inter-task communication works
-on a shared heap, and strongly suggests one should restrict the types of
+on a shared heap and strongly suggests one should restrict the types of
 data which may be passed between tasks (for example, in JavaScript, one
@@
 
-Before moving on to the formal treatment of our system, we'd like to give
-two more examples of language features which have an interesting interpretation
-when viewed in the setting of multiple tasks.
+Here are two more examples of language features which have an
+interesting interpretation when viewed in the setting of multiple tasks.
 
@@
 stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
-enforcing a stack discipline.  This is the trickiest part of the feature: care must be taken to ensure that information doesn't leak when
-the label is lowered. In fact, systems with this feature generally only
+enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
+the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
 achieve termination-insensitive non-interference: if the high secrecy
@@
 always evaluates to |true|, regardless of the value of |te|.
-\Red{TODO: note that if the target language allows inspecting if
-  result is exception we can implement Breeze's NAV (vs. just
-propagating)}
 
@@
 discuss them in more detail.
-
-In our coarse-grained floating-label approach, labels are associated with tasks.
 %
-The task label---we refer to the label of the currently executing task as the
-\emph{current label}---serves to protect everything in the task's scope;
-all data in a task shares this common label.
-%
-Hence before performing a read or a write, the IFC monitor inspects the
-current label to decide whether the operation is permitted.
+To enforce labels, the IFC monitor inspects the
+current label  before performing a read or a write to decide whether the operation is permitted.
 %
@@
 \[ |recvf ix1 ix2 ie1 ie2| \]
-binds the message and the senders task identifier
+binds the message and the sender's task identifier
 to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.

### 2014-07-08 paper/real.tex
Pass over parts of real.tex

@@
 In the introduction, we stated that the original motivation behind
-developing this embedding was in order to formally specify a
+this work was to formally specify a
 coarse-grained information flow control language for JavaScript.
 %
-Indeed, this work serves as the theoretical foundation for the
-JavaScript IFC systems built atop Node.js and Gecko layout engine.
-%
-In this section, we consider the application of our embedding to
-JavaScript for these two platforms, and two other real world target
-languages, Haskell, and C.
+Indeed, our formalism serves as the theoretical foundation for two
+IFC systems for JavaScript, built on top of Node.js as well as
+the web browser engine Gecko.
+
+In this section, we describe these two implementations.  Furthermore,
+we consider how our formalism could be applied to the C programming
+language, and connect it to a previous IFC system for Haskell.
 %
 Our goal is to show the flexibility of the embedding in settings with
-vastly different features and properties, as well as discuss the
+vastly different properties, as well as to discuss the
 semantic gap that must be overcome in some cases to apply our formalism
@@
 ECMAScript~\cite{ecma}, does not have any built-in
-functionality for I/O
-(we denote this language as |targetLangJS|).
+functionality for I/O.
+%(we denote this language as |targetLangJS|).
 %
-When JavaScript is embedded in web browser engines, such as Google's
-Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
-additional APIs such as the Document Object Model (DOM) or the file
-system get exposed as part of the runtime system.
-%
-In a similar manner, we can directly implement the embedded language
-|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
-of the runtime and running multiple instances of the JavaScript VM in
-separate OS-level threads.\footnote{
-  Indeed, the Gecko implementation of this work does this for Web
-  Workers that run operate OS threads~\cite{cowl}.
-}
+For this language, which we denote by |targetLangJS|, the IFC system
+|specLangJS roundrobinf| can be implemented by exposing IFC primitives
+to JavaScript as part of the runtime, and running multiple instances
+of the JavaScript virtual machine in separate OS-level threads.
 %
@@
 %
-(Consider, for instance, a server-side web application that wishes to
-create a new task for each HTTP request.)
+For instance, consider a server-side web application that
+creates a new task for each HTTP request.  The overhead would
+quickly become impractical.
 
 However, this issue of performance and JavaScript isolation is not
-unique to our work. 
-%
-In particular, layout engines rely on the isolation of content from
+unique to our work, and has been solved by browser engines,
+which
+rely on the isolation of content from
 different origins (e.g., two iframes of different origins) to
-implement the \emph{same-origin policy}.
+implement the same-origin policy.
 %
@@
 Google's V8 and Mozilla's SpiderMonkey provide a means for running
-JavaScript code in isolation, on disjoint sub-heaps of the same OS
-thread.
+JavaScript code in isolation in a single OS thread,
+on disjoint sub-heaps.
 %
 In V8, this unit of isolation is called a \emph{context}~\tocite{}; in
-SpiderMonkey, it called a \emph{compartment}~\tocite{}.
+SpiderMonkey, it is called a \emph{compartment}~\tocite{}.
 %
@@
 %
-(Gecko and Node.js expose features such as the DOM and
-file system by extending this global object.)
-%
 Naturally, our notion of a task for JavaScript directly corresponds to
 a context/compartment.
-%
-Below we describe some of the implementation details specific to
-Node.js and Gecko.
+
+When JavaScript is embedded in web browser engines, such as Google's
+Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
+additional APIs such as the Document Object Model (DOM) or the file
+system get exposed as part of the runtime system.
+These features are exposed by extending the global object, just like
+for the standard library.  For this reason, it is easy to modify
+these systems to remove arbitrary external effects when implementing
+an IFC system, and reintroducing important effects in a safe manner.
 
@@
 
-We implemented |specLangJS seqf| for Node.js in the form of a module
+We have implemented |specLangJS seqf| for Node.js in the form of a module
 (library), which does not modify the Node.js or V8 code-base in any
@@
 contexts whose global object only contains the standard JavaScript
-library and our IFC primitives (|send|, |sandbox|, etc.).
+library as well as our IFC primitives (such as |send| and |sandbox|).
 %
@@
 %
-In our formal treatement, |sandbox| is defined with |klone(tS) = tS0|,
+In our formal treatement, |sandbox| is defined with |ap klone tS = tS0|,
 where |tS0| is the global object corresponding to the standard
@@
 %
-As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
-by the trusted library code (the main Node.js context), that tracks
-the current label, messages, etc. of each task.
-%
-(This task is part of the trusted computing base (TCB) and has access
-to the full Node.js API.)
-%
-While V8 provides a means for sharing objects between contexts (used
-by same-origin contexts in Blink), our system conservatively restricts
-the kinds of messages that can be exchanged by tasks.
-%
-Concretely, and as mentioned in Section~\ref{sec:concrete}, we
-restrict |send| (and |sandbox|) to sending string values.
+All IFC primitives are mediated by the trusted library code (executing
+as the main Node.js context), which tracks the current label, messages,
+etc.\ of each task.  An example for |send|/|recv| is shown in
+Figure~\ref{fig:node}.
+
+%While V8 provides a means for sharing any object between contexts (used
+%by same-origin contexts in Blink),
+Our system conservatively restricts
+the kinds of messages that can be exchanged by tasks by
+only allowing string values to be exchanged via |send| (and |sandbox|).
 %
 In our formalization, this amounts to restricting the IFC language rule
-for |send| such that only strings can be shared:
+for |send| in the following way:
 %{
@@
 %
-Our implementation, however, is accompanied by a library that provides
-a more flexible standard library, which, among other things,
+For convenience, we have implemented a library that provides
+more flexible primitives, which, among other things,
 automatically marshalls JSON objects to/from strings on each
@@
 C programs are able to execute arbitrary (machine) code, access
-arbitrary memory, and perform arbitrary syscalls.
+arbitrary memory, and perform arbitrary system calls.
 %
@@
 %
-In addition, ring protection could be used to intercept syscalls performed by
+In addition, ring protection could be used to intercept system
+calls performed by
 a task and only permit those corresponding to our IFC language (such as
@@
 can be interpreted in the following way: calling from the target
-language to the IFC language corresponds to invoking a syscall.
+language to the IFC language corresponds to invoking a system call.
 %
-Creating a new task with the |sandbox| syscall corresponds to
-\emph{forking} a process.  Here, page tables limit what memory
-a task can access: we can ensure there will be no memory (effectively
-defining |klone(tS)
+Creating a new task with the |sandbox| system call corresponds to
+\emph{forking} a process.  Using page tables we can ensure that
+there will be no shared memory
+(effectively
+defining |ap klone tS
 = tS0|, where |tS0| is the set of pages necessary to bootstrap a
@@
 %
-Since C is not memory safe, conditions on these syscalls are
+Since C is not memory safe, conditions on these system calls are
 meaningless.
+
+We leave an actual implementation of an IFC system for C as
+future work.

### 2014-07-08 paper/abstract.tex
Fix up abstract
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

--- 2014-03-02 paper/abstract.tex
@@
     of information flow control.
-We present a coarse-grained IFC system that
+We formally specify a coarse-grained dynamic IFC system that
 can be implemented non-intrusively, resulting in
 much greater implementation efficiency than previous finer-grained approaches.
-The central concept is an isolation mechanism whose operation does not
-depend too much on the details of the programming language used.
-We thus present a \emph{general} method for adding IFC to existing
-languages that is largely \emph{indifferent} to the choice of language.
-Additionally, we describe how to relate optimized concrete implementations
-to the IFC systems produced by our technique and show how various
-proposed and existing IFC systems conform to our formal framework
-and therefore enjoy the semantic properties we prove.
+The central idea is that an IFC system should model
+a set of communicating isolated language runtimes.
+The result is a general method for adding IFC to existing
+languages that is largely indifferent to the choice of language.
+We describe how this methodology offers design principles for
+the construction of information flow control systems in more
+traiditional settings, as well as compositional proofs for optimized
+concrete implementations of IFC systems, which can be shown to
+have interference by relating them to their fully isolated variants.
 \end{abstract}

### 2014-07-08 paper/intro.tex
minor intro change
Space smithing
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-What distinguishes this setting from previous coarse-grained IFC
-systems?
+There are a number of points that distinguish this setting from
+previous coarse-grained IFC systems.
 %
@@
 tasks, these tasks can be coordinated together in ways that simulate
-traditional features in monolithic languages.  In fact, simulating
-features in this way is a very useful \emph{design tool} for discovering
+features of traditional languages.
+%
+In fact, simulating
+features in this way is a useful \emph{design tool} for discovering
 what variants of the features are permissible and which are not.
@@
 by characterizing isomorphisms between the operational semantics of our
-defined language and a concrete implementation, showing that if this
+abstract language and a concrete implementation, showing that if this
 relationship holds, then non-interference in the abstract specification

### 2014-07-08 paper/intro.tex
More space smithing
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
   with this IFC language and prove that the result provides
-  non-interference. (Section~\ref{sec:retrofit})
+  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
   \item We provide a proof technique to show the non-interference
   of a concrete semantics for a potentially optimized IFC language
-  by means of an isomorphism, and show a class of restrictions on
-  the IFC language that preserves non-interference. (Section~\ref{sec:formal}
-  and~\ref{sec:concrete})
+  by means of an isomorphism and show a class of restrictions on
+  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
   \item We have implemented an IFC system based on these semantics

### 2014-07-08 paper/retrofit.tex
Minor edits
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 Here are two more examples of language features which have an
-interesting interpretation when viewed in the setting of multiple tasks.
+interesting interpretation when interpreted as task communication.
 
@@
 Figure~\ref{fig:toLabeled}.
-However, this is not enough: in a stack discipline, one generally
+There is one more ingredient: in a stack discipline, one generally
 expects stack entries to be processed in order, rather than in parallel
@@
 the task queue corresponds to a specific \emph{scheduling policy} of
-these tasks.  The recasting of the problem to one of scheduling
-highlights the essential difference between termination-insensitive and
-termination-sensitive non-interference, and we will show how different
+these tasks.  In fact, the choice of scheduling here is the essential difference that
+determines whether or not one can prove termination-insensitive or
+termination-sensitive non-interference. We will show how different
 scheduling policies give different security guarantees.
@@
 Another language feature that has caused difficulty for
-many information flow control systems is exceptions handling,
+many information flow control systems is exception handling
 when built on top of this stack discipline.

### 2014-07-08 paper/rebuttal.txt
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 we have implemented do not deal with external effects: e.g.
-XMLHttpRequest as used in SWAPI essential wraps the "native" unsafe
+XMLHttpRequest as used in COWL essential wraps the "native" unsafe
 code. However, the treatment of external effects is very much
@@
 
-It's worth stating that we did not simply shoe-horn SWAPI and LIO into
+It's worth stating that we did not simply shoe-horn COWL and LIO into
 a "unified framework".  While our language uses ideas from LIO and
-SWAPI, we note that the current versions of these systems coevolved
+COWL, we note that the current versions of these systems coevolved
 with the concepts in the paper.  For instance, in LIO [53] (and Breeze
@@
 
-As reviewer 3 points out, the reference about SWAPI does not include
+As reviewer 3 points out, the reference about COWL does not include
 an URL.  It is available at http://deian.net/swapi.pdf and currently
@@
 
-Reviewer 3 asks about the values sent across channels in SWAPI.  For
+Reviewer 3 asks about the values sent across channels in COWL.  For
 simplicity, we require them to be strings in the paper, thought any

### 2014-07-08 paper/extensions.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 %%
-For example, SWAPI provides a labeled version of the XHR object, while
+For example, COWL provides a labeled version of the XHR object, while
 LIO implements a labeled file system, used in server-side web
@@
 Full details with formal reduction rules are provided
-in \appendixext{}, but omitted here for space reasons.
+in \appendixextfirst{}, but omitted here for space reasons.
 %}
@@
 %
-Systems like LIO, SWAPI, and Breeze additionally provide a discretionary access
+Systems like LIO, COWL, and Breeze additionally provide a discretionary access
 control (DAC) mechanism---called \emph{clearance}---at the language
@@
 %
-%Since both the LIO and SWAPI implementations already support such features,
+%Since both the LIO and COWL implementations already support such features,
 %we believe that extending our calculus to consider privileges is
@@
 
-Our implementation for Node.js and SWAPI both provide privileges, but
+Our implementation for Node.js and COWL both provide privileges, but
 we have not formalized this part any further.
@@
 This latter approach of wrapping unsafe primitives is, for example,
-used in SWAPI to allow for controlled network communication.
+used in COWL to allow for controlled network communication.
 %

### 2014-07-08 paper/jcm.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 taking ECMAScript as the target language and combining it with our IFC
-language should produce the formal semantics for SWAPI.  In this
+language should produce the formal semantics for COWL.  In this
 presentation, we use a simple, untyped lambda calculus with mutable
@@
 Two of the systems we describe have been implemented: the Haskell
-system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
+system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
 implementation of the IFC system for C to future work.
@@
 
-We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
+We describe COWL~\cite{swapi}, an implementation of this system for JavaScript
 (which we here denote by \ensuremath{\Red{\lambda_{\text{JS}}}}).
@@
 separate OS-level threads.\footnote{
- The Firefox implementation of SWAPI also considers the case where
+ The Firefox implementation of COWL also considers the case where
  tasks share the JavaScript runtime (and are cooperatively scheduled
@@
 %
-In SWAPI, the IFC language functionality is implemented in the JS
+In COWL, the IFC language functionality is implemented in the JS
 runtime much like browser layout engines implement the DOM, and expose
@@
 %
-Thus, the SWAPI implementation provides an IFC version of
+Thus, the COWL implementation provides an IFC version of
 \texttt{postMessage}, defined in terms of \ensuremath{\mathbf{send}}, that additionally
@@
 %
-As suggested by our formal semantics, SWAPI can directly leverage these
+As suggested by our formal semantics, COWL can directly leverage these
 mechanisms to implement the semantics of \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})}
@@
 %
-To address this, SWAPI additionally uses content security policy (CSP) and
+To address this, COWL additionally uses content security policy (CSP) and
 (iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
@@
 %% \Red{
-%% EZY:  This seems like useless detail about the SWAPI implementation
+%% EZY:  This seems like useless detail about the COWL implementation
 %% that is not relevant to this paper.
@@
 %% %
-%% Hence SWAPI only enforces IFC, and thus restricts external effects,
+%% Hence COWL only enforces IFC, and thus restricts external effects,
 %% when the JS code uses the new API.\footnote{
@@
 %% %
-%% Moreover, rather than disallowing all external effects, SWAPI allows
+%% Moreover, rather than disallowing all external effects, COWL allows
 %% controlled network communication by leveraging the fact that web
@@
 %
-For example, SWAPI provides a labeled version of the XHR object, while
+For example, COWL provides a labeled version of the XHR object, while
 LIO implements a labeled file system, use in server-side web
@@
 %
-Since both the LIO and SWAPI implementations already support such features,
+Since both the LIO and COWL implementations already support such features,
 we believe that extending our calculus to consider privileges is
@@
 %
-LIO, SWAPI, and Breeze additionally provide a discretionary access
+LIO, COWL, and Breeze additionally provide a discretionary access
 control mechanism---called \emph{clearance}---at the language

### 2014-07-08 paper/real.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 %% Two of the systems we describe have been implemented: the Haskell
-%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
+%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
 %% implementation of the IFC system for C to future work.
@@
 %
-Thus, the SWAPI implementation provides an IFC version of
+Thus, the COWL implementation provides an IFC version of
 \texttt{postMessage}, defined in terms of |send|, that additionally
@@
 %
-As suggested by our formal semantics, SWAPI can directly leverage these
+As suggested by our formal semantics, COWL can directly leverage these
 mechanisms to implement the semantics of |specLangJS roundrobinf|

### 2014-07-08 paper/concrete.tex
OK I think I socked the new intro
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Making a pass.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-\Red{TODO: intuition for why weakly is enough for TINI}
+Only weak isomorphism is necessary for TINI. Intuitively, this is because
+is not necessary to back-translate reduction sequences in $L'$ to
+$L$; by the definition of TINI, we have both reduction sequences in $L$
+by assumption.
 
@@
 
-This complicated behavior is counter to our initial motivation
-of implementing a single heap for efficiency.
+Isomorphism demands we implement this convoluted behavior,
+despite our initial motivation of a more efficient implementation.
 
@@
 
-\subsection{IFC Language with a Single Heap}
+\subsection{IFC Language with a Single Heap}\label{sec:single-heap}
 
-We are now ready to make our single heap IFC language precise and
+As a concrete instantiation of this proof technique, we show
+how to make our single heap IFC language precise and
 ensure its non-interference using the techniques presented.

### 2014-07-08 paper/concrete.tex
Remove some duplication
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 If the operational rules are adapted na\"ively to this new setting,
-then non-interference can be violated.  In particular, it is not
-sound to share references to a heap cell between different tasks.
-Otherwise, information can be trivially leaked by copying
-secret data to a shared reference in one task, and then
-reading it again by a another task with a lower label.
+then non-interference can be violated: as we mentioned earlier,
+shared mutable cells could result in violation of noninterference.
 What we would like is a way of characterizing safe modifications to
@@
 As a concrete instantiation of this proof technique, we show
-how to make our single heap IFC language precise and
+how to make implement our IFC language using a single heap and
 ensure its non-interference using the techniques presented.

### 2014-07-08 paper/real.tex
last paragraph of node

@@
 
-\Red{LOCK:deian}
 While the described system implements |specLangJS seqf|, server-side
@@
 %
+(This is safer than the approach of simply wrapping objects, which can
+potentially allow for accessing objects outside the context.)
+%
 This task is trusted to ensures that, for instance, labels are
-propagated to files and that tasks are tainted when reading sensitive
-files, as to preserve non-interference.
+propagated to files and the labels of the task performing the
+operations and the file in question are inspected appropriately, as to
+preserve non-interference.
 %
-\Red{go into how this is app specific and it's not a huge limitation
-  that our system does not capture this; e.g., even for fs semantics
-  can vary: are labels serialized or not. later let's us change policy
-more easily, the other is better for persistence}
+Unfortunately, while imposing such a proof burden on the
+framework developer is undesirable, this is also somewhat expected:
+different language environments expose different libraries for
+handling external I/O.
+%
+For instance, in the case of Node.js, how labels interact with the
+file system may even vary according to the application (e.g.,
+different from our implementation, Hails~\cite{hails} does not persist
+labels).
+%
+While we can extend our formalism to model a particular interface to
+the file system, HTTP client, etc. the applicability of this are
+unclear and left to future work.
+%
 

### 2014-07-08 paper/proofs.tex
Fix extended version link

@@
   For space reasons, we only sketch the structure of the proof here.
-  We refer the interested reader to Appendix~\ref{sec:appendix}
+  We refer the interested reader to
   \ifextended
+  Appendix~\ref{sec:appendix}
   \else
-  of the extended version (which we provide at
-  \url{http://www.scs.stanford.edu/~deian/ifc-inside_extended.pdf})
+  the appendix of the extended version of this paper
   \fi
   for a full proof.
-  The proof distinguishes two cases:
-  \begin{itemize}
-    \item If the task |it1| executed in |ic1| is erased, then there is no
+  The proof distinguishes two cases: (1) if the task |it1| executed in |ic1| is erased, then there is no
     need to take a step in |ic2|, as the computation in |ic1| does
     not have any visible effects after erasure.
-    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
+    (2) Otherwise, there must be a corresponding task |it2| in |ic2|, and
     it can take exactly the same reduction step as the task in |ic1|.
@@
     computation after erasure.
-  \end{itemize}
 \end{proof}

### 2014-07-08 paper/extensions.tex
Redify
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Edits for clarity, based on TODO
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 references, mutable variables (MVars)~\cite{CH96}, or channels,
-can be done in a similar manner.
-%
-In these cases, however, we must keep track of the additional state
-(as opposed to the labeled value case which requires no additional
-bookkeeping).
+can be done in a similar manner: these references are implemented
+in the IFC language, separately from any preexisting notions of
+mutable references in the target language.
 %
@@
 %
-Specifically, by amending |iS|, as in~\cite{lio,
+There is some minor additional state to track: specifically, by amending |iS|, as in~\cite{lio,
 stefan:addressing-covert}, we can allow threads to use these
@@
 
-TODO: provide them in the appendix, and refer to them here.
+\Red{TODO: provide them in the appendix, and refer to them here.}
 

### 2014-07-08 paper/retrofit.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Making a pass.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Edits for clarity, based on TODO
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 could be used to violate information flow control if the tasks had differing labels.
+At this point, the designer of an IFC system might add label checks to mutable references, to check the labels of the reader and writer---solving the leak, but also dooming the performance of mutable references in the system.
 
-While simple, this example demonstrates some of our general design principles.  When these
+Our design principles suggests a different resolution: when these
 constructs are treated as isolated tasks, each of which have their own heaps, it
-is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  From
-there, we can further ask: given the obviously safe formulation with
-separate heaps, can this fact be useful for showing the safety of a
-semantics which only has a single heap? (We answer this question
-positively in Section~\ref{sec:single-heap}.)  Finally, this na\"ive
-semantics violates expectations about how inter-task communication works
-on a shared heap and strongly suggests one should restrict the types of
+is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
+not be shared, the two systems are morally equivalent. (We elaborate on
+this formally in Section~\ref{sec:single-heap}.)  Finally, these
+semantics strongly suggest that one should restrict the types of
 data which may be passed between tasks (for example, in JavaScript, one
@@
 taking ECMAScript as the target language and combining it with our IFC
-language should produce the formal semantics for SWAPI.  In this
+language should produce the formal semantics for COWL~\cite{swapi}.  In this
 presentation, we use a simple, untyped lambda calculus with mutable

### 2014-07-08 paper/related.tex
Cut out monads related work
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-It has long been observed that information flow control and monads are
-closely related.  This observation has been used by Abadi et
-al.~\cite{abadi+:core} to structure access to private data by protecting
-it using a lattice of monads, one per security level. Russo et. al.~\cite{Russo+:Haskell08} extend this 
-idea to languages with side-effects. Our system uses
-monads in a conceptually different manner, where there is a single monad
-representing the information flow control computational effects; this
-is inline with the use of monads in other systems~\cite{Harrison05,lio,Devriese:2011}.
-Devriese and Piessens~\cite{Devriese:2011} utilize monad
-transformers as an essential component in their work.  However, their use
-of monad transformers is to explain when extra constraints on a non-information
-flow control aware base monad should be applied (i.e., during lifting).
-Harrison and Hook~\cite{Harrison05} define a notion of \emph{atomic noninterference},
-which is preserved through monad transformer application.  However, it is not
-clear what is the relationship between this notion and traditional noninterference,
-and their paper only proves a weaker property of no write down.
+%   It has long been observed that information flow control and monads are
+%   closely related.  This observation has been used by Abadi et
+%   al.~\cite{abadi+:core} to structure access to private data by protecting
+%   it using a lattice of monads, one per security level. Russo et. al.~\cite{Russo+:Haskell08} extend this 
+%   idea to languages with side-effects. Our system uses
+%   monads in a conceptually different manner, where there is a single monad
+%   representing the information flow control computational effects; this
+%   is inline with the use of monads in other systems~\cite{Harrison05,lio,Devriese:2011}.
+%   Devriese and Piessens~\cite{Devriese:2011} utilize monad
+%   transformers as an essential component in their work.  However, their use
+%   of monad transformers is to explain when extra constraints on a non-information
+%   flow control aware base monad should be applied (i.e., during lifting).
+%   Harrison and Hook~\cite{Harrison05} define a notion of \emph{atomic noninterference},
+%   which is preserved through monad transformer application.  However, it is not
+%   clear what is the relationship between this notion and traditional noninterference,
+%   and their paper only proves a weaker property of no write down.
 

### 2014-07-08 paper/real.tex
init of cowl

@@
 \subsubsection{Client-side embedding: Gecko}
-\Red{HERE}
 
-We remark that this is similar to the existing
-\texttt{postMessage} API used for iframe and worker
-communications~\cite{webworkers}.
+We now describe some of the implementation aspects of
+COWL~\cite{swapi}, for which this work serves as the theoretical
+underpinning.
 %
-Thus, the COWL implementation provides an IFC version of
-\texttt{postMessage}, defined in terms of |send|, that additionally
-takes a label argument.
+Since the architecture of COWL is similar to that of Node.js, we focus
+on the main differences.
 
+Most notably, tasks in COWL usually correspond to browsing contexts,
+such as iframes.
 %
-In turn, each task created with |sandbox| is
-executed in a separate thread, running a separate, \emph{fresh} instance of our
-modified JS runtime.
+Hence, the global object |tS0| also contains the DOM, the
+\verb|XMLHttpRequest| (XHR) object, etc.
 %
-Formally, |sandbox| is defined with |klone(tS) =
-tS0|, where |tS0| is the global object corresponding to the standard
-JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
-etc.).
-
-Unsurprisingly, our coarse-grained combined language approach has been
-inspired by existing browser (security) architectures.
-%
-Browsers, for example, isolate pages of different origins by running
-them in separate runtimes.
-%
-Similarly, they provide the worker JS object~\cite{webworkers}, which allows
-JavaScript to execute code in separate threads with separate JS
-runtimes (and fresh global objects).
-%
-In both cases, code relies on the \texttt{postMessage} message-passing
-API for communication, similar to our system.\footnote{
-  The message-passing approach is, in part, due to ECMAScript's lack
-  of well-defined semantics for concurrency.
-  %
-  Hence sharing and accessing objects such as the DOM across worker
-  threads is undefined.
+To ensure that JavaScript code cannot communicate using these objects
+(e.g., to the network with XHR or persistent storage using the DOM),
+COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
+  Since CSP does not yet address message passing or navigation, this
+  was addressed explicitly.
 }
 %
-As suggested by our formal semantics, COWL can directly leverage these
-mechanisms to implement the semantics of |specLangJS roundrobinf|
-without modifying the JS runtime or intrusively changing the browser
-layout engine.
+Note, that this does not prevent tasks from manipulating the DOM
+(e.g., to render information).
+%
+Rather, to enforce task-isolation, external effects due to DOM access
+are suppressed.
 

### 2014-07-08 paper/conclusion.tex

--- 2014-03-02 paper/conclusion.tex
@@
 
-We presented a formal semantics which describes how to extend arbitrary languages
-with language-based coarse-grained IFC. We prove the security guarantees
-TSNI and TINI, where the proof technique is parametrized on the
-target language, for two scheduling policies. In
-addition, we provided conditions on how to securely refine our formal semantics to
-consider optimizations required in practice. Finally, we described extensions to
-the core IFC language with more advanced concepts like labeled values, privileges,
-and a notation of clearance, and therefore connecting it with existing
-IFC implementations for Javascript, Haskell, and (in
-less detail) proposing IFC for C.
+In this paper, we argued that when designing a coarse-grained IFC
+system, it is better to start with a fully isolated, multi-task system
+and work one's way back to the model of a single language.  We showed
+how to prove systems designed this way can be proved noninterferent,
+without needing to rely on details of the target language, and
+we provided conditions on how to securely refine our formal semantics to
+consider optimizations required in practice.  We connected our semantics
+to existing IFC implementations for JavaScript and Haskell, and proposed
+an IFC system for C using hardware isolation.
+By systematically applying ideas from IFC in operating systems to programming languages,
+we hope to have elucidated some of the core design principles of coarse-grained,
+dynamic IFC systems.
 

### 2014-07-08 paper/concrete.tex

@@
 
-\item When we clone the heap, we have to create a copy of everything
-reachable from the sandboxed expression (not just the values for
-the memory addresses in the expression), and replace all addresses
+\item When we clone the heap, we have to copy everything
+reachable from the sandboxed expression and replace all addresses
 correspondingly.  Even worse, the behavior of sending a memory address
@@
 task was sandboxed;  if it did, then the address should be rewritten to the
-new one, otherwise to a fresh address.
+existing one.
 \end{itemize}

### 2014-07-08 paper/extensions.tex

@@
 In this section we show how to extend the language with several such
-constructs.
+constructs.  For space reasons, we mainly provide the high-level
+ideas here, and provide full formal semantics (including the soundness
+proof with the extensions) in \appendixextfirst{}.
 %
@@
 %
-
-Full details with formal reduction rules are provided
-in \appendixextfirst{}, but omitted here for space reasons.
 %}
@@
 reference implementations.
-Again, we omit details here and refer the interested reader
-to \appendixext{}, where this extension has been fully worked out.
 
@@
 brevity.
-
-\Red{TODO: provide them in the appendix, and refer to them here.}
 

### 2014-07-08 paper/real.tex
nits

@@
 our IFC monitor.\footnote{
-  Importantly, our libraries provide mostly-identical interfaces to
+  Importantly, we provide mostly-identical interfaces to
   the standard Node.js libraries, hiding the underlying
@@
 COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
-  Since CSP does not yet address message passing or navigation, this
+  Since CSP does not yet restrict message-passing or navigation, this
   was addressed explicitly.

### 2014-07-08 paper/real.tex
cowl done

@@
 
-However, a simple implementation of just associating a label with
-workers and browsing context (iframes and top-level pages) to enforce
-IFC on the executing JavaScript is not sufficient, as APIs which
-introduce extra computational effects must be manually made aware of information flow
-control.
+Simply disallowing all external effects for all browsing contexts is
+overly-restricting; pages typically load images, perform XHR requests,
+etc.
 %
-For example, the initial global object of a worker contains the
-\texttt{XMLHttpRequest} (XHR) object, while the global object of a
-browsing context additionally contains the DOM.
+Hence, rather than disallowing all external effects, COWL allows
+controlled network communication (inter-frame communication is
+dictated by our |send| rule) by associating an implicit label with a
+remote host: namely the label corresponding to its origin.
 %
-In both cases, JS code can trivially leak information (e.g., to the
-network with XHR or persistent storage using the DOM).
+In turn, when a task perform a request, the COWL runtime performs the
+same label check as that of |send|, e.g., does the task label flow to
+the remote origin label.
 %
-To address this, COWL additionally uses content security policy (CSP) and
-(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
-to the label of a task (worker or browsing context).  Accommodating these
-features lies outside the purview of our formalism.
-
-%% \Red{
-%% EZY:  This seems like useless detail about the COWL implementation
-%% that is not relevant to this paper.
-%% 
-%% Of course, simply disallowing all external effects for all browsing
-%% contexts would break most of the Web.
-%% %
-%% Hence COWL only enforces IFC, and thus restricts external effects,
-%% when the JS code uses the new API.\footnote{
-%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
-%%   restricting external effects we interpose ``standard''
-%%   \texttt{postMessage} communication to ensure that no information is
-%%   leaked between contexts that have opted-in and those that have not.
-%% }
-%% %
-%% Moreover, rather than disallowing all external effects, COWL allows
-%% controlled network communication by leveraging the fact that web
-%% pages already have an accompanying security policy: the same origin
-%% policy.
-%% %
-%% Hence, for example, a worker that has read data only sensitive to
-%% \texttt{http://bank.ch} can communicate with this domain; only once
-%% \texttt{http://aws.com} data is also included in the context will all
-%% network requests be blocked.
-%% %
-%% Of course, this requires that we use a concrete label format to
-%% express the policies; we refer the interested reader to~\tocite{} for
-%% more details.}
+While the external effects of COWL can be formally modeled, and indeed
+necessary, we do model these effects in our more general framework,
+since, like for Node.js case, this is a platform-specific detail.
+%
+Indeed, the labeled HTTP client semantics of our Node.js
+implementation and that of COWL differ, even though they're both
+JavaScript systems, simply because of the different settings.
 

### 2014-07-08 paper/real.tex
nit

@@
 While the external effects of COWL can be formally modeled, and indeed
-necessary, we do model these effects in our more general framework,
-since, like for Node.js case, this is a platform-specific detail.
+necessary, we do not model these effects in our more general
+framework, since, like for Node.js case, this is a platform-specific
+detail.
 %
-Indeed, the labeled HTTP client semantics of our Node.js
-implementation and that of COWL differ, even though they're both
-JavaScript systems, simply because of the different settings.
+Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
+though they're both JavaScript systems, simply because of the
+different environment.
 

### 2014-07-08 paper/real.tex
Minor touchups
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 we consider how our formalism could be applied to the C programming
-language, and connect it to a previous IFC system for Haskell.
+language and connect it to a previous IFC system for Haskell.
 %
-Our goal is to show the flexibility of the embedding in settings with
-vastly different properties, as well as to discuss the
-semantic gap that must be overcome in some cases to apply our formalism
+The goal of this section is to show the flexibility of the embedding in settings with
+vastly different properties and discuss the
+semantic gap that must be overcome to apply our formalism
 to other systems.
@@
 However, this issue of performance and JavaScript isolation is not
-unique to our work, and has been solved by browser engines,
-which
+unique to our work and has been solved by browser engines,
+which also
 rely on the isolation of content from
@@
 %
-In V8, this unit of isolation is called a \emph{context}~\tocite{}; in
-SpiderMonkey, it is called a \emph{compartment}~\tocite{}.
+In V8, this unit of isolation is called a \emph{context}; in
+SpiderMonkey, it is called a \emph{compartment}.
 %
@@
 these systems to remove arbitrary external effects when implementing
-an IFC system, and reintroducing important effects in a safe manner.
+an IFC system so important effects can be reintroduced in a safe manner.
 
@@
 Figure~\ref{fig:node}.
-
 %While V8 provides a means for sharing any object between contexts (used
@@
 (This is safer than the approach of simply wrapping objects, which can
-potentially allow for accessing objects outside the context.)
+potentially allow objects to be accessed outside the context.)
 %
-This task is trusted to ensures that, for instance, labels are
-propagated to files and the labels of the task performing the
-operations and the file in question are inspected appropriately, as to
-preserve non-interference.
+This task is trusted to ensures that labels are
+propagated to files and the labels of the task and the file in question permit
+this flow.
 %
@@
 file system may even vary according to the application (e.g.,
-different from our implementation, Hails~\cite{hails} does not persist
-labels).
+in the IFC system Hails~\cite{hails}, labels are not persisted).
 %
 While we can extend our formalism to model a particular interface to
-the file system, HTTP client, etc. the applicability of this are
+the file system, HTTP client, etc. the utility of this formalization is
 unclear and left to future work.
@@
 the remote origin label.
-%
-While the external effects of COWL can be formally modeled, and indeed
-necessary, we do not model these effects in our more general
-framework, since, like for Node.js case, this is a platform-specific
+
+Once again, while the external effects of COWL can be formally modeled,
+we do not model these effects in our more general framework, since, like
+for Node.js case, they are a platform-specific
 detail.
@@
 though they're both JavaScript systems, simply because of the
-different environment.
+differing environments.
 

### 2014-07-08 paper/real.tex
Mention web workers
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@
 
-Most notably, tasks in COWL usually correspond to browsing contexts,
-such as iframes.
-%
-Hence, the global object |tS0| also contains the DOM, the
+Tasks in COWL usually correspond to browsing contexts, such as iframes,
+where the global object |tS0| also contains the DOM, the
 \verb|XMLHttpRequest| (XHR) object, etc.
 %
+Existing browser APIs also offer \emph{web workers}, which can
+be spawned by JavaScript code and have
+the same isolation properties as tasks in our system.
+%
+The isolation of web workers was motivated by the lack of multithreading
+in JavaScript; however, their isolation properties are equally useful for information
+flow control.
+
 To ensure that JavaScript code cannot communicate using these objects
@@
 Note, that this does not prevent tasks from manipulating the DOM
-(e.g., to render information).
+(e.g., to render information), so external effects due to DOM access
+are also suppressed.
 %
-Rather, to enforce task-isolation, external effects due to DOM access
-are suppressed.
-
 Simply disallowing all external effects for all browsing contexts is
@@
 %
-Hence, rather than disallowing all external effects, COWL allows
+Hence, COWL allows
 controlled network communication (inter-frame communication is

### 2014-07-08 paper/real.tex
1st paragraph lio

--- 2014-07-08 paper/real.tex
@@
 \label{sec:real:hs}
-In contrast with the C embedding which relies on hardware protection
-mechanisms, a Haskell implementation can leverage Haskell's strong data
-abstraction and static type system, monadic approach to effects, and
-lightweight concurrency to implement the embedding in a more lightweight
-manner.  We briefly describe one such system, LIO~\cite{lio}, which
-implements IFC as a library.
+Our work borrows many ideas from the Haskell coarse-grained IFC
+system LIO~\cite{lio, stefan:addressing-covert}.
+%
+LIO relies on Haskell's strong type system and monadic encoding of
+side-effecting computations to achieve isolation and define the IFC
+sub-language.
+%
+Specifically LIO provides the \verb|LIO| monad as a way of restricting
+(almost all) side-effects; this monad also keeps track of a current
+label which is, in turn, used by functions such as |getLabel| to
+define the IFC core.
+%
+In the context of our framework, LIO can be understood as follows: the
+\emph{pure subset} of Haskell is the target language, while the
+monadic subset of Haskell in the \verb|LIO| monad is the IFC language.
 
-LIO is implemented by defining a new monad, \verb|LIO|, which wraps Haskell's \verb|IO|
-monad.
+Indeed, by rephrasing LIO in terms of our framework, we simplified
+LIO's treatment of exceptions, which have since been integrated in the
+code-base.
 %
-The purpose of this monad is twofold: it restricts the use of
-arbitrary effects that would ordinarily be allowed by the \verb|IO| monad,
-and it associates labels with tasks.
-%
-Computations in the \verb|LIO|
-monad can be thought to be operating within the IFC system.
-%
-One important aspect of using \verb|IO| as the base for this
-implementation is that it allows use of Haskell's efficient
-implementation of threads, channels, etc. (e.g., in the concurrent
-version of LIO, we use Haskell's \texttt{forkIO} to fork a lightweight
-thread in the case of |fork|~\cite{stefan:addressing-covert}), in
-contrast to defining them in a completely pure fashion (as suggested
-in Section~\ref{sec:monad}).
-
-What is the interpretation of this system as per Section~\ref{sec:retrofit}?
-%
-Here, the \emph{pure subset} of Haskell is the target language, while
-the monadic subset of Haskell in the \verb|LIO| monad is the IFC
-language.
-%
-Crucially, the lack of unrestricted mutation in the pure fragment of
-Haskell prevents direct communication between tasks, even when memory is
-shared between them.\footnote{However, lazy evaluation can still produce
-a covert channel.}
-
-Since this IFC system is implemented as a library in Haskell,
-implementation-wise, we must ensure that these languages are indeed the subsets of Haskell
-we claim, i.e., while the concrete language is all of Haskell, we must
-ensure that we can restrict programs to our subset of Haskell that
-encodes the combined language.
-%
-To this end, \verb|LIO| relies on Haskell's strong data abstraction and type system
-(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
-ensure that arbitrary \verb|IO| actions cannot be lifted into
-\verb|LIO|.
-%
-In other words, assuming \verb|LIO| is implemented correctly, programs
-written in the \verb|LIO| monad cannot perform arbitrary \verb|IO| actions
-without breaking abstraction.
-
-We refer the interested reader to~\cite{lio,stefan:addressing-covert} for
-additional details on the various implementations of this system.\footnote{It's worth noting that the proofs of non-interference we have given for asynchronous communication primitives are new and not in the original presentation of LIO.}
-
-\Red{TODO: note that if the target language allows inspecting if
-  result is exception we can implement Breeze's NAV (vs. just
-propagating)}
+we addressed a limitation in LIO.
 

### 2014-07-08 paper/appendix.tex
start of clearance in appendix

@@
 labeled references.
+
+We also give details for the clearance extension below.
+
+\subsection{Clearance}
+
+As we have outlined in Section~\ref{sec:clearance}, we first extend
+tasks with an additional label |ilc|, which corresponds to the
+clearance of that task, and provide two primitives to read and
+write that value:
+\[ |fullconfc id il ilc tS ie| \]
+
+\begin{figure}
+  %{
+  %format .->  = "\overset{\alpha}{\hookrightarrow}"
+  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
+  \begin{code}
+    ie  ::= cdots | getClearance | setClearance ie
+    iE  ::= cdots | setClearance iE
+  \end{code}
+  \begin{mathpar}
+      \inferrule[I-getClearance]
+      { }
+      {|
+        niconf iS id il ilc getClearance
+        ->
+        niconf iS id il ilc ilc
+        |}
+
+      \and
+      \inferrule[I-setClearance]
+      { }
+      {|
+        niconf iS id il ilc (setClearance ilc')
+        ->
+        niconf iS id il ilc' unit
+        |}
+  \end{mathpar}
+  \caption{Syntax and semantics for clearance.  These rules are
+    understood to be an addition to the existing rules given earlier,
+    except for the \textsc{I-sandbox} rule, which replaces the previous
+    one.
+    All existing rules do not modify the clearance.}
+  \label{fig:clearance}
+  %}
+\end{figure}
 

### 2014-07-08 paper/abstract.tex
improve abstract

@@
 of information flow control.
-We formally specify a coarse-grained dynamic IFC system that
-can be implemented non-intrusively, resulting in
-much greater implementation efficiency than previous finer-grained approaches.
-The central idea is that an IFC system should model
-a set of communicating isolated language runtimes.
-The result is a general method for adding IFC to existing
-languages that is largely indifferent to the choice of language.
+We formally define a system in which a coarse-grained dynamic IFC system
+can be designed once and then applied to any programming language
+for which external effects can be controlled.  We use
+this formalism to implement two IFC systems for JavaScript, and show how
+it applies to other languages such as C.
 We describe how this methodology offers design principles for

### 2014-07-08 paper/conclusion.tex
improve conclusions

@@
 and work one's way back to the model of a single language.  We showed
-how to prove systems designed this way can be proved noninterferent,
+how to prove systems designed this way can be proved non-interferent,
 without needing to rely on details of the target language, and
@@
 consider optimizations required in practice.  We connected our semantics
-to existing IFC implementations for JavaScript and Haskell, and proposed
+to two IFC implementations for JavaScript based on this formalism,
+explained how our methodology improved an exiting IFC system for Haskell,
+and proposed
 an IFC system for C using hardware isolation.

### 2014-07-08 paper/real.tex
lio

@@
 (almost all) side-effects; this monad also keeps track of a current
-label which is, in turn, used by functions such as |getLabel| to
-define the IFC core.
+label which is, in turn, used by trusted code when defining core IFC
+functions, such as |getLabel|.
 %
@@
 \emph{pure subset} of Haskell is the target language, while the
-monadic subset of Haskell in the \verb|LIO| monad is the IFC language.
+monadic subset of Haskell, operating in the \verb|LIO| monad, is the
+IFC language.
 
 Indeed, by rephrasing LIO in terms of our framework, we simplified
-LIO's treatment of exceptions, which have since been integrated in the
-code-base.
+LIO's treatment of exceptions.
 %
-we addressed a limitation in LIO.
+LIO originally associated labels with exceptions, in a
+similar style to fine-grained
+systems~\cite{stefan:2012:arxiv-flexible, Breeze}.
+%
+In particular, the label of an exception was set to the current label
+at the time of the throw, and used by a custom catch construct to
+raise the current label, thereby preventing leaks due exceptional
+control flows.
+%
+In addition to being overly complex, the interaction of exceptions
+with clearance (which sets an upper bound on the current label, see
+Section~\ref{sec:extensions:clearance}) was incorrect: the clearance
+was restored to the clearance at point of the catch (a consequence of
+defining \verb|LIO| using a State monad).
+%
+Moreover, pure exceptions (e.g., divide by zero) always percolated to
+trusted code, effectively allowing for denial of service attacks.
+%
+By using isolated tasks, and thus treating the current label (and
+clearance) as global, the underlying Haskell exception system can be
+used directly: exceptional control flow does not affect IFC.
 

### 2014-07-08 paper/abstract.tex

@@
 concrete implementations of IFC systems, which can be shown to
-have interference by relating them to their fully isolated variants.
+have non-interference by relating them to their fully isolated variants.
 \end{abstract}

### 2014-07-08 paper/real.tex
nits

@@
 similar style to fine-grained
-systems~\cite{stefan:2012:arxiv-flexible, Breeze}.
+systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
 %
@@
 with clearance (which sets an upper bound on the current label, see
-Section~\ref{sec:extensions:clearance}) was incorrect: the clearance
+Section~\ref{sec:clearance}) was incorrect: the clearance
 was restored to the clearance at point of the catch (a consequence of

### 2014-07-08 paper/real.tex
minor

@@
 %
-For instance, this isolation can be achieved using Dune's hardware protection
-mechanisms~\cite{Belay:2012:DSU:2387880.2387913}, similar to a simpler
-version of Wedge~\cite{Belay:2012:DSU:2387880.2387913,
+For instance, our notion of isolation can be achieved using Dune's
+hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
+similar to a simpler version of
+Wedge~\cite{Belay:2012:DSU:2387880.2387913,
 Bittau:2008:WSA:1387589.1387611} with an information flow control
@@
 implemented as a lightweight process, can only access the memory it
-allocates--tasks do not have access to any shared memory.
+allocates---tasks do not have access to any shared memory.
 %
@@
 %
-Dunes hardware protection mechanism allows us to provide a concrete
+Dune's hardware protection mechanism would allow us to provide a concrete
 implementation that is efficient and relatively simple to reason
@@
 meaningless.
-
-We leave an actual implementation of an IFC system for C as
-future work.
+%
+We leave the implementation of this IFC system for C to future work.

### 2014-07-08 paper/related.tex
minor

@@
 semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
-higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
-also been proposed for the web
+higher than 100\%~\cite{JSFlow}.  Alternatively, coarse-grained
+approaches to security have also been proposed for the web
 scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

### 2014-07-08 paper/real.tex
real

@@
 %
-Our implementation provides a library for creating new tasks, i.e.,
+Our implementation\footnote{The source code of our implementation can be found at
+  \codelink{}.} provides a library for creating new tasks, i.e.,
 contexts whose global object only contains the standard JavaScript
@@
 applications may require access to the file system, HTTP server, HTTP
-client, etc.
+client, or other APIs that have external effects.
 %
-Unfortunately, our formalism does not capture such external effects
-and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
+Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
+thus we
 %
-We, instead, implement libraries such as a labeled file system as
+instead implement libraries such as a labeled file system as
 message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
@@
 %
-(This is safer than the approach of simply wrapping objects, which can
-potentially allow objects to be accessed outside the context.)
+This is safer than the approach of simply wrapping objects, which can
+potentially allow objects to be accessed outside the context.
 %
@@
 Unfortunately, while imposing such a proof burden on the
-framework developer is undesirable, this is also somewhat expected:
+framework developer is undesirable, this also has to be expected:
 different language environments expose different libraries for
-handling external I/O.
+handling external I/O, and the correct treatment of external effects
+is application specific.
 %
@@
 %
-While we can extend our formalism to model a particular interface to
-the file system, HTTP client, etc. the utility of this formalization is
-unclear and left to future work.
+%While we can extend our formalism to model a particular interface to
+%the file system, HTTP client, etc. the utility of this formalization is
+%unclear and left to future work.
 %
@@
 \label{sec:real:hs}
-Our work borrows many ideas from the Haskell coarse-grained IFC
-system LIO~\cite{lio, stefan:addressing-covert}.
+Our work borrows ideas from a Haskell coarse-grained IFC
+system called LIO~\cite{lio, stefan:addressing-covert}.
 %
@@
 
-Indeed, by rephrasing LIO in terms of our framework, we simplified
-LIO's treatment of exceptions.
+%Indeed, by rephrasing LIO in terms of our framework, we simplified
+%LIO's treatment of exceptions.
 %
@@
 at the time of the throw, and used by a custom catch construct to
-raise the current label, thereby preventing leaks due exceptional
+raise the current label, thereby preventing leaks due to exceptional
 control flows.
@@
 %
-Moreover, pure exceptions (e.g., divide by zero) always percolated to
+Furthermore, pure exceptions (e.g., divide by zero) always percolated to
 trusted code, effectively allowing for denial of service attacks.
 %
-By using isolated tasks, and thus treating the current label (and
-clearance) as global, the underlying Haskell exception system can be
-used directly: exceptional control flow does not affect IFC.
+The insights gained when viewing coarse-grained IFC as presented in this
+paper led to a much cleaner, simpler treatment of exceptions in LIO,
+which has now been adapted by LIO.
+%By using isolated tasks, and thus treating the current label (and
+%clearance) as global, the underlying Haskell exception system can be
+%used directly: exceptional control flow does not affect IFC.
 

### 2014-07-08 paper/real.tex

@@
 
-\subsubsection{Server-side embedding: Node.js}
+\subsubsection{Server-side IFC: Node.js}
 
@@
 %
+We do not extend our formalism to account for the  particular
+interface to the file system, HTTP client, etc., as this is
+specific to the Node.js implementation and does not generalize
+to other systems.
 
-\subsubsection{Client-side embedding: Gecko}
+\subsubsection{Client-side IFC: Gecko}
 
 We now describe some of the implementation aspects of
-COWL~\cite{swapi}, for which this work serves as the theoretical
-underpinning.
+COWL, a JavaScript implementation of coarse-grained
+IFC for Mozilla's Gecko.  This work provides the formal basis for
+the implementation, and COWL is described in much more detail in~\cite{swapi}.
 %
@@
 
-Tasks in COWL usually correspond to browsing contexts, such as iframes,
-where the global object |tS0| also contains the DOM, the
-\verb|XMLHttpRequest| (XHR) object, etc.
+%Tasks in COWL  correspond to browsing contexts, such as iframes,
+%where the global object |tS0| also contains the DOM, the
+%\verb|XMLHttpRequest| (XHR) object, etc.
 %
-Existing browser APIs also offer \emph{web workers}, which can
+Existing browser APIs offer \emph{web workers}, which can
 be spawned by JavaScript code and have
@@
 
-To ensure that JavaScript code cannot communicate using these objects
+To ensure that JavaScript code cannot communicate using the global object
 (e.g., to the network with XHR or persistent storage using the DOM),
@@
   Since CSP does not yet restrict message-passing or navigation, this
-  was addressed explicitly.
+  was addressed explicitly in the implementation.
 }
@@
 Simply disallowing all external effects for all browsing contexts is
-overly-restricting; pages typically load images, perform XHR requests,
+overly-restricting; pages typically load images, perform XHR requests
+to dynamically load data,
 etc.
@@
 In turn, when a task perform a request, the COWL runtime performs the
-same label check as that of |send|, e.g., does the task label flow to
+same label check as that of |send|, namely that the task label can
+flow to
 the remote origin label.
@@
 we do not model these effects in our more general framework, since, like
-for Node.js case, they are a platform-specific
-detail.
+for Node.js case, they are application specific.
 %
-Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
-though they're both JavaScript systems, simply because of the
-differing environments.
+%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
+%though they're both JavaScript systems, simply because of the
+%differing environments.
 

### 2014-07-08 paper/extensions.tex
lio
nits
minor

@@
 \subsection{Clearance}
+\label{sec:clearance}
 %
@@
 An alternative approach is to model such effects as messages to/from
-certain labeled tasks.
+certain labeled tasks, an approach taken by our Node.js
+implementation.
 %
@@
 %
-This latter approach of wrapping unsafe primitives is, for example,
-used in COWL to allow for controlled network communication.
+An alternative approach of wrapping or modifying/restricting unsafe
+primitives is, for example, used in COWL and JSFlow to allow for
+controlled network communication.
 %
-By wrapping the default XHR object, for example, we can allow code
+By restricting the default XHR object, for example, COWL allows code
 to communicate with hosts according to the task's current label.

### 2014-10-13 paper/abstract.tex

--- 2014-07-08 paper/abstract.tex
@@
 \begin{abstract}
-Many important security problems in JavaScript, such as browser extension
-security, untrusted JavaScript libraries and
-safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
-of information flow control.
-We formally define a system in which a coarse-grained dynamic IFC system
-can be designed once and then applied to any programming language
-for which external effects can be controlled.  We use
-this formalism to implement two IFC systems for JavaScript, and show how
-it applies to other languages such as C.
-We describe how this methodology offers design principles for
-the construction of information flow control systems in more
-traiditional settings, as well as compositional proofs for optimized
-concrete implementations of IFC systems, which can be shown to
-have interference by relating them to their fully isolated variants.
+Many important security problems in JavaScript, such as browser
+extension security, untrusted JavaScript libraries and safe
+integration of mutually distrustful websites (mash-ups), may be
+effectively addressed using an efficient implementation of information
+flow control (IFC).  Unfortunately existing fine-grained approaches to
+JavaScript IFC require modifications to the language semantics, a
+non-goal for browser applications.  In this work we take the ideas of
+coarse-grained dynamic IFC to the limit and provide the theoretical
+foundation for a language-based approach that can be applied to any
+programming language for which external effects can be controlled.  We
+then apply this formalism to JavaScript, in the context of Node.js and
+Firefox, and show how it generalizes to other language
+implementations, including C and Haskell.  Our methodology offers
+design principles for the construction of information flow control
+systems when isolation can easily be achieved, as well as
+compositional proofs for optimized concrete implementations of these
+systems, by relating them to their fully isolated variants.
 \end{abstract}

### 2014-10-13 paper/extensions.tex

@@
 %
-An alternative approach of wrapping or modifying/restricting unsafe
-primitives is, for example, used in COWL and JSFlow to allow for
+An alternative approach of restricting or wrapping unsafe primitives
+is, for example, used in COWL and JSFlow, respectively, to allow for
 controlled network communication.
 %
-By restricting the default XHR object, for example, COWL allows code
-to communicate with hosts according to the task's current label.
+(By restricting the default XHR object, for example, COWL allows code
+to communicate with hosts according to the task's current label.)

### 2014-10-15 paper/abstract.tex
Refocus abstract

--- 2014-07-08 paper/abstract.tex
@@
 \begin{abstract}
-Many important security problems in JavaScript, such as browser extension
-security, untrusted JavaScript libraries and
-safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
-of information flow control.
-We formally define a system in which a coarse-grained dynamic IFC system
-can be designed once and then applied to any programming language
-for which external effects can be controlled.  We use
-this formalism to implement two IFC systems for JavaScript, and show how
-it applies to other languages such as C.
-We describe how this methodology offers design principles for
-the construction of information flow control systems in more
-traiditional settings, as well as compositional proofs for optimized
-concrete implementations of IFC systems, which can be shown to
-have interference by relating them to their fully isolated variants.
+Web sites could compromise users' privacy by accidentally incorporating
+error-prone or malicious third-party JavaScript. Informa\-tion-flow control
+(IFC) is a promising technique to securely incorporate untrusted JavaScript into
+web sites and it allows the safe integration of mutually distrustful websites
+(mash-ups). Unfortunately, existing IFC approaches demand non-trivial
+modifications to the JavaScript engine or a full instrumentation of the
+JavaScript semantics in order to track how information flows inside web
+applications. Inspired by operating system research, we present an alternative
+technique based on attaching a single IFC policy to a single browsing context,
+and therefore abstracting away from the internals of JavaScript. Specifically,
+we provide a coarse-grained IFC monitor which does not require any modifications
+to either JavaScript semantics or its engine---the approach only exposes a small
+API to the JavaScript code in order to interact with the monitor. To reason
+about our design principles, we describe a formal framework which then we
+instantiate to provide guarantees to out monitor implementation in Firefox.
 \end{abstract}

### 2014-10-15 paper/abstract.tex
Pass abstract

@@
 API to the JavaScript code in order to interact with the monitor. To reason
-about our design principles, we describe a formal framework which then we
-instantiate to provide guarantees to out monitor implementation in Firefox.
+about our design principles, we describe a formal framework which treat target
+languages (e.g. JavaScript) as black-boxes with a clear interface to the
+monitor. We instantiate our framework to provide security guarantees
+(i.e. non-interference) to an IFC monitor implemented in Firefox.
 \end{abstract}

### 2014-10-16 paper/abstract.tex
pass abstract

@@
 error-prone or malicious third-party JavaScript. Informa\-tion-flow control
-(IFC) is a promising technique to securely incorporate untrusted JavaScript into
-web sites and it allows the safe integration of mutually distrustful websites
-(mash-ups). Unfortunately, existing IFC approaches demand non-trivial
-modifications to the JavaScript engine or a full instrumentation of the
-JavaScript semantics in order to track how information flows inside web
-applications. Inspired by operating system research, we present an alternative
-technique based on attaching a single IFC policy to a single browsing context,
-and therefore abstracting away from the internals of JavaScript. Specifically,
-we provide a coarse-grained IFC monitor which does not require any modifications
-to either JavaScript semantics or its engine---the approach only exposes a small
-API to the JavaScript code in order to interact with the monitor. To reason
-about our design principles, we describe a formal framework which treat target
-languages (e.g. JavaScript) as black-boxes with a clear interface to the
-monitor. We instantiate our framework to provide security guarantees
-(i.e. non-interference) to an IFC monitor implemented in Firefox.
+(IFC) is a promising technique to secure web sites against untrusted JavaScript
+code. Unfortunately, existing IFC approaches demand non-trivial modifications to
+the JavaScript engine or a full instrumentation of the JavaScript semantics. In
+contrast, and inspired by operating system (OS) research, we present an
+alternative technique based on attaching a single IFC policy to a single
+execution context, and therefore abstracting away from the internals of
+JavaScript. Specifically, we provide a coarse-grained IFC monitor which does not
+require any modifications to either JavaScript's semantics or its engine---the
+approach only exposes a small API to JavaScript code in order to interact
+with the monitor. To reason about our design principles, we describe a formal
+framework which treat target languages, e.g. JavaScript, as black-boxes with a
+clear interface to the monitor. We instantiate our framework to provide security
+guarantees (i.e. non-interference) to an IFC monitor implemented in Firefox.
 \end{abstract}

### 2014-10-16 paper/intro.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Adapting intro

--- 2014-07-08 paper/intro.tex
@@
 websites that may not even be aware of each other's existence.)
-While just-in-time combination of untrusting components
-offers great flexibility, it also poses complex security challenges.
-In particular, maintaining data privacy in the face of malicious
-extensions, libraries, and mashup components has been difficult,
-and in general effectively impossible.
+%While just-in-time combination of untrusting components
+%offers great flexibility, it also poses complex security challenges.
+%In particular,
+Maintaining data privacy in the face of malicious
+extensions, libraries, and mashup components has been rather difficult.
+%and in general effectively impossible.
 
-Information flow control (IFC) is a promising technique
-that provides security
-by tracking the flow of sensitive data through a system.
-Untrusted code is confined so that it cannot exfiltrate data, except as
-per an information flow policy.  Significant research has been devoted to
-adding various forms of IFC to different kinds of programming languages
-and systems.  In the context of the web, however, there is a strong
-motivation to preserve JavaScript's semantics while retrofitting it with dynamic information
-flow control.
+Information flow control (IFC) is a promising technique that provides security
+by tracking the flow of sensitive data through a system.  Untrusted code is
+confined so that it cannot exfiltrate data, except as per an information flow
+policy.  Significant research has been devoted to adding various forms of IFC to
+different kinds of programming languages and systems.  In the context of the
+web, however, there is a strong motivation to preserve JavaScript's semantics
+and avoid any modification to its engine.
+%, while retrofitting it with dynamic
+%information flow control.
 
-One approach to information flow control is fine-grained tracking,
-which offers great flexibility.
-However, these systems
-require deep integration with the programming language and modify
-the semantics in non-trivial ways.  This makes fine-grained systems
-less suitable in contexts where preserving an existing language
-is important.
+%%% Ale: Related work?
+%% One approach to information flow control is fine-grained tracking,
+%% which offers great flexibility.
+%% However, these systems
+%% require deep integration with the programming language and modify
+%% the semantics in non-trivial ways.  This makes fine-grained systems
+%% less suitable in contexts where preserving an existing language
+%% is important.
 %
-Moreover, the task of adding fine-grained IFC even to a simple language is
-non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
-such as JavaScript, this challenge becomes almost insurmountable.
+%% Moreover, the task of adding fine-grained IFC even to a simple language is
+%% non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
+%% such as JavaScript, this challenge becomes almost insurmountable.
 
-In the alternative \textit{coarse-grained} approach to IFC,
-a system is divided into relatively coarse computational units,
-each with a single label dictating its security policy.
-Only
-communication between isolated computational units must be tracked.
-%A recent system named SWAPI~\cite{swapi} adds IFC to the
+Inspired by OS research~\cite{}, we present a \textit{coarse-grained} dynamic
+IFC monitor to JavaScript (as specified by ECMAScript~\cite{}). Specifically,
+JavaScript code is divided into relatively coarse computational units
+(i.e. workers), each with a single label dictating its security policy. As a
+result, it is just enough to track communication between isolated computational
+units.
+%A recent system named COWL~\cite{swapi} adds IFC to the
 %browser by identifying \emph{web workers} as an existing computational
@@
 %influencing the computation of less sensitive workers.
-This coarse-grained approach provides a number of advantages:
-(1) minimal changes to an
-existing programming language when adding IFC, which (2) allows
-the reuse of existing programs.  Furthermore, (3)
-reduced runtime overhead because checks need only
-be performed at isolation boundaries, compared to fine-grained
-systems were the runtime overhead can be impractical~\cite{JSFlow}.
-Finally, (4) associating
-a single security label with the entire computational unit simplifies
-understanding and reasoning about the correctness of the
-system, without information flow reasoning about the
-technical details of the semantics of the programming language.
+This technique provides a number of advantages: (1) no changes to JavaScript's
+semantics when adding IFC ---our approach only exposes an small API to
+JavaScript code in order to interact with the monitor---, and
+% which (2) allows
+%the reuse of existing programs.  Furthermore,
+(2) reduced runtime overhead because checks only need to be performed at isolation
+boundaries instead of at every instruction in the code~\cite{JSFlow}.
+%, compared to fine-grained systems were the runtime overhead can be
+% impractical~\cite{JSFlow}.
+Finally, (3) associating a single security label with the entire computational
+unit simplifies understanding and reasoning about the correctness of the system,
+without reasoning about most of the semantics details of JavaScript.
+% underlying programming language, i.e., JavaScript.
 
-In this paper, we take coarse-grained labeling~\cite{Zeldovich:2006,
-lio} to its logical extreme: an information flow control system should
-be thought of as multiple instances of completely isolated language
-runtimes or \emph{tasks}, with information flow control applied to
-inter-task communication.  We describe a formal system in which an IFC
-system can be designed once and then applied to any programming language
-which has control over external effects (e.g., JavaScript or C with
-access to hardware privilege separation).  We formalize this system
-using an approach by
-Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
-operational semantics and prove non-interference guarantees
-that are independent of the choice of specific target language.
+To reason about our monitor, we introduce a \emph{generic} formalism which
+translates coarse-grained IFC ideas~\cite{Zeldovich:2006} into a language-based
+setting: an information flow control system should be thought of as multiple
+instances of \emph{completely isolated language runtimes} or \emph{tasks}, with
+information flow control applied to inter-task communication.
+% We describe a
+% formal framework in which an IFC system can be designed once and then applied to
+% any programming language which has control over external effects like
+% JavaScript.
+%(e.g., JavaScript) or C with access to hardware privilege separation).
+We formalize our framework by using the Matthews-Findler's
+approach~\cite{Matthews:2007:OSM:1190216.1190220} for combining operational
+semantics and prove non-interference guarantees that are independent of the
+choice of the specific underlying programming language, e.g., JavaScript.
+%framework to , being one instead of
+%that ECMAScript. %target language.
 
-What distinguishes this setting from previous coarse-grained IFC
-systems?
-%
-First, even though the underlying semantic model involves communicating
-tasks, these tasks can be coordinated together in ways that simulate
-traditional features in monolithic languages.  In fact, simulating
-features in this way is a very useful \emph{design tool} for discovering
-what variants of the features are permissible and which are not.
-%
-Second, although completely separate tasks are semantically easy to
-reason about, real-world implementations often blur the lines between
-tasks in the name of efficiency.
-Characterizing what optimizations are permissible is subtle, since
-removing transitions from the operational semantics of a language can
-break non-interference.  We partially address this issue
-by characterizing isomorphisms between the operational semantics of our
-defined language and a concrete implementation, showing that if this
-relationship holds, then non-interference in the abstract specification
-carries over to the concrete implementation.
+%% There are a number of points that distinguish this setting from
+%% previous coarse-grained IFC systems.
+%% %
+%% First, even though the underlying semantic model involves communicating
+%% tasks, these tasks can be coordinated together in ways that simulate
+%% features of traditional languages.
+%% %
+%% In fact, simulating
+%% features in this way is a useful \emph{design tool} for discovering
+%% what variants of the features are permissible and which are not.
+%% %
+%% Second, although completely separate tasks are semantically easy to
+%% reason about, real-world implementations often blur the lines between
+%% tasks in the name of efficiency.
+%% Characterizing what optimizations are permissible is subtle, since
+%% removing transitions from the operational semantics of a language can
+%% break non-interference.  We partially address this issue
+%% by characterizing isomorphisms between the operational semantics of our
+%% abstract language and a concrete implementation, showing that if this
+%% relationship holds, then non-interference in the abstract specification
+%% carries over to the concrete implementation.
 
@@
 \begin{itemize}
-  \item We give formal semantics for a core coarse-grained
-  dynamic information flow control language free of non-IFC constructs.
-  We then show how a large class of target languages can be combined
-  with this IFC language and prove that the result provides
-  non-interference. (Section~\ref{sec:retrofit})
-  \item We provide a proof technique to show the non-interference
-  of a concrete semantics for a potentially optimized IFC language
-  by means of an isomorphism, and show a class of restrictions on
-  the IFC language that preserves non-interference. (Section~\ref{sec:formal}
-  and~\ref{sec:concrete})
-  \item We have implemented an IFC system based on these semantics
-  for Node.js, and we connect our formalism to another implementation
-  based on this work
-  for client-side JavaScript in Gecko~\cite{swapi}.
-  Furthermore, we outline an implementation for the C programming
-  language.
-  (Section~\ref{sec:real})
+  \item We give formal semantics for a core coarse-grained dynamic information
+    flow control monitor which is agnostic to non-IFC constructs.
+    %We show how a
+  \item We show non-interefence results when target languages exhibit a notion
+    of isolated computations and control of external side-effects.
+    %large class of target languages can be combined with this IFC language and
+    %prove that the result provides
+    %non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
+  %% \item We provide a proof technique to show the non-interference
+  %% of a concrete semantics for a potentially optimized IFC language
+  %% by means of an isomorphism and show a class of restrictions on
+  %% the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
+  \item
+  %We have implemented an IFC system based on these semantics
+  %or Node.js, and
+  We connect our formalism to COWL~\cite{swapi}, a
+  client-side IFC monitor for JavaScript in Firefox.
+  %Furthermore, we outline an implementation for the C programming
+  %language.
+  %(Section~\ref{sec:real})
 %  \item We show how to extend the Matthews-Findler method from just
@@
   more advanced concepts such as labeled values, labeled references, or a
-  notion of clearance. (Section~\ref{sec:extensions})
+  notion of clearance. %(Section~\ref{sec:extensions})
 \end{itemize}

### 2014-10-16 paper/intro.tex
Pass in intro, shrinking a bit

@@
 
-Inspired by OS research~\cite{}, we present a \textit{coarse-grained} dynamic
-IFC monitor to JavaScript (as specified by ECMAScript~\cite{}). Specifically,
-JavaScript code is divided into relatively coarse computational units
-(i.e. workers), each with a single label dictating its security policy. As a
-result, it is just enough to track communication between isolated computational
-units.
+Inspired by OS research~\cite{Zeldovich:2006}, we present a
+\textit{coarse-grained} dynamic IFC monitor to JavaScript (as specified by
+ECMAScript~\cite{ecma}). Specifically, JavaScript code is divided into relatively
+coarse computational units (i.e. workers), each with a single label dictating
+its security policy. As a result, it is just enough to track communication
+between isolated computational units.
 %A recent system named COWL~\cite{swapi} adds IFC to the
@@
 \begin{itemize}
-  \item We give formal semantics for a core coarse-grained dynamic information
-    flow control monitor which is agnostic to non-IFC constructs.
+  \item We give formal semantics for a generic coarse-grained dynamic
+    information flow control monitor which is agnostic to non-IFC constructs.
     %We show how a

### 2014-10-16 paper/intro.tex
Intro

@@
 semantics and prove non-interference guarantees that are independent of the
-choice of the specific underlying programming language, e.g., JavaScript.
+choice of the specific underlying programming language. %, e.g., JavaScript.
 %framework to , being one instead of

### 2014-10-16 paper/retrofit.tex
Pass on retrofit. Removed Mini-ES and clarify a bit what the embedding provides, i.e., a semantics which guarantees target language programs to be monitored

--- 2014-07-08 paper/retrofit.tex
@@
 
-Before moving on to the formal treatment of our system, we'd like to give
-a brief primer of information flow control and describe some example programs
-in our system, emphasizing the parallel between their implementation
-in a multi-task setting, and the traditional, ``monolithic'' programming
-language feature they simulate.
+%% Before moving on to the formal treatment of our system, we'd like to give
+%% a brief primer of information flow control and describe some example programs
+%% in our system, emphasizing the parallel between their implementation
+%% in a multi-task setting, and the traditional, ``monolithic'' programming
+%% language feature they simulate.
 
-Information flow control systems operate by associating data with \emph{labels},
-and specifying whether or not data tagged with one label |l1| can flow
-to another
-label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
-security policy (for example, confidential information should not flow to
-a public channel), and the work of specifying the semantics of an information
-flow language involves demonstrating that impermissible flows cannot happen,
-a property called \emph{non-interference}.
-%
-In our coarse-grained floating-label approach, labels are associated with tasks.
-%
-The task label---we refer to the label of the currently executing task as the
-\emph{current label}---serves to protect everything in the task's scope;
-all data in a task shares this common label.
+%% Information flow control systems operate by associating data with \emph{labels},
+%% and specifying whether or not data tagged with one label |l1| can flow
+%% to another
+%% label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
+%% security policy (for example, confidential information should not flow to
+%% a public channel), and the work of specifying the semantics of an information
+%% flow language involves demonstrating that impermissible flows cannot happen,
+%% a property called \emph{non-interference}.
+%% %
+%% In our coarse-grained floating-label approach, labels are associated with tasks.
+%% %
+%% The task label---we refer to the label of the currently executing task as the
+%% \emph{current label}---serves to protect everything in the task's scope;
+%% all data in a task shares this common label.
 
-For our first example, here is a program which spawns a new isolated task,
-and then sends it a mutable reference:
-\begin{align*}
-    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
-    & |in TI (send (IT i) l (IT (ref true)))|
-\end{align*}
-For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
-|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
-message, and then \textbf{send}s the task a mutable reference |(ref
-true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
-could be used to violate information flow control if the tasks had differing labels.
+%% For our first example, here is a program which spawns a new isolated task,
+%% and then sends it a mutable reference:
+%% \begin{align*}
+%%     & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
+%%     & |in TI (send (IT i) l (IT (ref true)))|
+%% \end{align*}
+%% For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
+%% |sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
+%% message, and then \textbf{send}s the task a mutable reference |(ref
+%% true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
+%% could be used to violate information flow control if the tasks had differing labels.
+At this point, the designer of an IFC system might add label checks to mutable references, to check the labels of the reader and writer---solving the leak, but also dooming the performance of mutable references in the system.
 
-While simple, this example demonstrates some of our general design principles.  When these
-constructs are treated as isolated tasks, each of which have their own heaps, it
-is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  From
-there, we can further ask: given the obviously safe formulation with
-separate heaps, can this fact be useful for showing the safety of a
-semantics which only has a single heap? (We answer this question
-positively in Section~\ref{sec:single-heap}.)  Finally, this na\"ive
-semantics violates expectations about how inter-task communication works
-on a shared heap and strongly suggests one should restrict the types of
-data which may be passed between tasks (for example, in JavaScript, one
-might only allow JSON objects to be passed between tasks, rather than
-general object structures).
+%% Our design principles suggests a different resolution: when these
+%% constructs are treated as isolated tasks, each of which have their own heaps, it
+%% is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
+%% not be shared, the two systems are morally equivalent. (We elaborate on
+%% this formally in Section~\ref{sec:single-heap}.)  Finally, these
+%% semantics strongly suggest that one should restrict the types of
+%% data which may be passed between tasks (for example, in JavaScript, one
+%% might only allow JSON objects to be passed between tasks, rather than
+%% general object structures).
 
-Here are two more examples of language features which have an
-interesting interpretation when viewed in the setting of multiple tasks.
+%% Here are two more examples of language features which have an
+%% interesting interpretation when interpreted as task communication.
 
-\paragraph{Stack frames versus scheduling}  One feature which is
-supported by some information flow control systems is the ability to
-temporarily raise the current label in order to do computation on data
-(as done by LIO's |toLabeled| and Breeze's
-brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
-stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
-enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
-the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
-achieve termination-insensitive non-interference: if the high secrecy
-section doesn't terminate, this is observable by the non-execution of
-the defunct public continuation.
+%% \paragraph{Stack frames versus scheduling}  One feature which is
+%% supported by some information flow control systems is the ability to
+%% temporarily raise the current label in order to do computation on data
+%% (as done by LIO's |toLabeled| and Breeze's
+%% brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
+%% stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
+%% enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
+%% the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
+%% achieve termination-insensitive non-interference: if the high secrecy
+%% section doesn't terminate, this is observable by the non-execution of
+%% the defunct public continuation.
 
-\begin{figure}
-\begin{align*}
-    & |toLabeled l te @= | \\
-    & |tab let i = taskId in| \\
-%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
-    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
-    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
-\end{align*}
-\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
-\end{figure}
+%% \begin{figure}
+%% \begin{align*}
+%%     & |toLabeled l te @= | \\
+%%     & |tab let i = taskId in| \\
+%% %%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+%%     & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
+%%     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
+%% \end{align*}
+%% \caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
+%% \end{figure}
 
-When considering tasks, we will instead say that the allocation of a new
-stack frame with a raised label corresponds to the creation of a new
-isolated task; a sample encoding using our language is shown in
-Figure~\ref{fig:toLabeled}.
-However, this is not enough: in a stack discipline, one generally
-expects stack entries to be processed in order, rather than in parallel
-as would be suggested by isolated tasks.  The sequential processing of
-the task queue corresponds to a specific \emph{scheduling policy} of
-these tasks.  The recasting of the problem to one of scheduling
-highlights the essential difference between termination-insensitive and
-termination-sensitive non-interference, and we will show how different
-scheduling policies give different security guarantees.
+%% When considering tasks, we will instead say that the allocation of a new
+%% stack frame with a raised label corresponds to the creation of a new
+%% isolated task; a sample encoding using our language is shown in
+%% Figure~\ref{fig:toLabeled}.
+%% There is one more ingredient: in a stack discipline, one generally
+%% expects stack entries to be processed in order, rather than in parallel
+%% as would be suggested by isolated tasks.  The sequential processing of
+%% the task queue corresponds to a specific \emph{scheduling policy} of
+%% these tasks.  In fact, the choice of scheduling here is the essential difference that
+%% determines whether or not one can prove termination-insensitive or
+%% termination-sensitive non-interference. We will show how different
+%% scheduling policies give different security guarantees.
 
-\paragraph{Exceptions versus message passing}
-Another language feature that has caused difficulty for
-many information flow control systems is exceptions handling,
-when built on top of this stack discipline.
-%
-The key difficulty appears when considering the propagation of exceptions
-across stack boundaries where the current label is restored.
-%
-If the exception crosses this boundary, it can leak information about the
-inner secret computation into a public computation; hence, one must
-explicitly ensure that |toLabeled| does not propagate exceptions.
+%% \paragraph{Exceptions versus message passing}
+%% Another language feature that has caused difficulty for
+%% many information flow control systems is exception handling
+%% when built on top of this stack discipline.
+%% %
+%% The key difficulty appears when considering the propagation of exceptions
+%% across stack boundaries where the current label is restored.
+%% %
+%% If the exception crosses this boundary, it can leak information about the
+%% inner secret computation into a public computation; hence, one must
+%% explicitly ensure that |toLabeled| does not propagate exceptions.
+%% %
+%% When stack frames are treated as isolated tasks, the correct semantics
+%% are achieved automatically.
+%% %
+%% Exceptions simply stop when the hit the top-level of a task:
+%% the only way for the frame to communicate information is by
+%% initiating inter-task message passing.
+%% %
+%% For instance,
+%% \begin{code}
+%% TI(toLabeled l (IT (if te then fail else true))); true
+%% \end{code}
+%% always evaluates to |true|, regardless of the value of |te|.
 
-When stack frames are treated as isolated tasks, the correct semantics
-are achieved automatically.
-%
-Exceptions simply stop when the hit the top-level of a task:
-the only way for the frame to communicate information is by
-initiating inter-task message passing.
-%
-For instance, 
-\begin{code}
-TI(toLabeled l (IT (if te then fail else true))); true
-\end{code}
-always evaluates to |true|, regardless of the value of |te|.
+%\subsection{Preliminaries}
 
-\subsection{Preliminaries}
+Our goal now is to describe how to take a \textbf{{\color{red} target
+language}}
+%with a formal operational semantics
+and combine it with an \textit{{\color{blue} information flow control language}}
+(or IFC-aware API).  It is precisely this combination what enables executing the
+target language under a coarse-grained IFC monitor. In Section~\ref{sec:real},
+we show that taking ECMAScript as the target language and combining it with our
+IFC language provides the formal semantics for COWL~\cite{swapi}.  In this
+section, we intentionally avoid too much detail about the target language; after
+all, our technique really does not care too much about what, exactly, is in
+there.
+% we discuss the proper
+% embedding in more detail in Section~\ref{sec:real}.
 
-Our goal now is to
-describe how to take a \textbf{{\color{red} target
-language}} with a formal operational semantics and combine it with an
-\textit{{\color{blue} information flow control language}}.  For example,
-taking ECMAScript as the target language and combining it with our IFC
-language should produce the formal semantics for SWAPI.  In this
-presentation, we use a simple, untyped lambda calculus with mutable
-references and fixpoint in place of ECMAScript, to demonstrate some of the key
-properties without having too much detail (and because the embedding really
-doesn't care about what, exactly, is in the target language); we discuss the proper
-embedding in more detail in Section~\ref{sec:real}.
+%use a simple,
+%untyped lambda calculus with mutable references and fixpoint in place of
+%ECMAScript,
+%to demonstrate some of the key properties without having too much
+%detail
 
@@
 
-\subsection{Target Language: Mini-ES}
+\subsection{Target Language}
 
-In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
-mutable references and fixpoint, prepared for combination with an
-information flow control language.  The presentation is mostly standard, and utilizes Felleisen-Hieb reduction
-semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
-operational semantics of the system.  One peculiarity is that our language
-defines an evaluation context |tE|, but, the evaluation rules have been
-expressed in terms of a different evaluation context |curlyRedE|;
-Here, we follow the approach of Matthews and
+%% In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
+%% mutable references and fixpoint, prepared for combination with an
+%% information flow control language.
+The framework assumes target languages utilizing
+%The presentation is mostly standard, and utilizes
+Felleisen-Hieb reduction semantics~\cite{Felleisen:1992:RRS:136293.136297} in
+order to define their operational semantics. Specifically, we require that a
+target language be expressed in terms of some global machine state |tS|, some
+evaluation context |tE|, some expressions |te|, some set of values |tv| and a
+\emph{deterministic} reduction relation on full configurations $|tS| \times |tE|
+\times |te|$.
+
+One peculiarity of our approach is that reductions rules in the target language
+are reformulated in terms of a different evaluation context |curlyRedE| (instead
+of |tE|); Here,
+we follow the approach of Matthews and
 Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining
-semantics of multiple languages. 
-To derive the usual operational semantics for this language, the evaluation
-context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
-However, when we combine this language with an IFC language, we
-reinterpret the meaning of this evaluation context.
+semantics of multiple languages. To derive the usual operational semantics for
+the target language, the evaluation context merely needs to be defined as |conf
+tS te @= tS, bracket tE te|.  However, when we combine this language with an IFC
+language, we reinterpret the meaning of |conf tS te|.
 
-In general, we require that a target language be expressed in terms
-of some global machine state |tS|, some evaluation context |tE|,
-some expressions |te|, some set of values |tv| and a \emph{deterministic}
-reduction relation on full configurations $|tS| \times |tE| \times |te|$.
+%% \begin{figure}
+%% \begin{code}
+%% tv   ::= \tx.te | true | false | ta
+%% te   ::= tv | tx | te te | if te then te else te
+%%        | ref te | !te | te := te | fix te
+%% tE   ::= tHole | tE te | tv tE | if tE then te else te
+%%        | ref tE | !tE | tE := te | tv := tE | fix tE
 
-\begin{figure}
-\begin{code}
-tv   ::= \tx.te | true | false | ta
-te   ::= tv | tx | te te | if te then te else te
-       | ref te | !te | te := te | fix te
-tE   ::= tHole | tE te | tv tE | if tE then te else te
-       | ref tE | !tE | tE := te | tv := tE | fix tE
+%% te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
+%% let tx = te1 in te2  @= (\tx.te2) te1
+%% \end{code}
 
-te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
-let tx = te1 in te2  @= (\tx.te2) te1
-\end{code}
+%% \begin{mathpar}
 
-\begin{mathpar}
+%% \inferrule[T-app]
+%% { } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}
 
-\inferrule[T-app]
-{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}
+%% \and
+%% \inferrule[T-ifTrue]
+%% { } {| conf tS (if true then te1 else te2) -> conf tS te1|}
 
-\and
-\inferrule[T-ifTrue]
-{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}
+%% \and
+%% \inferrule[T-ifFalse]
+%% { } {| conf tS (if false then te1 else te2) -> conf tS te2|}
 
-\and
-\inferrule[T-ifFalse]
-{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}
+%% \and
+%% \inferrule[T-ref]
+%% { | fresh ta | }
+%% {| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
 
-\and
-\inferrule[T-ref]
-{ | fresh ta | }
-{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
+%% \and
+%% \inferrule[T-deref]
+%% { |memberf ((ta, tv)) tS| }
+%% {| conf tS (!ta) -> conf tS (tv) |}
 
-\and
-\inferrule[T-deref]
-{ |memberf ((ta, tv)) tS| }
-{| conf tS (!ta) -> conf tS (tv) |}
+%% \and
+%% \inferrule[T-ass]
+%% { }
+%% {| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}
 
-\and
-\inferrule[T-ass]
-{ }
-{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}
+%% \and
+%% \inferrule[T-fix]
+%% { }
+%% {| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}
 
-\and
-\inferrule[T-fix]
-{ }
-{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}
+%% %\and
+%% %\inferrule[T-fail]
+%% %{ }
+%% %{| conf tS ( tE [ fail ] ) -> conf tS fail |}
+%% \end{mathpar}
 
-%\and
-%\inferrule[T-fail]
-%{ }
-%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
-\end{mathpar}
-
-\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
-mutable references and general recursion. |FV(te)| returns the set of free
-variables in expression |te|.}
-\label{fig:ml}
-\end{figure}
+%% \caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
+%% mutable references and general recursion. |FV(te)| returns the set of free
+%% variables in expression |te|.}
+%% \label{fig:ml}
+%% \end{figure}
 
@@
 %%     receiver must be at least as high as the message label.
-    \item A sandboxing operation used to spawn new isolated tasks. In
-    concurrent settings |fork| corresponds to a fork-like primitive,
-    whereas in a
-    sequential setting, it more closely resembles the LIO
-    |toLabeled|~\cite{lio} and Breeze
-    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.
+    \item A sandboxing operation used to spawn new isolated tasks. In concurrent
+      settings |fork| corresponds to a fork-like primitive, whereas in a
+      sequential setting, it more closely resembles a sub-computation which might
+      temporarily raise the floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.
 \end{itemize}
@@
 
-\subsection{The Embedding}
-Figure~\ref{fig:embedding}
-provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
-The most important feature of this embedding is that every task maintains its own
-copy of the target language global state and evaluation context, thus
-enforcing isolation between various tasks.  In more detail:
+\subsection{Monitored executions}
+Figure~\ref{fig:embedding} provides all of the rules responsible for % actually
+carrying out the embedding of the IFC language with the target language. The
+resulting semantics then guarantees that programs written in the target language are
+monitored. The most important feature of this embedding is that every task
+maintains its own copy of the target language global state and evaluation
+context, thus enforcing isolation between various tasks.  In more detail:
 
@@
 is the question of what the target language state of the new task should
-be.  Our rule is stated generically in terms of a function |klone|.
+be.  Our rule is stated generically in terms of a the function |klone|.
 Conservatively, |klone| may be simply thought of as the identity
@@
 when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
-to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
-discussion of the implications of the choice of |klone|, but all our
-security claims will hold regardless of the choice of |klone|.
+to remove certain entries from the state.
+\Red{Ale: TODO we need to say that what is important about k is that there is no
+sharing between tasks. Moreover, |klone| should be implementable either by the
+target language or its runtime system}
+% ---we will discuss   In Section~\ref{sec:concrete}, we give a more detailed
+% discussion of the implications of the choice of |klone|, but all our
+% security claims will hold regardless of the choice of |klone|.
 
@@
 %
-As an example, taking |targetLangML| as the target language, we can now define a
-blocking receive (inefficiently) in terms of the asynchronous |recv| as series
-of cross-language calls:
-\begin{code}
-  brecvf ix1 ix2 ie @=
-  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
-\end{code}
+%% As an example, taking |targetLangML| as the target language, we can now define a
+%% blocking receive (inefficiently) in terms of the asynchronous |recv| as series
+%% of cross-language calls:
+%% \begin{code}
+%%   brecvf ix1 ix2 ie @=
+%%   tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
+%% \end{code}
 
-We note that our embedding corresponds to the lump embedding
-of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
-treated opaquely in the other.
-%
-Indeed since our embedding is defined for an arbitrary language |targetLang|,
-we cannot do better.
-%
-However, when we have more information about the target language, it is
-possible to add rules for a natural embedding of expressions that occur in both
-languages.  In our specific example with |targetLangML|, we can choose to
-preserve booleans across language boundaries as follows:
-\begin{mathpar}
-\inferrule
-{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-\and
-\inferrule
-{ |b member {true, false}| } {| intE (TI b) -> intE b |}
-\end{mathpar}
+%% We note that our embedding corresponds to the lump embedding
+%% of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
+%% treated opaquely in the other.
+%% %
+%% Indeed since our embedding is defined for an arbitrary language |targetLang|,
+%% we cannot do better.
+%% %
+%% However, when we have more information about the target language, it is
+%% possible to add rules for a natural embedding of expressions that occur in both
+%% languages.  In our specific example with |targetLangML|, we can choose to
+%% preserve booleans across language boundaries as follows:
+%% \begin{mathpar}
+%% \inferrule
+%% { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
+%% \and
+%% \inferrule
+%% { |b member {true, false}| } {| intE (TI b) -> intE b |}
+%% \end{mathpar}
 
 For any target language |targetLang| and scheduling policy |alpha|, this
-embedding defines an IFC language, which we will
+embedding defines a coarse-grained IFC-aware language, which we will
 refer to as |specLang alpha targetLang|.

### 2014-10-16 paper/abstract.tex
nit on abstract

@@
 alternative technique based on attaching a single IFC policy to a single
-execution context, and therefore abstracting away from the internals of
+execution context, and therefore abstracting away from most of the internals of
 JavaScript. Specifically, we provide a coarse-grained IFC monitor which does not
 require any modifications to either JavaScript's semantics or its engine---the
-approach only exposes a small API to JavaScript code in order to interact
-with the monitor. To reason about our design principles, we describe a formal
+approach only exposes a small API to JavaScript code in order to interact with
+the monitor. To reason about our design principles, we describe a formal
 framework which treat target languages, e.g. JavaScript, as black-boxes with a

### 2014-10-16 paper/real.tex
remove Haskell and C explanations

@@
 
-\subsection{Haskell}
-\label{sec:real:hs}
-Our work borrows ideas from a Haskell coarse-grained IFC
-system called LIO~\cite{lio, stefan:addressing-covert}.
-%
-LIO relies on Haskell's strong type system and monadic encoding of
-side-effecting computations to achieve isolation and define the IFC
-sub-language.
-%
-Specifically LIO provides the \verb|LIO| monad as a way of restricting
-(almost all) side-effects; this monad also keeps track of a current
-label which is, in turn, used by trusted code when defining core IFC
-functions, such as |getLabel|.
-%
-In the context of our framework, LIO can be understood as follows: the
-\emph{pure subset} of Haskell is the target language, while the
-monadic subset of Haskell, operating in the \verb|LIO| monad, is the
-IFC language.
+%% \subsection{Haskell}
+%% \label{sec:real:hs}
+%% Our work borrows ideas from a Haskell coarse-grained IFC
+%% system called LIO~\cite{lio, stefan:addressing-covert}.
+%% %
+%% LIO relies on Haskell's strong type system and monadic encoding of
+%% side-effecting computations to achieve isolation and define the IFC
+%% sub-language.
+%% %
+%% Specifically LIO provides the \verb|LIO| monad as a way of restricting
+%% (almost all) side-effects; this monad also keeps track of a current
+%% label which is, in turn, used by trusted code when defining core IFC
+%% functions, such as |getLabel|.
+%% %
+%% In the context of our framework, LIO can be understood as follows: the
+%% \emph{pure subset} of Haskell is the target language, while the
+%% monadic subset of Haskell, operating in the \verb|LIO| monad, is the
+%% IFC language.
 
-%Indeed, by rephrasing LIO in terms of our framework, we simplified
-%LIO's treatment of exceptions.
-%
-LIO originally associated labels with exceptions, in a
-similar style to fine-grained
-systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
-%
-In particular, the label of an exception was set to the current label
-at the time of the throw, and used by a custom catch construct to
-raise the current label, thereby preventing leaks due to exceptional
-control flows.
-%
-In addition to being overly complex, the interaction of exceptions
-with clearance (which sets an upper bound on the current label, see
-Section~\ref{sec:clearance}) was incorrect: the clearance
-was restored to the clearance at point of the catch (a consequence of
-defining \verb|LIO| using a State monad).
-%
-Furthermore, pure exceptions (e.g., divide by zero) always percolated to
-trusted code, effectively allowing for denial of service attacks.
-%
-The insights gained when viewing coarse-grained IFC as presented in this
-paper led to a much cleaner, simpler treatment of exceptions in LIO,
-which has now been adapted by LIO.
-%By using isolated tasks, and thus treating the current label (and
-%clearance) as global, the underlying Haskell exception system can be
-%used directly: exceptional control flow does not affect IFC.
+%% %Indeed, by rephrasing LIO in terms of our framework, we simplified
+%% %LIO's treatment of exceptions.
+%% %
+%% LIO originally associated labels with exceptions, in a
+%% similar style to fine-grained
+%% systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
+%% %
+%% In particular, the label of an exception was set to the current label
+%% at the time of the throw, and used by a custom catch construct to
+%% raise the current label, thereby preventing leaks due to exceptional
+%% control flows.
+%% %
+%% In addition to being overly complex, the interaction of exceptions
+%% with clearance (which sets an upper bound on the current label, see
+%% Section~\ref{sec:clearance}) was incorrect: the clearance
+%% was restored to the clearance at point of the catch (a consequence of
+%% defining \verb|LIO| using a State monad).
+%% %
+%% Furthermore, pure exceptions (e.g., divide by zero) always percolated to
+%% trusted code, effectively allowing for denial of service attacks.
+%% %
+%% The insights gained when viewing coarse-grained IFC as presented in this
+%% paper led to a much cleaner, simpler treatment of exceptions in LIO,
+%% which has now been adapted by LIO.
+%% %By using isolated tasks, and thus treating the current label (and
+%% %clearance) as global, the underlying Haskell exception system can be
+%% %used directly: exceptional control flow does not affect IFC.
 
-\subsection{C}
-\label{sec:real:c}
-%
-C programs are able to execute arbitrary (machine) code, access
-arbitrary memory, and perform arbitrary system calls.
-%
-Thus, the confinement of C programs must be imposed by the underlying OS
-and hardware.
-%
-For instance, our notion of isolation can be achieved using Dune's
-hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
-similar to a simpler version of
-Wedge~\cite{Belay:2012:DSU:2387880.2387913,
-Bittau:2008:WSA:1387589.1387611} with an information flow control
-policy.
-%
-Using page tables, a (trusted) IFC runtime could ensure that each task,
-implemented as a lightweight process, can only access the memory it
-allocates---tasks do not have access to any shared memory.
-%
-In addition, ring protection could be used to intercept system
-calls performed by
-a task and only permit those corresponding to our IFC language (such as
-|getLabel| or |send|).
-%
-Dune's hardware protection mechanism would allow us to provide a concrete
-implementation that is efficient and relatively simple to reason
-about, but other sandboxing mechanisms could be used in place of Dune.
+%% \subsection{C}
+%% \label{sec:real:c}
+%% %
+%% C programs are able to execute arbitrary (machine) code, access
+%% arbitrary memory, and perform arbitrary system calls.
+%% %
+%% Thus, the confinement of C programs must be imposed by the underlying OS
+%% and hardware.
+%% %
+%% For instance, our notion of isolation can be achieved using Dune's
+%% hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
+%% similar to a simpler version of
+%% Wedge~\cite{Belay:2012:DSU:2387880.2387913,
+%% Bittau:2008:WSA:1387589.1387611} with an information flow control
+%% policy.
+%% %
+%% Using page tables, a (trusted) IFC runtime could ensure that each task,
+%% implemented as a lightweight process, can only access the memory it
+%% allocates---tasks do not have access to any shared memory.
+%% %
+%% In addition, ring protection could be used to intercept system
+%% calls performed by
+%% a task and only permit those corresponding to our IFC language (such as
+%% |getLabel| or |send|).
+%% %
+%% Dune's hardware protection mechanism would allow us to provide a concrete
+%% implementation that is efficient and relatively simple to reason
+%% about, but other sandboxing mechanisms could be used in place of Dune.
 
-In this setting, the combined language of Section~\ref{sec:retrofit}
-can be interpreted in the following way: calling from the target
-language to the IFC language corresponds to invoking a system call.
-%
-Creating a new task with the |sandbox| system call corresponds to
-\emph{forking} a process.  Using page tables we can ensure that
-there will be no shared memory
-(effectively
-defining |ap klone tS
-= tS0|, where |tS0| is the set of pages necessary to bootstrap a
-lightweight process.)
-%
-Similarly, control over page tables and protection bits allows us to
-define a |send| syscall that copies pages to our
-(trusted) runtime queue; and, correspondingly, a |recv| that copies
-the pages from the runtime queue to the (untrusted) receiver.
-%
-Since C is not memory safe, conditions on these system calls are
-meaningless.
-%
-We leave the implementation of this IFC system for C to future work.
+%% In this setting, the combined language of Section~\ref{sec:retrofit}
+%% can be interpreted in the following way: calling from the target
+%% language to the IFC language corresponds to invoking a system call.
+%% %
+%% Creating a new task with the |sandbox| system call corresponds to
+%% \emph{forking} a process.  Using page tables we can ensure that
+%% there will be no shared memory
+%% (effectively
+%% defining |ap klone tS
+%% = tS0|, where |tS0| is the set of pages necessary to bootstrap a
+%% lightweight process.)
+%% %
+%% Similarly, control over page tables and protection bits allows us to
+%% define a |send| syscall that copies pages to our
+%% (trusted) runtime queue; and, correspondingly, a |recv| that copies
+%% the pages from the runtime queue to the (untrusted) receiver.
+%% %
+%% Since C is not memory safe, conditions on these system calls are
+%% meaningless.
+%% %
+%% We leave the implementation of this IFC system for C to future work.

### 2014-10-16 paper/real.tex
Add todo for Deian in real and rephrase a bit the intro to the section

@@
 \label{sec:real}
+\Red{ALE: Here, Deian needs to fit the core part of COWL, i.e., with no external
+  effects. It will be nice to have the COWL API and map it to IFC-Inside}
 
@@
 %
-Indeed, our formalism serves as the theoretical foundation for two
-IFC systems for JavaScript, built on top of Node.js as well as
-the web browser engine Gecko.
+Indeed, we show how our formalism serves as the theoretical foundation for the
+core part of COWL~\cite{swapi}, a recent client-side coarse-grained IFC system
+for Firefox.
+%the web browser engine Gecko.
 
-In this section, we describe these two implementations.  Furthermore,
-we consider how our formalism could be applied to the C programming
-language and connect it to a previous IFC system for Haskell.
-%
-The goal of this section is to show the flexibility of the embedding in settings with
-vastly different properties and discuss the
-semantic gap that must be overcome to apply our formalism
-to other systems.
+%IFC systems for JavaScript, built on top of Node.js as well as
+
+%% Furthermore,
+%% we consider how our formalism could be applied to the C programming
+%% language and connect it to a previous IFC system for Haskell.
+%% %
+%% The goal of this section is to show the flexibility of the embedding in settings with
+%% vastly different properties and discuss the
+%% semantic gap that must be overcome to apply our formalism
+%% to other systems.
 %

### 2014-10-16 paper/extensions.tex
Pass on extensions

@@
 %%
-For example, COWL provides a labeled version of the XHR object, while
-LIO implements a labeled file system, used in server-side web
-applications~\cite{hails}.
+In fact, COWL provides a labeled version of the XHR object to perform external
+side-effects as well as labeled messages to avoid raising the
+floating-label in certain situations.
+
+%while
+%LIO implements a labeled file system, used in server-side web
+%applications~\cite{hails}.
 %%
@@
 %consider the addition of several labeled constructs to the abstract specification.
-In this section we show how to extend the language with several such
+In this section we show how to extend our framework with several such
 constructs.  For space reasons, we mainly provide the high-level
@@
 system can be extended with explicitly labeled
-values, much like those of LIO and
-Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
-inlinesep Labeled il ie|.
+values similarly as~\cite{lio, Hritcu:2013:YIB:2497621.2498098}:
+%, much like those of LIO and
+|iv ::= cdots inlinesep Labeled il ie|.
 %
-Following LIO, we say that the expression |ie| is protected by label |il|,
+%Following LIO,
+We say that the expression |ie| is protected by label |il|,
 while the label |il| itself is protected by the task's current label.
@@
 %
-The label of such values can be inspected the task without
+The label of such values can be inspected the a given task without
 requiring the current label to be raised.
@@
 %
-Systems like LIO, COWL, and Breeze additionally provide a discretionary access
+Similar to other systems, COWL additionally provide a discretionary access
 control (DAC) mechanism---called \emph{clearance}---at the language
-level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
+level~\cite{Zeldovich:2006,Hritcu:2013:YIB:2497621.2498098, lio}.
 %
@@
 accessing data (or communicating with entities) above a specified
-label, the clearance.
+label, i.e., the clearance.
 %
@@
 %
-However, this does not implement any DAC mechanism yet.
+To extend our framework with clearance, it is enough to
+a family of predicates to each rule
+%However, this does not implement any DAC mechanism yet.
 %
 To do so, we can restrict the language with a family of predicates
-$\mathcal{P}_\text{clearance}$:
-All rules that
+%$\mathcal{P}_\text{clearance}$:
+%All rules
+that
 raise the current label (e.g., \textsc{I-setLabel}), perform
 allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
-clearance (clearance should not be arbitrarily raised), a predicate
-that uses the clearance to impose DAC is used.
+clearance (clearance should not be arbitrarily raised).
+%, a predicate
+%that uses the clearance to impose DAC is used.
 %
@@
 current label from being raised above the clearance (and thus permit
-reads above the clearance).  The predicate $P := |il
+reads above the clearance).  More specifically, the predicate $P := |il
 canFlowTo il'|$ achieves this restriction, where |il'| is the
@@
 \subsection{Privileges}
-Decentralized IFC extends IFC with the decentralized label model of
-Myers and Liskov~\cite{myers:dlm} to allow for more general
-applications, including systems consisting of mutually distrustful
-parties.  In a decentralized system, a computation is executed with a
-set of \emph{privileges}, which, when exercised, allow the computation
-to declassify data (e.g., by lowering the current label).
+%Decentralized IFC extends IFC with the decentralized label model of
+%Myers and Liskov~\cite{myers:dlm} to allow for more general
+%applications, including systems consisting of mutually distrustful
+%parties.
+In COWL, as well as other decentralized IFC systems~\cite{myers:dlm}, a
+computation is executed with a set of \emph{privileges}, which, when exercised,
+allow the computation to declassify data (e.g., by lowering the current label).
 %
@@
 %
-The challenge with such an extension lies in the precise
-security guarantees that must be proved, which to the best of our
-knowledge is an open research problem.
-
-Our implementation for Node.js and COWL both provide privileges, but
-we have not formalized this part any further.
+The challenge with such an extension lies in the precise security guarantees
+that must be proved, which, to the best of our knowledge, is an open research
+problem.
 %
+%COWL provides support for privileges,
+We have not formalized this part any further.
 %Addressing this problem is a natural direction for this work.
@@
 
-In this section we state some limitations of the current system, and
-outline potential future directions to alleviate these limitations.
+In this section, we state some limitations of our formal approach, and
+outline potential future directions to alleviate them. %these limitations.
 

### 2014-10-16 paper/extensions.tex
Pass on limitations

@@
 %consider the addition of several labeled constructs to the abstract specification.
-In this section we show how to extend our framework with several such
+In this section, we show how to extend our framework with several such
 constructs.  For space reasons, we mainly provide the high-level
@@
 \label{sec:extensions:types}
+\Red{Ale: I don't get this part. Why are we talking about type-safety? Is the
+  problem that the combined semantics does not get stuck when the target does?
+  Is type-safety a manner to get progress?}
 
@@
 %
-For simplicity, we do not treat this, more-general class of schedulers;
+For simplicity, we do not treat more-general class of schedulers;
 doing so would require modifying our calculus to keep track of the
@@
 \emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
-which states that a program is secure only if |l|-equivalent results are
+where programs are secure only if |l|-equivalent results are
 deterministic.
@@
 %
-For example, code in an IFC browser must load resources or
-perform XHR to be useful.
+For example, COWL must load resources or perform XHR to be useful.
 
-Like labeled references, features with external effects must be
+Like labeled references, features with external effects must be explicitly
 modeled in the IFC language; we must reason about the precise security
@@
 %
-An alternative approach is to model such effects as messages to/from
-certain labeled tasks, an approach taken by our Node.js
-implementation.
-%
-These ``special'' tasks are trusted with access to the unlabeled
-primitives that can be used to perform the external effects; since the
-interface to these tasks is already part of the IFC language, the
-proof only requires showing that this task does not leak information.
-%
-An alternative approach of restricting or wrapping unsafe primitives
-is, for example, used in COWL and JSFlow, respectively, to allow for
-controlled network communication.
+%% An alternative approach is to model such effects as messages to/from
+%% certain labeled tasks, an approach taken by our Node.js
+%% implementation.
+%% %
+%% These ``special'' tasks are trusted with access to the unlabeled
+%% primitives that can be used to perform the external effects; since the
+%% interface to these tasks is already part of the IFC language, the
+%% proof only requires showing that this task does not leak information.
+%% %
+Alternatively, COWL and JSFlow wrap unsafe primitives
+%is, for example, used in COWL and JSFlow, respectively,
+in order to allow for controlled network communication.
 %

### 2014-10-16 paper/related.tex
Pass related

@@
 %control.
-Our information flow control system is closely related
-to the coarse-grained information systems used in operating systems such
+Our information flow control system is influenced by
+coarse-grained information systems used in operating systems such
 as Asbestos~\cite{efstathopoulos:asbestos},
-HiStar~\cite{Zeldovich:2006}, and Flume~\cite{krohn:flume}, as well as language-based
-\emph{floating-label IFC systems} such as LIO~\cite{lio},
+HiStar~\cite{Zeldovich:2006}, and Flume~\cite{krohn:flume}. Moreover, our work
+is closely related to language-based \emph{floating-label IFC systems} such as LIO~\cite{lio},
 and Breeze~\cite{Hritcu:2013:YIB:2497621.2498098}, where there is a
 monotonically increased label
-associated with threads of execution.
+associated with threads of execution. Different from LIO and Breeze, our
+framework handles asynchronous messages and provides security guarantees where
+no assumptions are made about the target language. In fact, our framework can be
+seen as a generalization of such approaches.
 Our treatment of termination-sensitive and termination-insensitive interference
@@
 cost of complexity (the system must accommodate the entirety of JavaScript's
-semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
-higher than 100\%~\cite{JSFlow}.  Alternatively, coarse-grained
-approaches to security have also been proposed for the web
-scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
+semantics).
+%Moreover, the runtime performance cost are sometimes too high, e.g.,
+%higher than 100\%~\cite{JSFlow}.
+Alternatively, coarse-grained approaches to security have also been proposed for
+the web scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
+Different from them, our formal results can accommodate with almost no effort to
+different versions of ECMAScripts, i.e., different target languages.
 
@@
 can find out when sending a message failed due to a forbidden information flow),
-and they include no security proofs.
+and they include no soundness results. %security proofs.
 
 There appears to be limited literature in general techniques for retrofitting
-information flow control to arbitrary languages; however, one time-honored
+information flow control into arbitrary languages; however, one time-honored
 technique is defining a fundamental calculus, for which other languages can be
@@
 
-Our definition of isomorphism of information flow control languages in
-Section~\ref{sec:concrete} is closely related to the idea of
-\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
-although as our system is deterministic, we do not use the theory in any
-deep way.
+%% Our definition of isomorphism of information flow control languages in
+%% Section~\ref{sec:concrete} is closely related to the idea of
+%% \emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
+%% although as our system is deterministic, we do not use the theory in any
+%% deep way.
 

### 2014-10-16 paper/conclusion.tex
Pass conclusions

--- 2014-07-08 paper/conclusion.tex
@@
 system, it is better to start with a fully isolated, multi-task system
-and work one's way back to the model of a single language.  We showed
-how to prove systems designed this way can be proved noninterferent,
-without needing to rely on details of the target language, and
-we provided conditions on how to securely refine our formal semantics to
-consider optimizations required in practice.  We connected our semantics
-to existing IFC implementations for JavaScript and Haskell, and proposed
-an IFC system for C using hardware isolation.
+and work one's way back to the model of a single IFC-aware language.  We showed
+a formal framework capable to prove secure (i.e. non-interferent) systems designed this way,
+without needing to rely on details of the target language.
+%, and
+%we provided conditions on how to securely refine our formal semantics to
+%consider optimizations required in practice.
+We provide soundness guarantees for the COWL's JavaScript monitor by simply
+connecting our framework to that implementation.
+%% to two IFC implementations for JavaScript based on this formalism,
+%% explained how our methodology improved an exiting IFC system for Haskell,
+%% and proposed
+%% an IFC system for C using hardware isolation.
 By systematically applying ideas from IFC in operating systems to programming languages,

### 2014-10-16 paper/formal.tex
Pointer to extended version

@@
 
-We are interested in proving non-interference about many programming
-languages.  This requires an appropriate definition of this notion
-that is language agnostic, so in this section, we present a few
-general definitions for what an information flow control language is
-and what non-interference properties it may have.  We also state
-theorems about our system which we prove in Section~\ref{sec:proofs}.
-In particular, we show that |specLang alpha targetLang|, with an appropriate
-scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
-without making any reference to properties of |targetLang|.
+% We are interested in proving non-interference about many programming
+% languages.
+%This requires an appropriate definition of this notion
+%that is language agnostic, so
+
+In this section, we present a few general and target-language agnostic
+definitions for what an information flow control language is and what
+non-interference properties it may have.  We also state theorems about our
+system. %which we prove in Section~\ref{sec:proofs}.  In particular, we show
+that |specLang alpha targetLang|, with an appropriate scheduler |alpha|,
+satisfies non-interference~\cite{Goguen82}, without making any reference to
+properties of |targetLang|. For technical details, interested readers can refer
+to the extended version of this paper~\footnote{\url{http://informationflowcontrol.net/ifc-inside/paper.pdf}}.
 
@@
 %
-consider a target language similar to |targetLangML| with an
-additional expression terminal |diverge| that denotes a divergent computation,
-i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
-sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
+consider a target language with a standard branching construct |if e then e else
+e|
+%similar to |targetLangML|
+and an additional expression terminal |diverge| that denotes a divergent
+computation, i.e., |diverge| always reduces to |diverge| and a simple label
+lattice |{pub, sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
 Consider the following two configurations in this language:

### 2014-10-17 paper/retrofit.tex
improve figures for one-column layout

--- 2014-07-08 paper/retrofit.tex
@@
 explicitly ensure that |toLabeled| does not propagate exceptions.
-
+%
 When stack frames are treated as isolated tasks, the correct semantics
@@
 tv   ::= \tx.te | true | false | ta
-te   ::= tv | tx | te te | if te then te else te
-       | ref te | !te | te := te | fix te
-tE   ::= tHole | tE te | tv tE | if tE then te else te
-       | ref tE | !tE | tE := te | tv := tE | fix tE
-
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fix te
+tE   ::= tHole | tE te | tv tE | if tE then te else te | ref tE | !tE | tE := te | tv := tE | fix tE
 te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
@@
 \end{code}
-
 \begin{mathpar}
@@
 \begin{code}
-lop  ::=  canFlowTo | lub | glb
-iv   ::=  id | il | true | false | unit
-ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie | getTaskId
-       |  sandbox ie | send ie ie ie | recvf ix ix ie ie
-iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE
-       |  send iE ie ie | send iv iE ie | send iv iv iE
-io   ::=  (il, id ie)
-Q    ::=  nil | io , Q
-iS   ::=  emptyset | bracket iS (mapsto id Q)
+iv   ::=  id | il | true | false | unit qquad qquad lop  ::=  canFlowTo | lub | glb
+ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie | getTaskId |  sandbox ie
+       | send ie ie ie | recvf ix ix ie ie
+iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE |  send iE ie ie | send iv iE ie | send iv iv iE
+io   ::=  (il, id ie)  qquad qquad   Q    ::=  nil | io , Q   qquad   iS   ::=  emptyset | bracket iS (mapsto id Q)
 \end{code}
-
 \begin{mathpar}
@@
 { |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
+
 \end{mathpar}
@@
 %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
-\begin{tabular}{ll}
+\begin{tabular}{lll}
 \begin{minipage}{.22\textwidth}
@@
 \end{code}
-\end{minipage}
-\end{tabular}
-
+\end{minipage} &
+\begin{minipage}{.42\textwidth}
 \begin{code}
@@
 \end{code}
-
+\end{minipage}
+\end{tabular}
 \begin{mathpar}
@@
 \begin{figure}
-  Concurrent, round robin:
+\begin{tabular}{ll}
+\begin{minipage}{.45\textwidth}
 \begin{code}
@@
 \end{code}
-  Sequential:
+\end{minipage} &
+\begin{minipage}{.45\textwidth}
 \begin{code}
@@
 \end{code}
-\caption{Scheduling policies}
+\end{minipage}
+\end{tabular}
+\caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}
 \label{fig:scheduler}

### 2014-10-17 paper/appendix.tex
move semantics to appendix

@@
 \appendix
+
+\section{Full Semantics for |targetLangML|}
+\label{sec:app:semantics}
+
+In Figure~\ref{fig:ml-full} we give the full semantics for |targetLangML|.  A subset
+of them has been given in Figure~\ref{fig:ml} earlier in the paper.
+
+\begin{figure}
+\begin{code}
+tv   ::= \tx.te | true | false | ta
+te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fix te
+tE   ::= tHole | tE te | tv tE | if tE then te else te | ref tE | !tE | tE := te | tv := tE | fix tE
+te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
+let tx = te1 in te2  @= (\tx.te2) te1
+\end{code}
+\begin{mathpar}
+
+\inferrule[T-app]
+{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}
+
+\and
+\inferrule[T-ifTrue]
+{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}
+
+\and
+\inferrule[T-ifFalse]
+{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}
+
+\and
+\inferrule[T-ref]
+{ | fresh ta | }
+{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
+
+\and
+\inferrule[T-deref]
+{ |memberf ((ta, tv)) tS| }
+{| conf tS (!ta) -> conf tS (tv) |}
+
+\and
+\inferrule[T-ass]
+{ }
+{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}
+
+\and
+\inferrule[T-fix]
+{ }
+{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}
+
+\end{mathpar}
+
+\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
+mutable references and general recursion. |FV(te)| returns the set of free
+variables in expression |te|.}
+\label{fig:ml-full}
+\end{figure}
 

### 2014-10-17 paper/retrofit.tex
move semantics to appendix

@@
 
-\begin{figure}
+When considering tasks, we will instead say that the allocation of a new
+stack frame with a raised label corresponds to the creation of a new
+isolated task; a sample encoding using our language is as follows:
 \begin{align*}
@@
 \end{align*}
-\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
-\end{figure}
-
-When considering tasks, we will instead say that the allocation of a new
-stack frame with a raised label corresponds to the creation of a new
-isolated task; a sample encoding using our language is shown in
-Figure~\ref{fig:toLabeled}.
 There is one more ingredient: in a stack discipline, one generally
@@
 
-\and
-\inferrule[T-ifFalse]
-{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}
-
-\and
-\inferrule[T-ref]
-{ | fresh ta | }
-{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}
-
-\and
-\inferrule[T-deref]
-{ |memberf ((ta, tv)) tS| }
-{| conf tS (!ta) -> conf tS (tv) |}
-
-\and
-\inferrule[T-ass]
-{ }
-{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}
-
-\and
-\inferrule[T-fix]
-{ }
-{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}
-
-%\and
-%\inferrule[T-fail]
-%{ }
-%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
 \end{mathpar}
@@
 \caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
-mutable references and general recursion. |FV(te)| returns the set of free
-variables in expression |te|.}
+mutable references and general recursion.  For space reasons we only show two
+representative reduction rules;  full rules can be found in \appref{sec:app:semantics}.}
 \label{fig:ml}

### 2014-10-17 paper/retrofit.tex
save some space in figures

@@
 Specifically, receiving a message using
-\[ |recvf ix1 ix2 ie1 ie2| \]
+$|recvf ix1 ix2 ie1 ie2|$
 binds the message and the sender's task identifier
@@
 |}
+\hspace*{-0.5cm}
 
@@
 |}
+\hspace*{-0.5cm}
 
 \and
-\inferrule[I-setLabel]
-{ |il canFlowTo il'| }
-{|
-niconf iS id il (setLabel il')
-->
-niconf iS id il' unit
-|}
+\inferrule[I-labelOp]
+{ |denot (il1 lop il2) = iv|}
+{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
 
@@
 
-\inferrule[I-labelOp]
-{ |denot (il1 lop il2) = iv|}
-{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
+\and
+\inferrule[I-setLabel]
+{ |il canFlowTo il'| }
+{|
+niconf iS id il (setLabel il')
+->
+niconf iS id il' unit
+|}
 

### 2014-10-17 paper/formal.tex
more space savings in figures

--- 2014-07-07 paper/formal.tex
@@
   \end{cases} \\
-  &|erase il emptyset = emptyset|\\
   &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
-    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
-    & \text{the label of thread |id|} \\
+    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is the label of thread |id|}\\
     |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
   \end{cases} \\
-  &|erase il Q = filter il Q|
+  &|erase il Q = filter il Q|  \qquad\qquad\qquad  |erase il emptyset = emptyset|
 \end{align*}
+\vspace*{-0.8cm}
 \caption{ Erasure function for tasks, queue maps, message queues, and

### 2014-10-17 paper/intro.tex
Small changes to the intro

--- 2014-10-16 paper/intro.tex
@@
 websites that may not even be aware of each other's existence.)
-%While just-in-time combination of untrusting components
-%offers great flexibility, it also poses complex security challenges.
-%In particular,
-Maintaining data privacy in the face of malicious
-extensions, libraries, and mashup components has been rather difficult.
-%and in general effectively impossible.
+While just-in-time combination of untrusting components
+offers great flexibility, it also poses complex security challenges.
+In particular, maintaining data privacy in the face of malicious
+extensions, libraries, and mashup components has been difficult,
+and in general effectively impossible.
 
-Information flow control (IFC) is a promising technique that provides security
-by tracking the flow of sensitive data through a system.  Untrusted code is
-confined so that it cannot exfiltrate data, except as per an information flow
-policy.  Significant research has been devoted to adding various forms of IFC to
-different kinds of programming languages and systems.  In the context of the
-web, however, there is a strong motivation to preserve JavaScript's semantics
-and avoid any modification to its engine.
-%, while retrofitting it with dynamic
-%information flow control.
+Information flow control (IFC) is a promising technique
+that provides security
+by tracking the flow of sensitive data through a system.
+Untrusted code is confined so that it cannot exfiltrate data, except as
+per an information flow policy.  Significant research has been devoted to
+adding various forms of IFC to different kinds of programming languages
+and systems.  In the context of the web, however, there is a strong
+motivation to preserve JavaScript's semantics \Red{and avoid any modifications
+  to its engine}, while retrofitting it with dynamic information
+flow control.
 
-%%% Ale: Related work?
-%% One approach to information flow control is fine-grained tracking,
-%% which offers great flexibility.
-%% However, these systems
-%% require deep integration with the programming language and modify
-%% the semantics in non-trivial ways.  This makes fine-grained systems
-%% less suitable in contexts where preserving an existing language
-%% is important.
+\Red{\sout{One approach to information flow control is fine-grained tracking,
+which offers great flexibility.
+However, these systems
+require deep integration with the programming language and modify
+the semantics in non-trivial ways.  This makes fine-grained systems
+less suitable in contexts where preserving an existing language
+is important.
 %
-%% Moreover, the task of adding fine-grained IFC even to a simple language is
-%% non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
-%% such as JavaScript, this challenge becomes almost insurmountable.
+Moreover, the task of adding fine-grained IFC even to a simple language is
+non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
+such as JavaScript, this challenge becomes almost insurmountable.}}
 
-Inspired by OS research~\cite{}, we present a \textit{coarse-grained} dynamic
-IFC monitor to JavaScript (as specified by ECMAScript~\cite{}). Specifically,
-JavaScript code is divided into relatively coarse computational units
-(i.e. workers), each with a single label dictating its security policy. As a
-result, it is just enough to track communication between isolated computational
-units.
+%In the alternative \textit{coarse-grained} approach to IFC,
+\Red{Operating systems research (e.g.~\cite{Zeldovich:2006}) proposes
+\textit{coarse-grained} approaches to IFC, where}
+a system is divided into relatively coarse computational units,
+each with a single label dictating its security policy.
+Only
+communication between isolated computational units must be tracked.
 %A recent system named COWL~\cite{swapi} adds IFC to the
@@
 %influencing the computation of less sensitive workers.
-This technique provides a number of advantages: (1) no changes to JavaScript's
-semantics when adding IFC ---our approach only exposes an small API to
-JavaScript code in order to interact with the monitor---, and
-% which (2) allows
-%the reuse of existing programs.  Furthermore,
-(2) reduced runtime overhead because checks only need to be performed at isolation
-boundaries instead of at every instruction in the code~\cite{JSFlow}.
-%, compared to fine-grained systems were the runtime overhead can be
-% impractical~\cite{JSFlow}.
-Finally, (3) associating a single security label with the entire computational
-unit simplifies understanding and reasoning about the correctness of the system,
-without reasoning about most of the semantics details of JavaScript.
-% underlying programming language, i.e., JavaScript.
+This coarse-grained approach provides a number of advantages:
+(1) minimal changes to an
+existing programming language when adding IFC, which (2) allows
+the reuse of existing programs.  Furthermore, (3)
+reduced runtime overhead because checks need only
+be performed at isolation boundaries
+\Red{instead of at every instruction in the code~(e.g. \cite{JSFlow})}.
+%, compared to fine-grained
+%systems were the runtime overhead can be impractical~\cite{JSFlow}.
+Finally, (4) associating
+a single security label with the entire computational unit simplifies
+understanding and reasoning about \Red{the security guarantees} of the
+system, without \sout{information flow} reasoning about \Red{most of} the
+technical details of the semantics of the \Red{underlying} programming language.
 
-To reason about our monitor, we introduce a \emph{generic} formalism which
-translates coarse-grained IFC ideas~\cite{Zeldovich:2006} into a language-based
-setting: an information flow control system should be thought of as multiple
-instances of \emph{completely isolated language runtimes} or \emph{tasks}, with
-information flow control applied to inter-task communication.
-% We describe a
-% formal framework in which an IFC system can be designed once and then applied to
-% any programming language which has control over external effects like
-% JavaScript.
-%(e.g., JavaScript) or C with access to hardware privilege separation).
-We formalize our framework by using the Matthews-Findler's
-approach~\cite{Matthews:2007:OSM:1190216.1190220} for combining operational
-semantics and prove non-interference guarantees that are independent of the
-choice of the specific underlying programming language, e.g., JavaScript.
-%framework to , being one instead of
-%that ECMAScript. %target language.
+In this paper, \Red{we present a framework which translates coarse-grained IFC
+ideas into a language-based setting}:
+%take coarse-grained labeling~\cite{Zeldovich:2006,
+%lio} to its logical extreme:
+an information flow control system should
+be thought of as multiple instances of completely isolated language
+runtimes or \emph{tasks}, with information flow control applied to
+inter-task communication.  We describe a formal system in which an IFC
+system can be designed once and then applied to any programming language
+which has control over external effects (e.g., JavaScript or C with
+access to hardware privilege separation).  We formalize this system
+using an approach by
+Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
+operational semantics and prove non-interference guarantees
+that are independent of the choice of specific target language.
 
-%% There are a number of points that distinguish this setting from
-%% previous coarse-grained IFC systems.
-%% %
-%% First, even though the underlying semantic model involves communicating
-%% tasks, these tasks can be coordinated together in ways that simulate
-%% features of traditional languages.
-%% %
-%% In fact, simulating
-%% features in this way is a useful \emph{design tool} for discovering
-%% what variants of the features are permissible and which are not.
-%% %
-%% Second, although completely separate tasks are semantically easy to
-%% reason about, real-world implementations often blur the lines between
-%% tasks in the name of efficiency.
-%% Characterizing what optimizations are permissible is subtle, since
-%% removing transitions from the operational semantics of a language can
-%% break non-interference.  We partially address this issue
-%% by characterizing isomorphisms between the operational semantics of our
-%% abstract language and a concrete implementation, showing that if this
-%% relationship holds, then non-interference in the abstract specification
-%% carries over to the concrete implementation.
+There are a number of points that distinguish this setting from
+previous coarse-grained IFC systems.
+%
+First, even though the underlying semantic model involves communicating
+tasks, these tasks can be coordinated together in ways that simulate
+features of traditional languages.
+%
+In fact, simulating
+features in this way is a useful \emph{design tool} for discovering
+what variants of the features are permissible and which are not.
+%
+Second, although completely separate tasks are semantically easy to
+reason about, real-world implementations often blur the lines between
+tasks in the name of efficiency.
+Characterizing what optimizations are permissible is subtle, since
+removing transitions from the operational semantics of a language can
+break non-interference.  We partially address this issue
+by characterizing isomorphisms between the operational semantics of our
+abstract language and a concrete implementation, showing that if this
+relationship holds, then non-interference in the abstract specification
+carries over to the concrete implementation.
 
@@
 \begin{itemize}
-  \item We give formal semantics for a core coarse-grained dynamic information
-    flow control monitor which is agnostic to non-IFC constructs.
-    %We show how a
-  \item We show non-interefence results when target languages exhibit a notion
-    of isolated computations and control of external side-effects.
-    %large class of target languages can be combined with this IFC language and
-    %prove that the result provides
-    %non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
-  %% \item We provide a proof technique to show the non-interference
-  %% of a concrete semantics for a potentially optimized IFC language
-  %% by means of an isomorphism and show a class of restrictions on
-  %% the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
-  \item
-  %We have implemented an IFC system based on these semantics
-  %or Node.js, and
-  We connect our formalism to COWL~\cite{swapi}, a
-  client-side IFC monitor for JavaScript in Firefox.
-  %Furthermore, we outline an implementation for the C programming
-  %language.
-  %(Section~\ref{sec:real})
+  \item We give formal semantics for a core coarse-grained
+  dynamic information flow control language free of non-IFC constructs.
+  We then show how a large class of target languages can be combined
+  with this IFC language and prove that the result provides
+  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
+  \item We provide a proof technique to show the non-interference
+  of a concrete semantics for a potentially optimized IFC language
+  by means of an isomorphism and show a class of restrictions on
+  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
+  \item We have implemented an IFC system based on these semantics
+  for Node.js, and we connect our formalism to another implementation
+  based on this work
+  for client-side JavaScript in Gecko~\cite{swapi}.
+  Furthermore, we outline an implementation for the C programming
+  language.
+  (Section~\ref{sec:real})
 %  \item We show how to extend the Matthews-Findler method from just
@@
   more advanced concepts such as labeled values, labeled references, or a
-  notion of clearance. %(Section~\ref{sec:extensions})
+  notion of clearance. (Section~\ref{sec:extensions})
 \end{itemize}

### 2014-10-17 paper/appendix.tex
move single heap to appendix

@@
 \end{figure}
+
+\section{IFC Language with a Single Heap}
+\label{sec:single-heap}
+
+As a concrete instantiation of this proof technique, we show
+how to make implement our IFC language using a single heap and
+ensure its non-interference using the techniques presented.
+First, we can construct the restricted language
+|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
+the family of always valid predicates, except for the ones for
+\textsc{I-sandbox} and \textsc{I-send}, which we define as
+$ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) $
+where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
+That is, we do not restrict any rules except for \textsc{I-sandbox}
+and \textsc{I-send}.
+Since $P$ only depends on |ie|, which is part of the current
+task and thus never erased w.r.t.\ the label of the first task,
+this language satisfies non-interference by Theorem~\ref{thm:restricted}.
+
+\begin{figure}
+
+  \begin{mathpar}
+    \inferrule[C-sandbox]
+    {
+      \mathcal{AV}(|ie|) = \emptyset{}\\
+      |iS' = bracket iS (mapsto id' nil)|\\
+      |it1 = oneheapfullconf id il (iniE id')|\\
+      |itnew = oneheapfullconf id' il (TI ie)|\\
+      |fresh id'|
+    }
+    {|
+      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
+      .->
+      iS'; tS; sched box (it1, ldots, itnew)
+    |}
+    \and
+    \inferrule[C-send]
+    {
+      \mathcal{AV}(|ie|) = \emptyset{}\\
+      |canFlowTo2 il il'|\\
+      |iS(id') = Q|\\
+      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
+    }
+    {|
+      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
+      ->
+      iS; tS; sched step (oneheapfullconf id il unit, ldots)
+    |}
+  \end{mathpar}
+
+  \caption{A selection of the reduction rules for |concreteLangMl alpha|.}
+  \label{fig:concrete}
+\end{figure}
+
+The essential parts of the semantics for the concrete language
+with a single heap,
+which we call |concreteLangMl alpha|,
+are given in Figure~\ref{fig:concrete}.  Most rules are
+straight-forward translations of the rules in Figures~\ref{fig:ifc}
+and~\ref{fig:embedding} but for a single heap.  For conciseness, we
+only show the interesting ones.
+Now, we can show an isomorphism between this language and
+|restrictedLangNoRef alpha targetLangML|, which
+(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
+non-interference for an appropriate scheduling policy |alpha|.
+
+To this end, we represent addresses in the concrete language as
+pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
+address in the abstract system\footnote{Note that this does
+  not make the isomorphism trivial, as in the single heap, there
+  is nothing preventing task 1 to access an address (2,|ta|).
+  Furthermore, it is common to represent addresses in this way
+  for efficient garbage collection of dead tasks.}.
+We also formulate the following well-formedness condition for
+configurations:
+\[
+  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
+  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
+\]
+Essentially, every address in a given task must have the correct
+identifier as the first part of the address.  It is easy to
+see that the initial configuration satisfies this condition, and
+any step in the concrete semantics preserves the condition.
+Therefore, we only need to consider well-formed configurations,
+which allows us to give the two required functions
+|f| and |finv| for the isomorphism.  For conciseness, we only give
+the interesting parts of their definition,
+and leave out the straight-forward proof that they
+actually provide an isomorphism.
+\begin{itemize}
+  \item Addresses can be directly translated with
+  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
+  an address |ta| that occurs in task |id|.
+  \item |f| splits the single heap into multiple heaps based on
+  the |id| of the addresses.  |finv| produces a single heap
+  by translating the addresses and collapsing everything to a single
+  store.
+\end{itemize}
 

### 2014-10-18 paper/concrete.tex

@@
 More precisely, instead of using a configuration of the form
-\[|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|\]
+$|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|$
 we would like a single global heap as in
-\[|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|\]
+$|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|$
 
@@
 
-\subsection{IFC Language with a Single Heap}\label{sec:single-heap}
-
-As a concrete instantiation of this proof technique, we show
-how to make implement our IFC language using a single heap and
-ensure its non-interference using the techniques presented.
-First, we can construct the restricted language
-|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
-the family of always valid predicates, except for the ones for
-\textsc{I-sandbox} and \textsc{I-send}, which we define as
-\[ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) \]
-where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
-That is, we do not restrict any rules except for \textsc{I-sandbox}
-and \textsc{I-send}.
-Since $P$ only depends on |ie|, which is part of the current
-task and thus never erased w.r.t.\ the label of the first task,
-this language satisfies non-interference by Theorem~\ref{thm:restricted}.
-
-\begin{figure}
-
-  \begin{mathpar}
-    \inferrule[C-sandbox]
-    {
-      \mathcal{AV}(|ie|) = \emptyset{}\\
-      |iS' = bracket iS (mapsto id' nil)|\\
-      |it1 = oneheapfullconf id il (iniE id')|\\
-      |itnew = oneheapfullconf id' il (TI ie)|\\
-      |fresh id'|
-    }
-    {|
-      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
-      .->
-      iS'; tS; sched box (it1, ldots, itnew)
-    |}
-    \and
-    \inferrule[C-send]
-    {
-      \mathcal{AV}(|ie|) = \emptyset{}\\
-      |canFlowTo2 il il'|\\
-      |iS(id') = Q|\\
-      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
-    }
-    {|
-      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
-      ->
-      iS; tS; sched step (oneheapfullconf id il unit, ldots)
-    |}
-  \end{mathpar}
-
-  \caption{A selection of the reduction rules for |concreteLangMl alpha|.}
-  \label{fig:concrete}
-\end{figure}
-
-The essential parts of the semantics for the concrete language
-with a single heap,
-which we call |concreteLangMl alpha|,
-are given in Figure~\ref{fig:concrete}.  Most rules are
-straight-forward translations of the rules in Figures~\ref{fig:ifc}
-and~\ref{fig:embedding} but for a single heap.  For conciseness, we
-only show the interesting ones.
-Now, we can show an isomorphism between this language and
-|restrictedLangNoRef alpha targetLangML|, which
-(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
-non-interference for an appropriate scheduling policy |alpha|.
-
-To this end, we represent addresses in the concrete language as
-pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
-address in the abstract system\footnote{Note that this does
-  not make the isomorphism trivial, as in the single heap, there
-  is nothing preventing task 1 to access an address (2,|ta|).
-  Furthermore, it is common to represent addresses in this way
-  for efficient garbage collection of dead tasks.}.
-We also formulate the following well-formedness condition for
-configurations:
-\[
-  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
-  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
-\]
-Essentially, every address in a given task must have the correct
-identifier as the first part of the address.  It is easy to
-see that the initial configuration satisfies this condition, and
-any step in the concrete semantics preserves the condition.
-Therefore, we only need to consider well-formed configurations,
-which allows us to give the two required functions
-|f| and |finv| for the isomorphism.  For conciseness, we only give
-the interesting parts of their definition,
-and leave out the straight-forward proof that they
-actually provide an isomorphism.
-\begin{itemize}
-  \item Addresses can be directly translated with
-  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
-  an address |ta| that occurs in task |id|.
-  \item |f| splits the single heap into multiple heaps based on
-  the |id| of the addresses.  |finv| produces a single heap
-  by translating the addresses and collapsing everything to a single
-  store.
-\end{itemize}
+In~\appref{sec:single-heap} we give an example how this formalism can be used
+to show non-intereference of an implementation of IFC with a single heap.

### 2014-10-18 paper/retrofit.tex
doom

@@
 true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
-could be used to violate information flow control if the tasks had differing labels.
-At this point, the designer of an IFC system might add label checks to mutable references, to check the labels of the reader and writer---solving the leak, but also dooming the performance of mutable references in the system.
+could be used to violate information flow control if the tasks had
+differing labels.  At this point, the designer of an IFC system might
+add label checks to mutable references, to check the labels of the
+reader and writer. While this solves the leak, for languages like
+JavaScript, where references are prevalently used, this also dooms the
+performance of the system.
 
@@
 \end{tabular}
+\vspace*{-0.5cm}
 \caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}

### 2014-10-18 paper/retrofit.tex
Reference toLabeled changed by the semantics of it

--- 2014-10-17 paper/retrofit.tex
@@
     whereas in a
-    sequential setting, it more closely resembles the LIO
+    sequential setting, it more closely resembles
+
+    \sout{the LIO
     |toLabeled|~\cite{lio} and Breeze
-    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.
+    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.}
+    \Red{
+      computations which might temporarely raise the current
+      floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.
+    }
 \end{itemize}

### 2014-10-18 paper/appendix.tex

@@
 
-In the main body of the paper we have only sketched the proof structure
-for Lemma~\ref{lemma:rr-tsni-general}.  Here we give it with full
-details, and first state and proof another lemma that will be used in that
-proof.
+In this section we prove the theorems we have stated in the paper.
+We first observe that the non-interference claims for the languages
+|specLang seqf targetLang| and |specLang roundrobinf targetLang|
+in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
+from Theorem~\ref{thm:restricted}, where the set
+of predicates is the set of always valid predicates (i.e., no restriction).
 
-%\begin{lemma}
-%  For any task lists |its|, |its'|, and tasks |it|, |it'| we have that
-%  if
-%  \begin{enumerate}
-%    \item |iconf iS (it1, its) .-> iconf iS' (its')|
-%    \item $|erase il it1|=|bullet|$
-%  \end{enumerate}
-%  then
-%\end{lemma}
+Before we proceed with the proof of Theorem~\ref{thm:restricted},
+we state and proof two lemmas we will use.
 
@@
 
-%\begin{lemma}
-%  \label{lemma:erase-context}
-%  For any expressions |ie1|, |ie2|, |ie1'|, context |iE1| as well as
-%  label |il|, if
-%  \[ |ie1= iHole2 iE1 ie1'| \quad \land \quad |erase il ie1 = erase il ie2| \]
-%  then there exist |iE2|, |ie2'| such that
-%  \[ |ie2= iHole2 iE2 ie2'| \quad \land \quad
-%  |erase il ie1' = erase il ie2'|\neq|bullet| \]
-%  Similarly, for any
-%  expressions |ie1|, |ie2|, |te1'|, context |iE1| as well as
-%  label |il|, if
-%  \[ |ie1= tHole2 iE1 te1'| \quad \land \quad |erase il ie1 = erase il ie2| \]
-%  then there exist |iE2|, |te2'| such that
-%  \[ |ie2= tHole2 iE2 te2'| \quad \land \quad
-%  |erase il te1' = erase il te2'|\neq|bullet| \]
-%\end{lemma}
-%\begin{proof}
-%  TODO
-%\end{proof}
-
-\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
+\begin{lemma}
+  \label{lemma:rr-tsni-general}
+  We consider, for any target language |targetLang|,
+  the restricted IFC language |restrictedLang alpha targetLang|
+  (according to Definition~\ref{def:restricted}).
+  Then,
+  for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
+  \begin{equation} \label{eq:tsni-lemma-lhs}
+  |ic1| \approx_{|il|} |ic2|
+  \qquad \text{and} \qquad
+  |ic1| |.->| |ic1'|
+  \end{equation}
+  there exists a configuration |ic2'| such that
+  \begin{equation} \label{eq:tsni-lemma-rhs}
+  |ic1'| \approx_{|il|} |ic2'|
+  \qquad \text{and} \qquad
+  |ic2| |.->|^* |ic2'|
+  \ \text{.}
+  \end{equation}
+\end{lemma}
+\begin{proof}
   First, we observe there must be at least one task in |ic1|, otherwise
@@
 \end{proof}
+With this, it is easy to proof Theorem~\ref{thm:restricted} as follows.
+\begin{proof}[Proof of Theorem~\ref{thm:restricted}, TSNI]
+% short version:
+%  We prove the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+%  The base case for derivations
+%  of length 0 is trivial, allowing
+%  us to simply chose $|ic2'=ic2|$.  In the step case,
+%  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as
+%  $|ic1| |.->| |ic1''| |.->|^n |ic1'|$
+%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
+%  the first step and
+%  the induction hypothesis to the rest of the derivation sequence,
+%  we directly get the desired property.
+  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
+  The base case for derivations
+  of length 0 is trivial, allowing
+  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
+  the theorem holds for derivation sequences of length up to $n$, and show that it also
+  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
+  \[
+  |ic1| |.->| |ic1''| |.->|^n |ic1'|
+  \]
+  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
+  |ic''| with
+  \begin{equation} \label{eq:tsni-proof-1}
+  |ic1''| \approx_{|il|} |ic2''|
+  \qquad \text{and} \qquad
+  |ic2| |.->|^* |ic2''|
+  \end{equation}
+  Applying the induction hypothesis to
+  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
+  \begin{equation} \label{eq:tsni-proof-2}
+  |ic1'| \approx_{|il|} |ic2'|
+  \qquad \text{and} \qquad
+  |ic2''| |.->|^* |ic2'|
+  \end{equation}
+  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
+  us the right-hand side of the implication in the TSNI
+  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
+\end{proof}
+
+%\begin{lemma}
+%  For any task lists |its|, |its'|, and tasks |it|, |it'| we have that
+%  if
+%  \begin{enumerate}
+%    \item |iconf iS (it1, its) .-> iconf iS' (its')|
+%    \item $|erase il it1|=|bullet|$
+%  \end{enumerate}
+%  then
+%\end{lemma}

### 2014-10-18 paper/retrofit.tex
more space saving

@@
 
-We note that our embedding corresponds to the lump embedding
-of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
-treated opaquely in the other.
-%
-Indeed since our embedding is defined for an arbitrary language |targetLang|,
-we cannot do better.
-%
-However, when we have more information about the target language, it is
-possible to add rules for a natural embedding of expressions that occur in both
-languages.  In our specific example with |targetLangML|, we can choose to
-preserve booleans across language boundaries as follows:
-\begin{mathpar}
-\inferrule
-{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
-\and
-\inferrule
-{ |b member {true, false}| } {| intE (TI b) -> intE b |}
-\end{mathpar}
+%We note that our embedding corresponds to the lump embedding
+%of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
+%treated opaquely in the other.
+%%
+%Indeed since our embedding is defined for an arbitrary language |targetLang|,
+%we cannot do better.
+%%
+%However, when we have more information about the target language, it is
+%possible to add rules for a natural embedding of expressions that occur in both
+%languages.  In our specific example with |targetLangML|, we can choose to
+%preserve booleans across language boundaries as follows:
+%\begin{mathpar}
+%\inferrule
+%{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
+%\and
+%\inferrule
+%{ |b member {true, false}| } {| intE (TI b) -> intE b |}
+%\end{mathpar}
 

### 2014-10-18 paper/intro.tex

@@
 and systems.  In the context of the web, however, there is a strong
-motivation to preserve JavaScript's semantics \Red{and avoid any modifications
-  to its engine}, while retrofitting it with dynamic information
+motivation to preserve JavaScript's semantics and avoid
+JavaScript-engine modifications, while retrofitting it with dynamic information
 flow control.
 
-\Red{\sout{One approach to information flow control is fine-grained tracking,
-which offers great flexibility.
-However, these systems
-require deep integration with the programming language and modify
-the semantics in non-trivial ways.  This makes fine-grained systems
-less suitable in contexts where preserving an existing language
-is important.
-%
-Moreover, the task of adding fine-grained IFC even to a simple language is
-non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
-such as JavaScript, this challenge becomes almost insurmountable.}}
-
 %In the alternative \textit{coarse-grained} approach to IFC,
-\Red{Operating systems research (e.g.~\cite{Zeldovich:2006}) proposes
-\textit{coarse-grained} approaches to IFC, where}
-a system is divided into relatively coarse computational units,
-each with a single label dictating its security policy.
-Only
-communication between isolated computational units must be tracked.
+The Operating Systems community has tackled this challenge (e.g.,
+in~\cite{Zeldovich:2006}) by taking a \textit{coarse-grained} approach
+to IFC: dividing an application into coarse computational units,
+each with a single label dictating its security policy, and only
+monitoring communication between them.
+%Only communication between isolated computational units must be tracked.
 %A recent system named COWL~\cite{swapi} adds IFC to the
@@
 %influencing the computation of less sensitive workers.
-This coarse-grained approach provides a number of advantages:
-(1) minimal changes to an
-existing programming language when adding IFC, which (2) allows
-the reuse of existing programs.  Furthermore, (3)
-reduced runtime overhead because checks need only
+This coarse-grained approach provides a number of advantages when
+compared to the fine-grained approaches typically employed by language-based systems.
+First, adding IFC does not require intrusive changes to an
+existing programming language, thereby also allowing
+the reuse of existing programs.  Second, it has a small
+runtime overhead because checks need only
 be performed at isolation boundaries
-\Red{instead of at every instruction in the code~(e.g. \cite{JSFlow})}.
+instead of (almost) every program instruction~(e.g.,~\cite{JSFlow}).
 %, compared to fine-grained
 %systems were the runtime overhead can be impractical~\cite{JSFlow}.
-Finally, (4) associating
+Finally, by associating
 a single security label with the entire computational unit simplifies
-understanding and reasoning about \Red{the security guarantees} of the
-system, without \sout{information flow} reasoning about \Red{most of} the
-technical details of the semantics of the \Red{underlying} programming language.
+understanding and reasoning about the security guarantees of the
+system, without reasoning about most of the
+technical details of the semantics of the underlying programming language.
+\Red{ds: this last senstence needs work}
 
-In this paper, \Red{we present a framework which translates coarse-grained IFC
-ideas into a language-based setting}:
+In this paper, we present a framework which brings coarse-grained IFC
+ideas into a language-based setting:
 %take coarse-grained labeling~\cite{Zeldovich:2006,
@@
 
-Our contributions can be summarized as follows:
+Our contributions can be summarized as follows: \Red{fixme:}
 \begin{itemize}
@@
   based on this work
-  for client-side JavaScript in Gecko~\cite{swapi}.
+  for client-side JavaScript in~\cite{swapi}.
   Furthermore, we outline an implementation for the C programming

### 2014-10-18 paper/retrofit.tex
wip

--- 2014-10-18 paper/retrofit.tex
@@
 general object structures).
+
+Existing language-based coarse-grained IFC
+system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible} allow
+a sub-computation to temporarily raise the floating-label; after its
+completion, the floating-label is restore to its original label. When this
+occurs, the enforcement must ensure, through several IFC checks, that information
+does not leak to the (less confidential) program continuation. The presence of
+exceptions clearly adds intricacies to the enforcement.
 

### 2014-10-18 paper/extensions.tex
move extensions and limitations to appendix
move extensions to appendix

--- 2014-10-13 paper/extensions.tex
@@
-\section{Extensions}
+\section{Extensions, Limitations, and Future Direction}
 \label{sec:extensions}
 \label{sec:extensions:labeled}
-
-%In this section we consider several extensions to our IFC system.
-%%
-%Specifically, we discuss how the specification language can be
-%extended to consider other IFC-aware features (e.g., fine-grained
-%labeled values), and talk about a static type system, as well as
-%more complex scheduling policies.
-%%
-%When considering these extensions we also discuss some limitations
-%of our approach.
 
@@
 constructs.
-%Different concrete IFC implementations may wish to extend our minimal
-%system with labeled constructs appropriate for their envisioned
-%applications.
-%%
 For example, COWL provides a labeled version of the XHR object, while
@@
 applications~\cite{hails}.
-%%
-%Below we
-%consider the addition of several labeled constructs to the abstract specification.
-In this section we show how to extend the language with several such
-constructs.  For space reasons, we mainly provide the high-level
-ideas here, and provide full formal semantics (including the soundness
+
+Our system can be extended with construct such as labeled values,
+labeled mutable references, clearance, and privileges.
+For space reasons, we provide full formal semantics (including the soundness
 proof with the extensions) in \appendixextfirst{}.
-%
-%We remark that that the non-interference proofs must account for the
-%new constructs, since they amend the IFC calculus semantics (usually
-%by addition).
-
-\subsection{Labeled values}
-%{
-%format Lb = "\textbf{Labeled}"
-%format label = "\textbf{label}"
-In traditional language-based dynamic IFC systems, a label is
-associated with values.
-%
-Hence, a program that, for example, simply writes labeled messages to
-a labeled log can operate on both public and sensitive values.
-Similarly, a task that receives a sensitive value and forwards it
-to another task does not have be be at a sensitive level, if the
-value is not inspected.
-%
-In its simplest form, our coarse grained system requires that the
-current label of a task be at least at the level of the sensitive data
-to reflect the fact that such data is in scope.
-
-If such fine-grained labeling of values is required, our base IFC
-system can be extended with explicitly labeled
-values, much like those of LIO and
-Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
-inlinesep Labeled il ie|.
-%
-Following LIO, we say that the expression |ie| is protected by label |il|,
-while the label |il| itself is protected by the task's current label.
-%
-%
-The label of such values can be inspected the task without
-requiring the current label to be raised.
-%
-However, when a task wishes to inspect the protected value |ie|, it
-must first raise its label to at least |il| to reflect that it is
-incorporating data at such sensitivity level in its scope.
-%
-When creating labeled values the label |il| must be above
-the current label; otherwise it cannot be said that protection has
-been transferred from the current label to |il|.
-%
-%}
-
-\subsection{Labeled mutable references/variables/channels}
-%
-Extending the calculus with other labeled features, such as
-references, mutable variables (MVars)~\cite{CH96}, or channels,
-can be done in a similar manner: these references are implemented
-in the IFC language, separately from any preexisting notions of
-mutable references in the target language.
-%
-%While we can modify the IFC calculus to add such labeled state to each
-%individual task, adding it to the system state |iS| leads to more
-%interesting use cases.
-%
-There is some minor additional state to track: specifically, by amending |iS|, as in~\cite{lio,
-stefan:addressing-covert}, we can allow threads to use these
-constructs to synchronize, or communicate with constructs other than
-|send|/|recv| in a safe manner.
-%
-For example, when extending the calculus with labeled references, |iS|
-additionally contains a store that maps addresses to a value
-and a label
-which can be read and written to by different tasks through a labeled
-reference implementations.
-
-\subsection{Clearance}
-\label{sec:clearance}
-%
-Systems like LIO, COWL, and Breeze additionally provide a discretionary access
-control (DAC) mechanism---called \emph{clearance}---at the language
-level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
-%
-This mechanisms is used to restrict a computation from allocating and
-accessing data (or communicating with entities) above a specified
-label, the clearance.
-%
-Amending our IFC language with clearance is straight forward,
-and, can be done using our notation of a restricted language.
-%
-To this end, we first extend tasks to track a clearance label
-alongside the current label, and amend the core IFC language with two
-new terminals for retrieving and setting this value.
-%
-Since this extension only adds a per-task mutable variable whose value
-has no influence on the system, all security guarantees still
-hold, by essentially the same proofs.
-%
-However, this does not implement any DAC mechanism yet.
-%
-To do so, we can restrict the language with a family of predicates
-$\mathcal{P}_\text{clearance}$:
-All rules that
-raise the current label (e.g., \textsc{I-setLabel}), perform
-allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
-clearance (clearance should not be arbitrarily raised), a predicate
-that uses the clearance to impose DAC is used.
-%
-For instance, the predicate for \textsc{I-setLabel} prevents the
-current label from being raised above the clearance (and thus permit
-reads above the clearance).  The predicate $P := |il
-canFlowTo il'|$ achieves this restriction, where |il'| is the
-clearance and |il| is the current
-label.
-%
-The other predicates are defined in a similar way and omitted for
-brevity.
-
-\subsection{Privileges}
-Decentralized IFC extends IFC with the decentralized label model of
-Myers and Liskov~\cite{myers:dlm} to allow for more general
-applications, including systems consisting of mutually distrustful
-parties.  In a decentralized system, a computation is executed with a
-set of \emph{privileges}, which, when exercised, allow the computation
-to declassify data (e.g., by lowering the current label).
-%
-Practical IFC systems
-(e.g.,~\cite{Zeldovich:2006, lio,
-  Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
-implement many applications.
-%
-%Since both the LIO and COWL implementations already support such features,
-%we believe that extending our calculus to consider privileges is
-%straight forward.
-%
-The challenge with such an extension lies in the precise
-security guarantees that must be proved, which to the best of our
-knowledge is an open research problem.
-
-Our implementation for Node.js and COWL both provide privileges, but
-we have not formalized this part any further.
-%
-%Addressing this problem is a natural direction for this work.
-
-\section{Limitations and Future Directions}
-
-In this section we state some limitations of the current system, and
-outline potential future directions to alleviate these limitations.
-
-\subsection{Type Safety}
-\label{sec:extensions:types}
-
-One important consideration for any new language feature is whether
-or not it preserves type safety.  If implementations are allowed to
-have undefined behavior when the system gets stuck, concerns of type
-safety can be directly applicable to security.
-
-In our presentation, we have demanded that implementations \emph{not}
-have undefined behavior when getting stuck: in such situations, the
-\textsc{I-noStep} rule applies, where the stuck thread should be dropped
-from execution.  Our combined language will be not get stuck, even if
-the target language could get stuck.  This sort of guarantee can be
-achieved at a coarse granularity for languages like C by using hard
-isolation.  However, for many other languages, this is too stringent a
-requirement.
-
-A possible way to relax this requirement is to drop the \textsc{I-noStep}
-rule, and instead demand type-safety of the combined language.  This
-depends on the type system of the target language, so it is difficult to
-make any general statements about how one would go about doing this.  However,
-there are few general remarks to be made:
-
-\begin{itemize}
-    \item In Matthews and Findler's original
-        paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
-        on using type boundaries to mediate between the type systems of
-        the two languages, i.e. handling conversions of values from
-        one language to the other.  These techniques are directly applicable here.
-
-    \item In the case of mini-ES, type safety proceeds by a preservation theorem
-        that refers to well-typed stores.  In our setting, there are now multiple
-        stores, and expressions may move from being interpreted with one store
-        to another (e.g. when an address is sent from one thread to
-        another); a clear violation of type safety.  In this case, operations
-        such as |send| have their typing rules require
-        the expressions being sent be typeable in an arbitrary well-typed store,
-        statically disallowing the sending of addresses, or any types which
-        may contain addresses.  In practice, this may be further restricted to
-        types which can be easily marshalled, e.g. strings.
-
-    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
-        influences the difficulty of the type-safety proof for
-        |sandbox| when the target language has a store.  When
-        $\kappa$ is identity, most expressions can be allowed, since the store
-        remains the same; if $\kappa$ drops the store, however, only closed expressions
-        can be sandboxed.
-\end{itemize}
-
-\subsection{Scheduling Policies}
-Our specification language is parametrized by a scheduling policy |alpha|, which
-maps a task list to a potentially different task list, i.e.,
-$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
-%
-As previously discussed, the precise definition of |alpha|
-dictates whether the language is TSNI, TINI, or neither.
-%
-We described two popular policies |roundrobinf| and
-|seqf| for which we showed TSNI and TINI, respectively.
-%
-However, our definitions allow for other scheduling policies based on the
-current task list---in fact, our formalism can be easily 
-extended to consider history~\cite{BartheRRS07}.
-%
-As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
-which always schedules less sensitive threads first; this can be
-employed to address external timing covert channels where an attacker
-can measure the delay between output events.\footnote{
-  When considering a label lattice that is not totally ordered, e.g.,
-  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
-  considerably more complex.
-}
-%
-More precisely, our calculus generalizes to a class of deterministic
-schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
-modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
-%greatest lower bound of all the labels on the task labels,\footnote{
-%  The label on a task's current label is the current label of the
-%  parent at the time of creation, i.e., the initial current label of
-%  the task.
-%} 
-scheduling decisions on public tasks do not depend on a sensitive task's
-state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
-is a task in the task list whose label is below (or incomparable to) the label
-of another task, this task (or another one at the same level) must eventually
-run.
-%
-The last condition is required for TSNI; languages relying on
-schedulers, such as |seqf|, that do not satisfy the low-progress
-condition can at most satisfy TINI.
-%
-For simplicity, we do not treat this, more-general class of schedulers;
-doing so would require modifying our calculus to keep track of the
-label on the current label of tasks and complicate the
-non-interference proofs.
-
-More fundamentally, our scheduler parametrization is limited in being
-deterministic, and thus extending the system to consider non-deterministic
-schedulers (or even non-deterministic target languages) is non-trivial.
-%
-%For instance,  we do not consider  schedulers that, among other, rely
-%on the global state |iS| or previous task configurations, as treated
-%in~\cite{russo2006securing}.
-%
-%Additionally, our definitions rely on deterministic relations,
-%
-Such extensions often apply security conditions which suffer 
-from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
-adapt non-trivial definitions as
-\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
-which states that a program is secure only if |l|-equivalent results are
-deterministic.
 

### 2014-10-18 paper/real.tex
Title section
improve figures for one-column layout
nodejs

--- 2014-07-08 paper/real.tex
@@
 
-In the introduction, we stated that the original motivation behind
-this work was to formally specify a
-coarse-grained information flow control language for JavaScript.
+In this section, we describe two JavaScript IFC implementations
+building on the theoretical foundations of this work.
 %
-Indeed, our formalism serves as the theoretical foundation for two
-IFC systems for JavaScript, built on top of Node.js as well as
-the web browser engine Gecko.
-
-In this section, we describe these two implementations.  Furthermore,
-we consider how our formalism could be applied to the C programming
-language and connect it to a previous IFC system for Haskell.
+Furthermore, we consider how our formalism could be applied to the C
+programming language and connect it to a previous IFC system for
+Haskell.
 %
-The goal of this section is to show the flexibility of the embedding in settings with
-vastly different properties and discuss the
-semantic gap that must be overcome to apply our formalism
-to other systems.
+%% The goal of this section is to show the flexibility of the embedding in settings with
+%% vastly different properties and discuss the
+%% semantic gap that must be overcome to apply our formalism
+%% to other systems.
 %
@@
 %
-Unfortunately, this becomes very costly when an application relies on
-many tasks.
+Unfortunately, this becomes very costly when a system, such as a
+server-side web application, relies on many tasks.
 %
-For instance, consider a server-side web application that
-creates a new task for each HTTP request.  The overhead would
-quickly become impractical.
+%% For instance, consider a server-side web application that
+%% creates a new task for each HTTP request.  The overhead would
+%% quickly become impractical.
 
-However, this issue of performance and JavaScript isolation is not
-unique to our work and has been solved by browser engines,
-which also
-rely on the isolation of content from
-different origins (e.g., two iframes of different origins) to
-implement the same-origin policy.
+Luckly, this issue is not unique to our work---browser layout engines
+also rely isolating code of different origins (e.g., according to the
+same-origin policy).
 %
 Since creating an OS thread for each iframe is expensive, both
-Google's V8 and Mozilla's SpiderMonkey provide a means for running
+the V8 and SpiderMonkey JavaScript engines provide a means for running
 JavaScript code in isolation in a single OS thread,
@@
 %
-Each context/compartment is associated with a global object, which, by
+(We will use these terms interchangably.)
+%
+Each context is associated with a global object, which, by
 default, implements the JavaScript standard library (e.g.,
@@
 %
-Naturally, our notion of a task for JavaScript directly corresponds to
-a context/compartment.
+Naturally, we adopt contexts to implement our notion of tasks.
 
-When JavaScript is embedded in web browser engines, such as Google's
-Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
+When JavaScript is embedded in browser layout engines, 
+or in server-side platforms such as Node.js,
 additional APIs such as the Document Object Model (DOM) or the file
@@
 These features are exposed by extending the global object, just like
-for the standard library.  For this reason, it is easy to modify
+the standard library.  For this reason, it is easy to modify
 these systems to remove arbitrary external effects when implementing
@@
 
-\subsubsection{Server-side IFC: Node.js}
-
-We have implemented |specLangJS seqf| for Node.js in the form of a module
-(library), which does not modify the Node.js or V8 code-base in any
-way.
-%
-Our implementation\footnote{The source code of our implementation can be found at
-  \codelink{}.} provides a library for creating new tasks, i.e.,
-contexts whose global object only contains the standard JavaScript
-library as well as our IFC primitives (such as |send| and |sandbox|).
-%
-In turn, these tasks can create new tasks with |sandbox|.
-%
-In our formal treatement, |sandbox| is defined with |ap klone tS = tS0|,
-where |tS0| is the global object corresponding to the standard
-JavaScript library and our IFC primitives.
-
-\begin{figure}
-\centerline{\includegraphics[width=\columnwidth]{figs/node}}
-\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
+\caption{\label{fig:node}
 This example shows how our trusted monitor (left) is used to mediate
@@
 %
-All IFC primitives are mediated by the trusted library code (executing
-as the main Node.js context), which tracks the current label, messages,
-etc.\ of each task.  An example for |send|/|recv| is shown in
+\subsubsection{Server-side Node.js IFC:}\ 
+We have implemented |specLangJS seqf| for Node.js in the form of a
+library, without modifying Node.js or the V8 JavaScript engine.
+%
+Our implementation\footnote{Available at \codelink{}.} provides a
+library for creating new tasks, i.e., contexts whose global object
+only contains the standard JavaScript library and our IFC primitives
+(e.g., |send| and |sandbox|).
+%
+When mapped to our formal treatement, |sandbox| is defined with |ap
+klone tS = tS0|, where |tS0| is the global object corresponding to the
+standard JavaScript library and our IFC primitives.
+%
+%These tasks can communicate and create new tasks, in turn.
+%
+These IFC operations are mediated by the trusted library code (executing
+as the main Node.js context), which tracks the state (current label, messages,
+etc.) of each task.  An example for |send|/|recv| is shown in
 Figure~\ref{fig:node}.
@@
 %by same-origin contexts in Blink),
-Our system conservatively restricts
-the kinds of messages that can be exchanged by tasks by
-only allowing string values to be exchanged via |send| (and |sandbox|).
+We remark that our system conservatively restricts
+the kinds of messages that can be exchanged, via |send| (and |sandbox|),
+to string values.
+%
+(We provide a convenience library which marshalls JSON objects to/from strings.)
 %
@@
 %
-For convenience, we have implemented a library that provides
-more flexible primitives, which, among other things,
-automatically marshalls JSON objects to/from strings on each
-|send|/|recv|.
 
-While the described system implements |specLangJS seqf|, server-side
-applications may require access to the file system, HTTP server, HTTP
-client, or other APIs that have external effects.
+While the described system implements |specLangJS seqf|, applications
+typically require access to libraries (e.g., the file system library
+\textsf{fs}) that that have external effects.
 %
-Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
-thus we
-%
-instead implement libraries such as a labeled file system as
+Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
+Instead, we implement libraries such as a labeled \textsf{fs} as
 message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
 in Figure~\ref{fig:node}) and the main Node.js task that implements
-our IFC monitor.\footnote{
-  Importantly, we provide mostly-identical interfaces to
-  the standard Node.js libraries, hiding the underlying
-  message-passing implementations.
-}
+the IFC monitor.
 %
-This is safer than the approach of simply wrapping objects, which can
-potentially allow objects to be accessed outside the context.
+While this is safer than simply wrapping unsafe objects, adding
+featuers such as the \textsf{fs} requires the code in the main task to
+ensures that labels are properly propagated and enforced.
 %
-This task is trusted to ensures that labels are
-propagated to files and the labels of the task and the file in question permit
-this flow.
-%
-Unfortunately, while imposing such a proof burden on the
-framework developer is undesirable, this also has to be expected:
+Unfortunately, while imposing such a proof burden
+is undesirable, this also has to be expected:
 different language environments expose different libraries for
@@
 %
-For instance, in the case of Node.js, how labels interact with the
-file system may even vary according to the application (e.g.,
-in the IFC system Hails~\cite{hails}, labels are not persisted).
+%% For instance, in the case of Node.js, how labels interact with the
+%% file system may even vary according to the application (e.g.,
+%% in the IFC system Hails~\cite{hails}, labels are not persisted).
 %
@@
 
-\subsubsection{Client-side IFC: Gecko}
-
+\subsubsection{Client-side COWL IFC:}\
 We now describe some of the implementation aspects of

### 2014-10-18 paper/appendix.tex
fix references

@@
 
-\section{Formal Extensions}
+\section{Extensions}
 \label{sec:appendix-extensions}
 
-Here we formally define the syntax and semantics of the extensions
-sketched in Section~\ref{sec:extensions}.
-In Figure~\ref{fig:labeled-vals} we show how labeled values can be added,
-while Figure~\ref{fig:labeled-refs} details labeled references formally.
-For labeled values, we assume that the constructor |Labeled| is not part
-of the surface syntax, but rather an internal construct.  Similarly,
-the construct |ial| is internal in the labeled reference implementation.
-These changes to the semantics require us to update the erasure function
-|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
-Note that the soundness proof in Appendix~\ref{sec:appendix}
-is done for the fully extended language with labeled values and
-labeled references.
+As mentioned in the main body of this paper,
+actual IFC implementations
+may wish to extend the minimal system with more specialized
+constructs.
+In this section we show how to extend the language with several such
+constructs.
+%
+%We remark that that the non-interference proofs must account for the
+%new constructs, since they amend the IFC calculus semantics (usually
+%by addition).
 
-We also give details for the clearance extension below.
+\subsection{Labeled values}
+%{
+%format Lb = "\textbf{Labeled}"
+%format label = "\textbf{label}"
+In traditional language-based dynamic IFC systems, a label is
+associated with values.
+%
+Hence, a program that, for example, simply writes labeled messages to
+a labeled log can operate on both public and sensitive values.
+Similarly, a task that receives a sensitive value and forwards it
+to another task does not have be be at a sensitive level, if the
+value is not inspected.
+%
+In its simplest form, our coarse grained system requires that the
+current label of a task be at least at the level of the sensitive data
+to reflect the fact that such data is in scope.
 
-\subsection{Clearance}
+If such fine-grained labeling of values is required, our base IFC
+system can be extended with explicitly labeled
+values, much like those of LIO and
+Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
+inlinesep Labeled il ie|.
+%
+Following LIO, we say that the expression |ie| is protected by label |il|,
+while the label |il| itself is protected by the task's current label.
+%
+%
+The label of such values can be inspected the task without
+requiring the current label to be raised.
+%
+However, when a task wishes to inspect the protected value |ie|, it
+must first raise its label to at least |il| to reflect that it is
+incorporating data at such sensitivity level in its scope.
+%
+When creating labeled values the label |il| must be above
+the current label; otherwise it cannot be said that protection has
+been transferred from the current label to |il|.
+%
+%}
 
-As we have outlined in Section~\ref{sec:clearance}, we first extend
-tasks with an additional label |ilc|, which corresponds to the
-clearance of that task, and provide two primitives to read and
-write that value:
-\[ |fullconfc id il ilc tS ie| \]
-
-\begin{figure}
-  %{
-  %format .->  = "\overset{\alpha}{\hookrightarrow}"
-  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
-  \begin{code}
-    ie  ::= cdots | getClearance | setClearance ie
-    iE  ::= cdots | setClearance iE
-  \end{code}
-  \begin{mathpar}
-      \inferrule[I-getClearance]
-      { }
-      {|
-        niconf iS id il ilc getClearance
-        ->
-        niconf iS id il ilc ilc
-        |}
-
-      \and
-      \inferrule[I-setClearance]
-      { }
-      {|
-        niconf iS id il ilc (setClearance ilc')
-        ->
-        niconf iS id il ilc' unit
-        |}
-  \end{mathpar}
-  \caption{Syntax and semantics for clearance.  These rules are
-    understood to be an addition to the existing rules given earlier,
-    except for the \textsc{I-sandbox} rule, which replaces the previous
-    one.
-    All existing rules do not modify the clearance.}
-  \label{fig:clearance}
-  %}
-\end{figure}
+In Figure~\ref{fig:labeled-vals}, we formally show how to add this
+extension to the language.
+We assume that the constructor |Labeled| is not part
+of the surface syntax, but rather an internal construct.
 
@@
 \end{figure}
+
+\subsection{Labeled mutable references/variables/channels}
+%
+Extending the calculus with other labeled features, such as
+references, mutable variables (MVars)~\cite{CH96}, or channels,
+can be done in a similar manner: these references are implemented
+in the IFC language, separately from any preexisting notions of
+mutable references in the target language.
+%
+%While we can modify the IFC calculus to add such labeled state to each
+%individual task, adding it to the system state |iS| leads to more
+%interesting use cases.
+%
+There is some minor additional state to track: specifically, by amending |iS|, as in~\cite{lio,
+stefan:addressing-covert}, we can allow threads to use these
+constructs to synchronize, or communicate with constructs other than
+|send|/|recv| in a safe manner.
+%
+For example, when extending the calculus with labeled references, |iS|
+additionally contains a store that maps addresses to a value
+and a label
+which can be read and written to by different tasks through a labeled
+reference implementations.
+
+In Figure~\ref{fig:labeled-refs} details labeled references formally.
+The construct |ial| is internal in the labeled reference implementation,
+and not part of the surface syntax.
+The changes to the language for labeled values and
+references require us to update the erasure function
+|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
 
@@
 
-\section{Full Non-Interference Proof}
+\subsection{Clearance}
+\label{sec:clearance}
+%
+Systems like LIO, COWL, and Breeze additionally provide a discretionary access
+control (DAC) mechanism---called \emph{clearance}---at the language
+level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
+%
+This mechanisms is used to restrict a computation from allocating and
+accessing data (or communicating with entities) above a specified
+label, the clearance.
+%
+Amending our IFC language with clearance is straight forward,
+and, can be done using our notation of a restricted language.
+%
+To this end, we first extend tasks to track a clearance label
+alongside the current label, and amend the core IFC language with two
+new terminals for retrieving and setting this value.
+%
+Since this extension only adds a per-task mutable variable whose value
+has no influence on the system, all security guarantees still
+hold, by essentially the same proofs.
+%
+However, this does not implement any DAC mechanism yet.
+%
+To do so, we can restrict the language with a family of predicates
+$\mathcal{P}_\text{clearance}$:
+All rules that
+raise the current label (e.g., \textsc{I-setLabel}), perform
+allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
+clearance (clearance should not be arbitrarily raised), a predicate
+that uses the clearance to impose DAC is used.
+%
+For instance, the predicate for \textsc{I-setLabel} prevents the
+current label from being raised above the clearance (and thus permit
+reads above the clearance).  The predicate $P := |il
+canFlowTo il'|$ achieves this restriction, where |il'| is the
+clearance and |il| is the current
+label.
+%
+The other predicates are defined in a similar way and omitted for
+brevity.
+
+\subsection{Privileges}
+Decentralized IFC extends IFC with the decentralized label model of
+Myers and Liskov~\cite{myers:dlm} to allow for more general
+applications, including systems consisting of mutually distrustful
+parties.  In a decentralized system, a computation is executed with a
+set of \emph{privileges}, which, when exercised, allow the computation
+to declassify data (e.g., by lowering the current label).
+%
+Practical IFC systems
+(e.g.,~\cite{Zeldovich:2006, lio,
+  Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
+implement many applications.
+%
+%Since both the LIO and COWL implementations already support such features,
+%we believe that extending our calculus to consider privileges is
+%straight forward.
+%
+The challenge with such an extension lies in the precise
+security guarantees that must be proved, which to the best of our
+knowledge is an open research problem.
+
+Our implementation for Node.js and COWL both provide privileges, but
+we have not formalized this part any further.
+
+%We also give details for the clearance extension below.
+%
+%\subsection{Clearance}
+%
+%As we have outlined in Section~\ref{sec:clearance}, we first extend
+%tasks with an additional label |ilc|, which corresponds to the
+%clearance of that task, and provide two primitives to read and
+%write that value:
+%\[ |fullconfc id il ilc tS ie| \]
+%
+%\begin{figure}
+%  %{
+%  %format .->  = "\overset{\alpha}{\hookrightarrow}"
+%  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
+%  \begin{code}
+%    ie  ::= cdots | getClearance | setClearance ie
+%    iE  ::= cdots | setClearance iE
+%  \end{code}
+%  \begin{mathpar}
+%      \inferrule[I-getClearance]
+%      { }
+%      {|
+%        niconf iS id il ilc getClearance
+%        ->
+%        niconf iS id il ilc ilc
+%        |}
+%      
+%      \and
+%      \inferrule[I-setClearance]
+%      { }
+%      {|
+%        niconf iS id il ilc (setClearance ilc')
+%        ->
+%        niconf iS id il ilc' unit
+%        |}
+%  \end{mathpar}
+%  \caption{Syntax and semantics for clearance.  These rules are
+%    understood to be an addition to the existing rules given earlier,
+%    except for the \textsc{I-sandbox} rule, which replaces the previous
+%    one.
+%    All existing rules do not modify the clearance.}
+%  \label{fig:clearance}
+%  %}
+%\end{figure}
+
+\section{Limitations and Future Directions}
+
+In this section we state some limitations of the current system, and
+outline potential future directions to alleviate these limitations.
+
+\subsection{Type Safety}
+\label{sec:extensions:types}
+
+One important consideration for any new language feature is whether
+or not it preserves type safety.  If implementations are allowed to
+have undefined behavior when the system gets stuck, concerns of type
+safety can be directly applicable to security.
+
+In our presentation, we have demanded that implementations \emph{not}
+have undefined behavior when getting stuck: in such situations, the
+\textsc{I-noStep} rule applies, where the stuck thread should be dropped
+from execution.  Our combined language will be not get stuck, even if
+the target language could get stuck.  This sort of guarantee can be
+achieved at a coarse granularity for languages like C by using hard
+isolation.  However, for many other languages, this is too stringent a
+requirement.
+
+A possible way to relax this requirement is to drop the \textsc{I-noStep}
+rule, and instead demand type-safety of the combined language.  This
+depends on the type system of the target language, so it is difficult to
+make any general statements about how one would go about doing this.  However,
+there are few general remarks to be made:
+
+\begin{itemize}
+    \item In Matthews and Findler's original
+        paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
+        on using type boundaries to mediate between the type systems of
+        the two languages, i.e. handling conversions of values from
+        one language to the other.  These techniques are directly applicable here.
+
+    \item In the case of mini-ES, type safety proceeds by a preservation theorem
+        that refers to well-typed stores.  In our setting, there are now multiple
+        stores, and expressions may move from being interpreted with one store
+        to another (e.g. when an address is sent from one thread to
+        another); a clear violation of type safety.  In this case, operations
+        such as |send| have their typing rules require
+        the expressions being sent be typeable in an arbitrary well-typed store,
+        statically disallowing the sending of addresses, or any types which
+        may contain addresses.  In practice, this may be further restricted to
+        types which can be easily marshalled, e.g. strings.
+
+    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
+        influences the difficulty of the type-safety proof for
+        |sandbox| when the target language has a store.  When
+        $\kappa$ is identity, most expressions can be allowed, since the store
+        remains the same; if $\kappa$ drops the store, however, only closed expressions
+        can be sandboxed.
+\end{itemize}
+
+\subsection{Scheduling Policies}
+Our specification language is parametrized by a scheduling policy |alpha|, which
+maps a task list to a potentially different task list, i.e.,
+$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
+%
+As previously discussed, the precise definition of |alpha|
+dictates whether the language is TSNI, TINI, or neither.
+%
+We described two popular policies |roundrobinf| and
+|seqf| for which we showed TSNI and TINI, respectively.
+%
+However, our definitions allow for other scheduling policies based on the
+current task list---in fact, our formalism can be easily 
+extended to consider history~\cite{BartheRRS07}.
+%
+As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
+which always schedules less sensitive threads first; this can be
+employed to address external timing covert channels where an attacker
+can measure the delay between output events.\footnote{
+  When considering a label lattice that is not totally ordered, e.g.,
+  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
+  considerably more complex.
+}
+%
+More precisely, our calculus generalizes to a class of deterministic
+schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
+modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
+%greatest lower bound of all the labels on the task labels,\footnote{
+%  The label on a task's current label is the current label of the
+%  parent at the time of creation, i.e., the initial current label of
+%  the task.
+%} 
+scheduling decisions on public tasks do not depend on a sensitive task's
+state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
+is a task in the task list whose label is below (or incomparable to) the label
+of another task, this task (or another one at the same level) must eventually
+run.
+%
+The last condition is required for TSNI; languages relying on
+schedulers, such as |seqf|, that do not satisfy the low-progress
+condition can at most satisfy TINI.
+%
+For simplicity, we do not treat this, more-general class of schedulers;
+doing so would require modifying our calculus to keep track of the
+label on the current label of tasks and complicate the
+non-interference proofs.
+
+More fundamentally, our scheduler parametrization is limited in being
+deterministic, and thus extending the system to consider non-deterministic
+schedulers (or even non-deterministic target languages) is non-trivial.
+%
+%For instance,  we do not consider  schedulers that, among other, rely
+%on the global state |iS| or previous task configurations, as treated
+%in~\cite{russo2006securing}.
+%
+%Additionally, our definitions rely on deterministic relations,
+%
+Such extensions often apply security conditions which suffer 
+from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
+adapt non-trivial definitions as
+\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
+which states that a program is secure only if |l|-equivalent results are
+deterministic.
+
+\section{Non-Interference Proof}
 \label{sec:appendix}
+\label{sec:app:proof}
 
 In this section we prove the theorems we have stated in the paper.
+Note that we prove soundness of the system including the formally
+defined extensions from Appendix~\ref{sec:appendix-extensions}.
 We first observe that the non-interference claims for the languages

### 2014-10-18 paper/retrofit.tex

--- 2014-10-18 paper/retrofit.tex
@@
 general object structures).
+
+\Red{
+Existing language-based coarse-grained IFC
+system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible} allow a
+sub-computation to temporarily raise the floating-label; after the
+sub-computation is done, the floating-label is restore to its original
+label. When this occurs, the enforcement must ensure, through IFC checks, that
+information does not leak to the (less confidential) program continuation. The
+presence of exceptions clearly adds intricacies to the enforcement---the
+exception should not cross from the sub-computation directly into the program
+continuation. In contrast, our system provides the same guarantees with no extra
+IFC checks: task are allowed to temporarily raise their floating-label, but the
+mere definition of isolated tasks guarantees that (a) tasks only transfer data
+to the program continuation by using intra-task communication means, and (b)
+exceptions cannot cross tasks boundaries.
+}
 

### 2014-10-18 paper/real.tex
remove haskel

--- 2014-10-16 paper/real.tex
@@
 \begin{figure}
-\centerline{\includegraphics[width=\columnwidth]{figs/node}}
+\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
 \caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
@@
 
-%% \subsection{Haskell}
-%% \label{sec:real:hs}
-%% Our work borrows ideas from a Haskell coarse-grained IFC
-%% system called LIO~\cite{lio, stefan:addressing-covert}.
-%% %
-%% LIO relies on Haskell's strong type system and monadic encoding of
-%% side-effecting computations to achieve isolation and define the IFC
-%% sub-language.
-%% %
-%% Specifically LIO provides the \verb|LIO| monad as a way of restricting
-%% (almost all) side-effects; this monad also keeps track of a current
-%% label which is, in turn, used by trusted code when defining core IFC
-%% functions, such as |getLabel|.
-%% %
-%% In the context of our framework, LIO can be understood as follows: the
-%% \emph{pure subset} of Haskell is the target language, while the
-%% monadic subset of Haskell, operating in the \verb|LIO| monad, is the
-%% IFC language.
+%\subsection{Haskell}
+%\label{sec:real:hs}
+%Our work borrows ideas from a Haskell coarse-grained IFC
+%system called LIO~\cite{lio, stefan:addressing-covert}.
+%%
+%LIO relies on Haskell's strong type system and monadic encoding of
+%side-effecting computations to achieve isolation and define the IFC
+%sub-language.
+%%
+%Specifically LIO provides the \verb|LIO| monad as a way of restricting
+%(almost all) side-effects; this monad also keeps track of a current
+%label which is, in turn, used by trusted code when defining core IFC
+%functions, such as |getLabel|.
+%%
+%In the context of our framework, LIO can be understood as follows: the
+%\emph{pure subset} of Haskell is the target language, while the
+%monadic subset of Haskell, operating in the \verb|LIO| monad, is the
+%IFC language.
+%
+%%Indeed, by rephrasing LIO in terms of our framework, we simplified
+%%LIO's treatment of exceptions.
+%%
+%LIO originally associated labels with exceptions, in a
+%similar style to fine-grained
+%systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
+%%
+%In particular, the label of an exception was set to the current label
+%at the time of the throw, and used by a custom catch construct to
+%raise the current label, thereby preventing leaks due to exceptional
+%control flows.
+%%
+%In addition to being overly complex, the interaction of exceptions
+%with clearance (which sets an upper bound on the current label, see
+%Section~\ref{sec:clearance}) was incorrect: the clearance
+%was restored to the clearance at point of the catch (a consequence of
+%defining \verb|LIO| using a State monad).
+%%
+%Furthermore, pure exceptions (e.g., divide by zero) always percolated to
+%trusted code, effectively allowing for denial of service attacks.
+%%
+%The insights gained when viewing coarse-grained IFC as presented in this
+%paper led to a much cleaner, simpler treatment of exceptions in LIO,
+%which has now been adapted by LIO.
+%%By using isolated tasks, and thus treating the current label (and
+%%clearance) as global, the underlying Haskell exception system can be
+%%used directly: exceptional control flow does not affect IFC.
 
-%% %Indeed, by rephrasing LIO in terms of our framework, we simplified
-%% %LIO's treatment of exceptions.
-%% %
-%% LIO originally associated labels with exceptions, in a
-%% similar style to fine-grained
-%% systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
-%% %
-%% In particular, the label of an exception was set to the current label
-%% at the time of the throw, and used by a custom catch construct to
-%% raise the current label, thereby preventing leaks due to exceptional
-%% control flows.
-%% %
-%% In addition to being overly complex, the interaction of exceptions
-%% with clearance (which sets an upper bound on the current label, see
-%% Section~\ref{sec:clearance}) was incorrect: the clearance
-%% was restored to the clearance at point of the catch (a consequence of
-%% defining \verb|LIO| using a State monad).
-%% %
-%% Furthermore, pure exceptions (e.g., divide by zero) always percolated to
-%% trusted code, effectively allowing for denial of service attacks.
-%% %
-%% The insights gained when viewing coarse-grained IFC as presented in this
-%% paper led to a much cleaner, simpler treatment of exceptions in LIO,
-%% which has now been adapted by LIO.
-%% %By using isolated tasks, and thus treating the current label (and
-%% %clearance) as global, the underlying Haskell exception system can be
-%% %used directly: exceptional control flow does not affect IFC.
+\subsection{C}
+\label{sec:real:c}
+%
+C programs are able to execute arbitrary (machine) code, access
+arbitrary memory, and perform arbitrary system calls.
+%
+Thus, the confinement of C programs must be imposed by the underlying OS
+and hardware.
+%
+For instance, our notion of isolation can be achieved using Dune's
+hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
+similar to a simpler version of
+Wedge~\cite{Belay:2012:DSU:2387880.2387913,
+Bittau:2008:WSA:1387589.1387611} with an information flow control
+policy.
+%
+Using page tables, a (trusted) IFC runtime could ensure that each task,
+implemented as a lightweight process, can only access the memory it
+allocates---tasks do not have access to any shared memory.
+%
+In addition, ring protection could be used to intercept system
+calls performed by
+a task and only permit those corresponding to our IFC language (such as
+|getLabel| or |send|).
+%
+Dune's hardware protection mechanism would allow us to provide a concrete
+implementation that is efficient and relatively simple to reason
+about, but other sandboxing mechanisms could be used in place of Dune.
 
-%% \subsection{C}
-%% \label{sec:real:c}
-%% %
-%% C programs are able to execute arbitrary (machine) code, access
-%% arbitrary memory, and perform arbitrary system calls.
-%% %
-%% Thus, the confinement of C programs must be imposed by the underlying OS
-%% and hardware.
-%% %
-%% For instance, our notion of isolation can be achieved using Dune's
-%% hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
-%% similar to a simpler version of
-%% Wedge~\cite{Belay:2012:DSU:2387880.2387913,
-%% Bittau:2008:WSA:1387589.1387611} with an information flow control
-%% policy.
-%% %
-%% Using page tables, a (trusted) IFC runtime could ensure that each task,
-%% implemented as a lightweight process, can only access the memory it
-%% allocates---tasks do not have access to any shared memory.
-%% %
-%% In addition, ring protection could be used to intercept system
-%% calls performed by
-%% a task and only permit those corresponding to our IFC language (such as
-%% |getLabel| or |send|).
-%% %
-%% Dune's hardware protection mechanism would allow us to provide a concrete
-%% implementation that is efficient and relatively simple to reason
-%% about, but other sandboxing mechanisms could be used in place of Dune.
-
-%% In this setting, the combined language of Section~\ref{sec:retrofit}
-%% can be interpreted in the following way: calling from the target
-%% language to the IFC language corresponds to invoking a system call.
-%% %
-%% Creating a new task with the |sandbox| system call corresponds to
-%% \emph{forking} a process.  Using page tables we can ensure that
-%% there will be no shared memory
-%% (effectively
-%% defining |ap klone tS
-%% = tS0|, where |tS0| is the set of pages necessary to bootstrap a
-%% lightweight process.)
-%% %
-%% Similarly, control over page tables and protection bits allows us to
-%% define a |send| syscall that copies pages to our
-%% (trusted) runtime queue; and, correspondingly, a |recv| that copies
-%% the pages from the runtime queue to the (untrusted) receiver.
-%% %
-%% Since C is not memory safe, conditions on these system calls are
-%% meaningless.
-%% %
-%% We leave the implementation of this IFC system for C to future work.
+In this setting, the combined language of Section~\ref{sec:retrofit}
+can be interpreted in the following way: calling from the target
+language to the IFC language corresponds to invoking a system call.
+%
+Creating a new task with the |sandbox| system call corresponds to
+\emph{forking} a process.  Using page tables we can ensure that
+there will be no shared memory
+(effectively
+defining |ap klone tS
+= tS0|, where |tS0| is the set of pages necessary to bootstrap a
+lightweight process.)
+%
+Similarly, control over page tables and protection bits allows us to
+define a |send| syscall that copies pages to our
+(trusted) runtime queue; and, correspondingly, a |recv| that copies
+the pages from the runtime queue to the (untrusted) receiver.
+%
+Since C is not memory safe, conditions on these system calls are
+meaningless.
+%
+We leave the implementation of this IFC system for C to future work.

### 2014-10-18 paper/real.tex

--- 2014-10-18 paper/real.tex
@@
 
-\subsection{Haskell}
-\label{sec:real:hs}
-Our work borrows ideas from a Haskell coarse-grained IFC
-system called LIO~\cite{lio, stefan:addressing-covert}.
+%\subsection{Haskell}
+%\label{sec:real:hs}
+%Our work borrows ideas from a Haskell coarse-grained IFC
+%system called LIO~\cite{lio, stefan:addressing-covert}.
+%%
+%LIO relies on Haskell's strong type system and monadic encoding of
+%side-effecting computations to achieve isolation and define the IFC
+%sub-language.
+%%
+%Specifically LIO provides the \verb|LIO| monad as a way of restricting
+%(almost all) side-effects; this monad also keeps track of a current
+%label which is, in turn, used by trusted code when defining core IFC
+%functions, such as |getLabel|.
+%%
+%In the context of our framework, LIO can be understood as follows: the
+%\emph{pure subset} of Haskell is the target language, while the
+%monadic subset of Haskell, operating in the \verb|LIO| monad, is the
+%IFC language.
 %
-LIO relies on Haskell's strong type system and monadic encoding of
-side-effecting computations to achieve isolation and define the IFC
-sub-language.
-%
-Specifically LIO provides the \verb|LIO| monad as a way of restricting
-(almost all) side-effects; this monad also keeps track of a current
-label which is, in turn, used by trusted code when defining core IFC
-functions, such as |getLabel|.
-%
-In the context of our framework, LIO can be understood as follows: the
-\emph{pure subset} of Haskell is the target language, while the
-monadic subset of Haskell, operating in the \verb|LIO| monad, is the
-IFC language.
-
-%Indeed, by rephrasing LIO in terms of our framework, we simplified
-%LIO's treatment of exceptions.
-%
-LIO originally associated labels with exceptions, in a
-similar style to fine-grained
-systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
-%
-In particular, the label of an exception was set to the current label
-at the time of the throw, and used by a custom catch construct to
-raise the current label, thereby preventing leaks due to exceptional
-control flows.
-%
-In addition to being overly complex, the interaction of exceptions
-with clearance (which sets an upper bound on the current label, see
-Section~\ref{sec:clearance}) was incorrect: the clearance
-was restored to the clearance at point of the catch (a consequence of
-defining \verb|LIO| using a State monad).
-%
-Furthermore, pure exceptions (e.g., divide by zero) always percolated to
-trusted code, effectively allowing for denial of service attacks.
-%
-The insights gained when viewing coarse-grained IFC as presented in this
-paper led to a much cleaner, simpler treatment of exceptions in LIO,
-which has now been adapted by LIO.
-%By using isolated tasks, and thus treating the current label (and
-%clearance) as global, the underlying Haskell exception system can be
-%used directly: exceptional control flow does not affect IFC.
+%%Indeed, by rephrasing LIO in terms of our framework, we simplified
+%%LIO's treatment of exceptions.
+%%
+%LIO originally associated labels with exceptions, in a
+%similar style to fine-grained
+%systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
+%%
+%In particular, the label of an exception was set to the current label
+%at the time of the throw, and used by a custom catch construct to
+%raise the current label, thereby preventing leaks due to exceptional
+%control flows.
+%%
+%In addition to being overly complex, the interaction of exceptions
+%with clearance (which sets an upper bound on the current label, see
+%Section~\ref{sec:clearance}) was incorrect: the clearance
+%was restored to the clearance at point of the catch (a consequence of
+%defining \verb|LIO| using a State monad).
+%%
+%Furthermore, pure exceptions (e.g., divide by zero) always percolated to
+%trusted code, effectively allowing for denial of service attacks.
+%%
+%The insights gained when viewing coarse-grained IFC as presented in this
+%paper led to a much cleaner, simpler treatment of exceptions in LIO,
+%which has now been adapted by LIO.
+%%By using isolated tasks, and thus treating the current label (and
+%%clearance) as global, the underlying Haskell exception system can be
+%%used directly: exceptional control flow does not affect IFC.
 

### 2014-10-18 paper/conclusion.tex
Removing Haskell

--- 2014-07-08 paper/conclusion.tex
@@
 to two IFC implementations for JavaScript based on this formalism,
-explained how our methodology improved an exiting IFC system for Haskell,
+%explained how our methodology improved an exiting IFC system for Haskell,
 and proposed

### 2014-10-18 paper/retrofit.tex
inline some things

@@
 For instance,
-\begin{code}
-TI(toLabeled l (IT (if te then fail else true))); true
-\end{code}
+$|TI(toLabeled l (IT (if te then fail else true))); true|$
 always evaluates to |true|, regardless of the value of |te|.
@@
 
-\paragraph{Notation}
+\vspace{1pt}
+\noindent
+\textit{Notation}
 We have typeset nonterminals of the target language using \textbf{{\color{red}

### 2014-10-18 paper/related.tex
Removing performance trashing to JSFlow

--- 2014-07-08 paper/related.tex
@@
 cost of complexity (the system must accommodate the entirety of JavaScript's
-semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
-higher than 100\%~\cite{JSFlow}.  Alternatively, coarse-grained
+semantics~\cite{JSFlow}).
+%Moreover, the runtime performance cost are sometimes too high, e.g.,
+%higher than 100\%~\cite{JSFlow}.
+Alternatively, coarse-grained
 approaches to security have also been proposed for the web
@@
 
-Our definition of isomorphism of information flow control languages in
-Section~\ref{sec:concrete} is closely related to the idea of
-\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
-although as our system is deterministic, we do not use the theory in any
-deep way.
+%Our definition of isomorphism of information flow control languages in
+%Section~\ref{sec:concrete} is closely related to the idea of
+%\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
+%although as our system is deterministic, we do not use the theory in any
+%deep way.
 

### 2014-10-18 paper/retrofit.tex
exceptions

--- 2014-10-18 paper/retrofit.tex
@@
 Existing language-based coarse-grained IFC
-system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible} allow
-a sub-computation to temporarily raise the floating-label; after its
-completion, the floating-label is restore to its original label. When this
-occurs, the enforcement must ensure, through several IFC checks, that information
-does not leak to the (less confidential) program continuation. The presence of
-exceptions clearly adds intricacies to the enforcement.
+system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
+allow a sub-computation to temporarily raise the floating-label; after
+the sub-computation is done, the floating-label is restored to its
+original label. When this occurs, the enforcement mechanism must
+ensure that information does not leak to the (less confidential)
+program continuation. The presence of exceptions adds yet more
+intricacies.  For instance, exceptions should not automatically
+propagate from a sub-computation directly into the program
+continuation, and, if such exceptions are allowed to be inspected, the
+floating-label at the point of the exception-raise must be tracked
+alongside the exception value~\cite{Hritcu:2013:YIB:2497621.2498098,
+stefan:2012:arxiv-flexiblea, Hedin:2012}.  In contrast, our system
+provides the same flexibility and guarantees with no extra checks: tasks
+are used to execute sub-computations, but the mere definition of
+isolated tasks guarantees that (a) tasks only transfer data to the
+program continuation by using inter-task communication means, and (b)
+exceptions do cross tasks boundaries automatically.
 
-Here are two more examples of language features which have an
-interesting interpretation when interpreted as task communication.
-
-\paragraph{Stack frames versus scheduling}  One feature which is
-supported by some information flow control systems is the ability to
-temporarily raise the current label in order to do computation on data
-(as done by LIO's |toLabeled| and Breeze's
-brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
-stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
-enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
-the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
-achieve termination-insensitive non-interference: if the high secrecy
-section doesn't terminate, this is observable by the non-execution of
-the defunct public continuation.
-
-When considering tasks, we will instead say that the allocation of a new
-stack frame with a raised label corresponds to the creation of a new
-isolated task; a sample encoding using our language is as follows:
-\begin{align*}
-    & |toLabeled l te @= | \\
-    & |tab let i = taskId in| \\
-%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
-    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
-    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
-\end{align*}
-There is one more ingredient: in a stack discipline, one generally
-expects stack entries to be processed in order, rather than in parallel
-as would be suggested by isolated tasks.  The sequential processing of
-the task queue corresponds to a specific \emph{scheduling policy} of
-these tasks.  In fact, the choice of scheduling here is the essential difference that
-determines whether or not one can prove termination-insensitive or
-termination-sensitive non-interference. We will show how different
-scheduling policies give different security guarantees.
-
-\paragraph{Exceptions versus message passing}
-Another language feature that has caused difficulty for
-many information flow control systems is exception handling
-when built on top of this stack discipline.
-%
-The key difficulty appears when considering the propagation of exceptions
-across stack boundaries where the current label is restored.
-%
-If the exception crosses this boundary, it can leak information about the
-inner secret computation into a public computation; hence, one must
-explicitly ensure that |toLabeled| does not propagate exceptions.
-%
-When stack frames are treated as isolated tasks, the correct semantics
-are achieved automatically.
-%
-Exceptions simply stop when the hit the top-level of a task:
-the only way for the frame to communicate information is by
-initiating inter-task message passing.
-%
-For instance,
-\begin{code}
-TI(toLabeled l (IT (if te then fail else true))); true
-\end{code}
-always evaluates to |true|, regardless of the value of |te|.
+%% Here are two more examples of language features which have an
+%% interesting interpretation when interpreted as task communication.
+%% 
+%% \paragraph{Stack frames versus scheduling}  One feature which is
+%% supported by some information flow control systems is the ability to
+%% temporarily raise the current label in order to do computation on data
+%% (as done by LIO's |toLabeled| and Breeze's
+%% brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
+%% stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
+%% enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
+%% the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
+%% achieve termination-insensitive non-interference: if the high secrecy
+%% section doesn't terminate, this is observable by the non-execution of
+%% the defunct public continuation.
+%% 
+%% When considering tasks, we will instead say that the allocation of a new
+%% stack frame with a raised label corresponds to the creation of a new
+%% isolated task; a sample encoding using our language is as follows:
+%% \begin{align*}
+%%     & |toLabeled l te @= | \\
+%%     & |tab let i = taskId in| \\
+%% %%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
+%%     & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
+%%     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
+%% \end{align*}
+%% There is one more ingredient: in a stack discipline, one generally
+%% expects stack entries to be processed in order, rather than in parallel
+%% as would be suggested by isolated tasks.  The sequential processing of
+%% the task queue corresponds to a specific \emph{scheduling policy} of
+%% these tasks.  In fact, the choice of scheduling here is the essential difference that
+%% determines whether or not one can prove termination-insensitive or
+%% termination-sensitive non-interference. We will show how different
+%% scheduling policies give different security guarantees.
+%% 
+%% \paragraph{Exceptions versus message passing}
+%% Another language feature that has caused difficulty for
+%% many information flow control systems is exception handling
+%% when built on top of this stack discipline.
+%% %
+%% The key difficulty appears when considering the propagation of exceptions
+%% across stack boundaries where the current label is restored.
+%% %
+%% If the exception crosses this boundary, it can leak information about the
+%% inner secret computation into a public computation; hence, one must
+%% explicitly ensure that |toLabeled| does not propagate exceptions.
+%% %
+%% When stack frames are treated as isolated tasks, the correct semantics
+%% are achieved automatically.
+%% %
+%% Exceptions simply stop when the hit the top-level of a task:
+%% the only way for the frame to communicate information is by
+%% initiating inter-task message passing.
+%% %
+%% For instance,
+%% \begin{code}
+%% TI(toLabeled l (IT (if te then fail else true))); true
+%% \end{code}
+%% always evaluates to |true|, regardless of the value of |te|.
 

### 2014-10-18 paper/retrofit.tex

@@
 
-Existing language-based coarse-grained IFC
-system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
+Existing language-based, coarse-grained IFC
+systems~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
 allow a sub-computation to temporarily raise the floating-label; after
@@
 
-%% Here are two more examples of language features which have an
-%% interesting interpretation when interpreted as task communication.
-%% 
-%% \paragraph{Stack frames versus scheduling}  One feature which is
-%% supported by some information flow control systems is the ability to
-%% temporarily raise the current label in order to do computation on data
-%% (as done by LIO's |toLabeled| and Breeze's
-%% brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
-%% stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
-%% enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
-%% the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
-%% achieve termination-insensitive non-interference: if the high secrecy
-%% section doesn't terminate, this is observable by the non-execution of
-%% the defunct public continuation.
-%% 
-%% When considering tasks, we will instead say that the allocation of a new
-%% stack frame with a raised label corresponds to the creation of a new
-%% isolated task; a sample encoding using our language is as follows:
-%% \begin{align*}
-%%     & |toLabeled l te @= | \\
-%%     & |tab let i = taskId in| \\
-%% %%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
-%%     & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
-%%     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
-%% \end{align*}
-%% There is one more ingredient: in a stack discipline, one generally
-%% expects stack entries to be processed in order, rather than in parallel
-%% as would be suggested by isolated tasks.  The sequential processing of
-%% the task queue corresponds to a specific \emph{scheduling policy} of
-%% these tasks.  In fact, the choice of scheduling here is the essential difference that
-%% determines whether or not one can prove termination-insensitive or
-%% termination-sensitive non-interference. We will show how different
-%% scheduling policies give different security guarantees.
-%% 
-%% \paragraph{Exceptions versus message passing}
-%% Another language feature that has caused difficulty for
-%% many information flow control systems is exception handling
-%% when built on top of this stack discipline.
-%% %
-%% The key difficulty appears when considering the propagation of exceptions
-%% across stack boundaries where the current label is restored.
-%% %
-%% If the exception crosses this boundary, it can leak information about the
-%% inner secret computation into a public computation; hence, one must
-%% explicitly ensure that |toLabeled| does not propagate exceptions.
-%% %
-%% When stack frames are treated as isolated tasks, the correct semantics
-%% are achieved automatically.
-%% %
-%% Exceptions simply stop when the hit the top-level of a task:
-%% the only way for the frame to communicate information is by
-%% initiating inter-task message passing.
-%% %
-%% For instance,
-%% \begin{code}
-%% TI(toLabeled l (IT (if te then fail else true))); true
-%% \end{code}
-%% always evaluates to |true|, regardless of the value of |te|.
-
 \subsection{Preliminaries}
@@
 \begin{code}
-  brecvf ix1 ix2 ie @=
-  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
+brecvf ix1 ix2 ie @= (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
 \end{code}

### 2014-10-18 paper/retrofit.tex
Crossing sout

@@
     sequential setting, it more closely resembles
-
-    \sout{the LIO
-    |toLabeled|~\cite{lio} and Breeze
-    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.}
-    \Red{
     computations which might temporarely raise the current
     floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.
-    }
+
 \end{itemize}

### 2014-10-18 paper/abstract.tex
Remove Haskell

--- 2014-10-16 paper/abstract.tex
@@
 \begin{abstract}
-Web sites could compromise users' privacy by accidentally incorporating
-error-prone or malicious third-party JavaScript. Informa\-tion-flow control
-(IFC) is a promising technique to secure web sites against untrusted JavaScript
-code. Unfortunately, existing IFC approaches demand non-trivial modifications to
-the JavaScript engine or a full instrumentation of the JavaScript semantics. In
-contrast, and inspired by operating system (OS) research, we present an
-alternative technique based on attaching a single IFC policy to a single
-execution context, and therefore abstracting away from the internals of
-JavaScript. Specifically, we provide a coarse-grained IFC monitor which does not
-require any modifications to either JavaScript's semantics or its engine---the
-approach only exposes a small API to JavaScript code in order to interact
-with the monitor. To reason about our design principles, we describe a formal
-framework which treat target languages, e.g. JavaScript, as black-boxes with a
-clear interface to the monitor. We instantiate our framework to provide security
-guarantees (i.e. non-interference) to an IFC monitor implemented in Firefox.
+Many important security problems in JavaScript, such as browser
+extension security, untrusted JavaScript libraries and safe
+integration of mutually distrustful websites (mash-ups), may be
+effectively addressed using an efficient implementation of information
+flow control (IFC).  Unfortunately existing fine-grained approaches to
+JavaScript IFC require modifications to the language semantics, a
+non-goal for browser applications.  In this work we take the ideas of
+coarse-grained dynamic IFC to the limit and provide the theoretical
+foundation for a language-based approach that can be applied to any
+programming language for which external effects can be controlled.  We
+then apply this formalism to JavaScript, in the context of Node.js and
+Firefox, and show how it generalizes to the C programmings language.  Our methodology offers
+design principles for the construction of information flow control
+systems when isolation can easily be achieved, as well as
+compositional proofs for optimized concrete implementations of these
+systems, by relating them to their fully isolated variants.
 \end{abstract}

### 2014-10-18 paper/retrofit.tex
fix
Missing ref

@@
 floating-label at the point of the exception-raise must be tracked
-alongside the exception value~\cite{Hritcu:2013:YIB:2497621.2498098,
-stefan:2012:arxiv-flexiblea, Hedin:2012}.  In contrast, our system
+alongside the exception
+value~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible,Hedin:2012}.
+In contrast, our system
 provides the same flexibility and guarantees with no extra checks: tasks
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{tabular}{ll}

### 2014-10-18 paper/retrofit.tex
Pass Section 2

@@
 constructs are treated as isolated tasks, each of which have their own heaps, it
-is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
+is obviously the case that there is no sharing; in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
 not be shared, the two systems are morally equivalent. (We elaborate on
@@
 taking ECMAScript as the target language and combining it with our IFC
-language should produce the formal semantics for COWL~\cite{swapi}.  In this
+language should produce the formal semantics for the core part of COWL~\cite{swapi}.  In this
 presentation, we use a simple, untyped lambda calculus with mutable
@@
 properties without having too much detail (and because the embedding really
-doesn't care about what, exactly, is in the target language); we discuss the proper
+does not care about what, exactly, is in the target language); we discuss the proper
 embedding in more detail in Section~\ref{sec:real}.
@@
 to allow the task to read from more sensitive entities at the cost of giving up
-the ability to write to certain entities.
+the ability to write to others. %certain entities.
 
@@
 We note that first class labels, tasks (albeit named differently), and
-operations for inspecting the current label are are essentially universal to
+operations for inspecting the current label are essentially universal to
 all floating-label systems.
@@
 Of course, other choices, such as blocking communication or labeled channels,
-are possible (see Section~\ref{sec:extensions}).
+are possible. %(see Section~\ref{sec:extensions}).
 %
@@
     %
-In the target language, an IFC expression appears as |TI ie| (``target-outside,
+In the target language, an IFC expression appears as |TI ie| (``\Red{T}arget-outside,
 IFC-inside''); in the IFC language, a target language expression appears as |IT
-te| ( ``IFC-outside, target-inside'').
+te| ( ``IFC-outside, target-{\color{blue}{I}}nside'').
     \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.
@@
 %
-While these definitions simply rely on the underlying scheduling policy,
-|alpha|, to modify the task list, as we describe in Sections~\ref{sec:formal}
+While these definitions simply rely on the underlying scheduling policy
+|alpha| to modify the task list, as we describe in Sections~\ref{sec:formal}
 and~\ref{sec:extensions}, these rules (notably, \textsc{I-noStep}) are crucial

### 2014-10-18 paper/formal.tex
Pass over formal

@@
 and what non-interference properties it may have.  We also state
-theorems about our system which we prove in Section~\ref{sec:proofs}.
+theorems about our system which we prove in
+\appref{sec:app:proof}.
 In particular, we show that |specLang alpha targetLang|, with an appropriate
@@
 %
-In other words if we take two |l|-equivalent configurations, then for every
+In other words, if we take two |l|-equivalent configurations, then for every
 intermediate step taken by the first configuration, there is a corresponding

### 2014-10-18 paper/concrete.tex
Pass Section 4

@@
 mechanisms in the language to achieve a separation of the heap.
-On the other hand, for other languages this
+On the other hand, for other languages, this
 strong isolation of tasks can be
@@
 then non-interference can be violated: as we mentioned earlier,
-shared mutable cells could result in violation of noninterference.
+shared mutable cells could result in violation of non-interference.
 What we would like is a way of characterizing safe modifications to
@@
 first place.  In a statically typed language, the type system could
-prevent this from happening, and we talk more about how our
-approach integrates with typed languages in
-Section~\ref{sec:extensions:types}.
+prevent this from happening.
+%, and we talk more about how our
+%approach integrates with typed languages in
+%Section~\ref{sec:extensions:types}.
 In dynamically typed languages such as |targetLangML|, we might

### 2014-10-18 paper/real.tex
Pass on real

@@
 Furthermore, we consider how our formalism could be applied to the C
-programming language and connect it to a previous IFC system for
-Haskell.
+programming language.
+% and connect it to a previous IFC system for
+%Haskell.
 %
@@
 Luckly, this issue is not unique to our work---browser layout engines
-also rely isolating code of different origins (e.g., according to the
+also rely on isolating code of different origins (e.g., according to the
 same-origin policy).
@@
 the standard library.  For this reason, it is easy to modify
-these systems to remove arbitrary external effects when implementing
-an IFC system so important effects can be reintroduced in a safe manner.
+these systems to forbid external effects when implementing
+an IFC system, so important effects can be reintroduced in a safe manner.
 
@@
 typically require access to libraries (e.g., the file system library
-\textsf{fs}) that that have external effects.
+\textsf{fs}) that have external effects.
 %
 Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
-Instead, we implement libraries such as a labeled \textsf{fs} as
+Instead, we implement libraries (like a labeled version of \textsf{fs}) as
 message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
@@
 ensures that labels are properly propagated and enforced.
+\red{ar: ds will fix the last sentence, no clear about wrapping objects}
 %
@@
 Creating a new task with the |sandbox| system call corresponds to
-\emph{forking} a process.  Using page tables we can ensure that
+\emph{forking} a process.  Using page tables, we can ensure that
 there will be no shared memory
@@
 %
-We leave the implementation of this IFC system for C to future work.
+We leave the implementation of this IFC system for C as future work.

### 2014-10-18 paper/retrofit.tex
fix reference

@@
 not be shared, the two systems are morally equivalent. (We elaborate on
-this formally in Section~\ref{sec:single-heap}.)  Finally, these
+this formally in Section~\ref{sec:concrete}.)  Finally, these
 semantics strongly suggest that one should restrict the types of

### 2014-10-18 paper/extensions.tex

@@
 constructs.
-For example, COWL provides a labeled version of the XHR object, while
-LIO implements a labeled file system, used in server-side web
-applications~\cite{hails}.
+For example, COWL provides a labeled version of the XHR object.
+%while LIO implements a labeled file system, used in server-side web
+%applications~\cite{hails}.
 
-Our system can be extended with construct such as labeled values,
+Our system can be extended with constructs such as labeled values,
 labeled mutable references, clearance, and privileges.
@@
 \label{sec:extensions:external}
-Our embedding assumes that the target language not have any
-primitives that can induce external-world effects.
+Our embedding assumes that the target language does not have any
+primitives that can induce external effects.
 %
@@
 %
-An alternative approach is to model such effects as messages to/from
+Alternatively, it is possible to model such effects as messages to/from
 certain labeled tasks, an approach taken by our Node.js
@@
 %
-An alternative approach of restricting or wrapping unsafe primitives
-is, for example, used in COWL and JSFlow, respectively, to allow for
-controlled network communication.
+Instead of restricting or wrapping unsafe primitives,
+COWL allow for
+controlled network communication at the context boundary.
 %

### 2014-10-18 paper/formal.tex
Pass section 3
minor stuff

@@
 general definitions for what an information flow control language is
-and what non-interference properties it may have.  We also state
-theorems about our system which we prove in
-\appref{sec:app:proof}.
+and what non-interference properties it may have.
 In particular, we show that |specLang alpha targetLang|, with an appropriate
@@
 without making any reference to properties of |targetLang|.
+We state the appropriate theorems here, and provide the formal
+proofs in
+\appref{sec:app:proof}.
 
@@
 The definition of an erasure function is quite important: it captures
-the attack model, stating what can and cannot be observed by the attacker.
+the attacker model, stating what can and cannot be observed by the attacker.
 %

### 2014-10-18 paper/appendix.tex
minor

@@
   &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
-  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
-  & \text{the label of thread |id|} \\
+  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is the label of thread |id|}\\
   |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}

### 2014-10-18 paper/real.tex
Macro fix
cowl

--- 2014-10-18 paper/real.tex
@@
 %
-\subsubsection{Server-side Node.js IFC:}\ 
+\paragraph{Server-side with Node.js:}
 We have implemented |specLangJS seqf| for Node.js in the form of a
@@
 While this is safer than simply wrapping unsafe objects, adding
-featuers such as the \textsf{fs} requires the code in the main task to
+features such as the \textsf{fs} requires the code in the main task to
 ensures that labels are properly propagated and enforced.
@@
 
-\subsubsection{Client-side COWL IFC:}\
-We now describe some of the implementation aspects of
-COWL, a JavaScript implementation of coarse-grained
-IFC for Mozilla's Gecko.  This work provides the formal basis for
-the implementation, and COWL is described in much more detail in~\cite{swapi}.
+\paragraph{Client-side with COWL:}
+This work provides the formal basis for the core part of the COWL
+client-side JavaScript IFC system~\cite{swapi}.
 %
-Since the architecture of COWL is similar to that of Node.js, we focus
-on the main differences.
+Like our Node.js implementation, COWL takes a coarse-grained approach
+to providing IFC for JavaScript programs.
+%
+Unlike our implementation, however, COWL's IFC monitor is implemented in
+the browser layout engine (though still leaving the JavaScript engine
+unmodified).
 
-%Tasks in COWL  correspond to browsing contexts, such as iframes,
-%where the global object |tS0| also contains the DOM, the
-%\verb|XMLHttpRequest| (XHR) object, etc.
+Furthermore, COWL repurposes existing contexts (e.g., iframes and
+pages) as IFC tasks, only imposing additional constraints on how they
+communicate.
 %
-Existing browser APIs offer \emph{web workers}, which can
-be spawned by JavaScript code and have
-the same isolation properties as tasks in our system.
+Much like Node.js case, at its core, the global object of a COWL task
+should only contain the standard JavaScript libraries and
+\texttt{postMessage}, whose semantics are modeled by our
+\textsc{JS-send} rule.
 %
-The isolation of web workers was motivated by the lack of multithreading
-in JavaScript; however, their isolation properties are equally useful for information
-flow control.
+However, existing contexts have objects such as the DOM and COWL must
+ensure that a task's external effects are restricted.
+%
+To this end, any communication (even via the DOM) is mediated at
+the context boundary by COWL.
 
-To ensure that JavaScript code cannot communicate using the global object
-(e.g., to the network with XHR or persistent storage using the DOM),
-COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
-  Since CSP does not yet restrict message-passing or navigation, this
-  was addressed explicitly in the implementation.
-}
+Simply disallowing all external effects for is overly-restricting for
+real-world applications (e.g., pages typically load images, perform
+XHR requests etc.).
 %
-Note, that this does not prevent tasks from manipulating the DOM
-(e.g., to render information), so external effects due to DOM access
-are also suppressed.
+Hence, COWL allows safe network communication by associating an
+implicit label with remote hosts (a host's label corresponds to
+its origin).
 %
-Simply disallowing all external effects for all browsing contexts is
-overly-restricting; pages typically load images, perform XHR requests
-to dynamically load data,
-etc.
+In turn, when a task perform a request, the COWL IFC monitor
+ensures that the task label can flow to the remote origin label.
 %
-Hence, COWL allows
-controlled network communication (inter-frame communication is
-dictated by our |send| rule) by associating an implicit label with a
-remote host: namely the label corresponding to its origin.
-%
-In turn, when a task perform a request, the COWL runtime performs the
-same label check as that of |send|, namely that the task label can
-flow to
-the remote origin label.
-
-Once again, while the external effects of COWL can be formally modeled,
-we do not model these effects in our more general framework, since, like
-for Node.js case, they are application specific.
+While the external effects of COWL can be formally modeled, we do not
+model these effects in our more general framework, since, like for
+Node.js case, they are specific to this system.
 %

### 2014-10-18 paper/abstract.tex

@@
 flow control (IFC).  Unfortunately existing fine-grained approaches to
-JavaScript IFC require modifications to the language semantics, a
-non-goal for browser applications.  In this work we take the ideas of
-coarse-grained dynamic IFC to the limit and provide the theoretical
+JavaScript IFC require modifications to the language semantics and its engine, a
+non-goal for browser applications.  In this work, we take the ideas of
+coarse-grained dynamic IFC and provide the theoretical
 foundation for a language-based approach that can be applied to any
@@
 compositional proofs for optimized concrete implementations of these
-systems, by relating them to their fully isolated variants.
+systems, by relating them to their isolated variants.
 \end{abstract}

### 2014-10-18 paper/conclusion.tex

@@
 system, it is better to start with a fully isolated, multi-task system
-and work one's way back to the model of a single language.  We showed
+and work one's way back to the model of a IFC language.  We showed
 how to prove systems designed this way can be proved non-interferent,

### 2014-10-18 paper/intro.tex
remove bogus intro

@@
 In particular, maintaining data privacy in the face of malicious
-extensions, libraries, and mashup components has been difficult,
-and in general effectively impossible.
+extensions, libraries, and mashup components has been difficult.
+%and in general effectively impossible.
 
@@
 operational semantics and prove non-interference guarantees
-that are independent of the choice of specific target language.
+that are independent of the choice of an specific target language.
 
@@
 
-Our contributions can be summarized as follows: \Red{fixme:}
+Our contributions can be summarized as follows:
 \begin{itemize}
@@
 %  but may be collections of threads executing nondeterministically.
-  \item We describe ways to enrich the core IFC language with
-  more advanced concepts such as labeled values, labeled references, or a
-  notion of clearance. (Section~\ref{sec:extensions})
+%  \item We describe ways to enrich the core IFC language with
+%  more advanced concepts such as labeled values, labeled references, or a
+%  notion of clearance. (Section~\ref{sec:extensions})
 \end{itemize}

### 2014-10-18 paper/real.tex

@@
 %
-\paragraph{Server-side with Node.js:}
+\paragraph{Server-side IFC for Node.js:}
 We have implemented |specLangJS seqf| for Node.js in the form of a
@@
 %
-While this is safer than simply wrapping unsafe objects, adding
+While this is safer than simply wrapping unsafe objects, which can
+potentially be exploited to access objects outside the context, adding
 features such as the \textsf{fs} requires the code in the main task to
@@
 
-\paragraph{Client-side with COWL:}
+\paragraph{Client-side IFC:}
 This work provides the formal basis for the core part of the COWL

### 2014-10-18 paper/retrofit.tex

@@
 to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
-Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
-and that tasks continues its execution with |ie2|.
+Otherwise, if there are no messages, that tasks continues its execution with |ie2|.
 We denote the filtering of the message queue by |filter il Q|,
@@
 IFC-inside''); in the IFC language, a target language expression appears as |IT
-te| ( ``IFC-outside, target-{\color{blue}{I}}nside'').
+te| ( ``{\color{blue}{I}}FC-outside, target-Inside'').
     \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.

### 2014-10-18 paper/real.tex
nits

@@
 Luckly, this issue is not unique to our work---browser layout engines
-also rely on isolating code of different origins (e.g., according to the
+also rely on isolating code executing in separate iframes (e.g., according to the
 same-origin policy).

### 2014-10-18 paper/retrofit.tex
nit
nits
target-Inside -> target-inside

@@
 
-For our first example, here is a program which spawns a new isolated task,
+As an example, here is a program which spawns a new isolated task,
 and then sends it a mutable reference:
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{code}
@@
 IFC-inside''); in the IFC language, a target language expression appears as |IT
-te| ( ``{\color{blue}{I}}FC-outside, target-Inside'').
+te| ( ``{\color{blue}{I}}FC-outside, target-inside'').
     \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.

### 2014-10-18 paper/real.tex
Pass over COWL

@@
 %
-Unlike our implementation, however, COWL's IFC monitor is implemented in
-the browser layout engine (though still leaving the JavaScript engine
+%Unlike our implementation,
+However, COWL's IFC monitor is implemented in
+the browser layout engine instead (though still leaving the JavaScript engine
 unmodified).
@@
 %
-Much like Node.js case, at its core, the global object of a COWL task
+As for Node.js, at its core, the global object of a COWL task
 should only contain the standard JavaScript libraries and
@@
 %
-However, existing contexts have objects such as the DOM and COWL must
-ensure that a task's external effects are restricted.
+However, existing contexts have objects such as the DOM, which
+demands COWL to restrict a task's external effects.
 %
-To this end, any communication (even via the DOM) is mediated at
-the context boundary by COWL.
+To this end, COWL mediates any communication (even via the DOM) at
+the context boundary. %by COWL.
 
-Simply disallowing all external effects for is overly-restricting for
+Simply disallowing all the external effects is overly-restricting for
 real-world applications (e.g., pages typically load images, perform
-XHR requests etc.).
+XHR requests, etc.).
 %
-Hence, COWL allows safe network communication by associating an
+In this light, COWL allows safe network communication by associating an
 implicit label with remote hosts (a host's label corresponds to
@@
 %
-In turn, when a task perform a request, the COWL IFC monitor
+In turn, when a task perform a request, the COWL's IFC monitor
 ensures that the task label can flow to the remote origin label.
@@
 While the external effects of COWL can be formally modeled, we do not
-model these effects in our more general framework, since, like for
+model them in our formalism, %more general framework,
+since, like for the
 Node.js case, they are specific to this system.

### 2014-10-18 paper/appendix.tex
add some qed's.

@@
 
-\section{IFC Language with a Single Heap}
+\section{Example IFC Language with a Single Heap}
 \label{sec:single-heap}
@@
 
-\section{Extensions}
+\section{Extending the Core Calculus}
 \label{sec:appendix-extensions}
@@
 
-\section{Limitations and Future Directions}
-
-In this section we state some limitations of the current system, and
-outline potential future directions to alleviate these limitations.
-
-\subsection{Type Safety}
-\label{sec:extensions:types}
-
-One important consideration for any new language feature is whether
-or not it preserves type safety.  If implementations are allowed to
-have undefined behavior when the system gets stuck, concerns of type
-safety can be directly applicable to security.
-
-In our presentation, we have demanded that implementations \emph{not}
-have undefined behavior when getting stuck: in such situations, the
-\textsc{I-noStep} rule applies, where the stuck thread should be dropped
-from execution.  Our combined language will be not get stuck, even if
-the target language could get stuck.  This sort of guarantee can be
-achieved at a coarse granularity for languages like C by using hard
-isolation.  However, for many other languages, this is too stringent a
-requirement.
-
-A possible way to relax this requirement is to drop the \textsc{I-noStep}
-rule, and instead demand type-safety of the combined language.  This
-depends on the type system of the target language, so it is difficult to
-make any general statements about how one would go about doing this.  However,
-there are few general remarks to be made:
-
-\begin{itemize}
-    \item In Matthews and Findler's original
-        paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
-        on using type boundaries to mediate between the type systems of
-        the two languages, i.e. handling conversions of values from
-        one language to the other.  These techniques are directly applicable here.
-
-    \item In the case of mini-ES, type safety proceeds by a preservation theorem
-        that refers to well-typed stores.  In our setting, there are now multiple
-        stores, and expressions may move from being interpreted with one store
-        to another (e.g. when an address is sent from one thread to
-        another); a clear violation of type safety.  In this case, operations
-        such as |send| have their typing rules require
-        the expressions being sent be typeable in an arbitrary well-typed store,
-        statically disallowing the sending of addresses, or any types which
-        may contain addresses.  In practice, this may be further restricted to
-        types which can be easily marshalled, e.g. strings.
-
-    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
-        influences the difficulty of the type-safety proof for
-        |sandbox| when the target language has a store.  When
-        $\kappa$ is identity, most expressions can be allowed, since the store
-        remains the same; if $\kappa$ drops the store, however, only closed expressions
-        can be sandboxed.
-\end{itemize}
-
-\subsection{Scheduling Policies}
-Our specification language is parametrized by a scheduling policy |alpha|, which
-maps a task list to a potentially different task list, i.e.,
-$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
-%
-As previously discussed, the precise definition of |alpha|
-dictates whether the language is TSNI, TINI, or neither.
-%
-We described two popular policies |roundrobinf| and
-|seqf| for which we showed TSNI and TINI, respectively.
-%
-However, our definitions allow for other scheduling policies based on the
-current task list---in fact, our formalism can be easily 
-extended to consider history~\cite{BartheRRS07}.
-%
-As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
-which always schedules less sensitive threads first; this can be
-employed to address external timing covert channels where an attacker
-can measure the delay between output events.\footnote{
-  When considering a label lattice that is not totally ordered, e.g.,
-  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
-  considerably more complex.
-}
-%
-More precisely, our calculus generalizes to a class of deterministic
-schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
-modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
-%greatest lower bound of all the labels on the task labels,\footnote{
-%  The label on a task's current label is the current label of the
-%  parent at the time of creation, i.e., the initial current label of
-%  the task.
-%} 
-scheduling decisions on public tasks do not depend on a sensitive task's
-state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
-is a task in the task list whose label is below (or incomparable to) the label
-of another task, this task (or another one at the same level) must eventually
-run.
-%
-The last condition is required for TSNI; languages relying on
-schedulers, such as |seqf|, that do not satisfy the low-progress
-condition can at most satisfy TINI.
-%
-For simplicity, we do not treat this, more-general class of schedulers;
-doing so would require modifying our calculus to keep track of the
-label on the current label of tasks and complicate the
-non-interference proofs.
-
-More fundamentally, our scheduler parametrization is limited in being
-deterministic, and thus extending the system to consider non-deterministic
-schedulers (or even non-deterministic target languages) is non-trivial.
-%
-%For instance,  we do not consider  schedulers that, among other, rely
-%on the global state |iS| or previous task configurations, as treated
-%in~\cite{russo2006securing}.
-%
-%Additionally, our definitions rely on deterministic relations,
-%
-Such extensions often apply security conditions which suffer 
-from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
-adapt non-trivial definitions as
-\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
-which states that a program is secure only if |l|-equivalent results are
-deterministic.
+%% \section{Limitations and Future Directions}
+%% 
+%% In this section we state some limitations of the current system, and
+%% outline potential future directions to alleviate these limitations.
+%% 
+%% \subsection{Type Safety}
+%% \label{sec:extensions:types}
+%% 
+%% One important consideration for any new language feature is whether
+%% or not it preserves type safety.  If implementations are allowed to
+%% have undefined behavior when the system gets stuck, concerns of type
+%% safety can be directly applicable to security.
+%% 
+%% In our presentation, we have demanded that implementations \emph{not}
+%% have undefined behavior when getting stuck: in such situations, the
+%% \textsc{I-noStep} rule applies, where the stuck thread should be dropped
+%% from execution.  Our combined language will be not get stuck, even if
+%% the target language could get stuck.  This sort of guarantee can be
+%% achieved at a coarse granularity for languages like C by using hard
+%% isolation.  However, for many other languages, this is too stringent a
+%% requirement.
+%% 
+%% A possible way to relax this requirement is to drop the \textsc{I-noStep}
+%% rule, and instead demand type-safety of the combined language.  This
+%% depends on the type system of the target language, so it is difficult to
+%% make any general statements about how one would go about doing this.  However,
+%% there are few general remarks to be made:
+%% 
+%% \begin{itemize}
+%%     \item In Matthews and Findler's original
+%%         paper~\cite{Matthews:2007:OSM:1190216.1190220}, an emphasis was
+%%         on using type boundaries to mediate between the type systems of
+%%         the two languages, i.e. handling conversions of values from
+%%         one language to the other.  These techniques are directly applicable here.
+%% 
+%%     \item In the case of mini-ES, type safety proceeds by a preservation theorem
+%%         that refers to well-typed stores.  In our setting, there are now multiple
+%%         stores, and expressions may move from being interpreted with one store
+%%         to another (e.g. when an address is sent from one thread to
+%%         another); a clear violation of type safety.  In this case, operations
+%%         such as |send| have their typing rules require
+%%         the expressions being sent be typeable in an arbitrary well-typed store,
+%%         statically disallowing the sending of addresses, or any types which
+%%         may contain addresses.  In practice, this may be further restricted to
+%%         types which can be easily marshalled, e.g. strings.
+%% 
+%%     \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
+%%         influences the difficulty of the type-safety proof for
+%%         |sandbox| when the target language has a store.  When
+%%         $\kappa$ is identity, most expressions can be allowed, since the store
+%%         remains the same; if $\kappa$ drops the store, however, only closed expressions
+%%         can be sandboxed.
+%% \end{itemize}
+%% 
+%% \subsection{Scheduling Policies}
+%% Our specification language is parametrized by a scheduling policy |alpha|, which
+%% maps a task list to a potentially different task list, i.e.,
+%% $\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
+%% %
+%% As previously discussed, the precise definition of |alpha|
+%% dictates whether the language is TSNI, TINI, or neither.
+%% %
+%% We described two popular policies |roundrobinf| and
+%% |seqf| for which we showed TSNI and TINI, respectively.
+%% %
+%% However, our definitions allow for other scheduling policies based on the
+%% current task list---in fact, our formalism can be easily 
+%% extended to consider history~\cite{BartheRRS07}.
+%% %
+%% As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
+%% which always schedules less sensitive threads first; this can be
+%% employed to address external timing covert channels where an attacker
+%% can measure the delay between output events.\footnote{
+%%   When considering a label lattice that is not totally ordered, e.g.,
+%%   DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
+%%   considerably more complex.
+%% }
+%% %
+%% More precisely, our calculus generalizes to a class of deterministic
+%% schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
+%% modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
+%% %greatest lower bound of all the labels on the task labels,\footnote{
+%% %  The label on a task's current label is the current label of the
+%% %  parent at the time of creation, i.e., the initial current label of
+%% %  the task.
+%% %} 
+%% scheduling decisions on public tasks do not depend on a sensitive task's
+%% state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
+%% is a task in the task list whose label is below (or incomparable to) the label
+%% of another task, this task (or another one at the same level) must eventually
+%% run.
+%% %
+%% The last condition is required for TSNI; languages relying on
+%% schedulers, such as |seqf|, that do not satisfy the low-progress
+%% condition can at most satisfy TINI.
+%% %
+%% For simplicity, we do not treat this, more-general class of schedulers;
+%% doing so would require modifying our calculus to keep track of the
+%% label on the current label of tasks and complicate the
+%% non-interference proofs.
+%% 
+%% More fundamentally, our scheduler parametrization is limited in being
+%% deterministic, and thus extending the system to consider non-deterministic
+%% schedulers (or even non-deterministic target languages) is non-trivial.
+%% %
+%% %For instance,  we do not consider  schedulers that, among other, rely
+%% %on the global state |iS| or previous task configurations, as treated
+%% %in~\cite{russo2006securing}.
+%% %
+%% %Additionally, our definitions rely on deterministic relations,
+%% %
+%% Such extensions often apply security conditions which suffer 
+%% from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
+%% adapt non-trivial definitions as
+%% \emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
+%% which states that a program is secure only if |l|-equivalent results are
+%% deterministic.
 
@@
   \end{description}
+  \qed
 \end{proof}
@@
   \end{itemize}
+  \qed
 \end{proof}
@@
   definition~\eqref{eq:tsni-rhs}, which concludes the proof.
+  \qed
 \end{proof}

### 2014-10-18 paper/conclusion.tex

@@
 system, it is better to start with a fully isolated, multi-task system
-and work one's way back to the model of a IFC language.  We showed
-how to prove systems designed this way can be proved non-interferent,
+and work one's way back to the model of a single language equipped
+with IFC.  We showed
+how to prove systems designed this way can be proved non-interferent
 without needing to rely on details of the target language, and

### 2014-10-18 paper/conclusion.tex
bringing haskell back

@@
 to two IFC implementations for JavaScript based on this formalism,
-%explained how our methodology improved an exiting IFC system for Haskell,
+explained how our methodology improved an exiting IFC system for Haskell,
 and proposed

### 2014-10-18 paper/real.tex
bringing haskell back

--- 2014-10-18 paper/real.tex
@@
 Furthermore, we consider how our formalism could be applied to the C
-programming language.
-% and connect it to a previous IFC system for
-%Haskell.
+programming language
+and connect it to a previous IFC system for
+Haskell.
 %
@@
 
-%\subsection{Haskell}
-%\label{sec:real:hs}
-%Our work borrows ideas from a Haskell coarse-grained IFC
-%system called LIO~\cite{lio, stefan:addressing-covert}.
-%%
-%LIO relies on Haskell's strong type system and monadic encoding of
-%side-effecting computations to achieve isolation and define the IFC
-%sub-language.
-%%
-%Specifically LIO provides the \verb|LIO| monad as a way of restricting
-%(almost all) side-effects; this monad also keeps track of a current
-%label which is, in turn, used by trusted code when defining core IFC
-%functions, such as |getLabel|.
-%%
-%In the context of our framework, LIO can be understood as follows: the
-%\emph{pure subset} of Haskell is the target language, while the
-%monadic subset of Haskell, operating in the \verb|LIO| monad, is the
-%IFC language.
+\subsection{Haskell}
+\label{sec:real:hs}
+Our work borrows ideas from the LIO Haskell coarse-grained IFC
+system~\cite{lio, stefan:addressing-covert}.
 %
-%%Indeed, by rephrasing LIO in terms of our framework, we simplified
-%%LIO's treatment of exceptions.
-%%
-%LIO originally associated labels with exceptions, in a
-%similar style to fine-grained
-%systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
-%%
-%In particular, the label of an exception was set to the current label
-%at the time of the throw, and used by a custom catch construct to
-%raise the current label, thereby preventing leaks due to exceptional
-%control flows.
-%%
-%In addition to being overly complex, the interaction of exceptions
-%with clearance (which sets an upper bound on the current label, see
-%Section~\ref{sec:clearance}) was incorrect: the clearance
-%was restored to the clearance at point of the catch (a consequence of
-%defining \verb|LIO| using a State monad).
-%%
-%Furthermore, pure exceptions (e.g., divide by zero) always percolated to
-%trusted code, effectively allowing for denial of service attacks.
-%%
-%The insights gained when viewing coarse-grained IFC as presented in this
-%paper led to a much cleaner, simpler treatment of exceptions in LIO,
-%which has now been adapted by LIO.
-%%By using isolated tasks, and thus treating the current label (and
-%%clearance) as global, the underlying Haskell exception system can be
-%%used directly: exceptional control flow does not affect IFC.
+LIO relies on Haskell's type system and monadic encoding of
+effects to achieve isolation and define the IFC sub-language.
+%
+Specifically, LIO provides the \verb|LIO| monad as a way of restricting
+(almost all) side-effects.
+%
+In the context of our framework, LIO can be understood as follows: the
+\emph{pure subset} of Haskell is the target language, while the
+monadic subset of Haskell, operating in the \verb|LIO| monad, is the
+IFC language.
+
+%Indeed, by rephrasing LIO in terms of our framework, we simplified
+%LIO's treatment of exceptions.
+%
+Different from our proposal, LIO originally associated labels with exceptions, in a
+similar style to fine-grained
+systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
+%
+In addition to being overly complex, the interaction of exceptions
+with clearance (which sets an upper bound on the floating label, see
+Section~\ref{sec:clearance}) was incorrect: the clearance
+was restored to the clearance at point of the catch.
+%
+Furthermore, pure exceptions (e.g., divide by zero) always percolated to
+trusted code, effectively allowing for denial of service attacks.
+%
+The insights gained when viewing coarse-grained IFC as presented in this
+paper led to a much cleaner, simpler treatment of exceptions in LIO,
+which has now been adapted by LIO.
+%By using isolated tasks, and thus treating the current label (and
+%clearance) as global, the underlying Haskell exception system can be
+%used directly: exceptional control flow does not affect IFC.
 

### 2014-10-18 paper/abstract.tex
haskell in the intro

@@
 programming language for which external effects can be controlled.  We
-then apply this formalism to JavaScript, in the context of Node.js and
-Firefox, and show how it generalizes to the C programmings language.  Our methodology offers
+then apply this formalism to server- and client-side JavaScript,
+show how it generalizes to the C programmings language, and connect it
+to the Haskell LIO system.  Our methodology offers
 design principles for the construction of information flow control

### 2014-10-18 paper/intro.tex
rm
bringing haskell back
haskell back in intro

@@
 technical details of the semantics of the underlying programming language.
-\Red{ds: this last senstence needs work}
 
@@
   the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
-  \item We have implemented an IFC system based on these semantics
+  \item We implemented an IFC system based on these semantics
   for Node.js, and we connect our formalism to another implementation
-  based on this work
-  for client-side JavaScript in~\cite{swapi}.
+  based on this work for client-side JavaScript~\cite{swapi}.
   Furthermore, we outline an implementation for the C programming
-  language.
+  language and describe improvements to the Haskell LIO system that
+  resulted from this framework.
   (Section~\ref{sec:real})

### 2014-10-18 paper/extensions.tex
minor fixes
nits

@@
-\section{Extensions, Limitations, and Future Direction}
+\section{Extensions and Limitations}
 \label{sec:extensions}
@@
 %applications~\cite{hails}.
-
+%
 Our system can be extended with constructs such as labeled values,
 labeled mutable references, clearance, and privileges.
-For space reasons, we provide full formal semantics (including the soundness
-proof with the extensions) in \appendixextfirst{}.
+For space reasons, we provide
+details of this, including the soundness
+proof with the extensions, in \appendixextfirst{}.
+%
+Here, we instead discuss a limitation of our formalism: the lack of
+external effects.
 
-\subsection{External Effects}
-\label{sec:extensions:external}
-Our embedding assumes that the target language does not have any
-primitives that can induce external effects.
+%\subsection{External Effects}
+%\label{sec:extensions:external}
+Specifically, our embedding assumes that the target language does not
+have any primitives that can induce external effects.
 %

### 2015-01-07 paper/appendix.tex
Figure -> Fig.

@@
 
-In Figure~\ref{fig:ml-full} we give the full semantics for |targetLangML|.  A subset
-of them has been given in Figure~\ref{fig:ml} earlier in the paper.
+In Fig.~\ref{fig:ml-full} we give the full semantics for |targetLangML|.  A subset
+of them has been given in Fig.~\ref{fig:ml} earlier in the paper.
 
@@
 which we call |concreteLangMl alpha|,
-are given in Figure~\ref{fig:concrete}.  Most rules are
-straight-forward translations of the rules in Figures~\ref{fig:ifc}
+are given in Fig.~\ref{fig:concrete}.  Most rules are
+straight-forward translations of the rules in Figs.~\ref{fig:ifc}
 and~\ref{fig:embedding} but for a single heap.  For conciseness, we
@@
 
-In Figure~\ref{fig:labeled-vals}, we formally show how to add this
+In Fig.~\ref{fig:labeled-vals}, we formally show how to add this
 extension to the language.
@@
 
-In Figure~\ref{fig:labeled-refs} details labeled references formally.
+In Fig.~\ref{fig:labeled-refs} details labeled references formally.
 The construct |ial| is internal in the labeled reference implementation,
@@
 references require us to update the erasure function
-|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
+|erasef il|, whose full definition is shown in Fig.~\ref{fig:erasure2}.
 
@@
     (e.g., |erase il (setLabel e) = setLabel (erase il e)|).
-    This definition replaces the one from Figure~\ref{fig:erasure}, which
+    This definition replaces the one from Fig.~\ref{fig:erasure}, which
     is for the IFC language without extensions.}

### 2015-01-07 paper/formal.tex
Figure -> Fig.

@@
 The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
-containing |bullet|, and Figure~\ref{fig:erasure} gives the precise definition for
+containing |bullet|, and Fig.~\ref{fig:erasure} gives the precise definition for
 our erasure function |erasef il|.
@@
 under the round-robin scheduler
-|roundrobinf| given in Figure~\ref{fig:scheduler}.
+|roundrobinf| given in Fig.~\ref{fig:scheduler}.
 
@@
 Consider, for example, the sequential scheduling policy |seqf| given in
-Figure~\ref{fig:scheduler}.
+Fig.~\ref{fig:scheduler}.
 %

### 2015-01-07 paper/real.tex
Figure -> Fig.

@@
 etc.) of each task.  An example for |send|/|recv| is shown in
-Figure~\ref{fig:node}.
+Fig.~\ref{fig:node}.
 %While V8 provides a means for sharing any object between contexts (used
@@
 message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
-in Figure~\ref{fig:node}) and the main Node.js task that implements
+in Fig.~\ref{fig:node}) and the main Node.js task that implements
 the IFC monitor.

### 2015-01-07 paper/retrofit.tex
Figure -> Fig.

@@
 
-In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
+In Fig.~\ref{fig:ml}, we give a simple, untyped lambda calculus with
 mutable references and fixpoint, prepared for combination with an
@@
 
-In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-task}
+In Fig.~\ref{fig:ifc}, we give the syntax and \emph{single-task}
 evaluation rules for a minimal information-flow control language.
@@
 \subsection{The Embedding}
-Figure~\ref{fig:embedding}
+Fig.~\ref{fig:embedding}
 provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
@@
 The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
-    Figure~\ref{fig:scheduler} defines two concrete schedulers.
+    Fig.~\ref{fig:scheduler} defines two concrete schedulers.
     \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),

### 2015-01-07 paper/concrete.tex
add some qed's.
presentational issue from reviewer 1

@@
 
-\begin{definition}[Isomorphism of information-flow control languages]
+\begin{definition}[Isomorphism of information flow control languages]
   A language |(C, .->, erasef l)| is \textit{isomorphic} to a
@@
   resulting configuration, $l$-equivalence and multi-step derivation back.
+  \qed
 \end{proof}
@@
   equivalence back using functoriality of |finv| over $l$-equivalences.
+  \qed
 \end{proof}

### 2015-01-07 paper/formal.tex
presentational issue from reviewer 1

@@
 
-TSNI states that if we take two |l|-equivalent configurations, and both
+TINI states that if we take two |l|-equivalent configurations, and both
 configurations reduce to final configurations (i.e.,

### 2015-01-07 paper/intro.tex
presentational issue from reviewer 1

@@
 using an approach by
-Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
+Matthews and Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
 operational semantics and prove non-interference guarantees
@@
 isolation of \emph{execution contexts}, e.g.\ an instance of the
-JavaScript engine, in order to add information-flow control to an
+JavaScript engine, in order to add information flow control to an
 existing language.  This is a very practical approach, as there are many

### 2015-01-07 paper/real.tex
presentational issue from reviewer 1

@@
 real-world applications (e.g., pages typically load images, perform
-XHR requests, etc.).
+network requests, etc.).
 %

### 2015-01-07 paper/retrofit.tex
presentational issue from reviewer 1

@@
 In Fig.~\ref{fig:ifc}, we give the syntax and \emph{single-task}
-evaluation rules for a minimal information-flow control language.
+evaluation rules for a minimal information flow control language.
 Ordinarily, information flow control languages are defined by directly
@@
 function, in which
-case the semantics of sandbox are such that the state of the target language is \emph{cloned}
+case the semantics of |sandbox| are such that the state of the target language is \emph{cloned}
 when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|

### 2015-01-07 paper/abstract.tex
reviewer 1 grammar/spelling

--- 2014-10-18 paper/abstract.tex
@@
 programming language for which external effects can be controlled.  We
-then apply this formalism to JavaScript, in the context of Node.js and
-Firefox, and show how it generalizes to the C programmings language.  Our methodology offers
+then apply this formalism to server- and client-side JavaScript,
+show how it generalizes to the C programming language, and connect it
+to the Haskell LIO system.  Our methodology offers
 design principles for the construction of information flow control

### 2015-01-07 paper/conclusion.tex
reviewer 1 grammar/spelling

@@
 with IFC.  We showed
-how to prove systems designed this way can be proved non-interferent
+how systems designed this way can be proved non-interferent
 without needing to rely on details of the target language, and

### 2015-01-07 paper/concrete.tex
reviewer 1 grammar/spelling

@@
 more tightly couple the integration of the target and IFC
-language by reusing existing infrastructure.  In the running example,
+languages by reusing existing infrastructure.  In the running example,
 a concrete implementation might use a single global heap.
@@
 This intuition of having a different (potentially more efficient)
-concrete semantics that behave like the abstract semantics
+concrete semantics that behaves like the abstract semantics
 can be formalized by the following definition:
@@
 Only weak isomorphism is necessary for TINI. Intuitively, this is because
-is not necessary to back-translate reduction sequences in $L'$ to
+it is not necessary to back-translate reduction sequences in $L'$ to
 $L$; by the definition of TINI, we have both reduction sequences in $L$
@@
 The rule for sandboxing is
-parametrized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
+parametrized by the strategy |klone| (see Section~\ref{sec:retrofit}),
 which defines what heap the new task
@@
 While this sounds plausible, it is worth noting that we are modifying the IFC language semantics,
-which raises the question whether non-interference is preserved.
+which raises the question of whether non-interference is preserved.
 This question can be subtle: it is easy to remove a transition from
@@
 if the restriction depends on secret data, then a public thread
-can observe if some other task terminates or not, and by that obtain
+can observe if some other task terminates or not, and from that obtain
 information about the secret data that was used to restrict the
@@
   by adding a predicate $P \in \mathcal P$ to the premise of
-  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
+  all rules other than \textsc{I-noStep}.  Furthermore, the predicates $P$
   can depend only on the \textit{erased} configuration

### 2015-01-07 paper/formal.tex
reviewer 1 grammar/spelling

@@
 list if its label does not flow to the attacker observation level |il|.
-Otherwise, we apply the erasure function homomorphically and remove any message
+Otherwise, we apply the erasure function homomorphically and remove any messages
 from the task's message queue that are more sensitive than |il|.
@@
 relation called |l|-equivalence on configurations: an attacker should
-not be able to distinguish two configuration that are |l|-equivalent.
+not be able to distinguish two configurations that are |l|-equivalent.
 %
@@
 Though we do not model labeled channels, extending the calculus with such a
-feature is straight forward, see Section~\ref{sec:extensions}.}
+feature is straightforward, see Section~\ref{sec:extensions}.}
 then the |sec| task's decision to diverge or not is directly leaked to a

### 2015-01-07 paper/intro.tex
reviewer 1 grammar/spelling

@@
 %systems were the runtime overhead can be impractical~\cite{JSFlow}.
-Finally, by associating
+Finally, associating
 a single security label with the entire computational unit simplifies
@@
 operational semantics and prove non-interference guarantees
-that are independent of the choice of an specific target language.
+that are independent of the choice of a specific target language.
 
@@
   by means of an isomorphism and show a class of restrictions on
-  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
-  \item We implemented an IFC system based on these semantics
+  the IFC language that preserves non-interference. (Section~\ref{sec:concrete})
+  \item We have implemented an IFC system based on these semantics
   for Node.js, and we connect our formalism to another implementation

### 2015-01-07 paper/real.tex
reviewer 1 grammar/spelling

@@
 
-Luckly, this issue is not unique to our work---browser layout engines
+Luckily, this issue is not unique to our work---browser layout engines
 also rely on isolating code executing in separate iframes (e.g., according to the
@@
 %
-(We will use these terms interchangably.)
+(We will use these terms interchangeably.)
 %
@@
 %
-When mapped to our formal treatement, |sandbox| is defined with |ap
+When mapped to our formal treatment, |sandbox| is defined with |ap
 klone tS = tS0|, where |tS0| is the global object corresponding to the
@@
 %
-As for Node.js, at its core, the global object of a COWL task
+As with Node.js, at its core, the global object of a COWL task
 should only contain the standard JavaScript libraries and
@@
 %
-In turn, when a task perform a request, the COWL's IFC monitor
+In turn, when a task perform a request, COWL's IFC monitor
 ensures that the task label can flow to the remote origin label.
@@
 %
-Different from our proposal, LIO originally associated labels with exceptions, in a
+Unlike our proposal, LIO originally associated labels with exceptions, in a
 similar style to fine-grained
@@
 paper led to a much cleaner, simpler treatment of exceptions in LIO,
-which has now been adapted by LIO.
+which has now been adopted by LIO.
 %By using isolated tasks, and thus treating the current label (and
@@
 = tS0|, where |tS0| is the set of pages necessary to bootstrap a
-lightweight process.)
+lightweight process).
 %

### 2015-01-07 paper/related.tex
presentational issue from reviewer 1
reviewer 1 grammar/spelling

@@
 SME considering one specific programming
-language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova
+language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
 al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
@@
 information flow control system for JavaScript.  Some of these systems attempt
-to perform fine-grained information flow of
+to perform fine-grained information flow control of
 JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
-control can result in less false alarms and target legacy code, it comes at the
+control can result in fewer false alarms and target legacy code, it comes at the
 cost of complexity (the system must accommodate the entirety of JavaScript's
@@
 The constructs in our IFC language, as well as the behavior of
-inter-thread communication, is reminiscent of distributed systems
+inter-thread communication, are reminiscent of distributed systems
 like Erlang~\cite{Armstrong03makingreliable}.  There is a close
@@
 encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
-encodes several IFC systems into Paralocks.  However, this line of work is
+encode several IFC systems into Paralocks.  However, this line of work is
 primarily focused on static enforcements.

### 2015-01-07 paper/retrofit.tex
reviewer 1 grammar/spelling

@@
 
-Before moving on to the formal treatment of our system, we'd like to give
+Before moving on to the formal treatment of our system, we give
 a brief primer of information flow control and describe some example programs
@@
 
-Our design principles suggests a different resolution: when these
+Our design principles suggest a different resolution: when these
 constructs are treated as isolated tasks, each of which have their own heaps, it
@@
 not be shared, the two systems are morally equivalent. (We elaborate on
-this formally in Section~\ref{sec:concrete}.)  Finally, these
-semantics strongly suggest that one should restrict the types of
+this formally in Section~\ref{sec:concrete}.)  Finally, this
+semantics strongly suggests that one should restrict the types of
 data which may be passed between tasks (for example, in JavaScript, one
@@
 references and fixpoint in place of ECMAScript, to demonstrate some of the key
-properties without having too much detail (and because the embedding really
+properties without including too much detail (and because the embedding really
 does not care about what, exactly, is in the target language); we discuss the proper
@@
 These operations are all defined with respect to an evaluation context
-|curlyBlueE| that represents the context of the current task which, by
-conventions is running. The evaluation context has three important pieces of
+|curlyBlueE| that represents the context of the current task which.
+The evaluation context has three important pieces of
 state: the global message queues |iS|, the current label |il| and the task ID |id|.
 
-We note that first class labels, tasks (albeit named differently), and
+We note that first-class labels, tasks (albeit named differently), and
 operations for inspecting the current label are essentially universal to
@@
 discussion.  When a task is sending a message using |send|, it also labels that
-message with a label |il'| (which must be above the tasks current label |il|).
+message with a label |il'| (which must be above the task's current label |il|).
 Messages can only be received by a task if its current label is
@@
 to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
-Otherwise, if there are no messages, that tasks continues its execution with |ie2|.
+Otherwise, if there are no messages, that task continues its execution with |ie2|.
 We denote the filtering of the message queue by |filter il Q|,
@@
 Fig.~\ref{fig:embedding}
-provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
+provides all of the rules responsible for actually carrying out the embedding of the IFC language within the target language.
 The most important feature of this embedding is that every task maintains its own
@@
     \item We extend the values, expressions and evaluation contexts of
-      both languages to allow for embeddings terms in one language to
+      both languages to allow for terms in one language to
       be embedded in the other, as

### 2015-01-07 paper/concrete.tex
minor errors from reviewer 1

@@
   by adding a predicate $P \in \mathcal P$ to the premise of
-  all rules other than \textsc{I-noStep}.  Furthermore, the predicates $P$
+  all rules other than \textsc{I-noStep}.  Furthermore, the predicate $P$
   can depend only on the \textit{erased} configuration

### 2015-01-07 paper/formal.tex
minor fixes from reviewer 2

@@
 (in two steps)
-to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
+to |ic1' = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
 any progress.

### 2015-01-07 paper/retrofit.tex
minor errors from reviewer 1
minor fixes from reviewer 2

@@
 discussion.  When a task is sending a message using |send|, it also labels that
-message with a label |il'| (which must be above the task's current label |il|).
+message with a label |il'| (which must be at or above the task's current label |il|).
 Messages can only be received by a task if its current label is
@@
 \[
-|filter il ((il', id, ie) , Q )| = \left\{
+|filter il (((il', id, ie) , Q) )| = \left\{
 \begin{array}{l l}
-|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
+|(il', id, ie) , (filter il Q)| & \quad \text{if |il' canFlowTo il|}\\
 |filter il Q| & \quad \text{otherwise}

### 2015-01-15 paper/concrete.tex
pass over everything except related and conclusion

@@
 then non-interference can be violated: as we mentioned earlier,
-shared mutable cells could result in violation of non-interference.
+shared mutable cells could be used to leak sensitive information.
 What we would like is a way of characterizing safe modifications to
@@
 
-\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
+\begin{theorem}[Isomorphism preserves TSNI]
   \label{thm:iso-tsni}
@@
 
-\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
+\begin{theorem}[Weak isomorphism preserves TINI]
   \label{thm:iso-tini}
@@
   |specLang alpha targetLang|, with the following exception:
-  The reduction rules are restricted
+  the reduction rules are restricted
   by adding a predicate $P \in \mathcal P$ to the premise of
@@
   |erase il ic|, where |il| is the label of the first task
-  in the task list and |ic| the full configuration.
+  in the task list and |ic| is the full configuration.
 \end{definition}

### 2015-01-15 paper/extensions.tex
presentational issue from reviewer 1
pass over everything except related and conclusion

@@
 constructs.
-For example, COWL provides a labeled version of the XHR object.
+For example, COWL provides a labeled version of the XMLHttpRequest (XHR) object,
+which is used to make network requests.
 %while LIO implements a labeled file system, used in server-side web
@@
 Previous approaches have modeled external effects by internalizing the
-effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
+effects as operations on labeled channels/references~\cite{stefan:addressing-covert}.
 %

### 2015-01-15 paper/real.tex
pass over everything except related and conclusion

@@
 Since creating an OS thread for each iframe is expensive, both
-the V8 and SpiderMonkey JavaScript engines provide a means for running
-JavaScript code in isolation in a single OS thread,
+the V8 and SpiderMonkey JavaScript engines provide means for running
+JavaScript code in isolation within a single OS thread,
 on disjoint sub-heaps.
@@
 these systems to forbid external effects when implementing
-an IFC system, so important effects can be reintroduced in a safe manner.
+an IFC system, ensuring that important effects can be reintroduced in a safe manner.
 
@@
 However, existing contexts have objects such as the DOM, which
-demands COWL to restrict a task's external effects.
+require COWL to restrict a task's external effects.
 %
@@
 %
-In turn, when a task perform a request, COWL's IFC monitor
+In turn, when a task performs a request, COWL's IFC monitor
 ensures that the task label can flow to the remote origin label.
@@
 The insights gained when viewing coarse-grained IFC as presented in this
-paper led to a much cleaner, simpler treatment of exceptions in LIO,
+paper led to a much cleaner, simpler treatment of exceptions,
 which has now been adopted by LIO.
@@
 hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
-similar to a simpler version of
+similar to 
 Wedge~\cite{Belay:2012:DSU:2387880.2387913,
-Bittau:2008:WSA:1387589.1387611} with an information flow control
+Bittau:2008:WSA:1387589.1387611}, but using an information flow control
 policy.
@@
 Similarly, control over page tables and protection bits allows us to
-define a |send| syscall that copies pages to our
+define a |send| system call that copies pages to our
 (trusted) runtime queue; and, correspondingly, a |recv| that copies

### 2015-01-15 paper/retrofit.tex
pass over everything except related and conclusion

@@
 security policy (for example, confidential information should not flow to
-a public channel), and the work of specifying the semantics of an information
+a public channel), while the work of specifying the semantics of an information
 flow language involves demonstrating that impermissible flows cannot happen,
-a property called \emph{non-interference}.
+a property called \emph{non-interference}~\cite{Goguen82}.
 %
@@
 presentation, we use a simple, untyped lambda calculus with mutable
-references and fixpoint in place of ECMAScript, to demonstrate some of the key
-properties without including too much detail (and because the embedding really
-does not care about what, exactly, is in the target language); we discuss the proper
-embedding in more detail in Section~\ref{sec:real}.
+references and fixpoint in place of ECMAScript to demonstrate some the key
+properties of the system (and, because the embedding does not care
+about the target language features); we discuss the proper embedding
+in more detail in Section~\ref{sec:real}.
 
@@
 a color copy of this paper, where target language nonterminals are colored \textbf{{\color{red} red}}
-while IFC language nonterminals are colored \textit{{\color{blue} blue}}.
+and IFC language nonterminals are colored \textit{{\color{blue} blue}}.
 
@@
 These operations are all defined with respect to an evaluation context
-|curlyBlueE| that represents the context of the current task which.
+|curlyBlueE| that represents the context of the current task.
 The evaluation context has three important pieces of

### 2015-01-15 paper/conclusion.tex
pass over related and conclusion

@@
 an IFC system for C using hardware isolation.
-By systematically applying ideas from IFC in operating systems to programming languages,
+By systematically applying ideas from IFC in operating systems to
+programming languages for which isolation can be achieved,
 we hope to have elucidated some of the core design principles of coarse-grained,

### 2015-01-15 paper/related.tex
pass over related and conclusion

@@
 One information flow control technique designed to handle legacy code is
-secure multi-execution (SME)~\cite{Devriese:2010}. It runs
+secure multi-execution (SME)~\cite{Devriese:2010}. SME runs
 multiple copies of the program, one per security level, where the semantics of
 I/O interactions is altered. Authors often present
-SME considering one specific programming
+SME in the context of a single, specific programming
 language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
 al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
-details of the underlying language is hidden.  Zanarini et
+details of the underlying language are hidden.  Zanarini et
 al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
 interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
-about which nothing is known except what is inferred from their I/O interactions
+about which nothing is known, except what can be inferred from their interaction
 with the environment. Similar to SME, our approach mediates I/O
@@
 
-One of the primary motivations behind this paper is constructing a practical
-information flow control system for JavaScript.  Some of these systems attempt
-to perform fine-grained information flow control of
-JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
-control can result in fewer false alarms and target legacy code, it comes at the
-cost of complexity (the system must accommodate the entirety of JavaScript's
-semantics~\cite{JSFlow}).
+One of the primary motivations behind this paper is the application of
+information flow control to JavaScript.  Previous systems 
+retrofitted JavaScript with fine-grained
+IFC~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained IFC can result
+in fewer false alarms and target legacy code, it comes at the
+cost of complexity: the system must accommodate the entirety of JavaScript's
+semantics~\cite{JSFlow}.
 %Moreover, the runtime performance cost are sometimes too high, e.g.,
 %higher than 100\%~\cite{JSFlow}.
-Alternatively, coarse-grained
+By contrast, coarse-grained
 approaches to security have also been proposed for the web
-scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
+scenario and tend to have simpler implications~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
 
@@
 The constructs in our IFC language, as well as the behavior of
-inter-thread communication, are reminiscent of distributed systems
-like Erlang~\cite{Armstrong03makingreliable}.  There is a close
+inter-task communication, are reminiscent of distributed systems like
+Erlang~\cite{Armstrong03makingreliable}.  There is a close
 correspondence: in distributed systems, isolation is required due to
 physical constraints; in information flow control, isolation is
-required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
-built an information flow control system on top of Erlang which is quite
-similar to ours.  However, they do not use a floating label system (processes
-can find out when sending a message failed due to a forbidden information flow),
-and they include no security proofs.
+required to enforce non-interference.  Papagiannis et
+al.~\cite{Papagiannis_enforcinguser} built an information flow control
+system on top of Erlang which shares some similarities to ours.
+However, they do not take a floating-label approach (processes can find
+out when sending a message failed due to a forbidden information
+flow), nor do they provide security proofs.
 
-There appears to be limited literature in general techniques for retrofitting
-information flow control to arbitrary languages; however, one time-honored
-technique is defining a fundamental calculus, for which other languages can be
+There is limited work on general techniques for retrofitting
+arbitrary languages with information flow control. However, one time-honored
+technique is to define a fundamental calculus for which other languages can be
 desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
-dependency by showing how various previous systems can be encoded in it; Tse and
+dependency by showing how various previous systems can be encoded in it. Tse and
 Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be

### 2015-01-15 paper/real.tex
reviewer 2 and 3 (first point): isolation is language-specific

@@
 
-In this section, we describe two JavaScript IFC implementations
+Our approach can be used to retrofit any language for which we
+can achieve isolation with information flow control.
+%
+Unfortunately, controlling the external effects of a real-world
+language, as to achieve isolation, is language-specific and varies
+from one language to another.\footnote{
+  Though we apply our framework to several real-world languages, it is
+  conceivable that there are languages for which isolation cannot be
+  easily achieved.
+}
+%
+Indeed, even for a single language (e.g., JavaScript), how one
+achieves isolation may vary according to the language runtime or
+embedding (e.g., server and browser).
+%
+
+In this section, we describe several implementations and their
+approaches to isolation.
+%
+In particular, we describe two JavaScript IFC implementations
 building on the theoretical foundations of this work.
 %
-Furthermore, we consider how our formalism could be applied to the C
-programming language
-and connect it to a previous IFC system for
+Then, we consider how our formalism could be applied to the C
+programming language and connect it to a previous IFC system for
 Haskell.
 %
+
 %% The goal of this section is to show the flexibility of the embedding in settings with

### 2015-01-15 paper/real.tex
reviewer 2: is string too restrictive

@@
 %by same-origin contexts in Blink),
-We remark that our system conservatively restricts
-the kinds of messages that can be exchanged, via |send| (and |sandbox|),
-to string values.
+Our system conservatively restricts the kinds of messages that can be
+exchanged, via |send| (and |sandbox|), to string values.
 %
-(We provide a convenience library which marshalls JSON objects to/from strings.)
 %
@@
 %
+Of course, we provide a convenience library which marshals JSON
+objects to/from strings.
+%
+We remark that this is not unlike existing message-passing JavaScript
+APIs, e.g., \texttt{postMessage}, which impose similar restrictions as
+to avoid sharing references between concurrent code.
 

### 2015-01-15 paper/real.tex
r2; address wrapping question

@@
 While this is safer than simply wrapping unsafe objects, which can
-potentially be exploited to access objects outside the context, adding
-features such as the \textsf{fs} requires the code in the main task to
-ensures that labels are properly propagated and enforced.
+potentially be exploited to access objects outside the context (e.g.,
+as seen with ADSafe, FBJS, and Caja~\cite{taly2011automated,
+maffeis2010object, maffeis2009language}), adding features such as the
+\textsf{fs} requires the code in the main task to ensures that labels
+are properly propagated and enforced.
 %

### 2015-01-15 paper/formal.tex
progress noninter

@@
 configuration that is |l|-equivalent to the first resultant configuration.
+By symmetry, this applies to all intermediate steps from the second configuration
+as well.
+%
+We remark that this notion of non-interfernce is similar to
+\emph{progress sensitive non-interference (PSNI)}, which accounts for
+leakage via progress (or termination) channels, as used for static
+systems~\cite{moore2012precise}.
 
-Our IFC language satisfies TSNI %under a particular
-%scheduling policy.
-%
-%Specifically, we consider the language
+Our IFC language satisfies TSNI 
+(and thus PSNI)
 under the round-robin scheduler

### 2015-01-15 paper/formal.tex
shorten to 20 pages

@@
 %
+\ifextended
 We remark that this notion of non-interfernce is similar to
@@
 systems~\cite{moore2012precise}.
+\fi
 
-Our IFC language satisfies TSNI 
+Our language satisfies TSNI 
+\ifextended
 (and thus PSNI)
+\fi
 under the round-robin scheduler
-|roundrobinf| given in Fig.~\ref{fig:scheduler}.
-
+|roundrobinf| of Fig.~\ref{fig:scheduler}.
+%
 \begin{theorem}[Concurrent IFC language is TSNI]

### 2015-01-15 paper/real.tex
shorten to 20 pages

@@
 potentially be exploited to access objects outside the context (e.g.,
-as seen with ADSafe, FBJS, and Caja~\cite{taly2011automated,
-maffeis2010object, maffeis2009language}), adding features such as the
+as seen with
+\ifextended
+ADSafe, FBJS, and Caja~\cite{taly2011automated, maffeis2010object, maffeis2009language}),
+\else
+ADSafe~\cite{taly2011automated}),
+\fi
+adding features such as the
 \textsf{fs} requires the code in the main task to ensures that labels
@@
 with clearance (which sets an upper bound on the floating label, see
-Section~\ref{sec:clearance}) was incorrect: the clearance
+\appref{sec:clearance}) was incorrect: the clearance
 was restored to the clearance at point of the catch.

### 2015-01-15 paper/related.tex
shorten to 20 pages

@@
 One information flow control technique designed to handle legacy code is
-secure multi-execution (SME)~\cite{Devriese:2010}. SME runs
+secure multi-execution (SME)~\cite{Devriese:2010,Rafnson:2013}. SME runs
 multiple copies of the program, one per security level, where the semantics of
-I/O interactions is altered. Authors often present
-SME in the context of a single, specific programming
-language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
-al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
+I/O interactions is altered.
+Bielova et
+al.~\cite{Biel-etal-11-TR} use a transition system to describe SME, where the
 details of the underlying language are hidden.  Zanarini et
@@
 retrofitted JavaScript with fine-grained
-IFC~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained IFC can result
+\ifextended
+IFC~\cite{Hedin:2012,ConDOM,JSFlow}.
+\else
+IFC~\cite{Hedin:2012,JSFlow}.
+\fi
+While fine-grained IFC can result
 in fewer false alarms and target legacy code, it comes at the
@@
 By contrast, coarse-grained
-approaches to security have also been proposed for the web
-scenario and tend to have simpler implications~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.
+approaches to security
+tend to have simpler implications~\cite{Yip:2009:PBS,DeGroef:2012}.
 
@@
 inter-task communication, are reminiscent of distributed systems like
-Erlang~\cite{Armstrong03makingreliable}.  There is a close
-correspondence: in distributed systems, isolation is required due to
+Erlang~\cite{Armstrong03makingreliable}.
+In distributed systems, isolation is required due to
 physical constraints; in information flow control, isolation is
@@
 al.~\cite{Papagiannis_enforcinguser} built an information flow control
-system on top of Erlang which shares some similarities to ours.
+system on top of Erlang that shares some similarities to ours.
 However, they do not take a floating-label approach (processes can find
